### 2020-06-20 paper_1/paper_1.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The title},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Title}
\author{First Author\textsuperscript{1}\ \& Ernst-August Doelle\textsuperscript{1,2}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: my@email.com}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

\title{The title}

\date{}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R (Version 3.6.1; R Core Team, 2019) and the R-package \emph{papaja} (Version 0.1.0.9942; Aust \& Barth, 2020) for all our analyses.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\endgroup

\end{document}

### 2020-06-22 paper_1/paper_1.Rmd

---
title             : "Through the eyes of the teacher"
shorttitle        : "Visual attention in teaching and learning processes"

author: 
  - name          : "Mandy Klatt"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Egelstraße 2a 04103 Leipzig"
    email         : "mandy.klatt@uni-leipzig.de"
  - name          : "Gregor Kachel"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Leipzig"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

## Participants

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

## Material

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

## Procedure

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

# Results

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

# Discussion

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2020-06-22 paper_1/schrott/Einzeldinge_Paper.Rmd

---
title             : "Einzeldinge Report"
shorttitle        : "Einzeldinge Report"

author: 
  - name          : "Gregor Kachel"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Kiepenheuerallee 5, 14669 Potsdam"
    email         : "kachel@fh-potsdam.de"
  - name          : "Ramiro Glauer"
    affiliation   : "1"
  - name          : "Jan Lonnemann"
    affiliation   : "2"
  - name          : "Frauke Hildebrandt"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "FH Potsdam"
  - id            : "2"
    institution   : "University of Potsdam"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Results and illustrations of pilot testings (pilot A, B & C) for Einzelinge.

keywords          : "Object Individuation"
wordcount         : "x"

bibliography      : ["library.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}

library("papaja")
library("tidyverse")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

## Previous Work
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

## Research Caveats
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

## what this paper is adding to the debate
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

# Study 1 MOCKDATA 
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

## Methods

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

## Participants
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

### Materials, Setting and Equipment
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

### Procedure
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

### Coding
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

### Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

### Results
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

# Discussion
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2020-06-23 paper_1/paper_1.Rmd
update plotting

@@
 
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements.
+The head unit is a measuring device with different sensitive sensors.
+A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
+Infrared light illuminators support the eye tracking sensors which record the eye orientation.
+The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
+The scene camera has a field of view of 90 deg.
+in 16:9 format (82 deg.
+horizontal and 52 deg.
+vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
+The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
+
+The Tobii Pro Glasses 2 software allows for non-screen based recordings of a participants’ attention while moving in real-world settings.
+The recordings of the glasses contain both HD-video from the subject’s perspective as well as the respective gaze data mapped onto the video.
+In order to map multiple recordings to AOIs, it is necessary to import the eye-tracking recordings into the Tobii Pro Analyzer software.
+Also, it is necessary to create a reference image of the scene in which one wishes to plot the gaze data (i.e.
+snapshot).
+Once the snapshot is imported, the gaze recordings of multiple recordings can be mapped to the reference image and analyzed in aggregated form.
+Tobii Pro does not allow to do AOI based analyses within Pro Lab.
+Also, the dependency on snapshot reference images makes this approach impractical when working in different settings, i.e.
+different classrooms with various participants.
+Finally, mapping gaze to people or any moving objects complicated the analyses further.
 

### 2020-06-23 studies/pilot A/plots/plotting_pilotA_030_manual_vs_hand_coding.R

@@ -1,0 +1,47 @@
+
+### PLOTTING PILOT A - 030 - manual coding vs. hand coding
+
+# Gregor KAchel, Mandy Klatt
+# January, 2020
+
+##########################################################################
+### load Libraries / install packages
+##########################################################################
+
+## http://www.eyetracking-r.com/
+
+
+# install.packages("tidyverse")
+# install.packages("lemon")
+
+library(tidyverse) # contains ggplot2, dplyr...and all the other good things
+library(lemon) # necessary for arranging multiple plots next to each other
+
+### MANUAL CODING
+##########################################################################
+### Prepare data event durations and proportion durations looking at Gregor, plant, teddy and computer
+##########################################################################
+
+# read in data while specifying locale allows to set "," 
+data_raw<-read_tsv("./Mandy1_PilotA_data_export_hand_coding_events.tsv", 
+                   locale = locale(decimal_mark = ","))
+
+view(data_raw)
+
+
+# select relevant columns via SELECT
+event_duration <- data_raw  %>% select(
+  'Recording timestamp',
+  Event, 
+  )
+
+ view(event_duration)
+ 
+ 
+# summarize time spend looking at Gregor
+ event_duration_sum <- event_duration %>%
+   group_by(Event) %>%
+   summarize(gregor = sum(B),
+             sumBfoo = sum(B[A=="foo"]))
+ 
+ 

### 2020-06-23 studies/pilot A/plots/plotting_pilotA_031_material_vs_class.R

@@ -1,0 +1,57 @@
+### PLOTTING PILOT A - 031 - material vs. class - automatic mapping
+
+# Gregor KAchel, Mandy Klatt
+# July, 2020
+
+##########################################################################
+### load Libraries / install packages
+##########################################################################
+
+## http://www.eyetracking-r.com/
+
+
+install.packages("tidyverse")
+install.packages("lemon")
+
+library(tidyverse) # contains ggplot2, dplyr...and all the other good things
+library(lemon) # necessary for arranging multiple plots next to each other
+
+### AUTOMATIC MAPPING
+##########################################################################
+### Prepare data TOTAL DURATION and PROPORTION DURATION of looking at AOIs Gregor, plant, teddy and computer
+##########################################################################
+
+# read in data while specifying locale allows to set "," 
+data_raw<-read_tsv("./Mandy1_PilotA_031_metrics_class.tsv", 
+                   locale = locale(decimal_mark = ","))
+
+view(data_raw)
+
+### TOTAL DURATION
+
+# select relevant columns via SELECT
+class_data_NA <- data_raw  %>% select(
+  Total_duration_of_fixations.computer,
+  Total_duration_of_fixations.gregor,
+  Total_duration_of_fixations.plant,
+  Total_duration_of_fixations.teddy
+  )
+
+view(class_data_NA)
+
+# drop rows with NAs
+class_data <- class_data_NA %>% filter(!is.na(Total_duration_of_fixations.computer+
+                                              Total_duration_of_fixations.gregor+
+                                              Total_duration_of_fixations.plant+
+                                              Total_duration_of_fixations.teddy))
+
+view(class_data)
+
+# create new column names that give total duration of looking A, B, Teddy and Urmenschen
+total_duration <- class_data  %>% 
+  rename (Computer = Total_duration_of_fixations.computer,
+          Gregor = Total_duration_of_fixations.gregor,
+          Plant = Total_duration_of_fixations.plant,
+          Teddy = Total_duration_of_fixations.teddy)
+
+view(total_duration)

### 2020-06-23 studies/pilot A/plots/plotting_pilotA_manual_vs_hand_coding.R

@@ -1,43 +1,0 @@
-
-### PLOTTING PILOT A - manual coding vs. hand coding
-
-# Gregor KAchel, Mandy Klatt
-# January, 2020
-
-##########################################################################
-### load Libraries / install packages
-##########################################################################
-
-## http://www.eyetracking-r.com/
-
-
-install.packages("tidyverse")
-install.packages("lemon")
-
-library(tidyverse) # contains ggplot2, dplyr...and all the other good things
-library(lemon) # necessary for arranging multiple plots next to each other
-
-### MANUAL CODING
-##########################################################################
-### Prepare data event durations and proportion durations looking at Gregor, plant, teddy and computer
-##########################################################################
-
-# read in data while specifying locale allows to set "," 
-data_raw<-read_tsv("./Mandy1_PilotA_data_export_hand_coding_events.tsv", 
-                   locale = locale(decimal_mark = ","))
-
-view(data_raw)
-
-
-# select relevant columns via SELECT
-event_duration <- data_raw  %>% select(
-  'Recording timestamp',                                      
-  'Computer timestamp',
-  Event, 
-  )
-
- view(event_duration)
-
-
-
-

### 2020-06-23 studies/pilot A/plots/plotting_pilotA_031_material_vs_class.R
Update plotting_pilotA_031_material_vs_class.R

@@ -47,7 +47,7 @@ class_data <- class_data_NA %>% filter(!is.na(Total_duration_of_fixations.comput
 
 view(class_data)
 
-# create new column names that give total duration of looking A, B, Teddy and Urmenschen
+# create new column names that give total duration of looking Computer, Gregor, Teddy and Plant
 total_duration <- class_data  %>% 
   rename (Computer = Total_duration_of_fixations.computer,
           Gregor = Total_duration_of_fixations.gregor,

### 2020-06-24 studies/pilot A/plots/plotting_pilotA_031_material_vs_class.R
update exposé

@@ -9,12 +9,14 @@
 
 ## http://www.eyetracking-r.com/
 
+if (!require(tidyverse)) install.packages("tidyverse", dep = TRUE)
+if (!require(lemon)) install.packages("lemon", dep = TRUE)
 
-install.packages("tidyverse")
-install.packages("lemon")
-
-library(tidyverse) # contains ggplot2, dplyr...and all the other good things
-library(lemon) # necessary for arranging multiple plots next to each other
+# install.packages("tidyverse")
+# install.packages("lemon")
+# 
+# library(tidyverse) # contains ggplot2, dplyr...and all the other good things
+# library(lemon) # necessary for arranging multiple plots next to each other
 
 ### AUTOMATIC MAPPING
 ##########################################################################

### 2020-06-30 studies/pilot A/plots/plotting_pilotA_031_material_vs_class.R
update plots

@@ -24,7 +24,7 @@ if (!require(lemon)) install.packages("lemon", dep = TRUE)
 ##########################################################################
 
 # read in data while specifying locale allows to set "," 
-data_raw<-read_tsv("./Mandy1_PilotA_031_metrics_class.tsv", 
+data_raw<-read_tsv("./Mandy1_PilotA_031_metrics_AOI.tsv", 
                    locale = locale(decimal_mark = ","))
 
 view(data_raw)
@@ -32,28 +32,130 @@ view(data_raw)
 ### TOTAL DURATION
 
 # select relevant columns via SELECT
-class_data_NA <- data_raw  %>% select(
+data_NA <- data_raw  %>% select(
+  Recording,
+  Toi,
   Total_duration_of_fixations.computer,
   Total_duration_of_fixations.gregor,
   Total_duration_of_fixations.plant,
-  Total_duration_of_fixations.teddy
+  Total_duration_of_fixations.teddy,
+  Total_duration_of_fixations.material
   )
 
-view(class_data_NA)
+view(data_NA)
 
 # drop rows with NAs
-class_data <- class_data_NA %>% filter(!is.na(Total_duration_of_fixations.computer+
+total_duration_data <- data_NA %>% filter(!is.na(Total_duration_of_fixations.computer+
                                               Total_duration_of_fixations.gregor+
                                               Total_duration_of_fixations.plant+
-                                              Total_duration_of_fixations.teddy))
+                                              Total_duration_of_fixations.teddy+
+                                              Total_duration_of_fixations.material))
+view(total_duration_data)
 
-view(class_data)
+# XXXGREGOR: ist hier wirklich nur "Entire Recording" wichtig oder auch die Snapshots als TOIs? 
+# filter only total_duration for time of interest = entire recording to get full data
+total_duration_data <- total_duration_data  %>% filter(
+  Toi == "Entire Recording")
+
+view(total_duration_data)
 
 # create new column names that give total duration of looking Computer, Gregor, Teddy and Plant
-total_duration <- class_data  %>% 
+total_duration <- total_duration_data  %>% 
   rename (Computer = Total_duration_of_fixations.computer,
           Gregor = Total_duration_of_fixations.gregor,
           Plant = Total_duration_of_fixations.plant,
-          Teddy = Total_duration_of_fixations.teddy)
[…]

### 2020-06-30 studies/pilot A/plots/plotting_pilotA_031_material_vs_class.R
exposé & plot

@@ -80,15 +80,14 @@ view(total_duration_long)
 
 ### create an additional data set with proportions of duration
 
-
 # create a new column with name sum_aois that gives the sum of looking at all AOIs
-total_duration <- total_duration  %>% mutate(sum_aois =
+proportion_duration <- total_duration  %>% mutate(sum_aois =
                                                Computer +
                                                Gregor+
                                                Plant+
                                                Teddy+
                                                Material)
-view(total_duration)
+view(proportion_duration)
 
 # create new columns that give proportion of the duration of looking at AOIs
 # relative duration divided by total duration is the proportion
@@ -101,10 +100,10 @@ proportion_duration <- total_duration  %>%
 
 view(proportion_duration)
 
-# # create data set of proportions in long format for plotting
-# proportion_duration_long  <- gather(proportion_duration, AOI, proportion, Computer:Material)
-# 
-# view(proportion_duration_long)
+# create data set of proportions in long format for plotting
+proportion_duration_long  <- gather(proportion_duration, AOI, proportion, Computer:Material)
+
+view(proportion_duration_long)
 
 
 #########################################################
@@ -125,7 +124,8 @@ total.plot.raw <- ggplot(total_duration_long, aes(x = AOI, y = duration, colour 
     "Total_duration_of_fixations.computer" = "Computer", 
     "Total_duration_of_fixations.gregor" = "Gregor",
     "Total_duration_of_fixations.teddy" = "Teddy",
-    "Total_duration_of_fixations.plant" = "Plant"
+    "Total_duration_of_fixations.plant" = "Plant",
+    "Total_duration_of_fixations.material" = "Material"
   ))
 
 total.plot.raw
@@ -144,18 +144,33 @@ prop.plot
 
 ### BARPLOTS
 ### Plot data TOTAL DURATION
-duration_plot <- ggplot(total_duration, aes(x = `AOI:`, y = X5))+
-  geom_bar(stat="identity", width=.5, fill="tomato") + 
-  labs (title = "Total duration (s)", 
-        x = 
-        "Total_duration_of_fixations.computer" = "Computer", 
-        "Total_duration_of_fixations.gregor" = "Gregor",
-        "Total_duration_of_fixations.teddy" = "Teddy",
-        "Total_duration_of_fixations.plant" = "Plant",
-        "Total_duration_of_fixation.material = Material",
-        y = "Total duration (s)")
[…]

### 2020-07-03 paper_1/paper_1.Rmd
update webpage+paper1+exposé

@@
 
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+For the sample recruitment of the subjects (N = 48, experts n = 24, novices n = 24), schools in the city of Leipzig in Saxony were contacted.
+The institutions as well as the subjects were informed in detail about the aim and intention of the dissertation project in advance.
+Participation in the study was voluntary and only took place after written consent has been given.
+
+The selection of the subjects was based on extreme groups, whereby professional experience is the crucial criterion for the selection of experts or novices.
+Novices were recruited as teachers who have been working in the teaching profession for no more than 3 years, whereas experts were considered to have professional experience of 10 years or more (@ Messer & Reusser, 2000).
 
 ## Material
+
+### Eye-tracking equipment
 
@@
 
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+A first important step in conducting Study I was the pilot phase, in which the measuring instruments were tested and evaluated in a Lab with subjects.
+
+After the pilot study, experts (n = 24) and novices (n = 24) were invited to the mobile Lab of the Department of Empirical School- and Classroom Research at the University of Leipzig.
+The two extreme groups were divided into groups of four.
+Subsequently, the subjects were asked to give a 15-minute lesson at six different dates.
+The duration of each appointment was about 2h30min: each extreme group had an 15min briefing, 15min lesson unit, 10min technical preparation and follow-up and 5min buffer/break.
+
+One person of the group acted as a teacher, the other three subjects as a class.
+The respondents representing the class received behavioral instructions to simulate typical events and disturbances in the classroom (e.g.
+putting their heads on the table, chatting, looking at their mobile phones, etc.) The classroom disturbances, divided into active and passive, were displayed as instructions during the lesson for all "students" but not the teacher.
+In order to avoid learning effects, the disturbances in each lesson were distributed pseudo-randomly over the short teaching phase.
+
+By using mobile eye-trackers, the gaze and behavior of the experts and novices was recorded during the lesson.
+In addition, what the participating teachers said was recorded with a portable microphone.
+Other sounds and voices were recorded using an audio recorder installed in the middle of the room.
+Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles.
+One camera was installed to film the class action from the side.
+Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back.
+Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded.
+
+After each recording, the subjects answered classroom management items using validated questionnaires, how present they perceived the teacher, and the teacher should give an assessment of the used classroom management.
+The lessons recorded on video were coded in a post-hoc procedure with a coding software by previously trained raters.
+
+The data on the teacher's attendance behavior obtained through the coding, eye-tracking and audio recordings were linked to the results of the questionnaires.
+The statistical data have been analyzed by using the program RStudio (Link: https://rstudio.com/).
 

### 2020-07-15 paper_1/paper_1.Rmd
introduction + research questions paper_1

--- 2020-06-23 paper_1/paper_1.Rmd
@@
 ```{r setup, include = FALSE}
+
 library("papaja")
@@
 
+# State of research
+
+Teaching and classroom management are multidimensional settings in which teachers have to respond immediately to events as they develop [@barnes2004significance].
+The different interests and abilities of students must be managed in a way that maximizes the active learning time of students and minimizes disruptions whilst teaching.
+Learning to develop such classroom management skills and to teach effectively is a complicated and complex process [@wolff2017see].
+
+During teaching, teachers must be able to select from a variety of visual and acoustic impressions to focus their attention on the essential and to distinguish between relevant and irrelevant events.
+This ability is called professional vision and is a key component of teacher expertise and successful teaching [@barth2017professionelle].
+Eye tracking technology has become a reliable means to study teachers’ visual focus of attention [@pouta2020student; @bogert2016visualperception; @wolff2017see]
+
+Educational research has repeatedly shown that there are differences between experienced and novice teachers in terms of perception and behavioral competencies [@barth2017professionelle; @bogert2016visualperception; @wolff2017see].
+For example, experts direct their attention more often and more evenly to all students, whereas novices only direct their attention to some students.
+The frequency and duration of fixations as eye movement are decisive [@stuermer2017eye].
+Mobile eye-tracking technology has also shown that experienced teachers distribute their focus more efficiently to solve tasks [@jarodzka2010eyes].
+Furthermore, in contrast to novices, experts are able to focus their attention on the entire class and guide the class while giving feedback to individual students and answering questions [@cortina2015low].
+
+## Research questions
+
+The first study is a laboratory study that uses a quasi-experimental cross-sectional study design to investigate whether the experience of teachers has an influence on the perception of and response to disruptions.
+The disturbances are experimentally varied using a previously written script.
+Thus, the aim is to find out whether differences in the allocation of attention between expertise groups can be detected in this controlled context.
+
+In order to answer this question, the hypothesis was formulated that teachers with more professional experience not only notice more disturbances but also notice them faster.
+In the hypothesis, therefore, it is necessary to check what has already been shown in the research literature: In complex teaching situations, experts have a more structured and elaborate professional knowledge than novices in order to perceive and interpret relevant events and to act appropriately [@berliner2001learning; @lachner2016makes].
+
 # Methods
@@
 
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-
 ## Participants
 
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+For the sample recruitment of the subjects (N = 48, experts n = 24, novices n = 24), schools in the city of Leipzig in Saxony were contacted.
+The institutions as well as the subjects were informed in detail about the aim and intention of the dissertation project in advance.
+Participation in the study was voluntary and only took place after written consent has been given.
 
-## Material
+The selection of the subjects was based on extreme groups, whereby professional experience is the crucial criterion for the selection of experts or novices.
+Novices were recruited as teachers who have been working in the teaching profession for no more than 3 years, whereas experts were considered to have professional experience of 10 years or more [@messner2000berufliche].
+
+## Procedure
+
+For this study, lesson units of n = 24 experts and n = 24 novices were recorded by the mobile laboratory of the Department of Empirical School and Classroom Research at the University of Leipzig.
+The two extreme groups were each divided into groups of four, with one group being invited on each of six different dates.
+All participants were asked to hold a 15-minute lesson.
+The duration of each appointment was approximately 2h30min: per extreme group 4 x 15min briefing, 15min lesson units, 10min technical preparation and follow-up and 5min buffer/break.
+
+One person from the group of 4 acted as a teacher, the other three subjects acted as the class.
+The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disturbances in the classroom (e.g.
+putting their heads on the table, chatting, looking at their mobile phones, etc.).
+
+The lesson disturbances were displayed as instructions during the lesson for all "students" but not the teacher.
+In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase.
+In addition, the order of the data collection was taken into account in the analyses and variance caused by order was controlled.
+
+By using mobile eye-trackers, the gaze and behavior of the experts and novices was recorded during the lesson.
+In addition, what the participating teachers said was recorded with a portable microphone.
+Other sounds and voices were recorded with an audio recorder installed in the middle of the laboratory.
+Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles.
+One camera was installed to film the class from the side.
+Two more cameras were installed on the blackboard and at the end of the laboratory to film the teacher and class from the front and back.
+In addition, it the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.
+
+The lessons recorded on video were coded in a post-hoc procedure with a coding software by previously trained raters.
+The statistical data have been analyzed by using the program RStudio [Link: https://rstudio.com/].
+
+## Measures
+
+### Eye-tracking equipment
 
@@
 Finally, mapping gaze to people or any moving objects complicated the analyses further.
-
-## Procedure
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 

### 2021-01-05 studies/2020_Aperol_Git/questionnaire data/gregor beispiele/Symlit_RMTS_pilot1_report/oldfiles_backup/Symlit_RMTS_plotting.Rmd
add examples

---
title: "Einzeldinge - Pilot and Preliminary Data"
author: "Gregor Kachel, Ramiro Glauer, Jan Lonnemann, Frauke Hildebrandt"
date: "03.04.2019"  
output: 
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    number_sections: false
    code_folding: hide
bibliography: library.bib
csl: apa.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

```{r load_packages, include = FALSE}

# install.packages("tidyverse")
# install.packages("ggplot2")

library(ggplot2)
library(tidyverse)

```

```{r part 1-1-1 data, echo = F}

# load tab delimited text file into R; file should be in the same folder as the script for "./" to select it
raw.data<-read.table("./einzeltab.txt",sep="\t", header=T) 
# subsetting only data trials
raw.data<-raw.data[raw.data$content=="data",]
# subsetting only valid trials, exclude drops
raw.data<-raw.data[raw.data$valid=="in",]
# subsetting only first trial, exclude second trial
raw.data<-raw.data[raw.data$trial=="1",]
# subsetting only 12 to 28 months of age
raw.data<-raw.data[raw.data$agem<="30",]
# creating categories by splitting age in the middle
raw.data$splitage <- ifelse(raw.data$agem >= 18, 
                            c("18-27"), c("12-17")) 
# creating categories by making age-groups in the middle
attach(raw.data)
raw.data$agecat[agem <= 18] <- "12mo"
raw.data$agecat[agem > 18 & agem <= 23] <- "18mo"
raw.data$agecat[agem >= 24] <- "24mo"
detach(raw.data)
# factor to numeric
#raw.data$correct<-as.numeric(levels(raw.data$correct))[raw.data$correct] 
# drop levels and check exclusion
raw.data<-droplevels(raw.data)
# str(raw.data)

# creating data test with test, control1 and control2
test.data<-raw.data[raw.data$condition=="test",]
test.data<-droplevels(test.data)
control1.data<-raw.data[raw.data$condition=="control1",]
control1.data<-droplevels(control1.data)
control2.data<-raw.data[raw.data$condition=="control2",]
control2.data<-droplevels(control2.data)

# str(test.data)

```

### Abstract

We collected data from one- and two-year-olds (N = ; ages etc) in a set-up in which an object is established as being special by having the experimenter and child engage with it temporarily. Then, two additional objects are revealed that look just like the first one. All objects are successively placed in three locations in front of the child. While they are identical with regard to surface features, one of them is special due to the shared history the experimenter and child have with it. At test, the child is prompted to retrieve the special one from the set of three indistinguishable objects relying solely on its location. In order to show that one-year-olds can generally succeed in tracking an object in a set of three items, an additional control condition tests children with items that are distinguishable on the basis of surface features (here colour).

### Descriptive Analysis and State of Data Collection

Table with overview of data.
```{r part 1-1-2 data, echo = F}

# load tab delimited text file into R; file should be in the same folder as the script for "./" to select it
raw.data<-read.table("./einzeltab.txt",sep="\t", header=T) 
# subsetting only data trials
raw.data<-raw.data[raw.data$content=="data",]
# subsetting only valid trials, exclude drops
raw.data<-raw.data[raw.data$valid=="in",]
# subsetting only first trial, exclude second trial
 raw.data<-raw.data[raw.data$trial=="1",]
# subsetting only 12 to 28 months of age
raw.data<-raw.data[raw.data$agem<="30",]
# creating categories by splitting age in the middle
raw.data$splitage <- ifelse(raw.data$agem >= 18, 
                            c("18-27"), c("12-17"))

# creating categories by making age-groups in the middle
attach(raw.data)
raw.data$agecat[agem <= 17] <- "12mo"
raw.data$agecat[agem > 17 & agem <= 23] <- "18mo"
raw.data$agecat[agem <= 18] <- "12mo"
raw.data$agecat[agem > 18 & agem <= 23] <- "18mo"
raw.data$agecat[agem >= 24] <- "24mo"
detach(raw.data)

# factor to numeric
raw.data$correct<-as.numeric(levels(raw.data$correct))[raw.data$correct] 
# drop levels and check exclusion
raw.data<-droplevels(raw.data)
# str(raw.data)

overview<-aggregate(raw.data$correct, list(raw.data$agecat, raw.data$condition), mean)
N<-aggregate(raw.data$id, list(raw.data$agecat, raw.data$condition), length)
colnames(N)<- c("Age","Condition","lengthresult")
overview<- cbind(overview, N$lengthresult)
colnames(overview)<- c("Age","Condition","% correct", "N")
overview

# overview<-aggregate(raw.data$correct, list(raw.data$splitage, raw.data$condition), mean)
# N<-aggregate(raw.data$id, list(raw.data$splitage, raw.data$condition), length)
# colnames(N)<- c("Age","Condition","lengthresult")
# overview<- cbind(overview, N$lengthresult)
# colnames(overview)<- c("Age","Condition","% correct", "N")
# overview

```

### Test

```{r plot1, echo = FALSE, fig.cap="TEST CONDITION. Count of children's correct (green) and incorrect (red) choices from a set of three itmes plotted against their age in months. Line depicts smoothed conditional means. Error bars are 95% confidence intervals based on non-parametric bootstraps.One trial per participant.", fig.width = 10, fig.height = 5, fig.scale = 1.5}

#  create plot here 
test.data$correct.factor <- factor(test.data$correct)

g <- ggplot(test.data, aes(x=agem)) + 
  geom_dotplot(aes(fill=correct.factor), stackgroups = TRUE, binwidth = 0.5, binpositions = "all") + 
  geom_smooth(aes(y = correct, col=condition), method="lm") +
  scale_x_continuous(breaks=c(11:30))

g + labs(y="Proportion Correct", 
         x="Age in Months")

```

### Control 1

```{r part 1-1-3 data, echo = F}

# load tab delimited text file into R; file should be in the same folder as the script for "./" to select it
control1.data<-read.table("./einzeltab.txt",sep="\t", header=T) 
# subsetting only data trials
control1.data<-control1.data[control1.data$content=="data",]
# subsetting only valid trials, exclude drops
control1.data<-control1.data[control1.data$valid=="in",]
# subsetting only first trial, exclude second trial
control1.data<-control1.data[control1.data$trial=="1",]
# subsetting only 12 to 28 months of age
control1.data<-control1.data[control1.data$agem<="28",]
# subsetting only trials in the test condition
control1.data<-control1.data[control1.data$condition=="control1",]
# drop levels and check exclusion
control1.data<-droplevels(control1.data)
# creating categories by splitting age in the middle
control1.data$splitage <- ifelse(control1.data$agem >= 18, 
                            c("18-27"), c("12-17")) 
# creating categories by making age-groups in the middle
attach(control1.data)
control1.data$agecat[agem <= 17] <- "12mo"
control1.data$agecat[agem > 17 & agem < 24] <- "18mo"
control1.data$agecat[agem >= 24] <- "24mo"
detach(control1.data)

# factor to numeric
control1.data$correct<-as.numeric(levels(control1.data$correct))[control1.data$correct]

control1.data$correct.factor <- factor(control1.data$correct)

```

```{r plot2, echo = FALSE, fig.cap="CONTROL1 CONDITION. Count of children's correct (green) and incorrect (red) choices from a set of three itmes plotted against their age in months. Line depicts smoothed conditional means. Error bars are 95% confidence intervals based on non-parametric bootstraps.One trial per participant.", fig.width = 10, fig.height = 5, fig.scale = 1.5}
#  create plot here

g <- ggplot(control1.data, aes(x=agem)) + 
  geom_dotplot(aes(fill=correct.factor), stackgroups = TRUE, binwidth = 0.5, binpositions = "all") + 
  geom_smooth(aes(y = correct, col=condition), method="lm") +
  scale_x_continuous(breaks=c(11:30))
g + labs(y="Proportion Correct", 
         x="Age in Months")

```
### Control 2

```{r part 1-1-4 data, echo = F}

# load tab delimited text file into R; file should be in the same folder as the script for "./" to select it
control2.data<-read.table("./einzeltab.txt",sep="\t", header=T) 
# subsetting only data trials
control2.data<-control2.data[control2.data$content=="data",]
# subsetting only valid trials, exclude drops
control2.data<-control2.data[control2.data$valid=="in",]
# subsetting only first trial, exclude second trial
control2.data<-control2.data[control2.data$trial=="1",]
# subsetting only 12 to 28 months of age
control2.data<-control2.data[control2.data$agem<="28",]
# subsetting only trials in the test condition
control2.data<-control2.data[control2.data$condition=="control2",]
# drop levels and check exclusion
control2.data<-droplevels(control2.data)
# creating categories by splitting age in the middle
control2.data$splitage <- ifelse(control2.data$agem >= 18, 
                            c("18-27"), c("12-17")) 
# creating categories by making age-groups in the middle
attach(control2.data)
control2.data$agecat[agem <= 17] <- "12mo"
control2.data$agecat[agem > 17 & agem < 24] <- "18mo"
control2.data$agecat[agem >= 24] <- "24mo"
detach(control2.data)

# factor to numeric
control2.data$correct<-as.numeric(levels(control2.data$correct))[control2.data$correct]

control2.data$correct.factor <- factor(control2.data$correct)

```

```{r plot3, echo = FALSE, fig.cap="control2 CONDITION. Count of children's correct (green) and incorrect (red) choices from a set of three itmes plotted against their age in months. Line depicts smoothed conditional means. Error bars are 95% confidence intervals based on non-parametric bootstraps.One trial per participant.", fig.width = 10, fig.height = 5, fig.scale = 1.5}
#  create plot here

g <- ggplot(control2.data, aes(x=agem)) + 
  geom_dotplot(aes(fill=correct.factor), stackgroups = TRUE, binwidth = 0.5, binpositions = "all") + 
  geom_smooth(aes(y = correct, col=condition), method="lm") +
  scale_x_continuous(breaks=c(11:30))
g + labs(y="Proportion Correct", 
         x="Age in Months")

```

### 2021-01-05 studies/2020_Aperol_Git/questionnaire data/gregor beispiele/eval_wise1920/evaluation_final_WS1920.Rmd
add examples

---
title: Evaluationsbericht BiWi2
author: "DozentIn: `r toString(params$Dozierende)` - WiSe 2019/2020"
date: \today
params:
  logo: ./pictures/logo.png
  cover: ./pictures/cover.png
  iblue: 2b4894
  igray: d4dbde
  Dozierende: "Gregor Kachel"
data: ./data/biwi2_evaldata.txt
documentclass: article
fontsize: 10
papersize: a4paper
output: 
  IReports::businessReport:
    keep_tex: TRUE
    latex_engine: xelatex
    resetStyleFiles: FALSE
header-includes: 
  - \newcommand{\logo}{`r gsub("_", "\\_", params$logo)`}
  - \newcommand{\cover}{`r gsub("_", "\\_", params$cover)`}
  - \newcommand{\iblue}{`r params$iblue`}
  - \newcommand{\igray}{`r params$igray`}
include-before:
  - \renewcommand{\contentsname}{Inhaltsverzeichnis}
  - \renewcommand{\pagename}{Biwi-2 Auswertung}
---

```{r setup, include = FALSE}
# packages from template
library(dplyr)
library(knitr)
library(xtable)
# packages we added
library(ggplot2)
library(ggpubr)
library(tidyverse)

# settings
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```

```{r load data, include=FALSE}
# # load the data from the "data" subfolder
# mock.data<-read.table("./data/biwi2_evaldata.txt",sep="\t", header=T)
# # exclude the sosci variables to get only relevant data
# mock.data<- mock.data %>% filter(scale != "sosci")

mock.data<- read.csv("./data/biwi_WS1920_final.csv", header = TRUE)
# exclude the sosci variables to get only relevant data
mock.data<- mock.data %>% filter(scale != "sosci")
# exclude cases of NAs in the response (column "value)
mock.data<- mock.data %>% drop_na(value)

```

\maketitle
\tableofcontents
\addcontentsline{toc}{section}{Contents}
\clearpage

\section{Allgemeines}
\subsection{Begrüßung}
Sehr geehrte Dozierende,  
Sie erhalten hier die Ergebnisse der automatisierten Auswertung der Evaluation Ihrer Lehrveranstaltungen des Seminars "Praxis- und Studienfeld Schule" aus dem Wintersemester 2019/2020. In diesem Auswertungsbericht werden die Mittelwerte der Erhebungsskalen im Fließtext dargestellt. Daten zu einzelnen Erhebungsitems werden graphisch wiedergegeben. Im gesamten Bericht werden die Daten zu aller Teilnehmenden mit den Daten aus dem Seminar von `r toString(params$Dozierende)` gegenübergestellt.

\subsection{Methodik und Darstellung}
Für die vorliegende Evaluation wurde ein Fragebogen mit ScoSci Survey (Leiner and Leiner 2014) erstellt. Studierende wurden per Mail oder QR-Code eingeladen, den Fragebogen online auszufüllen. Für die Verarbeitung der Daten nutzen wir R (R Core Team 2017) und die Softwarepakete aus der Sammlung tidyverse (Wickham 2017). Für Fragen zur Methodik oder Hintergründen der Erhebung schreiben Sie bitte an empschul[at]uni-leipzig.de.

\section{Demographie}
```{r participants, include=FALSE}

# to create all values for the entire set:
N <- length(unique(mock.data$ID)) # number of participants

# filter by parametervariable, i.e. create a subset for the individual lecturer
ind.data <- mock.data %>% filter(Dozierende == params$Dozierende)

# use the same code to create values for the subset
ind.N <- length(unique(ind.data$ID)) # number of participants for one lecturer

```
In diesem Semester haben insgesamt `r toString(N)` Studierende an der Evaluation des Praktikums Biwi2 teilgenommen. Aus dem Seminar von `r toString(params$Dozierende)` haben `r toString(ind.N)` Studierende den Fragebogen beantwortet. Die Tortendiagramme beziehen sich auf die Daten aller Studierenden.

```{r demographic pie charts side by side, echo=FALSE}

#in order to do demographic we need a dataset containing each subject once, so we filter by one item that everybody answered...THIS NEEDS TO BE DOUBLECHECKED
demo.data <- mock.data %>% filter(scale == "gesamt")

###### Gender Plot All ###
# create percentages for gender; NOTE! the next two lines work no matter how many levels the column has
gendertable <- table(demo.data$Geschlecht)
genderpercs <- as.data.frame(round((gendertable / sum(gendertable)),2))
# Create a basic bar
gender.plot = ggplot(genderpercs, aes(x="", y=Freq, fill=Var1)) + geom_bar(stat="identity", width=1)
# Convert to gender.plot (polar coordinates) and add labels
gender.plot = gender.plot + coord_polar("y", start=0) + geom_text(aes(label = paste0(round(Freq*100), "%")), position = position_stack(vjust = 0.5))
# Remove labels and add title
gender.plot = gender.plot + labs(x = NULL, y = NULL, fill = NULL, title = "Geschlecht")
# Tidy up the theme
gender.plot = gender.plot + theme_classic() + theme(axis.line = element_blank(),
                                                    axis.text = element_blank(),
                                                    axis.ticks = element_blank(),
                                                    plot.title = element_text(hjust = 0.5, color = "#666666"))+
   guides(fill = guide_legend(direction = "vertical"))

###### Studiengang Plot all
# create percentages for school
schooltable <- table(demo.data$Studiengang)
schoolpercs <- as.data.frame(round((schooltable / sum(schooltable)),2))
# Create a basic bar
school.plot = ggplot(schoolpercs, aes(x="", y=Freq, fill=Var1)) + geom_bar(stat="identity", width=1)
# Convert to school.plot (polar coordinates) and add labels
school.plot = school.plot + coord_polar("y", start=0) + geom_text(aes(label = paste0(round(Freq*100), "%")), position = position_stack(vjust = 0.5))
# Remove labels and add title
school.plot = school.plot + labs(x = NULL, y = NULL, fill = NULL, title = "Studiengang")
# Tidy up the theme
school.plot = school.plot + theme_classic() + theme(axis.line = element_blank(),
                                                    axis.text = element_blank(),
                                                    axis.ticks = element_blank(),
                                                    plot.title = element_text(hjust = 0.5, color = "#666666"))+
   guides(fill = guide_legend(direction = "vertical"))

###### Fachsemester Plot all
# create percentages for school
semtable <- table(demo.data$Fachsemester)
sempercs <- as.data.frame(round((semtable / sum(semtable)),2))
# Create a basic bar
sem.plot = ggplot(sempercs, aes(x="", y=Freq, fill=Var1)) + geom_bar(stat="identity", width=1)
# Convert to sem.plot (polar coordinates) and add labels
sem.plot = sem.plot + coord_polar("y", start=0) + geom_text(aes(label = paste0(round(Freq*100), "%")), position = position_stack(vjust = 0.5))
# Remove labels and add title
sem.plot = sem.plot + labs(x = NULL, y = NULL, fill = NULL, title = "Fachsemester")
# Tidy up the theme
sem.plot = sem.plot + theme_classic() + theme(axis.line = element_blank(),
                                              axis.text = element_blank(),
                                              axis.ticks = element_blank(),
                                              plot.title = element_text(hjust = 0.5, color = "#666666")) +
  guides(fill = guide_legend(direction = "vertical", ncol = 2))

# arrange all three plots next to each other ...this needs fixing
ggarrange(gender.plot, sem.plot,school.plot, ncol = 3, nrow = 1, 
          legend = "bottom", common.legend = F)

# Verbesserungsmöglichkeit:
# hier erklärt wie man die label auf die torten schreibt...
# https://www.r-graph-gallery.com/piechart-ggplot2.html

```

\pagebreak
\section{Bewertung des Moduls}
```{r Modul gesamtbewertung für fließtext, include=FALSE}
# filter by parametervariable, i.e. create a subset for the individual lecturer
Modul.data <- mock.data %>% filter(scale == "Modul")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
Modul.data <- Modul.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# Erstelle Mittelwert, min, max, sd der Modulbewertungen
meanModul <- mean(Modul.data$value)
minModul <- min(Modul.data$value)
maxModul <- max(Modul.data$value)
sdModul <- sd(Modul.data$value)
NModul<-length(unique(Modul.data$ID))
# filter by parametervariable, i.e. create a subset for the individual lecturer
ind.Modul.data <- Modul.data %>% filter(Dozierende == params$Dozierende)
# erstelle Mittelwert, min, max, sd for individual lecturer
ind.meanModul <- mean(ind.Modul.data$value)
ind.minModul <- min(ind.Modul.data$value)
ind.maxModul <- max(ind.Modul.data$value)
ind.sdModul <- sd(ind.Modul.data$value)
ind.NModul<-length(unique(ind.Modul.data$ID))
```
Der Mittelwert aller Items zur Evaluation des Moduls beträgt `r round(meanModul, 2)` (min = `r toString(minModul)`; max = `r toString(maxModul)`; SD = `r round(sdModul,2)`; N = `r toString(NModul)`; Lickert-Skala 1-5; 5 = beste Bewertung). Im Seminar von `r toString(params$Dozierende)` wurde das Modul insgesamt mit `r round(ind.meanModul, 2)` (min = `r toString(ind.minModul)`; max = `r toString(ind.maxModul)`; SD = `r round(ind.sdModul,2)`; N = `r toString(ind.NModul)`) bewertet.

```{r Modul horicontal Plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
# filter by parametervariable, i.e. create a subset for the individual lecturer
Modul.data <- mock.data %>% filter(scale == "Modul")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
Modul.data <- Modul.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to stick to the individual vs all style necessary for anonymized feedback in plotting
# we create a new vector from Dozierende that we call "Teilnehmende" and copy the names
# of the name called by the parameter but rename all others to "all"
# now the "fill ="option can use the new column to differentiate all vs parameter dozent

modul.plot.data <- Modul.data %>%
  mutate(Teilnehmende = ifelse(Dozierende == params$Dozierende, toString(params$Dozierende), "Alle Kurse"))
modul.plot.data$Teilnehmende <- as.factor(modul.plot.data$Teilnehmende)

# to create error bars, we need to summarise the data in a seperate dataframe
modul.plot.sd <-modul.plot.data %>% 
  group_by(itemfulltext, Teilnehmende, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot 
modul.plot<-ggplot(data = modul.plot.sd, 
                           aes(x = itemfulltext, y = mean, 
                               group=Teilnehmende, colour = Teilnehmende)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,5)+
  labs(data = modul.plot.data, y = "Ausprägung", x = NULL,
       title="Modulbewertung" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
modul.plot

```

```{r Modul gesamtbewertung Plot, fig.height = 3, fig.width = 5, message = FALSE, warning = FALSE , echo=FALSE}

# filter by parametervariable, i.e. create a subset for the individual lecturer
Modul.data <- mock.data %>% filter(scale == "Modul")
# value sometimes contained text before filtering, we have to convert the numbers to numeric
Modul.data <- Modul.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# to stick to the individual vs all style necessary for anonymized feedback in plotting
# we create a new vector from Dozierende that we call "Teilnehmende" and copy the names
# of the name called by the parameter but rename all others to "all"
# now the "fill ="option can use the new column to differentiate all vs parameter dozent

modul.plot.data <- Modul.data %>%
  mutate(Teilnehmende = ifelse(Dozierende == params$Dozierende, toString(params$Dozierende), "Alle Kurse"))
modul.plot.data$Teilnehmende <- as.factor(modul.plot.data$Teilnehmende)

# to create error bars, we need to summarise the data in a seperate dataframe
modul.plot.sd <-modul.plot.data %>% 
  group_by(item, Teilnehmende, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# THIS IS THREE PLOTS IN ONE - Hooray!
# as we call three plots and two dataframes, the first line requires dummy NULL entries 
modul.plot <- ggplot(data = NULL, mapping = aes(NULL)) +
  # then we call a violin from all data, trim = cut at limits, adjust = makes slender 
  geom_violin(data = Modul.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5),
              mapping = aes(x=item, y = value))+
  # a jitter plot Alle vs Individual (Teilnehmende), 
  geom_jitter(modul.plot.data, width = 0.1, inherit.aes = FALSE, size = 1,
              mapping = aes(x = item, y = value, colour = Teilnehmende))+
  # mean and SD via geom pointrange for all and individual (Teilnehmende)
  geom_crossbar(data = modul.plot.sd, position = "dodge", width = 0.5,
                aes(x=item, y = mean, ymin = mean-se, ymax = mean+se, colour = Teilnehmende))+
  # we can't make the violin transparent, so we change the bakground to white
  theme_light() +
  theme(legend.position="bottom") +
  # axis limits from 1 through 5
  ylim(1,5)+
  # label the plot, also here we have to call the data to get the item names
  labs(data = modul.plot.data, y = "Ausprägung", x = "Item",
       title="Modulbewertung",
       subtitle="Verteilung der Werte je Item und Mittelwerte der Items")
modul.plot

# solid advice on setting figure size in Markdown https://sebastiansauer.github.io/figure_sizing_knitr/

```

\pagebreak
\section{Bewertung des Praktikums}
```{r Praktikum.für fließtext, include=FALSE}
# filter by parametervariable, i.e. create a subset for the individual lecturer
Praktikum.data <- mock.data %>% filter(scale == "Praktikum")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
Praktikum.data <- Praktikum.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# Erstelle Mittelwert, min, max, sd der Praktikumbewertungen
meanPraktikum <- mean(Praktikum.data$value)
minPraktikum <- min(Praktikum.data$value)
maxPraktikum <- max(Praktikum.data$value)
sdPraktikum <- sd(Praktikum.data$value)
NPraktikum<-length(unique(Praktikum.data$ID))
# filter by parametervariable, i.e. create a subset for the individual lecturer
ind.Praktikum.data <- Praktikum.data %>% filter(Dozierende == params$Dozierende)
# erstelle Mittelwert, min, max, sd for individual lecturer
ind.meanPraktikum <- mean(ind.Praktikum.data$value)
ind.minPraktikum <- min(ind.Praktikum.data$value)
ind.maxPraktikum <- max(ind.Praktikum.data$value)
ind.sdPraktikum <- sd(ind.Praktikum.data$value)
ind.NPraktikum<-length(unique(ind.Praktikum.data$ID))
```
Der Mittelwert aller Items zur Evaluation des Praktikums beträgt `r round(meanPraktikum, 2)` (min = `r toString(minPraktikum)`; max = `r toString(maxPraktikum)`; SD = `r round(sdPraktikum,2)`; N = `r toString(NPraktikum)`; Lickert-Skala 1-5; 5 = beste Bewertung). Im Seminar von `r toString(params$Dozierende)` wurde das Praktikum insgesamt mit `r round(ind.meanPraktikum, 2)` (min = `r toString(ind.minPraktikum)`; max = `r toString(ind.maxPraktikum)`; SD = `r round(ind.sdPraktikum,2)`; N = `r toString(ind.NPraktikum)`) bewertet.

```{r Praktikum.horicontal Plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
# filter by parametervariable, i.e. create a subset for the individual lecturer
Praktikum.data <- mock.data %>% filter(scale == "Praktikum")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
Praktikum.data <- Praktikum.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to stick to the individual vs all style necessary for anonymized feedback in plotting
# we create a new vector from Dozierende that we call "Teilnehmende" and copy the names
# of the name called by the parameter but rename all others to "all"
# now the "fill ="option can use the new column to differentiate all vs parameter dozent

Prakitkumplot.data <- Praktikum.data %>%
  mutate(Teilnehmende = ifelse(Dozierende == params$Dozierende, toString(params$Dozierende), "Alle Kurse"))
Prakitkumplot.data$Teilnehmende <- as.factor(Prakitkumplot.data$Teilnehmende)

# to create error bars, we need to summarise the data in a seperate dataframe
Prakitkumplot.sd <-Prakitkumplot.data %>% 
  group_by(itemfulltext, Teilnehmende, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot 
Prakitkumplot.long<-ggplot(data = Prakitkumplot.sd, 
                      aes(x = itemfulltext, y = mean, 
                          group=Teilnehmende, colour = Teilnehmende)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,5)+
  labs(data = Prakitkumplot.data, y = "Ausprägung", x = NULL,
       title="Praktikumsbewertung" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 65))+
  coord_flip()
Prakitkumplot.long

```

```{r Praktikum.gesamtbewertung Plot, fig.height = 3, message = FALSE, warning = FALSE , echo=FALSE}

# filter by parametervariable, i.e. create a subset for the individual lecturer
Praktikum.data <- mock.data %>% filter(scale == "Praktikum")
# value sometimes contained text before filtering, we have to convert the numbers to numeric
Praktikum.data <- Praktikum.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# to stick to the individual vs all style necessary for anonymized feedback in plotting
# we create a new vector from Dozierende that we call "Teilnehmende" and copy the names
# of the name called by the parameter but rename all others to "all"
# now the "fill ="option can use the new column to differentiate all vs parameter dozent

Praktikum.plot.data <- Praktikum.data %>%
  mutate(Teilnehmende = ifelse(Dozierende == params$Dozierende, toString(params$Dozierende), "Alle Kurse"))
Praktikum.plot.data$Teilnehmende <- as.factor(Praktikum.plot.data$Teilnehmende)

# to create error bars, we need to summarise the data in a seperate dataframe
Praktikum.plot.sd <-Praktikum.plot.data %>% 
  group_by(item, Teilnehmende, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# THIS IS THREE PLOTS IN ONE - Hooray!
# as we call three plots and two dataframes, the first line requires dummy NULL entries 
Praktikum.plot <- ggplot(data = NULL, mapping = aes(NULL)) +
  # then we call a violin from all data, trim = cut at limits, adjust = makes slender 
  geom_violin(data = Praktikum.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5),
              mapping = aes(x=item, y = value))+
  # a jitter plot Alle vs Individual (Teilnehmende), 
  geom_jitter(Praktikum.plot.data, width = 0.1, inherit.aes = FALSE, size = 1,
              mapping = aes(x = item, y = value, colour = Teilnehmende))+
  # mean and SD via geom pointrange for all and individual (Teilnehmende)
  geom_crossbar(data = Praktikum.plot.sd, position = "dodge", width = 0.5,
                aes(x=item, y = mean, ymin = mean-se, ymax = mean+se, colour = Teilnehmende))+
  # we can't make the violin transparent, so we change the bakground to white
  theme_light() +
  theme(legend.position="bottom") +
  # axis limits from 1 through 5
  ylim(1,5)+
  # label the plot, also here we have to call the data to get the item names
  labs(data = Praktikum.plot.data, y = "Ausprägung", x = "Item",
       title="Praktikumsbewertung",
       subtitle="Verteilung der Werte je Item und Mittelwerte der Items")
Praktikum.plot

# solid advice on setting figure size in Markdown https://sebastiansauer.github.io/figure_sizing_knitr/

```

\pagebreak
\section{Bewertung der Veranstaltung}
```{r Veranstaltung.für fließtext, include=FALSE}
# filter by parametervariable, i.e. create a subset for the individual lecturer
Veranstaltung.data <- mock.data %>% filter(scale == "Veranstaltung")
Veranstaltung.data <- Veranstaltung.data %>% filter(value != "NA")
Veranstaltung.data <- Veranstaltung.data %>% filter(item != "OPT-OUT Option")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
Veranstaltung.data <- Veranstaltung.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# Erstelle Mittelwert, min, max, sd der Veranstaltungbewertungen
meanVeranstaltung <- mean(Veranstaltung.data$value)
minVeranstaltung <- min(Veranstaltung.data$value)
maxVeranstaltung <- max(Veranstaltung.data$value)
sdVeranstaltung <- sd(Veranstaltung.data$value)
NVeranstaltung<-length(unique(Veranstaltung.data$ID))
# filter by parametervariable, i.e. create a subset for the individual lecturer
ind.Veranstaltung.data <- Veranstaltung.data %>% filter(Dozierende == params$Dozierende)
# erstelle Mittelwert, min, max, sd for individual lecturer
ind.meanVeranstaltung <- mean(ind.Veranstaltung.data$value)
ind.minVeranstaltung <- min(ind.Veranstaltung.data$value)
ind.maxVeranstaltung <- max(ind.Veranstaltung.data$value)
ind.sdVeranstaltung <- sd(ind.Veranstaltung.data$value)
ind.NVeranstaltung<-length(unique(ind.Veranstaltung.data$ID))
```
Der Mittelwert aller Items zur Evaluation des Veranstaltungs beträgt `r round(meanVeranstaltung, 2)` (min = `r toString(minVeranstaltung)`; max = `r toString(maxVeranstaltung)`; SD = `r round(sdVeranstaltung,2)`; N = `r toString(NVeranstaltung)`; Lickert-Skala 1-5; 5 = beste Bewertung). Im Seminar von `r toString(params$Dozierende)` wurde das Veranstaltung insgesamt mit `r round(ind.meanVeranstaltung, 2)` (min = `r toString(ind.minVeranstaltung)`; max = `r toString(ind.maxVeranstaltung)`; SD = `r round(ind.sdVeranstaltung,2)`; N = `r toString(ind.NVeranstaltung)`) bewertet.

```{r Veranstaltung.horicontal Plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
# filter by parametervariable, i.e. create a subset for the individual lecturer
Veranstaltung.data <- mock.data %>% filter(scale == "Veranstaltung")
Veranstaltung.data <- Veranstaltung.data %>% filter(item != "OPT-OUT Option")
Veranstaltung.data <- Veranstaltung.data %>% filter(value != "NA")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
Veranstaltung.data <- Veranstaltung.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to stick to the individual vs all style necessary for anonymized feedback in plotting
# we create a new vector from Dozierende that we call "Teilnehmende" and copy the names
# of the name called by the parameter but rename all others to "all"
# now the "fill ="option can use the new column to differentiate all vs parameter dozent

Veranstaltung.plot.data <- Veranstaltung.data %>%
  mutate(Teilnehmende = ifelse(Dozierende == params$Dozierende, toString(params$Dozierende), "Alle Kurse"))
Veranstaltung.plot.data$Teilnehmende <- as.factor(Veranstaltung.plot.data$Teilnehmende)

# to create error bars, we need to summarise the data in a seperate dataframe
Veranstaltung.plot.sd <-Veranstaltung.plot.data %>% 
  group_by(itemfulltext, Teilnehmende, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot 
Veranstaltung.plot.long<-ggplot(data = Veranstaltung.plot.sd, 
                                aes(x = itemfulltext, y = mean, 
                                    group=Teilnehmende, colour = Teilnehmende)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  theme(legend.position="bottom") +
  ylim(1,5)+
  labs(data = Veranstaltung.plot.data, y = "Ausprägung", x = NULL,
       title="Veranstaltungsbewertung" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 65))+
  coord_flip()
Veranstaltung.plot.long

```

```{r Veranstaltung.gesamtbewertung Plot, fig.height = 3, message = FALSE, warning = FALSE , echo=FALSE}

# filter by parametervariable, i.e. create a subset for the individual lecturer
Veranstaltung.data <- mock.data %>% filter(scale == "Veranstaltung")
Veranstaltung.data <- Veranstaltung.data %>% filter(item != "OPT-OUT Option")
# value sometimes contained text before filtering, we have to convert the numbers to numeric
Veranstaltung.data <- Veranstaltung.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# to stick to the individual vs all style necessary for anonymized feedback in plotting
# we create a new vector from Dozierende that we call "Teilnehmende" and copy the names
# of the name called by the parameter but rename all others to "all"
# now the "fill ="option can use the new column to differentiate all vs parameter dozent

Veranstaltung.plot.data <- Veranstaltung.data %>%
  mutate(Teilnehmende = ifelse(Dozierende == params$Dozierende, toString(params$Dozierende), "Alle Kurse"))
Veranstaltung.plot.data$Teilnehmende <- as.factor(Veranstaltung.plot.data$Teilnehmende)

# to create error bars, we need to summarise the data in a seperate dataframe
Veranstaltung.plot.sd <-Veranstaltung.plot.data %>% 
  group_by(item, Teilnehmende, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# THIS IS THREE PLOTS IN ONE - Hooray!
# as we call three plots and two dataframes, the first line requires dummy NULL entries 
Veranstaltung.plot <- ggplot(data = NULL, mapping = aes(NULL)) +
  # then we call a violin from all data, trim = cut at limits, adjust = makes slender 
  geom_violin(data = Veranstaltung.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5),
              mapping = aes(x=item, y = value))+
  # a jitter plot Alle vs Individual (Teilnehmende), 
  geom_jitter(Veranstaltung.plot.data, width = 0.1, inherit.aes = FALSE, size = 1,
              mapping = aes(x = item, y = value, colour = Teilnehmende))+
  # mean and SD via geom pointrange for all and individual (Teilnehmende)
  geom_crossbar(data = Veranstaltung.plot.sd, position = "dodge", width = 0.5,
                aes(x=item, y = mean, ymin = mean-se, ymax = mean+se, colour = Teilnehmende))+
  # we can't make the violin transparent, so we change the bakground to white
  theme_light() +
  theme(legend.position="bottom") +
  # axis limits from 1 through 5
  ylim(1,5)+
  # label the plot, also here we have to call the data to get the item names
  labs(data = Veranstaltung.plot.data, y = "Ausprägung", x = "Item",
       title="Veranstaltungsbewertung",
       subtitle="Verteilung der Werte je Item und Mittelwerte der Items")
Veranstaltung.plot

```

\pagebreak
\section{Bewertung des Portfolios}
```{r Portfolio.für fließtext, include=FALSE}
# filter by parametervariable, i.e. create a subset for the individual lecturer
Portfolio.data <- mock.data %>% filter(scale == "Portfolio")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
Portfolio.data <- Portfolio.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# Erstelle Mittelwert, min, max, sd der Portfoliobewertungen
meanPortfolio <- mean(Portfolio.data$value)
minPortfolio <- min(Portfolio.data$value)
maxPortfolio <- max(Portfolio.data$value)
sdPortfolio <- sd(Portfolio.data$value)
NPortfolio<-length(unique(Portfolio.data$ID))
# filter by parametervariable, i.e. create a subset for the individual lecturer
ind.Portfolio.data <- Portfolio.data %>% filter(Dozierende == params$Dozierende)
# erstelle Mittelwert, min, max, sd for individual lecturer
ind.meanPortfolio <- mean(ind.Portfolio.data$value)
ind.minPortfolio <- min(ind.Portfolio.data$value)
ind.maxPortfolio <- max(ind.Portfolio.data$value)
ind.sdPortfolio <- sd(ind.Portfolio.data$value)
ind.NPortfolio<-length(unique(ind.Portfolio.data$ID))
```
Der Mittelwert aller Items zur Evaluation des Portfolios beträgt `r round(meanPortfolio, 2)` (min = `r toString(minPortfolio)`; max = `r toString(maxPortfolio)`; SD = `r round(sdPortfolio,2)`; N = `r toString(NPortfolio)`; Lickert-Skala 1-5; 5 = beste Bewertung). Im Seminar von `r toString(params$Dozierende)` wurde das Portfolio insgesamt mit `r round(ind.meanPortfolio, 2)` (min = `r toString(ind.minPortfolio)`; max = `r toString(ind.maxPortfolio)`; SD = `r round(ind.sdPortfolio,2)`; N = `r toString(ind.NPortfolio)`) bewertet.

```{r Portfolio.horicontal Plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
# filter by parametervariable, i.e. create a subset for the individual lecturer
Portfolio.data <- mock.data %>% filter(scale == "Portfolio")
Portfolio.data <- Portfolio.data %>% filter(item != "OPT-OUT Option")
Portfolio.data <- Portfolio.data %>% filter(value != "NA")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
Portfolio.data <- Portfolio.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to stick to the individual vs all style necessary for anonymized feedback in plotting
# we create a new vector from Portfolio that we call "Teilnehmende" and copy the names
# of the name called by the parameter but rename all others to "all"
# now the "fill ="option can use the new column to differentiate all vs parameter dozent
# Portfolio --> Portfolio

Portfolio.plot.data <- Portfolio.data %>%
  mutate(Teilnehmende = ifelse(Dozierende == params$Dozierende, toString(params$Dozierende), "Alle Kurse"))
Portfolio.plot.data$Teilnehmende <- as.factor(Portfolio.plot.data$Teilnehmende)

# to create error bars, we need to summarise the data in a seperate dataframe
Portfolio.plot.sd <-Portfolio.plot.data %>% 
  group_by(itemfulltext, Teilnehmende, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot 
Portfolio.plot.long<-ggplot(data = Portfolio.plot.sd, 
                             aes(x = itemfulltext, y = mean, 
                                 group=Teilnehmende, colour = Teilnehmende)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  theme(legend.position="bottom") +
  ylim(1,5)+
  labs(data = Portfolio.plot.data, y = "Ausprägung", x = NULL,
       title="Portfoliobewertung" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 50))+
  coord_flip()
Portfolio.plot.long

```

```{r Portfolio.gesamtbewertung Plot, fig.height = 3, fig.width = 5, message = FALSE, warning = FALSE , echo=FALSE}

# filter by parametervariable, i.e. create a subset for the individual lecturer
Portfolio.data <- mock.data %>% filter(scale == "Portfolio")
Portfolio.data <- Portfolio.data %>% filter(item != "OPT-OUT Option")
# value sometimes contained text before filtering, we have to convert the numbers to numeric
Portfolio.data <- Portfolio.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# to stick to the individual vs all style necessary for anonymized feedback in plotting
# we create a new vector from Portfolio that we call "Teilnehmende" and copy the names
# of the name called by the parameter but rename all others to "all"
# now the "fill ="option can use the new column to differentiate all vs parameter dozent

Portfolio.plot.data <- Portfolio.data %>%
  mutate(Teilnehmende = ifelse(Dozierende == params$Dozierende, toString(params$Dozierende), "Alle Kurse"))
Portfolio.plot.data$Teilnehmende <- as.factor(Portfolio.plot.data$Teilnehmende)

# to create error bars, we need to summarise the data in a seperate dataframe
Portfolio.plot.sd <-Portfolio.plot.data %>% 
  group_by(item, Teilnehmende, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# THIS IS THREE PLOTS IN ONE - Hooray!
# as we call three plots and two dataframes, the first line requires dummy NULL entries 
Portfolio.plot <- ggplot(data = NULL, mapping = aes(NULL)) +
  # then we call a violin from all data, trim = cut at limits, adjust = makes slender 
  geom_violin(data = Portfolio.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5),
              mapping = aes(x=item, y = value))+
  # a jitter plot Alle vs Individual (Teilnehmende), 
  geom_jitter(Portfolio.plot.data, width = 0.1, inherit.aes = FALSE, size = 1,
              mapping = aes(x = item, y = value, colour = Teilnehmende))+
  # mean and SD via geom pointrange for all and individual (Teilnehmende)
  geom_crossbar(data = Portfolio.plot.sd, position = "dodge", width = 0.5,
                aes(x=item, y = mean, ymin = mean-se, ymax = mean+se, colour = Teilnehmende))+
  # we can't make the violin transparent, so we change the bakground to white
  theme_light() +
  theme(legend.position="bottom") +
  # axis limits from 1 through 5
  ylim(1,5)+
  # label the plot, also here we have to call the data to get the item names
  labs(data = Portfolio.plot.data, y = "Ausprägung", x = "Item",
       title="Portfoliobewertung",
       subtitle="Verteilung der Werte je Item und Mittelwerte der Items")
  Portfolio.plot

```

\pagebreak
\section{Bewertung der Dozierenden}
```{r Dozierende.für fließtext, include=FALSE}
# filter by parametervariable, i.e. create a subset for the individual lecturer
Dozierende.data <- mock.data %>% filter(scale == "Dozent")
Dozierende.data <- Dozierende.data %>% filter(item != "OPT-OUT Option")
Dozierende.data <- Dozierende.data %>% filter(value != "NA")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
Dozierende.data <- Dozierende.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# Erstelle Mittelwert, min, max, sd der Dozierendebewertungen
meanDozierende <- mean(Dozierende.data$value)
minDozierende <- min(Dozierende.data$value)
maxDozierende <- max(Dozierende.data$value)
sdDozierende <- sd(Dozierende.data$value)
NDozierende<-length(unique(Dozierende.data$ID))
# filter by parametervariable, i.e. create a subset for the individual lecturer
ind.Dozierende.data <- Dozierende.data %>% filter(Dozierende == params$Dozierende)
# erstelle Mittelwert, min, max, sd for individual lecturer
ind.meanDozierende <- mean(ind.Dozierende.data$value)
ind.minDozierende <- min(ind.Dozierende.data$value)
ind.maxDozierende <- max(ind.Dozierende.data$value)
ind.sdDozierende <- sd(ind.Dozierende.data$value)
ind.NDozierende<-length(unique(ind.Dozierende.data$ID))
```
Der Mittelwert aller Items zur Evaluation der Dozierenden beträgt `r round(meanDozierende, 2)` (min = `r toString(minDozierende)`; max = `r toString(maxDozierende)`; SD = `r round(sdDozierende,2)`; N = `r toString(NDozierende)`; Lickert-Skala 1-5; 5 = beste Bewertung). Im Seminar von `r toString(params$Dozierende)` wurde der/die DozentIn insgesamt mit `r round(ind.meanDozierende, 2)` (min = `r toString(ind.minDozierende)`; max = `r toString(ind.maxDozierende)`; SD = `r round(ind.sdDozierende,2)`; N = `r toString(ind.NDozierende)`) bewertet.

```{r Dozierende.horicontal Plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
# filter by parametervariable, i.e. create a subset for the individual lecturer
Dozierende.data <- mock.data %>% filter(scale == "Dozent")
Dozierende.data <- Dozierende.data %>% filter(item != "OPT-OUT Option")
Dozierende.data <- Dozierende.data %>% filter(value != "NA")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
Dozierende.data <- Dozierende.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# to stick to the individual vs all style necessary for anonymized feedback in plotting
# we create a new vector from Dozierende that we call "Teilnehmende" and copy the names
# of the name called by the parameter but rename all others to "all"
# now the "fill ="option can use the new column to differentiate all vs parameter dozent
# Dozierende --> Portfolio

Dozierende.plot.data <- Dozierende.data %>%
  mutate(Teilnehmende = ifelse(Dozierende == params$Dozierende, toString(params$Dozierende), "Alle Kurse"))
Dozierende.plot.data$Teilnehmende <- as.factor(Dozierende.plot.data$Teilnehmende)

# to create error bars, we need to summarise the data in a seperate dataframe
Dozierende.plot.sd <-Dozierende.plot.data %>% 
  group_by(itemfulltext, Teilnehmende, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot 
Dozierende.plot.long<-ggplot(data = Dozierende.plot.sd, 
                                aes(x = itemfulltext, y = mean, 
                                    group=Teilnehmende, colour = Teilnehmende)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  theme(legend.position="bottom") +
  ylim(1,5)+
  labs(data = Dozierende.plot.data, y = "Ausprägung", x = NULL,
       title="Dozierendenbewertung" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
Dozierende.plot.long

```

```{r Dozierende.gesamtbewertung Plot, fig.height = 3, message = FALSE, warning = FALSE , echo=FALSE}

# filter by parametervariable, i.e. create a subset for the individual lecturer
Dozierende.data <- mock.data %>% filter(scale == "Dozent")
Dozierende.data <- Dozierende.data %>% filter(item != "OPT-OUT Option")
# value sometimes contained text before filtering, we have to convert the numbers to numeric
Dozierende.data <- Dozierende.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# to stick to the individual vs all style necessary for anonymized feedback in plotting
# we create a new vector from Dozierende that we call "Teilnehmende" and copy the names
# of the name called by the parameter but rename all others to "all"
# now the "fill ="option can use the new column to differentiate all vs parameter Dozeierende

Dozierende.plot.data <- Dozierende.data %>%
  mutate(Teilnehmende = ifelse(Dozierende == params$Dozierende, toString(params$Dozierende), "Alle Kurse"))
Dozierende.plot.data$Teilnehmende <- as.factor(Dozierende.plot.data$Teilnehmende)

# to create error bars, we need to summarise the data in a seperate dataframe
Dozierende.plot.sd <-Dozierende.plot.data %>% 
  group_by(item, Teilnehmende, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# THIS IS THREE PLOTS IN ONE - Hooray!
# as we call three plots and two dataframes, the first line requires dummy NULL entries 
Dozierende.plot <- ggplot(data = NULL, mapping = aes(NULL)) +
  # then we call a violin from all data, trim = cut at limits, adjust = makes slender 
  geom_violin(data = Dozierende.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5),
              mapping = aes(x=item, y = value))+
  # a jitter plot Alle vs Individual (Teilnehmende), 
  geom_jitter(Dozierende.plot.data, width = 0.1, inherit.aes = FALSE, size = 1,
              mapping = aes(x = item, y = value, colour = Teilnehmende))+
  # mean and SD via geom pointrange for all and individual (Teilnehmende)
  geom_crossbar(data = Dozierende.plot.sd, position = "dodge", width = 0.5,
                aes(x=item, y = mean, ymin = mean-se, ymax = mean+se, colour = Teilnehmende))+
  # we can't make the violin transparent, so we change the bakground to white
  theme_light() +
  theme(legend.position="bottom") +
  # axis limits from 1 through 5
  ylim(1,5)+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  # label the plot, also here we have to call the data to get the item names
  labs(data = Dozierende.plot.data, y = "Ausprägung", x = "Item",
       title="Dozierendenbewertung",
       subtitle="Verteilung der Werte je Item und Mittelwerte der Items")
Dozierende.plot

```

\pagebreak
\section{Schulnote für die Veranstaltung}
```{r Gesamtbewertung, include=FALSE}

# filter des Items Gesamtbewertung
Benotung.data <- mock.data %>% filter(item == "Benotung")

# value sometimes contains text, we have to convert the numbers to numeric, this is complicated due to the comma
Benotung.data <- Benotung.data %>%  mutate(value = as.numeric(sub(",", ".", value, fixed = TRUE)))

# Erstelle Mittelwert, min, max, sd der Benotung
meangrade <- mean(Benotung.data$value)
mingrade <- min(Benotung.data$value)
maxgrade <- max(Benotung.data$value)
sdgrade <- sd(Benotung.data$value)
Ngrade<-length(unique(Benotung.data$ID))
# filter by parametervariable, i.e. create a subset for the individual lecturer
ind.Benotung.data <- Benotung.data %>% filter(Dozierende == params$Dozierende)
# erstelle Mittelwert, min, max, sd for individual lecturer
ind.meangrade <- mean(ind.Benotung.data$value)
ind.mingrade <- min(ind.Benotung.data$value)
ind.maxgrade <- max(ind.Benotung.data$value)
ind.sdgrade <- sd(ind.Benotung.data$value)
ind.Ngrade<-length(unique(ind.Benotung.data$ID))

```
Die Teilnehmenden bewerteten die Veranstaltung mit einer Gesamtnote von `r round(meangrade, 2)` (min = `r toString(mingrade)`; max = `r toString(maxgrade)`; SD = `r round(sdgrade,2)`; N = `r toString(Ngrade)`; Schulnoten 1-6). Im Seminar von `r toString(params$Dozierende)` wurde die Veranstaltung mit einer Gesamtnote von `r round(ind.meangrade, 2)` (min = `r toString(ind.mingrade)`; max = `r toString(ind.maxgrade)`; SD = `r round(ind.sdgrade,2)`; N = `r toString(ind.Ngrade)`) bewertet.

\section{Angaben zu Fehlzeiten}
```{r Abwesenheit data prep, echo=FALSE}

Abwesenheit.count.data <- mock.data %>% filter(scale == "Abwesenheit")
Abwesenheit.count.data <- Abwesenheit.count.data %>% filter(item == "Anzahl")
# value sometimes contained text before filtering, we have to convert the numbers to numeric

Abwesenheit.count.data <- Abwesenheit.count.data %>%  mutate(value = as.numeric(as.character(factor(value))))
# Erstelle Mittelwert, min, max, sd der Modulbewertungen
meanAbwesenheit <- mean(Abwesenheit.count.data$value)
minAbwesenheit <- min(Abwesenheit.count.data$value)
maxAbwesenheit <- max(Abwesenheit.count.data$value)
sdAbwesenheit <- sd(Abwesenheit.count.data$value)
NAbwesenheit<-length(unique(Abwesenheit.count.data$ID))
# filter by parametervariable, i.e. create a subset for the individual lecturer
Abwesenheit.ind.count.data <- Abwesenheit.count.data %>% filter(Dozierende == params$Dozierende)
# erstelle Mittelwert, min, max, sd for individual lecturer
ind.meanAbwesenheit <- mean(Abwesenheit.ind.count.data$value)
ind.minAbwesenheit <- min(Abwesenheit.ind.count.data$value)
ind.maxAbwesenheit <- max(Abwesenheit.ind.count.data$value)
ind.sdAbwesenheit <- sd(Abwesenheit.ind.count.data$value)
ind.NAbwesenheit<-length(unique(Abwesenheit.ind.count.data$ID))

# optionen abwesenheit for  plotting
Abwesenheitsoptionen.data <- mock.data %>% filter(scale == "Abwesenheit")
Abwesenheitsoptionen.data <- Abwesenheitsoptionen.data %>% mutate(value = ifelse(value == "TRUE", "1", "0"))
Abwesenheitsoptionen.data <- Abwesenheitsoptionen.data %>% filter(item != "Anzahl")
Abwesenheitsoptionen.data <- Abwesenheitsoptionen.data %>%  mutate(value = as.numeric(as.character(factor(value))))
Abwesenheitsoptionen.data <- Abwesenheitsoptionen.data %>% filter(Dozierende == params$Dozierende)
# pro option Summieren um die Daten zum PLotten zu erstellen
Abwesenheit.plot.data <- Abwesenheitsoptionen.data %>% 
  group_by(item) %>%
  summarise(
    sum = sum(value),
         )

# filter der Items Warumfehlzeiten	
Abwesenheit.open.data <- mock.data %>% filter(scale == "offen")
Abwesenheit.open.data <- Abwesenheit.open.data %>% filter(value != "NA")
Abwesenheit.open.data <- Abwesenheit.open.data %>% filter(Dozierende == params$Dozierende)
# filter Abwesenheit.open.data
Abwesenheit.open.data <- Abwesenheit.open.data %>% filter(itemfulltext != "Was hätten Sie gern im Vorfeld des Praktikums geübt?")

```
Im allgemeinen gaben die Studierenden an, dass sie bei `r round(meanAbwesenheit, 2)` Veranstaltungen (min = `r toString(minAbwesenheit)`; max = `r toString(maxAbwesenheit)`; SD = `r round(sdAbwesenheit,2)`; N = `r toString(NAbwesenheit)` abwesend waren. Im Kurs von `r toString(params$Dozierende)` waren die Studierenden nach eigenen Angaben bei `r round(ind.meanAbwesenheit, 2)` Veranstaltungen  (min = `r toString(ind.minAbwesenheit)`; max = `r toString(ind.maxAbwesenheit)`; SD = `r round(ind.sdAbwesenheit,2)`; N = `r toString(ind.NAbwesenheit)`) abwesend. Auf eine offene Frage nach Gründen antworteten die Studierenden im Kurs von `r toString(params$Dozierende)` mit:

\vspace{5mm}
__`r toString(print(Abwesenheit.open.data$value, quote = TRUE))`__

\vspace{5mm}\
Weiterhin wurden Gründe für Abwesenheiten mit verschiedenen Antwortoptionen erhoben, wobei Mehrfachnennungen möglich waren. Im folgenden wird die Anzahl der Nennungen für alle Optionen im Kurs von `r toString(params$Dozierende)` angegeben (N = `r toString(ind.NAbwesenheit)`).

\vspace{5mm}
```{r Abwesenheit Plot,  fig.height = 3, message = FALSE, warning = FALSE , echo=FALSE}

# and here comes the long plot 
Abwesenheit.plot.long<-ggplot(data = Abwesenheit.plot.data, 
                             aes(x = item, y = sum)) +
  geom_point() +
  theme_light() +
  labs(y = "Gründe", x = NULL,
       title="Gründe für Abwesenheit" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
Abwesenheit.plot.long

```

\section{Übungswünsche}
```{r offene items, include=FALSE}
# filter der Items Warumfehlzeiten	
open.data <- mock.data %>% filter(scale == "offen")
open.data <- open.data %>% filter(value != "NA")
open.data <- open.data %>% filter(Dozierende == params$Dozierende)
# filter fehlzeitengruende.data
fehlzeitengruende.data <- open.data %>% filter(itemfulltext != "Was hätten Sie gern im Vorfeld des Praktikums geübt?")
# filter uebungswuensche.data
uebungswuensche.data <- open.data %>% filter(itemfulltext != "Was waren die Gründe für Ihre Fehlzeiten?")

```
Auf die Frage "Was hätten Sie gern im Vorfeld des Praktikums geübt?" antworteten die Studierenden im Kurs von `r toString(params$Dozierende)` mit:

\vspace{5mm}
__`r toString(print(uebungswuensche.data$value, quote = TRUE))`__

### 2021-01-05 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
add examples

---
title: "Pilot study _Aperol_: questionnaire data"
author: "Mandy Klatt, Gregor Kachel and Anne Deiglmayr"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### HOW TO PREPARE DATA IN EXCEL ###
# use filter to select only lines with an ID in it 
# (i.e. exclude all empty lines or lines with na, ?, x, etc)
# select all columns except the columns for comments
# copy/paste into a new spreadsheet
# click "save as" and choose file type "tab-delimited-text"
####################################

# load tab delimited text file into R; 
# file should be in a subfolder named "data" for the script to select it
raw.data<-read.table("./data/SymLit_RMTS_subjectlist_251220.txt",sep="\t", header=T)

# loading packages
# if a package is not installed on the current machine, it will install it
if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

# # change data structure: everything is turned into factors except for 
# main.data <- raw.data %>%
#   filter(what == "data"& valid == 1)  %>%
#   mutate(across(!correct&!agem&!aged, as.factor),
#          correct = as.integer(correct))

```

# Short Summary
This report provides a summary of the first pilot ran for SymLit_RMTS. Our aim for Pilot1 was to evaluate whether the tasks we are planning to use for SymLit_RMTS are appropriate for three- and four-year-old children. In a between-subjects design, three- and four-year-old children saw either a communicative framing of the task or a non-communicative task (condition (comm; non-comm) x agegroup (3yo; 4yo). Children were tested via online video calls. Since we were primarily interested in whether children understand the overall presentation of the task, we used very simple stimulus pairings in which the cue was a representation of the target stimulus (i.e. target is a circle; distractor is a square; cue is a drawn circle).

### Demographics
For pilot 1, we aimed at testing for four children in each condition and age-group. The table shows the state of data collection as of `r Sys.Date()`.

```{r overview demographics data table, echo=FALSE}
raw.data %>% # select data
  filter(what == "head") %>% # select only lines with data and only valid trials
  group_by(age, condition) %>%
  summarise(N = n_distinct(id),
            male = sum(sex),
            "mean age" = round(mean(agem), 2),
            "min age" = min(agem),
            "max age" = max(agem),
            "sd age" = round(sd(agem), 2),
            ) %>% 
  knitr::kable(digits = 2)

# demographics.data<- raw.data %>% # select data
#   filter(what == "head") %>% # select only lines with data and only valid trials
#   group_by(age, condition) %>%
#   summarise(N = n_distinct(id),
#             male = sum(sex),
#             "mean age" = round(mean(agem), 2),
#             "min age" = min(agem),
#             "max age" = max(agem),
#             "sd age" = round(sd(agem), 2),
#             )

```

### Performance in Familiarization Trials
All test sessions commence with a set of four familiarisation trials in which children have to point out the location of an item that was hidden in plain sight. These trials familiarize children with the task and ensure that the experimenter can read their responses (pointing) via the video call. Children need to succeed in at least half of the familiarization trials in order to progress to the test trials. In case children cannot point out the correct side of the screen, experimenters continue with a mock participation and participants would not be dropped from the sample.

```{r overview familiarization data table, echo=FALSE}
raw.data %>%
  filter(what == "data" & valid == "1" & trialtype == "fam") %>% 
  mutate(correct = as.integer(correct),
         valid = as.integer(valid))%>% 
  group_by(age, condition) %>%
  summarise(N = n_distinct(id),
            "trials/N" = round(sum(valid)/n_distinct(id), 2),
            "% correct" = round(mean(correct)*100, 2),
              ) %>% 
  knitr::kable(digits = 2)

```

### Performance in Test Trials
During the main phase of the study, children are presented with 16 test trials. In order to be submitted to the analyses, participants need to complete at least 8 test trials. Reasons for excluding trials include fuzziness and lack of attention, experimenter error, technical issues, and parental interference. Hence, the number of trials by participants can vary across conditions (cf. trials/N). Trials are coded as valid (valid = 1; drop = 0) and correct (correct = 1; error = 0). The table provides the percentages of correct choices during the main phase of the experiment.

```{r overview test data table, echo=FALSE}
raw.data %>% 
  filter(what == "data" & valid == "1" & trialtype == "test") %>% 
  mutate(correct = as.integer(correct),
         valid = as.integer(valid))%>% 
  group_by(age, condition) %>%
  summarise(N = n_distinct(id),
            "trials/N" = round(sum(valid)/n_distinct(id), 2),
            "% correct" = round(mean(correct)*100, 2),
              )  %>% 
  knitr::kable(digits = 2)

# test.data<-raw.data %>% # select data
#   filter(what == "data" & valid == "1" & trialtype == "test") %>% # select only lines with data and only valid trials
#   mutate(correct = as.integer(correct),
#          valid = as.integer(valid))%>% 
#   group_by(age, condition) %>%
#   summarise(N = n_distinct(id),
#             "trials/N" = round(sum(valid)/n_distinct(id), 2),
#             "% correct" = round(mean(correct)*100, 2),
#               )

# test.data<-raw.data %>% # select data
#   filter(what == "data" & valid == "1" & trialtype == "test") %>% # select only lines with data and only valid trials
#   mutate(correct = as.integer(correct),
#          valid = as.integer(valid))%>% 
#   group_by(age, condition) %>%
#   summarise(N = n_distinct(id),
#             "mean age" = round(mean(agem), 2),
#             "min age" = min(agem),
#             "max age" = max(agem),
#             #"sd age" = round(sd(agem), 2),
#             "trials/N" = round(sum(valid)/n_distinct(id), 2),
#             "% correct" = round(mean(correct)*100, 2)
#               ) 
# test.data %>% relocate("mean age", "min age", "max age", .after = "age")

```

### Proportion of Correct Choices
Graph provides boxplots and individual data for all experimental groups. Contrary to our hypothesis, children in both age-groups perform better in the non-communicative condition. The main reason behind this could be that the presentation of the communicative task is not clear enough. Mainly, we failed to get across that the monkey is actually drawing something for the children to help them. In the next phase we should make this more explicit. In general it needs to be noted that the number of participants per experimental group is very low. Other than that, data generally indicate that in both conditions and age-groups, children succeed in the task. Hence, our task in general and the video procedure in particular are age-appropriate and can be used to investigate our main research question.

```{r plot boxplot by groups, echo = FALSE}

test.ind.data <- raw.data %>%
  filter(what == "data" & valid == "1" & trialtype == "test") %>%
  select(id, age, condition, correct)  %>%
  mutate(correct = as.integer(correct),
         age = as.factor(age),
         condition = as.factor(condition),
         groups = paste(age,"-",condition)) %>%
  group_by(groups, age, condition, id) %>%
  summarise(proportion.correct = round(mean(correct)*100, 2))

test.all.data <- raw.data %>%
  filter(what == "data" & valid == "1" & trialtype == "test") %>%
  select(id, age, condition, correct)  %>%
  mutate(correct = as.integer(correct),
         age = as.factor(age),
         condition = as.factor(condition),
         groups = paste(age,"-",condition)) %>%
  group_by(groups, age, condition) %>%
  summarise(proportion.correct = round(mean(correct)*100, 2),
            sd = round(sd(correct)*100,2))

test.raw.data <- raw.data %>%
  filter(what == "data" & valid == "1" & trialtype == "test") %>%
  select(id, age, condition, correct)  %>%
  mutate(correct = as.integer(correct),
         age = as.factor(age),
         condition = as.factor(condition),
         groups = paste(age,"-",condition))

test.boxplot <-ggplot() +
  geom_boxplot(data = test.ind.data, aes(x = groups, y = proportion.correct), )+ # when there is more data add "notch = TRUE" for conf intervalls
  geom_jitter(data = test.ind.data, aes(x = groups, y = proportion.correct, colour=condition), size = 2, width = 0.1) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,102))+
  labs(x="Groups", y="Proportion Correct")+ # for title add --> title="Proportion of Correct Choices", 
  theme_classic()
   # geom_violin(data = test.raw.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5), mapping = aes(x=groups, y = correct))
test.boxplot

```

### Performance across trials
Children are tested without feedback. The experimenter merely acknowledges the participant's choice by saying "thank you". The plot below presents the proportion of correct choices across all test trials for both age groups and conditions.

```{r plot linegraph performance across trials, echo=FALSE}

trial.data <- raw.data %>% 
  filter(what == "data" & valid == "1" & trialtype == "test") %>% 
  mutate(correct = as.integer(correct),
         valid = as.integer(valid),
         trial = as.integer(trial))%>% 
  select(age, condition, trial, correct) %>%
  group_by(age, condition, trial) %>%
    summarise(correct = round(mean(correct)*100, 2))

trial.plot <- ggplot(trial.data, aes(x = trial, y=correct, colour=condition, linetype=condition))+
  geom_line()+
  geom_point()+
  scale_x_continuous(breaks=trial.data$trial)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,100))+
  labs(x="Trials", y="Proportion Correct")+ # to add a title --> title="Performance across test trials", 
  theme_classic() +
  facet_grid(age ~ .)
trial.plot

```

### Performance by items
In each trial, children were presented with a target and distractor shape as well as a cue matching the target shape. The counterbalancing ensures that all shapes occur both as target and distractor. Presentation in trials is counterbalanced. The graph below shows children's individual performance aggregated for all target shapes. More incorrect choices for a specific target could indicate that a cue is ambiguous.

```{r plot performance across items, echo=FALSE, warning=FALSE}

target.ind.data <- raw.data %>%
  filter(what == "data" & valid == "1" & trialtype == "test") %>%
  select(id, age, condition, tar, correct)  %>%
  mutate(correct = as.integer(correct),
         age = as.factor(age),
         condition = as.factor(condition),
         target = as.factor(tar),
         groups = paste(age,"-",condition)) %>%
  group_by(target,age, id) %>%
  summarise(proportion.correct = round(mean(correct)*100, 2))

target.boxplot <-ggplot() +
  geom_boxplot(data = target.ind.data, aes(x = target, y = proportion.correct),outlier.shape = NA)+ # when there is more data add "notch = TRUE" for conf intervalls
  geom_jitter(data = target.ind.data, aes(x = target, y = proportion.correct, colour=target), size = 2, width = 0.3) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,110))+
  labs(x="Target Shapes", y="Proportion Correct")+ # for title add --> title="Proportion of Correct Choices", 
  theme_classic()+
  facet_grid(age ~ .)
   # geom_violin(data = test.raw.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5), mapping = aes(x=groups, y = correct))
target.boxplot

```

In addition, the plot below shows individual performance across all distractor shapes. More incorrect choices for a specific distractor might indicate that children prefer to select that distractor over any target.

```{r plot performance across distractor items, echo=FALSE, warning=FALSE}

distractor.ind.data <- raw.data %>%
  filter(what == "data" & valid == "1" & trialtype == "test") %>%
  select(id, age, condition, dis, correct)  %>%
  mutate(correct = as.integer(correct),
         age = as.factor(age),
         condition = as.factor(condition),
         distractor = as.factor(dis),
         groups = paste(age,"-",condition)) %>%
  group_by(distractor,age, id) %>%
  summarise(proportion.correct = round(mean(correct)*100, 2))

distractor.boxplot <-ggplot() +
  geom_boxplot(data = distractor.ind.data, aes(x = distractor, y = proportion.correct),outlier.shape = NA)+ # when there is more data add "notch = TRUE" for conf intervalls
  geom_jitter(data = distractor.ind.data, aes(x = distractor, y = proportion.correct, colour=distractor), size = 2, width = 0.3) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,110))+
  labs(x="Distractor Shapes", y="Proportion Correct")+ # for title add --> title="Proportion of Correct Choices", 
  theme_classic()+
  facet_grid(age ~ .)
   # geom_violin(data = test.raw.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5), mapping = aes(x=groups, y = correct))
distractor.boxplot

```

### Testing individual performance against chance
For each individual, we used a binomial test to investigate whether their performance was significantly above chance level (p < 0.05; 50%). The table provides the number and proportion of individuals performing above chance for age experimental group.

```{r table individual performance against chance, echo=FALSE}

ind.binom.data <- raw.data %>%
    filter(what == "data" & valid == "1" & trialtype == "test") %>% 
    select(condition, age, id, correct) %>% 
    mutate(correct = as.integer(correct))%>% 
    group_by(condition, age, id) %>%
    summarise("% correct" = round(mean(correct)*100, 2),
              "sum correct" = sum(correct),
              "sum trials" = length(correct),
              "p" = round(binom.test(sum(correct), length(correct), 
                               p = 0.5, alternative = "greater")$p.value, 3),
              "sig" = if_else(p < 0.05, 1, 0)
              )

sum.binom.data <- ind.binom.data %>%
    group_by(age, condition) %>%
    summarise(N = n_distinct(id),
            "succesfull"  = sum(sig))

sum.binom.data %>%
  mutate("% successful" = (succesfull/N)*100)%>% 
  knitr::kable(digits = 2)

```

### Testing group performance against chance
To test whether each children in both age-group and condition performed above chance on a group level, we used Wilcoxon / Mann-Whitney-U tests.

xxx To Do xxx

```{r plot performance against chance, echo=FALSE}

# Alternative using one-sample t-tests from emopoint
# this is not working yet as the participants in 4<o comm are all 100% correct
# raw.data %>%
#   filter(what == "data" & valid == "1" & trialtype == "test") %>% 
#   mutate(correct = as.integer(correct)) %>%
#   group_by(condition, age, id) %>%
#   arrange(condition, age) %>%
#   summarise(correct = mean(correct)) %>%
#   summarise(correct = list(correct)) %>%
#   group_by(condition, age) %>%
#   mutate(m = mean(unlist(correct)),
#          sd = sd(unlist(correct)),
#          df= t.test(unlist(correct), mu = 0.5)$parameter,
#          t_value = t.test(unlist(correct), mu = 0.5)$statistic,
#          p = t.test(unlist(correct), mu = 0.5)$p.value,
#          d = cohensD(unlist(correct), mu = 0.5))%>%
#   select(condition,age, m,sd,t_value,p,d) %>% #add df
#   knitr::kable(digits = 2)

```

### Comparing Performance across age-groups and conditions
We used Wilcoxon/Mann-Whitney-U-tests to test for significant differences in children's performance across age-groups and conditions respectively.

xxx To Do xxx

### Full Analysis (GLMM, ANOVA)
We are going to analyze our outcome (correct choice 0/1) in a 2x2 design (condition (comm, noncomm); age (3yo, 4yo) using either a GLMM or ANOVA depending on prior tests on data structure and model stability.

xxx To Do xxx

# References

R Core Team (2019). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.

Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686, https://doi.org/10.21105/joss.01686

### 2021-01-05 studies/2020_Aperol_Git/questionnaire data/gregor beispiele/Symlit_RMTS_pilot1_report/oldfiles_backup/progress.R

@@ -1,0 +1,15 @@
+
+# loading packages; if a package is not installed, it will install it
+if (!require(bookdown)) install.packages('bookdown'); library(bookdown)
+if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
+
+### prepare file in excel
+# use filter to select only lines with an ID in it (i.e. exclude all empty lines or lines with na ? x etc)
+# select all lines except the columns for comments
+# copy/paste into a new spreadsheet
+# save as "tab-delimited-text"
+
+### prepare data
+# load tab delimited text file into R; file should be in the same folder as the script for "./" to select it
+raw.data<-read.table("./data/SymLit_RMTS_subjectlist_011220_V2.txt",sep="\t", header=T) 
+

### 2021-01-05 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
questionnaire data

@@
 # file should be in a subfolder named "data" for the script to select it
-raw.data<-read.table("./data/SymLit_RMTS_subjectlist_251220.txt",sep="\t", header=T)
+raw.data<-read.table("./data/questionnaire_value.txt",sep="\t", header=T)
 
+view(raw.data)
 # loading packages
@@
 # suppress "summarize" info. 
-# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+# if this line is committed, each table using the summarize function will be accompanied with a warning from the console
 options(dplyr.summarise.inform = FALSE)
@@
 
-```
-
-# Short Summary
-This report provides a summary of the first pilot ran for SymLit_RMTS.
-Our aim for Pilot1 was to evaluate whether the tasks we are planning to use for SymLit_RMTS are appropriate for three- and four-year-old children.
-In a between-subjects design, three- and four-year-old children saw either a communicative framing of the task or a non-communicative task (condition (comm; non-comm) x agegroup (3yo; 4yo).
-Children were tested via online video calls.
-Since we were primarily interested in whether children understand the overall presentation of the task, we used very simple stimulus pairings in which the cue was a representation of the target stimulus (i.e.
-target is a circle; distractor is a square; cue is a drawn circle).
-
-### Demographics
-For pilot 1, we aimed at testing for four children in each condition and age-group. The table shows the state of data collection as of `r Sys.Date()`.
-
-```{r overview demographics data table, echo=FALSE}
-raw.data %>% # select data
-  filter(what == "head") %>% # select only lines with data and only valid trials
-  group_by(age, condition) %>%
-  summarise(N = n_distinct(id),
-            male = sum(sex),
-            "mean age" = round(mean(agem), 2),
-            "min age" = min(agem),
-            "max age" = max(agem),
-            "sd age" = round(sd(agem), 2),
-            ) %>% 
-  knitr::kable(digits = 2)
-
-# demographics.data<- raw.data %>% # select data
-#   filter(what == "head") %>% # select only lines with data and only valid trials
-#   group_by(age, condition) %>%
-#   summarise(N = n_distinct(id),
-#             male = sum(sex),
-#             "mean age" = round(mean(agem), 2),
-#             "min age" = min(agem),
-#             "max age" = max(agem),
-#             "sd age" = round(sd(agem), 2),
-#             )
+# print(raw.data)
 
@@
 
-### Performance in Familiarization Trials
-All test sessions commence with a set of four familiarisation trials in which children have to point out the location of an item that was hidden in plain sight.
-These trials familiarize children with the task and ensure that the experimenter can read their responses (pointing) via the video call.
-Children need to succeed in at least half of the familiarization trials in order to progress to the test trials.
-In case children cannot point out the correct side of the screen, experimenters continue with a mock participation and participants would not be dropped from the sample.
+### Plotting questionnaire data
 
-```{r overview familiarization data table, echo=FALSE}
-raw.data %>%
-  filter(what == "data" & valid == "1" & trialtype == "fam") %>% 
-  mutate(correct = as.integer(correct),
-         valid = as.integer(valid))%>% 
-  group_by(age, condition) %>%
-  summarise(N = n_distinct(id),
-            "trials/N" = round(sum(valid)/n_distinct(id), 2),
-            "% correct" = round(mean(correct)*100, 2),
-              ) %>% 
-  knitr::kable(digits = 2)
+```{r plot classroom management boxplot by groups, echo = FALSE}
 
+### classroom management
+
+# filter by parameter variable, i.e. create a subset for each group (expert/novice/experimenter)
+km.data <- raw.data %>% filter(item == "Klassenmanagement",
+                               value.1 != "n.a.")
+
+# print(km.data)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value.1))))
+
+# create  mean, min, max, sd of classroom management
+meankm <- mean(km.data$value.1)
+minModul <- min(Modul.data$value)
+maxModul <- max(Modul.data$value)
+sdModul <- sd(Modul.data$value)
+NModul<-length(unique(Modul.data$ID))
+# filter by parametervariable, i.e. create a subset for the individual lecturer
+ind.Modul.data <- Modul.data %>% filter(Dozierende == params$Dozierende)
+# erstelle Mittelwert, min, max, sd for individual lecturer
+ind.meanModul <- mean(ind.Modul.data$value)
+ind.minModul <- min(ind.Modul.data$value)
+ind.maxModul <- max(ind.Modul.data$value)
+ind.sdModul <- sd(ind.Modul.data$value)
+ind.NModul<-length(unique(ind.Modul.data$ID))
 ```
-
-### Performance in Test Trials
-During the main phase of the study, children are presented with 16 test trials.
-In order to be submitted to the analyses, participants need to complete at least 8 test trials.
-Reasons for excluding trials include fuzziness and lack of attention, experimenter error, technical issues, and parental interference.
-Hence, the number of trials by participants can vary across conditions (cf.
-trials/N).
-Trials are coded as valid (valid = 1; drop = 0) and correct (correct = 1; error = 0).
-The table provides the percentages of correct choices during the main phase of the experiment.
-
-```{r overview test data table, echo=FALSE}
-raw.data %>% 
-  filter(what == "data" & valid == "1" & trialtype == "test") %>% 
-  mutate(correct = as.integer(correct),
-         valid = as.integer(valid))%>% 
-  group_by(age, condition) %>%
-  summarise(N = n_distinct(id),
-            "trials/N" = round(sum(valid)/n_distinct(id), 2),
-            "% correct" = round(mean(correct)*100, 2),
-              )  %>% 
-  knitr::kable(digits = 2)
-
-# test.data<-raw.data %>% # select data
-#   filter(what == "data" & valid == "1" & trialtype == "test") %>% # select only lines with data and only valid trials
-#   mutate(correct = as.integer(correct),
-#          valid = as.integer(valid))%>% 
-#   group_by(age, condition) %>%
-#   summarise(N = n_distinct(id),
-#             "trials/N" = round(sum(valid)/n_distinct(id), 2),
-#             "% correct" = round(mean(correct)*100, 2),
-#               )
-
-# test.data<-raw.data %>% # select data
-#   filter(what == "data" & valid == "1" & trialtype == "test") %>% # select only lines with data and only valid trials
-#   mutate(correct = as.integer(correct),
-#          valid = as.integer(valid))%>% 
-#   group_by(age, condition) %>%
-#   summarise(N = n_distinct(id),
-#             "mean age" = round(mean(agem), 2),
-#             "min age" = min(agem),
-#             "max age" = max(agem),
-#             #"sd age" = round(sd(agem), 2),
-#             "trials/N" = round(sum(valid)/n_distinct(id), 2),
-#             "% correct" = round(mean(correct)*100, 2)
-#               ) 
-# test.data %>% relocate("mean age", "min age", "max age", .after = "age")
-
-```
-
-### Proportion of Correct Choices
-Graph provides boxplots and individual data for all experimental groups.
-Contrary to our hypothesis, children in both age-groups perform better in the non-communicative condition.
-The main reason behind this could be that the presentation of the communicative task is not clear enough.
-Mainly, we failed to get across that the monkey is actually drawing something for the children to help them.
-In the next phase we should make this more explicit.
-In general it needs to be noted that the number of participants per experimental group is very low.
-Other than that, data generally indicate that in both conditions and age-groups, children succeed in the task.
-Hence, our task in general and the video procedure in particular are age-appropriate and can be used to investigate our main research question.
-
-```{r plot boxplot by groups, echo = FALSE}
 

### 2021-01-07 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
questionnaire

@@
 ---
-title: "Pilot study _Aperol_: questionnaire data"
+title: "Pilot study Aperol: questionnaire data"
 author: "Mandy Klatt, Gregor Kachel and Anne Deiglmayr"
@@
 # file should be in a subfolder named "data" for the script to select it
-raw.data<-read.table("./data/questionnaire_value.txt",sep="\t", header=T)
+raw.data<-read.table("./data/questionnaire_data_080121.txt",sep="\t", header=T)
 
-view(raw.data)
 # loading packages
@@
 
-# print(raw.data)
+view (raw.data)
 
@@
 # filter by parameter variable, i.e. create a subset for each group (expert/novice/experimenter)
-km.data <- raw.data %>% filter(item == "Klassenmanagement",
-                               value.1 != "n.a.")
+km.data <- raw.data %>% filter(item == "Klassenmanagement")
 
-# print(km.data)
+view (raw.data)
+class(raw.data$value)
 
 # value sometimes contained text before filtering, we have to convert the numbers to numeric
-km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value.1))))
+km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value))))
 
 # create  mean, min, max, sd of classroom management
-meankm <- mean(km.data$value.1)
-minModul <- min(Modul.data$value)
-maxModul <- max(Modul.data$value)
-sdModul <- sd(Modul.data$value)
-NModul<-length(unique(Modul.data$ID))
-# filter by parametervariable, i.e. create a subset for the individual lecturer
-ind.Modul.data <- Modul.data %>% filter(Dozierende == params$Dozierende)
-# erstelle Mittelwert, min, max, sd for individual lecturer
-ind.meanModul <- mean(ind.Modul.data$value)
-ind.minModul <- min(ind.Modul.data$value)
-ind.maxModul <- max(ind.Modul.data$value)
-ind.sdModul <- sd(ind.Modul.data$value)
-ind.NModul<-length(unique(ind.Modul.data$ID))
+meankm <- mean(km.data$value)
+minkm <- min(km.data$value)
+maxkm <- max(km.data$value)
+sdkm <- sd(km.data$value)
+Nkm<-length(unique(km.data$ID))
+
+# # filter by parametervariable, i.e. create a subset for the individual lecturer
+# ind.km.data <- km.data %>% filter(Dozierende == params$Dozierende)
+# # erstelle Mittelwert, min, max, sd for individual lecturer
+# ind.meankm <- mean(ind.km.data$value)
+# ind.minkm <- min(ind.km.data$value)
+# ind.maxkm <- max(ind.km.data$value)
+# ind.sdkm <- sd(ind.km.data$value)
+# ind.Nkm<-length(unique(ind.km.data$ID))
 ```
-
-test.ind.data <- raw.data %>%
-  filter(what == "data" & valid == "1" & trialtype == "test") %>%
-  select(id, age, condition, correct)  %>%
-  mutate(correct = as.integer(correct),
-         age = as.factor(age),
-         condition = as.factor(condition),
-         groups = paste(age,"-",condition)) %>%
-  group_by(groups, age, condition, id) %>%
-  summarise(proportion.correct = round(mean(correct)*100, 2))
-
-test.all.data <- raw.data %>%
-  filter(what == "data" & valid == "1" & trialtype == "test") %>%
-  select(id, age, condition, correct)  %>%
-  mutate(correct = as.integer(correct),
-         age = as.factor(age),
-         condition = as.factor(condition),
-         groups = paste(age,"-",condition)) %>%
-  group_by(groups, age, condition) %>%
-  summarise(proportion.correct = round(mean(correct)*100, 2),
-            sd = round(sd(correct)*100,2))
-
-test.raw.data <- raw.data %>%
-  filter(what == "data" & valid == "1" & trialtype == "test") %>%
-  select(id, age, condition, correct)  %>%
-  mutate(correct = as.integer(correct),
-         age = as.factor(age),
-         condition = as.factor(condition),
-         groups = paste(age,"-",condition))
-
-test.boxplot <-ggplot() +
-  geom_boxplot(data = test.ind.data, aes(x = groups, y = proportion.correct), )+ # when there is more data add "notch = TRUE" for conf intervalls
-  geom_jitter(data = test.ind.data, aes(x = groups, y = proportion.correct, colour=condition), size = 2, width = 0.1) +
-    scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,102))+
-  labs(x="Groups", y="Proportion Correct")+ # for title add --> title="Proportion of Correct Choices", 
-  theme_classic()
-   # geom_violin(data = test.raw.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5), mapping = aes(x=groups, y = correct))
-test.boxplot
-
-```
-
-### Performance across trials
-Children are tested without feedback.
-The experimenter merely acknowledges the participant's choice by saying "thank you".
-The plot below presents the proportion of correct choices across all test trials for both age groups and conditions.
-
-```{r plot linegraph performance across trials, echo=FALSE}
-
-trial.data <- raw.data %>% 
-  filter(what == "data" & valid == "1" & trialtype == "test") %>% 
-  mutate(correct = as.integer(correct),
-         valid = as.integer(valid),
-         trial = as.integer(trial))%>% 
-  select(age, condition, trial, correct) %>%
-  group_by(age, condition, trial) %>%
-    summarise(correct = round(mean(correct)*100, 2))
-
-trial.plot <- ggplot(trial.data, aes(x = trial, y=correct, colour=condition, linetype=condition))+
-  geom_line()+
-  geom_point()+
-  scale_x_continuous(breaks=trial.data$trial)+
-  scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,100))+
-  labs(x="Trials", y="Proportion Correct")+ # to add a title --> title="Performance across test trials", 
-  theme_classic() +
-  facet_grid(age ~ .)
-trial.plot
-
-```
-
-### Performance by items
-In each trial, children were presented with a target and distractor shape as well as a cue matching the target shape.
-The counterbalancing ensures that all shapes occur both as target and distractor.
-Presentation in trials is counterbalanced.
-The graph below shows children's individual performance aggregated for all target shapes.
-More incorrect choices for a specific target could indicate that a cue is ambiguous.
-
-```{r plot performance across items, echo=FALSE, warning=FALSE}
-
-target.ind.data <- raw.data %>%
-  filter(what == "data" & valid == "1" & trialtype == "test") %>%
-  select(id, age, condition, tar, correct)  %>%
-  mutate(correct = as.integer(correct),
-         age = as.factor(age),
-         condition = as.factor(condition),
-         target = as.factor(tar),
-         groups = paste(age,"-",condition)) %>%
-  group_by(target,age, id) %>%
-  summarise(proportion.correct = round(mean(correct)*100, 2))
-
-target.boxplot <-ggplot() +
-  geom_boxplot(data = target.ind.data, aes(x = target, y = proportion.correct),outlier.shape = NA)+ # when there is more data add "notch = TRUE" for conf intervalls
-  geom_jitter(data = target.ind.data, aes(x = target, y = proportion.correct, colour=target), size = 2, width = 0.3) +
-    scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,110))+
-  labs(x="Target Shapes", y="Proportion Correct")+ # for title add --> title="Proportion of Correct Choices", 
-  theme_classic()+
-  facet_grid(age ~ .)
-   # geom_violin(data = test.raw.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5), mapping = aes(x=groups, y = correct))
-target.boxplot
-
-```
-
-In addition, the plot below shows individual performance across all distractor shapes.
-More incorrect choices for a specific distractor might indicate that children prefer to select that distractor over any target.
-
-```{r plot performance across distractor items, echo=FALSE, warning=FALSE}
-
-distractor.ind.data <- raw.data %>%
-  filter(what == "data" & valid == "1" & trialtype == "test") %>%
-  select(id, age, condition, dis, correct)  %>%
-  mutate(correct = as.integer(correct),
-         age = as.factor(age),
-         condition = as.factor(condition),
-         distractor = as.factor(dis),
-         groups = paste(age,"-",condition)) %>%
-  group_by(distractor,age, id) %>%
-  summarise(proportion.correct = round(mean(correct)*100, 2))
-
-distractor.boxplot <-ggplot() +
-  geom_boxplot(data = distractor.ind.data, aes(x = distractor, y = proportion.correct),outlier.shape = NA)+ # when there is more data add "notch = TRUE" for conf intervalls
-  geom_jitter(data = distractor.ind.data, aes(x = distractor, y = proportion.correct, colour=distractor), size = 2, width = 0.3) +
-    scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,110))+
-  labs(x="Distractor Shapes", y="Proportion Correct")+ # for title add --> title="Proportion of Correct Choices", 
-  theme_classic()+
-  facet_grid(age ~ .)
-   # geom_violin(data = test.raw.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5), mapping = aes(x=groups, y = correct))
-distractor.boxplot
-
-```
-
-### Testing individual performance against chance
-For each individual, we used a binomial test to investigate whether their performance was significantly above chance level (p < 0.05; 50%).
-The table provides the number and proportion of individuals performing above chance for age experimental group.
-
-```{r table individual performance against chance, echo=FALSE}
-
-ind.binom.data <- raw.data %>%
-    filter(what == "data" & valid == "1" & trialtype == "test") %>% 
-    select(condition, age, id, correct) %>% 
-    mutate(correct = as.integer(correct))%>% 
-    group_by(condition, age, id) %>%
-    summarise("% correct" = round(mean(correct)*100, 2),
-              "sum correct" = sum(correct),
-              "sum trials" = length(correct),
-              "p" = round(binom.test(sum(correct), length(correct), 
-                               p = 0.5, alternative = "greater")$p.value, 3),
-              "sig" = if_else(p < 0.05, 1, 0)
-              )
-
-sum.binom.data <- ind.binom.data %>%
-    group_by(age, condition) %>%
-    summarise(N = n_distinct(id),
-            "succesfull"  = sum(sig))
-
-sum.binom.data %>%
-  mutate("% successful" = (succesfull/N)*100)%>% 
-  knitr::kable(digits = 2)
-
-```
-
-### Testing group performance against chance
-To test whether each children in both age-group and condition performed above chance on a group level, we used Wilcoxon / Mann-Whitney-U tests.
-
-xxx To Do xxx
-
-```{r plot performance against chance, echo=FALSE}
-
-# Alternative using one-sample t-tests from emopoint
-# this is not working yet as the participants in 4<o comm are all 100% correct
-# raw.data %>%
-#   filter(what == "data" & valid == "1" & trialtype == "test") %>% 
-#   mutate(correct = as.integer(correct)) %>%
-#   group_by(condition, age, id) %>%
-#   arrange(condition, age) %>%
-#   summarise(correct = mean(correct)) %>%
-#   summarise(correct = list(correct)) %>%
-#   group_by(condition, age) %>%
-#   mutate(m = mean(unlist(correct)),
-#          sd = sd(unlist(correct)),
-#          df= t.test(unlist(correct), mu = 0.5)$parameter,
-#          t_value = t.test(unlist(correct), mu = 0.5)$statistic,
-#          p = t.test(unlist(correct), mu = 0.5)$p.value,
-#          d = cohensD(unlist(correct), mu = 0.5))%>%
-#   select(condition,age, m,sd,t_value,p,d) %>% #add df
-#   knitr::kable(digits = 2)
-
-```
-
-### Comparing Performance across age-groups and conditions
-We used Wilcoxon/Mann-Whitney-U-tests to test for significant differences in children's performance across age-groups and conditions respectively.
-
-xxx To Do xxx
-
-### Full Analysis (GLMM, ANOVA)
-We are going to analyze our outcome (correct choice 0/1) in a 2x2 design (condition (comm, noncomm); age (3yo, 4yo) using either a GLMM or ANOVA depending on prior tests on data structure and model stability.
-
-xxx To Do xxx
-
-# References
-
-R Core Team (2019). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.
-
-Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686, https://doi.org/10.21105/joss.01686

### 2021-01-07 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
questionnaire update

--- 2021-01-05 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
@@
 # filter by parameter variable, i.e. create a subset for each group (expert/novice/experimenter)
-km.data <- raw.data %>% filter(item == "Klassenmanagement",
-                               value.1 != "n.a.")
+km.data <- raw.data %>% filter(item == "Klassenmanagement")
 
-# print(km.data)
+view (raw.data)
 
 # value sometimes contained text before filtering, we have to convert the numbers to numeric
-km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value.1))))
+km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value))))
 
 # create  mean, min, max, sd of classroom management
-meankm <- mean(km.data$value.1)
-minModul <- min(Modul.data$value)
-maxModul <- max(Modul.data$value)
-sdModul <- sd(Modul.data$value)
-NModul<-length(unique(Modul.data$ID))
+meankm <- mean(km.data$value)
+minkm <- min(km.data$value)
+maxkm <- max(km.data$value)
+sdkm <- sd(km.data$value)
+Nkm<-length(unique(km.data$ID))
+
+# # filter by parametervariable, i.e. create a subset for the individual lecturer
+# ind.km.data <- km.data %>% filter(Dozierende == params$Dozierende)
+# # erstelle Mittelwert, min, max, sd for individual lecturer
+# ind.meankm <- mean(ind.km.data$value)
+# ind.minkm <- min(ind.km.data$value)
+# ind.maxkm <- max(ind.km.data$value)
+# ind.sdkm <- sd(ind.km.data$value)
+# ind.Nkm<-length(unique(ind.km.data$ID))
+```
+The mean of the item "classroom management" is `r round(meankm, 2)` (min = `r minkm`; max = `r maxkm`; SD = `r round(sdkm,2)`; N = `r Nkm)`; lickert-scale 1-4; 4 = best rating).
+
+```{r classroom management horicontal Plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
 # filter by parametervariable, i.e. create a subset for the individual lecturer
-ind.Modul.data <- Modul.data %>% filter(Dozierende == params$Dozierende)
-# erstelle Mittelwert, min, max, sd for individual lecturer
-ind.meanModul <- mean(ind.Modul.data$value)
-ind.minModul <- min(ind.Modul.data$value)
-ind.maxModul <- max(ind.Modul.data$value)
-ind.sdModul <- sd(ind.Modul.data$value)
-ind.NModul<-length(unique(ind.Modul.data$ID))
-```
+km.data <- raw.data %>% filter(item == "Klassenmanagement")
 
-test.ind.data <- raw.data %>%
-  filter(what == "data" & valid == "1" & trialtype == "test") %>%
-  select(id, age, condition, correct)  %>%
-  mutate(correct = as.integer(correct),
-         age = as.factor(age),
-         condition = as.factor(condition),
-         groups = paste(age,"-",condition)) %>%
-  group_by(groups, age, condition, id) %>%
-  summarise(proportion.correct = round(mean(correct)*100, 2))
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value))))
 
-test.all.data <- raw.data %>%
-  filter(what == "data" & valid == "1" & trialtype == "test") %>%
-  select(id, age, condition, correct)  %>%
-  mutate(correct = as.integer(correct),
-         age = as.factor(age),
-         condition = as.factor(condition),
-         groups = paste(age,"-",condition)) %>%
-  group_by(groups, age, condition) %>%
-  summarise(proportion.correct = round(mean(correct)*100, 2),
-            sd = round(sd(correct)*100,2))
+view(km.data)
+# to stick to the individual vs all style necessary for anonymized feedback in plotting
+# we create a new vector from experiece that we call "expert" and copy the names
+# of the name called by the parameter but rename all others to "all"
+# now the "fill ="option can use the new column to differentiate all vs parameter dozent
 
-test.raw.data <- raw.data %>%
-  filter(what == "data" & valid == "1" & trialtype == "test") %>%
-  select(id, age, condition, correct)  %>%
-  mutate(correct = as.integer(correct),
-         age = as.factor(age),
-         condition = as.factor(condition),
-         groups = paste(age,"-",condition))
+km.plot.data <- km.data %>%
+  mutate(Teilnehmende = ifelse(Dozierende == params$Dozierende, toString(params$Dozierende), "Alle Kurse"))
+modul.plot.data$Teilnehmende <- as.factor(modul.plot.data$Teilnehmende)
 
-test.boxplot <-ggplot() +
-  geom_boxplot(data = test.ind.data, aes(x = groups, y = proportion.correct), )+ # when there is more data add "notch = TRUE" for conf intervalls
-  geom_jitter(data = test.ind.data, aes(x = groups, y = proportion.correct, colour=condition), size = 2, width = 0.1) +
-    scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,102))+
-  labs(x="Groups", y="Proportion Correct")+ # for title add --> title="Proportion of Correct Choices", 
-  theme_classic()
-   # geom_violin(data = test.raw.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5), mapping = aes(x=groups, y = correct))
-test.boxplot
+# to create error bars, we need to summarise the data in a seperate dataframe
+modul.plot.sd <-modul.plot.data %>% 
+  group_by(itemfulltext, Teilnehmende, .drop=TRUE) %>%
+  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# and here comes the long plot 
+modul.plot<-ggplot(data = modul.plot.sd, 
+                           aes(x = itemfulltext, y = mean, 
+                               group=Teilnehmende, colour = Teilnehmende)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,5)+
+  labs(data = modul.plot.data, y = "Ausprägung", x = NULL,
+       title="Modulbewertung" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+modul.plot
 
 ```
-
-### Performance across trials
-Children are tested without feedback.
-The experimenter merely acknowledges the participant's choice by saying "thank you".
-The plot below presents the proportion of correct choices across all test trials for both age groups and conditions.
-
 ```{r plot linegraph performance across trials, echo=FALSE}

### 2021-01-13 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
update questionnaire R scrpit & excel

@@
 # file should be in a subfolder named "data" for the script to select it
-raw.data<-read.table("./data/questionnaire_data_080121.txt",sep="\t", header=T)
+raw.data<-read.table("./data/short_questionnaire_data_1301211.txt",sep="\t", header=T)
 
@@
 
-# # change data structure: everything is turned into factors except for 
-# main.data <- raw.data %>%
-#   filter(what == "data"& valid == 1)  %>%
-#   mutate(across(!correct&!agem&!aged, as.factor),
-#          correct = as.integer(correct))
+### checking for missing values
+apply(is.na(raw.data), 2, which)
+
+# knock out NAs
+raw.data <- raw.data  %>% filter(
+  personID != "NA")
 
 view (raw.data)
+str(raw.data)
+
+```
+
+### Data collection
+For the pilot study, we collected data from . The table shows the state of data collection as of `r Sys.Date()`.
+
+```{r overview demographics data table, echo=FALSE}
+raw.data %>% # select data
+  group_by(session, target, perspective) %>%
+  summarise(N = n_distinct(personID),
+            male = sum(sex),
+            "mean age" = round(mean(age), 2),
+            "min age" = min(age),
+            "max age" = max(age),
+            "sd age" = round(sd(age), 2),
+            ) %>% 
+  knitr::kable(digits = 2)
 

### 2021-01-14 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
update questionnaire

--- 2021-01-07 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
@@
 
-# # change data structure: everything is turned into factors except for 
-# main.data <- raw.data %>%
-#   filter(what == "data"& valid == 1)  %>%
-#   mutate(across(!correct&!agem&!aged, as.factor),
-#          correct = as.integer(correct))
+### checking for missing values
+apply(is.na(raw.data), 2, which)
+
+# knock out NAs
+raw.data <- raw.data  %>% filter(
+  personID != "NA")
 
 view (raw.data)
+str(raw.data)
+
+```
+
+# Short Summary
+This report provides a summary of the questionnaire data of the first pilot APEROL.
+The aim was to explore connections between the visual attention of the teacher and students’ in-class experience of the teachers’ "withitness".
+The study was conducted as a lab study with simulated scripted mini-lessons (10min per lesson).
+Data was collected from N = 8 teachers and N = 2 observers in 2 sessions.
+In each session, one subject took the role of teacher, while the other teachers acted as the class.
+After each lesson, the subjects answered items on classroom management, especially on the teacher's behaviour, using validated questionnaires.
+An external observer also answered a questionnaire.
+In addition, the teacher is asked to give a self-assessment on his/her classroom management.
+
+### Data collection
+For the pilot study, we collected questionnaire data from N = `r sum(n_distinct(raw.data$personID))` subjects in `r sum(n_distinct(raw.data$session))` sessions.
+The questionnaires were answered after each lesson (10min) by an observer, the teacher and the other teachers acting as the class.
+
+The table shows the state of data collection as of `r Sys.Date()`.
+
+```{r overview demographics data table, echo=FALSE}
+raw.data %>% # select data
+  group_by(session, target, perspective) %>%
+  summarise(N = n_distinct(personID),
+            male = sum(sex),
+            "mean age" = round(mean(age), 2),
+            "min age" = min(age),
+            "max age" = max(age),
+            "sd age" = round(sd(age), 2),
+            ) %>% 
+  knitr::kable(digits = 2)
 
@@
 # filter by parameter variable, i.e. create a subset for each group (expert/novice/experimenter)
-km.data <- raw.data %>% filter(item == "Klassenmanagement")
+km.data <- raw.data %>% filter(scale == "Klassenmanagement")
 
-view (raw.data)
-class(raw.data$value)
+view (km.data)
 
@@
 Nkm<-length(unique(km.data$ID))
+```
 
-# # filter by parametervariable, i.e. create a subset for the individual lecturer
-# ind.km.data <- km.data %>% filter(Dozierende == params$Dozierende)
-# # erstelle Mittelwert, min, max, sd for individual lecturer
-# ind.meankm <- mean(ind.km.data$value)
-# ind.minkm <- min(ind.km.data$value)
-# ind.maxkm <- max(ind.km.data$value)
-# ind.sdkm <- sd(ind.km.data$value)
-# ind.Nkm<-length(unique(ind.km.data$ID))
-```
+### Comparing Performance across age-groups and conditions
+We used Wilcoxon/Mann-Whitney-U-tests to test for significant differences in children's performance across age-groups and conditions respectively.
+
+xxx To Do xxx
+
+### Full Analysis (GLMM, ANOVA)
+We are going to analyze our outcome (correct choice 0/1) in a 2x2 design (condition (comm, noncomm); age (3yo, 4yo) using either a GLMM or ANOVA depending on prior tests on data structure and model stability.
+
+xxx To Do xxx
+
+# References
+
+R Core Team (2019). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.
+
+Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686, https://doi.org/10.21105/joss.01686

### 2021-01-14 studies/2020_Aperol_Git/questionnaire data/backup/addition_questionnaire.R

@@ -1,0 +1,210 @@
+### Plotting questionnaire data
+
+```{r plot classroom management boxplot by groups, echo = FALSE}
+
+### classroom management
+
+# filter by parameter variable, i.e. create a subset for each group (expert/novice/experimenter)
+km.data <- raw.data %>% filter(item == "Klassenmanagement")
+
+view (raw.data)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+
+# create  mean, min, max, sd of classroom management
+meankm <- mean(km.data$value)
+minkm <- min(km.data$value)
+maxkm <- max(km.data$value)
+sdkm <- sd(km.data$value)
+Nkm<-length(unique(km.data$ID))
+
+
+# # filter by parametervariable, i.e. create a subset for the individual lecturer
+# ind.km.data <- km.data %>% filter(Dozierende == params$Dozierende)
+# # erstelle Mittelwert, min, max, sd for individual lecturer
+# ind.meankm <- mean(ind.km.data$value)
+# ind.minkm <- min(ind.km.data$value)
+# ind.maxkm <- max(ind.km.data$value)
+# ind.sdkm <- sd(ind.km.data$value)
+# ind.Nkm<-length(unique(ind.km.data$ID))
+```
+The mean of the item "classroom management" is `r round(meankm, 2)` (min = `r minkm`; max = `r maxkm`; SD = `r round(sdkm,2)`; N = `r Nkm)`; lickert-scale 1-4; 4 = best rating). 
+
+```{r classroom management horicontal Plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
+# filter by parametervariable, i.e. create a subset for the individual lecturer
+km.data <- raw.data %>% filter(item == "Klassenmanagement")
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+view(km.data)
+# to stick to the individual vs all style necessary for anonymized feedback in plotting
+# we create a new vector from experiece that we call "expert" and copy the names
+# of the name called by the parameter but rename all others to "all"
+# now the "fill ="option can use the new column to differentiate all vs parameter dozent
+
+km.plot.data <- km.data %>%
[…]

### 2021-01-18 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
update questionnaire

@@
 raw.data %>% # select data
-  group_by(session, target, perspective) %>%
+  group_by(session, perspective) %>%
   summarise(N = n_distinct(personID),
-            male = sum(sex),
+            "mean age" = round(mean(age), 2),
+            "min age" = min(age),
+            "max age" = max(age)
+            ) %>% 
+  knitr::kable(digits = 2)
+
+```
+
+### Plotting questionnaire data
+
+```{r mean classroom management by session, echo = FALSE}
+
+### classroom management session 1
+
+# filter by parameter variable, i.e. create a subset for each session
+km1.data <- raw.data %>% filter(scale == "Klassenmanagement",
+                               session == "1")
+
+view (km1.data)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+km1.data <- km1.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# create  mean, min, max, sd of classroom management
+meankm1 <- mean(km1.data$value)
+minkm1 <- min(km1.data$value)
+maxkm1 <- max(km1.data$value)
+sdkm1 <- sd(km1.data$value)
+Nkm1 <- length(unique(km1.data$personID))
+mdkm1 <- median(km1.data$value)
+
+km1.data <- raw.data %>% filter(scale == "Klassenmanagement",
+                               session == "1") %>% 
+  group_by(perspective, target) %>%
+  summarise(N = n_distinct(personID),
             "mean age" = round(mean(age), 2),
@@
 
+### classroom management session 2
+
+# filter by parameter variable, i.e. create a subset for each session
+km2.data <- raw.data %>% filter(scale == "Klassenmanagement",
+                               session == "2")
+
+view (km2.data)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+km2.data <- km2.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# create  mean, min, max, sd of classroom management
+meankm2 <- mean(km2.data$value)
+minkm2 <- min(km2.data$value)
+maxkm2 <- max(km2.data$value)
+sdkm2 <- sd(km2.data$value)
+Nkm2<-length(unique(km2.data$personID))
+
 ```
 
-### Plotting questionnaire data
+The item "classroom management"  was rated by the observer, the teacher and students on average in session 1 with `r round(meankm1, 2)` (min = `r minkm1`; max = `r maxkm1`; SD = `r round(sdkm1,2)`; N = `r Nkm1`; lickert-scale 1-4; 4 = best evaluation) and in session 2 with `r round(meankm2, 2)` (min = `r minkm2`; max = `r maxkm2`; SD = `r round(sdkm2,2)`; N = `r Nkm2`; lickert-scale 1-4; 4 = best evaluation).
 
-```{r plot classroom management boxplot by groups, echo = FALSE}
+```{r Modul horicontal Plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
 
-### classroom management
+# to create error bars, we need to summarise the data in a seperate dataframe
+modul.plot.sd <-modul.plot.data %>%
+  group_by(itemfulltext, Teilnehmende, .drop=TRUE) %>%
+  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
 
-# filter by parameter variable, i.e. create a subset for each group (expert/novice/experimenter)
-km.data <- raw.data %>% filter(scale == "Klassenmanagement")
+# and here comes the long plot
+modul.plot<-ggplot(data = modul.plot.sd,
+                           aes(x = itemfulltext, y = mean,
+                               group=Teilnehmende, colour = Teilnehmende)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,5)+
+  labs(data = modul.plot.data, y = "Ausprägung", x = NULL,
+       title="Modulbewertung" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+modul.plot
 
-view (km.data)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# create  mean, min, max, sd of classroom management
-meankm <- mean(km.data$value)
-minkm <- min(km.data$value)
-maxkm <- max(km.data$value)
-sdkm <- sd(km.data$value)
-Nkm<-length(unique(km.data$ID))
 ```

### 2021-01-19 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
update r markdown questionnaire

--- 2021-01-14 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
@@
 ---
-title: "Pilot study Aperol: questionnaire data"
+title: "Pilot study APEROL: questionnaire data"
 author: "Mandy Klatt, Gregor Kachel and Anne Deiglmayr"
@@
 
-view (raw.data)
-str(raw.data)
+# view (raw.data)
+# str(raw.data)
 
@@
 The study was conducted as a lab study with simulated scripted mini-lessons (10min per lesson).
-Data was collected from N = 8 teachers and N = 2 observers in 2 sessions.
+Data was collected from N = 8 teachers and N = 1 observer in 2 sessions.
+
 In each session, one subject took the role of teacher, while the other teachers acted as the class.
@@
 An external observer also answered a questionnaire.
-In addition, the teacher is asked to give a self-assessment on his/her classroom management.
+In addition, the teacher was asked to give a self-assessment on his/her classroom management.
 
@@
 For the pilot study, we collected questionnaire data from N = `r sum(n_distinct(raw.data$personID))` subjects in `r sum(n_distinct(raw.data$session))` sessions.
-The questionnaires were answered after each lesson (10min) by an observer, the teacher and the other teachers acting as the class.
+The questionnaires were answered after each lesson (10min) by an observer, the teacher and the three teachers acting as the class.
 
@@
 raw.data %>% # select data
-  group_by(session, target, perspective) %>%
+  group_by(session, perspective) %>%
   summarise(N = n_distinct(personID),
-            male = sum(sex),
             "mean age" = round(mean(age), 2),
             "min age" = min(age),
-            "max age" = max(age),
-            "sd age" = round(sd(age), 2),
+            "max age" = max(age)
             ) %>% 
@@
 
-### Plotting questionnaire data
+### Plotting scales
 
-```{r plot classroom management boxplot by groups, echo = FALSE}
+The graphs provide line plots for each perspective and target, plotted for the following scales for both sessions:
 
-### classroom management
+(1) classroom management
+(2) positive climate and motivation
+(3) clarity and structuredness
+(4) activation and support
+(5) presence: posture and gaze
+(6) presence: voice
+(7) presence: verbal and non-verbal intervention
+(8) turn taking
+(9) natural behaviour
 
-# filter by parameter variable, i.e. create a subset for each group (expert/novice/experimenter)
-km.data <- raw.data %>% filter(scale == "Klassenmanagement")
+#### Session 1
 
-view (km.data)
+#### classroom management
+
+```{r mean classroom management by session, echo = FALSE}
+
+### classroom management session 1
+
+# filter by parameter variable, i.e. create a subset for each session
+km1.data <- raw.data %>% filter(scale == "Klassenmanagement",
+                               session == "1")
+
+view (km1.data)
 
 # value sometimes contained text before filtering, we have to convert the numbers to numeric
-km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+km1.data <- km1.data %>%  mutate(value = as.numeric(as.character(factor(value))))
 
-# create  mean, min, max, sd of classroom management
-meankm <- mean(km.data$value)
-minkm <- min(km.data$value)
-maxkm <- max(km.data$value)
-sdkm <- sd(km.data$value)
-Nkm<-length(unique(km.data$ID))
+# # create  mean, min, max, sd of classroom management
+# meankm1 <- mean(km1.data$value)
+# minkm1 <- min(km1.data$value)
+# maxkm1 <- max(km1.data$value)
+# sdkm1 <- sd(km1.data$value)
+# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
+# mdkm1 <- median(km1.data$value)
+
 ```
 
-### Comparing Performance across age-groups and conditions
-We used Wilcoxon/Mann-Whitney-U-tests to test for significant differences in children's performance across age-groups and conditions respectively.
+The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***classroom management*** in session 1 for each perspective and target.
+The target always corresponds with the perspective of the teacher, i.e.
+teacher = target A.
 
-xxx To Do xxx
+``` {r classroom management data table, echo=FALSE}
 
-### Full Analysis (GLMM, ANOVA)
-We are going to analyze our outcome (correct choice 0/1) in a 2x2 design (condition (comm, noncomm); age (3yo, 4yo) using either a GLMM or ANOVA depending on prior tests on data structure and model stability.
+km1.data %>% # select data
+  group_by(target,perspective) %>%
+  summarise(N = n_distinct(personID),
+            "mean" = round(mean(value), 2),
+            "min" = min(value),
+            "max" = max(value),
+            "sd" = sd(value),
+            "median" = median(value)
+            ) %>% 
+  knitr::kable(digits = 2)
 
-xxx To Do xxx
+```
+
+```{r classroom management line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
+
+# to create error bars, we need to summarize the data in a separate data frame
+km1.plot.sd <- km1.data %>%
+  group_by(perspective, target, .drop=TRUE) %>%
+  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# and here comes the long plot
+km1.plot<-ggplot(data = km1.plot.sd,
+                   aes(x = perspective, y = mean,
+                       group = target, colour = target)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  labs(data = km1.data, y = "value", x = NULL,
+       title="classroom management" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+km1.plot
+
+```
+
+#### positive climate and motivation
+
+```{r mean positive climate and motivation by session, echo = FALSE}
+
+### positive climate and motivation session 1
+
+# filter by parameter variable, i.e. create a subset for each session
+lkm1.data <- raw.data %>% filter(scale == "Lernförderliches Klima und Motivierung",
+                               session == "1")
+
+view (lkm1.data)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+lkm1.data <- lkm1.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# # create  mean, min, max, sd of classroom management
+# meankm1 <- mean(km1.data$value)
+# minkm1 <- min(km1.data$value)
+# maxkm1 <- max(km1.data$value)
+# sdkm1 <- sd(km1.data$value)
+# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
+# mdkm1 <- median(km1.data$value)
+
+```
+
+The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***positive climate and motivation*** in session 1 for each perspective and target.
+The target always corresponds with the perspective of the teacher, i.e.
+teacher = target A.
+
+XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX
+
+``` {r positive climate and motivation data table, echo=FALSE}
+
+lkm1.data %>% # select data
+  group_by(target,perspective) %>%
+  summarise(N = n_distinct(personID),
+            "mean" = round(mean(value), 2),
+            "min" = min(value),
+            "max" = max(value),
+            "sd" = sd(value),
+            "median" = median(value)
+            ) %>% 
+  knitr::kable(digits = 2)
+
+```
+
+```{r positive climate and motivation line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
+
+# to create error bars, we need to summarize the data in a separate data frame
+lkm1.plot.sd <- lkm1.data %>%
+  group_by(perspective, target, .drop=TRUE) %>%
+  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# and here comes the long plot
+lkm1.plot<-ggplot(data = lkm1.plot.sd,
+                   aes(x = perspective, y = mean,
+                       group = target, colour = target)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  labs(data = lkm1.data, y = "value", x = NULL,
+       title="positive climate and motivation" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+lkm1.plot
+```
+
+XXX Order lieber Boxplots? Da würde ich gern noch die Mittelwerte mit einer Linie verbinden. XXX
+
+```{r plot boxplot by groups, echo = FALSE}
+lkm1.boxplot <- ggplot() +
+              geom_boxplot(data = lkm1.plot.sd, 
+                           aes(x = perspective, y = mean), )+ 
+  geom_line(data = lkm1.plot.sd, mapping = aes(x = perspective, y = mean)) + 
+  geom_jitter(data = lkm1.plot.sd, aes(x = perspective, y = mean, colour = target), size = 2, width = 0.1) +
+    scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,4))+
+  labs(x="perspective", y="value", title = "positive climate and motivation")+ 
+  theme_classic()
+lkm1.boxplot
+
+```
+
+#### clarity and structuredness
+
+```{r mean clarity and structuredness by session, echo = FALSE}
+
+### clarity and structuredness session 1
+
+# filter by parameter variable, i.e. create a subset for each session
+ks1.data <- raw.data %>% filter(scale == "Klarheit und Strukturiertheit",
+                               session == "1")
+
+view (ks1.data)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+ks1.data <- ks1.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# # create  mean, min, max, sd of classroom management
+# meankm1 <- mean(km1.data$value)
+# minkm1 <- min(km1.data$value)
+# maxkm1 <- max(km1.data$value)
+# sdkm1 <- sd(km1.data$value)
+# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
+# mdkm1 <- median(km1.data$value)
+
+```
+
+The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***clarity and structuredness*** in session 1 for each perspective and target.
+The target always corresponds with the perspective of the teacher, i.e.
+teacher = target A.
+
+XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX
+
+``` {r clarity and structuredness data table, echo=FALSE}
+
+ks1.data %>% # select data
+  group_by(target,perspective) %>%
+  summarise(N = n_distinct(personID),
+            "mean" = round(mean(value), 2),
+            "min" = min(value),
+            "max" = max(value),
+            "sd" = sd(value),
+            "median" = median(value)
+            ) %>% 
+  knitr::kable(digits = 2)
+
+```
+
+```{r clarity and structuredness line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
+
+# to create error bars, we need to summarize the data in a separate data frame
+ks1.plot.sd <- ks1.data %>%
+  group_by(perspective, target, .drop=TRUE) %>%
+  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# and here comes the long plot
+ks1.plot<-ggplot(data = ks1.plot.sd,
+                   aes(x = perspective, y = mean,
+                       group = target, colour = target)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  labs(data = ks1.data, y = "value", x = NULL,
+       title="clarity and structuredness" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+ks1.plot
+```
+
+#### activation and support
+
+```{r mean activation and support by session, echo = FALSE}
+
+### activation and support session 1
+
+# filter by parameter variable, i.e. create a subset for each session
+af1.data <- raw.data %>% filter(scale == "Aktivierung und Förderung",
+                               session == "1")
+
+view (af1.data)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+af1.data <- af1.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# # create  mean, min, max, sd of classroom management
+# meankm1 <- mean(km1.data$value)
+# minkm1 <- min(km1.data$value)
+# maxkm1 <- max(km1.data$value)
+# sdkm1 <- sd(km1.data$value)
+# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
+# mdkm1 <- median(km1.data$value)
+
+```
+
+The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***activation and support*** in session 1 for each perspective and target.
+The target always corresponds with the perspective of the teacher, i.e.
+teacher = target A.
+
+XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX
+
+``` {r activation and support data table, echo=FALSE}
+
+af1.data %>% # select data
+  group_by(target,perspective) %>%
+  summarise(N = n_distinct(personID),
+            "mean" = round(mean(value), 2),
+            "min" = min(value),
+            "max" = max(value),
+            "sd" = sd(value),
+            "median" = median(value)
+            ) %>% 
+  knitr::kable(digits = 2)
+
+```
+
+```{r activation and support line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
+
+# to create error bars, we need to summarize the data in a separate data frame
+af1.plot.sd <- af1.data %>%
+  group_by(perspective, target, .drop=TRUE) %>%
+  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# and here comes the long plot
+af1.plot<-ggplot(data = af1.plot.sd,
+                   aes(x = perspective, y = mean,
+                       group = target, colour = target)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  labs(data = af1.data, y = "value", x = NULL,
+       title="activation and support" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+af1.plot
+```
+
+#### presence: posture and gaze
+
+```{r mean presence: posture and gaze by session, echo = FALSE}
+
+### presence: posture and gaze session 1
+
+# filter by parameter variable, i.e. create a subset for each session
+phb1.data <- raw.data %>% filter(scale == "Präsenz/Haltung_Blick",
+                               session == "1")
+
+view (phb1.data)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+phb1.data <- phb1.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# # create  mean, min, max, sd of classroom management
+# meankm1 <- mean(km1.data$value)
+# minkm1 <- min(km1.data$value)
+# maxkm1 <- max(km1.data$value)
+# sdkm1 <- sd(km1.data$value)
+# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
+# mdkm1 <- median(km1.data$value)
+
+```
+
+The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***presence: posture and gaze*** in session 1 for each perspective and target.
+The target always corresponds with the perspective of the teacher, i.e.
+teacher = target A.
+
+XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX
+
+``` {r presence: posture and gaze data table, echo=FALSE}
+
+phb1.data %>% # select data
+  group_by(target,perspective) %>%
+  summarise(N = n_distinct(personID),
+            "mean" = round(mean(value), 2),
+            "min" = min(value),
+            "max" = max(value),
+            "sd" = sd(value),
+            "median" = median(value)
+            ) %>% 
+  knitr::kable(digits = 2)
+
+```
+
+```{r presence: posture and gaze line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
+
+# to create error bars, we need to summarize the data in a separate data frame
+phb1.plot.sd <- phb1.data %>%
+  group_by(perspective, target, .drop=TRUE) %>%
+  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# and here comes the long plot
+phb1.plot<-ggplot(data = phb1.plot.sd,
+                   aes(x = perspective, y = mean,
+                       group = target, colour = target)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  labs(data = phb1.data, y = "value", x = NULL,
+       title="presence: posture and gaze" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+phb1.plot
+
+```
+
+#### presence: voice
+XXX aus unerklärlichen Gründen wird mir "No data available in table" angezeigt, wenn ich versuche, Präsenz/Stimme für Session1 zu filtern. Hab den Fehler leider noch nicht gefunden... XXX
+```{r mean presence: voice by session, echo = FALSE}
+
+### presence: voice session 1
+
+# filter by parameter variable, i.e. create a subset for each session
+ps1.data <- raw.data %>% filter(scale == "Präsenz/Stimme",
+                                session == "1")
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+ps1.data <- ps1.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# # create  mean, min, max, sd of classroom management
+# meankm1 <- mean(km1.data$value)
+# minkm1 <- min(km1.data$value)
+# maxkm1 <- max(km1.data$value)
+# sdkm1 <- sd(km1.data$value)
+# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
+# mdkm1 <- median(km1.data$value)
+
+```
+
+The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***presence: voice*** in session 1 for each perspective and target.
+The target always corresponds with the perspective of the teacher, i.e.
+teacher = target A.
+
+XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX
+
+``` {r presence: voice data table, echo=FALSE}
+# 
+# ps1.data %>% # select data
+#   group_by(target,perspective) %>%
+#   summarise(N = n_distinct(personID),
+#             "mean" = round(mean(value), 2),
+#             "min" = min(value),
+#             "max" = max(value),
+#             "sd" = sd(value),
+#             "median" = median(value)
+#             ) %>% 
+#   knitr::kable(digits = 2)
+
+```
+
+```{r presence: voice line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
+
+# # to create error bars, we need to summarize the data in a separate data frame
+# ps1.plot.sd <- ps1.data %>%
+#   group_by(perspective, target, .drop=TRUE) %>%
+#   summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+# 
+# # and here comes the long plot
+# ps1.plot<-ggplot(data = ps1.plot.sd,
+#                    aes(x = perspective, y = mean,
+#                        group = target, colour = target)) +
+#   geom_line()+
+#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+#   theme_light() +
+#   ylim(1,4)+
+#   labs(data = ps1.data, y = "value", x = NULL,
+#        title="presence: voice" ,
+#        subtitle=NULL)+
+#   theme(legend.position="bottom",
+#         panel.spacing.x = ,
+#         plot.title = element_text(hjust = 0.5))+
+#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+#   coord_flip()
+# ps1.plot
+
+```
+
+#### presence: verbal and non-verbal intervention
+
+```{r mean presence: verbal and non-verbal intervention by session, echo = FALSE}
+
+### presence: verbal and non-verbal intervention session 1
+
+# filter by parameter variable, i.e. create a subset for each session
+pi1.data <- raw.data %>% filter(scale == "Präsenz/verbale_nonberbale Intervention",
+                               session == "1")
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+pi1.data <- pi1.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# # create  mean, min, max, sd of classroom management
+# meankm1 <- mean(km1.data$value)
+# minkm1 <- min(km1.data$value)
+# maxkm1 <- max(km1.data$value)
+# sdkm1 <- sd(km1.data$value)
+# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
+# mdkm1 <- median(km1.data$value)
+
+```
+
+The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***presence: verbal and non-verbal intervention*** in session 1 for each perspective and target.
+The target always corresponds with the perspective of the teacher, i.e.
+teacher = target A.
+
+XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX
+
+``` {r presence: verbal and non-verbal intervention data table, echo=FALSE}
+
+pi1.data %>% # select data
+  group_by(target,perspective) %>%
+  summarise(N = n_distinct(personID),
+            "mean" = round(mean(value), 2),
+            "min" = min(value),
+            "max" = max(value),
+            "sd" = sd(value),
+            "median" = median(value)
+            ) %>% 
+  knitr::kable(digits = 2)
+
+```
+
+```{r presence: verbal and non-verbal intervention line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
+
+# to create error bars, we need to summarize the data in a separate data frame
+pi1.plot.sd <- pi1.data %>%
+  group_by(perspective, target, .drop=TRUE) %>%
+  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# and here comes the long plot
+pi1.plot<-ggplot(data = pi1.plot.sd,
+                   aes(x = perspective, y = mean,
+                       group = target, colour = target)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  labs(data = pi1.data, y = "value", x = NULL,
+       title="presence: verbal and non-verbal intervention" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+pi1.plot
+
+```
+
+#### turn taking
+
+```{r mean turn taking by session, echo = FALSE}
+
+### turn taking session 1
+
+# filter by parameter variable, i.e. create a subset for each session
+redeanteil1.data <- raw.data %>% filter(scale == "Redeanteil",
+                               session == "1")
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+redeanteil1.data <- redeanteil1.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# # create  mean, min, max, sd of classroom management
+# meankm1 <- mean(km1.data$value)
+# minkm1 <- min(km1.data$value)
+# maxkm1 <- max(km1.data$value)
+# sdkm1 <- sd(km1.data$value)
+# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
+# mdkm1 <- median(km1.data$value)
+
+```
+
+The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***turn taking*** in session 1 for each perspective and target.
+The target always corresponds with the perspective of the teacher, i.e.
+teacher = target A.
+
+XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX
+
+``` {r turn taking data table, echo=FALSE}
+
+redeanteil1.data %>% # select data
+  group_by(target,perspective) %>%
+  summarise(N = n_distinct(personID),
+            "mean" = round(mean(value), 2),
+            "min" = min(value),
+            "max" = max(value),
+            "sd" = sd(value),
+            "median" = median(value)
+            ) %>% 
+  knitr::kable(digits = 2)
+
+```
+
+```{r turn taking line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
+
+# to create error bars, we need to summarize the data in a separate data frame
+redeanteil1.plot.sd <- redeanteil1.data %>%
+  group_by(perspective, target, .drop=TRUE) %>%
+  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# and here comes the long plot
+redeanteil1.plot<-ggplot(data = redeanteil1.plot.sd,
+                   aes(x = perspective, y = mean,
+                       group = target, colour = target)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1, 100)+
+  labs(data = redeanteil1.data, y = "value", x = NULL,
+       title="turn taking" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+redeanteil1.plot
+
+```
+
+#### natural behaviour
+
+```{r mean natural behaviour by session, echo = FALSE}
+
+### natural behaviour session 1
+
+# filter by parameter variable, i.e. create a subset for each session
+m1.data <- raw.data %>% filter(scale == "Manipulationsitem",
+                               session == "1")
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+m1.data <- m1.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# # create  mean, min, max, sd of classroom management
+# meankm1 <- mean(km1.data$value)
+# minkm1 <- min(km1.data$value)
+# maxkm1 <- max(km1.data$value)
+# sdkm1 <- sd(km1.data$value)
+# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
+# mdkm1 <- median(km1.data$value)
+
+```
+
+The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***natural behaviour*** in session 1 for each perspective and target.
+The target always corresponds with the perspective of the teacher, i.e.
+teacher = target A.
+
+XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX
+
+``` {r natural behaviour data table, echo=FALSE}
+
+m1.data %>% # select data
+  group_by(target,perspective) %>%
+  summarise(N = n_distinct(personID),
+            "mean" = round(mean(value), 2),
+            "min" = min(value),
+            "max" = max(value),
+            "sd" = sd(value),
+            "median" = median(value)
+            ) %>% 
+  knitr::kable(digits = 2)
+
+```
+
+```{r natural behaviour line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
+
+# to create error bars, we need to summarize the data in a separate data frame
+m1.plot.sd <- m1.data %>%
+  group_by(perspective, target, .drop=TRUE) %>%
+  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# and here comes the long plot
+m1.plot<-ggplot(data = m1.plot.sd,
+                   aes(x = perspective, y = mean,
+                       group = target, colour = target)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  labs(data = m1.data, y = "value", x = NULL,
+       title="natural behaviour" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+m1.plot
+```
+
+### TO DO
+
+- session 2 plotten
+- anderen plot für redeanteil (barplot?)
+- fehler finden für presence: voice
 

### 2021-01-20 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
update questionnaire

@@
 # file should be in a subfolder named "data" for the script to select it
-raw.data<-read.table("./data/short_questionnaire_data_1301211.txt",sep="\t", header=T)
+raw.data<-read.table("./data/short_questionnaire_data_2001211.txt",sep="\t", header=T)
 
 # loading packages
+# install.packages("stringr") # install stringr to use the filter() function with text data
+library(stringr)
+
 # if a package is not installed on the current machine, it will install it
@@
 ### Data collection
-For the pilot study, we collected questionnaire data from N = `r sum(n_distinct(raw.data$personID))` subjects in `r sum(n_distinct(raw.data$session))` sessions.
+For the pilot study, we collected questionnaire data from N = 8 subjects in `r sum(n_distinct(raw.data$session))` sessions.
 The questionnaires were answered after each lesson (10min) by an observer, the teacher and the three teachers acting as the class.
@@
 ```{r overview demographics data table, echo=FALSE}
+
+# counting male / female 
+sex <- raw.data %>% filter(what == "head")
+
+# # converting column "group" from character into numeric 
+# raw.data <- raw.data %>%  mutate(group = as.numeric(as.character(group)))
+
+# demographics, grouped by group, filtered by perspective (N, meanage, max, min age)
 raw.data %>% # select data
-  group_by(session, perspective) %>%
-  summarise(N = n_distinct(personID),
+  filter(perspective == "teacher") %>%
+  group_by(group) %>%
+  summarise(N = n_distinct(groupID),
+            "male" = sum(sex),
             "mean age" = round(mean(age), 2),

### 2021-01-21 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
update R script

--- 2021-01-18 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
@@
 # file should be in a subfolder named "data" for the script to select it
-raw.data<-read.table("./data/short_questionnaire_data_1301211.txt",sep="\t", header=T)
+raw.data<-read.table("./data/short_questionnaire_data_2101211.txt",sep="\t", header=T)
 
 # loading packages
+# install.packages("stringr") # install stringr to use the filter() function with text data
+library(stringr)
+
 # if a package is not installed on the current machine, it will install it
@@
 The study was conducted as a lab study with simulated scripted mini-lessons (10min per lesson).
-Data was collected from N = 8 teachers and N = 2 observers in 2 sessions.
+Data was collected from N = 8 teachers in 2 sessions.
+
 In each session, one subject took the role of teacher, while the other teachers acted as the class.
@@
 An external observer also answered a questionnaire.
-In addition, the teacher is asked to give a self-assessment on his/her classroom management.
+In addition, the teacher was asked to give a self-assessment on his/her classroom management.
 
 ### Data collection
-For the pilot study, we collected questionnaire data from N = `r sum(n_distinct(raw.data$personID))` subjects in `r sum(n_distinct(raw.data$session))` sessions.
-The questionnaires were answered after each lesson (10min) by an observer, the teacher and the other teachers acting as the class.
+For the pilot study, we collected questionnaire data from N = 8 subjects in `r sum(n_distinct(raw.data$session))` sessions.
+The questionnaires were answered after each lesson (10min) by an observer, the teacher and the three teachers acting as the class.
 
@@
 ```{r overview demographics data table, echo=FALSE}
-raw.data %>% # select data
-  group_by(session, perspective) %>%
-  summarise(N = n_distinct(personID),
+
+# demographics, grouped by group (N, gender, meanage, max, min age)
+raw.data %>%
+  filter(what == "head") %>%
+  group_by(group) %>%
+  summarise(N=n(),
+            "male" = sum(gender),
             "mean age" = round(mean(age), 2),
@@
 
-### Plotting questionnaire data
+### Plotting scales
 
-```{r mean classroom management by session, echo = FALSE}
+The questionnaire contains following scales:
 
-### classroom management session 1
+(1) classroom management
+(2) positive climate and motivation
+(3) clarity and structuredness
+(4) activation and support
+(5) presence: posture and gaze
+(6) presence: voice
+(7) presence: verbal and non-verbal intervention
+(8) turn taking
+(9) natural behaviour
 
-# filter by parameter variable, i.e. create a subset for each session
-km1.data <- raw.data %>% filter(scale == "Klassenmanagement",
-                               session == "1")
+```{r cleaning items, echo = FALSE}
 
-view (km1.data)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-km1.data <- km1.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# create  mean, min, max, sd of classroom management
-meankm1 <- mean(km1.data$value)
-minkm1 <- min(km1.data$value)
-maxkm1 <- max(km1.data$value)
-sdkm1 <- sd(km1.data$value)
-Nkm1 <- length(unique(km1.data$personID))
-mdkm1 <- median(km1.data$value)
-
-km1.data <- raw.data %>% filter(scale == "Klassenmanagement",
-                               session == "1") %>% 
-  group_by(perspective, target) %>%
-  summarise(N = n_distinct(personID),
-            "mean age" = round(mean(age), 2),
-            "min age" = min(age),
-            "max age" = max(age),
-            "sd age" = round(sd(age), 2),
-            ) %>% 
-  knitr::kable(digits = 2)
-
-### classroom management session 2
-
-# filter by parameter variable, i.e. create a subset for each session
-km2.data <- raw.data %>% filter(scale == "Klassenmanagement",
-                               session == "2")
-
-view (km2.data)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-km2.data <- km2.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# create  mean, min, max, sd of classroom management
-meankm2 <- mean(km2.data$value)
-minkm2 <- min(km2.data$value)
-maxkm2 <- max(km2.data$value)
-sdkm2 <- sd(km2.data$value)
-Nkm2<-length(unique(km2.data$personID))
+# to compare both sessions filter only Identical items
+raw.data <- raw.data  %>% filter(str_detect(shortID, 
+                                                 paste(c("km_mitbekommen",
+                                                         "km_klar",
+                                                         "km_ungestört",
+                                                         "km_aktiv",
+                                                         "lkm_freundlich",
+                                                         "lkm_interesse",
+                                                         "lkm_kritik",
+                                                         "lkm_ausreden",
+                                                         "lkm_überlegen",
+                                                         "lkm_rückmeldungen",
+                                                         "ks_funktion",
+                                                         "ks_verständlich",
+                                                         "ks_sichtbar",
+                                                         "af_beiträge",
+                                                         "af_wechselseitig",
+                                                         "af_nachdenken",
+                                                         "phb_stand",
+                                                         "phb_augen",
+                                                         "phb_blick",
+                                                         "phb_vorsichgeht",
+                                                         "phb_raum",
+                                                         "phb_gestik",
+                                                         "phb_alleangesehen",
+                                                         "ps_deutlich",
+                                                         "ps_klar",
+                                                         "ps_impulse",
+                                                         "pi_nonverbal",
+                                                         "pi_zubewegen",
+                                                         "pi_direkt",
+                                                         "redeanteil",
+                                                         "m_natürlich",
+                                                         "m_fiktiv",
+                                                         "m_verhalten"),
+                                                    collapse = '|')))
 
@@
 
-The item "classroom management"  was rated by the observer, the teacher and students on average in session 1 with `r round(meankm1, 2)` (min = `r minkm1`; max = `r maxkm1`; SD = `r round(sdkm1,2)`; N = `r Nkm1`; lickert-scale 1-4; 4 = best evaluation) and in session 2 with `r round(meankm2, 2)` (min = `r minkm2`; max = `r maxkm2`; SD = `r round(sdkm2,2)`; N = `r Nkm2`; lickert-scale 1-4; 4 = best evaluation).
+The scales on the quality of teaching are a validated questionnaire (Helmke 2014).Whereas the scales on the teacher's presence behaviour were derived from the research literature and were used in the pilot for the first time.
+For this reason, the various items for the scales ***presence*** are presented below.
 
-```{r Modul horicontal Plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
+### presence: posture and gaze
 
-# to create error bars, we need to summarise the data in a seperate dataframe
-modul.plot.sd <-modul.plot.data %>%
-  group_by(itemfulltext, Teilnehmende, .drop=TRUE) %>%
+```{r mean presence: posture and gaze, echo = FALSE}
+
+### presence: posture and gaze
+
+# filter by parameter variable, i.e. create a subset for presence: posture and gaze
+phb.data <- raw.data %>% filter(scale == "Präsenz/Haltung_Blick")
+
+view (phb.data)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+phb.data <- phb.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# create  mean, min, max, sd of presence: posture/gaze
+meanphb <- mean(phb.data$value)
+minphb <- min(phb.data$value)
+maxphb <- max(phb.data$value)
+sdphb <- sd(phb.data$value)
+Nphb <- phb.data %>% summarise(N = n_distinct(personID))
+
+# filter by parametervariable, i.e. create a subset for experts and novice
+expert.data <- phb.data %>% filter (group == "expert")
+novice.data <- phb.data %>% filter (group == "novice")
+
+# create mean, min, max, sd for expert/novice
+# expert
+expert.meanphb <- mean(expert.data$value)
+expert.minphb <- min(expert.data$value)
+expert.maxphb <- max(expert.data$value)
+expert.sdphb <- sd(expert.data$value)
+expert.Nphb<-length(unique(expert.data$personID))
+
+#novice
+novice.meanphb <- mean(novice.data$value)
+novice.minphb <- min(novice.data$value)
+novice.maxphb <- max(novice.data$value)
+novice.sdphb <- sd(novice.data$value)
+novice.Nphb<-length(unique(novice.data$personID))
+
+```
+
+The mean for all items of the scale ***presence: posture and gaze*** is `r round(meanphb, 2)` (min = `r minphb`; max = `r maxphb`; SD = `r round(sdphb,2)`; N = `r Nphb`; lickert-scale 1-4; 4 = best evaluation).
+
+The mini-lessons of the experts were evaluated on average with `r round(expert.meanphb, 2)` (min = `r expert.minphb`; max = `r expert.maxphb`; SD = `r round(expert.sdphb,2)`; N = `r expert.Nphb`).
+
+The mini-lessons of the novices were evaluated on average with `r round(novice.meanphb, 2)` (min = `r novice.minphb`; max = `r novice.maxphb`; SD = `r round(novice.sdphb,2)`; N = `r novice.Nphb`).
+
+```{r presence: posture and gaze line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
+
+phb.data$group <- as.factor(phb.data$group)
+
+# to create error bars, we need to summarize the data in a separate data frame
+phb.plot.sd <- phb.data %>%
+  filter (perspective == "teacher") %>%
+  group_by(group, item.wordings, .drop=TRUE) %>%
   summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
@@
 # and here comes the long plot
-modul.plot<-ggplot(data = modul.plot.sd,
-                           aes(x = itemfulltext, y = mean,
-                               group=Teilnehmende, colour = Teilnehmende)) +
+phb.plot<-ggplot(data = phb.plot.sd,
+                  aes(x = item.wordings, y = mean,
+                      group = group, colour = group)) +
   geom_line()+
@@
   theme_light() +
-  ylim(1,5)+
-  labs(data = modul.plot.data, y = "Ausprägung", x = NULL,
-       title="Modulbewertung" ,
+  ylim(1,4)+
+  facet_grid()+
+  labs(data = phb.data, y = "value", x = NULL,
+       title="presence: posture and gaze" ,
        subtitle=NULL)+
@@
   coord_flip()
-modul.plot
+phb.plot
 
@@
 
-### Comparing Performance across age-groups and conditions
-We used Wilcoxon/Mann-Whitney-U-tests to test for significant differences in children's performance across age-groups and conditions respectively.
+### Overview all scales
 
-xxx To Do xxx
+```{r mean classroom management, echo = FALSE}
 
-### Full Analysis (GLMM, ANOVA)
-We are going to analyze our outcome (correct choice 0/1) in a 2x2 design (condition (comm, noncomm); age (3yo, 4yo) using either a GLMM or ANOVA depending on prior tests on data structure and model stability.
+### classroom management
 
-xxx To Do xxx
+# filter by parameter variable, i.e. create a subset for each session
+km.data <- raw.data %>% filter(scale == "Klassenmanagement")
+
+view (km.data)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# create  mean, min, max, sd of classroom management
+km.data.plot %>% km.data %>%
+
+          meankm <- mean(km.data$value)
+          minkm <- min(km.data$value)
+          maxkm <- max(km.data$value)
+          sdkm <- sd(km.data$value)
+          Nkm <- km.data %>% summarise(N = n_distinct(personID))
+          mdkm <- median(km.data$value)
+
+```
+
+### to do
+
+- vergessen: Berufserfahrung bei Demographie mit aufnehmen
+- selbst und fremdeinschätzung durch facet_grid bei plot hinzufügen
 
 # References
+
+Helmke, A., Helmke, T., Lenske, G., Pham, G., Praetorius, A.
+K., Schrader, F.
+W., & AdeThurow, M.
+(2014).
+Unterrichtsdiagnostik mit EMU.
+Aus-und Fortbildung der Lehrkräfte in Hinblick auf Verbesserung der Diagnosefähigkeit, Umgang mit Heterogenität und individuelle Förderung, 149-163.
 

### 2021-01-21 studies/2020_Aperol_Git/questionnaire data/mean_scales.R

@@ -1,0 +1,667 @@
+#### Session 1 
+
+#### classroom management
+
+```{r mean classroom management by session, echo = FALSE}
+
+### classroom management session 1 
+
+# filter by parameter variable, i.e. create a subset for each session
+km1.data <- raw.data %>% filter(scale == "Klassenmanagement",
+                                session == "1")
+
+view (km1.data)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+km1.data <- km1.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+
+# # create  mean, min, max, sd of classroom management
+# meankm1 <- mean(km1.data$value)
+# minkm1 <- min(km1.data$value)
+# maxkm1 <- max(km1.data$value)
+# sdkm1 <- sd(km1.data$value)
+# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
+# mdkm1 <- median(km1.data$value)
+
+```
+
+The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***classroom management*** in session 1 for each perspective and target. The target always corresponds with the perspective of the teacher, i.e. teacher = target A. 
+
+``` {r classroom management data table, echo=FALSE}
+
+km1.data %>% # select data
+  group_by(target,perspective) %>%
+  summarise(N = n_distinct(personID),
+            "mean" = round(mean(value), 2),
+            "min" = min(value),
+            "max" = max(value),
+            "sd" = sd(value),
+            "median" = median(value)
+  ) %>% 
+  knitr::kable(digits = 2)
+
+```
+
+```{r classroom management line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
+
+# to create error bars, we need to summarize the data in a separate data frame
+km1.plot.sd <- km1.data %>%
+  group_by(perspective, target, .drop=TRUE) %>%
+  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# and here comes the long plot
+km1.plot<-ggplot(data = km1.plot.sd,
+                 aes(x = perspective, y = mean,
+                     group = target, colour = target)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
[…]

### 2021-01-22 paper_1/paper_1.Rmd
pics in manuscript paper1 AND tutorial papaja in paper1 folder

@@
 
-floatsintext      : no
+floatsintext      : yes
 figurelist        : no
@@
 Furthermore, in contrast to novices, experts are able to focus their attention on the entire class and guide the class while giving feedback to individual students and answering questions [@cortina2015low].
+
+Hey Mandy, hier wollte ich dir mal zeigen wie man Bilder in papaja einbindet. Viel Spass damit. Ein Beispiel für Tabellen und Graphen machen wir auch zeitnah.
+
+(ref:thisisdialectical-caption) Illustration of comic material that made the second author of this paper chuckle a bit. For advice on how to insert images, please see the code chunk.
+
+```{r dialectical, fig.cap = "(ref:thisisdialectical-caption)", fig.align = "center", echo = FALSE}
+
+knitr::include_graphics("./pictures/thisisdialectical.png", dpi = 108)
+
+# # How to insert images in papaja
+# - pictures must be png
+# - I created a pictures folder in the main folder, just dumb pictures there
+# - you just need to hand the name and path of the picture to the knitr::: function (see above)
+# - the dpi argument is for adjusting the size on the page in pixels
+
+# in order to write the caption, you have to use the line just above the code chunk (ref:YOURTEXT-caption) and then just write behing it
+# the code chunk then opens and after "r" it needs to provide a name for the code chunk, must be unique in the document
+# the fig.cap = then calls the text from the line just above
+# fig.align allows to position the pic on page, center ist probablby best
+# echo = false ensures that the code chunk does not occur in the pdf
+# Now, go and try putting your own images in the paper 
+#
+# TIP = check line 46 in this manuscript. THis section ets global properties for how graphs are put in the paper. 
+#         if floatsintext      : yes  --> pics, graphs, tables will be put where the code chunk is
+#         if floatsintext      : no   --> pics, graphs, tables will be put at the end as is required by some journals
+# TIP: check the folder "papaja_example&tutorial" that I put in this folder for paper1
+# Tip: make a bookmark of this and skim through it: http://frederikaust.com/papaja_man/
+
+```
 

### 2021-01-22 paper_1/paper_1.tex
pics in manuscript paper1 AND tutorial papaja in paper1 folder

@@
   english,
-  man]{apa6}
+  man,floatsintext]{apa6}
 \usepackage{lmodern}
@@
 \hypersetup{
-  pdftitle={The title},
+  pdftitle={Through the eyes of the teacher},
+  pdfauthor={Mandy Klatt1 \& Gregor Kachel1},
   pdflang={en-EN},
@@
   {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\HyOrg@maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
 \makeatother
-\shorttitle{Title}
-\author{First Author\textsuperscript{1}\ \& Ernst-August Doelle\textsuperscript{1,2}}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
-\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
-
-Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: my@email.com}
+\shorttitle{Visual attention in teaching and learning processes}
 \keywords{keywords\newline\indent Word count: X}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
 \usepackage{lineno}
@@
 
-\title{The title}
+\title{Through the eyes of the teacher}
+\author{Mandy Klatt\textsuperscript{1} \& Gregor Kachel\textsuperscript{1}}
+\date{}
 
-\date{}
+\authornote{
+
+Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+
+Enter author note here.
+
+Correspondence concerning this article should be addressed to Mandy Klatt, Egelstraße 2a 04103 Leipzig. E-mail: \href{mailto:mandy.klatt@uni-leipzig.de}{\nolinkurl{mandy.klatt@uni-leipzig.de}}
+
+}
+
+\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Leipzig}
 
@@
 
+\hypertarget{state-of-research}{%
+\section{State of research}\label{state-of-research}}
+
+Teaching and classroom management are multidimensional settings in which teachers have to respond immediately to events as they develop (Barnes, 2004).
+The different interests and abilities of students must be managed in a way that maximizes the active learning time of students and minimizes disruptions whilst teaching.
+Learning to develop such classroom management skills and to teach effectively is a complicated and complex process (Wolff, Jarodzka, \& Boshuizen, 2017).
+
+During teaching, teachers must be able to select from a variety of visual and acoustic impressions to focus their attention on the essential and to distinguish between relevant and irrelevant events.
+This ability is called professional vision and is a key component of teacher expertise and successful teaching (Barth, 2017).
+Eye tracking technology has become a reliable means to study teachers' visual focus of attention (Bogert, 2016; Pouta, Lehtinen, \& Palonen, 2020; Wolff et al., 2017)
+
+Educational research has repeatedly shown that there are differences between experienced and novice teachers in terms of perception and behavioral competencies (Barth, 2017; Bogert, 2016; Wolff et al., 2017).
+For example, experts direct their attention more often and more evenly to all students, whereas novices only direct their attention to some students.
+The frequency and duration of fixations as eye movement are decisive (Stuermer, Seidel, Mueller, Häusler, \& Cortina, 2017).
+Mobile eye-tracking technology has also shown that experienced teachers distribute their focus more efficiently to solve tasks (Jarodzka, Scheiter, Gerjets, \& Van Gog, 2010).
+Furthermore, in contrast to novices, experts are able to focus their attention on the entire class and guide the class while giving feedback to individual students and answering questions (Cortina, Miller, McKenzie, \& Epstein, 2015).
+
+Hey Mandy, hier wollte ich dir mal zeigen wie man Bilder in papaja einbindet. Viel Spass damit. Ein Beispiel für Tabellen und Graphen machen wir auch zeitnah.
+
+\begin{figure}
+
+{\centering \includegraphics{./pictures/thisisdialectical}
+
+}
+
+\caption{Illustration of comic material that made the second author of this paper chuckle a bit. For advice on how to insert images, please see the code chunk.}\label{fig:dialectical}
+\end{figure}
+
+\hypertarget{research-questions}{%
+\subsection{Research questions}\label{research-questions}}
+
+The first study is a laboratory study that uses a quasi-experimental cross-sectional study design to investigate whether the experience of teachers has an influence on the perception of and response to disruptions.
+The disturbances are experimentally varied using a previously written script.
+Thus, the aim is to find out whether differences in the allocation of attention between expertise groups can be detected in this controlled context.
+
+In order to answer this question, the hypothesis was formulated that teachers with more professional experience not only notice more disturbances but also notice them faster.
+In the hypothesis, therefore, it is necessary to check what has already been shown in the research literature: In complex teaching situations, experts have a more structured and elaborate professional knowledge than novices in order to perceive and interpret relevant events and to act appropriately (Berliner, 2001; Lachner, Jarodzka, \& Nückles, 2016).
+
 \hypertarget{methods}{%
@@
 
-\hypertarget{material}{%
-\subsection{Material}\label{material}}
+For the sample recruitment of the subjects (N = 48, experts n = 24, novices n = 24), schools in the city of Leipzig in Saxony were contacted.
+The institutions as well as the subjects were informed in detail about the aim and intention of the dissertation project in advance.
+Participation in the study was voluntary and only took place after written consent has been given.
+
+The selection of the subjects was based on extreme groups, whereby professional experience is the crucial criterion for the selection of experts or novices.
+Novices were recruited as teachers who have been working in the teaching profession for no more than 3 years, whereas experts were considered to have professional experience of 10 years or more (Messner \& Reusser, 2000).
 
@@
 
+For this study, lesson units of n = 24 experts and n = 24 novices were recorded by the mobile laboratory of the Department of Empirical School and Classroom Research at the University of Leipzig.
+The two extreme groups were each divided into groups of four, with one group being invited on each of six different dates.
+All participants were asked to hold a 15-minute lesson.
+The duration of each appointment was approximately 2h30min: per extreme group 4 x 15min briefing, 15min lesson units, 10min technical preparation and follow-up and 5min buffer/break.
+
+One person from the group of 4 acted as a teacher, the other three subjects acted as the class.
+The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disturbances in the classroom (e.g.~putting their heads on the table, chatting, looking at their mobile phones, etc.).
+
+The lesson disturbances were displayed as instructions during the lesson for all \enquote{students} but not the teacher.
+In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase.
+In addition, the order of the data collection was taken into account in the analyses and variance caused by order was controlled.
+
+By using mobile eye-trackers, the gaze and behavior of the experts and novices was recorded during the lesson.
+In addition, what the participating teachers said was recorded with a portable microphone.
+Other sounds and voices were recorded with an audio recorder installed in the middle of the laboratory.
+Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles.
+One camera was installed to film the class from the side.
+Two more cameras were installed on the blackboard and at the end of the laboratory to film the teacher and class from the front and back.
+In addition, it the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.
+
+The lessons recorded on video were coded in a post-hoc procedure with a coding software by previously trained raters.
+The statistical data have been analyzed by using the program RStudio {[}Link: \url{https://rstudio.com/}{]}.
+
+\hypertarget{measures}{%
+\subsection{Measures}\label{measures}}
+
+\hypertarget{eye-tracking-equipment}{%
+\subsubsection{Eye-tracking equipment}\label{eye-tracking-equipment}}
+
+A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements.
+The head unit is a measuring device with different sensitive sensors.
+A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
+Infrared light illuminators support the eye tracking sensors which record the eye orientation.
+The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
+The scene camera has a field of view of 90 deg.
+in 16:9 format (82 deg.
+horizontal and 52 deg.
+vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
+The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
+
+The Tobii Pro Glasses 2 software allows for non-screen based recordings of a participants' attention while moving in real-world settings.
+The recordings of the glasses contain both HD-video from the subject's perspective as well as the respective gaze data mapped onto the video.
+In order to map multiple recordings to AOIs, it is necessary to import the eye-tracking recordings into the Tobii Pro Analyzer software.
+Also, it is necessary to create a reference image of the scene in which one wishes to plot the gaze data (i.e.~snapshot).
+Once the snapshot is imported, the gaze recordings of multiple recordings can be mapped to the reference image and analyzed in aggregated form.
+Tobii Pro does not allow to do AOI based analyses within Pro Lab.
+Also, the dependency on snapshot reference images makes this approach impractical when working in different settings, i.e.~different classrooms with various participants.
+Finally, mapping gaze to people or any moving objects complicated the analyses further.
+
 \hypertarget{data-analysis}{%
@@
 
-We used R (Version 3.6.1; R Core Team, 2019) and the R-package \emph{papaja} (Version 0.1.0.9942; Aust \& Barth, 2020) for all our analyses.
+We used R (Version 4.0.2; R Core Team, 2019) and the R-packages \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), and \emph{papayar} (Muschelli, 2016) for all our analyses.
+
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 
@@
 
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+
 \hypertarget{discussion}{%
 \section{Discussion}\label{discussion}}
+
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 
@@
 
+\leavevmode\hypertarget{ref-barnes2004significance}{}%
+Barnes, D. (2004). The significance of teachers' frames for teaching. In \emph{Teachers and teaching} (pp. 16--38). Routledge.
+
+\leavevmode\hypertarget{ref-barth2017professionelle}{}%
+Barth, V. L. (2017). \emph{Professionelle wahrnehmung von störungen im unterricht}. Springer.
+
+\leavevmode\hypertarget{ref-berliner2001learning}{}%
+Berliner, D. C. (2001). Learning about and learning from expert teachers. \emph{International Journal of Educational Research}, \emph{35}(5), 463--482.
+
+\leavevmode\hypertarget{ref-bogert2016visualperception}{}%
+Bogert, N.
+J.
+van den.
+(2016).
+\emph{On teachers' visual perception and interpretation of classroom events using eye tracking and collaborative tagging methodologies}.
+Technische Universiteit Eindhoven.
+
+\leavevmode\hypertarget{ref-cortina2015low}{}%
+Cortina, K.
+S., Miller, K.
+F., McKenzie, R., \& Epstein, A.
+(2015).
+Where low and high inference data converge: Validation of class assessment of mathematics instruction using mobile eye tracking with expert and novice teachers.
+\emph{International Journal of Science and Mathematics Education}, \emph{13}(2), 389--403.
+
+\leavevmode\hypertarget{ref-jarodzka2010eyes}{}%
+Jarodzka, H., Scheiter, K., Gerjets, P., \& Van Gog, T. (2010). In the eyes of the beholder: How experts and novices interpret dynamic stimuli. \emph{Learning and Instruction}, \emph{20}(2), 146--154.
+
+\leavevmode\hypertarget{ref-lachner2016makes}{}%
+Lachner, A., Jarodzka, H., \& Nückles, M.
+(2016).
+What makes an expert teacher?
+Investigating teachers' professional vision and discourse abilities.
+\emph{Instructional Science}, \emph{44}(3), 197--203.
+
+\leavevmode\hypertarget{ref-messner2000berufliche}{}%
+Messner, H., \& Reusser, K. (2000). Die berufliche entwicklung von lehrpersonen als lebenslanger prozess. \emph{Beiträge Zur Lehrerinnen-Und Lehrerbildung}, \emph{18}(2), 157--171.
+
+\leavevmode\hypertarget{ref-R-papayar}{}%
+Muschelli, J. (2016). \emph{Papayar: View medical research images using the papaya javascript library}. Retrieved from \url{https://CRAN.R-project.org/package=papayar}
+
+\leavevmode\hypertarget{ref-pouta2020student}{}%
+Pouta, M., Lehtinen, E., \& Palonen, T. (2020). Student teachers' and experienced teachers' professional vision of students' understanding of the rational number concept.
+
 \leavevmode\hypertarget{ref-R-base}{}%
 R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-stuermer2017eye}{}%
+Stuermer, K., Seidel, T., Mueller, K., Häusler, J., \& Cortina, K.
+S.
+(2017).
+What is in the eye of preservice teachers while instructing?
+An eye-tracking study about attention processes in different teaching situations.
+\emph{Zeitschrift Für Erziehungswissenschaft}, \emph{20}(1), 75--92.
+
+\leavevmode\hypertarget{ref-wolff2017see}{}%
+Wolff, C.
+E., Jarodzka, H., \& Boshuizen, H.
+P.
+(2017).
+See and tell: Differences between expert and novice teachers' interpretations of problematic classroom management events.
+\emph{Teaching and Teacher Education}, \emph{66}, 295--308.
 

### 2021-01-22 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd

@@
             "min age" = min(age),
-            "max age" = max(age)
+            "max age" = max(age),
+            "experience" = round(mean(experience), 2)
             ) %>% 
@@
 phb.plot.sd <- phb.data %>%
-  filter (perspective == "teacher") %>%
   group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+names(phb.plot.sd)
 
@@
   ylim(1,4)+
-  facet_grid()+
+  facet_grid(~perspective)+
   labs(data = phb.data, y = "value", x = NULL,

### 2021-01-22 paper_1/paper_1.Rmd
table in paper1 with demo data

@@
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
+  Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 
@@
 
-library("papaja")
+# if a package is not installed on the current machine, it will install it
+if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
+if (!require(papaja)) install.packages('papaja'); library(papaja)
+
 r_refs("r-references.bib")
@@
 
+```{r demographicspilot1table,,echo=FALSE}
+
+# prepare data (selected from questionnaire data)
+quest.raw.data<-read.table("./data/short_questionnaire_data_2101211.txt",sep="\t", header=T)
+
+# knock out NAs
+quest.raw.data <- quest.raw.data  %>% filter(
+  personID != "NA")
+
+# create a basic table (tibble) using tidyverse functions
+demo.quest.table <- quest.raw.data %>%
+  filter(what == "head") %>%
+  group_by(group) %>%
+  summarise(N=n(),
+            "male" = sum(gender),
+            "mean age" = round(mean(age), 2),
+            "min age" = min(age),
+            "max age" = max(age),
+            "sd age" = round(sd(age), 2),
+            # "experience" = round(mean(experience), 2) # in order for this to work experience must be turned into integer via as.integer, maybe replace , with .
+            )
+
+# format and insert table in manuscript
+apa_table(
+  demo.quest.table,
+  caption = "Demographic Information",
+  # note = "Write Note here", 
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  )
+
+```
+
 The selection of the subjects was based on extreme groups, whereby professional experience is the crucial criterion for the selection of experts or novices.
@@
 ## Measures
+
+### Questionnaire Data
+*Describe how we collect questionnaire data (paper or online).
+Add some basic information about the structure of the questionnaire.* Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 
@@
 
+### Questionnaire Data
+*Start entering descriptives and plots here* Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+
 Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.

### 2021-01-22 paper_1/paper_1.tex
table in paper1 with demo data

@@
 \abstract{
-One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
-
-Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
-
-One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
-
-One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
-
-Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
-
-One or two sentences to put the results into a more \textbf{general context}.
-
-Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 }
@@
 
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:demographicspilot1table,}Demographic Information}
+
+\small{
+
+\begin{tabular}{lllllll}
+\toprule
+group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{male} & \multicolumn{1}{c}{mean age} & \multicolumn{1}{c}{min age} & \multicolumn{1}{c}{max age} & \multicolumn{1}{c}{sd age}\\
+\midrule
+expert & 2 & 1 & 47.50 & 44 & 51 & 4.95\\
+novice & 6 & 2 & 25.67 & 20 & 33 & 4.89\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 The selection of the subjects was based on extreme groups, whereby professional experience is the crucial criterion for the selection of experts or novices.
@@
 
+\hypertarget{questionnaire-data}{%
+\subsubsection{Questionnaire Data}\label{questionnaire-data}}
+
+\emph{Describe how we collect questionnaire data (paper or online).
+Add some basic information about the structure of the questionnaire.} Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+
 \hypertarget{eye-tracking-equipment}{%
@@
 
-We used R (Version 4.0.2; R Core Team, 2019) and the R-packages \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), and \emph{papayar} (Muschelli, 2016) for all our analyses.
+We used R (Version 4.0.2; R Core Team, 2019) and the R-packages \emph{\}dplyr} {[}@\}R-dplyr{]}, \emph{forcats} (Version 0.5.0; Wickham, 2020a), \emph{ggplot2} (Version 3.3.2; Wickham, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{papayar} (Muschelli, 2016), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.0.5; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.1.2; Wickham, 2020b), and \emph{tidyverse} (Version 1.3.0; Wickham et al., 2019) for all our analyses.
 
@@
 \section{Results}\label{results}}
+
+\hypertarget{questionnaire-data-1}{%
+\subsubsection{Questionnaire Data}\label{questionnaire-data-1}}
+
+\emph{Start entering descriptives and plots here} Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 
@@
 
+\leavevmode\hypertarget{ref-R-purrr}{}%
+Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
 \leavevmode\hypertarget{ref-jarodzka2010eyes}{}%
@@
 
+\leavevmode\hypertarget{ref-R-tibble}{}%
+Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+
 \leavevmode\hypertarget{ref-pouta2020student}{}%
@@
 
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\hypertarget{ref-R-stringr}{}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\hypertarget{ref-R-forcats}{}%
+Wickham, H. (2020a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\hypertarget{ref-R-tidyr}{}%
+Wickham, H. (2020b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., \ldots{} Yutani, H.
+(2019).
+Welcome to the tidyverse.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+\url{https://doi.org/10.21105/joss.01686}
+
+\leavevmode\hypertarget{ref-R-readr}{}%
+Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+
 \leavevmode\hypertarget{ref-wolff2017see}{}%

### 2021-01-22 paper_1/paper_1.Rmd
minor things

@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_pdf # hier kann man auch word irgendwie machen
 ---
@@
 
-```{r demographicspilot1table,,echo=FALSE}
+```{r demographicspilot1table,echo=FALSE}
 
@@
             "male" = sum(gender),
-            "mean age" = round(mean(age), 2),
+            "M age" = round(mean(age), 2),
             "min age" = min(age),
@@
   demo.quest.table,
-  caption = "Demographic Information",
+  caption = "Demographic Information and Teaching Experience",
   # note = "Write Note here", 

### 2021-01-22 paper_1/paper_1_supplement.Rmd
paper supplement

--- 2021-01-22 paper_1/paper_1.Rmd
@@
 
-Hey Mandy, hier wollte ich dir mal zeigen wie man Bilder in papaja einbindet. Viel Spass damit. Ein Beispiel für Tabellen und Graphen machen wir auch zeitnah.
-
-(ref:thisisdialectical-caption) Illustration of comic material that made the second author of this paper chuckle a bit. For advice on how to insert images, please see the code chunk.
-
-```{r dialectical, fig.cap = "(ref:thisisdialectical-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/thisisdialectical.png", dpi = 108)
-
-# # How to insert images in papaja
-# - pictures must be png
-# - I created a pictures folder in the main folder, just dumb pictures there
-# - you just need to hand the name and path of the picture to the knitr::: function (see above)
-# - the dpi argument is for adjusting the size on the page in pixels
-
-# in order to write the caption, you have to use the line just above the code chunk (ref:YOURTEXT-caption) and then just write behing it
-# the code chunk then opens and after "r" it needs to provide a name for the code chunk, must be unique in the document
-# the fig.cap = then calls the text from the line just above
-# fig.align allows to position the pic on page, center ist probablby best
-# echo = false ensures that the code chunk does not occur in the pdf
-# Now, go and try putting your own images in the paper 
-#
-# TIP = check line 46 in this manuscript. THis section ets global properties for how graphs are put in the paper. 
-#         if floatsintext      : yes  --> pics, graphs, tables will be put where the code chunk is
-#         if floatsintext      : no   --> pics, graphs, tables will be put at the end as is required by some journals
-# TIP: check the folder "papaja_example&tutorial" that I put in this folder for paper1
-# Tip: make a bookmark of this and skim through it: http://frederikaust.com/papaja_man/
-
-```
-
 ## Research questions
@@
 # prepare data (selected from questionnaire data)
-quest.raw.data<-read.table("./data/short_questionnaire_data_2101211.txt",sep="\t", header=T)
+quest.raw.data<-read.table("./data/short_questionnaire_data_2101211.txt", dec=",", sep="\t", header=T)
 
@@
   summarise(N=n(),
-            "male" = sum(gender),
-            "mean age" = round(mean(age), 2),
-            "min age" = min(age),
-            "max age" = max(age),
-            "sd age" = round(sd(age), 2),
-            # "experience" = round(mean(experience), 2) # in order for this to work experience must be turned into integer via as.integer, maybe replace , with .
+            "Male" = sum(gender),
+            "M age" = round(mean(age), 2),
+            "Min age" = min(age),
+            "Max age" = max(age),
+            "SD age" = round(sd(age), 2),
+            "M exp." = round(mean(experience), 2),
+            "Min exp." = min(experience),
+            "Max exp." = max(experience),
+            "SD exp." = round(sd(experience), 2),
            )
@@
   demo.quest.table,
-  caption = "Demographic Information",
+  caption = "Demographic Informationand and Teaching Experience",
   # note = "Write Note here", 
@@
 
-## Procedure
+## Data collection
+
+(ref:data_collection-caption) Illustration of comic material that made the second author of this paper chuckle a bit. For advice on how to insert images, please see the code chunk.
+
+```{r data collection, fig.cap = "(ref:data_collection-caption)", fig.align = "center", echo = FALSE}
+
+knitr::include_graphics("./pictures/data_collection.png", dpi = 108)
+
+# # How to insert images in papaja
+# - pictures must be png
+# - I created a pictures folder in the main folder, just dumb pictures there
+# - you just need to hand the name and path of the picture to the knitr::: function (see above)
+# - the dpi argument is for adjusting the size on the page in pixels
+
+# in order to write the caption, you have to use the line just above the code chunk (ref:YOURTEXT-caption) and then just write behing it
+# the code chunk then opens and after "r" it needs to provide a name for the code chunk, must be unique in the document
+# the fig.cap = then calls the text from the line just above
+# fig.align allows to position the pic on page, center ist probablby best
+# echo = false ensures that the code chunk does not occur in the pdf
+# Now, go and try putting your own images in the paper 
+#
+# TIP = check line 46 in this manuscript. THis section ets global properties for how graphs are put in the paper. 
+#         if floatsintext      : yes  --> pics, graphs, tables will be put where the code chunk is
+#         if floatsintext      : no   --> pics, graphs, tables will be put at the end as is required by some journals
+# TIP: check the folder "papaja_example&tutorial" that I put in this folder for paper1
+# Tip: make a bookmark of this and skim through it: http://frederikaust.com/papaja_man/
+
+```
 
@@
 ### Questionnaire Data
-*Describe how we collect questionnaire data (paper or online).
-Add some basic information about the structure of the questionnaire.* Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+*Describe how we collect questionnaire data (paper or online). Add some basic information about the structure of the questionnaire.*
+
+The questionnaire contains the following scales:
+
+(1) classroom management
+(2) positive climate and motivation
+(3) clarity and structuredness
+(4) activation and support
+(5) presence: posture and gaze
+(6) presence: voice
+(7) presence: verbal and non-verbal intervention
+(8) turn taking
+(9) natural behaviour
+
+The table below provides an overview over the mean, min, max and standard deviation of all scales.
+
+```{r table all sclaes, echo=FALSE}
+
+# prepare data (selected from questionnaire data)
+quest.raw.data<-read.table("./data/short_questionnaire_data_2101211.txt", dec=",", sep="\t", header=T)
+
+# knock out NAs
+quest.raw.data <- quest.raw.data  %>% filter(
+  personID != "NA")
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# create a basic table (tibble) using tidyverse functions 
+scale.quest.table <- quest.raw.data %>% # select data
+  group_by(group, scale) %>%
+  summarise("M scale" = round(mean(value), 2),
+            "min scale" = min(value),
+            "max sclae" = max(value),
+            "SD scale" = round(sd(value), 2),
+            )
+
+# format and insert table in manuscript
+apa_table(
+  scale.quest.table,
+  caption = "Mean values of all scales",
+  # note = "Write Note here", 
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  )
+
+```
 

### 2021-01-22 paper_1/paper_1_supplement.tex
paper supplement

--- 2021-01-22 paper_1/paper_1.tex
@@
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
+\usepackage{amsmath}
 \usepackage{ifxetex,ifluatex}
@@
   \usepackage{textcomp} % provide euro and other symbols
+  \usepackage{amssymb}
 \else % if luatex or xetex
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{graphicx,grffile}
+\usepackage{graphicx}
 \makeatletter
@@
 \fi
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 This ability is called professional vision and is a key component of teacher expertise and successful teaching (Barth, 2017).
-Eye tracking technology has become a reliable means to study teachers' visual focus of attention (Bogert, 2016; Pouta, Lehtinen, \& Palonen, 2020; Wolff et al., 2017)
+Eye tracking technology has become a reliable means to study teachers' visual focus of attention (Bogert, 2016; Pouta, Lehtinen, \& Palonen, 2020; Wolff, Jarodzka, \& Boshuizen, 2017)
 
-Educational research has repeatedly shown that there are differences between experienced and novice teachers in terms of perception and behavioral competencies (Barth, 2017; Bogert, 2016; Wolff et al., 2017).
+Educational research has repeatedly shown that there are differences between experienced and novice teachers in terms of perception and behavioral competencies (Barth, 2017; Bogert, 2016; Wolff, Jarodzka, \& Boshuizen, 2017).
 For example, experts direct their attention more often and more evenly to all students, whereas novices only direct their attention to some students.
@@
 Furthermore, in contrast to novices, experts are able to focus their attention on the entire class and guide the class while giving feedback to individual students and answering questions (Cortina, Miller, McKenzie, \& Epstein, 2015).
-
-Hey Mandy, hier wollte ich dir mal zeigen wie man Bilder in papaja einbindet. Viel Spass damit. Ein Beispiel für Tabellen und Graphen machen wir auch zeitnah.
-
-\begin{figure}
-
-{\centering \includegraphics{./pictures/thisisdialectical}
-
-}
-
-\caption{Illustration of comic material that made the second author of this paper chuckle a bit. For advice on how to insert images, please see the code chunk.}\label{fig:dialectical}
-\end{figure}
 
@@
 
-\caption{\label{tab:demographicspilot1table,}Demographic Information}
+\caption{\label{tab:demographicspilot1table,}Demographic Informationand and Teaching Experience}
 
@@
 
-\begin{tabular}{lllllll}
+\begin{tabular}{lllllllllll}
 \toprule
-group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{male} & \multicolumn{1}{c}{mean age} & \multicolumn{1}{c}{min age} & \multicolumn{1}{c}{max age} & \multicolumn{1}{c}{sd age}\\
+group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{M age} & \multicolumn{1}{c}{Min age} & \multicolumn{1}{c}{Max age} & \multicolumn{1}{c}{SD age} & \multicolumn{1}{c}{M exp.} & \multicolumn{1}{c}{Min exp.} & \multicolumn{1}{c}{Max exp.} & \multicolumn{1}{c}{SD exp.}\\
 \midrule
-expert & 2 & 1 & 47.50 & 44 & 51 & 4.95\\
-novice & 6 & 2 & 25.67 & 20 & 33 & 4.89\\
+expert & 2 & 1 & 47.50 & 44 & 51 & 4.95 & 20.00 & 15.00 & 25.00 & 7.07\\
+novice & 6 & 2 & 25.67 & 20 & 33 & 4.89 & 0.68 & 0.00 & 1.50 & 0.68\\
 \bottomrule
@@
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+\hypertarget{data-collection}{%
+\subsection{Data collection}\label{data-collection}}
+
+(ref:data\_collection-caption) Illustration of comic material that made the second author of this paper chuckle a bit. For advice on how to insert images, please see the code chunk.
+
+\textbackslash begin\{figure\}
+
+\{\centering \includegraphics{./pictures/data_collection}
+
+\}
+
+\textbackslash caption\{(ref:data\_collection-caption)\}(\#fig:data collection)
+\textbackslash end\{figure\}
 
@@
 
-The lesson disturbances were displayed as instructions during the lesson for all \enquote{students} but not the teacher.
+The lesson disturbances were displayed as instructions during the lesson for all ``students'' but not the teacher.
 In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase.
@@
 
-\emph{Describe how we collect questionnaire data (paper or online).
-Add some basic information about the structure of the questionnaire.} Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+\emph{Describe how we collect questionnaire data (paper or online). Add some basic information about the structure of the questionnaire.}
+
+The questionnaire contains the following scales:
+
+\begin{enumerate}
+\def\labelenumi{(\arabic{enumi})}
+\tightlist
+\item
+  classroom management
+\item
+  positive climate and motivation
+\item
+  clarity and structuredness
+\item
+  activation and support
+\item
+  presence: posture and gaze
+\item
+  presence: voice
+\item
+  presence: verbal and non-verbal intervention
+\item
+  turn taking
+\item
+  natural behaviour
+\end{enumerate}
+
+The table below provides an overview over the mean, min, max and standard deviation of all scales.
+
+\begin{verbatim}
+## Warning: Problem with `mutate()` input `value`.
+## i NAs durch Umwandlung erzeugt
+## i Input `value` is `as.numeric(as.character(factor(value)))`.
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in mask$eval_all_mutate(dots[[i]]): NAs durch Umwandlung erzeugt
+\end{verbatim}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:table all sclaes}Mean values of all scales}
+
+\small{
+
+\begin{tabular}{llllll}
+\toprule
+group & \multicolumn{1}{c}{scale} & \multicolumn{1}{c}{M scale} & \multicolumn{1}{c}{min scale} & \multicolumn{1}{c}{max sclae} & \multicolumn{1}{c}{SD scale}\\
+\midrule
+expert & Aktivierung und Förderung & 2.82 & 1.00 & 4.00 & 1.11\\
+expert & Klarheit und Strukturiertheit & 3.46 & 1.00 & 4.00 & 0.89\\
+expert & Klassenmanagement & 3.36 & 1.00 & 4.00 & 0.80\\
+expert & Lernförderliches Klima und Motivierung & 3.60 & 2.00 & 4.00 & 0.62\\
+expert & Manipulationsitem & 3.55 & 2.00 & 4.00 & 0.69\\
+expert & Manipulationsitem & 3.60 & 3.00 & 4.00 & 0.52\\
+expert & Präsenz/Haltung\_Blick & 3.29 & 1.00 & 4.00 & 0.92\\
+expert & Präsenz/Stimme & 2.70 & 1.00 & 4.00 & 1.16\\
+expert & Präsenz/Stimme\ \ & 3.57 & 2.00 & 4.00 & 0.63\\
+expert & Präsenz/verbale\_nonberbale Intervention & 3.07 & 2.00 & 4.00 & 0.78\\
+expert & Redeanteil & 74.20 & 60.00 & 95.00 & 10.53\\
+novice & Aktivierung und Förderung & NA & NA & NA & NA\\
+novice & Klarheit und Strukturiertheit & 3.21 & 1.00 & 4.00 & 0.87\\
+novice & Klassenmanagement & 2.85 & 0.00 & 4.00 & 0.91\\
+novice & Lernförderliches Klima und Motivierung & 3.11 & 0.00 & 4.00 & 0.90\\
+novice & Manipulationsitem & 2.90 & 2.00 & 4.00 & 0.45\\
+novice & Manipulationsitem & 3.20 & 2.00 & 4.00 & 0.75\\
+novice & Nachdenkzeit & NA & NA & NA & NA\\
+novice & Präsenz/Haltung\_Blick & 2.95 & 0.00 & 4.00 & 0.95\\
+novice & Präsenz/Stimme & 3.19 & 0.00 & 4.00 & 1.04\\
+novice & Präsenz/Stimme\ \ & 3.07 & 2.00 & 4.00 & 0.69\\
+novice & Präsenz/verbale\_nonberbale Intervention & 2.95 & 1.00 & 4.00 & 0.91\\
+novice & Redeanteil & 76.93 & 50.00 & 95.00 & 12.97\\
+novice & Störung & NA & NA & NA & NA\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 
@@
 
-We used R (Version 4.0.2; R Core Team, 2019) and the R-packages \emph{\}dplyr} {[}@\}R-dplyr{]}, \emph{forcats} (Version 0.5.0; Wickham, 2020a), \emph{ggplot2} (Version 3.3.2; Wickham, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{papayar} (Muschelli, 2016), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.0.5; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.1.2; Wickham, 2020b), and \emph{tidyverse} (Version 1.3.0; Wickham et al., 2019) for all our analyses.
+We used R {[}Version 4.0.3; R Core Team (2019){]} and the R-packages \emph{\}dplyr} {[}@\}R-dplyr{]}, \emph{forcats} {[}Version 0.5.0; Wickham (2020a){]}, \emph{ggplot2} {[}Version 3.3.2; Wickham (2016){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{papayar} (Muschelli, 2016), \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham, Hester, and Francois (2018){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.0.4; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.2; Wickham (2020b){]}, and \emph{tidyverse} {[}Version 1.3.0; Wickham et al.
+(2019){]} for all our analyses.
 
@@
 \hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
 \leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
 
@@
 (2015).
-Where low and high inference data converge: Validation of class assessment of mathematics instruction using mobile eye tracking with expert and novice teachers.
+Where low and high inference data converge: Validation of CLASS assessment of mathematics instruction using mobile eye tracking with expert and novice teachers.
 \emph{International Journal of Science and Mathematics Education}, \emph{13}(2), 389--403.
@@
 \leavevmode\hypertarget{ref-messner2000berufliche}{}%
-Messner, H., \& Reusser, K. (2000). Die berufliche entwicklung von lehrpersonen als lebenslanger prozess. \emph{Beiträge Zur Lehrerinnen-Und Lehrerbildung}, \emph{18}(2), 157--171.
+Messner, H., \& Reusser, K. (2000). Die berufliche entwicklung von lehrpersonen als lebenslanger prozess. \emph{Beitr{ä}ge Zur Lehrerinnen-Und Lehrerbildung}, \emph{18}(2), 157--171.
 
 \leavevmode\hypertarget{ref-R-papayar}{}%
-Muschelli, J. (2016). \emph{Papayar: View medical research images using the papaya javascript library}. Retrieved from \url{https://CRAN.R-project.org/package=papayar}
+Muschelli, J. (2016). \emph{Papayar: View medical research images using the papaya JavaScript library}. Retrieved from \url{https://CRAN.R-project.org/package=papayar}
 
@@
 An eye-tracking study about attention processes in different teaching situations.
-\emph{Zeitschrift Für Erziehungswissenschaft}, \emph{20}(1), 75--92.
+\emph{Zeitschrift f{ü}r Erziehungswissenschaft}, \emph{20}(1), 75--92.
 
 \leavevmode\hypertarget{ref-R-ggplot2}{}%
-Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
 
@@
 (2019).
-Welcome to the tidyverse.
+Welcome to the {tidyverse}.
 \emph{Journal of Open Source Software}, \emph{4}(43), 1686.
@@
 
+\end{CSLReferences}
+
 \endgroup

### 2021-01-22 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
paper supplement

@@
 # file should be in a subfolder named "data" for the script to select it
-raw.data<-read.table("./data/short_questionnaire_data_2101211.txt",sep="\t", header=T)
+# import: never forget to insert "dec="," for replacing values with "," by "."
+raw.data<-read.table("./data/short_questionnaire_data_2101211.txt", dec=",", sep="\t", header=T)
 
@@
 
-# demographics, grouped by group (N, gender, meanage, max, min age)
+# years of experience
+class(raw.data$experience)
+
+# converting numbers to numeric
+raw.data <- raw.data %>%  mutate(experience = as.numeric(as.character(factor(experience))))
+
+# demographics and years of experience, grouped by group (N, gender, M age, max, min age)
 raw.data %>%
@@
             "male" = sum(gender),
-            "mean age" = round(mean(age), 2),
+            "M age" = round(mean(age), 2),
             "min age" = min(age),
             "max age" = max(age),
-            "experience" = round(mean(experience), 2)
+            "SD age" = round(sd(age), 2),
+            "M experience" = round(mean(experience), 2),
+            "min experience" = min(experience),
+            "max experience" = max(experience),
+            "SD experience" = round(sd(experience), 2),
             ) %>% 
@@
 
-```{r mean classroom management, echo = FALSE}
+```{r table all sclaes, echo=FALSE}
 
-### classroom management
-
-# filter by parameter variable, i.e. create a subset for each session
-km.data <- raw.data %>% filter(scale == "Klassenmanagement")
-
-view (km.data)
+sum(is.na(raw.data$scale == "Aktivierung und Förderung"))
 
 # value sometimes contained text before filtering, we have to convert the numbers to numeric
-km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+raw.data <- raw.data %>%  mutate(value = as.numeric(as.character(factor(value))))
 
-# create  mean, min, max, sd of classroom management
-km.data.plot %>% km.data %>%
-
-          meankm <- mean(km.data$value)
-          minkm <- min(km.data$value)
-          maxkm <- max(km.data$value)
-          sdkm <- sd(km.data$value)
-          Nkm <- km.data %>% summarise(N = n_distinct(personID))
-          mdkm <- median(km.data$value)
+# create a table of all scales 
+raw.data %>% # select data
+  group_by(group, scale) %>%
+  summarise("M scale" = round(mean(value), 2),
+            "min scale" = min(value),
+            "max sclae" = max(value),
+            "SD scale" = round(sd(value), 2),
+            ) %>% 
+  knitr::kable(digits = 2)
 
 ```
-
-### to do
-
-- vergessen: Berufserfahrung bei Demographie mit aufnehmen
-- selbst und fremdeinschätzung durch facet_grid bei plot hinzufügen
 

### 2021-01-25 paper_1/paper_1.Rmd

@@
   personID != "NA")
+
+# converting numbers to numeric
+raw.data <- raw.data %>%  mutate(experience = as.numeric(as.character(factor(experience))))
 
@@
             "max age" = max(age),
-            "sd age" = round(sd(age), 2),
-            # "experience" = round(mean(experience), 2) # in order for this to work experience must be turned into integer via as.integer, maybe replace , with .
-            )
+            "SD age" = round(sd(age), 2),
+            "M experience" = round(mean(experience), 2),
+            "min experience" = min(experience),
+            "max experience" = max(experience),
+            "SD experience" = round(sd(experience), 2),
+            ) %>%
 

### 2021-01-25 paper_1/paper_1.tex

@@
 
-\caption{\label{tab:demographicspilot1table,}Demographic Information}
+\caption{\label{tab:demographicspilot1table}Demographic Information and Teaching Experience}
 
@@
 \toprule
-group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{male} & \multicolumn{1}{c}{mean age} & \multicolumn{1}{c}{min age} & \multicolumn{1}{c}{max age} & \multicolumn{1}{c}{sd age}\\
+group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{male} & \multicolumn{1}{c}{*M* age} & \multicolumn{1}{c}{min age} & \multicolumn{1}{c}{max age} & \multicolumn{1}{c}{sd age}\\
 \midrule

### 2021-01-27 paper_1/paper_1_supplement.Rmd
update manuscript

@@
     email         : "mandy.klatt@uni-leipzig.de"
-  - name          : "Gregor Kachel"
+  - name          : "Dr. Gregor Kachel"
+    affiliation   : "1, 2"
+  - name          : "Dr. Christin Lotz"
+    affiliation   : "1"
+  - name          : "Prof. Dr. Anne Deiglmayr"
     affiliation   : "1"
@@
     institution   : "University of Leipzig"
+  - id            : "2"
+    institution   : "MPI for Evolutionary Anthropology, Leipzig"
 
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
+  The study was carried out with the permission of Ethics Committee of the University of Leipzig.
 
 abstract: |
-  Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+  This document is a supplement to the paper.
 
@@
 
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
 # create a basic table (tibble) using tidyverse functions 
@@
             "max sclae" = max(value),
-            "SD scale" = round(sd(value), 2),
-            )
+            "SD scale" = round(sd(value), 2))
 

### 2021-01-27 paper_1/paper_1_supplement.tex
update manuscript

@@
   pdftitle={Through the eyes of the teacher},
-  pdfauthor={Mandy Klatt1 \& Gregor Kachel1},
+  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
   pdflang={en-EN},
@@
 \title{Through the eyes of the teacher}
-\author{Mandy Klatt\textsuperscript{1} \& Gregor Kachel\textsuperscript{1}}
+\author{Mandy Klatt\textsuperscript{1}, Dr.~Gregor Kachel\textsuperscript{1, 2}, Dr.~Christin Lotz\textsuperscript{1}, \& Prof.~Dr.~Anne Deiglmayr\textsuperscript{1}}
 \date{}
@@
 
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
+The study was carried out with the permission of Ethics Committee of the University of Leipzig.
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Leipzig}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Leipzig\\\textsuperscript{2} MPI for Evolutionary Anthropology, Leipzig}
 
 \abstract{
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+This document is a supplement to the paper.
 }
@@
 \begin{verbatim}
-## Warning: Problem with `mutate()` input `value`.
-## i NAs durch Umwandlung erzeugt
-## i Input `value` is `as.numeric(as.character(factor(value)))`.
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
+
+## Warning in mean.default(value): argument is not numeric or logical: returning NA
 \end{verbatim}
@@
 \begin{verbatim}
-## Warning in mask$eval_all_mutate(dots[[i]]): NAs durch Umwandlung erzeugt
+## Warning in var(if (is.vector(x) || is.factor(x)) x else as.double(x), na.rm =
+## na.rm): NAs durch Umwandlung erzeugt
+
+## Warning in var(if (is.vector(x) || is.factor(x)) x else as.double(x), na.rm =
+## na.rm): NAs durch Umwandlung erzeugt
+
+## Warning in var(if (is.vector(x) || is.factor(x)) x else as.double(x), na.rm =
+## na.rm): NAs durch Umwandlung erzeugt
 \end{verbatim}
@@
 \midrule
-expert & Aktivierung und Förderung & 2.82 & 1.00 & 4.00 & 1.11\\
-expert & Klarheit und Strukturiertheit & 3.46 & 1.00 & 4.00 & 0.89\\
-expert & Klassenmanagement & 3.36 & 1.00 & 4.00 & 0.80\\
-expert & Lernförderliches Klima und Motivierung & 3.60 & 2.00 & 4.00 & 0.62\\
-expert & Manipulationsitem & 3.55 & 2.00 & 4.00 & 0.69\\
-expert & Manipulationsitem & 3.60 & 3.00 & 4.00 & 0.52\\
-expert & Präsenz/Haltung\_Blick & 3.29 & 1.00 & 4.00 & 0.92\\
-expert & Präsenz/Stimme & 2.70 & 1.00 & 4.00 & 1.16\\
-expert & Präsenz/Stimme\ \ & 3.57 & 2.00 & 4.00 & 0.63\\
-expert & Präsenz/verbale\_nonberbale Intervention & 3.07 & 2.00 & 4.00 & 0.78\\
-expert & Redeanteil & 74.20 & 60.00 & 95.00 & 10.53\\
-novice & Aktivierung und Förderung & NA & NA & NA & NA\\
-novice & Klarheit und Strukturiertheit & 3.21 & 1.00 & 4.00 & 0.87\\
-novice & Klassenmanagement & 2.85 & 0.00 & 4.00 & 0.91\\
-novice & Lernförderliches Klima und Motivierung & 3.11 & 0.00 & 4.00 & 0.90\\
-novice & Manipulationsitem & 2.90 & 2.00 & 4.00 & 0.45\\
-novice & Manipulationsitem & 3.20 & 2.00 & 4.00 & 0.75\\
-novice & Nachdenkzeit & NA & NA & NA & NA\\
-novice & Präsenz/Haltung\_Blick & 2.95 & 0.00 & 4.00 & 0.95\\
-novice & Präsenz/Stimme & 3.19 & 0.00 & 4.00 & 1.04\\
-novice & Präsenz/Stimme\ \ & 3.07 & 2.00 & 4.00 & 0.69\\
-novice & Präsenz/verbale\_nonberbale Intervention & 2.95 & 1.00 & 4.00 & 0.91\\
-novice & Redeanteil & 76.93 & 50.00 & 95.00 & 12.97\\
-novice & Störung & NA & NA & NA & NA\\
+expert & Aktivierung und Förderung & NA & 1 & 4 & 1.11\\
+expert & Klarheit und Strukturiertheit & NA & 1 & 4 & 0.89\\
+expert & Klassenmanagement & NA & 1 & 4 & 0.80\\
+expert & Lernförderliches Klima und Motivierung & NA & 2 & 4 & 0.62\\
+expert & Manipulationsitem & NA & 2 & 4 & 0.69\\
+expert & Manipulationsitem & NA & 3 & 4 & 0.52\\
+expert & Präsenz/Haltung\_Blick & NA & 1 & 4 & 0.92\\
+expert & Präsenz/Stimme & NA & 1 & 4 & 1.16\\
+expert & Präsenz/Stimme\ \ & NA & 2 & 4 & 0.63\\
+expert & Präsenz/verbale\_nonberbale Intervention & NA & 2 & 4 & 0.78\\
+expert & Redeanteil & NA & 60 & 95 & 10.53\\
+novice & Aktivierung und Förderung & NA & - & 4 & NA\\
+novice & Klarheit und Strukturiertheit & NA & 1 & 4 & 0.87\\
+novice & Klassenmanagement & NA & 0 & 4 & 0.91\\
+novice & Lernförderliches Klima und Motivierung & NA & 0 & 4 & 0.90\\
+novice & Manipulationsitem & NA & 2 & 4 & 0.45\\
+novice & Manipulationsitem & NA & 2 & 4 & 0.75\\
+novice & Nachdenkzeit & NA & - & 5-10 & NA\\
+novice & Präsenz/Haltung\_Blick & NA & 0 & 4 & 0.95\\
+novice & Präsenz/Stimme & NA & 0 & 4 & 1.04\\
+novice & Präsenz/Stimme\ \ & NA & 2 & 4 & 0.69\\
+novice & Präsenz/verbale\_nonberbale Intervention & NA & 1 & 4 & 0.91\\
+novice & Redeanteil & NA & 50 & 95 & 12.97\\
+novice & Störung & NA & - & Stift auf Papier schreiben & NA\\
 \bottomrule

### 2021-01-27 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
update manuscript

@@
 # import: never forget to insert "dec="," for replacing values with "," by "."
-raw.data<-read.table("./data/short_questionnaire_data_2101211.txt", dec=",", sep="\t", header=T)
+raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)
 
@@
                                                          "pi_direkt",
-                                                         "redeanteil",
                                                          "m_natürlich",
@@
 
-sum(is.na(raw.data$scale == "Aktivierung und Förderung"))
-
 # value sometimes contained text before filtering, we have to convert the numbers to numeric

### 2021-01-28 paper_1/paper_1.Rmd
update manuscript

@@
 # converting numbers to numeric
-raw.data <- raw.data %>%  mutate(experience = as.numeric(as.character(factor(experience))))
+quest.raw.data <- quest.raw.data %>% mutate(experience = as.numeric(as.character(factor(experience))))
 
@@
             "max experience" = max(experience),
-            "SD experience" = round(sd(experience), 2),
-            ) %>%
+            "SD experience" = round(sd(experience), 2))
 

### 2021-01-28 paper_1/paper_1.tex
update manuscript

@@
 
-\begin{tabular}{lllllll}
+\begin{tabular}{lllllllllll}
 \toprule
-group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{male} & \multicolumn{1}{c}{*M* age} & \multicolumn{1}{c}{min age} & \multicolumn{1}{c}{max age} & \multicolumn{1}{c}{sd age}\\
+group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{male} & \multicolumn{1}{c}{M age} & \multicolumn{1}{c}{min age} & \multicolumn{1}{c}{max age} & \multicolumn{1}{c}{SD age} & \multicolumn{1}{c}{M experience} & \multicolumn{1}{c}{min experience} & \multicolumn{1}{c}{max experience} & \multicolumn{1}{c}{SD experience}\\
 \midrule
-expert & 2 & 1 & 47.50 & 44 & 51 & 4.95\\
-novice & 6 & 2 & 25.67 & 20 & 33 & 4.89\\
+expert & 2 & 1 & 47.50 & 44 & 51 & 4.95 & 20.00 & 15.00 & 25.00 & 7.07\\
+novice & 6 & 2 & 25.67 & 20 & 33 & 4.89 & 0.68 & 0.00 & 1.50 & 0.68\\
 \bottomrule

### 2021-01-28 paper_1/paper_1_supplement.Rmd
update manuscript

@@
 floatsintext      : yes
-figurelist        : no
-tablelist         : no
+figsintext        : yes
+figurelist        : yes
+tablelist         : yes
 footnotelist      : no
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : bookdown::word_document2 #papaja::apa6_pdf #
 ---
@@
 
-```{r analysis-preferences}
+```{r analysis-preferences, echo = FALSE}
 # Seed for random number generation
@@
 
-```{r demographicspilot1table,,echo=FALSE}
+```{r demographicspilottable, echo = FALSE}
 
 # prepare data (selected from questionnaire data)
-quest.raw.data<-read.table("./data/short_questionnaire_data_2101211.txt", dec=",", sep="\t", header=T)
+quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)
 
@@
 
-# in order to write the caption, you have to use the line just above the code chunk (ref:YOURTEXT-caption) and then just write behing it
+# in order to write the caption, you have to use the line just above the code chunk (ref:YOURTEXT-caption) and then just write behind it
 # the code chunk then opens and after "r" it needs to provide a name for the code chunk, must be unique in the document
@@
 (7) presence: verbal and non-verbal intervention
-(8) turn taking
-(9) natural behaviour
+(8) natural behaviour
 
@@
 
-```{r table all sclaes, echo=FALSE}
+```{r table all scales, echo = FALSE}
 
 # prepare data (selected from questionnaire data)
-quest.raw.data<-read.table("./data/short_questionnaire_data_2101211.txt", dec=",", sep="\t", header=T)
+quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)
 
@@
   personID != "NA")
+
+# to compare both sessions filter only Identical items
+quest.raw.data <- quest.raw.data  %>% filter(str_detect(shortID, 
+                                                 paste(c("km_mitbekommen",
+                                                         "km_klar",
+                                                         "km_ungestört",
+                                                         "km_aktiv",
+                                                         "lkm_freundlich",
+                                                         "lkm_interesse",
+                                                         "lkm_kritik",
+                                                         "lkm_ausreden",
+                                                         "lkm_überlegen",
+                                                         "lkm_rückmeldungen",
+                                                         "ks_funktion",
+                                                         "ks_verständlich",
+                                                         "ks_sichtbar",
+                                                         "af_beiträge",
+                                                         "af_wechselseitig",
+                                                         "af_nachdenken",
+                                                         "phb_stand",
+                                                         "phb_augen",
+                                                         "phb_blick",
+                                                         "phb_vorsichgeht",
+                                                         "phb_raum",
+                                                         "phb_gestik",
+                                                         "phb_alleangesehen",
+                                                         "ps_deutlich",
+                                                         "ps_klar",
+                                                         "ps_impulse",
+                                                         "pi_nonverbal",
+                                                         "pi_zubewegen",
+                                                         "pi_direkt",
+                                                         "m_natürlich",
+                                                         "m_fiktiv",
+                                                         "m_verhalten"),
+                                                    collapse = '|')))
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
 
@@
             "SD scale" = round(sd(value), 2))
+
+# remove duplicate labels from the table column "group" to create the APA-style omission of categorical variables
+# this is easier than the stub_indent option in apa_table
+scale.quest.table$group[duplicated(scale.quest.table$group)] <- ""
 
@@
 )
+
+```
+
+In addition, we plotted all scales for experts and novices. Graph provides boxplots and individual data for both groups.
+
+```{r boxplot scales, echo = FALSE}
+# prepare data (selected from questionnaire data)
+quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)
+
+# knock out NAs
+quest.raw.data <- quest.raw.data  %>% filter(
+  personID != "NA")
+
+# to compare both sessions filter only Identical items
+quest.raw.data <- quest.raw.data  %>% filter(str_detect(shortID, 
+                                                 paste(c("km_mitbekommen",
+                                                         "km_klar",
+                                                         "km_ungestört",
+                                                         "km_aktiv",
+                                                         "lkm_freundlich",
+                                                         "lkm_interesse",
+                                                         "lkm_kritik",
+                                                         "lkm_ausreden",
+                                                         "lkm_überlegen",
+                                                         "lkm_rückmeldungen",
+                                                         "ks_funktion",
+                                                         "ks_verständlich",
+                                                         "ks_sichtbar",
+                                                         "af_beiträge",
+                                                         "af_wechselseitig",
+                                                         "af_nachdenken",
+                                                         "phb_stand",
+                                                         "phb_augen",
+                                                         "phb_blick",
+                                                         "phb_vorsichgeht",
+                                                         "phb_raum",
+                                                         "phb_gestik",
+                                                         "phb_alleangesehen",
+                                                         "ps_deutlich",
+                                                         "ps_klar",
+                                                         "ps_impulse",
+                                                         "pi_nonverbal",
+                                                         "pi_zubewegen",
+                                                         "pi_direkt",
+                                                         "m_natürlich",
+                                                         "m_fiktiv",
+                                                         "m_verhalten"),
+                                                    collapse = '|')))
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
+
+quest.plot <- quest.raw.data %>%
+  ggplot( aes(x=scale, y=value, fill=scale)) +
+    geom_boxplot() +
+    scale_x_discrete(guide = guide_axis(angle = 70)) +
+    geom_jitter(color="black", size=0.4, alpha=0.9) +
+    theme_light() +
+    theme(
+      legend.position="none",
+      plot.title = element_text(size=11)
+    ) +
+    facet_grid(~group)+
+    ggtitle("Boxplot with individual points for all scales") +
+    xlab("")
+# quest.plot
+
+```
+
+(ref:boxplot_all_scales-caption) Boxplot with individual points for all scales
+
+```{r boxplot_all_scales, fig.cap = "(ref:boxplot_all_scales-caption)", fig.align = "center", echo = FALSE}
+
+knitr::include_graphics("./pictures/boxplot_all_scales.png", dpi = 108)
+
+```
+
+In addition, we evaluated the duration of the speaking time during the lesson in the questionnaire by external and self-assessment.
+The following graph shows the duration of speaking time for experts and novices.
+
+```{r duration speaking time, echo = FALSE}
+# prepare data (selected from questionnaire data)
+quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)
+
+# knock out NAs
+quest.raw.data <- quest.raw.data  %>% filter(
+  personID != "NA")
+
+# to compare both sessions filter only Identical items
+quest.raw.data <- quest.raw.data  %>% filter(str_detect(scale, 
+                                                 paste(c("Duration of speaking time"),
+                                                    collapse = '|')))
+view(quest.raw.data)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
+
+speaking.plot <- quest.raw.data %>%
+  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
+    geom_boxplot() +
+    geom_jitter(color="black", size=0.4, alpha=0.9) +
+    theme_light() +
+    theme(
+      legend.position="none",
+      plot.title = element_text(size=11)) +
+    facet_grid(group~perspective) +
+    ggtitle("Boxplot with individual points for Duration of speaking time") +
+    xlab("")
+speaking.plot
 

### 2021-01-28 paper_1/paper_1_supplement.tex
update manuscript

@@
 \usepackage{csquotes}
+\usepackage[titles]{tocloft}
+\cftpagenumbersoff{figure}
+\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
+\renewcommand{\cftfigaftersnum}{.\space}
+\setlength{\cftfigindent}{0pt}
+\setlength{\cftafterloftitleskip}{0pt}
+\settowidth{\cftfignumwidth}{Figure 10.\qquad}
+\cftpagenumbersoff{table}
+\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
+\renewcommand{\cfttabaftersnum}{.\space}
+\setlength{\cfttabindent}{0pt}
+\setlength{\cftafterloftitleskip}{0pt}
+\settowidth{\cfttabnumwidth}{Table 10.\qquad}
 \ifxetex
@@
 
-\caption{\label{tab:demographicspilot1table,}Demographic Informationand and Teaching Experience}
+\caption{\label{tab:demographicspilottable}Demographic Informationand and Teaching Experience}
 
@@
 \item
-  turn taking
-\item
   natural behaviour
@@
 The table below provides an overview over the mean, min, max and standard deviation of all scales.
-
-\begin{verbatim}
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-
-## Warning in mean.default(value): argument is not numeric or logical: returning NA
-\end{verbatim}
-
-\begin{verbatim}
-## Warning in var(if (is.vector(x) || is.factor(x)) x else as.double(x), na.rm =
-## na.rm): NAs durch Umwandlung erzeugt
-
-## Warning in var(if (is.vector(x) || is.factor(x)) x else as.double(x), na.rm =
-## na.rm): NAs durch Umwandlung erzeugt
-
-## Warning in var(if (is.vector(x) || is.factor(x)) x else as.double(x), na.rm =
-## na.rm): NAs durch Umwandlung erzeugt
-\end{verbatim}
 
@@
 
-\caption{\label{tab:table all sclaes}Mean values of all scales}
+\caption{\label{tab:table all scales}Mean values of all scales}
 
@@
 \midrule
-expert & Aktivierung und Förderung & NA & 1 & 4 & 1.11\\
-expert & Klarheit und Strukturiertheit & NA & 1 & 4 & 0.89\\
-expert & Klassenmanagement & NA & 1 & 4 & 0.80\\
-expert & Lernförderliches Klima und Motivierung & NA & 2 & 4 & 0.62\\
-expert & Manipulationsitem & NA & 2 & 4 & 0.69\\
-expert & Manipulationsitem & NA & 3 & 4 & 0.52\\
-expert & Präsenz/Haltung\_Blick & NA & 1 & 4 & 0.92\\
-expert & Präsenz/Stimme & NA & 1 & 4 & 1.16\\
-expert & Präsenz/Stimme\ \ & NA & 2 & 4 & 0.63\\
-expert & Präsenz/verbale\_nonberbale Intervention & NA & 2 & 4 & 0.78\\
-expert & Redeanteil & NA & 60 & 95 & 10.53\\
-novice & Aktivierung und Förderung & NA & - & 4 & NA\\
-novice & Klarheit und Strukturiertheit & NA & 1 & 4 & 0.87\\
-novice & Klassenmanagement & NA & 0 & 4 & 0.91\\
-novice & Lernförderliches Klima und Motivierung & NA & 0 & 4 & 0.90\\
-novice & Manipulationsitem & NA & 2 & 4 & 0.45\\
-novice & Manipulationsitem & NA & 2 & 4 & 0.75\\
-novice & Nachdenkzeit & NA & - & 5-10 & NA\\
-novice & Präsenz/Haltung\_Blick & NA & 0 & 4 & 0.95\\
-novice & Präsenz/Stimme & NA & 0 & 4 & 1.04\\
-novice & Präsenz/Stimme\ \ & NA & 2 & 4 & 0.69\\
-novice & Präsenz/verbale\_nonberbale Intervention & NA & 1 & 4 & 0.91\\
-novice & Redeanteil & NA & 50 & 95 & 12.97\\
-novice & Störung & NA & - & Stift auf Papier schreiben & NA\\
+expert & Activation and support & 3.33 & 2.00 & 4.00 & 0.80\\
+ & Clarity and structuredness & 3.70 & 1.00 & 4.00 & 0.73\\
+ & Classroom management & 3.23 & 1.00 & 4.00 & 0.90\\
+ & Natural behaviour & 3.57 & 2.00 & 4.00 & 0.63\\
+ & Positive climate and motivation & 3.60 & 2.00 & 4.00 & 0.62\\
+ & Presence: posture/gaze & 3.29 & 1.00 & 4.00 & 0.92\\
+ & Presence: verbal and non-verbal intervention & 3.07 & 2.00 & 4.00 & 0.78\\
+ & Presence: voice & 3.57 & 2.00 & 4.00 & 0.63\\
+novice & Activation and support & 2.23 & 0.00 & 4.00 & 1.39\\
+ & Clarity and structuredness & 3.35 & 1.00 & 4.00 & 0.76\\
+ & Classroom management & 2.82 & 1.00 & 4.00 & 0.90\\
+ & Natural behaviour & 3.13 & 2.00 & 4.00 & 0.71\\
+ & Positive climate and motivation & 3.11 & 0.00 & 4.00 & 0.90\\
+ & Presence: posture/gaze & 2.95 & 0.00 & 4.00 & 0.95\\
+ & Presence: verbal and non-verbal intervention & 2.88 & 1.00 & 4.00 & 0.97\\
+ & Presence: voice & 3.30 & 2.00 & 4.00 & 0.74\\
 \bottomrule
@@
 
+\clearpage
+\renewcommand{\listfigurename}{Figure captions}
+
+\clearpage
+\renewcommand{\listtablename}{Table captions}
+
 \end{document}

### 2021-01-28 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
update manuscript

@@
 # filter by parameter variable, i.e. create a subset for presence: posture and gaze
-phb.data <- raw.data %>% filter(scale == "Präsenz/Haltung_Blick")
+phb.data <- raw.data %>% filter(scale == "Presence: posture/gaze")
 
@@
 
-names(phb.plot.sd)
-
 # and here comes the long plot
@@
 # create a table of all scales 
-raw.data %>% # select data
+table.scales <- raw.data %>% # select data
   group_by(group, scale) %>%

### 2021-01-29 paper_1/paper_1_supplement.Rmd
update manuscript -> plots

@@
 figsintext        : yes
-figurelist        : yes
-tablelist         : yes
+figurelist        : no
+tablelist         : no
 footnotelist      : no
@@
 classoption       : "man"
-output            : bookdown::word_document2 #papaja::apa6_pdf #
+output            : papaja::apa6_pdf
 ---
@@
 
-The first study is a laboratory study that uses a quasi-experimental cross-sectional study design to investigate whether the experience of teachers has an influence on the perception of and response to disruptions.
-The disturbances are experimentally varied using a previously written script.
-Thus, the aim is to find out whether differences in the allocation of attention between expertise groups can be detected in this controlled context.
+The aim of the pilot study was to investigate whether there are differences in how expert and novice teachers manage scripted classroom disruptions.
+The disruptions were experimentally varied using a previously written script.
+Thus, our aim was to find out whether differences in the allocation of attention between expertise groups can be detected in this controlled context.
 
-In order to answer this question, the hypothesis was formulated that teachers with more professional experience not only notice more disturbances but also notice them faster.
+In order to answer this question, the hypothesis was formulated that teachers with more professional experience not only notice more disruptions but also notice them faster.
 In the hypothesis, therefore, it is necessary to check what has already been shown in the research literature: In complex teaching situations, experts have a more structured and elaborate professional knowledge than novices in order to perceive and interpret relevant events and to act appropriately [@berliner2001learning; @lachner2016makes].
@@
 For the sample recruitment of the subjects (N = 48, experts n = 24, novices n = 24), schools in the city of Leipzig in Saxony were contacted.
-The institutions as well as the subjects were informed in detail about the aim and intention of the dissertation project in advance.
+The institutions as well as the subjects were informed in detail about the aim and intention of the study in advance.
 Participation in the study was voluntary and only took place after written consent has been given.
@@
 
-(ref:data_collection-caption) Illustration of comic material that made the second author of this paper chuckle a bit. For advice on how to insert images, please see the code chunk.
+(ref:data_collection-caption) Example for the set up during a mini-lesson
 
@@
 
-For this study, lesson units of n = 24 experts and n = 24 novices were recorded by the mobile laboratory of the Department of Empirical School and Classroom Research at the University of Leipzig.
-The two extreme groups were each divided into groups of four, with one group being invited on each of six different dates.
-All participants were asked to hold a 15-minute lesson.
-The duration of each appointment was approximately 2h30min: per extreme group 4 x 15min briefing, 15min lesson units, 10min technical preparation and follow-up and 5min buffer/break.
+For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig.
+The subjects were divided into groups of four, so the study was conducted on two different sessions.
+All participants were asked to hold a 10-minute lesson.
+The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering the questionnaire.
 
 One person from the group of 4 acted as a teacher, the other three subjects acted as the class.
-The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disturbances in the classroom (e.g.
+The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disruptions in the classroom (e.g.
 putting their heads on the table, chatting, looking at their mobile phones, etc.).
 
-The lesson disturbances were displayed as instructions during the lesson for all "students" but not the teacher.
+The lesson disruptions were displayed as instructions during the lesson for all "students" but not the teacher.
 In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase.
@@
 By using mobile eye-trackers, the gaze and behavior of the experts and novices was recorded during the lesson.
-In addition, what the participating teachers said was recorded with a portable microphone.
-Other sounds and voices were recorded with an audio recorder installed in the middle of the laboratory.
+In addition, the speech and sounds and voices were recorded with an audio recorder installed in the middle of the Lab.
 Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles.
 One camera was installed to film the class from the side.
-Two more cameras were installed on the blackboard and at the end of the laboratory to film the teacher and class from the front and back.
-In addition, it the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.
+Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back.
+Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.
 
@@
 
-The questionnaire contains the following scales:
+The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes. 
+The scales on the quality of teaching are a validated questionnaire (@helmke2014unterrichtsdiagnostik).
+Whereas the scales on the teacher's presence behaviour were derived from the research literature (@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen) and were used in the pilot for the first time.
 
-(1) classroom management
-(2) positive climate and motivation
-(3) clarity and structuredness
-(4) activation and support
-(5) presence: posture and gaze
-(6) presence: voice
-(7) presence: verbal and non-verbal intervention
-(8) natural behaviour
+The following scales were assessed:
+
+(1) Classroom management
+(2) Positive climate and motivation
+(3) Clarity and structuredness
+(4) Activation and support
+(5) Presence: posture and gaze
+(6) Presence: voice
+(7) Presence: verbal and non-verbal intervention
+(8) Natural behaviour
 
@@
 
-In addition, we plotted all scales for experts and novices. Graph provides boxplots and individual data for both groups.
+The individual items of a scale were further represented in graphs.
 
-```{r boxplot scales, echo = FALSE}
-# prepare data (selected from questionnaire data)
-quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)
+(1) Classroom management
+```{r classroom management line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
 
-# knock out NAs
-quest.raw.data <- quest.raw.data  %>% filter(
-  personID != "NA")
+### classroom management
 
-# to compare both sessions filter only Identical items
-quest.raw.data <- quest.raw.data  %>% filter(str_detect(shortID, 
-                                                 paste(c("km_mitbekommen",
-                                                         "km_klar",
-                                                         "km_ungestört",
-                                                         "km_aktiv",
-                                                         "lkm_freundlich",
-                                                         "lkm_interesse",
-                                                         "lkm_kritik",
-                                                         "lkm_ausreden",
-                                                         "lkm_überlegen",
-                                                         "lkm_rückmeldungen",
-                                                         "ks_funktion",
-                                                         "ks_verständlich",
-                                                         "ks_sichtbar",
-                                                         "af_beiträge",
-                                                         "af_wechselseitig",
-                                                         "af_nachdenken",
-                                                         "phb_stand",
-                                                         "phb_augen",
-                                                         "phb_blick",
-                                                         "phb_vorsichgeht",
-                                                         "phb_raum",
-                                                         "phb_gestik",
-                                                         "phb_alleangesehen",
-                                                         "ps_deutlich",
-                                                         "ps_klar",
-                                                         "ps_impulse",
-                                                         "pi_nonverbal",
-                                                         "pi_zubewegen",
-                                                         "pi_direkt",
-                                                         "m_natürlich",
-                                                         "m_fiktiv",
-                                                         "m_verhalten"),
-                                                    collapse = '|')))
+# filter by parameter variable, i.e. create a subset for classroom management
+cm.data <- quest.raw.data %>% filter(scale == "Classroom management")
 
 # value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
+cm.data <- cm.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# to create error bars, we need to summarize the data in a separate data frame
+cm.plot.sd <- cm.data %>%
+  group_by(group, item.wordings, .drop=TRUE) %>%
+  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# long plot
+cm.plot<-ggplot(data = cm.plot.sd,
+                  aes(x = item.wordings, y = mean,
+                      group = group, colour = group)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  facet_grid(~perspective)+
+  labs(data = cm.data, y = "value", x = NULL,
+       title="Classroom management" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5),
+        axis.text.y = element_text(size = 6))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+cm.plot
+
+```
+
+(2) Positive climate and motivation
+```{r Positive climate and motivation line plots,  fig.width=6, fig.height = 7, message = FALSE, warning = FALSE , echo=FALSE}
+
+### Positive climate and motivation
+
+# filter by parameter variable, i.e. create a subset for Positive climate and motivation
+pcm.data <- quest.raw.data %>% filter(scale == "Positive climate and motivation")
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+pcm.data <- pcm.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# to create error bars, we need to summarize the data in a separate data frame
+pcm.plot.sd <- pcm.data %>%
+  group_by(group, item.wordings, .drop=TRUE) %>%
+  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# long plot
+pcm.plot<-ggplot(data = pcm.plot.sd,
+                  aes(x = item.wordings, y = mean,
+                      group = group, colour = group)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  facet_grid(~perspective)+
+  labs(data = pcm.data, y = "value", x = NULL,
+       title="Positive climate and motivation" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5),
+        axis.text.y = element_text(size = 5))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+pcm.plot
+
+```
+
+(3) Clarity and structuredness
+```{r Clarity and structuredness line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+
+### Clarity and structuredness
+
+# filter by parameter variable, i.e. create a subset for Clarity and structuredness
+cs.data <- quest.raw.data %>% filter(scale == "Clarity and structuredness")
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+cs.data <- cs.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# to create error bars, we need to summarize the data in a separate data frame
+cs.plot.sd <- cs.data %>%
+  group_by(group, item.wordings, .drop=TRUE) %>%
+  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# long plot
+cs.plot<-ggplot(data = cs.plot.sd,
+                  aes(x = item.wordings, y = mean,
+                      group = group, colour = group)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  facet_grid(~perspective)+
+  labs(data = cs.data, y = "value", x = NULL,
+       title="Clarity and structuredness" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5),
+        axis.text.y = element_text(size = 6))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+cs.plot
+
+```
+
+(4) Activation and support
+```{r Activation and support line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+
+### Activation and support
+
+# filter by parameter variable, i.e. create a subset for Activation and support
+as.data <- quest.raw.data %>% filter(scale == "Activation and support")
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+as.data <- as.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# to create error bars, we need to summarize the data in a separate data frame
+as.plot.sd <- as.data %>%
+  group_by(group, item.wordings, .drop=TRUE) %>%
+  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# long plot
+as.plot<-ggplot(data = as.plot.sd,
+                  aes(x = item.wordings, y = mean,
+                      group = group, colour = group)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  facet_grid(~perspective)+
+  labs(data = as.data, y = "value", x = NULL,
+       title="Activation and support" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5),
+        axis.text.y = element_text(size = 6))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+as.plot
+
+```
+
+(5) Presence: posture and gaze
+```{r Presence: posture and gaze line plots, fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+
+### presence: posture and gaze 
+# filter by parameter variable, i.e. create a subset for Presence: posture and gaze
+ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# to create error bars, we need to summarize the data in a separate data frame
+ppg.plot.sd <- ppg.data %>%
+  group_by(group, item.wordings, .drop=TRUE) %>%
+  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# long plot
+ppg.plot<-ggplot(data = ppg.plot.sd,
+                  aes(x = item.wordings, y = mean,
+                      group = group, colour = group)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  facet_grid(~perspective)+
+  labs(data = ppg.data, y = "value", x = NULL,
+       title="Presence: posture and gaze" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5),
+        axis.text.y = element_text(size = 6))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+ppg.plot
+
+```
+
+(6) Presence: voice
+```{r Presence: voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+
+### Presence: voice 
+# filter by parameter variable, i.e. create a subset for Presence: voice
+pv.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# to create error bars, we need to summarize the data in a separate data frame
+pv.plot.sd <- pv.data %>%
+  group_by(group, item.wordings, .drop=TRUE) %>%
+  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# long plot
+pv.plot<-ggplot(data = pv.plot.sd,
+                  aes(x = item.wordings, y = mean,
+                      group = group, colour = group)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  facet_grid(~perspective)+
+  labs(data = pv.data, y = "value", x = NULL,
+       title="Presence: voice" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5),
+        axis.text.y = element_text(size = 6))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+pv.plot
+
+```
+
+(7) Presence: verbal and non-verbal intervention
+```{r Presence: verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+
+### Presence: verbal and non-verbal intervention 
+# filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
+pvni.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# to create error bars, we need to summarize the data in a separate data frame
+pvni.plot.sd <- pvni.data %>%
+  group_by(group, item.wordings, .drop=TRUE) %>%
+  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# long plot
+pvni.plot<-ggplot(data = pvni.plot.sd,
+                  aes(x = item.wordings, y = mean,
+                      group = group, colour = group)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  facet_grid(~perspective)+
+  labs(data = pvni.data, y = "value", x = NULL,
+       title="Presence: verbal and non-verbal intervention" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5),
+        axis.text.y = element_text(size = 6))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+pvni.plot
+
+```
+
+(8) Natural behaviour
+```{r Natural behaviour line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+
+### Natural behaviour 
+# filter by parameter variable, i.e. create a subset for Natural behaviour
+nb.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+nb.data <- nb.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# to create error bars, we need to summarize the data in a separate data frame
+nb.plot.sd <- nb.data %>%
+  group_by(group, item.wordings, .drop=TRUE) %>%
+  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# long plot
+nb.plot<-ggplot(data = nb.plot.sd,
+                  aes(x = item.wordings, y = mean,
+                      group = group, colour = group)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  facet_grid(~perspective)+
+  labs(data = nb.data, y = "value", x = NULL,
+       title="Natural behaviour" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5),
+        axis.text.y = element_text(size = 6))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+nb.plot
+
+```
+
+In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
+```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE}
 
@@
     xlab("")
-# quest.plot
+quest.plot
 
@@
 
-(ref:boxplot_all_scales-caption) Boxplot with individual points for all scales
+Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment.
+The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.
 
-```{r boxplot_all_scales, fig.cap = "(ref:boxplot_all_scales-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/boxplot_all_scales.png", dpi = 108)
-
-```
-
-In addition, we evaluated the duration of the speaking time during the lesson in the questionnaire by external and self-assessment.
-The following graph shows the duration of speaking time for experts and novices.
-
-```{r duration speaking time, echo = FALSE}
+```{r Duration speaking time, fig.width=5, fig.height = 5, echo = FALSE}
 # prepare data (selected from questionnaire data)
@@
       legend.position="none",
-      plot.title = element_text(size=11)) +
+      plot.title = element_text(size=11),
+      axis.text.x = element_text(size = 8)) +
     facet_grid(group~perspective) +
@@
 The Tobii Pro Glasses 2 software allows for non-screen based recordings of a participants’ attention while moving in real-world settings.
-The recordings of the glasses contain both HD-video from the subject’s perspective as well as the respective gaze data mapped onto the video.
+The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video.
 In order to map multiple recordings to AOIs, it is necessary to import the eye-tracking recordings into the Tobii Pro Analyzer software.

### 2021-01-29 paper_1/paper_1_supplement.tex
update manuscript -> plots

@@
 \usepackage{csquotes}
-\usepackage[titles]{tocloft}
-\cftpagenumbersoff{figure}
-\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
-\renewcommand{\cftfigaftersnum}{.\space}
-\setlength{\cftfigindent}{0pt}
-\setlength{\cftafterloftitleskip}{0pt}
-\settowidth{\cftfignumwidth}{Figure 10.\qquad}
-\cftpagenumbersoff{table}
-\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
-\renewcommand{\cfttabaftersnum}{.\space}
-\setlength{\cfttabindent}{0pt}
-\setlength{\cftafterloftitleskip}{0pt}
-\settowidth{\cfttabnumwidth}{Table 10.\qquad}
 \ifxetex
@@
 
-The first study is a laboratory study that uses a quasi-experimental cross-sectional study design to investigate whether the experience of teachers has an influence on the perception of and response to disruptions.
-The disturbances are experimentally varied using a previously written script.
-Thus, the aim is to find out whether differences in the allocation of attention between expertise groups can be detected in this controlled context.
+The aim of the pilot study was to investigate whether there are differences in how expert and novice teachers manage scripted classroom disruptions.
+The disruptions were experimentally varied using a previously written script.
+Thus, our aim was to find out whether differences in the allocation of attention between expertise groups can be detected in this controlled context.
 
-In order to answer this question, the hypothesis was formulated that teachers with more professional experience not only notice more disturbances but also notice them faster.
+In order to answer this question, the hypothesis was formulated that teachers with more professional experience not only notice more disruptions but also notice them faster.
 In the hypothesis, therefore, it is necessary to check what has already been shown in the research literature: In complex teaching situations, experts have a more structured and elaborate professional knowledge than novices in order to perceive and interpret relevant events and to act appropriately (Berliner, 2001; Lachner, Jarodzka, \& Nückles, 2016).
@@
 
-(ref:data\_collection-caption) Illustration of comic material that made the second author of this paper chuckle a bit. For advice on how to insert images, please see the code chunk.
+(ref:data\_collection-caption) Example for the set up during a mini-lesson
 
@@
 
-For this study, lesson units of n = 24 experts and n = 24 novices were recorded by the mobile laboratory of the Department of Empirical School and Classroom Research at the University of Leipzig.
-The two extreme groups were each divided into groups of four, with one group being invited on each of six different dates.
-All participants were asked to hold a 15-minute lesson.
-The duration of each appointment was approximately 2h30min: per extreme group 4 x 15min briefing, 15min lesson units, 10min technical preparation and follow-up and 5min buffer/break.
+For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig.
+The subjects were divided into groups of four, so the study was conducted on two different sessions.
+All participants were asked to hold a 10-minute lesson.
+The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering the questionnaire.
 
 One person from the group of 4 acted as a teacher, the other three subjects acted as the class.
-The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disturbances in the classroom (e.g.~putting their heads on the table, chatting, looking at their mobile phones, etc.).
+The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disruptions in the classroom (e.g.~putting their heads on the table, chatting, looking at their mobile phones, etc.).
 
-The lesson disturbances were displayed as instructions during the lesson for all ``students'' but not the teacher.
+The lesson disruptions were displayed as instructions during the lesson for all ``students'' but not the teacher.
 In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase.
@@
 
-The questionnaire contains the following scales:
+The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes.
+The scales on the quality of teaching are a validated questionnaire (Helmke et al.
+(2014)).
+Whereas the scales on the teacher's presence behaviour were derived from the research literature (Brophy (1986); Kiel, Frey, Weiß, and Weiss (2013); Kounin (2006); Marzano (2007); Nolting (2012)) and were used in the pilot for the first time.
+
+The following scales were assessed:
 
@@
 \item
-  classroom management
+  Classroom management
 \item
-  positive climate and motivation
+  Positive climate and motivation
 \item
-  clarity and structuredness
+  Clarity and structuredness
 \item
-  activation and support
+  Activation and support
 \item
-  presence: posture and gaze
+  Presence: posture and gaze
 \item
-  presence: voice
+  Presence: voice
 \item
-  presence: verbal and non-verbal intervention
+  Presence: verbal and non-verbal intervention
 \item
-  natural behaviour
+  Natural behaviour
 \end{enumerate}
@@
 
+The individual items of a scale were further represented in graphs.
+
+\begin{enumerate}
+\def\labelenumi{(\arabic{enumi})}
+\item
+  Classroom management
+  \includegraphics{paper_1_supplement_files/figure-latex/classroom management line plots-1.pdf}
+\item
+  Positive climate and motivation
+  \includegraphics{paper_1_supplement_files/figure-latex/Positive climate and motivation line plots-1.pdf}
+\item
+  Clarity and structuredness
+  \includegraphics{paper_1_supplement_files/figure-latex/Clarity and structuredness line plots-1.pdf}
+\item
+  Activation and support
+  \includegraphics{paper_1_supplement_files/figure-latex/Activation and support line plots-1.pdf}
+\item
+  Presence: posture and gaze
+  \includegraphics{paper_1_supplement_files/figure-latex/Presence: posture and gaze line plots-1.pdf}
+\item
+  Presence: voice
+  \includegraphics{paper_1_supplement_files/figure-latex/Presence: voice line plots-1.pdf}
+\item
+  Presence: verbal and non-verbal intervention
+  \includegraphics{paper_1_supplement_files/figure-latex/Presence: verbal and non-verbal intervention line plots-1.pdf}
+\item
+  Natural behaviour
+  \includegraphics{paper_1_supplement_files/figure-latex/Natural behaviour line plots-1.pdf}
+\end{enumerate}
+
+In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
+\includegraphics{paper_1_supplement_files/figure-latex/boxplot scales-1.pdf}
+
+Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment.
+The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.
+
+\includegraphics{paper_1_supplement_files/figure-latex/Duration speaking time-1.pdf}
+
 \hypertarget{eye-tracking-equipment}{%
@@
 The Tobii Pro Glasses 2 software allows for non-screen based recordings of a participants' attention while moving in real-world settings.
-The recordings of the glasses contain both HD-video from the subject's perspective as well as the respective gaze data mapped onto the video.
+The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video.
 In order to map multiple recordings to AOIs, it is necessary to import the eye-tracking recordings into the Tobii Pro Analyzer software.
@@
 
+\leavevmode\hypertarget{ref-brophy1986classroom}{}%
+Brophy, J. (1986). Classroom management techniques. \emph{Education and Urban Society}, \emph{18}(2), 182--194.
+
 \leavevmode\hypertarget{ref-cortina2015low}{}%
@@
 
+\leavevmode\hypertarget{ref-helmke2014unterrichtsdiagnostik}{}%
+Helmke, A., Helmke, T., Lenske, G., Pham, G., Praetorius, A.-K., Schrader, F.-W., \& AdeThurow, M.
+(2014).
+Unterrichtsdiagnostik mit EMU.
+\emph{Aus-Und Fortbildung Der Lehrkr{ä}fte in Hinblick Auf Verbesserung Der Diagnosef{ä}higkeit, Umgang Mit Heterogenit{ä}t Und Individuelle F{ö}rderung}, 149--163.
+
 \leavevmode\hypertarget{ref-R-purrr}{}%
@@
 Jarodzka, H., Scheiter, K., Gerjets, P., \& Van Gog, T. (2010). In the eyes of the beholder: How experts and novices interpret dynamic stimuli. \emph{Learning and Instruction}, \emph{20}(2), 146--154.
+
+\leavevmode\hypertarget{ref-kiel2013trainingsbuch}{}%
+Kiel, E., Frey, A., Weiß, S., \& Weiss, S. (2013). \emph{Trainingsbuch klassenf{ü}hrung} (Vol. 3992). UTB.
+
+\leavevmode\hypertarget{ref-kounin2006techniken}{}%
+Kounin, J. S. (2006). \emph{Techniken der klassenf{ü}hrung}. Waxmann Verlag.
 
@@
 \emph{Instructional Science}, \emph{44}(3), 197--203.
+
+\leavevmode\hypertarget{ref-marzano2007art}{}%
+Marzano, R. J. (2007). \emph{The art and science of teaching: A comprehensive framework for effective instruction}. Ascd.
 
@@
 Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+
+\leavevmode\hypertarget{ref-nolting2012storungen}{}%
+Nolting, H.-P. (2012). \emph{St{ö}rungen in der schulklasse}. Beltz.
 
@@
 
-\clearpage
-\renewcommand{\listfigurename}{Figure captions}
-
-\clearpage
-\renewcommand{\listtablename}{Table captions}
-
 \end{document}

### 2021-01-29 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
update manuscript -> plots

@@
         panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5))+
+        plot.title = element_text(hjust = 0.5),
+        axis.text.y = element_text(size = 3.5))+
   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+

### 2021-01-29 paper_1/paper_1_supplement_with_presence.Rmd
plots plots und noch mehr plots

--- 2021-01-29 paper_1/paper_1_supplement.Rmd
@@
 
-keywords          : "keywords"
-wordcount         : "X"
+keywords          : "Professional Vision, Expert-Novice-Paradigm, Eye-Tracking"
+wordcount         : "1949"
 
@@
 floatsintext      : yes
-figsintext        : yes
 figurelist        : no
@@
 
-(ref:data_collection-caption) Example for the set up during a mini-lesson
+(ref:datacollection-caption) Example for set up during a mini-lesson
 
-```{r data collection, fig.cap = "(ref:data_collection-caption)", fig.align = "center", echo = FALSE}
+```{r datacollection, fig.cap = "(ref:datacollection-caption)", fig.align = "center", echo = FALSE}
 
-knitr::include_graphics("./pictures/data_collection.png", dpi = 108)
+knitr::include_graphics("./pictures/datacollection.png", dpi = 108)
 
@@
 (4) Activation and support
-(5) Presence: posture and gaze
+(5) Presence: posture/gaze
 (6) Presence: voice
@@
 
+\newpage
 The individual items of a scale were further represented in graphs.
@@
 ```
-
+\newpage
 (2) Positive climate and motivation
@@
 ```
-
+\newpage
 (3) Clarity and structuredness
@@
 ```
-
+\newpage
 (4) Activation and support
@@
 ```
+\newpage
+(5) Presence: posture/gaze
+```{r Presence: posture/gaze line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
 
-(5) Presence: posture and gaze
-```{r Presence: posture and gaze line plots, fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+### Presence: posture/gaze
 
-### presence: posture and gaze 
-# filter by parameter variable, i.e. create a subset for Presence: posture and gaze
+# filter by parameter variable, i.e. create a subset for Presence: posture/gaze
 ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
@@
   labs(data = ppg.data, y = "value", x = NULL,
-       title="Presence: posture and gaze" ,
+       title="Presence: posture/gaze" ,
        subtitle=NULL)+
@@
 
+\newpage
 (6) Presence: voice
@@
 # filter by parameter variable, i.e. create a subset for Presence: voice
-pv.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
+pv.data <- quest.raw.data %>% filter(scale == "Presence: voice")
 
@@
 ```
-
+\newpage
 (7) Presence: verbal and non-verbal intervention
@@
 # filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
-pvni.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
+pvni.data <- quest.raw.data %>% filter(scale == "Presence: verbal and non-verbal intervention")
 
@@
 ```
-
+\newpage
 (8) Natural behaviour
@@
 # filter by parameter variable, i.e. create a subset for Natural behaviour
-nb.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
+nb.data <- quest.raw.data %>% filter(scale == "Natural behaviour")
 
@@
 ```
-
+\newpage
 In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
@@
 ```
-
+\newpage
 Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment.
@@
 ```
+\newpage
 

### 2021-01-29 paper_1/paper_1_supplement_without_presence.Rmd
plots plots und noch mehr plots

--- 2021-01-29 paper_1/paper_1_supplement_with_presence.Rmd
@@
 
-(ref:datacollection-caption) Example for set up during a mini-lesson
+(ref:datacollection-caption) Example for set-up during a mini-lesson
 
@@
 knitr::include_graphics("./pictures/datacollection.png", dpi = 108)
-
-# # How to insert images in papaja
-# - pictures must be png
-# - I created a pictures folder in the main folder, just dumb pictures there
-# - you just need to hand the name and path of the picture to the knitr::: function (see above)
-# - the dpi argument is for adjusting the size on the page in pixels
-
-# in order to write the caption, you have to use the line just above the code chunk (ref:YOURTEXT-caption) and then just write behind it
-# the code chunk then opens and after "r" it needs to provide a name for the code chunk, must be unique in the document
-# the fig.cap = then calls the text from the line just above
-# fig.align allows to position the pic on page, center ist probablby best
-# echo = false ensures that the code chunk does not occur in the pdf
-# Now, go and try putting your own images in the paper 
-#
-# TIP = check line 46 in this manuscript. THis section ets global properties for how graphs are put in the paper. 
-#         if floatsintext      : yes  --> pics, graphs, tables will be put where the code chunk is
-#         if floatsintext      : no   --> pics, graphs, tables will be put at the end as is required by some journals
-# TIP: check the folder "papaja_example&tutorial" that I put in this folder for paper1
-# Tip: make a bookmark of this and skim through it: http://frederikaust.com/papaja_man/
 
@@
 ```
-\newpage
-(5) Presence: posture/gaze
-```{r Presence: posture/gaze line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
 
-### Presence: posture/gaze
-
-# filter by parameter variable, i.e. create a subset for Presence: posture/gaze
-ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-ppg.plot.sd <- ppg.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-ppg.plot<-ggplot(data = ppg.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = ppg.data, y = "value", x = NULL,
-       title="Presence: posture/gaze" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-ppg.plot
-
-```
-
-\newpage
-(6) Presence: voice
-```{r Presence: voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-
-### Presence: voice 
-# filter by parameter variable, i.e. create a subset for Presence: voice
-pv.data <- quest.raw.data %>% filter(scale == "Presence: voice")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-pv.plot.sd <- pv.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-pv.plot<-ggplot(data = pv.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = pv.data, y = "value", x = NULL,
-       title="Presence: voice" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-pv.plot
-
-```
-\newpage
-(7) Presence: verbal and non-verbal intervention
-```{r Presence: verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-
-### Presence: verbal and non-verbal intervention 
-# filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
-pvni.data <- quest.raw.data %>% filter(scale == "Presence: verbal and non-verbal intervention")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-pvni.plot.sd <- pvni.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-pvni.plot<-ggplot(data = pvni.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = pvni.data, y = "value", x = NULL,
-       title="Presence: verbal and non-verbal intervention" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-pvni.plot
-
-```
 \newpage

### 2021-01-29 paper_1/paper_1_supplement_without_presence.tex
plots plots und noch mehr plots

--- 2021-01-29 paper_1/paper_1_supplement.tex
@@
   pdflang={en-EN},
-  pdfkeywords={keywords},
+  pdfkeywords={Professional Vision, Expert-Novice-Paradigm, Eye-Tracking},
   hidelinks,
@@
 \shorttitle{Visual attention in teaching and learning processes}
-\keywords{keywords\newline\indent Word count: X}
+\keywords{Professional Vision, Expert-Novice-Paradigm, Eye-Tracking\newline\indent Word count: 1949}
 \usepackage{lineno}
@@
 
-(ref:data\_collection-caption) Example for the set up during a mini-lesson
+\begin{figure}
 
-\textbackslash begin\{figure\}
+{\centering \includegraphics{./pictures/datacollection}
 
-\{\centering \includegraphics{./pictures/data_collection}
+}
 
-\}
-
-\textbackslash caption\{(ref:data\_collection-caption)\}(\#fig:data collection)
-\textbackslash end\{figure\}
+\caption{Example for set-up during a mini-lesson}\label{fig:datacollection}
+\end{figure}
 
@@
 \item
-  Presence: posture and gaze
+  Presence: posture/gaze
 \item
@@
 
+\newpage
+
 The individual items of a scale were further represented in graphs.
@@
 \def\labelenumi{(\arabic{enumi})}
+\tightlist
 \item
   Classroom management
-  \includegraphics{paper_1_supplement_files/figure-latex/classroom management line plots-1.pdf}
+  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/classroom management line plots-1.pdf}
+  \newpage
 \item
   Positive climate and motivation
-  \includegraphics{paper_1_supplement_files/figure-latex/Positive climate and motivation line plots-1.pdf}
+  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/Positive climate and motivation line plots-1.pdf}
+  \newpage
 \item
   Clarity and structuredness
-  \includegraphics{paper_1_supplement_files/figure-latex/Clarity and structuredness line plots-1.pdf}
+  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/Clarity and structuredness line plots-1.pdf}
+  \newpage
 \item
   Activation and support
-  \includegraphics{paper_1_supplement_files/figure-latex/Activation and support line plots-1.pdf}
-\item
-  Presence: posture and gaze
-  \includegraphics{paper_1_supplement_files/figure-latex/Presence: posture and gaze line plots-1.pdf}
-\item
-  Presence: voice
-  \includegraphics{paper_1_supplement_files/figure-latex/Presence: voice line plots-1.pdf}
-\item
-  Presence: verbal and non-verbal intervention
-  \includegraphics{paper_1_supplement_files/figure-latex/Presence: verbal and non-verbal intervention line plots-1.pdf}
+  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/Activation and support line plots-1.pdf}
+\end{enumerate}
+
+\newpage
+
+\begin{enumerate}
+\def\labelenumi{(\arabic{enumi})}
+\setcounter{enumi}{7}
+\tightlist
 \item
   Natural behaviour
-  \includegraphics{paper_1_supplement_files/figure-latex/Natural behaviour line plots-1.pdf}
+  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/Natural behaviour line plots-1.pdf}
+  \newpage
+  In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
+  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/boxplot scales-1.pdf}
+  \newpage
+  Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment.
+The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.
 \end{enumerate}
 
-In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
-\includegraphics{paper_1_supplement_files/figure-latex/boxplot scales-1.pdf}
-
-Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment.
-The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.
-
-\includegraphics{paper_1_supplement_files/figure-latex/Duration speaking time-1.pdf}
+\includegraphics{paper_1_supplement_without_presence_files/figure-latex/Duration speaking time-1.pdf}
+\newpage
 

### 2021-02-02 paper_1/paper_1.tex
update manuscript -> plots
demotable in paper1 jetzt mit label

--- 2021-01-25 paper_1/paper_1.tex
@@
 
-Hey Mandy, hier wollte ich dir mal zeigen wie man Bilder in papaja einbindet. Viel Spass damit. Ein Beispiel für Tabellen und Graphen machen wir auch zeitnah.
-
 \begin{figure}

### 2021-02-02 paper_1/schrott/paper_1_supplement_with_presence.tex
creating word + pdf paper1_supplement

--- 2021-01-29 paper_1/paper_1_supplement_without_presence.tex
@@
 
-\caption{Example for set-up during a mini-lesson}\label{fig:datacollection}
+\caption{Example for set up during a mini-lesson}\label{fig:datacollection}
 \end{figure}
@@
   Classroom management
-  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/classroom management line plots-1.pdf}
+  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/classroom management line plots-1.pdf}
   \newpage
@@
   Positive climate and motivation
-  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/Positive climate and motivation line plots-1.pdf}
+  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/Positive climate and motivation line plots-1.pdf}
   \newpage
@@
   Clarity and structuredness
-  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/Clarity and structuredness line plots-1.pdf}
+  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/Clarity and structuredness line plots-1.pdf}
   \newpage
@@
   Activation and support
-  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/Activation and support line plots-1.pdf}
+  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/Activation and support line plots-1.pdf}
+  \newpage
 \end{enumerate}
 
+\begin{figure}
+
+{\centering \includegraphics{./pictures/presenceposturegaze}
+
+}
+
+\caption{(5) Presence: posture/gaze}\label{fig:presenceposturegaze}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+
+{\centering \includegraphics{./pictures/presencevoice}
+
+}
+
+\caption{(6) Presence: voice}\label{fig:presencevoice}
+\end{figure}
+\newpage
+
+\begin{figure}
+
+{\centering \includegraphics{./pictures/presenceverbalnonverbalintervention}
+
+}
+
+\caption{(7) Presence: verbal and non-verbal intervention}\label{fig:presenceverbalnonverbalintervention}
+\end{figure}
 \newpage
@@
   Natural behaviour
-  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/Natural behaviour line plots-1.pdf}
+  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/Natural behaviour line plots-1.pdf}
   \newpage
   In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
-  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/boxplot scales-1.pdf}
+  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/boxplot scales-1.pdf}
   \newpage
@@
 
-\includegraphics{paper_1_supplement_without_presence_files/figure-latex/Duration speaking time-1.pdf}
+\includegraphics{paper_1_supplement_with_presence_files/figure-latex/Duration speaking time-1.pdf}
 \newpage

### 2021-02-02 paper_1/schrott/paper_1_supplement_without_presence.tex
creating word + pdf paper1_supplement

--- 2021-01-29 paper_1/paper_1_supplement_without_presence.tex
@@
 
-\caption{\label{tab:demographicspilottable}Demographic Informationand and Teaching Experience}
+\caption{\label{tab:demographicspilot1table}Demographic Informationand and Teaching Experience}
 
@@
 
-The table below provides an overview over the mean, min, max and standard deviation of all scales.
+\ref{tab:allscales} The table provides an overview over the mean, range and standard deviation of all scales.
 
@@
 
-\caption{\label{tab:table all scales}Mean values of all scales}
+\caption{\label{tab:allscales}Mean values of all scales}
 

### 2021-02-03 paper_1/paper_1_supplement.Rmd
update paper 1

@@
 authornote: |
-  The study was carried out with the permission of Ethics Committee of the University of Leipzig.
+  The study was carried out with the permission of the Ethics Committee of the University of Leipzig.
 
 abstract: |
-  This document is a supplement to the paper.
+  This document is a supplement to the paper and shows first graphs findings from the pilot study.
 
-keywords          : "keywords"
-wordcount         : "X"
+keywords          : "Professional Vision, Expert-Novice-Paradigm, Eye-Tracking"
+wordcount         : "1949"
 
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_pdf #bookdown::word_document2
 ---
@@
 
-The table below provides an overview over the mean, min, max and standard deviation of all scales.
+The table at the end of the manuscript provides an overview over the mean, the range and standard deviation of all scales.
 
@@
 
-The individual items of a scale were further represented in graphs.
+\newpage
+The individual items of a scale are further represented in graphs.
 
@@
 ```
+\newpage
 
-(5) Presence: posture and gaze
-```{r Presence: posture and gaze line plots, fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+(ref:presenceposturegaze-caption) (5) Presence: posture/gaze
 
-### presence: posture and gaze 
-# filter by parameter variable, i.e. create a subset for Presence: posture and gaze
-ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
+```{r presenceposturegaze, fig.cap = "(ref:presenceposturegaze-caption)", fig.align = "center", echo = FALSE}
 
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+knitr::include_graphics("./pictures/presenceposturegaze.png", dpi = 108)
 
-# to create error bars, we need to summarize the data in a separate data frame
-ppg.plot.sd <- ppg.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+# ```{r Presence: posture/gaze line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
 
-# long plot
-ppg.plot<-ggplot(data = ppg.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = ppg.data, y = "value", x = NULL,
-       title="Presence: posture and gaze" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-ppg.plot
+# ### Presence: posture/gaze 
+# 
+# # filter by parameter variable, i.e. create a subset for Presence: posture/gaze
+# ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
+# 
+# # value sometimes contained text before filtering, we have to convert the numbers to numeric
+# ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+# 
+# # to create error bars, we need to summarize the data in a separate data frame
+# ppg.plot.sd <- ppg.data %>%
+#   group_by(group, item.wordings, .drop=TRUE) %>%
+#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+# 
+# # long plot
+# ppg.plot<-ggplot(data = ppg.plot.sd,
+#                   aes(x = item.wordings, y = mean,
+#                       group = group, colour = group)) +
+#   geom_line()+
+#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+#   theme_light() +
+#   ylim(1,4)+
+#   facet_grid(~perspective)+
+#   labs(data = ppg.data, y = "value", x = NULL,
+#        title="Presence: posture/gaze" ,
+#        subtitle=NULL)+
+#   theme(legend.position="bottom",
+#         panel.spacing.x = ,
+#         plot.title = element_text(hjust = 0.5),
+#         axis.text.y = element_text(size = 6))+
+#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+#   coord_flip()
+# ppg.plot
 
@@
 
-(6) Presence: voice
-```{r Presence: voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+\newpage
 
-### Presence: voice 
-# filter by parameter variable, i.e. create a subset for Presence: voice
-pv.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
+(ref:presencevoice-caption) (6) Presence: voice
 
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+```{r presencevoice, fig.cap = "(ref:presencevoice-caption)", fig.align = "center", echo = FALSE}
 
-# to create error bars, we need to summarize the data in a separate data frame
-pv.plot.sd <- pv.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+knitr::include_graphics("./pictures/presencevoice.png", dpi = 108)
 
-# long plot
-pv.plot<-ggplot(data = pv.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = pv.data, y = "value", x = NULL,
-       title="Presence: voice" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-pv.plot
+# ```{r Presence: voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+# 
+# ### Presence: voice 
+# # filter by parameter variable, i.e. create a subset for Presence: voice
+# pv.data <- quest.raw.data %>% filter(scale == "Presence: voice")
+# 
+# # value sometimes contained text before filtering, we have to convert the numbers to numeric
+# pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+# 
+# # to create error bars, we need to summarize the data in a separate data frame
+# pv.plot.sd <- pv.data %>%
+#   group_by(group, item.wordings, .drop=TRUE) %>%
+#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+# 
+# # long plot
+# pv.plot<-ggplot(data = pv.plot.sd,
+#                   aes(x = item.wordings, y = mean,
+#                       group = group, colour = group)) +
+#   geom_line()+
+#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+#   theme_light() +
+#   ylim(1,4)+
+#   facet_grid(~perspective)+
+#   labs(data = pv.data, y = "value", x = NULL,
+#        title="Presence: voice" ,
+#        subtitle=NULL)+
+#   theme(legend.position="bottom",
+#         panel.spacing.x = ,
+#         plot.title = element_text(hjust = 0.5),
+#         axis.text.y = element_text(size = 6))+
+#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+#   coord_flip()
+# pv.plot
 
 ```
+\newpage
 
-(7) Presence: verbal and non-verbal intervention
-```{r Presence: verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+(ref:presenceverbalnonverbalintervention-caption) (7) Presence: verbal and non-verbal intervention
 
-### Presence: verbal and non-verbal intervention 
-# filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
-pvni.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
+```{r presenceverbalnonverbalintervention, fig.cap = "(ref:presenceverbalnonverbalintervention-caption)", fig.align = "center", echo = FALSE}
 
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+knitr::include_graphics("./pictures/presenceverbalnonverbalintervention.png", dpi = 108)
 
-# to create error bars, we need to summarize the data in a separate data frame
-pvni.plot.sd <- pvni.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-pvni.plot<-ggplot(data = pvni.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = pvni.data, y = "value", x = NULL,
-       title="Presence: verbal and non-verbal intervention" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-pvni.plot
+# ```{r Presence: verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+# 
+# ### Presence: verbal and non-verbal intervention 
+# # filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
+# pvni.data <- quest.raw.data %>% filter(scale == "Presence: verbal and non-verbal intervention")
+# 
+# # value sometimes contained text before filtering, we have to convert the numbers to numeric
+# pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+# 
+# # to create error bars, we need to summarize the data in a separate data frame
+# pvni.plot.sd <- pvni.data %>%
+#   group_by(group, item.wordings, .drop=TRUE) %>%
+#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+# 
+# # long plot
+# pvni.plot<-ggplot(data = pvni.plot.sd,
+#                   aes(x = item.wordings, y = mean,
+#                       group = group, colour = group)) +
+#   geom_line()+
+#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+#   theme_light() +
+#   ylim(1,4)+
+#   facet_grid(~perspective)+
+#   labs(data = pvni.data, y = "value", x = NULL,
+#        title="Presence: verbal and non-verbal intervention" ,
+#        subtitle=NULL)+
+#   theme(legend.position="bottom",
+#         panel.spacing.x = ,
+#         plot.title = element_text(hjust = 0.5),
+#         axis.text.y = element_text(size = 6))+
+#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+#   coord_flip()
+# pvni.plot
 
 ```
-
+\newpage
 (8) Natural behaviour
@@
 ```
+\newpage
+In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
 
-In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
 ```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE}
@@
 Finally, mapping gaze to people or any moving objects complicated the analyses further.
+
+### Eye-Tracking Data
+
+#### Gaze relational index (GRI)
+
+The GRI is a measure of visual expertise in information processing.
+This metric is calculated as the ratio of mean fixation duration to fixation count.
+The GRI is higher for novices than for experts.
+(@gegenfurtner2020gaze)
+
+```{r GRItable, echo = FALSE}
+
+# prepare data (selected from questionnaire data)
+et.raw.data<-read.table("./data/Aperol_pilot_02_glasses_fixation_metrics.tsv", dec=",", sep="\t", header=T)
+
+# calculate GRI
+
+# create a basic table (tibble) using tidyverse functions
+et.quest.table <- et.raw.data %>%
+  summarise("M Fixation Number" = round(mean(Number_of_whole_fixations), 2),
+            "SE Fixation Number" = round(se(Number_of_whole_fixations), 2),
+            "M Duration Fixation" = round(mean(Total_duration_of_whole_fixations)),
+            "SE Duration Fixation" = round(se(Total_duration_of_whole_fixations))
+            )
+
+# format and insert table in manuscript
+apa_table(
+  et.quest.table,
+  caption = "Number and Duration of fixations",
+  # note = "Write Note here", 
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  )
+
+```
+
+### Coding Data
+
+The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (@kuckartz2019analyzing).
+The following coding scheme has been developed for coding:
 

### 2021-02-03 paper_1/paper_1_supplement.tex
update paper 1

@@
 
-The study was carried out with the permission of Ethics Committee of the University of Leipzig.
+The study was carried out with the permission of the Ethics Committee of the University of Leipzig.
 
@@
 \abstract{
-This document is a supplement to the paper.
+This document is a supplement to the paper and shows first graphs findings from the pilot study.
 }
@@
 
-(ref:data\_collection-caption) Example for the set up during a mini-lesson
+\begin{figure}
 
-\textbackslash begin\{figure\}
+{\centering \includegraphics{./pictures/datacollection}
 
-\{\centering \includegraphics{./pictures/data_collection}
+}
 
-\}
-
-\textbackslash caption\{(ref:data\_collection-caption)\}(\#fig:data collection)
-\textbackslash end\{figure\}
+\caption{Example for set up during a mini-lesson}\label{fig:datacollection}
+\end{figure}
 
@@
 
-The individual items of a scale were further represented in graphs.
+\newpage
+
+The individual items of a scale are further represented in graphs.
 
@@
 \def\labelenumi{(\arabic{enumi})}
+\tightlist
 \item
@@
   \includegraphics{paper_1_supplement_files/figure-latex/classroom management line plots-1.pdf}
+  \newpage
 \item
@@
   \includegraphics{paper_1_supplement_files/figure-latex/Positive climate and motivation line plots-1.pdf}
+  \newpage
 \item
@@
   \includegraphics{paper_1_supplement_files/figure-latex/Clarity and structuredness line plots-1.pdf}
+  \newpage
 \item
@@
   \includegraphics{paper_1_supplement_files/figure-latex/Activation and support line plots-1.pdf}
-\item
-  Presence: posture and gaze
-  \includegraphics{paper_1_supplement_files/figure-latex/Presence: posture and gaze line plots-1.pdf}
-\item
-  Presence: voice
-  \includegraphics{paper_1_supplement_files/figure-latex/Presence: voice line plots-1.pdf}
-\item
-  Presence: verbal and non-verbal intervention
-  \includegraphics{paper_1_supplement_files/figure-latex/Presence: verbal and non-verbal intervention line plots-1.pdf}
+  \newpage
+\end{enumerate}
+
+\begin{figure}
+
+{\centering \includegraphics{./pictures/presenceposturegaze}
+
+}
+
+\caption{(5) Presence: posture/gaze}\label{fig:presenceposturegaze}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+
+{\centering \includegraphics{./pictures/presencevoice}
+
+}
+
+\caption{(6) Presence: voice}\label{fig:presencevoice}
+\end{figure}
+\newpage
+
+\begin{figure}
+
+{\centering \includegraphics{./pictures/presenceverbalnonverbalintervention}
+
+}
+
+\caption{(7) Presence: verbal and non-verbal intervention}\label{fig:presenceverbalnonverbalintervention}
+\end{figure}
+\newpage
+
+\begin{enumerate}
+\def\labelenumi{(\arabic{enumi})}
+\setcounter{enumi}{7}
+\tightlist
 \item
@@
   \includegraphics{paper_1_supplement_files/figure-latex/Natural behaviour line plots-1.pdf}
+  \newpage
+  In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
 \end{enumerate}
 
-In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
 \includegraphics{paper_1_supplement_files/figure-latex/boxplot scales-1.pdf}
-
+\newpage
 Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment.
@@
 \includegraphics{paper_1_supplement_files/figure-latex/Duration speaking time-1.pdf}
+\newpage
 
@@
 Finally, mapping gaze to people or any moving objects complicated the analyses further.
+
+\hypertarget{eye-tracking-data}{%
+\subsubsection{Eye-Tracking Data}\label{eye-tracking-data}}
+
+\hypertarget{gaze-relational-index-gri}{%
+\paragraph{Gaze relational index (GRI)}\label{gaze-relational-index-gri}}
+
+The GRI is a measure of visual expertise in information processing.
+This metric is calculated as the ratio of mean fixation duration to fixation count.
+The GRI is higher for novices than for experts.
+(Gegenfurtner et al.
+(2020))
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:GRItable}Number and Duration of fixations}
+
+\small{
+
+\begin{tabular}{llll}
+\toprule
+M Fixation Number & \multicolumn{1}{c}{SE Fixation Number} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{SE Duration Fixation}\\
+\midrule
+842.50 & 146.69 & 382,411.00 & 95,132.00\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\hypertarget{coding-data}{%
+\subsubsection{Coding Data}\label{coding-data}}
+
+The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz and Rädiker (2019)). Therefore, a coding scheme was
 
@@
 
+\leavevmode\hypertarget{ref-gegenfurtner2020gaze}{}%
+Gegenfurtner, A., Boucheix, J.-M., Gruber, H., Hauser, F., Lehtinen, E., \& Lowe, R.
+K.
+(2020).
+The gaze relational index as a measure of visual expertise.
+\emph{Journal of Expertise.
+East Lansing, Michigan: Michigan State University, 2020, Vol.
+3, Iss.
+1}.
+
 \leavevmode\hypertarget{ref-helmke2014unterrichtsdiagnostik}{}%
@@
 Kounin, J. S. (2006). \emph{Techniken der klassenf{ü}hrung}. Waxmann Verlag.
+
+\leavevmode\hypertarget{ref-kuckartz2019analyzing}{}%
+Kuckartz, U., \& Rädiker, S. (2019). \emph{Analyzing qualitative data with MAXQDA}. Springer.
 

### 2021-02-04 paper_1/paper_1_supplement.Rmd
added table GRI

@@
 # prepare data (selected from questionnaire data)
-et.raw.data<-read.table("./data/Aperol_pilot_02_glasses_fixation_metrics.tsv", dec=",", sep="\t", header=T)
+et.raw.data<-read.table("./data/Aperol_pilot_glasses_raw_fixation_saccades_metrics.tsv", dec=",", sep="\t", header=T)
+
+# converting to integer to numeric
+et.raw.data <- et.raw.data %>%  mutate(Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
+                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations))
 
 # calculate GRI 
+view(et.raw.data)
 
 # create a basic table (tibble) using tidyverse functions
-et.quest.table <- et.raw.data %>%
-  summarise("M Fixation Number" = round(mean(Number_of_whole_fixations), 2),
-            "SE Fixation Number" = round(se(Number_of_whole_fixations), 2),
-            "M Duration Fixation" = round(mean(Total_duration_of_whole_fixations)),
-            "SE Duration Fixation" = round(se(Total_duration_of_whole_fixations))
+et.raw.table <- et.raw.data %>%
+  group_by(Participant, Variable) %>%
+  summarise("Fixation Number" = Number_of_whole_fixations,
+            "M Duration Fixation" = mean(Total_duration_of_whole_fixations),
+            "SE Duration Fixation" = round(se(Total_duration_of_whole_fixations, na.rm = TRUE), 2),
+            "GRI" = round(mean(Total_duration_of_whole_fixations) / Number_of_whole_fixations)
             )
@@
 apa_table(
-  et.quest.table,
-  caption = "Number and Duration of fixations",
+  et.raw.table,
+  caption = "Number and Duration (in msec) of Fixations",
   # note = "Write Note here", 

### 2021-02-04 paper_1/paper_1_supplement.tex
added table GRI

@@
 
+\begin{verbatim}
+## # A tibble: 8 x 6
+## # Groups:   Participant [8]
+##   Participant Variable `Fixation Number` `M Duration Fix~ `SE Duration Fi~   GRI
+##   <chr>       <chr>                <dbl>            <dbl>            <dbl> <dbl>
+## 1 01_01_D     Expert                 803           316571               NA   394
+## 2 01_02_A     Expert                1070           385812               NA   361
+## 3 01_03_B     Novice                 617           374315               NA   607
+## 4 01_04_C     Novice                 769           384537               NA   500
+## 5 02_01_A     Novice                 569           101541               NA   178
+## 6 02_02_B     Novice                1140           520431               NA   457
+## 7 02_03_C     Novice                1048           469018               NA   448
+## 8 02_04_D     Novice                 613           438655               NA   716
+\end{verbatim}
+
 \begin{table}[h]
@@
 
-\caption{\label{tab:GRItable}Number and Duration of fixations}
+\caption{\label{tab:GRItable}Number and Duration (in msec) of Fixations}
 
@@
 
-\begin{tabular}{llll}
+\begin{tabular}{llllll}
 \toprule
-M Fixation Number & \multicolumn{1}{c}{SE Fixation Number} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{SE Duration Fixation}\\
+Participant & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{SE Duration Fixation} & \multicolumn{1}{c}{GRI}\\
 \midrule
-842.50 & 146.69 & 382,411.00 & 95,132.00\\
+01\_01\_D & Expert & 803.00 & 316,571.00 & NA & 394.00\\
+01\_02\_A & Expert & 1,070.00 & 385,812.00 & NA & 361.00\\
+01\_03\_B & Novice & 617.00 & 374,315.00 & NA & 607.00\\
+01\_04\_C & Novice & 769.00 & 384,537.00 & NA & 500.00\\
+02\_01\_A & Novice & 569.00 & 101,541.00 & NA & 178.00\\
+02\_02\_B & Novice & 1,140.00 & 520,431.00 & NA & 457.00\\
+02\_03\_C & Novice & 1,048.00 & 469,018.00 & NA & 448.00\\
+02\_04\_D & Novice & 613.00 & 438,655.00 & NA & 716.00\\
 \bottomrule
@@
 
-The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz and Rädiker (2019)). Therefore, a coding scheme was
+The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz and Rädiker (2019)).
+The following coding scheme has been developed for coding:
 

### 2021-02-04 paper_1/paper_1_supplement.Rmd
table GRI

@@
 if (!require(papaja)) install.packages('papaja'); library(papaja)
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
 
@@
 # calculate GRI
-view(et.raw.data)
 
@@
   summarise("Fixation Number" = Number_of_whole_fixations,
-            "M Duration Fixation" = mean(Total_duration_of_whole_fixations),
-            "SE Duration Fixation" = round(se(Total_duration_of_whole_fixations, na.rm = TRUE), 2),
-            "GRI" = round(mean(Total_duration_of_whole_fixations) / Number_of_whole_fixations)
-            )
+            "Average Duration Fixation" = Average_duration_of_whole_fixations,
+            "SE Duration Fixation" = se(Total_duration_of_whole_fixations),
+            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
+view(et.raw.table)
 
@@
   )
+
+```
+
+```{r boxplot GRI, fig.width=6, fig.height = 8, echo = FALSE}
+
+et.plot <- et.raw.data %>%
+  ggplot(aes(x=Number_of_whole_fixations, y=value, fill=scale)) +
+    geom_boxplot() +
+    scale_x_discrete(guide = guide_axis(angle = 70)) +
+    geom_jitter(color="black", size=0.4, alpha=0.9) +
+    theme_light() +
+    theme(
+      legend.position="none",
+      plot.title = element_text(size=11)
+    ) +
+    facet_grid(~Variable)+
+    ggtitle("Boxplot with individual points for Number of fixations") +
+    xlab("")
+et.plot
 

### 2021-02-04 paper_1/paper_1_supplement.tex
table GRI

@@
 
-\begin{verbatim}
-## # A tibble: 8 x 6
-## # Groups:   Participant [8]
-##   Participant Variable `Fixation Number` `M Duration Fix~ `SE Duration Fi~   GRI
-##   <chr>       <chr>                <dbl>            <dbl>            <dbl> <dbl>
-## 1 01_01_D     Expert                 803           316571               NA   394
-## 2 01_02_A     Expert                1070           385812               NA   361
-## 3 01_03_B     Novice                 617           374315               NA   607
-## 4 01_04_C     Novice                 769           384537               NA   500
-## 5 02_01_A     Novice                 569           101541               NA   178
-## 6 02_02_B     Novice                1140           520431               NA   457
-## 7 02_03_C     Novice                1048           469018               NA   448
-## 8 02_04_D     Novice                 613           438655               NA   716
-\end{verbatim}
-
 \begin{table}[h]

### 2021-02-08 paper_1/paper_1_supplement.Rmd
added coded speaking time

@@
 
+quest.raw.data <- quest.raw.data %>% mutate (speaking.data)
+
 speaking.plot <- quest.raw.data %>%
@@
 
-# converting to integer to numeric
+# converting integer to numeric
 et.raw.data <- et.raw.data %>%  mutate(Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
@@
             "SE Duration Fixation" = se(Total_duration_of_whole_fixations),
+            "TOI length" = TOI,
             "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
@@
 The following coding scheme has been developed for coding:
+
+``` {r coded speaking time, echo = FALSE}
+### read in data for 01_01_expert_D
+speaking.data.01.01 <- read.table("./data/Aperol_pilot_01_01_expert_D_cam4.txt", dec=",", sep="\t", header=T)
+
+### select relevant columns
+speaking.data.01.01 <- speaking.data.01.01  %>% select(
+  Dokumentgruppe,
+  Dokumentname,
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+str(speaking.data.01.01)
+
+### checking for missing values
+is.na(speaking.data.01.01)
+which(is.na(speaking.data.01.01))
+
+### filter only speaking time of teacher and "kodiert von Anna" as row 
+speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
+                                           Dokumentgruppe == "kodiert von Anna")
+
+speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)
+
+# read in data for 01_02_expert_A
+speaking.data.01.02 <- read.table("./data/Aperol_pilot_01_02_expert_A_cam1_AL", dec=",", sep="\t", header=T)
+
+### select relevant columns
+speaking.data.01.02 <- speaking.data.01.02 %>% select(
+  Dokumentgruppe,
+  Dokumentname,
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+str(speaking.data.01.02)
+
+### checking for missing values
+is.na(speaking.data.01.01)
+which(is.na(speaking.data.01.01))
+
+### filter only speaking time of teacher and "kodiert von Anna" as row 
+speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
+                                           Dokumentgruppe == "kodiert von Anna")
+
+speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)
+
+```
 

### 2021-02-08 paper_1/paper_1_supplement.Rmd
coding speaking time

@@
 
-The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (@kuckartz2019analyzing).
-The following coding scheme has been developed for coding:
+The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (@kuckartz2019analyzing). The following coding scheme was developed:
+
+-
+
+First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher.
+The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.
 
@@
 ### read in data for 01_01_expert_D
-speaking.data.01.01 <- read.table("./data/Aperol_pilot_01_01_expert_D_cam4.txt", dec=",", sep="\t", header=T)
+speaking.data.01.01 <- read.delim("./data/Aperol_pilot_01_01_expert_D_cam4_AL_MK.txt", dec=",", sep="\t", header=T)
 
@@
 # read in data for 01_02_expert_A
-speaking.data.01.02 <- read.table("./data/Aperol_pilot_01_02_expert_A_cam1_AL", dec=",", sep="\t", header=T)
+speaking.data.01.02 <- read.delim("./data/Aperol_pilot_01_02_expert_A_cam1_AL.txt", dec=",", sep="\t", header=T)
+
+view(speaking.data.01.02)
 
@@
 speaking.data.01.02 <- speaking.data.01.02 %>% select(
-  Dokumentgruppe,
   Dokumentname,
@@
 
-str(speaking.data.01.02)
+### checking for missing values
+is.na(speaking.data.01.02)
+which(is.na(speaking.data.01.02))
+
+### filter only speaking time of teacher as row 
+speaking.data.01.02 <- speaking.data.01.02 %>% filter (Code == "speaking time\\teacher")
+
+view(speaking.data.01.02)
+
+speaking.data.01.02 <- sum(speaking.data.01.02$Abdeckungsgrad..)
+
+# read in data for 01_03_novice_B
+speaking.data.01.03 <- read.delim("./data/Aperol_pilot_01_03_novice_B_cam1.txt", dec=",", sep="\t", header=T)
+
+view(speaking.data.01.03)
+
+### select relevant columns
+speaking.data.01.03 <- speaking.data.01.03 %>% select(
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+str(speaking.data.01.03)
 
 ### checking for missing values
-is.na(speaking.data.01.01)
-which(is.na(speaking.data.01.01))
+is.na(speaking.data.01.03)
+which(is.na(speaking.data.01.03))
 
-### filter only speaking time of teacher and "kodiert von Anna" as row 
-speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
+### filter only speaking time of teacher as row 
+speaking.data.01.03 <- speaking.data.01.03 %>% filter (Code == "speaking time\\teachter")
+
+speaking.data.01.03 <- sum(speaking.data.01.03$Abdeckungsgrad..)
+
+# read in data for 01_04_novice_C
+speaking.data.01.04 <- read.delim("./data/Aperol_pilot_01_04_novice_C_cam1.txt", dec=",", sep="\t", header=T)
+
+view(speaking.data.01.04)
+
+### select relevant columns
+speaking.data.01.04 <- speaking.data.01.04 %>% select(
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+str(speaking.data.01.04)
+
+### checking for missing values
+is.na(speaking.data.01.04)
+which(is.na(speaking.data.01.04))
+
+### filter only speaking time of teacher as row 
+speaking.data.01.04 <- speaking.data.01.04 %>% filter (Code == "speaking time\\teachter")
+
+speaking.data.01.04 <- sum(speaking.data.01.04$Abdeckungsgrad..)
+
+# read in data for 02_01_novice_A
+speaking.data.02.01 <- read.delim("./data/Aperol_pilot_02_01_novice_A_glasses.txt", dec=",", sep="\t", header=T)
+
+view(speaking.data.02.01)
+
+### select relevant columns
+speaking.data.02.01 <- speaking.data.02.01 %>% select(
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+str(speaking.data.02.01)
+
+### checking for missing values
+is.na(speaking.data.02.01)
+which(is.na(speaking.data.02.01))
+
+### filter only speaking time of teacher as row 
+speaking.data.02.01 <- speaking.data.02.01 %>% filter (Code == "speaking time\\teacher")
+
+speaking.data.02.01 <- sum(speaking.data.02.01$Abdeckungsgrad..)
+
+# read in data for 02_02_novice_B
+speaking.data.02.02 <- read.delim("./data/Aperol_pilot_02_02_novice_B_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
+
+view(speaking.data.02.02)
+
+### select relevant columns
+speaking.data.02.02 <- speaking.data.02.02 %>% select(
+  Dokumentgruppe,
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+str(speaking.data.02.02)
+
+### checking for missing values
+is.na(speaking.data.02.02)
+which(is.na(speaking.data.02.02))
+
+### filter only speaking time of teacher as row 
+speaking.data.02.02 <- speaking.data.02.02 %>% filter (Code == "speaking time\\teacher",
                                                        Dokumentgruppe == "kodiert von Anna")
 
-speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)
+speaking.data.02.02 <- sum(speaking.data.02.02$Abdeckungsgrad..)
+
+# read in data for 02_03_novice_C
+speaking.data.02.03 <- read.delim("./data/Aperol_pilot_02_03_novice_C_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
+
+view(speaking.data.02.03)
+
+### select relevant columns
+speaking.data.02.03 <- speaking.data.02.03 %>% select(
+  Dokumentgruppe,
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+str(speaking.data.02.03)
+
+### checking for missing values
+is.na(speaking.data.02.03)
+which(is.na(speaking.data.02.03))
+
+### filter only speaking time of teacher as row 
+speaking.data.02.03 <- speaking.data.02.03 %>% filter (Code == "speaking time\\teachter",
+                                                       Dokumentgruppe == "02_03_kodiert von Anna")
+
+speaking.data.02.03 <- sum(speaking.data.02.03$Abdeckungsgrad..)
+
+# read in data for 02_04_novice_D
+speaking.data.02.04 <- read.delim("./data/Aperol_pilot_02_04_novice_D_cam1.txt", dec=",", sep="\t", header=T)
+
+view(speaking.data.02.04)
+
+### select relevant columns
+speaking.data.02.04 <- speaking.data.02.04 %>% select(
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+str(speaking.data.02.04)
+
+### checking for missing values
+is.na(speaking.data.02.04)
+which(is.na(speaking.data.02.04))
+
+### filter only speaking time of teacher as row 
+speaking.data.02.04 <- speaking.data.02.04 %>% filter (Code == "speaking time\\teachter")
+
+speaking.data.02.04 <- sum(speaking.data.02.04$Abdeckungsgrad..)
+
+# read in table with coded speaking time included
+speaking.data <- read.delim("./data/plus_coded_speaking_time_questionnaire_data_0802.txt", dec=",", sep="\t", header=T)
+
+# to compare both sessions filter only Identical items
+speaking.data <- speaking.data  %>% filter(str_detect(scale, 
+                                                 paste(c("Duration of speaking time"),
+                                                    collapse = '|')))
+
+view(speaking.data)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+speaking.data <- speaking.data %>%  mutate(value = as.numeric(value))
+
+speaking.plot <- speaking.data %>%
+  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
+    geom_boxplot() +
+    geom_jitter(color="black", size=0.4, alpha=0.9) +
+    theme_light() +
+    theme(
+      legend.position="none",
+      plot.title = element_text(size=11),
+      axis.text.x = element_text(size = 8)) +
+    facet_grid(group~perspective) +
+    ggtitle("Boxplot with individual points for Duration of speaking time") +
+    xlab("")
+speaking.plot
 

### 2021-02-09 paper_1/paper_1_supplement.Rmd
added excel table AOI long format

@@
 
-## Data collection
+## Procedure/ Data collection
+
+### Set up
+
+For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig.
+The subjects were divided into groups of four, so the study was conducted on two different sessions.
+All participants were asked to hold a 10-minute lesson.
+The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering questionnaires.
+
+One person from the group of 4 acted as a teacher, the other three subjects acted as the class.
+The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disruptions in the classroom (e.g.
+putting their heads on the table, chatting, looking at their mobile phones, etc.).
+
+The lesson disruptions were displayed as instructions during the lesson for all "students" but not the teacher.
+In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase.
+In addition, the order of the data collection was taken into account in the analyses and variance caused by order was controlled.
 
@@
 
-For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig.
-The subjects were divided into groups of four, so the study was conducted on two different sessions.
-All participants were asked to hold a 10-minute lesson.
-The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering the questionnaire.
-
-One person from the group of 4 acted as a teacher, the other three subjects acted as the class.
-The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disruptions in the classroom (e.g.
-putting their heads on the table, chatting, looking at their mobile phones, etc.).
-
-The lesson disruptions were displayed as instructions during the lesson for all "students" but not the teacher.
-In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase.
-In addition, the order of the data collection was taken into account in the analyses and variance caused by order was controlled.
-
-By using mobile eye-trackers, the gaze and behavior of the experts and novices was recorded during the lesson.
-In addition, the speech and sounds and voices were recorded with an audio recorder installed in the middle of the Lab.
+### Questionnaire data
+
+After each mini-lesson, the subjects answered items on the teaching quality using a validated questionnaire ((@helmke2014unterrichtsdiagnostik)) and scales on the teacher's presence behavior.
+An external observer also completed the questionnaire.
+In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire.
+
+### Behavioral data
+
+The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab.
 Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles.
@@
 
-The lessons recorded on video were coded in a post-hoc procedure with a coding software by previously trained raters.
-The statistical data have been analyzed by using the program RStudio [Link: https://rstudio.com/].
-
-## Measures
+### Eyetracking data
+
+A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants.
+The head unit is a measuring device with different sensitive sensors.
+A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
+Infrared light illuminators support the eye tracking sensors which record the eye orientation.
+The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
+The scene camera has a field of view of 90 deg.
+in 16:9 format (82 deg.
+horizontal and 52 deg.
+vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
+The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
+
+## Coding/ Data preparation/ Reliability
 
 ### Questionnaire Data
-*Describe how we collect questionnaire data (paper or online). Add some basic information about the structure of the questionnaire.*
 
@@
 The scales on the quality of teaching are a validated questionnaire (@helmke2014unterrichtsdiagnostik).
-Whereas the scales on the teacher's presence behaviour were derived from the research literature (@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen) and were used in the pilot for the first time.
+Whereas the scales on the teacher's presence behavior were derived from the research literature (@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen) and were used in the pilot for the first time.
 
@@
 
-### Eye-tracking equipment
-
-A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements.
-The head unit is a measuring device with different sensitive sensors.
-A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
-Infrared light illuminators support the eye tracking sensors which record the eye orientation.
-The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
-The scene camera has a field of view of 90 deg.
-in 16:9 format (82 deg.
-horizontal and 52 deg.
-vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
-The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
-
-The Tobii Pro Glasses 2 software allows for non-screen based recordings of a participants’ attention while moving in real-world settings.
+### Behavioral Data
+
+The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (@kuckartz2019analyzing). The following coding scheme was developed:
+
+First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher.
+The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.
+
+``` {r coded speaking time, echo = FALSE}
+### read in data for 01_01_expert_D
+speaking.data.01.01 <- read.delim("./data/Aperol_pilot_01_01_expert_D_cam4_AL_MK.txt", dec=",", sep="\t", header=T)
+
+### select relevant columns
+speaking.data.01.01 <- speaking.data.01.01  %>% select(
+  Dokumentgruppe,
+  Dokumentname,
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+str(speaking.data.01.01)
+
+### checking for missing values
+is.na(speaking.data.01.01)
+which(is.na(speaking.data.01.01))
+
+### filter only speaking time of teacher and "kodiert von Anna" as row 
+speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
+                                           Dokumentgruppe == "kodiert von Anna")
+
+speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)
+
+# read in data for 01_02_expert_A
+speaking.data.01.02 <- read.delim("./data/Aperol_pilot_01_02_expert_A_cam1_AL.txt", dec=",", sep="\t", header=T)
+
+view(speaking.data.01.02)
+
+### select relevant columns
+speaking.data.01.02 <- speaking.data.01.02 %>% select(
+  Dokumentname,
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+### checking for missing values
+is.na(speaking.data.01.02)
+which(is.na(speaking.data.01.02))
+
+### filter only speaking time of teacher as row 
+speaking.data.01.02 <- speaking.data.01.02 %>% filter (Code == "speaking time\\teacher")
+
+view(speaking.data.01.02)
+
+speaking.data.01.02 <- sum(speaking.data.01.02$Abdeckungsgrad..)
+
+# read in data for 01_03_novice_B
+speaking.data.01.03 <- read.delim("./data/Aperol_pilot_01_03_novice_B_cam1.txt", dec=",", sep="\t", header=T)
+
+view(speaking.data.01.03)
+
+### select relevant columns
+speaking.data.01.03 <- speaking.data.01.03 %>% select(
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+str(speaking.data.01.03)
+
+### checking for missing values
+is.na(speaking.data.01.03)
+which(is.na(speaking.data.01.03))
+
+### filter only speaking time of teacher as row 
+speaking.data.01.03 <- speaking.data.01.03 %>% filter (Code == "speaking time\\teachter")
+
+speaking.data.01.03 <- sum(speaking.data.01.03$Abdeckungsgrad..)
+
+# read in data for 01_04_novice_C
+speaking.data.01.04 <- read.delim("./data/Aperol_pilot_01_04_novice_C_cam1.txt", dec=",", sep="\t", header=T)
+
+view(speaking.data.01.04)
+
+### select relevant columns
+speaking.data.01.04 <- speaking.data.01.04 %>% select(
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+str(speaking.data.01.04)
+
+### checking for missing values
+is.na(speaking.data.01.04)
+which(is.na(speaking.data.01.04))
+
+### filter only speaking time of teacher as row 
+speaking.data.01.04 <- speaking.data.01.04 %>% filter (Code == "speaking time\\teachter")
+
+speaking.data.01.04 <- sum(speaking.data.01.04$Abdeckungsgrad..)
+
+# read in data for 02_01_novice_A
+speaking.data.02.01 <- read.delim("./data/Aperol_pilot_02_01_novice_A_glasses.txt", dec=",", sep="\t", header=T)
+
+view(speaking.data.02.01)
+
+### select relevant columns
+speaking.data.02.01 <- speaking.data.02.01 %>% select(
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+str(speaking.data.02.01)
+
+### checking for missing values
+is.na(speaking.data.02.01)
+which(is.na(speaking.data.02.01))
+
+### filter only speaking time of teacher as row 
+speaking.data.02.01 <- speaking.data.02.01 %>% filter (Code == "speaking time\\teacher")
+
+speaking.data.02.01 <- sum(speaking.data.02.01$Abdeckungsgrad..)
+
+# read in data for 02_02_novice_B
+speaking.data.02.02 <- read.delim("./data/Aperol_pilot_02_02_novice_B_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
+
+view(speaking.data.02.02)
+
+### select relevant columns
+speaking.data.02.02 <- speaking.data.02.02 %>% select(
+  Dokumentgruppe,
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+str(speaking.data.02.02)
+
+### checking for missing values
+is.na(speaking.data.02.02)
+which(is.na(speaking.data.02.02))
+
+### filter only speaking time of teacher as row 
+speaking.data.02.02 <- speaking.data.02.02 %>% filter (Code == "speaking time\\teacher",
+                                                       Dokumentgruppe == "kodiert von Anna")
+
+speaking.data.02.02 <- sum(speaking.data.02.02$Abdeckungsgrad..)
+
+# read in data for 02_03_novice_C
+speaking.data.02.03 <- read.delim("./data/Aperol_pilot_02_03_novice_C_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
+
+view(speaking.data.02.03)
+
+### select relevant columns
+speaking.data.02.03 <- speaking.data.02.03 %>% select(
+  Dokumentgruppe,
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+str(speaking.data.02.03)
+
+### checking for missing values
+is.na(speaking.data.02.03)
+which(is.na(speaking.data.02.03))
+
+### filter only speaking time of teacher as row 
+speaking.data.02.03 <- speaking.data.02.03 %>% filter (Code == "speaking time\\teachter",
+                                                       Dokumentgruppe == "02_03_kodiert von Anna")
+
+speaking.data.02.03 <- sum(speaking.data.02.03$Abdeckungsgrad..)
+
+# read in data for 02_04_novice_D
+speaking.data.02.04 <- read.delim("./data/Aperol_pilot_02_04_novice_D_cam1.txt", dec=",", sep="\t", header=T)
+
+view(speaking.data.02.04)
+
+### select relevant columns
+speaking.data.02.04 <- speaking.data.02.04 %>% select(
+  Code,
+  Anfang,
+  Ende,
+  Fläche,
+  Abdeckungsgrad..)
+
+str(speaking.data.02.04)
+
+### checking for missing values
+is.na(speaking.data.02.04)
+which(is.na(speaking.data.02.04))
+
+### filter only speaking time of teacher as row 
+speaking.data.02.04 <- speaking.data.02.04 %>% filter (Code == "speaking time\\teachter")
+
+speaking.data.02.04 <- sum(speaking.data.02.04$Abdeckungsgrad..)
+
+# read in table with coded speaking time included
+speaking.data <- read.delim("./data/plus_coded_speaking_time_questionnaire_data_0802.txt", dec=",", sep="\t", header=T)
+
+# to compare both sessions filter only Identical items
+speaking.data <- speaking.data  %>% filter(str_detect(scale, 
+                                                 paste(c("Duration of speaking time"),
+                                                    collapse = '|')))
+
+view(speaking.data)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+speaking.data <- speaking.data %>%  mutate(value = as.numeric(value))
+
+speaking.plot <- speaking.data %>%
+  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
+    geom_boxplot() +
+    geom_jitter(color="black", size=0.4, alpha=0.9) +
+    theme_light() +
+    theme(
+      legend.position="none",
+      plot.title = element_text(size=11),
+      axis.text.x = element_text(size = 8)) +
+    facet_grid(group~perspective) +
+    ggtitle("Boxplot with individual points for Duration of speaking time") +
+    xlab("")
+speaking.plot
+
+```
+
+### Eyetracking Data
+
+The Tobii Pro Lab 2 software was used to analyze the teachers' visual attetion during each mini-lesson.
+The software allows for non-screen based recordings of a participants’ attention while moving in real-world settings.
 The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video.
-In order to map multiple recordings to AOIs, it is necessary to import the eye-tracking recordings into the Tobii Pro Analyzer software.
-Also, it is necessary to create a reference image of the scene in which one wishes to plot the gaze data (i.e.
-snapshot).
-Once the snapshot is imported, the gaze recordings of multiple recordings can be mapped to the reference image and analyzed in aggregated form.
+In order to map multiple recordings to AOIs, we first imported the eye-tracking recordings into the Tobii Pro Analyzer software.
+Second, we created dynamic Areas of Interest (AOI) manually to plot the gaze data.
+Once the AOIs are created, the gaze recordings of multiple recordings can be mapped and analyzed in aggregated form.
 Tobii Pro does not allow to do AOI based analyses within Pro Lab.
-Also, the dependency on snapshot reference images makes this approach impractical when working in different settings, i.e.
-different classrooms with various participants.
-Finally, mapping gaze to people or any moving objects complicated the analyses further.
-
-### Eye-Tracking Data
+So we exported a tsv.
+file to do further analyses in the software R.
 
@@
 # prepare data (selected from questionnaire data)
-et.raw.data<-read.table("./data/Aperol_pilot_glasses_raw_fixation_saccades_metrics.tsv", dec=",", sep="\t", header=T)
+et.raw.data<-read.table("./data/Aperol_pilot_glasses_AOI.tsv", dec=",", sep="\t", header=T)
 
@@
 
-# calculate GRI
+# calculate the GRI
 
@@
             "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
+
 view(et.raw.table)
@@
 
-### Coding Data
-
-The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (@kuckartz2019analyzing). The following coding scheme was developed:
-
--
-
-First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher.
-The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.
-
-``` {r coded speaking time, echo = FALSE}
-### read in data for 01_01_expert_D
-speaking.data.01.01 <- read.delim("./data/Aperol_pilot_01_01_expert_D_cam4_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.01 <- speaking.data.01.01  %>% select(
-  Dokumentgruppe,
-  Dokumentname,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-str(speaking.data.01.01)
-
-### checking for missing values
-is.na(speaking.data.01.01)
-which(is.na(speaking.data.01.01))
-
-### filter only speaking time of teacher and "kodiert von Anna" as row 
-speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
-                                           Dokumentgruppe == "kodiert von Anna")
-
-speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)
-
-# read in data for 01_02_expert_A
-speaking.data.01.02 <- read.delim("./data/Aperol_pilot_01_02_expert_A_cam1_AL.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.01.02)
-
-### select relevant columns
-speaking.data.01.02 <- speaking.data.01.02 %>% select(
-  Dokumentname,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### checking for missing values
-is.na(speaking.data.01.02)
-which(is.na(speaking.data.01.02))
-
-### filter only speaking time of teacher as row 
-speaking.data.01.02 <- speaking.data.01.02 %>% filter (Code == "speaking time\\teacher")
-
-view(speaking.data.01.02)
-
-speaking.data.01.02 <- sum(speaking.data.01.02$Abdeckungsgrad..)
-
-# read in data for 01_03_novice_B
-speaking.data.01.03 <- read.delim("./data/Aperol_pilot_01_03_novice_B_cam1.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.01.03)
-
-### select relevant columns
-speaking.data.01.03 <- speaking.data.01.03 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-str(speaking.data.01.03)
-
-### checking for missing values
-is.na(speaking.data.01.03)
-which(is.na(speaking.data.01.03))
-
-### filter only speaking time of teacher as row 
-speaking.data.01.03 <- speaking.data.01.03 %>% filter (Code == "speaking time\\teachter")
-
-speaking.data.01.03 <- sum(speaking.data.01.03$Abdeckungsgrad..)
-
-# read in data for 01_04_novice_C
-speaking.data.01.04 <- read.delim("./data/Aperol_pilot_01_04_novice_C_cam1.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.01.04)
-
-### select relevant columns
-speaking.data.01.04 <- speaking.data.01.04 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-str(speaking.data.01.04)
-
-### checking for missing values
-is.na(speaking.data.01.04)
-which(is.na(speaking.data.01.04))
-
-### filter only speaking time of teacher as row 
-speaking.data.01.04 <- speaking.data.01.04 %>% filter (Code == "speaking time\\teachter")
-
-speaking.data.01.04 <- sum(speaking.data.01.04$Abdeckungsgrad..)
-
-# read in data for 02_01_novice_A
-speaking.data.02.01 <- read.delim("./data/Aperol_pilot_02_01_novice_A_glasses.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.02.01)
-
-### select relevant columns
-speaking.data.02.01 <- speaking.data.02.01 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-str(speaking.data.02.01)
-
-### checking for missing values
-is.na(speaking.data.02.01)
-which(is.na(speaking.data.02.01))
-
-### filter only speaking time of teacher as row 
-speaking.data.02.01 <- speaking.data.02.01 %>% filter (Code == "speaking time\\teacher")
-
-speaking.data.02.01 <- sum(speaking.data.02.01$Abdeckungsgrad..)
-
-# read in data for 02_02_novice_B
-speaking.data.02.02 <- read.delim("./data/Aperol_pilot_02_02_novice_B_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.02.02)
-
-### select relevant columns
-speaking.data.02.02 <- speaking.data.02.02 %>% select(
-  Dokumentgruppe,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-str(speaking.data.02.02)
-
-### checking for missing values
-is.na(speaking.data.02.02)
-which(is.na(speaking.data.02.02))
-
-### filter only speaking time of teacher as row 
-speaking.data.02.02 <- speaking.data.02.02 %>% filter (Code == "speaking time\\teacher",
-                                                       Dokumentgruppe == "kodiert von Anna")
-
-speaking.data.02.02 <- sum(speaking.data.02.02$Abdeckungsgrad..)
-
-# read in data for 02_03_novice_C
-speaking.data.02.03 <- read.delim("./data/Aperol_pilot_02_03_novice_C_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.02.03)
-
-### select relevant columns
-speaking.data.02.03 <- speaking.data.02.03 %>% select(
-  Dokumentgruppe,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-str(speaking.data.02.03)
-
-### checking for missing values
-is.na(speaking.data.02.03)
-which(is.na(speaking.data.02.03))
-
-### filter only speaking time of teacher as row 
-speaking.data.02.03 <- speaking.data.02.03 %>% filter (Code == "speaking time\\teachter",
-                                                       Dokumentgruppe == "02_03_kodiert von Anna")
-
-speaking.data.02.03 <- sum(speaking.data.02.03$Abdeckungsgrad..)
-
-# read in data for 02_04_novice_D
-speaking.data.02.04 <- read.delim("./data/Aperol_pilot_02_04_novice_D_cam1.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.02.04)
-
-### select relevant columns
-speaking.data.02.04 <- speaking.data.02.04 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-str(speaking.data.02.04)
-
-### checking for missing values
-is.na(speaking.data.02.04)
-which(is.na(speaking.data.02.04))
-
-### filter only speaking time of teacher as row 
-speaking.data.02.04 <- speaking.data.02.04 %>% filter (Code == "speaking time\\teachter")
-
-speaking.data.02.04 <- sum(speaking.data.02.04$Abdeckungsgrad..)
-
-# read in table with coded speaking time included
-speaking.data <- read.delim("./data/plus_coded_speaking_time_questionnaire_data_0802.txt", dec=",", sep="\t", header=T)
-
-# to compare both sessions filter only Identical items
-speaking.data <- speaking.data  %>% filter(str_detect(scale, 
-                                                 paste(c("Duration of speaking time"),
-                                                    collapse = '|')))
-
-view(speaking.data)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-speaking.data <- speaking.data %>%  mutate(value = as.numeric(value))
-
-speaking.plot <- speaking.data %>%
-  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
-    geom_boxplot() +
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    theme_light() +
-    theme(
-      legend.position="none",
-      plot.title = element_text(size=11),
-      axis.text.x = element_text(size = 8)) +
-    facet_grid(group~perspective) +
-    ggtitle("Boxplot with individual points for Duration of speaking time") +
-    xlab("")
-speaking.plot
-
-```
-
 ## Data analysis
@@
 
+### Questionnaire Data
+
+### Behavioral Data
+
+### Eyetracking Data
+
 # Results
-
-### Questionnaire Data
-*Start entering descriptives and plots here* Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 
@@
 
+### Questionnaire Data
+
+### Behavioral Data
+
+### Eyetracking Data
+
 # Discussion

### 2021-02-09 paper_1/paper_1_supplement.Rmd
update GRI

@@
 ```
-\newpage
-Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment.
-The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.
-
-```{r Duration speaking time, fig.width=5, fig.height = 5, echo = FALSE}
-# prepare data (selected from questionnaire data)
-quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)
-
-# knock out NAs
-quest.raw.data <- quest.raw.data  %>% filter(
-  personID != "NA")
-
-# to compare both sessions filter only Identical items
-quest.raw.data <- quest.raw.data  %>% filter(str_detect(scale, 
-                                                 paste(c("Duration of speaking time"),
-                                                    collapse = '|')))
-view(quest.raw.data)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
-
-quest.raw.data <- quest.raw.data %>% mutate (speaking.data)
-
-speaking.plot <- quest.raw.data %>%
-  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
-    geom_boxplot() +
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    theme_light() +
-    theme(
-      legend.position="none",
-      plot.title = element_text(size=11),
-      axis.text.x = element_text(size = 8)) +
-    facet_grid(group~perspective) +
-    ggtitle("Boxplot with individual points for Duration of speaking time") +
-    xlab("")
-speaking.plot
-
-```
+
 \newpage
@@
 # prepare data (selected from questionnaire data)
-et.raw.data<-read.table("./data/Aperol_pilot_glasses_AOI.tsv", dec=",", sep="\t", header=T)
+et.data<-read.table("./data/Aperol_pilot_glasses_AOI.txt", dec=",", sep="\t", header=T)
+
+view(et.data)
+str(et.data)
 
 # converting integer to numeric
-et.raw.data <- et.raw.data %>%  mutate(Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations))
+et.data <- et.data %>%  mutate(Number.of.fixations.in.AOI = as.numeric(Number.of.fixations.in.AOI))
 
@@
 # create a basic table (tibble) using tidyverse functions
-et.raw.table <- et.raw.data %>%
-  group_by(Participant, Variable) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Average Duration Fixation" = Average_duration_of_whole_fixations,
-            "SE Duration Fixation" = se(Total_duration_of_whole_fixations),
-            "TOI length" = TOI,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-
-view(et.raw.table)
+et.table <- et.data %>%
+  group_by(PersonID, Group) %>%
+  summarise("Fixation Number" = Number.of.fixations.in.AOI,
+            "Fixation Duration" = Total.duration.of.fixation.in.AOI..msec.,
+            "Average Duration Fixation" = Average.duration.of.fixation.in.AOI..msec.,
+            "SE Duration Fixation" = se(Total.duration.of.fixation.in.AOI..msec.),
+            "TOI" = Total.Time.of.Interest.Duration..msec.,
+            "GRI" = Average.duration.of.fixation.in.AOI..msec. / Number.of.fixations.in.AOI)
+
+view(et.table)
 
@@
 apa_table(
-  et.raw.table,
+  et.table,
   caption = "Number and Duration (in msec) of Fixations",
@@
 ```{r boxplot GRI, fig.width=6, fig.height = 8, echo = FALSE}
-
-et.plot <- et.raw.data %>%
-  ggplot(aes(x=Number_of_whole_fixations, y=value, fill=scale)) +
-    geom_boxplot() +
-    scale_x_discrete(guide = guide_axis(angle = 70)) +
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    theme_light() +
-    theme(
-      legend.position="none",
-      plot.title = element_text(size=11)
-    ) +
-    facet_grid(~Variable)+
-    ggtitle("Boxplot with individual points for Number of fixations") +
-    xlab("")
-et.plot
+# 
+# et.plot <- et.raw.data %>%
+#   ggplot(aes(x=Number_of_whole_fixations, y=value, fill=scale)) +
+#     geom_boxplot() +
+#     scale_x_discrete(guide = guide_axis(angle = 70)) +
+#     geom_jitter(color="black", size=0.4, alpha=0.9) +
+#     theme_light() +
+#     theme(
+#       legend.position="none",
+#       plot.title = element_text(size=11)
+#     ) +
+#     facet_grid(~Variable)+
+#     ggtitle("Boxplot with individual points for Number of fixations") +
+#     xlab("")
+# et.plot
 

### 2021-02-09 paper_1/paper_1_supplement.tex
update GRI

--- 2021-02-03 paper_1/paper_1_supplement.tex
@@
 
-\hypertarget{data-collection}{%
-\subsection{Data collection}\label{data-collection}}
-
-\begin{figure}
-
-{\centering \includegraphics{./pictures/datacollection}
-
-}
-
-\caption{Example for set up during a mini-lesson}\label{fig:datacollection}
-\end{figure}
+\hypertarget{procedure-data-collection}{%
+\subsection{Procedure/ Data collection}\label{procedure-data-collection}}
+
+\hypertarget{set-up}{%
+\subsubsection{Set up}\label{set-up}}
 
@@
 All participants were asked to hold a 10-minute lesson.
-The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering the questionnaire.
+The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering questionnaires.
 
@@
 
-By using mobile eye-trackers, the gaze and behavior of the experts and novices was recorded during the lesson.
-In addition, the speech and sounds and voices were recorded with an audio recorder installed in the middle of the Lab.
+\begin{figure}
+
+{\centering \includegraphics{./pictures/datacollection}
+
+}
+
+\caption{Example for set up during a mini-lesson}\label{fig:datacollection}
+\end{figure}
+
+\hypertarget{questionnaire-data}{%
+\subsubsection{Questionnaire data}\label{questionnaire-data}}
+
+After each mini-lesson, the subjects answered items on the teaching quality using a validated questionnaire ((Helmke et al.
+(2014))) and scales on the teacher's presence behavior.
+An external observer also completed the questionnaire.
+In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire.
+
+\hypertarget{behavioral-data}{%
+\subsubsection{Behavioral data}\label{behavioral-data}}
+
+The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab.
 Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles.
@@
 
-The lessons recorded on video were coded in a post-hoc procedure with a coding software by previously trained raters.
-The statistical data have been analyzed by using the program RStudio {[}Link: \url{https://rstudio.com/}{]}.
-
-\hypertarget{measures}{%
-\subsection{Measures}\label{measures}}
-
-\hypertarget{questionnaire-data}{%
-\subsubsection{Questionnaire Data}\label{questionnaire-data}}
-
-\emph{Describe how we collect questionnaire data (paper or online). Add some basic information about the structure of the questionnaire.}
+\hypertarget{eyetracking-data}{%
+\subsubsection{Eyetracking data}\label{eyetracking-data}}
+
+A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants.
+The head unit is a measuring device with different sensitive sensors.
+A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
+Infrared light illuminators support the eye tracking sensors which record the eye orientation.
+The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
+The scene camera has a field of view of 90 deg.
+in 16:9 format (82 deg.
+horizontal and 52 deg.
+vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
+The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
+
+\hypertarget{coding-data-preparation-reliability}{%
+\subsection{Coding/ Data preparation/ Reliability}\label{coding-data-preparation-reliability}}
+
+\hypertarget{questionnaire-data-1}{%
+\subsubsection{Questionnaire Data}\label{questionnaire-data-1}}
 
@@
 (2014)).
-Whereas the scales on the teacher's presence behaviour were derived from the research literature (Brophy (1986); Kiel, Frey, Weiß, and Weiss (2013); Kounin (2006); Marzano (2007); Nolting (2012)) and were used in the pilot for the first time.
+Whereas the scales on the teacher's presence behavior were derived from the research literature (Brophy (1986); Kiel, Frey, Weiß, and Weiss (2013); Kounin (2006); Marzano (2007); Nolting (2012)) and were used in the pilot for the first time.
 
@@
 \includegraphics{paper_1_supplement_files/figure-latex/boxplot scales-1.pdf}
+
 \newpage
-Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment.
-The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.
-
-\includegraphics{paper_1_supplement_files/figure-latex/Duration speaking time-1.pdf}
-\newpage
-
-\hypertarget{eye-tracking-equipment}{%
-\subsubsection{Eye-tracking equipment}\label{eye-tracking-equipment}}
-
-A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements.
-The head unit is a measuring device with different sensitive sensors.
-A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
-Infrared light illuminators support the eye tracking sensors which record the eye orientation.
-The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
-The scene camera has a field of view of 90 deg.
-in 16:9 format (82 deg.
-horizontal and 52 deg.
-vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
-The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
-
-The Tobii Pro Glasses 2 software allows for non-screen based recordings of a participants' attention while moving in real-world settings.
+
+\hypertarget{behavioral-data-1}{%
+\subsubsection{Behavioral Data}\label{behavioral-data-1}}
+
+The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz and Rädiker (2019)). The following coding scheme was developed:
+
+First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher.
+The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.
+
+\begin{verbatim}
+## 'data.frame':    325 obs. of  7 variables:
+##  $ Dokumentgruppe  : chr  "kodiert von Anna" "kodiert von Anna" "kodiert von Anna" "kodiert von Anna" ...
+##  $ Dokumentname    : chr  "Aperol_pilot_01_01_expert_D_cam4" "Aperol_pilot_01_01_expert_D_cam4" "Aperol_pilot_01_01_expert_D_cam4" "Aperol_pilot_01_01_expert_D_cam4" ...
+##  $ Code            : chr  "Phase\\lesson begin" "speaking time\\teacher" "speaking time\\teacher" "speaking time\\student" ...
+##  $ Anfang          : chr  "0:00:44,0" "0:00:44,3" "0:00:49,2" "0:00:51,0" ...
+##  $ Ende            : chr  "0:00:44,2" "0:00:47,2" "0:00:50,7" "0:00:52,7" ...
+##  $ Fläche          : chr  "00:00:00,2" "00:00:02,8" "00:00:01,4" "00:00:01,6" ...
+##  $ Abdeckungsgrad..: num  0.04 0.39 0.19 0.22 0.12 0.13 0.19 1.58 7.3 0.54 ...
+\end{verbatim}
+
+\begin{verbatim}
+##        Dokumentgruppe Dokumentname  Code Anfang  Ende Fläche Abdeckungsgrad..
+##   [1,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [2,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [3,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [4,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [5,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [6,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [7,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [8,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [9,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [10,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [11,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [12,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [13,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [14,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [15,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [16,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [17,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [18,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [19,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [20,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [21,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [22,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [23,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [24,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [25,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [26,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [27,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [28,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [29,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [30,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [31,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [32,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [33,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [34,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [35,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [36,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [37,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [38,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [39,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [40,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [41,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [42,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [43,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [44,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [45,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [46,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [47,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [48,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [49,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [50,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [51,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [52,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [53,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [54,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [55,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [56,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [57,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [58,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [59,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [60,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [61,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [62,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [63,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [64,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [65,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [66,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [67,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [68,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [69,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [70,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [71,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [72,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [73,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [74,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [75,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [76,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [77,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [78,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [79,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [80,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [81,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [82,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [83,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [84,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [85,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [86,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [87,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [88,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [89,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [90,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [91,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [92,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [93,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [94,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [95,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [96,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [97,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [98,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [99,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [100,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [101,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [102,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [103,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [104,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [105,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [106,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [107,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [108,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [109,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [110,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [111,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [112,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [113,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [114,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [115,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [116,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [117,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [118,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [119,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [120,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [121,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [122,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [123,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [124,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [125,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [126,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [127,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [128,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [129,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [130,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [131,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [132,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [133,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [134,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [135,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [136,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [137,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [138,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [139,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [140,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [141,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [142,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [143,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [144,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [145,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [146,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [147,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [148,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [149,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [150,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [151,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [152,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [153,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [154,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [155,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [156,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [157,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [158,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [159,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [160,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [161,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [162,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [163,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [164,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [165,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [166,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [167,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [168,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [169,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [170,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [171,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [172,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [173,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [174,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [175,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [176,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [177,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [178,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [179,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [180,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [181,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [182,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [183,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [184,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [185,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [186,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [187,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [188,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [189,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [190,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [191,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [192,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [193,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [194,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [195,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [196,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [197,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [198,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [199,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [200,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [201,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [202,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [203,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [204,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [205,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [206,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [207,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [208,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [209,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [210,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [211,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [212,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [213,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [214,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [215,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [216,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [217,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [218,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [219,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [220,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [221,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [222,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [223,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [224,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [225,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [226,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [227,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [228,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [229,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [230,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [231,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [232,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [233,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [234,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [235,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [236,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [237,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [238,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [239,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [240,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [241,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [242,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [243,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [244,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [245,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [246,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [247,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [248,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [249,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [250,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [251,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [252,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [253,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [254,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [255,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [256,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [257,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [258,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [259,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [260,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [261,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [262,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [263,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [264,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [265,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [266,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [267,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [268,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [269,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [270,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [271,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [272,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [273,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [274,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [275,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [276,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [277,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [278,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [279,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [280,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [281,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [282,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [283,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [284,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [285,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [286,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [287,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [288,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [289,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [290,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [291,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [292,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [293,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [294,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [295,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [296,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [297,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [298,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [299,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [300,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [301,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [302,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [303,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [304,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [305,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [306,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [307,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [308,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [309,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [310,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [311,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [312,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [313,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [314,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [315,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [316,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [317,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [318,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [319,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [320,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [321,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [322,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [323,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [324,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [325,]          FALSE        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+\end{verbatim}
+
+\begin{verbatim}
+## integer(0)
+\end{verbatim}
+
+\begin{verbatim}
+##        Dokumentname  Code Anfang  Ende Fläche Abdeckungsgrad..
+##   [1,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [2,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [3,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [4,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [5,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [6,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [7,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [8,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [9,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [10,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [11,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [12,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [13,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [14,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [15,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [16,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [17,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [18,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [19,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [20,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [21,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [22,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [23,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [24,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [25,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [26,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [27,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [28,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [29,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [30,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [31,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [32,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [33,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [34,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [35,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [36,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [37,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [38,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [39,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [40,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [41,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [42,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [43,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [44,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [45,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [46,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [47,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [48,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [49,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [50,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [51,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [52,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [53,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [54,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [55,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [56,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [57,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [58,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [59,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [60,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [61,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [62,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [63,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [64,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [65,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [66,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [67,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [68,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [69,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [70,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [71,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [72,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [73,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [74,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [75,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [76,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [77,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [78,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [79,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [80,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [81,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [82,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [83,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [84,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [85,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [86,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [87,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [88,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [89,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [90,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [91,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [92,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [93,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [94,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [95,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [96,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [97,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [98,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [99,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [100,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [101,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [102,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [103,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [104,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [105,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [106,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [107,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [108,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [109,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [110,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [111,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [112,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [113,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [114,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [115,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [116,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [117,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [118,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [119,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [120,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [121,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [122,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [123,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [124,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [125,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [126,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [127,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [128,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [129,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [130,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [131,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [132,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [133,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [134,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [135,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [136,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [137,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [138,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [139,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [140,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [141,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [142,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [143,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [144,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [145,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [146,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [147,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [148,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [149,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [150,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [151,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [152,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [153,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [154,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [155,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [156,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [157,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [158,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [159,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [160,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [161,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [162,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [163,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [164,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [165,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [166,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [167,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [168,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [169,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [170,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [171,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [172,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [173,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [174,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [175,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [176,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [177,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [178,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [179,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [180,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [181,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [182,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [183,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [184,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [185,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [186,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [187,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [188,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [189,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [190,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [191,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [192,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [193,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [194,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [195,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [196,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [197,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [198,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [199,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [200,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [201,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [202,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [203,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [204,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [205,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [206,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [207,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [208,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [209,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [210,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [211,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [212,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [213,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [214,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [215,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [216,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [217,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [218,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [219,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [220,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [221,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [222,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [223,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [224,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [225,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [226,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [227,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [228,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [229,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [230,]        FALSE FALSE  FALSE FALSE  FALSE            FALSE
+\end{verbatim}
+
+\begin{verbatim}
+## integer(0)
+\end{verbatim}
+
+\begin{verbatim}
+## 'data.frame':    179 obs. of  5 variables:
+##  $ Code            : chr  "Phase\\lesson begin" "speaking time\\teachter" "Phase\\teachers lecture" "Phase\\single" ...
+##  $ Anfang          : chr  "0:00:44,4" "0:00:44,4" "0:00:44,4" "0:01:20,8" ...
+##  $ Ende            : chr  "0:00:44,6" "0:01:20,7" "0:01:20,7" "0:01:51,7" ...
+##  $ Fläche          : chr  "00:00:00,1" "00:00:36,3" "00:00:36,3" "00:00:30,8" ...
+##  $ Abdeckungsgrad..: num  0.03 5.15 5.15 4.37 0.04 0.96 0.62 0.02 0.04 0.16 ...
+\end{verbatim}
+
+\begin{verbatim}
+##         Code Anfang  Ende Fläche Abdeckungsgrad..
+##   [1,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [2,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [3,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [4,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [5,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [6,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [7,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [8,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [9,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [10,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [11,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [12,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [13,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [14,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [15,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [16,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [17,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [18,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [19,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [20,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [21,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [22,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [23,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [24,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [25,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [26,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [27,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [28,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [29,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [30,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [31,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [32,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [33,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [34,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [35,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [36,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [37,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [38,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [39,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [40,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [41,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [42,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [43,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [44,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [45,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [46,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [47,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [48,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [49,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [50,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [51,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [52,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [53,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [54,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [55,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [56,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [57,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [58,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [59,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [60,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [61,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [62,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [63,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [64,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [65,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [66,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [67,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [68,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [69,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [70,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [71,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [72,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [73,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [74,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [75,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [76,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [77,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [78,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [79,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [80,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [81,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [82,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [83,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [84,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [85,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [86,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [87,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [88,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [89,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [90,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [91,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [92,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [93,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [94,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [95,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [96,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [97,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [98,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [99,] FALSE  FALSE FALSE  FALSE            FALSE
+## [100,] FALSE  FALSE FALSE  FALSE            FALSE
+## [101,] FALSE  FALSE FALSE  FALSE            FALSE
+## [102,] FALSE  FALSE FALSE  FALSE            FALSE
+## [103,] FALSE  FALSE FALSE  FALSE            FALSE
+## [104,] FALSE  FALSE FALSE  FALSE            FALSE
+## [105,] FALSE  FALSE FALSE  FALSE            FALSE
+## [106,] FALSE  FALSE FALSE  FALSE            FALSE
+## [107,] FALSE  FALSE FALSE  FALSE            FALSE
+## [108,] FALSE  FALSE FALSE  FALSE            FALSE
+## [109,] FALSE  FALSE FALSE  FALSE            FALSE
+## [110,] FALSE  FALSE FALSE  FALSE            FALSE
+## [111,] FALSE  FALSE FALSE  FALSE            FALSE
+## [112,] FALSE  FALSE FALSE  FALSE            FALSE
+## [113,] FALSE  FALSE FALSE  FALSE            FALSE
+## [114,] FALSE  FALSE FALSE  FALSE            FALSE
+## [115,] FALSE  FALSE FALSE  FALSE            FALSE
+## [116,] FALSE  FALSE FALSE  FALSE            FALSE
+## [117,] FALSE  FALSE FALSE  FALSE            FALSE
+## [118,] FALSE  FALSE FALSE  FALSE            FALSE
+## [119,] FALSE  FALSE FALSE  FALSE            FALSE
+## [120,] FALSE  FALSE FALSE  FALSE            FALSE
+## [121,] FALSE  FALSE FALSE  FALSE            FALSE
+## [122,] FALSE  FALSE FALSE  FALSE            FALSE
+## [123,] FALSE  FALSE FALSE  FALSE            FALSE
+## [124,] FALSE  FALSE FALSE  FALSE            FALSE
+## [125,] FALSE  FALSE FALSE  FALSE            FALSE
+## [126,] FALSE  FALSE FALSE  FALSE            FALSE
+## [127,] FALSE  FALSE FALSE  FALSE            FALSE
+## [128,] FALSE  FALSE FALSE  FALSE            FALSE
+## [129,] FALSE  FALSE FALSE  FALSE            FALSE
+## [130,] FALSE  FALSE FALSE  FALSE            FALSE
+## [131,] FALSE  FALSE FALSE  FALSE            FALSE
+## [132,] FALSE  FALSE FALSE  FALSE            FALSE
+## [133,] FALSE  FALSE FALSE  FALSE            FALSE
+## [134,] FALSE  FALSE FALSE  FALSE            FALSE
+## [135,] FALSE  FALSE FALSE  FALSE            FALSE
+## [136,] FALSE  FALSE FALSE  FALSE            FALSE
+## [137,] FALSE  FALSE FALSE  FALSE            FALSE
+## [138,] FALSE  FALSE FALSE  FALSE            FALSE
+## [139,] FALSE  FALSE FALSE  FALSE            FALSE
+## [140,] FALSE  FALSE FALSE  FALSE            FALSE
+## [141,] FALSE  FALSE FALSE  FALSE            FALSE
+## [142,] FALSE  FALSE FALSE  FALSE            FALSE
+## [143,] FALSE  FALSE FALSE  FALSE            FALSE
+## [144,] FALSE  FALSE FALSE  FALSE            FALSE
+## [145,] FALSE  FALSE FALSE  FALSE            FALSE
+## [146,] FALSE  FALSE FALSE  FALSE            FALSE
+## [147,] FALSE  FALSE FALSE  FALSE            FALSE
+## [148,] FALSE  FALSE FALSE  FALSE            FALSE
+## [149,] FALSE  FALSE FALSE  FALSE            FALSE
+## [150,] FALSE  FALSE FALSE  FALSE            FALSE
+## [151,] FALSE  FALSE FALSE  FALSE            FALSE
+## [152,] FALSE  FALSE FALSE  FALSE            FALSE
+## [153,] FALSE  FALSE FALSE  FALSE            FALSE
+## [154,] FALSE  FALSE FALSE  FALSE            FALSE
+## [155,] FALSE  FALSE FALSE  FALSE            FALSE
+## [156,] FALSE  FALSE FALSE  FALSE            FALSE
+## [157,] FALSE  FALSE FALSE  FALSE            FALSE
+## [158,] FALSE  FALSE FALSE  FALSE            FALSE
+## [159,] FALSE  FALSE FALSE  FALSE            FALSE
+## [160,] FALSE  FALSE FALSE  FALSE            FALSE
+## [161,] FALSE  FALSE FALSE  FALSE            FALSE
+## [162,] FALSE  FALSE FALSE  FALSE            FALSE
+## [163,] FALSE  FALSE FALSE  FALSE            FALSE
+## [164,] FALSE  FALSE FALSE  FALSE            FALSE
+## [165,] FALSE  FALSE FALSE  FALSE            FALSE
+## [166,] FALSE  FALSE FALSE  FALSE            FALSE
+## [167,] FALSE  FALSE FALSE  FALSE            FALSE
+## [168,] FALSE  FALSE FALSE  FALSE            FALSE
+## [169,] FALSE  FALSE FALSE  FALSE            FALSE
+## [170,] FALSE  FALSE FALSE  FALSE            FALSE
+## [171,] FALSE  FALSE FALSE  FALSE            FALSE
+## [172,] FALSE  FALSE FALSE  FALSE            FALSE
+## [173,] FALSE  FALSE FALSE  FALSE            FALSE
+## [174,] FALSE  FALSE FALSE  FALSE            FALSE
+## [175,] FALSE  FALSE FALSE  FALSE            FALSE
+## [176,] FALSE  FALSE FALSE  FALSE            FALSE
+## [177,] FALSE  FALSE FALSE  FALSE            FALSE
+## [178,] FALSE  FALSE FALSE  FALSE            FALSE
+## [179,] FALSE  FALSE FALSE  FALSE            FALSE
+\end{verbatim}
+
+\begin{verbatim}
+## integer(0)
+\end{verbatim}
+
+\begin{verbatim}
+## 'data.frame':    190 obs. of  5 variables:
+##  $ Code            : chr  "Phase\\lesson begin" "speaking time\\teachter" "speaking time\\student" "speaking time\\teachter" ...
+##  $ Anfang          : chr  "0:00:56,9" "0:00:56,9" "0:01:00,7" "0:01:01,8" ...
+##  $ Ende            : chr  "0:00:57,6" "0:01:01,0" "0:01:03,0" "0:01:03,0" ...
+##  $ Fläche          : chr  "00:00:00,6" "00:00:04,0" "00:00:02,3" "00:00:01,1" ...
+##  $ Abdeckungsgrad..: num  0.09 0.59 0.34 0.17 0.24 0.24 0.1 5.54 0.07 3.39 ...
+\end{verbatim}
+
+\begin{verbatim}
+##         Code Anfang  Ende Fläche Abdeckungsgrad..
+##   [1,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [2,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [3,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [4,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [5,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [6,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [7,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [8,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [9,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [10,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [11,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [12,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [13,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [14,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [15,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [16,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [17,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [18,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [19,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [20,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [21,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [22,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [23,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [24,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [25,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [26,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [27,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [28,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [29,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [30,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [31,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [32,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [33,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [34,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [35,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [36,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [37,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [38,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [39,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [40,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [41,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [42,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [43,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [44,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [45,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [46,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [47,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [48,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [49,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [50,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [51,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [52,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [53,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [54,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [55,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [56,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [57,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [58,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [59,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [60,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [61,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [62,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [63,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [64,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [65,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [66,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [67,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [68,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [69,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [70,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [71,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [72,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [73,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [74,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [75,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [76,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [77,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [78,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [79,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [80,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [81,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [82,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [83,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [84,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [85,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [86,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [87,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [88,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [89,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [90,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [91,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [92,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [93,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [94,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [95,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [96,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [97,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [98,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [99,] FALSE  FALSE FALSE  FALSE            FALSE
+## [100,] FALSE  FALSE FALSE  FALSE            FALSE
+## [101,] FALSE  FALSE FALSE  FALSE            FALSE
+## [102,] FALSE  FALSE FALSE  FALSE            FALSE
+## [103,] FALSE  FALSE FALSE  FALSE            FALSE
+## [104,] FALSE  FALSE FALSE  FALSE            FALSE
+## [105,] FALSE  FALSE FALSE  FALSE            FALSE
+## [106,] FALSE  FALSE FALSE  FALSE            FALSE
+## [107,] FALSE  FALSE FALSE  FALSE            FALSE
+## [108,] FALSE  FALSE FALSE  FALSE            FALSE
+## [109,] FALSE  FALSE FALSE  FALSE            FALSE
+## [110,] FALSE  FALSE FALSE  FALSE            FALSE
+## [111,] FALSE  FALSE FALSE  FALSE            FALSE
+## [112,] FALSE  FALSE FALSE  FALSE            FALSE
+## [113,] FALSE  FALSE FALSE  FALSE            FALSE
+## [114,] FALSE  FALSE FALSE  FALSE            FALSE
+## [115,] FALSE  FALSE FALSE  FALSE            FALSE
+## [116,] FALSE  FALSE FALSE  FALSE            FALSE
+## [117,] FALSE  FALSE FALSE  FALSE            FALSE
+## [118,] FALSE  FALSE FALSE  FALSE            FALSE
+## [119,] FALSE  FALSE FALSE  FALSE            FALSE
+## [120,] FALSE  FALSE FALSE  FALSE            FALSE
+## [121,] FALSE  FALSE FALSE  FALSE            FALSE
+## [122,] FALSE  FALSE FALSE  FALSE            FALSE
+## [123,] FALSE  FALSE FALSE  FALSE            FALSE
+## [124,] FALSE  FALSE FALSE  FALSE            FALSE
+## [125,] FALSE  FALSE FALSE  FALSE            FALSE
+## [126,] FALSE  FALSE FALSE  FALSE            FALSE
+## [127,] FALSE  FALSE FALSE  FALSE            FALSE
+## [128,] FALSE  FALSE FALSE  FALSE            FALSE
+## [129,] FALSE  FALSE FALSE  FALSE            FALSE
+## [130,] FALSE  FALSE FALSE  FALSE            FALSE
+## [131,] FALSE  FALSE FALSE  FALSE            FALSE
+## [132,] FALSE  FALSE FALSE  FALSE            FALSE
+## [133,] FALSE  FALSE FALSE  FALSE            FALSE
+## [134,] FALSE  FALSE FALSE  FALSE            FALSE
+## [135,] FALSE  FALSE FALSE  FALSE            FALSE
+## [136,] FALSE  FALSE FALSE  FALSE            FALSE
+## [137,] FALSE  FALSE FALSE  FALSE            FALSE
+## [138,] FALSE  FALSE FALSE  FALSE            FALSE
+## [139,] FALSE  FALSE FALSE  FALSE            FALSE
+## [140,] FALSE  FALSE FALSE  FALSE            FALSE
+## [141,] FALSE  FALSE FALSE  FALSE            FALSE
+## [142,] FALSE  FALSE FALSE  FALSE            FALSE
+## [143,] FALSE  FALSE FALSE  FALSE            FALSE
+## [144,] FALSE  FALSE FALSE  FALSE            FALSE
+## [145,] FALSE  FALSE FALSE  FALSE            FALSE
+## [146,] FALSE  FALSE FALSE  FALSE            FALSE
+## [147,] FALSE  FALSE FALSE  FALSE            FALSE
+## [148,] FALSE  FALSE FALSE  FALSE            FALSE
+## [149,] FALSE  FALSE FALSE  FALSE            FALSE
+## [150,] FALSE  FALSE FALSE  FALSE            FALSE
+## [151,] FALSE  FALSE FALSE  FALSE            FALSE
+## [152,] FALSE  FALSE FALSE  FALSE            FALSE
+## [153,] FALSE  FALSE FALSE  FALSE            FALSE
+## [154,] FALSE  FALSE FALSE  FALSE            FALSE
+## [155,] FALSE  FALSE FALSE  FALSE            FALSE
+## [156,] FALSE  FALSE FALSE  FALSE            FALSE
+## [157,] FALSE  FALSE FALSE  FALSE            FALSE
+## [158,] FALSE  FALSE FALSE  FALSE            FALSE
+## [159,] FALSE  FALSE FALSE  FALSE            FALSE
+## [160,] FALSE  FALSE FALSE  FALSE            FALSE
+## [161,] FALSE  FALSE FALSE  FALSE            FALSE
+## [162,] FALSE  FALSE FALSE  FALSE            FALSE
+## [163,] FALSE  FALSE FALSE  FALSE            FALSE
+## [164,] FALSE  FALSE FALSE  FALSE            FALSE
+## [165,] FALSE  FALSE FALSE  FALSE            FALSE
+## [166,] FALSE  FALSE FALSE  FALSE            FALSE
+## [167,] FALSE  FALSE FALSE  FALSE            FALSE
+## [168,] FALSE  FALSE FALSE  FALSE            FALSE
+## [169,] FALSE  FALSE FALSE  FALSE            FALSE
+## [170,] FALSE  FALSE FALSE  FALSE            FALSE
+## [171,] FALSE  FALSE FALSE  FALSE            FALSE
+## [172,] FALSE  FALSE FALSE  FALSE            FALSE
+## [173,] FALSE  FALSE FALSE  FALSE            FALSE
+## [174,] FALSE  FALSE FALSE  FALSE            FALSE
+## [175,] FALSE  FALSE FALSE  FALSE            FALSE
+## [176,] FALSE  FALSE FALSE  FALSE            FALSE
+## [177,] FALSE  FALSE FALSE  FALSE            FALSE
+## [178,] FALSE  FALSE FALSE  FALSE            FALSE
+## [179,] FALSE  FALSE FALSE  FALSE            FALSE
+## [180,] FALSE  FALSE FALSE  FALSE            FALSE
+## [181,] FALSE  FALSE FALSE  FALSE            FALSE
+## [182,] FALSE  FALSE FALSE  FALSE            FALSE
+## [183,] FALSE  FALSE FALSE  FALSE            FALSE
+## [184,] FALSE  FALSE FALSE  FALSE            FALSE
+## [185,] FALSE  FALSE FALSE  FALSE            FALSE
+## [186,] FALSE  FALSE FALSE  FALSE            FALSE
+## [187,] FALSE  FALSE FALSE  FALSE            FALSE
+## [188,] FALSE  FALSE FALSE  FALSE            FALSE
+## [189,] FALSE  FALSE FALSE  FALSE            FALSE
+## [190,] FALSE  FALSE FALSE  FALSE            FALSE
+\end{verbatim}
+
+\begin{verbatim}
+## integer(0)
+\end{verbatim}
+
+\begin{verbatim}
+## 'data.frame':    125 obs. of  5 variables:
+##  $ Code            : chr  "Phase\\lesson begin" "speaking time\\teacher" "speaking time\\student" "speaking time\\teacher" ...
+##  $ Anfang          : chr  "0:00:41,5" "0:00:41,8" "0:00:42,3" "0:00:45,9" ...
+##  $ Ende            : chr  "0:00:41,7" "0:00:42,3" "0:00:44,7" "0:00:47,6" ...
+##  $ Fläche          : chr  "00:00:00,2" "00:00:00,5" "00:00:02,3" "00:00:01,6" ...
+##  $ Abdeckungsgrad..: num  0.03 0.07 0.32 0.23 0.41 2.17 0.47 0.11 0.27 4.01 ...
+\end{verbatim}
+
+\begin{verbatim}
+##         Code Anfang  Ende Fläche Abdeckungsgrad..
+##   [1,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [2,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [3,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [4,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [5,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [6,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [7,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [8,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [9,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [10,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [11,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [12,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [13,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [14,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [15,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [16,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [17,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [18,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [19,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [20,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [21,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [22,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [23,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [24,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [25,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [26,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [27,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [28,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [29,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [30,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [31,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [32,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [33,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [34,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [35,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [36,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [37,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [38,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [39,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [40,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [41,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [42,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [43,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [44,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [45,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [46,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [47,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [48,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [49,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [50,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [51,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [52,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [53,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [54,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [55,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [56,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [57,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [58,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [59,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [60,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [61,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [62,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [63,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [64,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [65,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [66,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [67,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [68,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [69,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [70,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [71,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [72,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [73,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [74,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [75,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [76,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [77,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [78,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [79,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [80,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [81,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [82,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [83,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [84,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [85,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [86,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [87,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [88,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [89,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [90,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [91,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [92,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [93,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [94,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [95,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [96,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [97,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [98,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [99,] FALSE  FALSE FALSE  FALSE            FALSE
+## [100,] FALSE  FALSE FALSE  FALSE            FALSE
+## [101,] FALSE  FALSE FALSE  FALSE            FALSE
+## [102,] FALSE  FALSE FALSE  FALSE            FALSE
+## [103,] FALSE  FALSE FALSE  FALSE            FALSE
+## [104,] FALSE  FALSE FALSE  FALSE            FALSE
+## [105,] FALSE  FALSE FALSE  FALSE            FALSE
+## [106,] FALSE  FALSE FALSE  FALSE            FALSE
+## [107,] FALSE  FALSE FALSE  FALSE            FALSE
+## [108,] FALSE  FALSE FALSE  FALSE            FALSE
+## [109,] FALSE  FALSE FALSE  FALSE            FALSE
+## [110,] FALSE  FALSE FALSE  FALSE            FALSE
+## [111,] FALSE  FALSE FALSE  FALSE            FALSE
+## [112,] FALSE  FALSE FALSE  FALSE            FALSE
+## [113,] FALSE  FALSE FALSE  FALSE            FALSE
+## [114,] FALSE  FALSE FALSE  FALSE            FALSE
+## [115,] FALSE  FALSE FALSE  FALSE            FALSE
+## [116,] FALSE  FALSE FALSE  FALSE            FALSE
+## [117,] FALSE  FALSE FALSE  FALSE            FALSE
+## [118,] FALSE  FALSE FALSE  FALSE            FALSE
+## [119,] FALSE  FALSE FALSE  FALSE            FALSE
+## [120,] FALSE  FALSE FALSE  FALSE            FALSE
+## [121,] FALSE  FALSE FALSE  FALSE            FALSE
+## [122,] FALSE  FALSE FALSE  FALSE            FALSE
+## [123,] FALSE  FALSE FALSE  FALSE            FALSE
+## [124,] FALSE  FALSE FALSE  FALSE            FALSE
+## [125,] FALSE  FALSE FALSE  FALSE            FALSE
+\end{verbatim}
+
+\begin{verbatim}
+## integer(0)
+\end{verbatim}
+
+\begin{verbatim}
+## 'data.frame':    425 obs. of  6 variables:
+##  $ Dokumentgruppe  : chr  "kodiert von Anna" "kodiert von Anna" "kodiert von Anna" "kodiert von Anna" ...
+##  $ Code            : chr  "Phase\\lesson begin" "speaking time\\teacher" "speaking time\\teacher" "speaking time\\student" ...
+##  $ Anfang          : chr  "0:00:10,8" "0:00:10,9" "0:00:15,7" "0:00:19,2" ...
+##  $ Ende            : chr  "0:00:11,1" "0:00:14,8" "0:00:19,0" "0:00:20,7" ...
+##  $ Fläche          : chr  "00:00:00,2" "00:00:03,8" "00:00:03,3" "00:00:01,5" ...
+##  $ Abdeckungsgrad..: num  0.03 0.56 0.49 0.22 1.45 1.74 2.59 2.82 0.09 0.04 ...
+\end{verbatim}
+
+\begin{verbatim}
+##        Dokumentgruppe  Code Anfang  Ende Fläche Abdeckungsgrad..
+##   [1,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [2,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [3,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [4,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [5,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [6,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [7,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [8,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [9,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [10,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [11,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [12,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [13,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [14,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [15,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [16,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [17,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [18,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [19,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [20,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [21,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [22,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [23,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [24,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [25,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [26,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [27,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [28,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [29,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [30,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [31,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [32,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [33,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [34,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [35,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [36,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [37,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [38,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [39,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [40,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [41,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [42,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [43,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [44,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [45,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [46,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [47,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [48,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [49,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [50,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [51,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [52,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [53,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [54,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [55,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [56,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [57,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [58,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [59,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [60,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [61,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [62,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [63,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [64,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [65,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [66,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [67,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [68,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [69,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [70,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [71,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [72,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [73,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [74,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [75,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [76,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [77,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [78,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [79,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [80,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [81,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [82,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [83,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [84,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [85,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [86,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [87,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [88,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [89,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [90,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [91,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [92,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [93,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [94,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [95,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [96,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [97,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [98,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [99,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [100,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [101,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [102,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [103,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [104,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [105,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [106,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [107,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [108,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [109,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [110,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [111,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [112,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [113,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [114,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [115,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [116,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [117,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [118,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [119,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [120,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [121,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [122,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [123,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [124,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [125,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [126,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [127,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [128,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [129,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [130,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [131,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [132,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [133,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [134,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [135,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [136,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [137,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [138,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [139,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [140,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [141,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [142,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [143,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [144,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [145,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [146,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [147,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [148,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [149,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [150,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [151,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [152,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [153,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [154,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [155,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [156,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [157,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [158,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [159,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [160,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [161,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [162,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [163,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [164,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [165,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [166,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [167,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [168,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [169,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [170,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [171,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [172,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [173,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [174,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [175,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [176,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [177,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [178,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [179,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [180,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [181,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [182,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [183,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [184,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [185,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [186,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [187,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [188,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [189,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [190,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [191,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [192,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [193,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [194,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [195,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [196,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [197,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [198,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [199,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [200,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [201,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [202,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [203,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [204,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [205,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [206,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [207,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [208,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [209,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [210,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [211,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [212,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [213,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [214,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [215,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [216,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [217,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [218,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [219,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [220,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [221,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [222,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [223,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [224,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [225,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [226,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [227,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [228,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [229,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [230,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [231,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [232,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [233,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [234,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [235,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [236,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [237,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [238,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [239,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [240,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [241,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [242,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [243,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [244,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [245,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [246,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [247,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [248,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [249,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [250,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [251,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [252,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [253,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [254,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [255,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [256,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [257,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [258,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [259,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [260,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [261,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [262,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [263,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [264,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [265,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [266,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [267,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [268,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [269,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [270,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [271,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [272,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [273,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [274,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [275,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [276,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [277,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [278,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [279,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [280,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [281,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [282,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [283,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [284,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [285,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [286,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [287,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [288,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [289,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [290,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [291,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [292,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [293,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [294,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [295,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [296,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [297,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [298,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [299,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [300,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [301,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [302,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [303,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [304,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [305,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [306,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [307,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [308,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [309,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [310,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [311,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [312,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [313,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [314,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [315,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [316,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [317,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [318,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [319,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [320,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [321,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [322,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [323,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [324,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [325,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [326,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [327,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [328,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [329,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [330,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [331,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [332,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [333,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [334,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [335,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [336,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [337,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [338,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [339,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [340,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [341,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [342,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [343,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [344,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [345,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [346,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [347,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [348,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [349,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [350,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [351,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [352,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [353,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [354,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [355,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [356,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [357,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [358,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [359,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [360,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [361,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [362,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [363,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [364,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [365,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [366,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [367,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [368,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [369,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [370,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [371,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [372,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [373,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [374,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [375,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [376,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [377,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [378,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [379,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [380,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [381,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [382,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [383,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [384,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [385,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [386,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [387,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [388,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [389,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [390,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [391,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [392,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [393,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [394,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [395,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [396,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [397,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [398,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [399,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [400,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [401,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [402,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [403,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [404,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [405,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [406,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [407,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [408,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [409,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [410,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [411,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [412,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [413,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [414,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [415,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [416,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [417,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [418,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [419,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [420,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [421,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [422,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [423,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [424,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [425,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+\end{verbatim}
+
+\begin{verbatim}
+## integer(0)
+\end{verbatim}
+
+\begin{verbatim}
+## 'data.frame':    335 obs. of  6 variables:
+##  $ Dokumentgruppe  : chr  "02_03_kodiert von Mandy" "02_03_kodiert von Mandy" "02_03_kodiert von Mandy" "02_03_kodiert von Mandy" ...
+##  $ Code            : chr  "Phase\\lesson begin" "speaking time\\teachter" "Phase\\teachers lecture" "speaking time\\teachter" ...
+##  $ Anfang          : chr  "0:00:14,7" "0:00:15,0" "0:00:22,0" "0:00:22,1" ...
+##  $ Ende            : chr  "0:00:15,0" "0:00:20,7" "0:00:55,2" "0:00:28,0" ...
+##  $ Fläche          : chr  "00:00:00,3" "00:00:05,7" "00:00:33,2" "00:00:05,8" ...
+##  $ Abdeckungsgrad..: num  0.04 0.84 4.89 0.86 3.71 ...
+\end{verbatim}
+
+\begin{verbatim}
+##        Dokumentgruppe  Code Anfang  Ende Fläche Abdeckungsgrad..
+##   [1,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [2,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [3,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [4,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [5,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [6,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [7,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [8,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##   [9,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [10,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [11,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [12,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [13,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [14,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [15,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [16,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [17,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [18,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [19,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [20,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [21,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [22,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [23,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [24,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [25,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [26,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [27,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [28,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [29,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [30,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [31,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [32,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [33,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [34,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [35,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [36,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [37,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [38,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [39,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [40,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [41,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [42,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [43,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [44,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [45,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [46,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [47,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [48,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [49,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [50,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [51,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [52,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [53,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [54,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [55,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [56,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [57,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [58,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [59,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [60,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [61,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [62,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [63,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [64,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [65,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [66,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [67,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [68,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [69,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [70,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [71,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [72,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [73,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [74,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [75,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [76,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [77,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [78,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [79,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [80,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [81,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [82,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [83,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [84,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [85,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [86,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [87,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [88,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [89,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [90,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [91,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [92,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [93,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [94,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [95,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [96,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [97,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [98,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+##  [99,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [100,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [101,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [102,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [103,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [104,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [105,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [106,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [107,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [108,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [109,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [110,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [111,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [112,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [113,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [114,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [115,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [116,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [117,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [118,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [119,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [120,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [121,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [122,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [123,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [124,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [125,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [126,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [127,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [128,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [129,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [130,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [131,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [132,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [133,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [134,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [135,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [136,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [137,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [138,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [139,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [140,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [141,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [142,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [143,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [144,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [145,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [146,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [147,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [148,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [149,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [150,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [151,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [152,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [153,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [154,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [155,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [156,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [157,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [158,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [159,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [160,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [161,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [162,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [163,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [164,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [165,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [166,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [167,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [168,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [169,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [170,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [171,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [172,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [173,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [174,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [175,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [176,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [177,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [178,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [179,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [180,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [181,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [182,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [183,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [184,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [185,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [186,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [187,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [188,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [189,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [190,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [191,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [192,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [193,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [194,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [195,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [196,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [197,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [198,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [199,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [200,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [201,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [202,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [203,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [204,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [205,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [206,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [207,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [208,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [209,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [210,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [211,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [212,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [213,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [214,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [215,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [216,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [217,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [218,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [219,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [220,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [221,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [222,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [223,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [224,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [225,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [226,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [227,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [228,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [229,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [230,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [231,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [232,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [233,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [234,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [235,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [236,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [237,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [238,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [239,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [240,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [241,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [242,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [243,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [244,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [245,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [246,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [247,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [248,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [249,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [250,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [251,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [252,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [253,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [254,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [255,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [256,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [257,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [258,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [259,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [260,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [261,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [262,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [263,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [264,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [265,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [266,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [267,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [268,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [269,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [270,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [271,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [272,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [273,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [274,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [275,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [276,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [277,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [278,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [279,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [280,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [281,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [282,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [283,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [284,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [285,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [286,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [287,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [288,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [289,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [290,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [291,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [292,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [293,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [294,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [295,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [296,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [297,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [298,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [299,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [300,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [301,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [302,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [303,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [304,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [305,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [306,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [307,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [308,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [309,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [310,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [311,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [312,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [313,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [314,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [315,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [316,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [317,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [318,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [319,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [320,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [321,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [322,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [323,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [324,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [325,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [326,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [327,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [328,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [329,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [330,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [331,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [332,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [333,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [334,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+## [335,]          FALSE FALSE  FALSE FALSE  FALSE            FALSE
+\end{verbatim}
+
+\begin{verbatim}
+## integer(0)
+\end{verbatim}
+
+\begin{verbatim}
+## 'data.frame':    271 obs. of  5 variables:
+##  $ Code            : chr  "Phase\\lesson begin" "speaking time\\teachter" "speaking time\\student" "speaking time\\teachter" ...
+##  $ Anfang          : chr  "0:00:17,1" "0:00:17,1" "0:00:21,6" "0:00:24,6" ...
+##  $ Ende            : chr  "0:00:17,4" "0:00:19,9" "0:00:22,8" "0:00:25,5" ...
+##  $ Fläche          : chr  "00:00:00,2" "00:00:02,7" "00:00:01,1" "00:00:00,8" ...
+##  $ Abdeckungsgrad..: num  0.04 0.39 0.16 0.12 0.37 0.47 2.05 2.3 0.13 0.14 ...
+\end{verbatim}
+
+\begin{verbatim}
+##         Code Anfang  Ende Fläche Abdeckungsgrad..
+##   [1,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [2,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [3,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [4,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [5,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [6,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [7,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [8,] FALSE  FALSE FALSE  FALSE            FALSE
+##   [9,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [10,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [11,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [12,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [13,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [14,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [15,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [16,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [17,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [18,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [19,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [20,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [21,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [22,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [23,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [24,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [25,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [26,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [27,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [28,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [29,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [30,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [31,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [32,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [33,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [34,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [35,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [36,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [37,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [38,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [39,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [40,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [41,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [42,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [43,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [44,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [45,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [46,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [47,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [48,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [49,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [50,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [51,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [52,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [53,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [54,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [55,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [56,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [57,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [58,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [59,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [60,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [61,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [62,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [63,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [64,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [65,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [66,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [67,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [68,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [69,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [70,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [71,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [72,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [73,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [74,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [75,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [76,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [77,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [78,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [79,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [80,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [81,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [82,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [83,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [84,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [85,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [86,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [87,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [88,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [89,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [90,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [91,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [92,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [93,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [94,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [95,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [96,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [97,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [98,] FALSE  FALSE FALSE  FALSE            FALSE
+##  [99,] FALSE  FALSE FALSE  FALSE            FALSE
+## [100,] FALSE  FALSE FALSE  FALSE            FALSE
+## [101,] FALSE  FALSE FALSE  FALSE            FALSE
+## [102,] FALSE  FALSE FALSE  FALSE            FALSE
+## [103,] FALSE  FALSE FALSE  FALSE            FALSE
+## [104,] FALSE  FALSE FALSE  FALSE            FALSE
+## [105,] FALSE  FALSE FALSE  FALSE            FALSE
+## [106,] FALSE  FALSE FALSE  FALSE            FALSE
+## [107,] FALSE  FALSE FALSE  FALSE            FALSE
+## [108,] FALSE  FALSE FALSE  FALSE            FALSE
+## [109,] FALSE  FALSE FALSE  FALSE            FALSE
+## [110,] FALSE  FALSE FALSE  FALSE            FALSE
+## [111,] FALSE  FALSE FALSE  FALSE            FALSE
+## [112,] FALSE  FALSE FALSE  FALSE            FALSE
+## [113,] FALSE  FALSE FALSE  FALSE            FALSE
+## [114,] FALSE  FALSE FALSE  FALSE            FALSE
+## [115,] FALSE  FALSE FALSE  FALSE            FALSE
+## [116,] FALSE  FALSE FALSE  FALSE            FALSE
+## [117,] FALSE  FALSE FALSE  FALSE            FALSE
+## [118,] FALSE  FALSE FALSE  FALSE            FALSE
+## [119,] FALSE  FALSE FALSE  FALSE            FALSE
+## [120,] FALSE  FALSE FALSE  FALSE            FALSE
+## [121,] FALSE  FALSE FALSE  FALSE            FALSE
+## [122,] FALSE  FALSE FALSE  FALSE            FALSE
+## [123,] FALSE  FALSE FALSE  FALSE            FALSE
+## [124,] FALSE  FALSE FALSE  FALSE            FALSE
+## [125,] FALSE  FALSE FALSE  FALSE            FALSE
+## [126,] FALSE  FALSE FALSE  FALSE            FALSE
+## [127,] FALSE  FALSE FALSE  FALSE            FALSE
+## [128,] FALSE  FALSE FALSE  FALSE            FALSE
+## [129,] FALSE  FALSE FALSE  FALSE            FALSE
+## [130,] FALSE  FALSE FALSE  FALSE            FALSE
+## [131,] FALSE  FALSE FALSE  FALSE            FALSE
+## [132,] FALSE  FALSE FALSE  FALSE            FALSE
+## [133,] FALSE  FALSE FALSE  FALSE            FALSE
+## [134,] FALSE  FALSE FALSE  FALSE            FALSE
+## [135,] FALSE  FALSE FALSE  FALSE            FALSE
+## [136,] FALSE  FALSE FALSE  FALSE            FALSE
+## [137,] FALSE  FALSE FALSE  FALSE            FALSE
+## [138,] FALSE  FALSE FALSE  FALSE            FALSE
+## [139,] FALSE  FALSE FALSE  FALSE            FALSE
+## [140,] FALSE  FALSE FALSE  FALSE            FALSE
+## [141,] FALSE  FALSE FALSE  FALSE            FALSE
+## [142,] FALSE  FALSE FALSE  FALSE            FALSE
+## [143,] FALSE  FALSE FALSE  FALSE            FALSE
+## [144,] FALSE  FALSE FALSE  FALSE            FALSE
+## [145,] FALSE  FALSE FALSE  FALSE            FALSE
+## [146,] FALSE  FALSE FALSE  FALSE            FALSE
+## [147,] FALSE  FALSE FALSE  FALSE            FALSE
+## [148,] FALSE  FALSE FALSE  FALSE            FALSE
+## [149,] FALSE  FALSE FALSE  FALSE            FALSE
+## [150,] FALSE  FALSE FALSE  FALSE            FALSE
+## [151,] FALSE  FALSE FALSE  FALSE            FALSE
+## [152,] FALSE  FALSE FALSE  FALSE            FALSE
+## [153,] FALSE  FALSE FALSE  FALSE            FALSE
+## [154,] FALSE  FALSE FALSE  FALSE            FALSE
+## [155,] FALSE  FALSE FALSE  FALSE            FALSE
+## [156,] FALSE  FALSE FALSE  FALSE            FALSE
+## [157,] FALSE  FALSE FALSE  FALSE            FALSE
+## [158,] FALSE  FALSE FALSE  FALSE            FALSE
+## [159,] FALSE  FALSE FALSE  FALSE            FALSE
+## [160,] FALSE  FALSE FALSE  FALSE            FALSE
+## [161,] FALSE  FALSE FALSE  FALSE            FALSE
+## [162,] FALSE  FALSE FALSE  FALSE            FALSE
+## [163,] FALSE  FALSE FALSE  FALSE            FALSE
+## [164,] FALSE  FALSE FALSE  FALSE            FALSE
+## [165,] FALSE  FALSE FALSE  FALSE            FALSE
+## [166,] FALSE  FALSE FALSE  FALSE            FALSE
+## [167,] FALSE  FALSE FALSE  FALSE            FALSE
+## [168,] FALSE  FALSE FALSE  FALSE            FALSE
+## [169,] FALSE  FALSE FALSE  FALSE            FALSE
+## [170,] FALSE  FALSE FALSE  FALSE            FALSE
+## [171,] FALSE  FALSE FALSE  FALSE            FALSE
+## [172,] FALSE  FALSE FALSE  FALSE            FALSE
+## [173,] FALSE  FALSE FALSE  FALSE            FALSE
+## [174,] FALSE  FALSE FALSE  FALSE            FALSE
+## [175,] FALSE  FALSE FALSE  FALSE            FALSE
+## [176,] FALSE  FALSE FALSE  FALSE            FALSE
+## [177,] FALSE  FALSE FALSE  FALSE            FALSE
+## [178,] FALSE  FALSE FALSE  FALSE            FALSE
+## [179,] FALSE  FALSE FALSE  FALSE            FALSE
+## [180,] FALSE  FALSE FALSE  FALSE            FALSE
+## [181,] FALSE  FALSE FALSE  FALSE            FALSE
+## [182,] FALSE  FALSE FALSE  FALSE            FALSE
+## [183,] FALSE  FALSE FALSE  FALSE            FALSE
+## [184,] FALSE  FALSE FALSE  FALSE            FALSE
+## [185,] FALSE  FALSE FALSE  FALSE            FALSE
+## [186,] FALSE  FALSE FALSE  FALSE            FALSE
+## [187,] FALSE  FALSE FALSE  FALSE            FALSE
+## [188,] FALSE  FALSE FALSE  FALSE            FALSE
+## [189,] FALSE  FALSE FALSE  FALSE            FALSE
+## [190,] FALSE  FALSE FALSE  FALSE            FALSE
+## [191,] FALSE  FALSE FALSE  FALSE            FALSE
+## [192,] FALSE  FALSE FALSE  FALSE            FALSE
+## [193,] FALSE  FALSE FALSE  FALSE            FALSE
+## [194,] FALSE  FALSE FALSE  FALSE            FALSE
+## [195,] FALSE  FALSE FALSE  FALSE            FALSE
+## [196,] FALSE  FALSE FALSE  FALSE            FALSE
+## [197,] FALSE  FALSE FALSE  FALSE            FALSE
+## [198,] FALSE  FALSE FALSE  FALSE            FALSE
+## [199,] FALSE  FALSE FALSE  FALSE            FALSE
+## [200,] FALSE  FALSE FALSE  FALSE            FALSE
+## [201,] FALSE  FALSE FALSE  FALSE            FALSE
+## [202,] FALSE  FALSE FALSE  FALSE            FALSE
+## [203,] FALSE  FALSE FALSE  FALSE            FALSE
+## [204,] FALSE  FALSE FALSE  FALSE            FALSE
+## [205,] FALSE  FALSE FALSE  FALSE            FALSE
+## [206,] FALSE  FALSE FALSE  FALSE            FALSE
+## [207,] FALSE  FALSE FALSE  FALSE            FALSE
+## [208,] FALSE  FALSE FALSE  FALSE            FALSE
+## [209,] FALSE  FALSE FALSE  FALSE            FALSE
+## [210,] FALSE  FALSE FALSE  FALSE            FALSE
+## [211,] FALSE  FALSE FALSE  FALSE            FALSE
+## [212,] FALSE  FALSE FALSE  FALSE            FALSE
+## [213,] FALSE  FALSE FALSE  FALSE            FALSE
+## [214,] FALSE  FALSE FALSE  FALSE            FALSE
+## [215,] FALSE  FALSE FALSE  FALSE            FALSE
+## [216,] FALSE  FALSE FALSE  FALSE            FALSE
+## [217,] FALSE  FALSE FALSE  FALSE            FALSE
+## [218,] FALSE  FALSE FALSE  FALSE            FALSE
+## [219,] FALSE  FALSE FALSE  FALSE            FALSE
+## [220,] FALSE  FALSE FALSE  FALSE            FALSE
+## [221,] FALSE  FALSE FALSE  FALSE            FALSE
+## [222,] FALSE  FALSE FALSE  FALSE            FALSE
+## [223,] FALSE  FALSE FALSE  FALSE            FALSE
+## [224,] FALSE  FALSE FALSE  FALSE            FALSE
+## [225,] FALSE  FALSE FALSE  FALSE            FALSE
+## [226,] FALSE  FALSE FALSE  FALSE            FALSE
+## [227,] FALSE  FALSE FALSE  FALSE            FALSE
+## [228,] FALSE  FALSE FALSE  FALSE            FALSE
+## [229,] FALSE  FALSE FALSE  FALSE            FALSE
+## [230,] FALSE  FALSE FALSE  FALSE            FALSE
+## [231,] FALSE  FALSE FALSE  FALSE            FALSE
+## [232,] FALSE  FALSE FALSE  FALSE            FALSE
+## [233,] FALSE  FALSE FALSE  FALSE            FALSE
+## [234,] FALSE  FALSE FALSE  FALSE            FALSE
+## [235,] FALSE  FALSE FALSE  FALSE            FALSE
+## [236,] FALSE  FALSE FALSE  FALSE            FALSE
+## [237,] FALSE  FALSE FALSE  FALSE            FALSE
+## [238,] FALSE  FALSE FALSE  FALSE            FALSE
+## [239,] FALSE  FALSE FALSE  FALSE            FALSE
+## [240,] FALSE  FALSE FALSE  FALSE            FALSE
+## [241,] FALSE  FALSE FALSE  FALSE            FALSE
+## [242,] FALSE  FALSE FALSE  FALSE            FALSE
+## [243,] FALSE  FALSE FALSE  FALSE            FALSE
+## [244,] FALSE  FALSE FALSE  FALSE            FALSE
+## [245,] FALSE  FALSE FALSE  FALSE            FALSE
+## [246,] FALSE  FALSE FALSE  FALSE            FALSE
+## [247,] FALSE  FALSE FALSE  FALSE            FALSE
+## [248,] FALSE  FALSE FALSE  FALSE            FALSE
+## [249,] FALSE  FALSE FALSE  FALSE            FALSE
+## [250,] FALSE  FALSE FALSE  FALSE            FALSE
+## [251,] FALSE  FALSE FALSE  FALSE            FALSE
+## [252,] FALSE  FALSE FALSE  FALSE            FALSE
+## [253,] FALSE  FALSE FALSE  FALSE            FALSE
+## [254,] FALSE  FALSE FALSE  FALSE            FALSE
+## [255,] FALSE  FALSE FALSE  FALSE            FALSE
+## [256,] FALSE  FALSE FALSE  FALSE            FALSE
+## [257,] FALSE  FALSE FALSE  FALSE            FALSE
+## [258,] FALSE  FALSE FALSE  FALSE            FALSE
+## [259,] FALSE  FALSE FALSE  FALSE            FALSE
+## [260,] FALSE  FALSE FALSE  FALSE            FALSE
+## [261,] FALSE  FALSE FALSE  FALSE            FALSE
+## [262,] FALSE  FALSE FALSE  FALSE            FALSE
+## [263,] FALSE  FALSE FALSE  FALSE            FALSE
+## [264,] FALSE  FALSE FALSE  FALSE            FALSE
+## [265,] FALSE  FALSE FALSE  FALSE            FALSE
+## [266,] FALSE  FALSE FALSE  FALSE            FALSE
+## [267,] FALSE  FALSE FALSE  FALSE            FALSE
+## [268,] FALSE  FALSE FALSE  FALSE            FALSE
+## [269,] FALSE  FALSE FALSE  FALSE            FALSE
+## [270,] FALSE  FALSE FALSE  FALSE            FALSE
+## [271,] FALSE  FALSE FALSE  FALSE            FALSE
+\end{verbatim}
+
+\begin{verbatim}
+## integer(0)
+\end{verbatim}
+
+\includegraphics{paper_1_supplement_files/figure-latex/coded speaking time-1.pdf}
+
+\hypertarget{eyetracking-data-1}{%
+\subsubsection{Eyetracking Data}\label{eyetracking-data-1}}
+
+The Tobii Pro Lab 2 software was used to analyze the teachers' visual attetion during each mini-lesson.
+The software allows for non-screen based recordings of a participants' attention while moving in real-world settings.
 The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video.
-In order to map multiple recordings to AOIs, it is necessary to import the eye-tracking recordings into the Tobii Pro Analyzer software.
-Also, it is necessary to create a reference image of the scene in which one wishes to plot the gaze data (i.e.~snapshot).
-Once the snapshot is imported, the gaze recordings of multiple recordings can be mapped to the reference image and analyzed in aggregated form.
+In order to map multiple recordings to AOIs, we first imported the eye-tracking recordings into the Tobii Pro Analyzer software.
+Second, we created dynamic Areas of Interest (AOI) manually to plot the gaze data.
+Once the AOIs are created, the gaze recordings of multiple recordings can be mapped and analyzed in aggregated form.
 Tobii Pro does not allow to do AOI based analyses within Pro Lab.
-Also, the dependency on snapshot reference images makes this approach impractical when working in different settings, i.e.~different classrooms with various participants.
-Finally, mapping gaze to people or any moving objects complicated the analyses further.
-
-\hypertarget{eye-tracking-data}{%
-\subsubsection{Eye-Tracking Data}\label{eye-tracking-data}}
+So we exported a tsv.
+file to do further analyses in the software R.
 
@@
 
+\begin{verbatim}
+## 'data.frame':    80 obs. of  15 variables:
+##  $ ID                                        : int  1 2 3 4 5 6 7 8 9 10 ...
+##  $ Recording                                 : int  33 33 33 33 33 33 33 33 33 33 ...
+##  $ Label                                     : chr  "Aperol_pilot_01_04_novice_C_glasses" "Aperol_pilot_01_04_novice_C_glasses" "Aperol_pilot_01_04_novice_C_glasses" "Aperol_pilot_01_04_novice_C_glasses" ...
+##  $ Group                                     : chr  "novice" "novice" "novice" "novice" ...
+##  $ PersonID                                  : chr  "C" "C" "C" "C" ...
+##  $ Session                                   : int  1 1 1 1 1 1 1 1 1 1 ...
+##  $ Unit                                      : int  1 1 1 1 1 1 1 1 1 1 ...
+##  $ Type.of.disruption                        : chr  "chatting with neighbor" "yelling" "asking a question" "walking around" ...
+##  $ Total.duration.of.fixation.in.AOI..sec.   : num  5.89 9.5 5.74 6.62 0.92 ...
+##  $ Total.duration.of.fixation.in.AOI..msec.  : num  5889 9500 5745 6617 920 ...
+##  $ Average.duration.of.fixation.in.AOI..sec. : num  0.28 0.73 0.96 0.33 0.31 0.67 0.36 0.81 0.53 1.13 ...
+##  $ Average.duration.of.fixation.in.AOI..msec.: num  280 731 957 331 307 ...
+##  $ Number.of.fixations.in.AOI                : int  21 13 6 20 3 17 12 8 8 15 ...
+##  $ Total.Time.of.Interest.Duration..sec.     : num  724 724 724 724 724 ...
+##  $ Total.Time.of.Interest.Duration..msec.    : num  723922 723922 723922 723922 723922 ...
+\end{verbatim}
+
 \begin{table}[h]
@@
 
-\begin{tabular}{llll}
+\begin{tabular}{llllllll}
 \toprule
-M Fixation Number & \multicolumn{1}{c}{SE Fixation Number} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{SE Duration Fixation}\\
+PersonID & \multicolumn{1}{c}{Group} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{Average Duration Fixation} & \multicolumn{1}{c}{SE Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
 \midrule
-842.50 & 146.69 & 382,411.00 & 95,132.00\\
+A & expert & 14.00 & 6,980.81 & 498.63 & 1,034.60 & 838,025.59 & 35.62\\
+A & expert & 7.00 & 4,674.45 & 667.78 & 1,034.60 & 838,025.59 & 95.40\\
+A & expert & 15.00 & 4,217.56 & 281.17 & 1,034.60 & 838,025.59 & 18.74\\
+A & expert & 26.00 & 4,740.12 & 182.31 & 1,034.60 & 838,025.59 & 7.01\\
+A & expert & 26.00 & 7,275.66 & 279.83 & 1,034.60 & 838,025.59 & 10.76\\
+A & expert & 22.00 & 9,295.02 & 422.50 & 1,034.60 & 838,025.59 & 19.20\\
+A & expert & 19.00 & 7,155.72 & 376.62 & 1,034.60 & 838,025.59 & 19.82\\
+A & expert & 30.00 & 11,273.40 & 375.78 & 1,034.60 & 838,025.59 & 12.53\\
+A & expert & 25.00 & 5,387.20 & 215.49 & 1,034.60 & 838,025.59 & 8.62\\
+A & expert & 13.00 & 14,400.23 & 1,107.71 & 1,034.60 & 838,025.59 & 85.21\\
+A & novice & 9.00 & 1,499.18 & 166.58 & 1,144.21 & 729,762.37 & 18.51\\
+A & novice & 21.00 & 8,307.13 & 395.58 & 1,144.21 & 729,762.37 & 18.84\\
+A & novice & 1.00 & 159.91 & 159.91 & 1,144.21 & 729,762.37 & 159.91\\
+A & novice & 5.00 & 341.45 & 68.29 & 1,144.21 & 729,762.37 & 13.66\\
+A & novice & 38.00 & 7,131.35 & 187.67 & 1,144.21 & 729,762.37 & 4.94\\
+A & novice & 18.00 & 2,154.55 & 119.70 & 1,144.21 & 729,762.37 & 6.65\\
+A & novice & 8.00 & 1,363.86 & 170.48 & 1,144.21 & 729,762.37 & 21.31\\
+A & novice & 20.00 & 3,437.99 & 170.48 & 1,144.21 & 729,762.37 & 8.52\\
+A & novice & 9.00 & 1,174.07 & 130.45 & 1,144.21 & 729,762.37 & 14.49\\
+A & novice & 28.00 & 10,183.38 & 363.69 & 1,144.21 & 729,762.37 & 12.99\\
+B & novice & 16.00 & 11,435.47 & 714.72 & 1,235.77 & 744,444.49 & 44.67\\
+B & novice & 8.00 & 5,403.07 & 675.38 & 1,235.77 & 744,444.49 & 84.42\\
+B & novice & 9.00 & 7,182.87 & 798.10 & 1,235.77 & 744,444.49 & 88.68\\
+B & novice & 21.00 & 19,342.95 & 921.09 & 1,235.77 & 744,444.49 & 43.86\\
+B & novice & 21.00 & 20,068.02 & 955.62 & 1,235.77 & 744,444.49 & 45.51\\
+B & novice & 6.00 & 8,090.41 & 1,348.40 & 1,235.77 & 744,444.49 & 224.73\\
+B & novice & 10.00 & 5,353.29 & 535.33 & 1,235.77 & 744,444.49 & 53.53\\
+B & novice & 14.00 & 10,168.97 & 726.36 & 1,235.77 & 744,444.49 & 51.88\\
+B & novice & 36.00 & 19,857.95 & 551.61 & 1,235.77 & 744,444.49 & 15.32\\
+B & novice & 18.00 & 10,375.46 & 576.42 & 1,235.77 & 744,444.49 & 32.02\\
+B & novice & 11.00 & 3,859.60 & 350.87 & 1,235.77 & 730,565.01 & 31.90\\
+B & novice & 9.00 & 5,537.67 & 615.30 & 1,235.77 & 730,565.01 & 68.37\\
+B & novice & 7.00 & 4,593.66 & 656.24 & 1,235.77 & 730,565.01 & 93.75\\
+B & novice & 10.00 & 7,031.68 & 703.17 & 1,235.77 & 730,565.01 & 70.32\\
+B & novice & 9.00 & 3,477.94 & 386.44 & 1,235.77 & 730,565.01 & 42.94\\
+B & novice & 18.00 & 8,328.93 & 462.72 & 1,235.77 & 730,565.01 & 25.71\\
+B & novice & 9.00 & 3,269.13 & 363.24 & 1,235.77 & 730,565.01 & 40.36\\
+B & novice & 25.00 & 5,227.18 & 209.09 & 1,235.77 & 730,565.01 & 8.36\\
+B & novice & 4.00 & 2,418.56 & 604.64 & 1,235.77 & 730,565.01 & 151.16\\
+B & novice & 13.00 & 12,524.66 & 963.44 & 1,235.77 & 730,565.01 & 74.11\\
+C & novice & 21.00 & 5,889.47 & 280.45 & 963.62 & 723,922.27 & 13.35\\
+C & novice & 13.00 & 9,500.22 & 730.79 & 963.62 & 723,922.27 & 56.21\\
+C & novice & 6.00 & 5,744.89 & 957.48 & 963.62 & 723,922.27 & 159.58\\
+C & novice & 20.00 & 6,616.62 & 330.83 & 963.62 & 723,922.27 & 16.54\\
+C & novice & 3.00 & 919.80 & 306.60 & 963.62 & 723,922.27 & 102.20\\
+C & novice & 17.00 & 11,339.68 & 667.04 & 963.62 & 723,922.27 & 39.24\\
+C & novice & 12.00 & 4,280.81 & 356.73 & 963.62 & 723,922.27 & 29.73\\
+C & novice & 8.00 & 6,456.24 & 807.03 & 963.62 & 723,922.27 & 100.88\\
+C & novice & 8.00 & 4,277.53 & 534.69 & 963.62 & 723,922.27 & 66.84\\
+C & novice & 15.00 & 16,953.86 & 1,130.26 & 963.62 & 723,922.27 & 75.35\\
+C & novice & 10.00 & 7,867.69 & 786.77 & 963.62 & 737,604.07 & 78.68\\
+C & novice & 15.00 & 13,418.17 & 894.55 & 963.62 & 737,604.07 & 59.64\\
+C & novice & 5.00 & 4,717.15 & 943.43 & 963.62 & 737,604.07 & 188.69\\
+C & novice & 11.00 & 5,617.35 & 510.67 & 963.62 & 737,604.07 & 46.42\\
+C & novice & 8.00 & 3,698.21 & 462.28 & 963.62 & 737,604.07 & 57.78\\
+C & novice & 25.00 & 9,921.86 & 396.88 & 963.62 & 737,604.07 & 15.88\\
+C & novice & 10.00 & 2,648.60 & 264.86 & 963.62 & 737,604.07 & 26.49\\
+C & novice & 13.00 & 4,392.88 & 337.91 & 963.62 & 737,604.07 & 25.99\\
+C & novice & 27.00 & 9,751.48 & 361.17 & 963.62 & 737,604.07 & 13.38\\
+C & novice & 19.00 & 15,753.36 & 829.12 & 963.62 & 737,604.07 & 43.64\\
+D & expert & 6.00 & 4,235.49 & 705.91 & 1,971.55 & 781,978.04 & 117.65\\
+D & expert & 7.00 & 2,978.23 & 425.46 & 1,971.55 & 781,978.04 & 60.78\\
+D & expert & 3.00 & 1,443.21 & 481.07 & 1,971.55 & 781,978.04 & 160.36\\
+D & expert & 35.00 & 20,863.43 & 596.10 & 1,971.55 & 781,978.04 & 17.03\\
+D & expert & 10.00 & 5,475.55 & 547.56 & 1,971.55 & 781,978.04 & 54.76\\
+D & expert & 6.00 & 3,468.42 & 578.07 & 1,971.55 & 781,978.04 & 96.35\\
+D & expert & 7.00 & 4,622.55 & 660.36 & 1,971.55 & 781,978.04 & 94.34\\
+D & expert & 10.00 & 4,976.97 & 497.70 & 1,971.55 & 781,978.04 & 49.77\\
+D & expert & 15.00 & 7,805.47 & 520.36 & 1,971.55 & 781,978.04 & 34.69\\
+D & expert & 10.00 & 15,834.07 & 1,583.41 & 1,971.55 & 781,978.04 & 158.34\\
+D & novice & 5.00 & 18,600.29 & 1,959.01 & 2,291.16 & 747,729.29 & 391.80\\
+D & novice & 9.00 & 469.84 & 1,953.66 & 2,291.16 & 747,729.29 & 217.07\\
+D & novice & 3.00 & 8,822.52 & 179.90 & 2,291.16 & 747,729.29 & 59.97\\
+D & novice & 9.00 & 3,957.60 & 582.63 & 2,291.16 & 747,729.29 & 64.74\\
+D & novice & 7.00 & 219.85 & 2,318.57 & 2,291.16 & 747,729.29 & 331.22\\
+D & novice & 1.00 & 16,229.98 & 219.85 & 2,291.16 & 747,729.29 & 219.85\\
+D & novice & 2.00 & 5,243.62 & 1,978.80 & 2,291.16 & 747,729.29 & 989.40\\
+D & novice & 12.00 & 539.70 & 735.21 & 2,291.16 & 747,729.29 & 61.27\\
+D & novice & 2.00 & 17,582.95 & 234.92 & 2,291.16 & 747,729.29 & 117.46\\
+D & novice & 14.00 & 9,795.03 & 1,328.59 & 2,291.16 & 747,729.29 & 94.90\\
 \bottomrule
@@
 \end{table}
-
-\hypertarget{coding-data}{%
-\subsubsection{Coding Data}\label{coding-data}}
-
-The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz and Rädiker (2019)). Therefore, a coding scheme was
 
@@
 
+\hypertarget{questionnaire-data-2}{%
+\subsubsection{Questionnaire Data}\label{questionnaire-data-2}}
+
+\hypertarget{behavioral-data-2}{%
+\subsubsection{Behavioral Data}\label{behavioral-data-2}}
+
+\hypertarget{eyetracking-data-2}{%
+\subsubsection{Eyetracking Data}\label{eyetracking-data-2}}
+
 \hypertarget{results}{%
 \section{Results}\label{results}}
-
-\hypertarget{questionnaire-data-1}{%
-\subsubsection{Questionnaire Data}\label{questionnaire-data-1}}
-
-\emph{Start entering descriptives and plots here} Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 
@@
 Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+
+\hypertarget{questionnaire-data-3}{%
+\subsubsection{Questionnaire Data}\label{questionnaire-data-3}}
+
+\hypertarget{behavioral-data-3}{%
+\subsubsection{Behavioral Data}\label{behavioral-data-3}}
+
+\hypertarget{eyetracking-data-3}{%
+\subsubsection{Eyetracking Data}\label{eyetracking-data-3}}
 

### 2021-02-10 paper_1/paper_1_supplement.Rmd
GRI table

@@
   - id            : "1"
-    institution   : "University of Leipzig"
+    institution   : "Leipzig University"
   - id            : "2"
-    institution   : "MPI for Evolutionary Anthropology, Leipzig"
+    institution   : "Max-Planck University for Evolutionary Anthropology"
 
 authornote: |
-  The study was carried out with the permission of the Ethics Committee of the University of Leipzig.
+  The Ethics Advisory Board of Leipzig University has dealt with the research project and has come to the conclusion that there are no objections to the implementation of this research project.
+The Ethics Advisory Board points out that the scientific and ethical responsibilty for the implementation of the project remains with the project director.
 
@@
 
-The table at the end of the manuscript provides an overview over the mean, the range and standard deviation of all scales.
+The table provides an overview over the mean, the range and standard deviation of all scales.
 
@@
 
+- phase - lesson begin, state event: teacher starts the lesson with a noise, talk, taking a position in class
+- phase - lesson end,	state event: teacher finishes the lesson with a noise, talk, taking a position in class
+- phase - organization/transition points, state event: any situation that does not imply effective learning time (fetching chalk, working material, organizing desks, opening windows, printing work results etc.)
+- phase - single,	state event: any individual student activity on a given task (reading, writing, drawing etc.)
+- phase - group, state event: any student activity on a given task together in a group of at least 3 students (reading, writing, drawing etc.)
+- phase - class discussion, state event: discussion in class, teacher talks to class/individual/group
+- phase - pair: state event: any student activity on a given task together in a team of 2 students (reading, writing, drawing etc.)
+- phase - teachers lecture, state event: any teacher's presentation on a certain topic which maybe supported by a PPP, PREZI, notes on board, OHP etc.
+- phase - other, state event: not categorizable
+- phase - break, state event: e.g. drinking, relaxation exercises
+- phase - external interruption, state event: external interruptions (e.g. fire alarm, technical problems, other teachers coming into the room)
+
+- speaking time - teacher, state event
+- speaking time - students, state event
+
+- disruption - chatting with neighbor, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+- disruption - asking a question, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+- disruption - yelling, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+- disruption - looking at phone, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+- disruption - staring out of window, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+- disruption - drawing, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+- disruption - head on table, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+- disruption - clicking pen, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+- disruption - drumming hands, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+- disruption - walking around, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+
 First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher.
@@
 
-``` {r coded speaking time, echo = FALSE}
+```{r coded speaking time, echo = FALSE}
 ### read in data for 01_01_expert_D
@@
 
-str(speaking.data.01.01)
-
-### checking for missing values
-is.na(speaking.data.01.01)
-which(is.na(speaking.data.01.01))
-
 ### filter only speaking time of teacher and "kodiert von Anna" as row 
@@
                                            Dokumentgruppe == "kodiert von Anna")
-
 speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)
@@
 speaking.data.01.02 <- read.delim("./data/Aperol_pilot_01_02_expert_A_cam1_AL.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.01.02)
 
@@
 
-### checking for missing values
-is.na(speaking.data.01.02)
-which(is.na(speaking.data.01.02))
-
 ### filter only speaking time of teacher as row 
 speaking.data.01.02 <- speaking.data.01.02 %>% filter (Code == "speaking time\\teacher")
-
-view(speaking.data.01.02)
-
 speaking.data.01.02 <- sum(speaking.data.01.02$Abdeckungsgrad..)
@@
 speaking.data.01.03 <- read.delim("./data/Aperol_pilot_01_03_novice_B_cam1.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.01.03)
 
@@
 
-str(speaking.data.01.03)
-
-### checking for missing values
-is.na(speaking.data.01.03)
-which(is.na(speaking.data.01.03))
-
 ### filter only speaking time of teacher as row 
 speaking.data.01.03 <- speaking.data.01.03 %>% filter (Code == "speaking time\\teachter")
-
 speaking.data.01.03 <- sum(speaking.data.01.03$Abdeckungsgrad..)
@@
 speaking.data.01.04 <- read.delim("./data/Aperol_pilot_01_04_novice_C_cam1.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.01.04)
 
@@
 
-str(speaking.data.01.04)
-
-### checking for missing values
-is.na(speaking.data.01.04)
-which(is.na(speaking.data.01.04))
-
 ### filter only speaking time of teacher as row 
@@
 speaking.data.02.01 <- read.delim("./data/Aperol_pilot_02_01_novice_A_glasses.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.02.01)
 
@@
 
-str(speaking.data.02.01)
-
-### checking for missing values
-is.na(speaking.data.02.01)
-which(is.na(speaking.data.02.01))
-
 ### filter only speaking time of teacher as row 
 speaking.data.02.01 <- speaking.data.02.01 %>% filter (Code == "speaking time\\teacher")
-
 speaking.data.02.01 <- sum(speaking.data.02.01$Abdeckungsgrad..)
@@
 speaking.data.02.02 <- read.delim("./data/Aperol_pilot_02_02_novice_B_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.02.02)
 
@@
 
-str(speaking.data.02.02)
-
-### checking for missing values
-is.na(speaking.data.02.02)
-which(is.na(speaking.data.02.02))
-
 ### filter only speaking time of teacher as row 
@@
                                                        Dokumentgruppe == "kodiert von Anna")
-
 speaking.data.02.02 <- sum(speaking.data.02.02$Abdeckungsgrad..)
@@
 speaking.data.02.03 <- read.delim("./data/Aperol_pilot_02_03_novice_C_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.02.03)
 
@@
 
-str(speaking.data.02.03)
-
-### checking for missing values
-is.na(speaking.data.02.03)
-which(is.na(speaking.data.02.03))
-
 ### filter only speaking time of teacher as row 
@@
                                                        Dokumentgruppe == "02_03_kodiert von Anna")
-
 speaking.data.02.03 <- sum(speaking.data.02.03$Abdeckungsgrad..)
@@
 speaking.data.02.04 <- read.delim("./data/Aperol_pilot_02_04_novice_D_cam1.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.02.04)
 
@@
 
-str(speaking.data.02.04)
-
-### checking for missing values
-is.na(speaking.data.02.04)
-which(is.na(speaking.data.02.04))
-
 ### filter only speaking time of teacher as row 
 speaking.data.02.04 <- speaking.data.02.04 %>% filter (Code == "speaking time\\teachter")
+speaking.data.02.04 <- sum(speaking.data.02.04$Abdeckungsgrad..)
 
-speaking.data.02.04 <- sum(speaking.data.02.04$Abdeckungsgrad..)
+```
+
+```{r speaking plot, echo=FALSE}
 
@@
                                                     collapse = '|')))
-
-view(speaking.data)
 
@@
 # prepare data (selected from questionnaire data)
-et.data<-read.table("./data/Aperol_pilot_glasses_AOI.txt", dec=",", sep="\t", header=T)
-
-view(et.data)
-str(et.data)
+et.raw.data<-read.table("./data/Aperol_pilot_glasses_raw_fixation_saccades_metrics.tsv", dec=",", sep="\t", header=T)
 
 # converting integer to numeric
-et.data <- et.data %>%  mutate(Number.of.fixations.in.AOI = as.numeric(Number.of.fixations.in.AOI))
+et.raw.data <- et.raw.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
+                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
+                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
+                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
+                                       )
 
 # calculate the GRI 
-
 # create a basic table (tibble) using tidyverse functions
-et.table <- et.data %>%
-  group_by(PersonID, Group) %>%
-  summarise("Fixation Number" = Number.of.fixations.in.AOI,
-            "Fixation Duration" = Total.duration.of.fixation.in.AOI..msec.,
-            "Average Duration Fixation" = Average.duration.of.fixation.in.AOI..msec.,
-            "SE Duration Fixation" = se(Total.duration.of.fixation.in.AOI..msec.),
-            "TOI" = Total.Time.of.Interest.Duration..msec.,
-            "GRI" = Average.duration.of.fixation.in.AOI..msec. / Number.of.fixations.in.AOI)
-
-view(et.table)
+et.raw.table <- et.raw.data %>%
+  group_by(Participant, Variable) %>%
+  summarise("Fixation Number" = Number_of_whole_fixations,
+            "Fixation Duration" = Total_duration_of_whole_fixations,
+            "M Duration Fixation" = Average_duration_of_whole_fixations,
+            "TOI" = Duration_of_interval,
+            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
 
@@
 apa_table(
-  et.table,
+  et.raw.table,
   caption = "Number and Duration (in msec) of Fixations",
@@
   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
   )

### 2021-02-10 paper_1/paper_1_supplement.tex
GRI table

--- 2021-02-04 paper_1/paper_1_supplement.tex
@@
 
-The study was carried out with the permission of the Ethics Committee of the University of Leipzig.
+The Ethics Advisory Board of Leipzig University has dealt with the research project and has come to the conclusion that there are no objections to the implementation of this research project.
+The Ethics Advisory Board points out that the scientific and ethical responsibilty for the implementation of the project remains with the project director.
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Leipzig\\\textsuperscript{2} MPI for Evolutionary Anthropology, Leipzig}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Leipzig University\\\textsuperscript{2} Max-Planck University for Evolutionary Anthropology}
 
@@
 
-\hypertarget{data-collection}{%
-\subsection{Data collection}\label{data-collection}}
+\hypertarget{procedure-data-collection}{%
+\subsection{Procedure/ Data collection}\label{procedure-data-collection}}
+
+\hypertarget{set-up}{%
+\subsubsection{Set up}\label{set-up}}
+
+For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig.
+The subjects were divided into groups of four, so the study was conducted on two different sessions.
+All participants were asked to hold a 10-minute lesson.
+The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering questionnaires.
+
+One person from the group of 4 acted as a teacher, the other three subjects acted as the class.
+The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disruptions in the classroom (e.g.~putting their heads on the table, chatting, looking at their mobile phones, etc.).
+
+The lesson disruptions were displayed as instructions during the lesson for all ``students'' but not the teacher.
+In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase.
+In addition, the order of the data collection was taken into account in the analyses and variance caused by order was controlled.
 
@@
 
-For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig.
-The subjects were divided into groups of four, so the study was conducted on two different sessions.
-All participants were asked to hold a 10-minute lesson.
-The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering the questionnaire.
+\hypertarget{questionnaire-data}{%
+\subsubsection{Questionnaire data}\label{questionnaire-data}}
 
-One person from the group of 4 acted as a teacher, the other three subjects acted as the class.
-The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disruptions in the classroom (e.g.~putting their heads on the table, chatting, looking at their mobile phones, etc.).
+After each mini-lesson, the subjects answered items on the teaching quality using a validated questionnaire ((Helmke et al.
+(2014))) and scales on the teacher's presence behavior.
+An external observer also completed the questionnaire.
+In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire.
 
-The lesson disruptions were displayed as instructions during the lesson for all ``students'' but not the teacher.
-In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase.
-In addition, the order of the data collection was taken into account in the analyses and variance caused by order was controlled.
+\hypertarget{behavioral-data}{%
+\subsubsection{Behavioral data}\label{behavioral-data}}
 
-By using mobile eye-trackers, the gaze and behavior of the experts and novices was recorded during the lesson.
-In addition, the speech and sounds and voices were recorded with an audio recorder installed in the middle of the Lab.
+The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab.
 Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles.
@@
 
-The lessons recorded on video were coded in a post-hoc procedure with a coding software by previously trained raters.
-The statistical data have been analyzed by using the program RStudio {[}Link: \url{https://rstudio.com/}{]}.
+\hypertarget{eyetracking-data}{%
+\subsubsection{Eyetracking data}\label{eyetracking-data}}
 
-\hypertarget{measures}{%
-\subsection{Measures}\label{measures}}
+A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants.
+The head unit is a measuring device with different sensitive sensors.
+A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
+Infrared light illuminators support the eye tracking sensors which record the eye orientation.
+The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
+The scene camera has a field of view of 90 deg.
+in 16:9 format (82 deg.
+horizontal and 52 deg.
+vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
+The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
 
-\hypertarget{questionnaire-data}{%
-\subsubsection{Questionnaire Data}\label{questionnaire-data}}
+\hypertarget{coding-data-preparation-reliability}{%
+\subsection{Coding/ Data preparation/ Reliability}\label{coding-data-preparation-reliability}}
 
-\emph{Describe how we collect questionnaire data (paper or online). Add some basic information about the structure of the questionnaire.}
+\hypertarget{questionnaire-data-1}{%
+\subsubsection{Questionnaire Data}\label{questionnaire-data-1}}
 
@@
 \includegraphics{paper_1_supplement_files/figure-latex/boxplot scales-1.pdf}
-\newpage
-Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment.
-The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.
 
-\includegraphics{paper_1_supplement_files/figure-latex/Duration speaking time-1.pdf}
 \newpage
 
-\hypertarget{eye-tracking-equipment}{%
-\subsubsection{Eye-tracking equipment}\label{eye-tracking-equipment}}
+\hypertarget{behavioral-data-1}{%
+\subsubsection{Behavioral Data}\label{behavioral-data-1}}
 
-A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements.
-The head unit is a measuring device with different sensitive sensors.
-A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
-Infrared light illuminators support the eye tracking sensors which record the eye orientation.
-The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
-The scene camera has a field of view of 90 deg.
-in 16:9 format (82 deg.
-horizontal and 52 deg.
-vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
-The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
+The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz and Rädiker (2019)). The following coding scheme was developed:
 
-The Tobii Pro Glasses 2 software allows for non-screen based recordings of a participants' attention while moving in real-world settings.
+\begin{itemize}
+\item
+  phase - lesson begin, state event: teacher starts the lesson with a noise, talk, taking a position in class
+\item
+  phase - lesson end, state event: teacher finishes the lesson with a noise, talk, taking a position in class
+\item
+  phase - organization/transition points, state event: any situation that does not imply effective learning time (fetching chalk, working material, organizing desks, opening windows, printing work results etc.)
+\item
+  phase - single, state event: any individual student activity on a given task (reading, writing, drawing etc.)
+\item
+  phase - group, state event: any student activity on a given task together in a group of at least 3 students (reading, writing, drawing etc.)
+\item
+  phase - class discussion, state event: discussion in class, teacher talks to class/individual/group
+\item
+  phase - pair: state event: any student activity on a given task together in a team of 2 students (reading, writing, drawing etc.)
+\item
+  phase - teachers lecture, state event: any teacher's presentation on a certain topic which maybe supported by a PPP, PREZI, notes on board, OHP etc.
+\item
+  phase - other, state event: not categorizable
+\item
+  phase - break, state event: e.g.~drinking, relaxation exercises
+\item
+  phase - external interruption, state event: external interruptions (e.g.~fire alarm, technical problems, other teachers coming into the room)
+\item
+  speaking time - teacher, state event
+\item
+  speaking time - students, state event
+\item
+  disruption - chatting with neighbor, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+\item
+  disruption - asking a question, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+\item
+  disruption - yelling, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+\item
+  disruption - looking at phone, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+\item
+  disruption - staring out of window, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+\item
+  disruption - drawing, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+\item
+  disruption - head on table, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+\item
+  disruption - clicking pen, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+\item
+  disruption - drumming hands, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+\item
+  disruption - walking around, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
+\end{itemize}
+
+First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher.
+The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.
+
+\includegraphics{paper_1_supplement_files/figure-latex/speaking plot-1.pdf}
+
+\hypertarget{eyetracking-data-1}{%
+\subsubsection{Eyetracking Data}\label{eyetracking-data-1}}
+
+The Tobii Pro Lab 2 software was used to analyze the teachers' visual attetion during each mini-lesson.
+The software allows for non-screen based recordings of a participants' attention while moving in real-world settings.
 The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video.
-In order to map multiple recordings to AOIs, it is necessary to import the eye-tracking recordings into the Tobii Pro Analyzer software.
-Also, it is necessary to create a reference image of the scene in which one wishes to plot the gaze data (i.e.~snapshot).
-Once the snapshot is imported, the gaze recordings of multiple recordings can be mapped to the reference image and analyzed in aggregated form.
+In order to map multiple recordings to AOIs, we first imported the eye-tracking recordings into the Tobii Pro Analyzer software.
+Second, we created dynamic Areas of Interest (AOI) manually to plot the gaze data.
+Once the AOIs are created, the gaze recordings of multiple recordings can be mapped and analyzed in aggregated form.
 Tobii Pro does not allow to do AOI based analyses within Pro Lab.
-Also, the dependency on snapshot reference images makes this approach impractical when working in different settings, i.e.~different classrooms with various participants.
-Finally, mapping gaze to people or any moving objects complicated the analyses further.
-
-\hypertarget{eye-tracking-data}{%
-\subsubsection{Eye-Tracking Data}\label{eye-tracking-data}}
+So we exported a tsv.
+file to do further analyses in the software R.
 
@@
 
-\small{
+\scriptsize{
 
-\begin{tabular}{llllll}
+\begin{tabular}{lllllll}
 \toprule
-Participant & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{SE Duration Fixation} & \multicolumn{1}{c}{GRI}\\
+Participant & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
 \midrule
-01\_01\_D & Expert & 803.00 & 316,571.00 & NA & 394.00\\
-01\_02\_A & Expert & 1,070.00 & 385,812.00 & NA & 361.00\\
-01\_03\_B & Novice & 617.00 & 374,315.00 & NA & 607.00\\
-01\_04\_C & Novice & 769.00 & 384,537.00 & NA & 500.00\\
-02\_01\_A & Novice & 569.00 & 101,541.00 & NA & 178.00\\
-02\_02\_B & Novice & 1,140.00 & 520,431.00 & NA & 457.00\\
-02\_03\_C & Novice & 1,048.00 & 469,018.00 & NA & 448.00\\
-02\_04\_D & Novice & 613.00 & 438,655.00 & NA & 716.00\\
+01\_01\_D & Expert & 803.00 & 316,571.00 & 394.00 & 781,978.00 & 0.49\\
+01\_02\_A & Expert & 1,070.00 & 385,812.00 & 361.00 & 838,026.00 & 0.34\\
+01\_03\_B & Novice & 617.00 & 374,315.00 & 607.00 & 744,444.00 & 0.98\\
+01\_04\_C & Novice & 769.00 & 384,537.00 & 500.00 & 723,922.00 & 0.65\\
+02\_01\_A & Novice & 569.00 & 101,541.00 & 178.00 & 729,762.00 & 0.31\\
+02\_02\_B & Novice & 1,140.00 & 520,431.00 & 457.00 & 730,565.00 & 0.40\\
+02\_03\_C & Novice & 1,048.00 & 469,018.00 & 448.00 & 737,604.00 & 0.43\\
+02\_04\_D & Novice & 613.00 & 438,655.00 & 716.00 & 747,729.00 & 1.17\\
 \bottomrule
@@
 \end{table}
-
-\hypertarget{coding-data}{%
-\subsubsection{Coding Data}\label{coding-data}}
-
-The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz and Rädiker (2019)).
-The following coding scheme has been developed for coding:
 

### 2021-02-11 paper_1/paper_1_supplement.Rmd
paper 1 GRI

@@
 
+################## TEST SECTION
+
 ```{r boxplot GRI, fig.width=6, fig.height = 8, echo = FALSE}
@@
 ```
+
+```{r calibration phase TOI, echo = FALSE}
+
+# prepare data (selected from questionnaire data)
+et.calib.data<-read.table("./data/Aperol_pilot_glasses_raw_ALL_metrics_calib_without_AOI_snapshot.tsv", dec=",", sep="\t", header=T)
+
+# converting integer to numeric
+et.calib.data <- et.calib.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
+                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
+                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
+                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
+                                       )
+# select relevant rows 
+et.calib.data <- et.calib.data %>% filter(TOI == "Calibration phase")
+
+# calculate the GRI 
+# create a basic table (tibble) using tidyverse functions
+et.calib.table <- et.calib.data %>%
+  group_by(Participant, Variable1) %>%
+  summarise("Fixation Number" = Number_of_whole_fixations,
+            "Fixation Duration" = Total_duration_of_whole_fixations,
+            "M Duration Fixation" = Average_duration_of_whole_fixations,
+            "TOI" = Duration_of_interval,
+            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
+
+# format and insert table in manuscript
+apa_table(
+  et.calib.table,
+  caption = "Number and Duration (in msec) of Fixations during calibration",
+  # note = "Write Note here", 
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  )
+
+```
+
+#########################################
 

### 2021-02-11 paper_1/paper_1_supplement.tex
paper 1 GRI

@@
 
+TEST SECTION
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:calibration phase TOI}Number and Duration (in msec) of Fixations during calibration}
+
+\scriptsize{
+
+\begin{tabular}{lllllll}
+\toprule
+Participant & \multicolumn{1}{c}{Variable1} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
+\midrule
+01\_01\_D & Expert & 9.00 & 14,372.00 & 1,597.00 & 16,470.00 & 177.44\\
+01\_02\_A & Expert & 10.00 & 10,194.00 & 1,019.00 & 13,335.00 & 101.90\\
+01\_03\_B & Novice & 17.00 & 9,234.00 & 543.00 & 10,615.00 & 31.94\\
+01\_04\_C & Novice & 14.00 & 15,311.00 & 1,094.00 & 17,224.00 & 78.14\\
+02\_01\_A & Novice & 13.00 & 5,157.00 & 397.00 & 17,902.00 & 30.54\\
+02\_02\_B & Novice & 12.00 & 10,654.00 & 888.00 & 12,325.00 & 74.00\\
+02\_03\_C & Novice & 18.00 & 14,151.00 & 786.00 & 16,494.00 & 43.67\\
+02\_04\_D & Novice & 14.00 & 19,128.00 & 1,366.00 & 20,964.00 & 97.57\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 \hypertarget{data-analysis}{%

### 2021-02-15 paper_1/paper_1_supplement_new_table.Rmd
new manuscript with scale analysis

--- 2021-02-11 paper_1/paper_1_supplement.Rmd
@@
 if (!require(papaja)) install.packages('papaja'); library(papaja)
+if (!require(psych)) install.packages('psych'); library(psych)
 
@@
 
-For the sample recruitment of the subjects (N = 48, experts n = 24, novices n = 24), schools in the city of Leipzig in Saxony were contacted.
+For the sample recruitment of the subjects (N = 8, experts n = 2, novices n = 6), schools in the city of Leipzig in Saxony were contacted.
 The institutions as well as the subjects were informed in detail about the aim and intention of the study in advance.
@@
 
-After each mini-lesson, the subjects answered items on the teaching quality using a validated questionnaire ((@helmke2014unterrichtsdiagnostik)) and scales on the teacher's presence behavior.
-An external observer also completed the questionnaire.
-In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire.
+After each mini-lesson, the students answered items on the teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and scales on the teacher's presence behavior (students n = 24).
+In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire after each mini-lesson (teachers n = 8).
 
@@
 The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes. 
-The scales on the quality of teaching are a validated questionnaire (@helmke2014unterrichtsdiagnostik).
-Whereas the scales on the teacher's presence behavior were derived from the research literature (@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen) and were used in the pilot for the first time.
+The scales on the quality of teaching are a validated questionnaire [@helmke2014unterrichtsdiagnostik].
+Whereas the scales on the teacher's presence behavior were derived from the research literature [@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen] and were used in the pilot for the first time.
+The questionnaire is 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
+Data was obtained from N = 32 subjects (students n = 24, teachers n = 8).
 
@@
 
-# prepare data (selected from questionnaire data)
-quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)
+# prepare data (selected from questionnaire data) - only equal items and without observer
+quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)
 
-# knock out NAs
+# knock out NAs and duration of speaking time
 quest.raw.data <- quest.raw.data  %>% filter(
-  personID != "NA")
-
-# to compare both sessions filter only Identical items
-quest.raw.data <- quest.raw.data  %>% filter(str_detect(shortID, 
-                                                 paste(c("km_mitbekommen",
-                                                         "km_klar",
-                                                         "km_ungestört",
-                                                         "km_aktiv",
-                                                         "lkm_freundlich",
-                                                         "lkm_interesse",
-                                                         "lkm_kritik",
-                                                         "lkm_ausreden",
-                                                         "lkm_überlegen",
-                                                         "lkm_rückmeldungen",
-                                                         "ks_funktion",
-                                                         "ks_verständlich",
-                                                         "ks_sichtbar",
-                                                         "af_beiträge",
-                                                         "af_wechselseitig",
-                                                         "af_nachdenken",
-                                                         "phb_stand",
-                                                         "phb_augen",
-                                                         "phb_blick",
-                                                         "phb_vorsichgeht",
-                                                         "phb_raum",
-                                                         "phb_gestik",
-                                                         "phb_alleangesehen",
-                                                         "ps_deutlich",
-                                                         "ps_klar",
-                                                         "ps_impulse",
-                                                         "pi_nonverbal",
-                                                         "pi_zubewegen",
-                                                         "pi_direkt",
-                                                         "m_natürlich",
-                                                         "m_fiktiv",
-                                                         "m_verhalten"),
-                                                    collapse = '|')))
+  personID != "NA",
+  itemID != "8")
+view(quest.raw.data)
 
@@
 
+# calculate Cronbach's Alpha
+# select relevant columns
+quest.raw.data.column <- quest.raw.data %>% select(itemID, value)
+view(quest.raw.data.column)
+# changing long format into wide format 
+quest.raw.data.wide <- spread (quest.raw.data.column, itemID, value)
+view(quest.raw.data.wide)
+
+quest.raw.data.wide <- as_tibble(quest.raw.data) %>%          
+                          select(scale, value) %>%             # select columns of interest
+                          mutate(id = row_number()) %>%         # create a row identifier
+                          spread(scale, value)                 # reshape dataset
+
+view(quest.raw.data.wide)
+
 # create a basic table (tibble) using tidyverse functions 
 scale.quest.table <- quest.raw.data %>% # select data
-  group_by(group, scale) %>%
+  group_by(scale) %>%
   summarise("M scale" = round(mean(value), 2),
+            "SD scale" = round(sd(value), 2),
             "min scale" = min(value),
-            "max sclae" = max(value),
-            "SD scale" = round(sd(value), 2))
-
-# remove duplicate labels from the table column "group" to create the APA-style omission of categorical variables
-# this is easier than the stub_indent option in apa_table
-scale.quest.table$group[duplicated(scale.quest.table$group)] <- ""
+            "max sclae" = max(value))
 
@@
 (1) Classroom management
-```{r classroom management line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+```{r classroom management line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = Items for Classroom Management}
 
@@
 
-# filter by parameter variable, i.e. create a subset for classroom management
+# filter by parameter variable, i.e. create a subset for classroom management without perspective "observer"
 cm.data <- quest.raw.data %>% filter(scale == "Classroom management")
+
+view(cm.data)
 
@@
                   aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
+                      group = perspective, colour = perspective)) +
   geom_line()+
@@
 (2) Positive climate and motivation
-```{r Positive climate and motivation line plots,  fig.width=6, fig.height = 7, message = FALSE, warning = FALSE , echo=FALSE}
+```{r Positive climate and motivation line plots,  fig.width=6, fig.height = 7, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = Items for Positive climate and motivation}
 
@@
 (3) Clarity and structuredness
-```{r Clarity and structuredness line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+```{r Clarity and structuredness line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = Items for Clarity and structuredness}
 
@@
 (4) Activation and support
-```{r Activation and support line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+```{r Activation and support line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = Items for Activation and support}
 
@@
 (8) Natural behaviour
-```{r Natural behaviour line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+```{r Natural behaviour line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = Items for Natural beaviour}
 
@@
 
-```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE}
+```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE, fig.cap = Boxplots and individual data for experts and novices}
 
 quest.plot <- quest.raw.data %>%
-  ggplot( aes(x=scale, y=value, fill=scale)) +
+  ggplot(aes(x=scale, y=value, fill=scale)) +
     geom_boxplot() +
@@
 
-The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (@kuckartz2019analyzing). The following coding scheme was developed:
+The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters [@kuckartz2019analyzing]. The following coding scheme was developed:
 
@@
 
-```{r coded speaking time, echo = FALSE}
+```{r coded speaking time, echo = FALSE }
 ### read in data for 01_01_expert_D
@@
 The GRI is higher for novices than for experts.
-(@gegenfurtner2020gaze)
+[@gegenfurtner2020gaze]
 
@@
   )
-
-```
-
-################## TEST SECTION
-
-```{r boxplot GRI, fig.width=6, fig.height = 8, echo = FALSE}
-# 
-# et.plot <- et.raw.data %>%
-#   ggplot(aes(x=Number_of_whole_fixations, y=value, fill=scale)) +
-#     geom_boxplot() +
-#     scale_x_discrete(guide = guide_axis(angle = 70)) +
-#     geom_jitter(color="black", size=0.4, alpha=0.9) +
-#     theme_light() +
-#     theme(
-#       legend.position="none",
-#       plot.title = element_text(size=11)
-#     ) +
-#     facet_grid(~Variable)+
-#     ggtitle("Boxplot with individual points for Number of fixations") +
-#     xlab("")
-# et.plot
 

### 2021-02-15 paper_1/paper_1_supplement_new_table.tex
new manuscript with scale analysis

--- 2021-02-11 paper_1/paper_1_supplement.tex
@@
 
-After each mini-lesson, the subjects answered items on the teaching quality using a validated questionnaire ((Helmke et al.
-(2014))) and scales on the teacher's presence behavior.
-An external observer also completed the questionnaire.
-In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire.
+After each mini-lesson, the students answered items on the teaching quality using a validated questionnaire (Helmke et al., 2014) and scales on the teacher's presence behavior (students n = 24).
+In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire after each mini-lesson (teachers n = 8).
 
@@
 The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes.
-The scales on the quality of teaching are a validated questionnaire (Helmke et al.
-(2014)).
-Whereas the scales on the teacher's presence behavior were derived from the research literature (Brophy (1986); Kiel, Frey, Weiß, and Weiss (2013); Kounin (2006); Marzano (2007); Nolting (2012)) and were used in the pilot for the first time.
+The scales on the quality of teaching are a validated questionnaire (Helmke et al., 2014).
+Whereas the scales on the teacher's presence behavior were derived from the research literature (Brophy, 1986; Kiel, Frey, Weiß, \& Weiss, 2013; Kounin, 2006; Marzano, 2007; Nolting, 2012) and were used in the pilot for the first time.
+The questionnaire is 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
+Data was obtained from N = 32 subjects (students n = 24, teachers n = 8).
 
@@
 
-\begin{tabular}{llllll}
+\begin{tabular}{lllll}
 \toprule
-group & \multicolumn{1}{c}{scale} & \multicolumn{1}{c}{M scale} & \multicolumn{1}{c}{min scale} & \multicolumn{1}{c}{max sclae} & \multicolumn{1}{c}{SD scale}\\
+scale & \multicolumn{1}{c}{M scale} & \multicolumn{1}{c}{SD scale} & \multicolumn{1}{c}{min scale} & \multicolumn{1}{c}{max sclae}\\
 \midrule
-expert & Activation and support & 3.33 & 2.00 & 4.00 & 0.80\\
- & Clarity and structuredness & 3.70 & 1.00 & 4.00 & 0.73\\
- & Classroom management & 3.23 & 1.00 & 4.00 & 0.90\\
- & Natural behaviour & 3.57 & 2.00 & 4.00 & 0.63\\
- & Positive climate and motivation & 3.60 & 2.00 & 4.00 & 0.62\\
- & Presence: posture/gaze & 3.29 & 1.00 & 4.00 & 0.92\\
- & Presence: verbal and non-verbal intervention & 3.07 & 2.00 & 4.00 & 0.78\\
- & Presence: voice & 3.57 & 2.00 & 4.00 & 0.63\\
-novice & Activation and support & 2.23 & 0.00 & 4.00 & 1.39\\
- & Clarity and structuredness & 3.35 & 1.00 & 4.00 & 0.76\\
- & Classroom management & 2.82 & 1.00 & 4.00 & 0.90\\
- & Natural behaviour & 3.13 & 2.00 & 4.00 & 0.71\\
- & Positive climate and motivation & 3.11 & 0.00 & 4.00 & 0.90\\
- & Presence: posture/gaze & 2.95 & 0.00 & 4.00 & 0.95\\
- & Presence: verbal and non-verbal intervention & 2.88 & 1.00 & 4.00 & 0.97\\
- & Presence: voice & 3.30 & 2.00 & 4.00 & 0.74\\
+Activation and support & 2.45 & 1.37 & 0.00 & 4.00\\
+Clarity and structuredness & 3.41 & 0.81 & 1.00 & 4.00\\
+Classroom management & 2.97 & 0.94 & 1.00 & 4.00\\
+Natural behaviour & 3.28 & 0.74 & 2.00 & 4.00\\
+Positive climate and motivation & 3.27 & 0.89 & 0.00 & 4.00\\
+Presence: posture/gaze & 3.10 & 0.96 & 0.00 & 4.00\\
+Presence: verbal and non-verbal intervention & 3.07 & 0.82 & 1.00 & 4.00\\
+Presence: voice & 3.40 & 0.72 & 2.00 & 4.00\\
 \bottomrule
@@
   Classroom management
-  \includegraphics{paper_1_supplement_files/figure-latex/classroom management line plots-1.pdf}
+  \includegraphics{paper_1_supplement_new_table_files/figure-latex/classroom management line plots-1.pdf}
   \newpage
@@
   Positive climate and motivation
-  \includegraphics{paper_1_supplement_files/figure-latex/Positive climate and motivation line plots-1.pdf}
+  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Positive climate and motivation line plots-1.pdf}
   \newpage
@@
   Clarity and structuredness
-  \includegraphics{paper_1_supplement_files/figure-latex/Clarity and structuredness line plots-1.pdf}
+  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Clarity and structuredness line plots-1.pdf}
   \newpage
@@
   Activation and support
-  \includegraphics{paper_1_supplement_files/figure-latex/Activation and support line plots-1.pdf}
+  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Activation and support line plots-1.pdf}
   \newpage
@@
   Natural behaviour
-  \includegraphics{paper_1_supplement_files/figure-latex/Natural behaviour line plots-1.pdf}
+  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Natural behaviour line plots-1.pdf}
   \newpage
@@
 
-\includegraphics{paper_1_supplement_files/figure-latex/boxplot scales-1.pdf}
+\includegraphics{paper_1_supplement_new_table_files/figure-latex/boxplot scales-1.pdf}
 
@@
 
-\includegraphics{paper_1_supplement_files/figure-latex/speaking plot-1.pdf}
+\includegraphics{paper_1_supplement_new_table_files/figure-latex/speaking plot-1.pdf}
 
@@
 The GRI is higher for novices than for experts.
-(Gegenfurtner et al.
-(2020))
+(Gegenfurtner et al., 2020)
 
@@
 \end{table}
-
-TEST SECTION
 
@@
 
-We used R {[}Version 4.0.3; R Core Team (2019){]} and the R-packages \emph{\}dplyr} {[}@\}R-dplyr{]}, \emph{forcats} {[}Version 0.5.0; Wickham (2020a){]}, \emph{ggplot2} {[}Version 3.3.2; Wickham (2016){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{papayar} (Muschelli, 2016), \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham, Hester, and Francois (2018){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.0.4; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.2; Wickham (2020b){]}, and \emph{tidyverse} {[}Version 1.3.0; Wickham et al.
+We used R {[}Version 4.0.3; R Core Team (2019){]} and the R-packages \emph{\}dplyr} {[}@\}R-dplyr{]}, \emph{forcats} {[}Version 0.5.0; Wickham (2020a){]}, \emph{ggplot2} {[}Version 3.3.2; Wickham (2016){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{papayar} (Muschelli, 2016), \emph{psych} {[}Version 2.0.12; Revelle (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham, Hester, and Francois (2018){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.0.4; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.2; Wickham (2020b){]}, and \emph{tidyverse} {[}Version 1.3.0; Wickham et al.
 (2019){]} for all our analyses.
@@
 
+\leavevmode\hypertarget{ref-R-psych}{}%
+Revelle, W.
+(2020).
+\emph{Psych: Procedures for psychological, psychometric, and personality research}.
+Evanston, Illinois: Northwestern University.
+Retrieved from \url{https://CRAN.R-project.org/package=psych}
+
 \leavevmode\hypertarget{ref-stuermer2017eye}{}%

### 2021-02-16 paper_1/paper_1_supplement_new_table.Rmd
added alpha for each scale (self-assessment/students)

@@
 if (!require(papaja)) install.packages('papaja'); library(papaja)
-if (!require(psych)) install.packages('psych'); library(psych)
+if (!require(psych)) install.packages('psych'); library(psych) # stats
+if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
+if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
 
@@
 
-The table provides an overview over the mean, the range and standard deviation of all scales.
-
-```{r table all scales, echo = FALSE}
+Table \@ref(tab:table-all-scales-self-assessment) provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness & Kurtosis of all scales for the teachers' self-assessment.
+
+```{r table-all-scales-self-assessment, echo = FALSE}
 
@@
   personID != "NA",
-  itemID != "8")
-view(quest.raw.data)
+  itemID != "8",
+  perspective == "self-assessment")
 
@@
 
-# calculate Cronbach's Alpha
-# select relevant columns
-quest.raw.data.column <- quest.raw.data %>% select(itemID, value)
-view(quest.raw.data.column)
-# changing long format into wide format 
-quest.raw.data.wide <- spread (quest.raw.data.column, itemID, value)
-view(quest.raw.data.wide)
-
-quest.raw.data.wide <- as_tibble(quest.raw.data) %>%          
-                          select(scale, value) %>%             # select columns of interest
-                          mutate(id = row_number()) %>%         # create a row identifier
-                          spread(scale, value)                 # reshape dataset
-
-view(quest.raw.data.wide)
-
-# create a basic table (tibble) using tidyverse functions 
-scale.quest.table <- quest.raw.data %>% # select data
+# calculate Cronbach's Alpha for each scale
+
+# activation & support
+self.as.wide <- quest.raw.data %>%
+                          filter (scale == "Activation and support") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+self.alpha.as <- alpha(self.as.wide[,-1])
+self.alpha.as
+
+#clarity & structuredness
+self.cs.wide <- quest.raw.data %>%
+                          filter (scale == "Clarity and structuredness") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+self.alpha.cs <- alpha(self.cs.wide[,-1])
+self.alpha.cs
+
+#classroom management
+self.cm.wide <- quest.raw.data %>%
+                          filter (scale == "Classroom management") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+self.alpha.cm <- alpha(self.cm.wide[,-1])
+self.alpha.cm
+
+#natural behaviour
+self.nb.wide <- quest.raw.data %>%
+                          filter (scale == "Natural behaviour") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+self.alpha.nb <- alpha(self.nb.wide[,-1])
+self.alpha.nb
+
+#positive climate and motivation
+self.pcm.wide <- quest.raw.data %>%
+                          filter (scale == "Positive climate and motivation") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+self.alpha.pcm <- alpha(self.pcm.wide[,-1])
+self.alpha.pcm
+
+#presence: posture & gaze
+self.ppg.wide <- quest.raw.data %>%
+                          filter (scale == "Presence: posture/gaze") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+self.alpha.ppg <- alpha(self.ppg.wide[,-1])
+self.alpha.ppg
+
+#presence: verbal and non-verbal intervention
+self.pvni.wide <- quest.raw.data %>%
+                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+self.alpha.pvni <- alpha(self.pvni.wide[,-1])
+self.alpha.pvni
+
+#presence: voice
+self.pv.wide <- quest.raw.data %>%
+                          filter (scale == "Presence: voice") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+self.alpha.pv <- alpha(self.pv.wide[,-1])
+self.alpha.pv
+
+############################################### 
+#Presence without subscales
+self.p.wide <- quest.raw.data %>%
+                          filter(str_detect(scale,
+                                        paste(c(
+                                        "Presence: voice", 
+                                        "Presence: verbal and non-verbal intervention", 
+                                        "Presence: posture/gaze"),
+                                         collapse = '|'))) %>% 
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+self.alpha.p <- alpha(self.p.wide[,-1])
+self.alpha.p
+
+###############################################
+
+# item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
+
+###############################################
+
+# create a basic table (tibble) using tidyverse functions for teachers' self assessment 
+teacher.scale.quest.table <- quest.raw.data %>% # select data
+  filter(perspective == "self-assessment")%>%
   group_by(scale) %>%
-  summarise("M scale" = round(mean(value), 2),
-            "SD scale" = round(sd(value), 2),
-            "min scale" = min(value),
-            "max sclae" = max(value))
+  summarise("M" = round(mean(value), 2),
+            "SD" = round(sd(value), 2),
+            "Min" = min(value),
+            "Max" = max(value),
+            "Skewness" = skewness(value),
+            "Kurtosis" = kurtosis(value))
+
+view(teacher.scale.quest.table)
 
@@
 apa_table(
-  scale.quest.table,
-  caption = "Mean values of all scales",
+  teacher.scale.quest.table,
+  caption = "Scale analysis for teachers' self-assessment",
   # note = "Write Note here", 
@@
 
+Table \@ref(tab:table-all-scales-students) provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness & Kurtosis of all scales for the students' perception of the teacher's behaviour in class.
+
+```{r table-all-scales-students, echo = FALSE}
+
+# prepare data (selected from questionnaire data) - only equal items and without observer
+quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)
+
+# knock out NAs and duration of speaking time
+quest.raw.data <- quest.raw.data  %>% filter(
+  personID != "NA",
+  itemID != "8",
+  perspective == "student")
+view(quest.raw.data)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
+
+# calculate Cronbach's Alpha for each scale of students' peception
+
+# activation & support
+stud.as.wide <- quest.raw.data %>%
+                          filter (scale == "Activation and support") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+stud.alpha.as <- alpha(stud.as.wide[,-1])
+stud.alpha.as
+
+#clarity & structuredness
+stud.cs.wide <- quest.raw.data %>%
+                          filter (scale == "Clarity and structuredness") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+stud.alpha.cs <- alpha(stud.cs.wide[,-1])
+stud.alpha.cs
+
+#classroom management
+stud.cm.wide <- quest.raw.data %>%
+                          filter (scale == "Classroom management") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+stud.alpha.cm <- alpha(stud.cm.wide[,-1])
+stud.alpha.cm
+
+#natural behaviour
+stud.nb.wide <- quest.raw.data %>%
+                          filter (scale == "Natural behaviour") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+stud.alpha.nb <- alpha(stud.nb.wide[,-1])
+stud.alpha.nb
+
+#positive climate and motivation
+stud.pcm.wide <- quest.raw.data %>%
+                          filter (scale == "Positive climate and motivation") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+stud.alpha.pcm <- alpha(stud.pcm.wide[,-1])
+stud.alpha.pcm
+
+#presence: posture & gaze
+stud.ppg.wide <- quest.raw.data %>%
+                          filter (scale == "Presence: posture/gaze") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+stud.alpha.ppg <- alpha(stud.ppg.wide[,-1])
+stud.alpha.ppg
+
+#presence: verbal and non-verbal intervention
+stud.pvni.wide <- quest.raw.data %>%
+                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+stud.alpha.pvni <- alpha(stud.pvni.wide[,-1])
+stud.alpha.pvni
+
+#presence: voice
+stud.pv.wide <- quest.raw.data %>%
+                          filter (scale == "Presence: voice") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+stud.alpha.pv <- alpha(stud.pv.wide[,-1])
+stud.alpha.pv
+
+############################################### 
+#Presence without subscales
+stud.p.wide <- quest.raw.data %>%
+                          filter(str_detect(scale,
+                                        paste(c(
+                                        "Presence: voice", 
+                                        "Presence: verbal and non-verbal intervention", 
+                                        "Presence: posture/gaze"),
+                                         collapse = '|'))) %>% 
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+stud.alpha.p <- alpha(stud.p.wide[,-1])
+stud.alpha.p
+
+###############################################
+
+# create a basic table (tibble) using tidyverse functions for teacher self assessment 
+student.scale.quest.table <- quest.raw.data %>% # select data
+  filter(perspective == "student")%>%
+  group_by(scale) %>%
+  summarise("M" = round(mean(value), 2),
+            "SD" = round(sd(value), 2),
+            "Min" = min(value),
+            "Max" = max(value),
+            "Skewness" = skewness(value),
+            "Kurtosis" = kurtosis(value))
+
+view(student.scale.quest.table)
+
+# format and insert table in manuscript
+apa_table(
+  student.scale.quest.table,
+  caption = "Scale analysis for students' perspective",
+  # note = "Write Note here", 
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+)
+
+```
+
 \newpage
@@
 (1) Classroom management
-```{r classroom management line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = Items for Classroom Management}
+```{r Line Plots Classroom Management, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, fig.cap="Items for Classroom Management"}
 
@@
 (2) Positive climate and motivation
-```{r Positive climate and motivation line plots,  fig.width=6, fig.height = 7, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = Items for Positive climate and motivation}
+```{r Positive climate and motivation line plots,  fig.width=6, fig.height = 7, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Positive climate and motivation"}
 
@@
 (3) Clarity and structuredness
-```{r Clarity and structuredness line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = Items for Clarity and structuredness}
+```{r Clarity and structuredness line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Clarity and structuredness"}
 
@@
 (4) Activation and support
-```{r Activation and support line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = Items for Activation and support}
+```{r Activation and support line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Activation and support"}
 
@@
 (8) Natural behaviour
-```{r Natural behaviour line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = Items for Natural beaviour}
+```{r Natural behaviour line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Natural Behaviour"}
 
@@
 
-```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE, fig.cap = Boxplots and individual data for experts and novices}
+```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE, fig.cap = "Boxplots and individual data for experts and novices"}
 

### 2021-02-16 paper_1/paper_1_supplement_new_table.tex
added alpha for each scale (self-assessment/students)

@@
 
-The table provides an overview over the mean, the range and standard deviation of all scales.
+Table \ref{tab:table-all-scales-self-assessment} provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness \& Kurtosis of all scales for the teachers' self-assessment.
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = self.as.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
+##       0.85      0.87    0.85      0.69 6.8 0.095  2.5 0.97     0.62
+## 
+##  lower alpha upper     95% confidence boundaries
+## 0.67 0.85 1.04 
+## 
+##  Reliability if an item is dropped:
+##                  raw_alpha std.alpha G6(smc) average_r  S/N alpha se var.r
+## af_beiträge           0.75      0.76    0.62      0.62  3.2    0.169    NA
+## af_nachdenken         0.71      0.74    0.59      0.59  2.9    0.185    NA
+## af_wechselseitig      0.93      0.93    0.87      0.87 13.7    0.049    NA
+##                  med.r
+## af_beiträge       0.62
+## af_nachdenken     0.59
+## af_wechselseitig  0.87
+## 
+##  Item statistics 
+##                  n raw.r std.r r.cor r.drop mean   sd
+## af_beiträge      8  0.90  0.92  0.90   0.80  3.0 0.93
+## af_nachdenken    8  0.92  0.93  0.92   0.81  2.4 1.06
+## af_wechselseitig 8  0.86  0.82  0.65   0.62  2.0 1.31
+## 
+## Non missing response frequency for each item
+##                     1    2    3    4 miss
+## af_beiträge      0.00 0.38 0.25 0.38    0
+## af_nachdenken    0.25 0.25 0.38 0.12    0
+## af_wechselseitig 0.50 0.25 0.00 0.25    0
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in alpha(self.cs.wide[, -1]): Some items were negatively correlated with the total scale and probably 
+## should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Some items ( ks_sichtbar ) were negatively correlated with the total scale and 
+## probably should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in sqrt(Vtc): NaNs wurden erzeugt
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = self.cs.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r   S/N  ase mean   sd median_r
+##      -0.76      -1.1   -0.36     -0.36 -0.53 0.94  2.8 0.53    -0.36
+## 
+##  lower alpha upper     95% confidence boundaries
+## -2.6 -0.76 1.08 
+## 
+##  Reliability if an item is dropped:
+##                 raw_alpha std.alpha G6(smc) average_r   S/N alpha se var.r
+## ks_sichtbar         -0.75     -0.36    0.13     -0.36 -0.26       NA     0
+## ks_verständlich     -0.17     -0.36    0.13     -0.36 -0.26       NA     0
+##                 med.r
+## ks_sichtbar     -0.36
+## ks_verständlich -0.36
+## 
+##  Item statistics 
+##                 n raw.r std.r r.cor r.drop mean   sd
+## ks_sichtbar     8  0.88  0.57   NaN  -0.36  3.1 1.13
+## ks_verständlich 8  0.13  0.57   NaN  -0.36  2.5 0.53
+## 
+## Non missing response frequency for each item
+##                    1    2    3   4 miss
+## ks_sichtbar     0.12 0.12 0.25 0.5    0
+## ks_verständlich 0.00 0.50 0.50 0.0    0
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = self.cm.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
+##       0.83      0.82    0.93      0.54 4.6 0.084  2.4 0.72     0.55
+## 
+##  lower alpha upper     95% confidence boundaries
+## 0.67 0.83 1 
+## 
+##  Reliability if an item is dropped:
+##                raw_alpha std.alpha G6(smc) average_r S/N alpha se var.r med.r
+## km_aktiv            0.84      0.83    0.83      0.62 5.0    0.091 0.049  0.57
+## km_klar             0.71      0.68    0.86      0.42 2.2    0.172 0.167  0.44
+## km_mitbekommen      0.89      0.89    0.94      0.74 8.4    0.070 0.033  0.82
+## km_ungestört        0.65      0.63    0.70      0.37 1.7    0.182 0.101  0.53
+## 
+##  Item statistics 
+##                n raw.r std.r r.cor r.drop mean   sd
+## km_aktiv       8  0.73  0.73  0.71   0.56  2.0 0.76
+## km_klar        8  0.93  0.92  0.90   0.84  2.5 1.07
+## km_mitbekommen 8  0.60  0.62  0.51   0.40  2.8 0.71
+## km_ungestört   8  0.97  0.97  0.99   0.93  2.5 0.93
+## 
+## Non missing response frequency for each item
+##                   1    2    3    4 miss
+## km_aktiv       0.25 0.50 0.25 0.00    0
+## km_klar        0.12 0.50 0.12 0.25    0
+## km_mitbekommen 0.00 0.38 0.50 0.12    0
+## km_ungestört   0.12 0.38 0.38 0.12    0
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = self.nb.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
+##        0.9       0.9    0.87      0.76 9.4 0.061  2.8 0.71     0.76
+## 
+##  lower alpha upper     95% confidence boundaries
+## 0.78 0.9 1.02 
+## 
+##  Reliability if an item is dropped:
+##             raw_alpha std.alpha G6(smc) average_r  S/N alpha se var.r med.r
+## m_fiktiv         0.91      0.91    0.83      0.83 10.1    0.065    NA  0.83
+## m_natürlich      0.81      0.81    0.68      0.68  4.2    0.135    NA  0.68
+## m_verhalten      0.86      0.86    0.76      0.76  6.4    0.096    NA  0.76
+## 
+##  Item statistics 
+##             n raw.r std.r r.cor r.drop mean   sd
+## m_fiktiv    8  0.88  0.89  0.79   0.75  3.0 0.76
+## m_natürlich 8  0.94  0.94  0.92   0.87  2.6 0.74
+## m_verhalten 8  0.92  0.91  0.86   0.81  2.9 0.83
+## 
+## Non missing response frequency for each item
+##                2    3    4 miss
+## m_fiktiv    0.25 0.50 0.25    0
+## m_natürlich 0.50 0.38 0.12    0
+## m_verhalten 0.38 0.38 0.25    0
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = self.pcm.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r S/N  ase mean   sd median_r
+##       0.78      0.78    0.97      0.37 3.5 0.11  2.9 0.61     0.41
+## 
+##  lower alpha upper     95% confidence boundaries
+## 0.57 0.78 1 
+## 
+##  Reliability if an item is dropped:
+##                   raw_alpha std.alpha G6(smc) average_r S/N alpha se var.r
+## lkm_ausreden           0.81      0.81    0.88      0.47 4.4     0.10 0.083
+## lkm_freundlich         0.80      0.78    0.91      0.41 3.5     0.09 0.120
+## lkm_interesse          0.73      0.74    0.98      0.36 2.8     0.15 0.114
+## lkm_kritik             0.69      0.66    0.84      0.28 2.0     0.16 0.122
+## lkm_rückmeldungen      0.67      0.68    0.79      0.30 2.1     0.18 0.088
+## lkm_überlegen          0.77      0.78    0.88      0.41 3.5     0.12 0.091
+##                   med.r
+## lkm_ausreden       0.48
+## lkm_freundlich     0.46
+## lkm_interesse      0.41
+## lkm_kritik         0.24
+## lkm_rückmeldungen  0.41
+## lkm_überlegen      0.43
+## 
+##  Item statistics 
+##                   n raw.r std.r r.cor r.drop mean   sd
+## lkm_ausreden      8  0.32  0.46  0.46   0.20  3.2 0.46
+## lkm_freundlich    8  0.51  0.59  0.59   0.31  3.1 0.83
+## lkm_interesse     8  0.80  0.72  0.66   0.63  2.6 1.19
+## lkm_kritik        8  0.88  0.90  0.91   0.82  3.0 0.76
+## lkm_rückmeldungen 8  0.91  0.86  0.87   0.85  2.5 0.93
+## lkm_überlegen     8  0.66  0.60  0.60   0.48  2.6 0.92
+## 
+## Non missing response frequency for each item
+##                      1    2    3    4 miss
+## lkm_ausreden      0.00 0.00 0.75 0.25    0
+## lkm_freundlich    0.00 0.25 0.38 0.38    0
+## lkm_interesse     0.25 0.12 0.38 0.25    0
+## lkm_kritik        0.00 0.25 0.50 0.25    0
+## lkm_rückmeldungen 0.12 0.38 0.38 0.12    0
+## lkm_überlegen     0.12 0.25 0.50 0.12    0
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in cor.smooth(r): Matrix was not positive definite, smoothing was done
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = self.ppg.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
+##       0.85      0.86    0.94      0.47 6.3 0.077  2.7 0.69     0.45
+## 
+##  lower alpha upper     95% confidence boundaries
+## 0.7 0.85 1.01 
+## 
+##  Reliability if an item is dropped:
+##                   raw_alpha std.alpha G6(smc) average_r S/N alpha se var.r
+## phb_alleangesehen      0.87      0.88    0.97      0.55 7.3    0.072 0.099
+## phb_augen              0.81      0.82    0.98      0.44 4.7    0.104 0.113
+## phb_blick              0.79      0.80    0.99      0.40 3.9    0.114 0.102
+## phb_gestik             0.88      0.88    0.96      0.56 7.5    0.066 0.081
+## phb_raum               0.88      0.89    0.97      0.57 8.1    0.068 0.078
+## phb_stand              0.78      0.80    0.86      0.40 4.0    0.118 0.107
+## phb_vorsichgeht        0.80      0.80    0.94      0.40 3.9    0.108 0.110
+##                   med.r
+## phb_alleangesehen  0.49
+## phb_augen          0.45
+## phb_blick          0.42
+## phb_gestik         0.52
+## phb_raum           0.62
+## phb_stand          0.42
+## phb_vorsichgeht    0.42
+## 
+##  Item statistics 
+##                   n raw.r std.r r.cor r.drop mean   sd
+## phb_alleangesehen 8  0.51  0.52  0.46   0.35  3.0 0.93
+## phb_augen         8  0.85  0.84  0.83   0.76  3.4 1.06
+## phb_blick         8  0.96  0.96  0.98   0.94  2.8 0.89
+## phb_gestik        8  0.52  0.50  0.48   0.33  2.6 1.06
+## phb_raum          8  0.43  0.45  0.36   0.26  1.8 0.89
+## phb_stand         8  0.95  0.95  0.97   0.93  2.9 0.99
+## phb_vorsichgeht   8  0.96  0.96  0.96   0.94  2.5 0.76
+## 
+## Non missing response frequency for each item
+##                      1    2    3    4 miss
+## phb_alleangesehen 0.12 0.00 0.62 0.25    0
+## phb_augen         0.12 0.00 0.25 0.62    0
+## phb_blick         0.12 0.12 0.62 0.12    0
+## phb_gestik        0.12 0.38 0.25 0.25    0
+## phb_raum          0.50 0.25 0.25 0.00    0
+## phb_stand         0.12 0.12 0.50 0.25    0
+## phb_vorsichgeht   0.12 0.25 0.62 0.00    0
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in alpha(self.pvni.wide[, -1]): Some items were negatively correlated with the total scale and probably 
+## should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Some items ( pi_nonverbal ) were negatively correlated with the total scale and 
+## probably should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in sqrt(Vtc): NaNs wurden erzeugt
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = self.pvni.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r   S/N ase mean   sd median_r
+##      -0.75     -0.81   -0.42     -0.18 -0.45   1  2.8 0.35    -0.17
+## 
+##  lower alpha upper     95% confidence boundaries
+## -2.76 -0.75 1.26 
+## 
+##  Reliability if an item is dropped:
+##              raw_alpha std.alpha G6(smc) average_r   S/N alpha se var.r  med.r
+## pi_direkt        -0.58     -0.72  -0.264    -0.264 -0.42     0.95    NA -0.264
+## pi_nonverbal     -0.21     -0.22  -0.098    -0.098 -0.18     0.81    NA -0.098
+## pi_zubewegen     -0.38     -0.40  -0.165    -0.165 -0.28     0.94    NA -0.165
+## 
+##  Item statistics 
+##              n raw.r std.r r.cor r.drop mean   sd
+## pi_direkt    8  0.49  0.53   NaN  -0.22  3.2 0.71
+## pi_nonverbal 8  0.64  0.41   NaN  -0.30  2.4 0.92
+## pi_zubewegen 8  0.20  0.46   NaN  -0.29  2.6 0.52
+## 
+## Non missing response frequency for each item
+##                 1    2    3    4 miss
+## pi_direkt    0.00 0.12 0.50 0.38    0
+## pi_nonverbal 0.12 0.50 0.25 0.12    0
+## pi_zubewegen 0.00 0.38 0.62 0.00    0
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = self.pv.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r S/N  ase mean   sd median_r
+##       0.77      0.76    0.82      0.51 3.2 0.12  2.8 0.62     0.54
+## 
+##  lower alpha upper     95% confidence boundaries
+## 0.53 0.77 1.01 
+## 
+##  Reliability if an item is dropped:
+##             raw_alpha std.alpha G6(smc) average_r  S/N alpha se var.r med.r
+## ps_deutlich      0.65      0.70    0.54      0.54 2.32    0.213    NA  0.54
+## ps_impulse       0.89      0.89    0.79      0.79 7.75    0.081    NA  0.79
+## ps_klar          0.31      0.34    0.21      0.21 0.52    0.434    NA  0.21
+## 
+##  Item statistics 
+##             n raw.r std.r r.cor r.drop mean   sd
+## ps_deutlich 8  0.87  0.81  0.76   0.64  2.9 0.83
+## ps_impulse  8  0.62  0.71  0.52   0.39  2.6 0.52
+## ps_klar     8  0.96  0.95  0.95   0.88  2.9 0.83
+## 
+## Non missing response frequency for each item
+##                2    3    4 miss
+## ps_deutlich 0.38 0.38 0.25    0
+## ps_impulse  0.38 0.62 0.00    0
+## ps_klar     0.38 0.38 0.25    0
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in cor.smooth(r): Matrix was not positive definite, smoothing was done
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in alpha(self.p.wide[, -1]): Some items were negatively correlated with the total scale and probably 
+## should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Some items ( pi_nonverbal ) were negatively correlated with the total scale and 
+## probably should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = self.p.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r S/N ase mean   sd median_r
+##       0.74      0.74    0.73      0.18 2.8 0.1  2.7 0.42     0.18
+## 
+##  lower alpha upper     95% confidence boundaries
+## 0.54 0.74 0.95 
+## 
+##  Reliability if an item is dropped:
+##                   raw_alpha std.alpha G6(smc) average_r S/N var.r med.r
+## phb_alleangesehen      0.71      0.70    0.74      0.16 2.3  0.20 0.159
+## phb_augen              0.70      0.70    0.72      0.16 2.4  0.18 0.159
+## phb_blick              0.66      0.66    0.67      0.14 1.9  0.17 0.145
+## phb_gestik             0.74      0.73    0.75      0.19 2.8  0.20 0.178
+## phb_raum               0.74      0.72    0.72      0.18 2.6  0.20 0.178
+## phb_stand              0.65      0.65    0.67      0.14 1.9  0.17 0.129
+## phb_vorsichgeht        0.68      0.66    0.68      0.14 1.9  0.18 0.096
+## pi_direkt              0.76      0.76    0.75      0.21 3.1  0.21 0.273
+## pi_nonverbal           0.84      0.83    0.81      0.29 4.9  0.12 0.291
+## pi_zubewegen           0.76      0.76    0.78      0.21 3.1  0.21 0.214
+## ps_deutlich            0.71      0.70    0.77      0.17 2.4  0.20 0.145
+## ps_impulse             0.74      0.72    0.74      0.18 2.6  0.21 0.202
+## ps_klar                0.68      0.66    0.69      0.14 2.0  0.19 0.130
+## 
+##  Item statistics 
+##                   n  raw.r std.r  r.cor r.drop mean   sd
+## phb_alleangesehen 8  0.617  0.65  0.644  0.495  3.0 0.93
+## phb_augen         8  0.673  0.62  0.587  0.545  3.4 1.06
+## phb_blick         8  0.908  0.88  0.845  0.872  2.8 0.89
+## phb_gestik        8  0.453  0.38  0.257  0.280  2.6 1.06
+## phb_raum          8  0.439  0.49  0.389  0.296  1.8 0.89
+## phb_stand         8  0.956  0.92  0.891  0.935  2.9 0.99
+## phb_vorsichgeht   8  0.893  0.87  0.834  0.859  2.5 0.76
+## pi_direkt         8  0.147  0.18  0.023  0.019  3.2 0.71
+## pi_nonverbal      8 -0.723 -0.71 -1.014 -0.789  2.4 0.92
+## pi_zubewegen      8  0.075  0.17  0.072 -0.019  2.6 0.52
+## ps_deutlich       8  0.638  0.60  0.622  0.534  2.9 0.83
+## ps_impulse        8  0.376  0.47  0.452  0.291  2.6 0.52
+## ps_klar           8  0.855  0.86  0.819  0.805  2.9 0.83
+## 
+## Non missing response frequency for each item
+##                      1    2    3    4 miss
+## phb_alleangesehen 0.12 0.00 0.62 0.25    0
+## phb_augen         0.12 0.00 0.25 0.62    0
+## phb_blick         0.12 0.12 0.62 0.12    0
+## phb_gestik        0.12 0.38 0.25 0.25    0
+## phb_raum          0.50 0.25 0.25 0.00    0
+## phb_stand         0.12 0.12 0.50 0.25    0
+## phb_vorsichgeht   0.12 0.25 0.62 0.00    0
+## pi_direkt         0.00 0.12 0.50 0.38    0
+## pi_nonverbal      0.12 0.50 0.25 0.12    0
+## pi_zubewegen      0.00 0.38 0.62 0.00    0
+## ps_deutlich       0.00 0.38 0.38 0.25    0
+## ps_impulse        0.00 0.38 0.62 0.00    0
+## ps_klar           0.00 0.38 0.38 0.25    0
+\end{verbatim}
 
@@
 
-\caption{\label{tab:table all scales}Mean values of all scales}
+\caption{\label{tab:table-all-scales-self-assessment}Scale analysis for teachers' self-assessment}
 
@@
 
-\begin{tabular}{lllll}
+\begin{tabular}{lllllll}
 \toprule
-scale & \multicolumn{1}{c}{M scale} & \multicolumn{1}{c}{SD scale} & \multicolumn{1}{c}{min scale} & \multicolumn{1}{c}{max sclae}\\
+scale & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis}\\
 \midrule
-Activation and support & 2.45 & 1.37 & 0.00 & 4.00\\
-Clarity and structuredness & 3.41 & 0.81 & 1.00 & 4.00\\
-Classroom management & 2.97 & 0.94 & 1.00 & 4.00\\
-Natural behaviour & 3.28 & 0.74 & 2.00 & 4.00\\
-Positive climate and motivation & 3.27 & 0.89 & 0.00 & 4.00\\
-Presence: posture/gaze & 3.10 & 0.96 & 0.00 & 4.00\\
-Presence: verbal and non-verbal intervention & 3.07 & 0.82 & 1.00 & 4.00\\
-Presence: voice & 3.40 & 0.72 & 2.00 & 4.00\\
+Activation and support & 2.46 & 1.14 & 1.00 & 4.00 & 0.10 & 1.65\\
+Clarity and structuredness & 2.81 & 0.91 & 1.00 & 4.00 & -0.17 & 2.17\\
+Classroom management & 2.44 & 0.88 & 1.00 & 4.00 & 0.19 & 2.38\\
+Natural behaviour & 2.83 & 0.76 & 2.00 & 4.00 & 0.28 & 1.84\\
+Positive climate and motivation & 2.85 & 0.87 & 1.00 & 4.00 & -0.49 & 2.65\\
+Presence: posture/gaze & 2.70 & 1.01 & 1.00 & 4.00 & -0.44 & 2.15\\
+Presence: verbal and non-verbal intervention & 2.75 & 0.79 & 1.00 & 4.00 & -0.07 & 2.48\\
+Presence: voice & 2.79 & 0.72 & 2.00 & 4.00 & 0.32 & 2.03\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+Table \ref{tab:table-all-scales-students} provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness \& Kurtosis of all scales for the students' perception of the teacher's behaviour in class.
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = stud.as.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r  S/N  ase mean   sd median_r
+##       0.48       0.5    0.41      0.25 0.99 0.17  2.6 0.71     0.22
+## 
+##  lower alpha upper     95% confidence boundaries
+## 0.14 0.48 0.82 
+## 
+##  Reliability if an item is dropped:
+##                  raw_alpha std.alpha G6(smc) average_r  S/N alpha se var.r
+## af_beiträge           0.34      0.35    0.22      0.22 0.55     0.26    NA
+## af_nachdenken         0.49      0.54    0.37      0.37 1.18     0.18    NA
+## af_wechselseitig      0.26      0.27    0.16      0.16 0.37     0.29    NA
+##                  med.r
+## af_beiträge       0.22
+## af_nachdenken     0.37
+## af_wechselseitig  0.16
+## 
+##  Item statistics 
+##                   n raw.r std.r r.cor r.drop mean   sd
+## af_beiträge      24  0.64  0.72  0.49   0.35  3.3 0.75
+## af_nachdenken    24  0.64  0.65  0.31   0.23  2.6 0.97
+## af_wechselseitig 24  0.82  0.75  0.55   0.37  2.0 1.25
+## 
+## Non missing response frequency for each item
+##                     1    2    3    4 miss
+## af_beiträge      0.04 0.04 0.50 0.42    0
+## af_nachdenken    0.12 0.33 0.33 0.21    0
+## af_wechselseitig 0.58 0.00 0.25 0.17    0
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = stud.cs.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r S/N  ase mean   sd median_r
+##       0.62      0.64    0.47      0.47 1.8 0.15  3.6 0.58     0.47
+## 
+##  lower alpha upper     95% confidence boundaries
+## 0.34 0.62 0.91 
+## 
+##  Reliability if an item is dropped:
+##                 raw_alpha std.alpha G6(smc) average_r S/N alpha se var.r med.r
+## ks_sichtbar          0.64      0.47    0.22      0.47 0.9       NA     0  0.47
+## ks_verständlich      0.35      0.47    0.22      0.47 0.9       NA     0  0.47
+## 
+##  Item statistics 
+##                  n raw.r std.r r.cor r.drop mean   sd
+## ks_sichtbar     24  0.90  0.86  0.59   0.47  3.5 0.78
+## ks_verständlich 24  0.81  0.86  0.59   0.47  3.6 0.58
+## 
+## Non missing response frequency for each item
+##                    1    2    3    4 miss
+## ks_sichtbar     0.04 0.04 0.25 0.67    0
+## ks_verständlich 0.00 0.04 0.29 0.67    0
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = stud.cm.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
+##       0.75      0.75    0.73      0.42 2.9 0.085  3.2 0.69     0.37
+## 
+##  lower alpha upper     95% confidence boundaries
+## 0.58 0.75 0.91 
+## 
+##  Reliability if an item is dropped:
+##                raw_alpha std.alpha G6(smc) average_r S/N alpha se  var.r med.r
+## km_aktiv            0.59      0.59    0.50      0.33 1.5    0.143 0.0038  0.35
+## km_klar             0.68      0.68    0.59      0.41 2.1    0.114 0.0063  0.37
+## km_mitbekommen      0.76      0.76    0.73      0.52 3.2    0.085 0.0319  0.50
+## km_ungestört        0.70      0.70    0.67      0.44 2.4    0.109 0.0555  0.36
+## 
+##  Item statistics 
+##                 n raw.r std.r r.cor r.drop mean   sd
+## km_aktiv       24  0.85  0.85  0.83   0.70  3.0 0.93
+## km_klar        24  0.76  0.77  0.70   0.56  3.3 0.86
+## km_mitbekommen 24  0.66  0.66  0.45   0.40  3.3 0.92
+## km_ungestört   24  0.74  0.74  0.59   0.52  3.1 0.93
+## 
+## Non missing response frequency for each item
+##                   1    2    3    4 miss
+## km_aktiv       0.04 0.29 0.29 0.38    0
+## km_klar        0.04 0.12 0.33 0.50    0
+## km_mitbekommen 0.08 0.04 0.33 0.54    0
+## km_ungestört   0.08 0.12 0.42 0.38    0
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = stud.nb.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
+##       0.85      0.85    0.82      0.66 5.8 0.056  3.4 0.59     0.61
+## 
+##  lower alpha upper     95% confidence boundaries
+## 0.74 0.85 0.96 
+## 
+##  Reliability if an item is dropped:
+##             raw_alpha std.alpha G6(smc) average_r S/N alpha se var.r med.r
+## m_fiktiv         0.71      0.71    0.56      0.56 2.5    0.120    NA  0.56
+## m_natürlich      0.89      0.90    0.82      0.82 8.9    0.044    NA  0.82
+## m_verhalten      0.75      0.75    0.61      0.61 3.1    0.103    NA  0.61
+## 
+##  Item statistics 
+##              n raw.r std.r r.cor r.drop mean   sd
+## m_fiktiv    23  0.92  0.92  0.89   0.79  3.4 0.72
+## m_natürlich 23  0.83  0.82  0.64   0.61  3.3 0.71
+## m_verhalten 23  0.89  0.90  0.86   0.77  3.5 0.59
+## 
+## Non missing response frequency for each item
+##                2    3    4 miss
+## m_fiktiv    0.13 0.35 0.52    0
+## m_natürlich 0.13 0.39 0.48    0
+## m_verhalten 0.04 0.43 0.52    0
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = stud.pcm.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r S/N  ase mean  sd median_r
+##       0.82      0.81    0.86      0.41 4.2 0.05  3.4 0.6     0.44
+## 
+##  lower alpha upper     95% confidence boundaries
+## 0.72 0.82 0.92 
+## 
+##  Reliability if an item is dropped:
+##                   raw_alpha std.alpha G6(smc) average_r S/N alpha se var.r
+## lkm_ausreden           0.78      0.77    0.78      0.40 3.3    0.063 0.043
+## lkm_freundlich         0.85      0.86    0.86      0.54 5.9    0.048 0.014
+## lkm_interesse          0.79      0.76    0.85      0.39 3.2    0.060 0.079
+## lkm_kritik             0.81      0.80    0.85      0.44 3.9    0.052 0.062
+## lkm_rückmeldungen      0.76      0.74    0.81      0.36 2.8    0.067 0.075
+## lkm_überlegen          0.75      0.72    0.76      0.34 2.6    0.070 0.057
+##                   med.r
+## lkm_ausreden       0.41
+## lkm_freundlich     0.54
+## lkm_interesse      0.42
+## lkm_kritik         0.51
+## lkm_rückmeldungen  0.41
+## lkm_überlegen      0.43
+## 
+##  Item statistics 
+##                    n raw.r std.r r.cor r.drop mean   sd
+## lkm_ausreden      24  0.77  0.75  0.75   0.66  3.6 0.77
+## lkm_freundlich    24  0.32  0.41  0.31   0.20  3.7 0.46
+## lkm_interesse     24  0.78  0.76  0.68   0.64  3.2 0.96
+## lkm_kritik        24  0.68  0.65  0.54   0.51  3.2 0.88
+## lkm_rückmeldungen 24  0.84  0.84  0.80   0.73  3.3 0.92
+## lkm_überlegen     24  0.87  0.88  0.90   0.79  3.4 0.83
+## 
+## Non missing response frequency for each item
+##                      1    2    3    4 miss
+## lkm_ausreden      0.04 0.04 0.17 0.75    0
+## lkm_freundlich    0.00 0.00 0.29 0.71    0
+## lkm_interesse     0.04 0.25 0.21 0.50    0
+## lkm_kritik        0.08 0.04 0.46 0.42    0
+## lkm_rückmeldungen 0.08 0.04 0.33 0.54    0
+## lkm_überlegen     0.04 0.08 0.29 0.58    0
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in alpha(stud.ppg.wide[, -1]): Some items were negatively correlated with the total scale and probably 
+## should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Some items ( phb_stand ) were negatively correlated with the total scale and 
+## probably should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = stud.ppg.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r S/N  ase mean   sd median_r
+##       0.59      0.54    0.74      0.14 1.2 0.11  3.2 0.39     0.17
+## 
+##  lower alpha upper     95% confidence boundaries
+## 0.37 0.59 0.81 
+## 
+##  Reliability if an item is dropped:
+##                   raw_alpha std.alpha G6(smc) average_r  S/N alpha se var.r
+## phb_alleangesehen      0.58      0.54    0.74     0.163 1.17    0.119 0.120
+## phb_augen              0.59      0.52    0.74     0.156 1.10    0.113 0.138
+## phb_blick              0.34      0.26    0.47     0.055 0.35    0.187 0.074
+## phb_gestik             0.43      0.36    0.66     0.085 0.56    0.160 0.106
+## phb_raum               0.67      0.61    0.76     0.203 1.53    0.086 0.109
+## phb_stand              0.68      0.68    0.76     0.259 2.09    0.096 0.073
+## phb_vorsichgeht        0.39      0.31    0.54     0.070 0.45    0.171 0.100
+##                   med.r
+## phb_alleangesehen 0.182
+## phb_augen         0.135
+## phb_blick         0.062
+## phb_gestik        0.135
+## phb_raum          0.215
+## phb_stand         0.215
+## phb_vorsichgeht   0.062
+## 
+##  Item statistics 
+##                    n raw.r std.r  r.cor r.drop mean   sd
+## phb_alleangesehen 24  0.45 0.425  0.287  0.231  3.5 0.66
+## phb_augen         24  0.33 0.455  0.291  0.158  3.6 0.49
+## phb_blick         24  0.90 0.876  0.972  0.827  3.5 0.72
+## phb_gestik        24  0.77 0.748  0.706  0.577  3.0 0.86
+## phb_raum          24  0.40 0.256  0.085  0.048  2.1 0.97
+## phb_stand         24 -0.14 0.025 -0.130 -0.295  3.7 0.46
+## phb_vorsichgeht   24  0.82 0.813  0.880  0.671  3.3 0.82
+## 
+## Non missing response frequency for each item
+##                      1    2    3    4 miss
+## phb_alleangesehen 0.00 0.08 0.29 0.62    0
+## phb_augen         0.00 0.00 0.38 0.62    0
+## phb_blick         0.04 0.00 0.42 0.54    0
+## phb_gestik        0.04 0.25 0.42 0.29    0
+## phb_raum          0.33 0.33 0.25 0.08    0
+## phb_stand         0.00 0.00 0.29 0.71    0
+## phb_vorsichgeht   0.04 0.08 0.38 0.50    0
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in alpha(stud.pvni.wide[, -1]): Some items were negatively correlated with the total scale and probably 
+## should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Some items ( pi_direkt ) were negatively correlated with the total scale and 
+## probably should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = stud.pvni.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r S/N  ase mean   sd median_r
+##        0.2      0.16    0.23     0.062 0.2 0.27  3.2 0.46     0.18
+## 
+##  lower alpha upper     95% confidence boundaries
+## -0.34 0.2 0.73 
+## 
+##  Reliability if an item is dropped:
+##              raw_alpha std.alpha G6(smc) average_r   S/N alpha se var.r med.r
+## pi_direkt         0.40      0.40    0.25      0.25  0.68     0.24    NA  0.25
+## pi_nonverbal      0.30      0.30    0.18      0.18  0.44     0.28    NA  0.18
+## pi_zubewegen     -0.64     -0.66   -0.25     -0.25 -0.40     0.66    NA -0.25
+## 
+##  Item statistics 
+##               n raw.r std.r r.cor r.drop mean   sd
+## pi_direkt    24  0.43  0.51 0.063 -0.040  3.6 0.65
+## pi_nonverbal 24  0.59  0.55 0.181  0.038  2.8 0.78
+## pi_zubewegen 24  0.80  0.78 0.636  0.356  3.1 0.80
+## 
+## Non missing response frequency for each item
+##                 1    2    3    4 miss
+## pi_direkt    0.00 0.08 0.21 0.71    0
+## pi_nonverbal 0.04 0.29 0.50 0.17    0
+## pi_zubewegen 0.04 0.12 0.50 0.33    0
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = stud.pv.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r S/N ase mean   sd median_r
+##       0.71      0.72    0.65      0.46 2.6 0.1  3.6 0.48     0.44
+## 
+##  lower alpha upper     95% confidence boundaries
+## 0.51 0.71 0.92 
+## 
+##  Reliability if an item is dropped:
+##             raw_alpha std.alpha G6(smc) average_r  S/N alpha se var.r med.r
+## ps_deutlich      0.61      0.62    0.44      0.44 1.60     0.16    NA  0.44
+## ps_impulse       0.76      0.76    0.61      0.61 3.08     0.10    NA  0.61
+## ps_klar          0.49      0.50    0.33      0.33 0.98     0.20    NA  0.33
+## 
+##  Item statistics 
+##              n raw.r std.r r.cor r.drop mean   sd
+## ps_deutlich 24  0.79  0.81  0.67   0.54  3.6 0.58
+## ps_impulse  24  0.76  0.74  0.50   0.43  3.5 0.66
+## ps_klar     24  0.84  0.85  0.77   0.64  3.6 0.58
+## 
+## Non missing response frequency for each item
+##                2    3    4 miss
+## ps_deutlich 0.04 0.29 0.67    0
+## ps_impulse  0.08 0.29 0.62    0
+## ps_klar     0.04 0.29 0.67    0
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in alpha(stud.p.wide[, -1]): Some items were negatively correlated with the total scale and probably 
+## should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Some items ( phb_stand ) were negatively correlated with the total scale and 
+## probably should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Reliability analysis   
+## Call: alpha(x = stud.p.wide[, -1])
+## 
+##   raw_alpha std.alpha G6(smc) average_r S/N   ase mean   sd median_r
+##       0.71      0.67    0.89      0.13   2 0.081  3.3 0.33     0.11
+## 
+##  lower alpha upper     95% confidence boundaries
+## 0.55 0.71 0.87 
+## 
+##  Reliability if an item is dropped:
+##                   raw_alpha std.alpha G6(smc) average_r S/N alpha se var.r
+## phb_alleangesehen      0.68      0.63    0.86     0.125 1.7    0.088 0.079
+## phb_augen              0.72      0.68    0.90     0.150 2.1    0.080 0.083
+## phb_blick              0.63      0.57    0.83     0.099 1.3    0.106 0.068
+## phb_gestik             0.65      0.60    0.86     0.110 1.5    0.100 0.072
+## phb_raum               0.70      0.65    0.87     0.135 1.9    0.081 0.078
+## phb_stand              0.74      0.73    0.90     0.182 2.7    0.073 0.066
+## phb_vorsichgeht        0.65      0.60    0.85     0.110 1.5    0.099 0.072
+## pi_direkt              0.72      0.69    0.90     0.155 2.2    0.078 0.078
+## pi_nonverbal           0.67      0.62    0.86     0.122 1.7    0.093 0.070
+## pi_zubewegen           0.70      0.66    0.87     0.141 2.0    0.082 0.079
+## ps_deutlich            0.72      0.67    0.89     0.147 2.1    0.077 0.078
+## ps_impulse             0.67      0.61    0.87     0.115 1.6    0.092 0.079
+## ps_klar                0.70      0.65    0.85     0.133 1.8    0.081 0.076
+##                   med.r
+## phb_alleangesehen 0.097
+## phb_augen         0.137
+## phb_blick         0.062
+## phb_gestik        0.101
+## phb_raum          0.101
+## phb_stand         0.181
+## phb_vorsichgeht   0.093
+## pi_direkt         0.152
+## pi_nonverbal      0.101
+## pi_zubewegen      0.093
+## ps_deutlich       0.152
+## ps_impulse        0.084
+## ps_klar           0.114
+## 
+##  Item statistics 
+##                    n raw.r std.r r.cor r.drop mean   sd
+## phb_alleangesehen 24  0.52  0.53  0.53  0.401  3.5 0.66
+## phb_augen         24  0.19  0.25  0.16  0.077  3.6 0.49
+## phb_blick         24  0.84  0.83  0.85  0.781  3.5 0.72
+## phb_gestik        24  0.72  0.70  0.69  0.606  3.0 0.86
+## phb_raum          24  0.49  0.42  0.40  0.295  2.1 0.97
+## phb_stand         24 -0.21 -0.11 -0.18 -0.308  3.7 0.46
+## phb_vorsichgeht   24  0.72  0.70  0.72  0.608  3.3 0.82
+## pi_direkt         24  0.22  0.19  0.12  0.075  3.6 0.65
+## pi_nonverbal      24  0.62  0.57  0.57  0.490  2.8 0.78
+## pi_zubewegen      24  0.41  0.35  0.33  0.244  3.1 0.80
+## ps_deutlich       24  0.20  0.28  0.23  0.066  3.6 0.58
+## ps_impulse        24  0.63  0.65  0.62  0.526  3.5 0.66
+## ps_klar           24  0.37  0.44  0.44  0.250  3.6 0.58
+## 
+## Non missing response frequency for each item
+##                      1    2    3    4 miss
+## phb_alleangesehen 0.00 0.08 0.29 0.62    0
+## phb_augen         0.00 0.00 0.38 0.62    0
+## phb_blick         0.04 0.00 0.42 0.54    0
+## phb_gestik        0.04 0.25 0.42 0.29    0
+## phb_raum          0.33 0.33 0.25 0.08    0
+## phb_stand         0.00 0.00 0.29 0.71    0
+## phb_vorsichgeht   0.04 0.08 0.38 0.50    0
+## pi_direkt         0.00 0.08 0.21 0.71    0
+## pi_nonverbal      0.04 0.29 0.50 0.17    0
+## pi_zubewegen      0.04 0.12 0.50 0.33    0
+## ps_deutlich       0.00 0.04 0.29 0.67    0
+## ps_impulse        0.00 0.08 0.29 0.62    0
+## ps_klar           0.00 0.04 0.29 0.67    0
+\end{verbatim}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:table-all-scales-students}Scale analysis for students' perspective}
+
+\small{
+
+\begin{tabular}{lllllll}
+\toprule
+scale & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis}\\
+\midrule
+Activation and support & 2.64 & 1.13 & 1.00 & 4.00 & -0.32 & 1.73\\
+Clarity and structuredness & 3.58 & 0.68 & 1.00 & 4.00 & -1.75 & 6.09\\
+Classroom management & 3.18 & 0.91 & 1.00 & 4.00 & -0.87 & 2.86\\
+Natural behaviour & 3.41 & 0.67 & 2.00 & 4.00 & -0.68 & 2.38\\
+Positive climate and motivation & 3.41 & 0.83 & 1.00 & 4.00 & -1.40 & 4.29\\
+Presence: posture/gaze & 3.24 & 0.89 & 1.00 & 4.00 & -1.05 & 3.31\\
+Presence: verbal and non-verbal intervention & 3.18 & 0.81 & 1.00 & 4.00 & -0.66 & 2.70\\
+Presence: voice & 3.60 & 0.60 & 2.00 & 4.00 & -1.18 & 3.36\\
 \bottomrule
@@
   Classroom management
-  \includegraphics{paper_1_supplement_new_table_files/figure-latex/classroom management line plots-1.pdf}
+  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Line Plots Classroom Management-1.pdf}
   \newpage
@@
 
+\begin{figure}
+\centering
 \includegraphics{paper_1_supplement_new_table_files/figure-latex/boxplot scales-1.pdf}
+\caption{(\#fig:boxplot scales)Boxplots and individual data for experts and novices}
+\end{figure}
 
@@
 
-The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz and Rädiker (2019)). The following coding scheme was developed:
+The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz \& Rädiker, 2019). The following coding scheme was developed:
 
@@
 
-We used R {[}Version 4.0.3; R Core Team (2019){]} and the R-packages \emph{\}dplyr} {[}@\}R-dplyr{]}, \emph{forcats} {[}Version 0.5.0; Wickham (2020a){]}, \emph{ggplot2} {[}Version 3.3.2; Wickham (2016){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{papayar} (Muschelli, 2016), \emph{psych} {[}Version 2.0.12; Revelle (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham, Hester, and Francois (2018){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.0.4; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.2; Wickham (2020b){]}, and \emph{tidyverse} {[}Version 1.3.0; Wickham et al.
+We used R {[}Version 4.0.3; R Core Team (2019){]} and the R-packages \emph{\}dplyr} {[}@\}R-dplyr{]}, \emph{forcats} {[}Version 0.5.0; Wickham (2020a){]}, \emph{ggplot2} {[}Version 3.3.2; Wickham (2016){]}, \emph{moments} {[}Version 0.14; Komsta and Novomestky (2015){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{papayar} (Muschelli, 2016), \emph{psych} {[}Version 2.0.12; Revelle (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham, Hester, and Francois (2018){]}, \emph{sjPlot} {[}Version 2.8.7; Lüdecke (2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.0.4; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.2; Wickham (2020b){]}, and \emph{tidyverse} {[}Version 1.3.0; Wickham et al.
 (2019){]} for all our analyses.
@@
 
+\leavevmode\hypertarget{ref-R-moments}{}%
+Komsta, L., \& Novomestky, F. (2015). \emph{Moments: Moments, cumulants, skewness, kurtosis and related tests}. Retrieved from \url{https://CRAN.R-project.org/package=moments}
+
 \leavevmode\hypertarget{ref-kounin2006techniken}{}%
@@
 \emph{Instructional Science}, \emph{44}(3), 197--203.
+
+\leavevmode\hypertarget{ref-R-sjPlot}{}%
+Lüdecke, D. (2021). \emph{sjPlot: Data visualization for statistics in social science}. Retrieved from \url{https://CRAN.R-project.org/package=sjPlot}
 

### 2021-02-22 paper_1/paper_1_supplement_new_table.Rmd
update alpha

@@
 # create a basic table (tibble) using tidyverse functions for teachers' self assessment 
+# adding alpha column
+
 teacher.scale.quest.table <- quest.raw.data %>% # select data

### 2021-02-23 paper_1/paper_1_supplement_new_table.Rmd
Update paper_1_supplement_new_table.Rmd

@@
 
+##############################################
 # calculate Cronbach's Alpha for each scale
-
 # activation & support
@@
 
-#presence: verbal and non-verbal intervention
-self.pvni.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pvni <- alpha(self.pvni.wide[,-1])
-self.alpha.pvni
-
 #presence: voice
@@
 
-############################################### 
+#presence: verbal/non-verbal intervention
+self.pvni.wide <- quest.raw.data %>%
+                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
+                          select(shortID, value) %>%
+                          group_by(shortID) %>%
+                          mutate(id=row_number()) %>%
+                          spread(shortID, value)
+
+self.alpha.pvni <- alpha(self.pvni.wide[,-1])
+self.alpha.pvni
+
 #Presence without subscales
@@
 
+# correlation between all presences' items
+cor.test(self.p.wide$phb_alleangesehen, self.p.wide$phb_alleangesehen, method=c("pearson"))
+
+##############################################
+
+# item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
+
+# activation & support
+tab_itemscale(self.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# classroom management
+tab_itemscale(self.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# clarity & structuredness
+tab_itemscale(self.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# natural behaviour
+tab_itemscale(self.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# postive clima and motivation
+tab_itemscale(self.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# presence without subscales
+tab_itemscale(self.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# presence: posture & gaze
+tab_itemscale(self.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# presence: voice
+tab_itemscale(self.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# presence: verbal/non-verbal intervention
+tab_itemscale(self.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
 ###############################################
 
-# item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
-
-###############################################
-
 # create a basic table (tibble) using tidyverse functions for teachers' self assessment
-# adding alpha column
 
@@
 
+###############################################
+
 # calculate Cronbach's Alpha for each scale of students' peception
@@
 
-############################################### 
 #Presence without subscales
@@
 ###############################################
+
+# item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
+
+# activation & support
+tab_itemscale(stud.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# classroom management
+tab_itemscale(stud.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# clarity & structuredness
+tab_itemscale(stud.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# natural behaviour
+tab_itemscale(stud.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# positive clima and motivation
+tab_itemscale(stud.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# presence without subscales
+tab_itemscale(stud.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# presence: posture & gaze
+tab_itemscale(stud.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# presence: voice
+tab_itemscale(stud.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# presence: verbal/non-verbal intervention
+tab_itemscale(stud.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
 

### 2021-02-24 paper_1/paper_1_supplement_new_table.Rmd
scale analysis + correlation presence items

@@
 
-# correlation between all presences' items
-cor.test(self.p.wide$phb_alleangesehen, self.p.wide$phb_alleangesehen, method=c("pearson"))
+##############################################
+# #####correlation between all presences' items
+# SELF-ASSESSMENT
+# install.packages("Hmisc")
+library("Hmisc")
+
+# function to format the correlation matrix
+flattenCorrMatrix <- function(cormat, pmat) {
+  ut <- upper.tri(cormat)
+  data.frame(
+    row = rownames(cormat)[row(cormat)[ut]],
+    column = rownames(cormat)[col(cormat)[ut]],
+    cor  =(cormat)[ut],
+    p = pmat[ut]
+    )
+}
+
+res1.self<-rcorr(as.matrix(self.p.wide[,-1]))
+
+flattenCorrMatrix(res2$r, res2$P)
+
+res2.self<-flattenCorrMatrix(res2$r, res2$P)
+
+# Visualization correlation matrix
+# Use corrplot() function: Draw a correlogram
+
+# install.packages("corrplot")
+library("corrplot")
+
+# Insignificant correlation are crossed
+corrplot(res1.self$r, type="upper", order="hclust",
+         p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
+# Insignificant correlations are leaved blank
+corrplot(res1.self$r, type="upper", order="hclust",
+         p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
 
@@
 stud.alpha.p
-
+##############################################
+# #####correlation between all presences' items
+# SELF-ASSESSMENT
+# install.packages("Hmisc")
+library("Hmisc")
+
+# function to format the correlation matrix
+flattenCorrMatrix <- function(cormat, pmat) {
+  ut <- upper.tri(cormat)
+  data.frame(
+    row = rownames(cormat)[row(cormat)[ut]],
+    column = rownames(cormat)[col(cormat)[ut]],
+    cor  =(cormat)[ut],
+    p = pmat[ut]
+    )
+}
+
+res1.stud<-rcorr(as.matrix(stud.p.wide[,-1]))
+
+flattenCorrMatrix(res1.stud$r, res1.stud$P)
+
+res2.stud<-flattenCorrMatrix(res1.stud$r, res1.stud$P)
+
+# Visualization correlation matrix
+# Use corrplot() function: Draw a correlogram
+
+# install.packages("corrplot")
+library("corrplot")
+
+# Insignificant correlation are crossed
+corrplot(res1.stud$r, type="upper", order="hclust",
+         p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
+# Insignificant correlations are leaved blank
+corrplot(res1.stud$r, type="upper", order="hclust",
+         p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
 ###############################################

### 2021-02-25 paper_1/paper_1_supplement_new_table.Rmd
update item analysis

@@
 
-res1.self<-rcorr(as.matrix(self.p.wide[,-1]))
-
-flattenCorrMatrix(res2$r, res2$P)
-
-res2.self<-flattenCorrMatrix(res2$r, res2$P)
+res1.self<-cor(self.p.wide[,-1])
+
+rm(res1.self)
+flattenCorrMatrix(res1.self$r, res1.self$P)
+
+res1.self<-flattenCorrMatrix(res1.self$r, res1.self$P)
+
+res2 <- rcorr(as.matrix(res1.self))
+res2
 
@@
 
-res1.stud<-rcorr(as.matrix(stud.p.wide[,-1]))
-
-flattenCorrMatrix(res1.stud$r, res1.stud$P)
-
-res2.stud<-flattenCorrMatrix(res1.stud$r, res1.stud$P)
+res1.stud<-cor(stud.p.wide[,-1])
+
+# res1.stud<-rcorr(as.matrix(stud.p.wide[,-1]))
+# 
+# flattenCorrMatrix(res1.stud$r, res1.stud$P)
+# 
+# res2.stud<-flattenCorrMatrix(res1.stud$r, res1.stud$P)
 
@@
 
-# Insignificant correlation are crossed
-corrplot(res1.stud$r, type="upper", order="hclust",
-         p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
-# Insignificant correlations are leaved blank
-corrplot(res1.stud$r, type="upper", order="hclust",
-         p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
-###############################################
+# # Insignificant correlation are crossed
+# corrplot(res1.stud$r, type="upper", order="hclust",
+#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
+# # Insignificant correlations are leaved blank
+# corrplot(res1.stud$r, type="upper", order="hclust",
+#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
+# ###############################################
 

### 2021-02-26 paper_1/paper_1_supplement_new_table.Rmd
update scale item analysis

--- 2021-02-23 paper_1/paper_1_supplement_new_table.Rmd
@@
 ##############################################
+
 # calculate Cronbach's Alpha for each scale
@@
 self.alpha.as <- alpha(self.as.wide[,-1])
-self.alpha.as
 
@@
 self.alpha.cs <- alpha(self.cs.wide[,-1])
-self.alpha.cs
 
@@
 self.alpha.cm <- alpha(self.cm.wide[,-1])
-self.alpha.cm
 
@@
 self.alpha.nb <- alpha(self.nb.wide[,-1])
-self.alpha.nb
 
@@
 self.alpha.pcm <- alpha(self.pcm.wide[,-1])
-self.alpha.pcm
 
@@
 self.alpha.ppg <- alpha(self.ppg.wide[,-1])
-self.alpha.ppg
 
@@
 self.alpha.pv <- alpha(self.pv.wide[,-1])
-self.alpha.pv
 
@@
 self.alpha.pvni <- alpha(self.pvni.wide[,-1])
-self.alpha.pvni
 
@@
 self.alpha.p <- alpha(self.p.wide[,-1])
-self.alpha.p
-
-# correlation between all presences' items
-cor.test(self.p.wide$phb_alleangesehen, self.p.wide$phb_alleangesehen, method=c("pearson"))
 
@@
 
-# item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
-
-# activation & support
-tab_itemscale(self.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-# classroom management
-tab_itemscale(self.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-# clarity & structuredness
-tab_itemscale(self.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-# natural behaviour
-tab_itemscale(self.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-# postive clima and motivation
-tab_itemscale(self.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-# presence without subscales
-tab_itemscale(self.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-# presence: posture & gaze
-tab_itemscale(self.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# presence: voice
-tab_itemscale(self.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# presence: verbal/non-verbal intervention
-tab_itemscale(self.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
+# 
+# # activation & support
+# tab_itemscale(self.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# 
+# # classroom management
+# tab_itemscale(self.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# 
+# # clarity & structuredness
+# tab_itemscale(self.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# 
+# # natural behaviour
+# tab_itemscale(self.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# 
+# # postive clima and motivation
+# tab_itemscale(self.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# 
+# # presence without subscales
+# tab_itemscale(self.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# 
+# # presence: posture & gaze
+# tab_itemscale(self.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# # presence: voice
+# tab_itemscale(self.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# # presence: verbal/non-verbal intervention
+# tab_itemscale(self.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+##############################################
+
+# add alphas to excel table 
+# read in new data 
+quest.raw.data.alpha <- read.table("./data/short_questionnaire_data_260221_alpha.txt", dec=",", sep="\t", header=T)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+quest.raw.data.alpha <- quest.raw.data.alpha %>%  mutate(alpha = as.numeric(alpha))
+
+##############################################
+
+# #####correlation between all presences' items
+# SELF-ASSESSMENT
+# install.packages("Hmisc")
+# library("Hmisc")
+
+# function cr() to format the correlation matrix
+res1.self<-cor(self.p.wide[,-1])
+
+# Visualization correlation matrix
+# Use corrplot() function: Draw a correlogram
+
+# # install.packages("corrplot")
+# library("corrplot")
+# 
+# # Insignificant correlation are crossed
+# corrplot(res1.self$r, type="upper", order="hclust",
+#          p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
+# # Insignificant correlations are leaved blank
+# corrplot(res1.self$r, type="upper", order="hclust",
+#          p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
 
@@
 # create a basic table (tibble) using tidyverse functions for teachers' self assessment 
-
-teacher.scale.quest.table <- quest.raw.data %>% # select data
+# Change Number of Digits in Global R Options to reduce the number of digits after the decimal point to two
+options(digits = 2)
+
+teacher.scale.quest.table <- quest.raw.data.alpha %>% # select data
   filter(perspective == "self-assessment")%>%
@@
             "Skewness" = skewness(value),
-            "Kurtosis" = kurtosis(value))
-
-view(teacher.scale.quest.table)
+            "Kurtosis" = kurtosis(value),
+            "Cronbach's α" = mean(alpha))
 
@@
 stud.alpha.as <- alpha(stud.as.wide[,-1])
-stud.alpha.as
 
@@
 stud.alpha.cs <- alpha(stud.cs.wide[,-1])
-stud.alpha.cs
 
@@
 stud.alpha.cm <- alpha(stud.cm.wide[,-1])
-stud.alpha.cm
 
@@
 stud.alpha.nb <- alpha(stud.nb.wide[,-1])
-stud.alpha.nb
 
@@
 stud.alpha.pcm <- alpha(stud.pcm.wide[,-1])
-stud.alpha.pcm
 
@@
 stud.alpha.ppg <- alpha(stud.ppg.wide[,-1])
-stud.alpha.ppg
 
@@
 stud.alpha.pvni <- alpha(stud.pvni.wide[,-1])
-stud.alpha.pvni
 
@@
 stud.alpha.pv <- alpha(stud.pv.wide[,-1])
-stud.alpha.pv
 
@@
 stud.alpha.p <- alpha(stud.p.wide[,-1])
-stud.alpha.p
-
-###############################################
-
-# item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
-
-# activation & support
-tab_itemscale(stud.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-# classroom management
-tab_itemscale(stud.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-# clarity & structuredness
-tab_itemscale(stud.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-# natural behaviour
-tab_itemscale(stud.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-# positive clima and motivation
-tab_itemscale(stud.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-# presence without subscales
-tab_itemscale(stud.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-# presence: posture & gaze
-tab_itemscale(stud.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# presence: voice
-tab_itemscale(stud.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# presence: verbal/non-verbal intervention
-tab_itemscale(stud.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# ###############################################
+
+# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
+# 
+# # activation & support
+# tab_itemscale(stud.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# 
+# # classroom management
+# tab_itemscale(stud.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# 
+# # clarity & structuredness
+# tab_itemscale(stud.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# 
+# # natural behaviour
+# tab_itemscale(stud.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# 
+# # positive clima and motivation
+# tab_itemscale(stud.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# 
+# # presence without subscales
+# tab_itemscale(stud.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# 
+# # presence: posture & gaze
+# tab_itemscale(stud.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# # presence: voice
+# tab_itemscale(stud.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# # presence: verbal/non-verbal intervention
+# tab_itemscale(stud.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+##############################################
+# #####correlation between all presences' items
+# SELF-ASSESSMENT
+# install.packages("Hmisc")
+library("Hmisc")
+
+# # function to format the correlation matrix
+# flattenCorrMatrix <- function(cormat, pmat) {
+#   ut <- upper.tri(cormat)
+#   data.frame(
+#     row = rownames(cormat)[row(cormat)[ut]],
+#     column = rownames(cormat)[col(cormat)[ut]],
+#     cor  =(cormat)[ut],
+#     p = pmat[ut]
+#     )
+# }
+# 
+# res1.stud<-cor(stud.p.wide[,-1])
+
+# res1.stud<-rcorr(as.matrix(stud.p.wide[,-1]))
+# 
+# flattenCorrMatrix(res1.stud$r, res1.stud$P)
+# 
+# res2.stud<-flattenCorrMatrix(res1.stud$r, res1.stud$P)
+
+# Visualization correlation matrix
+# Use corrplot() function: Draw a correlogram
+
+# install.packages("corrplot")
+library("corrplot")
+
+# # Insignificant correlation are crossed
+# corrplot(res1.stud$r, type="upper", order="hclust",
+#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
+# # Insignificant correlations are leaved blank
+# corrplot(res1.stud$r, type="upper", order="hclust",
+#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
+
+##############################################
+
+# add alphas to excel table 
+# read in new data 
+quest.raw.data.alpha <- read.table("./data/short_questionnaire_data_260221_alpha.txt", dec=",", sep="\t", header=T)
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+quest.raw.data.alpha <- quest.raw.data.alpha %>%  mutate(alpha = as.numeric(alpha))
+
+##############################################
 
 # create a basic table (tibble) using tidyverse functions for teacher self assessment 
-student.scale.quest.table <- quest.raw.data %>% # select data
+student.scale.quest.table <- quest.raw.data.alpha %>% # select data
   filter(perspective == "student")%>%
@@
             "Skewness" = skewness(value),
-            "Kurtosis" = kurtosis(value))
-
-view(student.scale.quest.table)
+            "Kurtosis" = kurtosis(value),
+            "Cronbach's α" = mean(alpha))
 

### 2021-02-26 paper_1/paper_1_supplement_new_table.tex
update scale item analysis

--- 2021-02-15 paper_1/paper_1_supplement_new_table.tex
@@
 
-{\centering \includegraphics{./pictures/datacollection}
+{\centering \includegraphics[width=5.94in]{./pictures/datacollection}
 
@@
 
-The table provides an overview over the mean, the range and standard deviation of all scales.
+Table \ref{tab:table-all-scales-self-assessment} provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness \& Kurtosis of all scales for the teachers' self-assessment.
+
+\begin{verbatim}
+## Warning in alpha(self.cs.wide[, -1]): Some items were negatively correlated with the total scale and probably 
+## should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Some items ( ks_sichtbar ) were negatively correlated with the total scale and 
+## probably should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in sqrt(Vtc): NaNs wurden erzeugt
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in cor.smooth(r): Matrix was not positive definite, smoothing was done
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in alpha(self.pvni.wide[, -1]): Some items were negatively correlated with the total scale and probably 
+## should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Some items ( pi_nonverbal ) were negatively correlated with the total scale and 
+## probably should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in sqrt(Vtc): NaNs wurden erzeugt
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in cor.smooth(r): Matrix was not positive definite, smoothing was done
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in alpha(self.p.wide[, -1]): Some items were negatively correlated with the total scale and probably 
+## should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Some items ( pi_nonverbal ) were negatively correlated with the total scale and 
+## probably should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+
+## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
+\end{verbatim}
 
@@
 
-\begin{tabular}{lllll}
+\begin{tabular}{llllllll}
 \toprule
-scale & \multicolumn{1}{c}{M scale} & \multicolumn{1}{c}{SD scale} & \multicolumn{1}{c}{min scale} & \multicolumn{1}{c}{max sclae}\\
+scale & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Cronbach's a}\\
 \midrule
-Activation and support & 2.45 & 1.37 & 0.00 & 4.00\\
-Clarity and structuredness & 3.41 & 0.81 & 1.00 & 4.00\\
-Classroom management & 2.97 & 0.94 & 1.00 & 4.00\\
-Natural behaviour & 3.28 & 0.74 & 2.00 & 4.00\\
-Positive climate and motivation & 3.27 & 0.89 & 0.00 & 4.00\\
-Presence: posture/gaze & 3.10 & 0.96 & 0.00 & 4.00\\
-Presence: verbal and non-verbal intervention & 3.07 & 0.82 & 1.00 & 4.00\\
-Presence: voice & 3.40 & 0.72 & 2.00 & 4.00\\
+Activation and support & 2.46 & 1.14 & 1 & 4 & 0.10 & 1.65 & 0.85\\
+Clarity and structuredness & 2.81 & 0.91 & 1 & 4 & -0.17 & 2.17 & -0.76\\
+Classroom management & 2.44 & 0.88 & 1 & 4 & 0.19 & 2.38 & 0.83\\
+Natural behaviour & 2.83 & 0.76 & 2 & 4 & 0.28 & 1.84 & 0.90\\
+Positive climate and motivation & 2.85 & 0.87 & 1 & 4 & -0.49 & 2.65 & 0.78\\
+Presence: posture/gaze & 2.70 & 1.01 & 1 & 4 & -0.44 & 2.15 & 0.85\\
+Presence: verbal and non-verbal intervention & 2.75 & 0.79 & 1 & 4 & -0.07 & 2.48 & -0.75\\
+Presence: voice & 2.79 & 0.72 & 2 & 4 & 0.32 & 2.03 & 0.77\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+Table \ref{tab:table-all-scales-students} provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness \& Kurtosis of all scales for the students' perception of the teacher's behaviour in class.
+
+\begin{verbatim}
+## Warning in alpha(stud.ppg.wide[, -1]): Some items were negatively correlated with the total scale and probably 
+## should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Some items ( phb_stand ) were negatively correlated with the total scale and 
+## probably should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in alpha(stud.pvni.wide[, -1]): Some items were negatively correlated with the total scale and probably 
+## should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Some items ( pi_direkt ) were negatively correlated with the total scale and 
+## probably should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in alpha(stud.p.wide[, -1]): Some items were negatively correlated with the total scale and probably 
+## should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{verbatim}
+## Some items ( phb_stand ) were negatively correlated with the total scale and 
+## probably should be reversed.  
+## To do this, run the function again with the 'check.keys=TRUE' option
+\end{verbatim}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:table-all-scales-students}Scale analysis for students' perspective}
+
+\small{
+
+\begin{tabular}{llllllll}
+\toprule
+scale & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Cronbach's a}\\
+\midrule
+Activation and support & 2.64 & 1.13 & 1 & 4 & -0.32 & 1.73 & 0.48\\
+Clarity and structuredness & 3.58 & 0.68 & 1 & 4 & -1.75 & 6.09 & 0.62\\
+Classroom management & 3.18 & 0.91 & 1 & 4 & -0.87 & 2.86 & 0.75\\
+Natural behaviour & 3.43 & 0.67 & 2 & 4 & -0.74 & 2.46 & 0.85\\
+Positive climate and motivation & 3.41 & 0.83 & 1 & 4 & -1.40 & 4.29 & 0.82\\
+Presence: posture/gaze & 3.24 & 0.89 & 1 & 4 & -1.05 & 3.31 & 0.59\\
+Presence: verbal and non-verbal intervention & 3.18 & 0.81 & 1 & 4 & -0.66 & 2.70 & 0.20\\
+Presence: voice & 3.60 & 0.60 & 2 & 4 & -1.18 & 3.36 & 0.71\\
 \bottomrule
@@
 
-{\centering \includegraphics{./pictures/presenceposturegaze}
+{\centering \includegraphics[width=5.33in]{./pictures/presenceposturegaze}
 
@@
 
-{\centering \includegraphics{./pictures/presencevoice}
+{\centering \includegraphics[width=5.33in]{./pictures/presencevoice}
 
@@
 
-{\centering \includegraphics{./pictures/presenceverbalnonverbalintervention}
+{\centering \includegraphics[width=5.33in]{./pictures/presenceverbalnonverbalintervention}
 

### 2021-03-01 paper_1/paper_1_supplement_new_table.Rmd
update GRI (calib - lesson + head - intervention)

@@
   group_by(scale) %>%
-  summarise("M" = round(mean(value), 2),
+  summarise("N items" = n_distinct(shortID),
+            "M" = round(mean(value), 2),
             "SD" = round(sd(value), 2),
@@
 
+```{r Calib end to lession start TOI, echo = FALSE}
+
+# prepare data (selected from questionnaire data)
+et.calib.lesson.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_calib_end_lesson_start.tsv", dec=",", sep="\t", header=T)
+
+# converting integer to numeric
+et.calib.lesson.data <- et.calib.lesson.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
+                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
+                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
+                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
+                                       )
+options(digits = 2)
+
+# calculate the GRI 
+# create a basic table (tibble) using tidyverse functions
+et.calib.lesson.table <- et.calib.lesson.data %>%
+  group_by(Participant, Variable1) %>%
+  summarise("Fixation Number" = Number_of_whole_fixations,
+            "Fixation Duration" = Total_duration_of_whole_fixations,
+            "M Duration Fixation" = Average_duration_of_whole_fixations,
+            "TOI" = Duration_of_interval,
+            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
+
+# format and insert table in manuscript
+apa_table(
+  et.calib.lesson.table,
+  caption = "Number and Duration (in msec) of Fixations Calibration End to Lesson Start",
+  # note = "Write Note here", 
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  )
+
+```
+
+```{r Disturbance "head on table" to first intervention, echo = FALSE}
+
+# prepare data (selected from questionnaire data)
+et.distub.head.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_head_on_table_session1.tsv", dec=",", sep="\t", header=T)
+
+# converting integer to numeric
+et.distub.head.data <- et.distub.head.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
+                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
+                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
+                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
+                                       )
+options(digits = 2)
+
+# calculate the GRI 
+# create a basic table (tibble) using tidyverse functions
+et.distub.head.table <- et.distub.head.data %>%
+  group_by(Participant, Variable1) %>%
+  summarise("Fixation Number" = Number_of_whole_fixations,
+            "Fixation Duration" = Total_duration_of_whole_fixations,
+            "M Duration Fixation" = Average_duration_of_whole_fixations,
+            "TOI" = Duration_of_interval,
+            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
+view(et.distub.head.data)
+
+# format and insert table in manuscript
+apa_table(
+  et.distub.head.table,
+  caption = "Number and Duration (in msec) of Fixations for Disturbance 'head on table' to first intervention",
+  # note = "Write Note here", 
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  )
+
+```
+
 #########################################

### 2021-03-01 paper_1/paper_1_supplement_new_table.tex
update GRI (calib - lesson + head - intervention)

@@
 
-\begin{tabular}{llllllll}
+\begin{tabular}{lllllllll}
 \toprule
-scale & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Cronbach's a}\\
+scale & \multicolumn{1}{c}{N items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Cronbach's a}\\
 \midrule
-Activation and support & 2.46 & 1.14 & 1 & 4 & 0.10 & 1.65 & 0.85\\
-Clarity and structuredness & 2.81 & 0.91 & 1 & 4 & -0.17 & 2.17 & -0.76\\
-Classroom management & 2.44 & 0.88 & 1 & 4 & 0.19 & 2.38 & 0.83\\
-Natural behaviour & 2.83 & 0.76 & 2 & 4 & 0.28 & 1.84 & 0.90\\
-Positive climate and motivation & 2.85 & 0.87 & 1 & 4 & -0.49 & 2.65 & 0.78\\
-Presence: posture/gaze & 2.70 & 1.01 & 1 & 4 & -0.44 & 2.15 & 0.85\\
-Presence: verbal and non-verbal intervention & 2.75 & 0.79 & 1 & 4 & -0.07 & 2.48 & -0.75\\
-Presence: voice & 2.79 & 0.72 & 2 & 4 & 0.32 & 2.03 & 0.77\\
+Activation and support & 3 & 2.46 & 1.14 & 1 & 4 & 0.10 & 1.65 & 0.85\\
+Clarity and structuredness & 2 & 2.81 & 0.91 & 1 & 4 & -0.17 & 2.17 & -0.76\\
+Classroom management & 4 & 2.44 & 0.88 & 1 & 4 & 0.19 & 2.38 & 0.83\\
+Natural behaviour & 3 & 2.83 & 0.76 & 2 & 4 & 0.28 & 1.84 & 0.90\\
+Positive climate and motivation & 6 & 2.85 & 0.87 & 1 & 4 & -0.49 & 2.65 & 0.78\\
+Presence: posture/gaze & 7 & 2.70 & 1.01 & 1 & 4 & -0.44 & 2.15 & 0.85\\
+Presence: verbal and non-verbal intervention & 3 & 2.75 & 0.79 & 1 & 4 & -0.07 & 2.48 & -0.75\\
+Presence: voice & 3 & 2.79 & 0.72 & 2 & 4 & 0.32 & 2.03 & 0.77\\
 \bottomrule
@@
 
-\begin{tabular}{llllllll}
+\begin{tabular}{lllllllll}
 \toprule
-scale & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Cronbach's a}\\
+scale & \multicolumn{1}{c}{N items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Cronbach's a}\\
 \midrule
-Activation and support & 2.64 & 1.13 & 1 & 4 & -0.32 & 1.73 & 0.48\\
-Clarity and structuredness & 3.58 & 0.68 & 1 & 4 & -1.75 & 6.09 & 0.62\\
-Classroom management & 3.18 & 0.91 & 1 & 4 & -0.87 & 2.86 & 0.75\\
-Natural behaviour & 3.43 & 0.67 & 2 & 4 & -0.74 & 2.46 & 0.85\\
-Positive climate and motivation & 3.41 & 0.83 & 1 & 4 & -1.40 & 4.29 & 0.82\\
-Presence: posture/gaze & 3.24 & 0.89 & 1 & 4 & -1.05 & 3.31 & 0.59\\
-Presence: verbal and non-verbal intervention & 3.18 & 0.81 & 1 & 4 & -0.66 & 2.70 & 0.20\\
-Presence: voice & 3.60 & 0.60 & 2 & 4 & -1.18 & 3.36 & 0.71\\
+Activation and support & 3 & 2.64 & 1.13 & 1 & 4 & -0.32 & 1.73 & 0.48\\
+Clarity and structuredness & 2 & 3.58 & 0.68 & 1 & 4 & -1.75 & 6.09 & 0.62\\
+Classroom management & 4 & 3.18 & 0.91 & 1 & 4 & -0.87 & 2.86 & 0.75\\
+Natural behaviour & 3 & 3.43 & 0.67 & 2 & 4 & -0.74 & 2.46 & 0.85\\
+Positive climate and motivation & 6 & 3.41 & 0.83 & 1 & 4 & -1.40 & 4.29 & 0.82\\
+Presence: posture/gaze & 7 & 3.24 & 0.89 & 1 & 4 & -1.05 & 3.31 & 0.59\\
+Presence: verbal and non-verbal intervention & 3 & 3.18 & 0.81 & 1 & 4 & -0.66 & 2.70 & 0.20\\
+Presence: voice & 3 & 3.60 & 0.60 & 2 & 4 & -1.18 & 3.36 & 0.71\\
 \bottomrule
@@
 
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:Calib end to lession start TOI}Number and Duration (in msec) of Fixations Calibration End to Lesson Start}
+
+\scriptsize{
+
+\begin{tabular}{lllllll}
+\toprule
+Participant & \multicolumn{1}{c}{Variable1} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
+\midrule
+01\_01\_D & Expert & 101.00 & 38,177.00 & 378.00 & 53,133.00 & 3.74\\
+01\_02\_A & Expert & 27.00 & 6,736.00 & 249.00 & 15,502.00 & 9.22\\
+01\_03\_B & Novice & 57.00 & 36,378.00 & 638.00 & 58,763.00 & 11.19\\
+01\_04\_C & Novice & 65.00 & 22,387.00 & 344.00 & 39,235.00 & 5.29\\
+02\_01\_A & Novice & 14.00 & 2,619.00 & 187.00 & 30,195.00 & 13.36\\
+02\_02\_B & Novice & 46.00 & 15,851.00 & 345.00 & 30,297.00 & 7.50\\
+02\_03\_C & Novice & 86.00 & 27,643.00 & 321.00 & 42,603.00 & 3.73\\
+02\_04\_D & Novice & 53.00 & 27,783.00 & 524.00 & 36,204.00 & 9.89\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 \hypertarget{data-analysis}{%
@@
 
-We used R {[}Version 4.0.3; R Core Team (2019){]} and the R-packages \emph{\}dplyr} {[}@\}R-dplyr{]}, \emph{forcats} {[}Version 0.5.0; Wickham (2020a){]}, \emph{ggplot2} {[}Version 3.3.2; Wickham (2016){]}, \emph{moments} {[}Version 0.14; Komsta and Novomestky (2015){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{papayar} (Muschelli, 2016), \emph{psych} {[}Version 2.0.12; Revelle (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham, Hester, and Francois (2018){]}, \emph{sjPlot} {[}Version 2.8.7; Lüdecke (2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.0.4; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.2; Wickham (2020b){]}, and \emph{tidyverse} {[}Version 1.3.0; Wickham et al.
+We used R {[}Version 4.0.3; R Core Team (2019){]} and the R-packages \emph{\}dplyr} {[}@\}R-dplyr{]}, \emph{corrplot2017} (Wei \& Simko, 2017), \emph{forcats} {[}Version 0.5.0; Wickham (2020a){]}, \emph{Formula} {[}Version 1.2.4; Zeileis and Croissant (2010){]}, \emph{ggplot2} {[}Version 3.3.2; Wickham (2016){]}, \emph{Hmisc} {[}Version 4.4.2; Harrell Jr, Charles Dupont, and others.
+(2020){]}, \emph{lattice} {[}Version 0.20.41; Sarkar (2008){]}, \emph{moments} {[}Version 0.14; Komsta and Novomestky (2015){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{papayar} (Muschelli, 2016), \emph{psych} {[}Version 2.0.12; Revelle (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham, Hester, and Francois (2018){]}, \emph{sjPlot} {[}Version 2.8.7; Lüdecke (2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{survival} {[}Version 3.2.7; Terry M.
+Therneau and Patricia M.
+Grambsch (2000){]}, \emph{tibble} {[}Version 3.0.4; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.2; Wickham (2020b){]}, and \emph{tidyverse} {[}Version 1.3.0; Wickham et al.
 (2019){]} for all our analyses.
@@
 
+\leavevmode\hypertarget{ref-R-Hmisc}{}%
+Harrell Jr, F. E., Charles Dupont, with contributions from, \& others., many. (2020). \emph{Hmisc: Harrell miscellaneous}. Retrieved from \url{https://CRAN.R-project.org/package=Hmisc}
+
 \leavevmode\hypertarget{ref-helmke2014unterrichtsdiagnostik}{}%
@@
 
+\leavevmode\hypertarget{ref-R-lattice}{}%
+Sarkar, D. (2008). \emph{Lattice: Multivariate data visualization with r}. New York: Springer. Retrieved from \url{http://lmdvr.r-forge.r-project.org}
+
 \leavevmode\hypertarget{ref-stuermer2017eye}{}%
@@
 \emph{Zeitschrift f{ü}r Erziehungswissenschaft}, \emph{20}(1), 75--92.
+
+\leavevmode\hypertarget{ref-R-survival-book}{}%
+Terry M. Therneau, \& Patricia M. Grambsch. (2000). \emph{Modeling survival data: Extending the {C}ox model}. New York: Springer.
+
+\leavevmode\hypertarget{ref-R-corrplot2017}{}%
+Wei, T., \& Simko, V. (2017). \emph{R package "corrplot": Visualization of a correlation matrix}. Retrieved from \url{https://github.com/taiyun/corrplot}
 
@@
 
+\leavevmode\hypertarget{ref-R-Formula}{}%
+Zeileis, A., \& Croissant, Y.
+(2010).
+Extended model formulas in {R}: Multiple parts and multiple responses.
+\emph{Journal of Statistical Software}, \emph{34}(1), 1--13.
+\url{https://doi.org/10.18637/jss.v034.i01}
+
 \end{CSLReferences}

### 2021-03-03 paper_1/paper_1_supplement_new_table.Rmd
update paper supplement

@@
   demo.quest.table,
-  caption = "Demographic Informationand and Teaching Experience",
+  caption = "Demographic Information and Teaching Experience",
   # note = "Write Note here", 
@@
 
-```{r table-all-scales-self-assessment, echo = FALSE}
+```{r table-all-scales-self-assessment, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
 )
@@
 
-```{r table-all-scales-students, echo = FALSE}
+```{r table-all-scales-students, echo=FALSE, message=FALSE, warning=FALSE}
 

### 2021-03-03 paper_1/paper_1_supplement_new_table.tex
update paper supplement

@@
 
-\caption{\label{tab:demographicspilottable}Demographic Informationand and Teaching Experience}
+\caption{\label{tab:demographicspilottable}Demographic Information and Teaching Experience}
 
@@
 \begin{verbatim}
-## Warning in alpha(self.cs.wide[, -1]): Some items were negatively correlated with the total scale and probably 
-## should be reversed.  
-## To do this, run the function again with the 'check.keys=TRUE' option
-\end{verbatim}
-
-\begin{verbatim}
 ## Some items ( ks_sichtbar ) were negatively correlated with the total scale and 
 ## probably should be reversed.  
-## To do this, run the function again with the 'check.keys=TRUE' option
-\end{verbatim}
-
-\begin{verbatim}
-## Warning in sqrt(Vtc): NaNs wurden erzeugt
-\end{verbatim}
-
-\begin{verbatim}
-## Warning in cor.smooth(r): Matrix was not positive definite, smoothing was done
-\end{verbatim}
-
-\begin{verbatim}
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-\end{verbatim}
-
-\begin{verbatim}
-## Warning in alpha(self.pvni.wide[, -1]): Some items were negatively correlated with the total scale and probably 
-## should be reversed.  
 ## To do this, run the function again with the 'check.keys=TRUE' option
@@
 \begin{verbatim}
-## Warning in sqrt(Vtc): NaNs wurden erzeugt
-\end{verbatim}
-
-\begin{verbatim}
-## Warning in cor.smooth(r): Matrix was not positive definite, smoothing was done
-\end{verbatim}
-
-\begin{verbatim}
-## Warning in alpha(self.p.wide[, -1]): Some items were negatively correlated with the total scale and probably 
-## should be reversed.  
-## To do this, run the function again with the 'check.keys=TRUE' option
-\end{verbatim}
-
-\begin{verbatim}
 ## Some items ( pi_nonverbal ) were negatively correlated with the total scale and 
@@
 ## To do this, run the function again with the 'check.keys=TRUE' option
-\end{verbatim}
-
-\begin{verbatim}
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-\end{verbatim}
-
-\begin{verbatim}
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
-
-## Warning in cor.smooth(R): Matrix was not positive definite, smoothing was done
 \end{verbatim}
@@
 
-\small{
+\tiny{
 
@@
 \begin{verbatim}
-## Warning in alpha(stud.ppg.wide[, -1]): Some items were negatively correlated with the total scale and probably 
-## should be reversed.  
-## To do this, run the function again with the 'check.keys=TRUE' option
-\end{verbatim}
-
-\begin{verbatim}
 ## Some items ( phb_stand ) were negatively correlated with the total scale and 
@@
 \begin{verbatim}
-## Warning in alpha(stud.pvni.wide[, -1]): Some items were negatively correlated with the total scale and probably 
-## should be reversed.  
-## To do this, run the function again with the 'check.keys=TRUE' option
-\end{verbatim}
-
-\begin{verbatim}
 ## Some items ( pi_direkt ) were negatively correlated with the total scale and 
 ## probably should be reversed.  
-## To do this, run the function again with the 'check.keys=TRUE' option
-\end{verbatim}
-
-\begin{verbatim}
-## Warning in alpha(stud.p.wide[, -1]): Some items were negatively correlated with the total scale and probably 
-## should be reversed.  
 ## To do this, run the function again with the 'check.keys=TRUE' option
@@
 
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:Disturbance "head on table" to first intervention}Number and Duration (in msec) of Fixations for Disturbance 'head on table' to first intervention}
+
+\scriptsize{
+
+\begin{tabular}{lllllll}
+\toprule
+Participant & \multicolumn{1}{c}{Variable1} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
+\midrule
+01\_01\_D & Expert & 3.00 & 2,079.00 & 693.00 & 5,735.00 & 231.00\\
+01\_02\_A & Expert & 7.00 & 2,778.00 & 397.00 & 8,454.00 & 56.71\\
+01\_03\_B & Novice & 1.00 & 460.00 & 460.00 & 3,493.00 & 460.00\\
+01\_04\_C & Novice & 29.00 & 12,653.00 & 436.00 & 16,245.00 & 15.03\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 \hypertarget{data-analysis}{%

### 2021-03-04 paper_1/AOI_plots.R
Create AOI_plots.R

@@ -1,0 +1,23 @@
+
+if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
+if (!require(papaja)) install.packages('papaja'); library(papaja)
+if (!require(psych)) install.packages('psych'); library(psych) # stats
+if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
+if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
+
+# prepare data (selected from AOI data)
+et.raw.data<-read.table("./data/Aperol_pilot_glasses_AOI.txt", dec=",", sep="\t", header=T) 
+
+# create a basic table (tibble) using tidyverse functions for all disruptions 
+# Change Number of Digits in Global R Options to reduce the number of digits after the decimal point to two
+options(digits = 2)              
+
+et.table <- et.raw.data %>% # select data
+  group_by(Type.of.disruption, Group) %>%
+  summarise("Total Duration of Fixations" = Total.duration.of.fixation.in.AOI..sec.,
+            "Average Duration of Fixations" = Average.duration.of.fixation.in.AOI..sec.,
+            "Number of Fixations" = Number.of.fixations.in.AOI)

### 2021-03-05 paper_1/AOI_plots.R
Update AOI_plots.R

@@ -12,12 +12,28 @@ options(dplyr.summarise.inform = FALSE)
 # prepare data (selected from AOI data)
 et.raw.data<-read.table("./data/Aperol_pilot_glasses_AOI.txt", dec=",", sep="\t", header=T) 
 
+# convert into numeric
+et.raw.data <- et.raw.data %>%  mutate(Total.duration.of.fixation.in.AOI..sec. = as.numeric(Total.duration.of.fixation.in.AOI..sec.),
+                                       Average.duration.of.fixation.in.AOI..sec. = as.numeric(Average.duration.of.fixation.in.AOI..sec.),
+                                       Number.of.fixations.in.AOI = as.numeric (Number.of.fixations.in.AOI),
+                                       Total.Time.of.Interest.Duration..sec. = as.numeric(Total.Time.of.Interest.Duration..sec.))
+
+
 # create a basic table (tibble) using tidyverse functions for all disruptions 
 # Change Number of Digits in Global R Options to reduce the number of digits after the decimal point to two
 options(digits = 2)              
 
-et.table <- et.raw.data %>% # select data
+et.table <- et.raw.data %>%
   group_by(Type.of.disruption, Group) %>%
-  summarise("Total Duration of Fixations" = Total.duration.of.fixation.in.AOI..sec.,
-            "Average Duration of Fixations" = Average.duration.of.fixation.in.AOI..sec.,
-            "Number of Fixations" = Number.of.fixations.in.AOI)
+  filter(Type.of.disruption != "staring out the window") %>%
+  rename ('Type of Disruption' = Type.of.disruption) %>%
+  summarise("Mean Duration of Fixations" = mean(Total.duration.of.fixation.in.AOI..sec.),
+            "Number of Fixations" = mean(Number.of.fixations.in.AOI),
+            "TOI" = mean(Total.Time.of.Interest.Duration..sec.))
+ 
+# create new columns that give proportion of the duration of looking at AOIs
+# relative duration divided by total duration is the proportion
+proportion.et.data <- et.raw.data %>% 
+  group_by(Type.of.disruption, Group) %>%
+  summarise(Proportion = Average.duration.of.fixation.in.AOI..sec./Total.duration.of.fixation.in.AOI..sec.)
+

### 2021-03-15 paper_1/AOI_plots.R
aufräumen

@@ -47,6 +47,7 @@ total.plot <- ggplot(et.raw.data, aes(x = Type.of.disruption, y = Total.duration
   scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
   scale_x_discrete(guide = guide_axis(angle = 70)) +
   geom_boxplot()+
+  geom_jitter(color="black", size=0.4, alpha=0.5) +
   facet_wrap(~ Group, nrow = 1)+
   theme_light() +
   theme(legend.position="none")+
@@ -74,6 +75,7 @@ number.plot <- ggplot(et.raw.data, aes(x = Type.of.disruption, y = Number.of.fix
   scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
   scale_x_discrete(guide = guide_axis(angle = 70)) +
   geom_boxplot()+
+  geom_jitter(color="black", size=0.4, alpha=0.5) +
   facet_wrap(~ Group, nrow = 1)+
   theme_light() +
   theme(legend.position="none")+

### 2021-03-17 paper_1/paper_1_supplement_et_aoi.Rmd
update plots GRI

--- 2021-02-26 paper_1/paper_1_supplement_new_table.Rmd
@@
 # if a package is not installed on the current machine, it will install it
+if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
 if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
-if (!require(papaja)) install.packages('papaja'); library(papaja)
+if (!require(papaja)) install.packages("papaja"); library(papaja)
 if (!require(psych)) install.packages('psych'); library(psych) # stats
@@
 
-### Questionnaire data
-
-After each mini-lesson, the students answered items on the teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and scales on the teacher's presence behavior (students n = 24).
-In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire after each mini-lesson (teachers n = 8).
-
-### Behavioral data
-
-The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab.
-Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles.
-One camera was installed to film the class from the side.
-Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back.
-Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.
-
 ### Eyetracking data
@@
 
-### Questionnaire Data
-
-The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes. 
-The scales on the quality of teaching are a validated questionnaire [@helmke2014unterrichtsdiagnostik].
-Whereas the scales on the teacher's presence behavior were derived from the research literature [@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen] and were used in the pilot for the first time.
-The questionnaire is 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
-Data was obtained from N = 32 subjects (students n = 24, teachers n = 8).
-
-The following scales were assessed:
-
-(1) Classroom management
-(2) Positive climate and motivation
-(3) Clarity and structuredness
-(4) Activation and support
-(5) Presence: posture/gaze
-(6) Presence: voice
-(7) Presence: verbal and non-verbal intervention
-(8) Natural behaviour
-
-Table \@ref(tab:table-all-scales-self-assessment) provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness & Kurtosis of all scales for the teachers' self-assessment.
-
-```{r table-all-scales-self-assessment, echo = FALSE}
-
-# prepare data (selected from questionnaire data) - only equal items and without observer
-quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)
-
-# knock out NAs and duration of speaking time
-quest.raw.data <- quest.raw.data  %>% filter(
-  personID != "NA",
-  itemID != "8",
-  perspective == "self-assessment")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
-
-##############################################
-
-# calculate Cronbach's Alpha for each scale
-# activation & support
-self.as.wide <- quest.raw.data %>%
-                          filter (scale == "Activation and support") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-self.alpha.as <- alpha(self.as.wide[,-1])
-
-#clarity & structuredness
-self.cs.wide <- quest.raw.data %>%
-                          filter (scale == "Clarity and structuredness") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.cs <- alpha(self.cs.wide[,-1])
-
-#classroom management
-self.cm.wide <- quest.raw.data %>%
-                          filter (scale == "Classroom management") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.cm <- alpha(self.cm.wide[,-1])
-
-#natural behaviour
-self.nb.wide <- quest.raw.data %>%
-                          filter (scale == "Natural behaviour") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.nb <- alpha(self.nb.wide[,-1])
-
-#positive climate and motivation
-self.pcm.wide <- quest.raw.data %>%
-                          filter (scale == "Positive climate and motivation") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pcm <- alpha(self.pcm.wide[,-1])
-
-#presence: posture & gaze
-self.ppg.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: posture/gaze") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.ppg <- alpha(self.ppg.wide[,-1])
-
-#presence: voice
-self.pv.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: voice") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pv <- alpha(self.pv.wide[,-1])
-
-#presence: verbal/non-verbal intervention
-self.pvni.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pvni <- alpha(self.pvni.wide[,-1])
-
-#Presence without subscales
-self.p.wide <- quest.raw.data %>%
-                          filter(str_detect(scale,
-                                        paste(c(
-                                        "Presence: voice", 
-                                        "Presence: verbal and non-verbal intervention", 
-                                        "Presence: posture/gaze"),
-                                         collapse = '|'))) %>% 
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.p <- alpha(self.p.wide[,-1])
-
-##############################################
-
-# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
-# 
-# # activation & support
-# tab_itemscale(self.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # classroom management
-# tab_itemscale(self.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # clarity & structuredness
-# tab_itemscale(self.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # natural behaviour
-# tab_itemscale(self.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # postive clima and motivation
-# tab_itemscale(self.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence without subscales
-# tab_itemscale(self.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence: posture & gaze
-# tab_itemscale(self.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: voice
-# tab_itemscale(self.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: verbal/non-verbal intervention
-# tab_itemscale(self.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-##############################################
-
-# add alphas to excel table 
-# read in new data 
-quest.raw.data.alpha <- read.table("./data/short_questionnaire_data_260221_alpha.txt", dec=",", sep="\t", header=T)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data.alpha <- quest.raw.data.alpha %>%  mutate(alpha = as.numeric(alpha))
-
-##############################################
-
-# #####correlation between all presences' items
-# SELF-ASSESSMENT
-# install.packages("Hmisc")
-# library("Hmisc")
-
-# function cr() to format the correlation matrix
-res1.self<-cor(self.p.wide[,-1])
-
-# Visualization correlation matrix
-# Use corrplot() function: Draw a correlogram
-
-# # install.packages("corrplot")
-# library("corrplot")
-# 
-# # Insignificant correlation are crossed
-# corrplot(res1.self$r, type="upper", order="hclust",
-#          p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
-# # Insignificant correlations are leaved blank
-# corrplot(res1.self$r, type="upper", order="hclust",
-#          p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
-
-###############################################
-
-# create a basic table (tibble) using tidyverse functions for teachers' self assessment 
-# Change Number of Digits in Global R Options to reduce the number of digits after the decimal point to two
-options(digits = 2)
-
-teacher.scale.quest.table <- quest.raw.data.alpha %>% # select data
-  filter(perspective == "self-assessment")%>%
-  group_by(scale) %>%
-  summarise("M" = round(mean(value), 2),
-            "SD" = round(sd(value), 2),
-            "Min" = min(value),
-            "Max" = max(value),
-            "Skewness" = skewness(value),
-            "Kurtosis" = kurtosis(value),
-            "Cronbach's α" = mean(alpha))
-
-# format and insert table in manuscript
-apa_table(
-  teacher.scale.quest.table,
-  caption = "Scale analysis for teachers' self-assessment",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-```
-
-Table \@ref(tab:table-all-scales-students) provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness & Kurtosis of all scales for the students' perception of the teacher's behaviour in class.
-
-```{r table-all-scales-students, echo = FALSE}
-
-# prepare data (selected from questionnaire data) - only equal items and without observer
-quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)
-
-# knock out NAs and duration of speaking time
-quest.raw.data <- quest.raw.data  %>% filter(
-  personID != "NA",
-  itemID != "8",
-  perspective == "student")
-view(quest.raw.data)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
-
-###############################################
-
-# calculate Cronbach's Alpha for each scale of students' peception
-
-# activation & support
-stud.as.wide <- quest.raw.data %>%
-                          filter (scale == "Activation and support") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-stud.alpha.as <- alpha(stud.as.wide[,-1])
-
-#clarity & structuredness
-stud.cs.wide <- quest.raw.data %>%
-                          filter (scale == "Clarity and structuredness") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.cs <- alpha(stud.cs.wide[,-1])
-
-#classroom management
-stud.cm.wide <- quest.raw.data %>%
-                          filter (scale == "Classroom management") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.cm <- alpha(stud.cm.wide[,-1])
-
-#natural behaviour
-stud.nb.wide <- quest.raw.data %>%
-                          filter (scale == "Natural behaviour") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.nb <- alpha(stud.nb.wide[,-1])
-
-#positive climate and motivation
-stud.pcm.wide <- quest.raw.data %>%
-                          filter (scale == "Positive climate and motivation") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.pcm <- alpha(stud.pcm.wide[,-1])
-
-#presence: posture & gaze
-stud.ppg.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: posture/gaze") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.ppg <- alpha(stud.ppg.wide[,-1])
-
-#presence: verbal and non-verbal intervention
-stud.pvni.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.pvni <- alpha(stud.pvni.wide[,-1])
-
-#presence: voice
-stud.pv.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: voice") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.pv <- alpha(stud.pv.wide[,-1])
-
-#Presence without subscales
-stud.p.wide <- quest.raw.data %>%
-                          filter(str_detect(scale,
-                                        paste(c(
-                                        "Presence: voice", 
-                                        "Presence: verbal and non-verbal intervention", 
-                                        "Presence: posture/gaze"),
-                                         collapse = '|'))) %>% 
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.p <- alpha(stud.p.wide[,-1])
-
-# ###############################################
-
-# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
-# 
-# # activation & support
-# tab_itemscale(stud.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # classroom management
-# tab_itemscale(stud.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # clarity & structuredness
-# tab_itemscale(stud.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # natural behaviour
-# tab_itemscale(stud.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # positive clima and motivation
-# tab_itemscale(stud.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence without subscales
-# tab_itemscale(stud.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence: posture & gaze
-# tab_itemscale(stud.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: voice
-# tab_itemscale(stud.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: verbal/non-verbal intervention
-# tab_itemscale(stud.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-##############################################
-# #####correlation between all presences' items
-# SELF-ASSESSMENT
-# install.packages("Hmisc")
-library("Hmisc")
-
-# # function to format the correlation matrix
-# flattenCorrMatrix <- function(cormat, pmat) {
-#   ut <- upper.tri(cormat)
-#   data.frame(
-#     row = rownames(cormat)[row(cormat)[ut]],
-#     column = rownames(cormat)[col(cormat)[ut]],
-#     cor  =(cormat)[ut],
-#     p = pmat[ut]
-#     )
-# }
-# 
-# res1.stud<-cor(stud.p.wide[,-1])
-
-# res1.stud<-rcorr(as.matrix(stud.p.wide[,-1]))
-# 
-# flattenCorrMatrix(res1.stud$r, res1.stud$P)
-# 
-# res2.stud<-flattenCorrMatrix(res1.stud$r, res1.stud$P)
-
-# Visualization correlation matrix
-# Use corrplot() function: Draw a correlogram
-
-# install.packages("corrplot")
-library("corrplot")
-
-# # Insignificant correlation are crossed
-# corrplot(res1.stud$r, type="upper", order="hclust",
-#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
-# # Insignificant correlations are leaved blank
-# corrplot(res1.stud$r, type="upper", order="hclust",
-#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
-
-##############################################
-
-# add alphas to excel table 
-# read in new data 
-quest.raw.data.alpha <- read.table("./data/short_questionnaire_data_260221_alpha.txt", dec=",", sep="\t", header=T)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data.alpha <- quest.raw.data.alpha %>%  mutate(alpha = as.numeric(alpha))
-
-##############################################
-
-# create a basic table (tibble) using tidyverse functions for teacher self assessment 
-student.scale.quest.table <- quest.raw.data.alpha %>% # select data
-  filter(perspective == "student")%>%
-  group_by(scale) %>%
-  summarise("M" = round(mean(value), 2),
-            "SD" = round(sd(value), 2),
-            "Min" = min(value),
-            "Max" = max(value),
-            "Skewness" = skewness(value),
-            "Kurtosis" = kurtosis(value),
-            "Cronbach's α" = mean(alpha))
-
-# format and insert table in manuscript
-apa_table(
-  student.scale.quest.table,
-  caption = "Scale analysis for students' perspective",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-```
-
-\newpage
-The individual items of a scale are further represented in graphs.
-
-(1) Classroom management
-```{r Line Plots Classroom Management, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, fig.cap="Items for Classroom Management"}
-
-### classroom management
-
-# filter by parameter variable, i.e. create a subset for classroom management without perspective "observer"
-cm.data <- quest.raw.data %>% filter(scale == "Classroom management")
-
-view(cm.data)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-cm.data <- cm.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-cm.plot.sd <- cm.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-cm.plot<-ggplot(data = cm.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = perspective, colour = perspective)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = cm.data, y = "value", x = NULL,
-       title="Classroom management" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-cm.plot
-
-```
-\newpage
-(2) Positive climate and motivation
-```{r Positive climate and motivation line plots,  fig.width=6, fig.height = 7, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Positive climate and motivation"}
-
-### Positive climate and motivation
-
-# filter by parameter variable, i.e. create a subset for Positive climate and motivation
-pcm.data <- quest.raw.data %>% filter(scale == "Positive climate and motivation")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-pcm.data <- pcm.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-pcm.plot.sd <- pcm.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-pcm.plot<-ggplot(data = pcm.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = pcm.data, y = "value", x = NULL,
-       title="Positive climate and motivation" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 5))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-pcm.plot
-
-```
-\newpage
-(3) Clarity and structuredness
-```{r Clarity and structuredness line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Clarity and structuredness"}
-
-### Clarity and structuredness
-
-# filter by parameter variable, i.e. create a subset for Clarity and structuredness
-cs.data <- quest.raw.data %>% filter(scale == "Clarity and structuredness")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-cs.data <- cs.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-cs.plot.sd <- cs.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-cs.plot<-ggplot(data = cs.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = cs.data, y = "value", x = NULL,
-       title="Clarity and structuredness" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-cs.plot
-
-```
-\newpage
-(4) Activation and support
-```{r Activation and support line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Activation and support"}
-
-### Activation and support
-
-# filter by parameter variable, i.e. create a subset for Activation and support
-as.data <- quest.raw.data %>% filter(scale == "Activation and support")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-as.data <- as.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-as.plot.sd <- as.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-as.plot<-ggplot(data = as.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = as.data, y = "value", x = NULL,
-       title="Activation and support" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-as.plot
-
-```
-\newpage
-
-(ref:presenceposturegaze-caption) (5) Presence: posture/gaze
-
-```{r presenceposturegaze, fig.cap = "(ref:presenceposturegaze-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presenceposturegaze.png", dpi = 108)
-
-# ```{r Presence: posture/gaze line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-
-# ### Presence: posture/gaze 
-# 
-# # filter by parameter variable, i.e. create a subset for Presence: posture/gaze
-# ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# ppg.plot.sd <- ppg.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# ppg.plot<-ggplot(data = ppg.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = ppg.data, y = "value", x = NULL,
-#        title="Presence: posture/gaze" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# ppg.plot
-
-```
-
-\newpage
-
-(ref:presencevoice-caption) (6) Presence: voice
-
-```{r presencevoice, fig.cap = "(ref:presencevoice-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presencevoice.png", dpi = 108)
-
-# ```{r Presence: voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-# 
-# ### Presence: voice 
-# # filter by parameter variable, i.e. create a subset for Presence: voice
-# pv.data <- quest.raw.data %>% filter(scale == "Presence: voice")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# pv.plot.sd <- pv.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# pv.plot<-ggplot(data = pv.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = pv.data, y = "value", x = NULL,
-#        title="Presence: voice" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# pv.plot
-
-```
-\newpage
-
-(ref:presenceverbalnonverbalintervention-caption) (7) Presence: verbal and non-verbal intervention
-
-```{r presenceverbalnonverbalintervention, fig.cap = "(ref:presenceverbalnonverbalintervention-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presenceverbalnonverbalintervention.png", dpi = 108)
-
-# ```{r Presence: verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-# 
-# ### Presence: verbal and non-verbal intervention 
-# # filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
-# pvni.data <- quest.raw.data %>% filter(scale == "Presence: verbal and non-verbal intervention")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# pvni.plot.sd <- pvni.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# pvni.plot<-ggplot(data = pvni.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = pvni.data, y = "value", x = NULL,
-#        title="Presence: verbal and non-verbal intervention" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# pvni.plot
-
-```
-\newpage
-(8) Natural behaviour
-```{r Natural behaviour line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Natural Behaviour"}
-
-### Natural behaviour 
-# filter by parameter variable, i.e. create a subset for Natural behaviour
-nb.data <- quest.raw.data %>% filter(scale == "Natural behaviour")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-nb.data <- nb.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-nb.plot.sd <- nb.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-nb.plot<-ggplot(data = nb.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = nb.data, y = "value", x = NULL,
-       title="Natural behaviour" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-nb.plot
-
-```
-\newpage
-In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
-
-```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE, fig.cap = "Boxplots and individual data for experts and novices"}
-
-quest.plot <- quest.raw.data %>%
-  ggplot(aes(x=scale, y=value, fill=scale)) +
-    geom_boxplot() +
-    scale_x_discrete(guide = guide_axis(angle = 70)) +
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    theme_light() +
-    theme(
-      legend.position="none",
-      plot.title = element_text(size=11)
-    ) +
-    facet_grid(~group)+
-    ggtitle("Boxplot with individual points for all scales") +
-    xlab("")
-quest.plot
-
-```
-
-\newpage
-
-### Behavioral Data
-
-The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters [@kuckartz2019analyzing]. The following coding scheme was developed:
-
-- phase - lesson begin, state event: teacher starts the lesson with a noise, talk, taking a position in class
-- phase - lesson end,	state event: teacher finishes the lesson with a noise, talk, taking a position in class
-- phase - organization/transition points, state event: any situation that does not imply effective learning time (fetching chalk, working        material, organizing desks, opening windows, printing work results etc.)
-- phase - single,	state event: any individual student activity on a given task (reading, writing, drawing etc.)
-- phase - group, state event: any student activity on a given task together in a group of at least 3 students (reading, writing, drawing etc.)
-- phase - class discussion, state event: discussion in class, teacher talks to class/individual/group
-- phase - pair: state event: any student activity on a given task together in a team of 2 students (reading, writing, drawing etc.)
-- phase - teachers lecture, state event: any teacher's presentation on a certain topic which maybe supported by a PPP, PREZI, notes on board,    OHP etc.
-- phase - other, state event: not categorizable
-- phase - break, state event: e.g. drinking, relaxation exercises
-- phase - external interruption, state event: external interruptions (e.g. fire alarm, technical problems, other teachers coming into the room)
-
-- speaking time - teacher, state event
-- speaking time - students, state event
-
-- disruption - chatting with neighbor, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - asking a question, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - yelling, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - looking at phone, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - staring out of window, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - drawing, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - head on table, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - clicking pen, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - drumming hands, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - walking around, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-
-First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher.
-The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.
-
-```{r coded speaking time, echo = FALSE }
-### read in data for 01_01_expert_D
-speaking.data.01.01 <- read.delim("./data/Aperol_pilot_01_01_expert_D_cam4_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.01 <- speaking.data.01.01  %>% select(
-  Dokumentgruppe,
-  Dokumentname,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher and "kodiert von Anna" as row 
-speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
-                                           Dokumentgruppe == "kodiert von Anna")
-speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)
-
-# read in data for 01_02_expert_A
-speaking.data.01.02 <- read.delim("./data/Aperol_pilot_01_02_expert_A_cam1_AL.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.02 <- speaking.data.01.02 %>% select(
-  Dokumentname,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.01.02 <- speaking.data.01.02 %>% filter (Code == "speaking time\\teacher")
-speaking.data.01.02 <- sum(speaking.data.01.02$Abdeckungsgrad..)
-
-# read in data for 01_03_novice_B
-speaking.data.01.03 <- read.delim("./data/Aperol_pilot_01_03_novice_B_cam1.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.03 <- speaking.data.01.03 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.01.03 <- speaking.data.01.03 %>% filter (Code == "speaking time\\teachter")
-speaking.data.01.03 <- sum(speaking.data.01.03$Abdeckungsgrad..)
-
-# read in data for 01_04_novice_C
-speaking.data.01.04 <- read.delim("./data/Aperol_pilot_01_04_novice_C_cam1.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.04 <- speaking.data.01.04 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.01.04 <- speaking.data.01.04 %>% filter (Code == "speaking time\\teachter")
-
-speaking.data.01.04 <- sum(speaking.data.01.04$Abdeckungsgrad..)
-
-# read in data for 02_01_novice_A
-speaking.data.02.01 <- read.delim("./data/Aperol_pilot_02_01_novice_A_glasses.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.01 <- speaking.data.02.01 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.01 <- speaking.data.02.01 %>% filter (Code == "speaking time\\teacher")
-speaking.data.02.01 <- sum(speaking.data.02.01$Abdeckungsgrad..)
-
-# read in data for 02_02_novice_B
-speaking.data.02.02 <- read.delim("./data/Aperol_pilot_02_02_novice_B_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.02 <- speaking.data.02.02 %>% select(
-  Dokumentgruppe,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.02 <- speaking.data.02.02 %>% filter (Code == "speaking time\\teacher",
-                                                       Dokumentgruppe == "kodiert von Anna")
-speaking.data.02.02 <- sum(speaking.data.02.02$Abdeckungsgrad..)
-
-# read in data for 02_03_novice_C
-speaking.data.02.03 <- read.delim("./data/Aperol_pilot_02_03_novice_C_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.03 <- speaking.data.02.03 %>% select(
-  Dokumentgruppe,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.03 <- speaking.data.02.03 %>% filter (Code == "speaking time\\teachter",
-                                                       Dokumentgruppe == "02_03_kodiert von Anna")
-speaking.data.02.03 <- sum(speaking.data.02.03$Abdeckungsgrad..)
-
-# read in data for 02_04_novice_D
-speaking.data.02.04 <- read.delim("./data/Aperol_pilot_02_04_novice_D_cam1.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.04 <- speaking.data.02.04 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.04 <- speaking.data.02.04 %>% filter (Code == "speaking time\\teachter")
-speaking.data.02.04 <- sum(speaking.data.02.04$Abdeckungsgrad..)
-
-```
-
-```{r speaking plot, echo=FALSE}
-
-# read in table with coded speaking time included
-speaking.data <- read.delim("./data/plus_coded_speaking_time_questionnaire_data_0802.txt", dec=",", sep="\t", header=T)
-
-# to compare both sessions filter only Identical items
-speaking.data <- speaking.data  %>% filter(str_detect(scale, 
-                                                 paste(c("Duration of speaking time"),
-                                                    collapse = '|')))
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-speaking.data <- speaking.data %>%  mutate(value = as.numeric(value))
-
-speaking.plot <- speaking.data %>%
-  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
-    geom_boxplot() +
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    theme_light() +
-    theme(
-      legend.position="none",
-      plot.title = element_text(size=11),
-      axis.text.x = element_text(size = 8)) +
-    facet_grid(group~perspective) +
-    ggtitle("Boxplot with individual points for Duration of speaking time") +
-    xlab("")
-speaking.plot
-
-```
-
 ### Eyetracking Data
@@
 
-#### Gaze relational index (GRI)
+#### Areas of Interest (GRI)
 
-The GRI is a measure of visual expertise in information processing.
-This metric is calculated as the ratio of mean fixation duration to fixation count.
-The GRI is higher for novices than for experts.
-[@gegenfurtner2020gaze]
+``` {r AOIs, echo=FALSE} 
+if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
+if (!require(papaja)) install.packages('papaja'); library(papaja)
+if (!require(psych)) install.packages('psych'); library(psych) # stats
+if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
+if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
 
-```{r GRItable, echo = FALSE}
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
 
-# prepare data (selected from questionnaire data)
-et.raw.data<-read.table("./data/Aperol_pilot_glasses_raw_fixation_saccades_metrics.tsv", dec=",", sep="\t", header=T)
+# prepare data (selected from AOI data)
+et.raw.data<-read.table("./data/Aperol_pilot_glasses_AOI.txt", dec=",", sep="\t", header=T)
 
-# converting integer to numeric
-et.raw.data <- et.raw.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
+# convert into numeric
+et.raw.data <- et.raw.data %>%  mutate(Total.duration.of.fixation.in.AOI..sec. = as.numeric(Total.duration.of.fixation.in.AOI..sec.),
+                                       Average.duration.of.fixation.in.AOI..sec. = as.numeric(Average.duration.of.fixation.in.AOI..sec.),
+                                       Number.of.fixations.in.AOI = as.numeric (Number.of.fixations.in.AOI),
+                                       Total.Time.of.Interest.Duration..sec. = as.numeric(Total.Time.of.Interest.Duration..sec.))
 
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.raw.table <- et.raw.data %>%
-  group_by(Participant, Variable) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
+# create a basic table (tibble) using tidyverse functions for all disruptions 
+# Change Number of Digits in Global R Options to reduce the number of digits after the decimal point to two
+options(digits = 2)
 
-# format and insert table in manuscript
-apa_table(
-  et.raw.table,
-  caption = "Number and Duration (in msec) of Fixations",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
+et.table <- et.raw.data %>%
+  group_by(Type.of.disruption, Group) %>%
+  filter(Type.of.disruption != "staring out the window") %>%
+  rename ('Type of Disruption' = Type.of.disruption) %>%
+  summarise("Mean Duration of Fixations" = mean(Total.duration.of.fixation.in.AOI..sec.),
+            "Number of Fixations" = mean(Number.of.fixations.in.AOI),
+            "TOI" = mean(Total.Time.of.Interest.Duration..sec.))
 
-```
+# create a new column with name Total that gives the sum duration in sec of looking at all AOIs
+et.raw.data <- et.raw.data %>% mutate(Total = sum(Total.duration.of.fixation.in.AOI..sec.))
 
-```{r calibration phase TOI, echo = FALSE}
+# create new columns that give proportion of the duration of looking at AOIs
+# relative duration divided by total duration is the proportion
+proportion.et.data <- et.raw.data %>% group_by(Group, Type.of.disruption) %>% 
+                                      mutate(Proportion = Total.duration.of.fixation.in.AOI..sec./Total)
 
-# prepare data (selected from questionnaire data)
-et.calib.data<-read.table("./data/Aperol_pilot_glasses_raw_ALL_metrics_calib_without_AOI_snapshot.tsv", dec=",", sep="\t", header=T)
+### Plot data TOTAL
+total.plot <- ggplot(et.raw.data, aes(x = Type.of.disruption, y = Total.duration.of.fixation.in.AOI..sec., fill = Type.of.disruption)) +
+  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
+  scale_x_discrete(guide = guide_axis(angle = 70)) +
+  geom_boxplot()+
+  geom_jitter(color="black", size=0.4, alpha=0.5) +
+  facet_wrap(~ Group, nrow = 1)+
+  theme_light() +
+  theme(legend.position="none")+
+  labs(y = "Total Duration of Looking at AOIs in sec", x = "AOI")
 
-# converting integer to numeric
-et.calib.data <- et.calib.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-# select relevant rows 
-et.calib.data <- et.calib.data %>% filter(TOI == "Calibration phase")
+total.plot
 
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.calib.table <- et.calib.data %>%
-  group_by(Participant, Variable1) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
+### Plot data PROPORTIONS
+prop.plot <- ggplot(proportion.et.data, aes(x = Type.of.disruption, y = Proportion, fill = Type.of.disruption)) +
+  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
+  scale_x_discrete(guide = guide_axis(angle = 70)) +
+  geom_boxplot()+
+  facet_wrap(~ Group, nrow = 1)+
+  theme_light() +
+  theme(legend.position="none")+
+  labs(y = "Proportion of Looking at AOIs", x = "AOI")
 
-# format and insert table in manuscript
-apa_table(
-  et.calib.table,
-  caption = "Number and Duration (in msec) of Fixations during calibration",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
+prop.plot
+
+### Plot Number of Fixations
+number.plot <- ggplot(et.raw.data, aes(x = Type.of.disruption, y = Number.of.fixations.in.AOI, fill = Type.of.disruption)) +
+  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
+  scale_x_discrete(guide = guide_axis(angle = 70)) +
+  geom_boxplot()+
+  geom_jitter(color="black", size=0.4, alpha=0.5) +
+  facet_wrap(~ Group, nrow = 1)+
+  theme_light() +
+  theme(legend.position="none")+
+  labs(y = "Number of Fixations in AOI", x = "AOI")
+
+number.plot
+
+# ### Plot Average duration of fixation
+# average.plot <- ggplot(et.table, aes(x = "Type of Disruption", y = "Mean Duration of Fixations", fill = "Type of Disruption")) +
+#   scale_x_discrete(guide = guide_axis(angle = 70)) +
+#   geom_bar(aes(y="Mean Duration of Fixations")) + 
+#   facet_wrap(~ Group)+
+#   theme_light() +
+#   theme(legend.position="none")+
+#   labs(y = "Average Duration of Looking at AOIs in sec", x = "AOI")
+# 
+# average.plot
 
@@
 
-### Questionnaire Data
-
-### Behavioral Data
-
 ### Eyetracking Data
@@
 Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-
-### Questionnaire Data
-
-### Behavioral Data
 

### 2021-03-17 paper_1/paper_1_supplement_et_gri.Rmd
update plots GRI

--- 2021-03-03 paper_1/paper_1_supplement_new_table.Rmd
@@
 ## Coding/ Data preparation/ Reliability
-
-### Questionnaire Data
-
-The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes. 
-The scales on the quality of teaching are a validated questionnaire [@helmke2014unterrichtsdiagnostik].
-Whereas the scales on the teacher's presence behavior were derived from the research literature [@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen] and were used in the pilot for the first time.
-The questionnaire is 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
-Data was obtained from N = 32 subjects (students n = 24, teachers n = 8).
-
-The following scales were assessed:
-
-(1) Classroom management
-(2) Positive climate and motivation
-(3) Clarity and structuredness
-(4) Activation and support
-(5) Presence: posture/gaze
-(6) Presence: voice
-(7) Presence: verbal and non-verbal intervention
-(8) Natural behaviour
-
-Table \@ref(tab:table-all-scales-self-assessment) provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness & Kurtosis of all scales for the teachers' self-assessment.
-
-```{r table-all-scales-self-assessment, echo=FALSE, message=FALSE, warning=FALSE}
-
-# prepare data (selected from questionnaire data) - only equal items and without observer
-quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)
-
-# knock out NAs and duration of speaking time
-quest.raw.data <- quest.raw.data  %>% filter(
-  personID != "NA",
-  itemID != "8",
-  perspective == "self-assessment")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
-
-##############################################
-
-# calculate Cronbach's Alpha for each scale
-# activation & support
-self.as.wide <- quest.raw.data %>%
-                          filter (scale == "Activation and support") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-self.alpha.as <- alpha(self.as.wide[,-1])
-
-#clarity & structuredness
-self.cs.wide <- quest.raw.data %>%
-                          filter (scale == "Clarity and structuredness") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.cs <- alpha(self.cs.wide[,-1])
-
-#classroom management
-self.cm.wide <- quest.raw.data %>%
-                          filter (scale == "Classroom management") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.cm <- alpha(self.cm.wide[,-1])
-
-#natural behaviour
-self.nb.wide <- quest.raw.data %>%
-                          filter (scale == "Natural behaviour") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.nb <- alpha(self.nb.wide[,-1])
-
-#positive climate and motivation
-self.pcm.wide <- quest.raw.data %>%
-                          filter (scale == "Positive climate and motivation") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pcm <- alpha(self.pcm.wide[,-1])
-
-#presence: posture & gaze
-self.ppg.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: posture/gaze") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.ppg <- alpha(self.ppg.wide[,-1])
-
-#presence: voice
-self.pv.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: voice") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pv <- alpha(self.pv.wide[,-1])
-
-#presence: verbal/non-verbal intervention
-self.pvni.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pvni <- alpha(self.pvni.wide[,-1])
-
-#Presence without subscales
-self.p.wide <- quest.raw.data %>%
-                          filter(str_detect(scale,
-                                        paste(c(
-                                        "Presence: voice", 
-                                        "Presence: verbal and non-verbal intervention", 
-                                        "Presence: posture/gaze"),
-                                         collapse = '|'))) %>% 
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.p <- alpha(self.p.wide[,-1])
-
-##############################################
-
-# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
-# 
-# # activation & support
-# tab_itemscale(self.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # classroom management
-# tab_itemscale(self.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # clarity & structuredness
-# tab_itemscale(self.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # natural behaviour
-# tab_itemscale(self.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # postive clima and motivation
-# tab_itemscale(self.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence without subscales
-# tab_itemscale(self.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence: posture & gaze
-# tab_itemscale(self.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: voice
-# tab_itemscale(self.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: verbal/non-verbal intervention
-# tab_itemscale(self.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-##############################################
-
-# add alphas to excel table 
-# read in new data 
-quest.raw.data.alpha <- read.table("./data/short_questionnaire_data_260221_alpha.txt", dec=",", sep="\t", header=T)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data.alpha <- quest.raw.data.alpha %>%  mutate(alpha = as.numeric(alpha))
-
-##############################################
-
-# #####correlation between all presences' items
-# SELF-ASSESSMENT
-# install.packages("Hmisc")
-# library("Hmisc")
-
-# function cr() to format the correlation matrix
-res1.self<-cor(self.p.wide[,-1])
-
-# Visualization correlation matrix
-# Use corrplot() function: Draw a correlogram
-
-# # install.packages("corrplot")
-# library("corrplot")
-# 
-# # Insignificant correlation are crossed
-# corrplot(res1.self$r, type="upper", order="hclust",
-#          p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
-# # Insignificant correlations are leaved blank
-# corrplot(res1.self$r, type="upper", order="hclust",
-#          p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
-
-###############################################
-
-# create a basic table (tibble) using tidyverse functions for teachers' self assessment 
-# Change Number of Digits in Global R Options to reduce the number of digits after the decimal point to two
-options(digits = 2)
-
-teacher.scale.quest.table <- quest.raw.data.alpha %>% # select data
-  filter(perspective == "self-assessment")%>%
-  group_by(scale) %>%
-  summarise("N items" = n_distinct(shortID),
-            "M" = round(mean(value), 2),
-            "SD" = round(sd(value), 2),
-            "Min" = min(value),
-            "Max" = max(value),
-            "Skewness" = skewness(value),
-            "Kurtosis" = kurtosis(value),
-            "Cronbach's α" = mean(alpha))
-
-# format and insert table in manuscript
-apa_table(
-  teacher.scale.quest.table,
-  caption = "Scale analysis for teachers' self-assessment",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-```
-
-Table \@ref(tab:table-all-scales-students) provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness & Kurtosis of all scales for the students' perception of the teacher's behaviour in class.
-
-```{r table-all-scales-students, echo=FALSE, message=FALSE, warning=FALSE}
-
-# prepare data (selected from questionnaire data) - only equal items and without observer
-quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)
-
-# knock out NAs and duration of speaking time
-quest.raw.data <- quest.raw.data  %>% filter(
-  personID != "NA",
-  itemID != "8",
-  perspective == "student")
-view(quest.raw.data)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
-
-###############################################
-
-# calculate Cronbach's Alpha for each scale of students' peception
-
-# activation & support
-stud.as.wide <- quest.raw.data %>%
-                          filter (scale == "Activation and support") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-stud.alpha.as <- alpha(stud.as.wide[,-1])
-
-#clarity & structuredness
-stud.cs.wide <- quest.raw.data %>%
-                          filter (scale == "Clarity and structuredness") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.cs <- alpha(stud.cs.wide[,-1])
-
-#classroom management
-stud.cm.wide <- quest.raw.data %>%
-                          filter (scale == "Classroom management") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.cm <- alpha(stud.cm.wide[,-1])
-
-#natural behaviour
-stud.nb.wide <- quest.raw.data %>%
-                          filter (scale == "Natural behaviour") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.nb <- alpha(stud.nb.wide[,-1])
-
-#positive climate and motivation
-stud.pcm.wide <- quest.raw.data %>%
-                          filter (scale == "Positive climate and motivation") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.pcm <- alpha(stud.pcm.wide[,-1])
-
-#presence: posture & gaze
-stud.ppg.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: posture/gaze") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.ppg <- alpha(stud.ppg.wide[,-1])
-
-#presence: verbal and non-verbal intervention
-stud.pvni.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.pvni <- alpha(stud.pvni.wide[,-1])
-
-#presence: voice
-stud.pv.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: voice") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.pv <- alpha(stud.pv.wide[,-1])
-
-#Presence without subscales
-stud.p.wide <- quest.raw.data %>%
-                          filter(str_detect(scale,
-                                        paste(c(
-                                        "Presence: voice", 
-                                        "Presence: verbal and non-verbal intervention", 
-                                        "Presence: posture/gaze"),
-                                         collapse = '|'))) %>% 
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.p <- alpha(stud.p.wide[,-1])
-
-# ###############################################
-
-# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
-# 
-# # activation & support
-# tab_itemscale(stud.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # classroom management
-# tab_itemscale(stud.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # clarity & structuredness
-# tab_itemscale(stud.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # natural behaviour
-# tab_itemscale(stud.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # positive clima and motivation
-# tab_itemscale(stud.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence without subscales
-# tab_itemscale(stud.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence: posture & gaze
-# tab_itemscale(stud.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: voice
-# tab_itemscale(stud.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: verbal/non-verbal intervention
-# tab_itemscale(stud.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-##############################################
-# #####correlation between all presences' items
-# SELF-ASSESSMENT
-# install.packages("Hmisc")
-library("Hmisc")
-
-# # function to format the correlation matrix
-# flattenCorrMatrix <- function(cormat, pmat) {
-#   ut <- upper.tri(cormat)
-#   data.frame(
-#     row = rownames(cormat)[row(cormat)[ut]],
-#     column = rownames(cormat)[col(cormat)[ut]],
-#     cor  =(cormat)[ut],
-#     p = pmat[ut]
-#     )
-# }
-# 
-# res1.stud<-cor(stud.p.wide[,-1])
-
-# res1.stud<-rcorr(as.matrix(stud.p.wide[,-1]))
-# 
-# flattenCorrMatrix(res1.stud$r, res1.stud$P)
-# 
-# res2.stud<-flattenCorrMatrix(res1.stud$r, res1.stud$P)
-
-# Visualization correlation matrix
-# Use corrplot() function: Draw a correlogram
-
-# install.packages("corrplot")
-library("corrplot")
-
-# # Insignificant correlation are crossed
-# corrplot(res1.stud$r, type="upper", order="hclust",
-#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
-# # Insignificant correlations are leaved blank
-# corrplot(res1.stud$r, type="upper", order="hclust",
-#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
-
-##############################################
-
-# add alphas to excel table 
-# read in new data 
-quest.raw.data.alpha <- read.table("./data/short_questionnaire_data_260221_alpha.txt", dec=",", sep="\t", header=T)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data.alpha <- quest.raw.data.alpha %>%  mutate(alpha = as.numeric(alpha))
-
-##############################################
-
-# create a basic table (tibble) using tidyverse functions for teacher self assessment 
-student.scale.quest.table <- quest.raw.data.alpha %>% # select data
-  filter(perspective == "student")%>%
-  group_by(scale) %>%
-  summarise("N items" = n_distinct(shortID),
-            "M" = round(mean(value), 2),
-            "SD" = round(sd(value), 2),
-            "Min" = min(value),
-            "Max" = max(value),
-            "Skewness" = skewness(value),
-            "Kurtosis" = kurtosis(value),
-            "Cronbach's α" = mean(alpha))
-
-# format and insert table in manuscript
-apa_table(
-  student.scale.quest.table,
-  caption = "Scale analysis for students' perspective",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-```
-
-\newpage
-The individual items of a scale are further represented in graphs.
-
-(1) Classroom management
-```{r Line Plots Classroom Management, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, fig.cap="Items for Classroom Management"}
-
-### classroom management
-
-# filter by parameter variable, i.e. create a subset for classroom management without perspective "observer"
-cm.data <- quest.raw.data %>% filter(scale == "Classroom management")
-
-view(cm.data)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-cm.data <- cm.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-cm.plot.sd <- cm.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-cm.plot<-ggplot(data = cm.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = perspective, colour = perspective)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = cm.data, y = "value", x = NULL,
-       title="Classroom management" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-cm.plot
-
-```
-\newpage
-(2) Positive climate and motivation
-```{r Positive climate and motivation line plots,  fig.width=6, fig.height = 7, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Positive climate and motivation"}
-
-### Positive climate and motivation
-
-# filter by parameter variable, i.e. create a subset for Positive climate and motivation
-pcm.data <- quest.raw.data %>% filter(scale == "Positive climate and motivation")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-pcm.data <- pcm.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-pcm.plot.sd <- pcm.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-pcm.plot<-ggplot(data = pcm.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = pcm.data, y = "value", x = NULL,
-       title="Positive climate and motivation" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 5))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-pcm.plot
-
-```
-\newpage
-(3) Clarity and structuredness
-```{r Clarity and structuredness line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Clarity and structuredness"}
-
-### Clarity and structuredness
-
-# filter by parameter variable, i.e. create a subset for Clarity and structuredness
-cs.data <- quest.raw.data %>% filter(scale == "Clarity and structuredness")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-cs.data <- cs.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-cs.plot.sd <- cs.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-cs.plot<-ggplot(data = cs.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = cs.data, y = "value", x = NULL,
-       title="Clarity and structuredness" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-cs.plot
-
-```
-\newpage
-(4) Activation and support
-```{r Activation and support line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Activation and support"}
-
-### Activation and support
-
-# filter by parameter variable, i.e. create a subset for Activation and support
-as.data <- quest.raw.data %>% filter(scale == "Activation and support")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-as.data <- as.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-as.plot.sd <- as.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-as.plot<-ggplot(data = as.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = as.data, y = "value", x = NULL,
-       title="Activation and support" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-as.plot
-
-```
-\newpage
-
-(ref:presenceposturegaze-caption) (5) Presence: posture/gaze
-
-```{r presenceposturegaze, fig.cap = "(ref:presenceposturegaze-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presenceposturegaze.png", dpi = 108)
-
-# ```{r Presence: posture/gaze line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-
-# ### Presence: posture/gaze 
-# 
-# # filter by parameter variable, i.e. create a subset for Presence: posture/gaze
-# ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# ppg.plot.sd <- ppg.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# ppg.plot<-ggplot(data = ppg.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = ppg.data, y = "value", x = NULL,
-#        title="Presence: posture/gaze" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# ppg.plot
-
-```
-
-\newpage
-
-(ref:presencevoice-caption) (6) Presence: voice
-
-```{r presencevoice, fig.cap = "(ref:presencevoice-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presencevoice.png", dpi = 108)
-
-# ```{r Presence: voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-# 
-# ### Presence: voice 
-# # filter by parameter variable, i.e. create a subset for Presence: voice
-# pv.data <- quest.raw.data %>% filter(scale == "Presence: voice")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# pv.plot.sd <- pv.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# pv.plot<-ggplot(data = pv.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = pv.data, y = "value", x = NULL,
-#        title="Presence: voice" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# pv.plot
-
-```
-\newpage
-
-(ref:presenceverbalnonverbalintervention-caption) (7) Presence: verbal and non-verbal intervention
-
-```{r presenceverbalnonverbalintervention, fig.cap = "(ref:presenceverbalnonverbalintervention-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presenceverbalnonverbalintervention.png", dpi = 108)
-
-# ```{r Presence: verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-# 
-# ### Presence: verbal and non-verbal intervention 
-# # filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
-# pvni.data <- quest.raw.data %>% filter(scale == "Presence: verbal and non-verbal intervention")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# pvni.plot.sd <- pvni.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# pvni.plot<-ggplot(data = pvni.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = pvni.data, y = "value", x = NULL,
-#        title="Presence: verbal and non-verbal intervention" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# pvni.plot
-
-```
-\newpage
-(8) Natural behaviour
-```{r Natural behaviour line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Natural Behaviour"}
-
-### Natural behaviour 
-# filter by parameter variable, i.e. create a subset for Natural behaviour
-nb.data <- quest.raw.data %>% filter(scale == "Natural behaviour")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-nb.data <- nb.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-nb.plot.sd <- nb.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-nb.plot<-ggplot(data = nb.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = nb.data, y = "value", x = NULL,
-       title="Natural behaviour" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-nb.plot
-
-```
-\newpage
-In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
-
-```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE, fig.cap = "Boxplots and individual data for experts and novices"}
-
-quest.plot <- quest.raw.data %>%
-  ggplot(aes(x=scale, y=value, fill=scale)) +
-    geom_boxplot() +
-    scale_x_discrete(guide = guide_axis(angle = 70)) +
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    theme_light() +
-    theme(
-      legend.position="none",
-      plot.title = element_text(size=11)
-    ) +
-    facet_grid(~group)+
-    ggtitle("Boxplot with individual points for all scales") +
-    xlab("")
-quest.plot
-
-```
-
-\newpage
-
-### Behavioral Data
-
-The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters [@kuckartz2019analyzing]. The following coding scheme was developed:
-
-- phase - lesson begin, state event: teacher starts the lesson with a noise, talk, taking a position in class
-- phase - lesson end,	state event: teacher finishes the lesson with a noise, talk, taking a position in class
-- phase - organization/transition points, state event: any situation that does not imply effective learning time (fetching chalk, working        material, organizing desks, opening windows, printing work results etc.)
-- phase - single,	state event: any individual student activity on a given task (reading, writing, drawing etc.)
-- phase - group, state event: any student activity on a given task together in a group of at least 3 students (reading, writing, drawing etc.)
-- phase - class discussion, state event: discussion in class, teacher talks to class/individual/group
-- phase - pair: state event: any student activity on a given task together in a team of 2 students (reading, writing, drawing etc.)
-- phase - teachers lecture, state event: any teacher's presentation on a certain topic which maybe supported by a PPP, PREZI, notes on board,    OHP etc.
-- phase - other, state event: not categorizable
-- phase - break, state event: e.g. drinking, relaxation exercises
-- phase - external interruption, state event: external interruptions (e.g. fire alarm, technical problems, other teachers coming into the room)
-
-- speaking time - teacher, state event
-- speaking time - students, state event
-
-- disruption - chatting with neighbor, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - asking a question, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - yelling, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - looking at phone, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - staring out of window, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - drawing, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - head on table, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - clicking pen, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - drumming hands, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - walking around, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-
-First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher.
-The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.
-
-```{r coded speaking time, echo = FALSE }
-### read in data for 01_01_expert_D
-speaking.data.01.01 <- read.delim("./data/Aperol_pilot_01_01_expert_D_cam4_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.01 <- speaking.data.01.01  %>% select(
-  Dokumentgruppe,
-  Dokumentname,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher and "kodiert von Anna" as row 
-speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
-                                           Dokumentgruppe == "kodiert von Anna")
-speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)
-
-# read in data for 01_02_expert_A
-speaking.data.01.02 <- read.delim("./data/Aperol_pilot_01_02_expert_A_cam1_AL.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.02 <- speaking.data.01.02 %>% select(
-  Dokumentname,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.01.02 <- speaking.data.01.02 %>% filter (Code == "speaking time\\teacher")
-speaking.data.01.02 <- sum(speaking.data.01.02$Abdeckungsgrad..)
-
-# read in data for 01_03_novice_B
-speaking.data.01.03 <- read.delim("./data/Aperol_pilot_01_03_novice_B_cam1.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.03 <- speaking.data.01.03 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.01.03 <- speaking.data.01.03 %>% filter (Code == "speaking time\\teachter")
-speaking.data.01.03 <- sum(speaking.data.01.03$Abdeckungsgrad..)
-
-# read in data for 01_04_novice_C
-speaking.data.01.04 <- read.delim("./data/Aperol_pilot_01_04_novice_C_cam1.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.04 <- speaking.data.01.04 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.01.04 <- speaking.data.01.04 %>% filter (Code == "speaking time\\teachter")
-
-speaking.data.01.04 <- sum(speaking.data.01.04$Abdeckungsgrad..)
-
-# read in data for 02_01_novice_A
-speaking.data.02.01 <- read.delim("./data/Aperol_pilot_02_01_novice_A_glasses.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.01 <- speaking.data.02.01 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.01 <- speaking.data.02.01 %>% filter (Code == "speaking time\\teacher")
-speaking.data.02.01 <- sum(speaking.data.02.01$Abdeckungsgrad..)
-
-# read in data for 02_02_novice_B
-speaking.data.02.02 <- read.delim("./data/Aperol_pilot_02_02_novice_B_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.02 <- speaking.data.02.02 %>% select(
-  Dokumentgruppe,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.02 <- speaking.data.02.02 %>% filter (Code == "speaking time\\teacher",
-                                                       Dokumentgruppe == "kodiert von Anna")
-speaking.data.02.02 <- sum(speaking.data.02.02$Abdeckungsgrad..)
-
-# read in data for 02_03_novice_C
-speaking.data.02.03 <- read.delim("./data/Aperol_pilot_02_03_novice_C_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.03 <- speaking.data.02.03 %>% select(
-  Dokumentgruppe,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.03 <- speaking.data.02.03 %>% filter (Code == "speaking time\\teachter",
-                                                       Dokumentgruppe == "02_03_kodiert von Anna")
-speaking.data.02.03 <- sum(speaking.data.02.03$Abdeckungsgrad..)
-
-# read in data for 02_04_novice_D
-speaking.data.02.04 <- read.delim("./data/Aperol_pilot_02_04_novice_D_cam1.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.04 <- speaking.data.02.04 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.04 <- speaking.data.02.04 %>% filter (Code == "speaking time\\teachter")
-speaking.data.02.04 <- sum(speaking.data.02.04$Abdeckungsgrad..)
-
-```
-
-```{r speaking plot, echo=FALSE}
-
-# read in table with coded speaking time included
-speaking.data <- read.delim("./data/plus_coded_speaking_time_questionnaire_data_0802.txt", dec=",", sep="\t", header=T)
-
-# to compare both sessions filter only Identical items
-speaking.data <- speaking.data  %>% filter(str_detect(scale, 
-                                                 paste(c("Duration of speaking time"),
-                                                    collapse = '|')))
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-speaking.data <- speaking.data %>%  mutate(value = as.numeric(value))
-
-speaking.plot <- speaking.data %>%
-  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
-    geom_boxplot() +
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    theme_light() +
-    theme(
-      legend.position="none",
-      plot.title = element_text(size=11),
-      axis.text.x = element_text(size = 8)) +
-    facet_grid(group~perspective) +
-    ggtitle("Boxplot with individual points for Duration of speaking time") +
-    xlab("")
-speaking.plot
-
-```
 
@@
 
-```{r GRItable, echo = FALSE}
+The first table provides an overview over the mean duration and number of fixation for each subject and disruptive behaviour. 
+Additionally, we calculated the Gaze Relation Index according @gegenfurtner2020gaze and the "new" Gaze Relational Index considering the Time of Interest as an important factor.
+
+```{r GRItable1, echo = FALSE}
 
 # prepare data (selected from questionnaire data)
-et.raw.data<-read.table("./data/Aperol_pilot_glasses_raw_fixation_saccades_metrics.tsv", dec=",", sep="\t", header=T)
+et.toi.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_all_TOI.tsv", dec=",", sep="\t", header=T)
 
 # converting integer to numeric
-et.raw.data <- et.raw.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
+et.toi.data <- et.toi.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
                                        Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
                                        Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
+                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations))
 
@@
 # create a basic table (tibble) using tidyverse functions
-et.raw.table <- et.raw.data %>%
-  group_by(Participant, Variable) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
+et.toi.table1 <- et.toi.data %>%
+  group_by(TOI) %>%
+  summarise("ID" = Participant,
+            "Group" = Variable1,
+            "DurTOI" = Duration_of_interval,
+            "M Dur Fix" = mean(Total_duration_of_whole_fixations),
+            "Number Fix" = Number_of_whole_fixations,
+            "TimeTOI Dur" = Duration_of_interval/mean(Total_duration_of_whole_fixations),
+            "OldGRI" = mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations,
+            "NewGRI" = (Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations)
 
@@
 apa_table(
-  et.raw.table,
-  caption = "Number and Duration (in msec) of Fixations",
+  et.toi.table1,
+  caption = "GRI",
   # note = "Write Note here", 
@@
   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
   )
@@
 ```
+
+The second table gives an overview over the mean duration of fixation, the mean number of fixation, the mean duration of an interval and the mean value with standard deviation of the "old" and "new" Gaze Relational Index.
+
+```{r GRItable2, echo = FALSE}
+
+# prepare data (selected from questionnaire data)
+et.toi.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_all_TOI.tsv", dec=",", sep="\t", header=T)
+
+# converting integer to numeric
+et.toi.data <- et.toi.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
+                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
+                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
+                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations))
+
+# calculate the GRI 
+# create a basic table (tibble) using tidyverse functions
+et.toi.table2 <- et.toi.data %>%
+  group_by(Variable1, TOI) %>%
+  rename("Group" = Variable1) %>%
+  summarise("M Fixation Duration" = mean(Total_duration_of_whole_fixations),
+            "M Number Fixation" = mean(Number_of_whole_fixations),
+            "M TOI" = mean(Duration_of_interval),
+            "M Old GRI" = mean(mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations),
+            "SD Old GRI" = sd(mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations),
+            "M New GRI" = mean((Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations),
+            "SD New GRI" = sd((Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations))
+
+# format and insert table in manuscript
+apa_table(
+  et.toi.table2,
+  caption = "GRI",
+  # note = "Write Note here", 
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  )
+
+```
+
+The third table sums up all values in table 2 for expert and novice teachers.
+
+```{r GRItable3, echo = FALSE}
+
+# prepare data (selected from questionnaire data)
+et.toi.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_all_TOI.tsv", dec=",", sep="\t", header=T)
+
+# converting integer to numeric
+et.toi.data <- et.toi.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
+                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
+                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
+                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations))
+
+# calculate the GRI 
+# create a basic table (tibble) using tidyverse functions
+et.toi.table3 <- et.toi.data %>%
+  group_by(Variable1) %>%
+  rename("Group" = Variable1) %>%
+  summarise("M Fixation Duration" = mean(Total_duration_of_whole_fixations),
+            "M Number Fixation" = mean(Number_of_whole_fixations),
+            "M TOI" = mean(Duration_of_interval),
+            "M Old GRI" = mean(mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations),
+            "SD Old GRI" = sd(mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations),
+            "M New GRI" = mean((Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations),
+            "SD New GRI" = sd((Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations))
+
+# format and insert table in manuscript
+apa_table(
+  et.toi.table3,
+  caption = "GRI",
+  # note = "Write Note here", 
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  )
+
+```
+
+The table below shows the value of the GRI for the calibration phase as the Time of Interest.
 
@@
 
+The table below shows the value of the GRI for the phase between the calibration phase and the lesson start as the Time of Interest.
+
 ```{r Calib end to lession start TOI, echo = FALSE}
@@
 ```
+\newpage
 
-```{r Disturbance "head on table" to first intervention, echo = FALSE}
+#### Plotting GRI
 
-# prepare data (selected from questionnaire data)
-et.distub.head.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_head_on_table_session1.tsv", dec=",", sep="\t", header=T)
+``` {r GRI plots, fig.width=10, fig.height = 6, echo=FALSE}
 
-# converting integer to numeric
-et.distub.head.data <- et.distub.head.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-options(digits = 2)
+### TOTAL duration of fixations during TOIs
+total.gri.plot <- ggplot(et.toi.data, aes(x = TOI, y = Total_duration_of_whole_fixations, fill = TOI)) +
+  scale_x_discrete(guide = guide_axis(angle = 70)) +
+  geom_boxplot()+
+  geom_jitter(color="black", size=0.4, alpha=0.5) +
+  facet_wrap(~ Variable1, nrow = 1)+
+  theme_light() +
+  theme(legend.position="none")+
+  labs(y = "Total Duration of Fixations in TOI", x = "TOI")
 
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.distub.head.table <- et.distub.head.data %>%
-  group_by(Participant, Variable1) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-view(et.distub.head.data)
+total.gri.plot
 
-# format and insert table in manuscript
-apa_table(
-  et.distub.head.table,
-  caption = "Number and Duration (in msec) of Fixations for Disturbance 'head on table' to first intervention",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
+### PROPORTION of duration
+
+# create wide format data set to calculate the proportion of fixations in TOIs 
+prop.dur.wide <- prop.duration %>%
+                          select(TOI, Total_duration_of_whole_fixations, Variable1) %>%
+                          group_by(TOI) %>%
+                          mutate(id=row_number()) %>%
+                          spread(TOI, Total_duration_of_whole_fixations)
+
+# create a new column with name Sum_TOI that gives the sum of all fixations in TOI 
+prop.dur.wide <- prop.dur.wide  %>% mutate(Sum_TOI = sum(`Asking question`,
+                                                        `Calibration phase`,
+                                                        `Chatting with neighbour`,
+                                                        `Clicking pen`,
+                                                        `Drawing on paper`,
+                                                        `Drumming hands`,
+                                                        `Looking at phone`,
+                                                        `Putting head on table`,
+                                                        `Yelling`))
+
+# create new columns that give proportion of the duration of TOIs
+# relative duration divided by total duration is the proportion
+prop.dur.wide <- prop.dur.wide  %>% 
+                      mutate(`Asking question` = `Asking question`/Sum_TOI)   %>% 
+                      mutate(`Calibration phase` = `Calibration phase`/Sum_TOI)   %>% 
+                      mutate(`Chatting with neighbour` = `Chatting with neighbour`/Sum_TOI)   %>% 
+                      mutate(`Clicking pen` = `Clicking pen`/Sum_TOI)   %>% 
+                      mutate(`Drawing on paper` = `Drawing on paper`/Sum_TOI) %>%
+                      mutate(`Drumming hands` = `Drumming hands`/Sum_TOI) %>%
+                      mutate(`Looking at phone` = `Looking at phone`/Sum_TOI) %>%
+                      mutate(`Putting head on table` = `Putting head on table`/Sum_TOI) %>%
+                      mutate(`Yelling` = `Yelling`/Sum_TOI)
+
+# create data set of proportions in long format for plotting
+prop.dur.long  <- gather(prop.dur.wide, TOI, Proportion, `Asking question`:`Yelling`)
+
+### Proportion of fixations during TOIs
+prop.gri.plot <- ggplot(prop.dur.long, aes(x = TOI, y = Proportion, fill = TOI)) +
+  scale_y_continuous(limits = c(0, 0.05)) +
+  geom_boxplot()+
+  facet_wrap(TOI~Variable1, nrow = 1)+
+  theme_light() +
+   theme(legend.position="none",
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank()) +
+  labs(y = "Proportion of Fixations in TOI", x = "TOI")
+
+prop.gri.plot
+
+### NUMBER of fixations during TOIs
+
+number.gri.plot <- ggplot(et.toi.data, aes(y = Number_of_whole_fixations, fill = TOI)) +
+  scale_y_continuous(limits = c(0, 100)) +
+  geom_boxplot()+
+  facet_wrap(TOI ~ Variable1, nrow = 2)+
+  theme_light() +
+  theme(legend.position="none",
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank()) +
+  labs(y = "Number of Fixations in TOI", x = "TOI")
+
+number.gri.plot
+
+### LENGTH of TOI
+### facet grid for group
+length.group.gri.plot <- ggplot(et.toi.data, aes(x = TOI, y = Duration_of_interval, fill = TOI)) +
+  geom_boxplot()+
+  geom_jitter(color="black", size=0.4, alpha=0.5) +
+  facet_grid(~ Variable1)+
+  theme_light() +
+  theme(legend.position="none")+
+  labs(y = "Length of TOI", x = "TOI")
+
+length.group.gri.plot
+
+### facet wrap for TOI
+length.toi.gri.plot <- ggplot(et.toi.data, aes(x = TOI, y = Duration_of_interval, fill = TOI)) +
+  geom_boxplot()+
+  geom_jitter(color="black", size=0.4, alpha=0.5) +
+  facet_wrap(TOI~Variable1, nrow=2)+
+  theme_light() +
+  theme(legend.position="none",
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  labs(y = "Length of TOI", x = "TOI")
+
+length.toi.gri.plot
+
+### OLD GRI
+
+### facet wrap for group
+old.gri.group.plot <- ggplot(et.toi.table1, aes(x = TOI, y = OldGRI, fill = TOI)) +
+  scale_x_discrete(guide = guide_axis(angle = 70)) +
+  geom_boxplot()+
+  geom_jitter(color="black", size=0.4, alpha=0.5) +
+  facet_wrap(~Group)+
+  theme_light() +
+  theme(legend.position="none") +
+  labs(y = "Old GRI", x = "TOI")
+
+old.gri.group.plot
+
+### facet wrap for TOI
+old.gri.toi.plot <- ggplot(et.toi.table1, aes(x = TOI, y = OldGRI, fill = TOI)) +
+  geom_boxplot()+
+  geom_jitter(color="black", size=0.4, alpha=0.5) +
+  facet_wrap(TOI~Group, nrow=2)+
+  theme_light() +
+  theme(legend.position="none",
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  labs(y = "Old GRI", x = "TOI")
+
+old.gri.toi.plot
+
+### NEW GRI
+### facet wrap for group
+new.gri.group.plot <- ggplot(et.toi.table1, aes(x = TOI, y = NewGRI, fill = TOI)) +
+  scale_x_discrete(guide = guide_axis(angle = 70)) +
+  scale_y_continuous(limits = c(0, 3))+
+  geom_boxplot()+
+  geom_jitter(color="black", size=0.4, alpha=0.5) +
+  facet_wrap(~Group)+
+  theme_light() +
+  theme(legend.position="none") +
+  labs(y = "New GRI", x = "TOI")
+
+new.gri.group.plot
+
+### facet wrap for TOI
+new.gri.toi.plot <- ggplot(et.toi.table1, aes(x = TOI, y = NewGRI, fill = TOI)) +
+  scale_y_continuous(limits = c(0, 3))+
+  geom_boxplot()+
+  geom_jitter(color="black", size=0.4, alpha=0.5) +
+  facet_wrap(TOI~Group, nrow=2)+
+  theme_light() +
+  theme(legend.position="none",
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+
+  labs(y = "New GRI", x = "TOI")
+
+new.gri.toi.plot
 

### 2021-03-17 paper_1/paper_1_supplement_et_gri.tex
update plots GRI

--- 2021-03-03 paper_1/paper_1_supplement_new_table.tex
@@
 
-\hypertarget{questionnaire-data}{%
-\subsubsection{Questionnaire data}\label{questionnaire-data}}
-
-After each mini-lesson, the students answered items on the teaching quality using a validated questionnaire (Helmke et al., 2014) and scales on the teacher's presence behavior (students n = 24).
-In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire after each mini-lesson (teachers n = 8).
-
-\hypertarget{behavioral-data}{%
-\subsubsection{Behavioral data}\label{behavioral-data}}
-
-The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab.
-Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles.
-One camera was installed to film the class from the side.
-Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back.
-Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.
-
 \hypertarget{eyetracking-data}{%
@@
 \subsection{Coding/ Data preparation/ Reliability}\label{coding-data-preparation-reliability}}
-
-\hypertarget{questionnaire-data-1}{%
-\subsubsection{Questionnaire Data}\label{questionnaire-data-1}}
-
-The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes.
-The scales on the quality of teaching are a validated questionnaire (Helmke et al., 2014).
-Whereas the scales on the teacher's presence behavior were derived from the research literature (Brophy, 1986; Kiel, Frey, Weiß, \& Weiss, 2013; Kounin, 2006; Marzano, 2007; Nolting, 2012) and were used in the pilot for the first time.
-The questionnaire is 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
-Data was obtained from N = 32 subjects (students n = 24, teachers n = 8).
-
-The following scales were assessed:
-
-\begin{enumerate}
-\def\labelenumi{(\arabic{enumi})}
-\tightlist
-\item
-  Classroom management
-\item
-  Positive climate and motivation
-\item
-  Clarity and structuredness
-\item
-  Activation and support
-\item
-  Presence: posture/gaze
-\item
-  Presence: voice
-\item
-  Presence: verbal and non-verbal intervention
-\item
-  Natural behaviour
-\end{enumerate}
-
-Table \ref{tab:table-all-scales-self-assessment} provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness \& Kurtosis of all scales for the teachers' self-assessment.
-
-\begin{verbatim}
-## Some items ( ks_sichtbar ) were negatively correlated with the total scale and 
-## probably should be reversed.  
-## To do this, run the function again with the 'check.keys=TRUE' option
-\end{verbatim}
-
-\begin{verbatim}
-## Some items ( pi_nonverbal ) were negatively correlated with the total scale and 
-## probably should be reversed.  
-## To do this, run the function again with the 'check.keys=TRUE' option
-\end{verbatim}
-
-\begin{verbatim}
-## Some items ( pi_nonverbal ) were negatively correlated with the total scale and 
-## probably should be reversed.  
-## To do this, run the function again with the 'check.keys=TRUE' option
-\end{verbatim}
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:table-all-scales-self-assessment}Scale analysis for teachers' self-assessment}
-
-\tiny{
-
-\begin{tabular}{lllllllll}
-\toprule
-scale & \multicolumn{1}{c}{N items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Cronbach's a}\\
-\midrule
-Activation and support & 3 & 2.46 & 1.14 & 1 & 4 & 0.10 & 1.65 & 0.85\\
-Clarity and structuredness & 2 & 2.81 & 0.91 & 1 & 4 & -0.17 & 2.17 & -0.76\\
-Classroom management & 4 & 2.44 & 0.88 & 1 & 4 & 0.19 & 2.38 & 0.83\\
-Natural behaviour & 3 & 2.83 & 0.76 & 2 & 4 & 0.28 & 1.84 & 0.90\\
-Positive climate and motivation & 6 & 2.85 & 0.87 & 1 & 4 & -0.49 & 2.65 & 0.78\\
-Presence: posture/gaze & 7 & 2.70 & 1.01 & 1 & 4 & -0.44 & 2.15 & 0.85\\
-Presence: verbal and non-verbal intervention & 3 & 2.75 & 0.79 & 1 & 4 & -0.07 & 2.48 & -0.75\\
-Presence: voice & 3 & 2.79 & 0.72 & 2 & 4 & 0.32 & 2.03 & 0.77\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-Table \ref{tab:table-all-scales-students} provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness \& Kurtosis of all scales for the students' perception of the teacher's behaviour in class.
-
-\begin{verbatim}
-## Some items ( phb_stand ) were negatively correlated with the total scale and 
-## probably should be reversed.  
-## To do this, run the function again with the 'check.keys=TRUE' option
-\end{verbatim}
-
-\begin{verbatim}
-## Some items ( pi_direkt ) were negatively correlated with the total scale and 
-## probably should be reversed.  
-## To do this, run the function again with the 'check.keys=TRUE' option
-\end{verbatim}
-
-\begin{verbatim}
-## Some items ( phb_stand ) were negatively correlated with the total scale and 
-## probably should be reversed.  
-## To do this, run the function again with the 'check.keys=TRUE' option
-\end{verbatim}
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:table-all-scales-students}Scale analysis for students' perspective}
-
-\tiny{
-
-\begin{tabular}{lllllllll}
-\toprule
-scale & \multicolumn{1}{c}{N items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Cronbach's a}\\
-\midrule
-Activation and support & 3 & 2.64 & 1.13 & 1 & 4 & -0.32 & 1.73 & 0.48\\
-Clarity and structuredness & 2 & 3.58 & 0.68 & 1 & 4 & -1.75 & 6.09 & 0.62\\
-Classroom management & 4 & 3.18 & 0.91 & 1 & 4 & -0.87 & 2.86 & 0.75\\
-Natural behaviour & 3 & 3.43 & 0.67 & 2 & 4 & -0.74 & 2.46 & 0.85\\
-Positive climate and motivation & 6 & 3.41 & 0.83 & 1 & 4 & -1.40 & 4.29 & 0.82\\
-Presence: posture/gaze & 7 & 3.24 & 0.89 & 1 & 4 & -1.05 & 3.31 & 0.59\\
-Presence: verbal and non-verbal intervention & 3 & 3.18 & 0.81 & 1 & 4 & -0.66 & 2.70 & 0.20\\
-Presence: voice & 3 & 3.60 & 0.60 & 2 & 4 & -1.18 & 3.36 & 0.71\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\newpage
-
-The individual items of a scale are further represented in graphs.
-
-\begin{enumerate}
-\def\labelenumi{(\arabic{enumi})}
-\tightlist
-\item
-  Classroom management
-  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Line Plots Classroom Management-1.pdf}
-  \newpage
-\item
-  Positive climate and motivation
-  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Positive climate and motivation line plots-1.pdf}
-  \newpage
-\item
-  Clarity and structuredness
-  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Clarity and structuredness line plots-1.pdf}
-  \newpage
-\item
-  Activation and support
-  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Activation and support line plots-1.pdf}
-  \newpage
-\end{enumerate}
-
-\begin{figure}
-
-{\centering \includegraphics[width=5.33in]{./pictures/presenceposturegaze}
-
-}
-
-\caption{(5) Presence: posture/gaze}\label{fig:presenceposturegaze}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-
-{\centering \includegraphics[width=5.33in]{./pictures/presencevoice}
-
-}
-
-\caption{(6) Presence: voice}\label{fig:presencevoice}
-\end{figure}
-\newpage
-
-\begin{figure}
-
-{\centering \includegraphics[width=5.33in]{./pictures/presenceverbalnonverbalintervention}
-
-}
-
-\caption{(7) Presence: verbal and non-verbal intervention}\label{fig:presenceverbalnonverbalintervention}
-\end{figure}
-\newpage
-
-\begin{enumerate}
-\def\labelenumi{(\arabic{enumi})}
-\setcounter{enumi}{7}
-\tightlist
-\item
-  Natural behaviour
-  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Natural behaviour line plots-1.pdf}
-  \newpage
-  In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
-\end{enumerate}
-
-\begin{figure}
-\centering
-\includegraphics{paper_1_supplement_new_table_files/figure-latex/boxplot scales-1.pdf}
-\caption{(\#fig:boxplot scales)Boxplots and individual data for experts and novices}
-\end{figure}
-
-\newpage
-
-\hypertarget{behavioral-data-1}{%
-\subsubsection{Behavioral Data}\label{behavioral-data-1}}
-
-The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz \& Rädiker, 2019). The following coding scheme was developed:
-
-\begin{itemize}
-\item
-  phase - lesson begin, state event: teacher starts the lesson with a noise, talk, taking a position in class
-\item
-  phase - lesson end, state event: teacher finishes the lesson with a noise, talk, taking a position in class
-\item
-  phase - organization/transition points, state event: any situation that does not imply effective learning time (fetching chalk, working material, organizing desks, opening windows, printing work results etc.)
-\item
-  phase - single, state event: any individual student activity on a given task (reading, writing, drawing etc.)
-\item
-  phase - group, state event: any student activity on a given task together in a group of at least 3 students (reading, writing, drawing etc.)
-\item
-  phase - class discussion, state event: discussion in class, teacher talks to class/individual/group
-\item
-  phase - pair: state event: any student activity on a given task together in a team of 2 students (reading, writing, drawing etc.)
-\item
-  phase - teachers lecture, state event: any teacher's presentation on a certain topic which maybe supported by a PPP, PREZI, notes on board, OHP etc.
-\item
-  phase - other, state event: not categorizable
-\item
-  phase - break, state event: e.g.~drinking, relaxation exercises
-\item
-  phase - external interruption, state event: external interruptions (e.g.~fire alarm, technical problems, other teachers coming into the room)
-\item
-  speaking time - teacher, state event
-\item
-  speaking time - students, state event
-\item
-  disruption - chatting with neighbor, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - asking a question, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - yelling, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - looking at phone, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - staring out of window, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - drawing, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - head on table, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - clicking pen, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - drumming hands, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - walking around, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\end{itemize}
-
-First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher.
-The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.
-
-\includegraphics{paper_1_supplement_new_table_files/figure-latex/speaking plot-1.pdf}
 
@@
 
+The first table provides an overview over the
+
 \begin{table}[h]
@@
 
-\caption{\label{tab:GRItable}Number and Duration (in msec) of Fixations}
+\caption{\label{tab:GRItable1}GRI}
 
-\scriptsize{
+\tiny{
 
-\begin{tabular}{lllllll}
+\begin{tabular}{lllllllll}
 \toprule
-Participant & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
+TOI & \multicolumn{1}{c}{ID} & \multicolumn{1}{c}{Group} & \multicolumn{1}{c}{DurTOI} & \multicolumn{1}{c}{M Dur Fix} & \multicolumn{1}{c}{Number Fix} & \multicolumn{1}{c}{TimeTOI Dur} & \multicolumn{1}{c}{OldGRI} & \multicolumn{1}{c}{NewGRI}\\
 \midrule
-01\_01\_D & Expert & 803.00 & 316,571.00 & 394.00 & 781,978.00 & 0.49\\
-01\_02\_A & Expert & 1,070.00 & 385,812.00 & 361.00 & 838,026.00 & 0.34\\
-01\_03\_B & Novice & 617.00 & 374,315.00 & 607.00 & 744,444.00 & 0.98\\
-01\_04\_C & Novice & 769.00 & 384,537.00 & 500.00 & 723,922.00 & 0.65\\
-02\_01\_A & Novice & 569.00 & 101,541.00 & 178.00 & 729,762.00 & 0.31\\
-02\_02\_B & Novice & 1,140.00 & 520,431.00 & 457.00 & 730,565.00 & 0.40\\
-02\_03\_C & Novice & 1,048.00 & 469,018.00 & 448.00 & 737,604.00 & 0.43\\
-02\_04\_D & Novice & 613.00 & 438,655.00 & 716.00 & 747,729.00 & 1.17\\
+Asking question & 01\_04\_C & Novice & 3,869.00 & 2,925.62 & 3.00 & 1.32 & 975.21 & 0.44\\
+Asking question & 01\_02\_A & Expert & 7,112.00 & 2,925.62 & 13.00 & 2.43 & 225.05 & 0.19\\
+Asking question & 01\_03\_B & Novice & 12,863.00 & 2,925.62 & 4.00 & 4.40 & 731.41 & 1.10\\
+Asking question & 01\_01\_D & Expert & 7,648.00 & 2,925.62 & 7.00 & 2.61 & 417.95 & 0.37\\
+Asking question & 02\_01\_A & Novice & 7,422.00 & 2,925.62 & 3.00 & 2.54 & 975.21 & 0.85\\
+Asking question & 02\_02\_B & Novice & 7,082.00 & 2,925.62 & 9.00 & 2.42 & 325.07 & 0.27\\
+Asking question & 02\_03\_C & Novice & 8,045.00 & 2,925.62 & 8.00 & 2.75 & 365.70 & 0.34\\
+Asking question & 02\_04\_D & Novice & 6,595.00 & 2,925.62 & 6.00 & 2.25 & 487.60 & 0.38\\
+Calibration phase & 01\_04\_C & Novice & 17,224.00 & 12,275.12 & 14.00 & 1.40 & 876.79 & 0.10\\
+Calibration phase & 01\_02\_A & Expert & 13,335.00 & 12,275.12 & 10.00 & 1.09 & 1,227.51 & 0.11\\
+Calibration phase & 01\_03\_B & Novice & 10,615.00 & 12,275.12 & 17.00 & 0.86 & 722.07 & 0.05\\
+Calibration phase & 01\_01\_D & Expert & 16,470.00 & 12,275.12 & 9.00 & 1.34 & 1,363.90 & 0.15\\
+Calibration phase & 02\_01\_A & Novice & 17,902.00 & 12,275.12 & 13.00 & 1.46 & 944.24 & 0.11\\
+Calibration phase & 02\_02\_B & Novice & 12,325.00 & 12,275.12 & 12.00 & 1.00 & 1,022.93 & 0.08\\
+Calibration phase & 02\_03\_C & Novice & 16,494.00 & 12,275.12 & 18.00 & 1.34 & 681.95 & 0.07\\
+Calibration phase & 02\_04\_D & Novice & 20,964.00 & 12,275.12 & 14.00 & 1.71 & 876.79 & 0.12\\
+Chatting with neighbour & 01\_04\_C & Novice & 9,843.00 & 4,070.12 & 27.00 & 2.42 & 150.75 & 0.09\\
+Chatting with neighbour & 01\_02\_A & Expert & 2,607.00 & 4,070.12 & 1.00 & 0.64 & 4,070.12 & 0.64\\
+Chatting with neighbour & 01\_03\_B & Novice & 11,060.00 & 4,070.12 & 10.00 & 2.72 & 407.01 & 0.27\\
+Chatting with neighbour & 01\_01\_D & Expert & 6,612.00 & 4,070.12 & 3.00 & 1.62 & 1,356.71 & 0.54\\
+Chatting with neighbour & 02\_01\_A & Novice & 7,429.00 & 4,070.12 & 5.00 & 1.83 & 814.02 & 0.37\\
+Chatting with neighbour & 02\_02\_B & Novice & 8,397.00 & 4,070.12 & 11.00 & 2.06 & 370.01 & 0.19\\
+Chatting with neighbour & 02\_03\_C & Novice & 11,713.00 & 4,070.12 & 11.00 & 2.88 & 370.01 & 0.26\\
+Chatting with neighbour & 02\_04\_D & Novice & 11,443.00 & 4,070.12 & 4.00 & 2.81 & 1,017.53 & 0.70\\
+Clicking pen & 01\_04\_C & Novice & 12,980.00 & 8,809.75 & 4.00 & 1.47 & 2,202.44 & 0.37\\
+Clicking pen & 01\_02\_A & Expert & 12,071.00 & 8,809.75 & 20.00 & 1.37 & 440.49 & 0.07\\
+Clicking pen & 01\_03\_B & Novice & 26,272.00 & 8,809.75 & 16.00 & 2.98 & 550.61 & 0.19\\
+Clicking pen & 01\_01\_D & Expert & 11,597.00 & 8,809.75 & 11.00 & 1.32 & 800.89 & 0.12\\
+Clicking pen & 02\_01\_A & Novice & 16,114.00 & 8,809.75 & 11.00 & 1.83 & 800.89 & 0.17\\
+Clicking pen & 02\_02\_B & Novice & 9,409.00 & 8,809.75 & 12.00 & 1.07 & 734.15 & 0.09\\
+Clicking pen & 02\_03\_C & Novice & 16,269.00 & 8,809.75 & 27.00 & 1.85 & 326.29 & 0.07\\
+Clicking pen & 02\_04\_D & Novice & 24,220.00 & 8,809.75 & 19.00 & 2.75 & 463.67 & 0.14\\
+Drawing on paper & 01\_04\_C & Novice & 39,979.00 & 34,414.38 & 27.00 & 1.16 & 1,274.61 & 0.04\\
+Drawing on paper & 01\_02\_A & Expert & 44,971.00 & 34,414.38 & 87.00 & 1.31 & 395.57 & 0.02\\
+Drawing on paper & 01\_03\_B & Novice & 129,708.00 & 34,414.38 & 79.00 & 3.77 & 435.62 & 0.05\\
+Drawing on paper & 01\_01\_D & Expert & 74,511.00 & 34,414.38 & 92.00 & 2.17 & 374.07 & 0.02\\
+Drawing on paper & 02\_01\_A & Novice & 43,469.00 & 34,414.38 & 31.00 & 1.26 & 1,110.14 & 0.04\\
+Drawing on paper & 02\_02\_B & Novice & 147,788.00 & 34,414.38 & 295.00 & 4.29 & 116.66 & 0.01\\
+Drawing on paper & 02\_03\_C & Novice & 26,495.00 & 34,414.38 & 46.00 & 0.77 & 748.14 & 0.02\\
+Drawing on paper & 02\_04\_D & Novice & 27,915.00 & 34,414.38 & 11.00 & 0.81 & 3,128.58 & 0.07\\
+Drumming hands & 01\_04\_C & Novice & 43,507.00 & 11,415.88 & 41.00 & 3.81 & 278.44 & 0.09\\
+Drumming hands & 01\_02\_A & Expert & 20,530.00 & 11,415.88 & 27.00 & 1.80 & 422.81 & 0.07\\
+Drumming hands & 01\_03\_B & Novice & 12,615.00 & 11,415.88 & 6.00 & 1.11 & 1,902.65 & 0.18\\
+Drumming hands & 01\_01\_D & Expert & 23,121.00 & 11,415.88 & 17.00 & 2.03 & 671.52 & 0.12\\
+Drumming hands & 02\_01\_A & Novice & 62,326.00 & 11,415.88 & 50.00 & 5.46 & 228.32 & 0.11\\
+Drumming hands & 02\_02\_B & Novice & 24,699.00 & 11,415.88 & 25.00 & 2.16 & 456.64 & 0.09\\
+Drumming hands & 02\_03\_C & Novice & 27,775.00 & 11,415.88 & 49.00 & 2.43 & 232.98 & 0.05\\
+Drumming hands & 02\_04\_D & Novice & 14,998.00 & 11,415.88 & 9.00 & 1.31 & 1,268.43 & 0.15\\
+Looking at phone & 01\_04\_C & Novice & 7,984.00 & 11,563.00 & 8.00 & 0.69 & 1,445.38 & 0.09\\
+Looking at phone & 01\_02\_A & Expert & 19,897.00 & 11,563.00 & 28.00 & 1.72 & 412.96 & 0.06\\
+Looking at phone & 01\_03\_B & Novice & 40,427.00 & 11,563.00 & 30.00 & 3.50 & 385.43 & 0.12\\
+Looking at phone & 01\_01\_D & Expert & 32,387.00 & 11,563.00 & 29.00 & 2.80 & 398.72 & 0.10\\
+Looking at phone & 02\_01\_A & Novice & 33,557.00 & 11,563.00 & 14.00 & 2.90 & 825.93 & 0.21\\
+Looking at phone & 02\_02\_B & Novice & 16,321.00 & 11,563.00 & 19.00 & 1.41 & 608.58 & 0.07\\
+Looking at phone & 02\_03\_C & Novice & 28,223.00 & 11,563.00 & 47.00 & 2.44 & 246.02 & 0.05\\
+Looking at phone & 02\_04\_D & Novice & 31,944.00 & 11,563.00 & 19.00 & 2.76 & 608.58 & 0.15\\
+Putting head on table & 01\_04\_C & Novice & 20,929.00 & 17,049.88 & 38.00 & 1.23 & 448.68 & 0.03\\
+Putting head on table & 01\_02\_A & Expert & 23,402.00 & 17,049.88 & 27.00 & 1.37 & 631.48 & 0.05\\
+Putting head on table & 01\_03\_B & Novice & 39,159.00 & 17,049.88 & 41.00 & 2.30 & 415.85 & 0.06\\
+Putting head on table & 01\_01\_D & Expert & 6,354.00 & 17,049.88 & 4.00 & 0.37 & 4,262.47 & 0.09\\
+Putting head on table & 02\_01\_A & Novice & 51,225.00 & 17,049.88 & 45.00 & 3.00 & 378.89 & 0.07\\
+Putting head on table & 02\_02\_B & Novice & 11,322.00 & 17,049.88 & 20.00 & 0.66 & 852.49 & 0.03\\
+Putting head on table & 02\_03\_C & Novice & 61,713.00 & 17,049.88 & 81.00 & 3.62 & 210.49 & 0.04\\
+Putting head on table & 02\_04\_D & Novice & 57,484.00 & 17,049.88 & 42.00 & 3.37 & 405.95 & 0.08\\
+Yelling & 01\_04\_C & Novice & 6,083.00 & 889.50 & 1.00 & 6.84 & 889.50 & 6.84\\
+Yelling & 01\_02\_A & Expert & 1,995.00 & 889.50 & 1.00 & 2.24 & 889.50 & 2.24\\
+Yelling & 01\_03\_B & Novice & 6,527.00 & 889.50 & 1.00 & 7.34 & 889.50 & 7.34\\
+Yelling & 01\_01\_D & Expert & 2,245.00 & 889.50 & 1.00 & 2.52 & 889.50 & 2.52\\
+Yelling & 02\_01\_A & Novice & 9,105.00 & 889.50 & 7.00 & 10.24 & 127.07 & 1.46\\
+Yelling & 02\_02\_B & Novice & 2,548.00 & 889.50 & 5.00 & 2.86 & 177.90 & 0.57\\
+Yelling & 02\_03\_C & Novice & 2,992.00 & 889.50 & 2.00 & 3.36 & 444.75 & 1.68\\
+Yelling & 02\_04\_D & Novice & 12,416.00 & 889.50 & 1.00 & 13.96 & 889.50 & 13.96\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:GRItable2}GRI}
+
+\tiny{
+
+\begin{tabular}{lllllllll}
+\toprule
+Group & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{M Fixation Duration} & \multicolumn{1}{c}{M Number Fixation} & \multicolumn{1}{c}{M TOI} & \multicolumn{1}{c}{M Old GRI} & \multicolumn{1}{c}{SD Old GRI} & \multicolumn{1}{c}{M New GRI} & \multicolumn{1}{c}{SD New GRI}\\
+\midrule
+Expert & Asking question & 2,108.50 & 10.00 & 7,380.00 & 231.70 & 98.30 & 0.39 & 0.18\\
+Expert & Calibration phase & 12,283.00 & 9.50 & 14,902.50 & 1,296.54 & 96.50 & 0.13 & 0.03\\
+Expert & Chatting with neighbour & 1,829.00 & 2.00 & 4,609.50 & 1,219.33 & 862.20 & 1.32 & 0.16\\
+Expert & Clicking pen & 5,416.50 & 15.50 & 11,834.00 & 381.62 & 156.68 & 0.15 & 0.06\\
+Expert & Drawing on paper & 25,514.50 & 89.50 & 59,741.00 & 285.30 & 11.27 & 0.03 & 0.01\\
+Expert & Drumming hands & 8,405.00 & 22.00 & 21,825.50 & 402.85 & 129.48 & 0.13 & 0.05\\
+Expert & Looking at phone & 8,484.50 & 28.50 & 26,142.00 & 297.79 & 7.39 & 0.11 & 0.03\\
+Expert & Putting head on table & 7,605.50 & 15.50 & 14,878.00 & 1,091.53 & 1,145.29 & 0.16 & 0.07\\
+Expert & Yelling & 580.00 & 1.00 & 2,120.00 & 580.00 & 0.00 & 3.66 & 0.30\\
+Novice & Asking question & 3,198.00 & 5.50 & 7,646.00 & 703.26 & 320.81 & 0.51 & 0.30\\
+Novice & Calibration phase & 12,272.50 & 14.67 & 15,920.67 & 853.95 & 130.15 & 0.09 & 0.03\\
+Novice & Chatting with neighbour & 4,817.17 & 11.33 & 9,980.83 & 617.28 & 384.64 & 0.26 & 0.18\\
+Novice & Clicking pen & 9,940.83 & 14.83 & 17,544.00 & 955.00 & 774.90 & 0.15 & 0.09\\
+Novice & Drawing on paper & 37,381.00 & 81.50 & 69,225.67 & 1,233.52 & 1,156.72 & 0.04 & 0.02\\
+Novice & Drumming hands & 12,419.50 & 30.00 & 30,986.67 & 791.90 & 760.35 & 0.10 & 0.04\\
+Novice & Looking at phone & 12,589.17 & 22.83 & 26,409.33 & 747.59 & 459.89 & 0.10 & 0.05\\
+Novice & Putting head on table & 20,198.00 & 44.50 & 40,305.33 & 535.53 & 252.70 & 0.04 & 0.02\\
+Novice & Yelling & 992.67 & 2.83 & 6,611.83 & 635.78 & 409.08 & 4.76 & 4.60\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:GRItable3}GRI}
+
+\tiny{
+
+\begin{tabular}{llllllll}
+\toprule
+Group & \multicolumn{1}{c}{M Fixation Duration} & \multicolumn{1}{c}{M Number Fixation} & \multicolumn{1}{c}{M TOI} & \multicolumn{1}{c}{M Old GRI} & \multicolumn{1}{c}{SD Old GRI} & \multicolumn{1}{c}{M New GRI} & \multicolumn{1}{c}{SD New GRI}\\
+\midrule
+Expert & 8,025.17 & 21.50 & 18,159.17 & 1,953.05 & 2,871.09 & 0.16 & 0.08\\
+Novice & 12,645.43 & 25.33 & 24,958.93 & 1,878.32 & 2,902.64 & 0.13 & 0.15\\
 \bottomrule
@@
 
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:Disturbance "head on table" to first intervention}Number and Duration (in msec) of Fixations for Disturbance 'head on table' to first intervention}
-
-\scriptsize{
-
-\begin{tabular}{lllllll}
-\toprule
-Participant & \multicolumn{1}{c}{Variable1} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
-\midrule
-01\_01\_D & Expert & 3.00 & 2,079.00 & 693.00 & 5,735.00 & 231.00\\
-01\_02\_A & Expert & 7.00 & 2,778.00 & 397.00 & 8,454.00 & 56.71\\
-01\_03\_B & Novice & 1.00 & 460.00 & 460.00 & 3,493.00 & 460.00\\
-01\_04\_C & Novice & 29.00 & 12,653.00 & 436.00 & 16,245.00 & 15.03\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
 \hypertarget{data-analysis}{%
@@
 
-\hypertarget{questionnaire-data-2}{%
-\subsubsection{Questionnaire Data}\label{questionnaire-data-2}}
+\hypertarget{questionnaire-data}{%
+\subsubsection{Questionnaire Data}\label{questionnaire-data}}
 
-\hypertarget{behavioral-data-2}{%
-\subsubsection{Behavioral Data}\label{behavioral-data-2}}
+\hypertarget{behavioral-data}{%
+\subsubsection{Behavioral Data}\label{behavioral-data}}
 
@@
 
-\hypertarget{questionnaire-data-3}{%
-\subsubsection{Questionnaire Data}\label{questionnaire-data-3}}
+\hypertarget{questionnaire-data-1}{%
+\subsubsection{Questionnaire Data}\label{questionnaire-data-1}}
 
-\hypertarget{behavioral-data-3}{%
-\subsubsection{Behavioral Data}\label{behavioral-data-3}}
+\hypertarget{behavioral-data-1}{%
+\subsubsection{Behavioral Data}\label{behavioral-data-1}}
 
@@
 
-\leavevmode\hypertarget{ref-brophy1986classroom}{}%
-Brophy, J. (1986). Classroom management techniques. \emph{Education and Urban Society}, \emph{18}(2), 182--194.
-
 \leavevmode\hypertarget{ref-cortina2015low}{}%
@@
 
-\leavevmode\hypertarget{ref-helmke2014unterrichtsdiagnostik}{}%
-Helmke, A., Helmke, T., Lenske, G., Pham, G., Praetorius, A.-K., Schrader, F.-W., \& AdeThurow, M.
-(2014).
-Unterrichtsdiagnostik mit EMU.
-\emph{Aus-Und Fortbildung Der Lehrkr{ä}fte in Hinblick Auf Verbesserung Der Diagnosef{ä}higkeit, Umgang Mit Heterogenit{ä}t Und Individuelle F{ö}rderung}, 149--163.
-
 \leavevmode\hypertarget{ref-R-purrr}{}%
@@
 
-\leavevmode\hypertarget{ref-kiel2013trainingsbuch}{}%
-Kiel, E., Frey, A., Weiß, S., \& Weiss, S. (2013). \emph{Trainingsbuch klassenf{ü}hrung} (Vol. 3992). UTB.
-
 \leavevmode\hypertarget{ref-R-moments}{}%
 Komsta, L., \& Novomestky, F. (2015). \emph{Moments: Moments, cumulants, skewness, kurtosis and related tests}. Retrieved from \url{https://CRAN.R-project.org/package=moments}
-
-\leavevmode\hypertarget{ref-kounin2006techniken}{}%
-Kounin, J. S. (2006). \emph{Techniken der klassenf{ü}hrung}. Waxmann Verlag.
-
-\leavevmode\hypertarget{ref-kuckartz2019analyzing}{}%
-Kuckartz, U., \& Rädiker, S. (2019). \emph{Analyzing qualitative data with MAXQDA}. Springer.
 
@@
 
-\leavevmode\hypertarget{ref-marzano2007art}{}%
-Marzano, R. J. (2007). \emph{The art and science of teaching: A comprehensive framework for effective instruction}. Ascd.
-
 \leavevmode\hypertarget{ref-messner2000berufliche}{}%
@@
 Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
-
-\leavevmode\hypertarget{ref-nolting2012storungen}{}%
-Nolting, H.-P. (2012). \emph{St{ö}rungen in der schulklasse}. Beltz.
 

### 2021-05-20 paper_1/paper_1_supplement_et_aoi.Rmd
update manual AOIs

@@
 
-#### Areas of Interest (GRI)
+#### DYNAMIC Areas of Interest (AOI)
 
-``` {r AOIs, echo=FALSE} 
+``` {r dAOIs, echo=FALSE} 
 if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
@@
 
+#### MANUAL Areas of Interest (AOI)
+
+``` {r mAOIs, echo=FALSE} 
+if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
+if (!require(papaja)) install.packages('papaja'); library(papaja)
+if (!require(psych)) install.packages('psych'); library(psych) # stats
+if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
+if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
+
+# prepare data (selected from AOI data)
+et.raw.data<-read.table("./Aperol_pilot_AOI_glasses_metrics_session01.txt", dec=",", sep="\t", header=T)
+
+# convert into numeric
+et.raw.data <- et.raw.data %>%  mutate(Total.duration.of.fixation.in.AOI..sec. = as.numeric(Total.duration.of.fixation.in.AOI..sec.),
+                                       Average.duration.of.fixation.in.AOI..sec. = as.numeric(Average.duration.of.fixation.in.AOI..sec.),
+                                       Number.of.fixations.in.AOI = as.numeric (Number.of.fixations.in.AOI),
+                                       Total.Time.of.Interest.Duration..sec. = as.numeric(Total.Time.of.Interest.Duration..sec.))
+
+# create a basic table (tibble) using tidyverse functions for all disruptions 
+# Change Number of Digits in Global R Options to reduce the number of digits after the decimal point to two
+options(digits = 2)
+
+et.table <- et.raw.data %>%
+  group_by(Type.of.disruption, Group) %>%
+  filter(Type.of.disruption != "staring out the window") %>%
+  rename ('Type of Disruption' = Type.of.disruption) %>%
+  summarise("Mean Duration of Fixations" = mean(Total.duration.of.fixation.in.AOI..sec.),
+            "Number of Fixations" = mean(Number.of.fixations.in.AOI),
+            "TOI" = mean(Total.Time.of.Interest.Duration..sec.))
+
+# create a new column with name Total that gives the sum duration in sec of looking at all AOIs
+et.raw.data <- et.raw.data %>% mutate(Total = sum(Total.duration.of.fixation.in.AOI..sec.))
+
+# create new columns that give proportion of the duration of looking at AOIs
+# relative duration divided by total duration is the proportion
+proportion.et.data <- et.raw.data %>% group_by(Group, Type.of.disruption) %>% 
+                                      mutate(Proportion = Total.duration.of.fixation.in.AOI..sec./Total)
+
+### Plot data TOTAL
+total.plot <- ggplot(et.raw.data, aes(x = Type.of.disruption, y = Total.duration.of.fixation.in.AOI..sec., fill = Type.of.disruption)) +
+  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
+  scale_x_discrete(guide = guide_axis(angle = 70)) +
+  geom_boxplot()+
+  geom_jitter(color="black", size=0.4, alpha=0.5) +
+  facet_wrap(~ Group, nrow = 1)+
+  theme_light() +
+  theme(legend.position="none")+
+  labs(y = "Total Duration of Looking at AOIs in sec", x = "AOI")
+
+total.plot
+
+### Plot data PROPORTIONS
+prop.plot <- ggplot(proportion.et.data, aes(x = Type.of.disruption, y = Proportion, fill = Type.of.disruption)) +
+  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
+  scale_x_discrete(guide = guide_axis(angle = 70)) +
+  geom_boxplot()+
+  facet_wrap(~ Group, nrow = 1)+
+  theme_light() +
+  theme(legend.position="none")+
+  labs(y = "Proportion of Looking at AOIs", x = "AOI")
+
+prop.plot
+
+### Plot Number of Fixations
+number.plot <- ggplot(et.raw.data, aes(x = Type.of.disruption, y = Number.of.fixations.in.AOI, fill = Type.of.disruption)) +
+  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
+  scale_x_discrete(guide = guide_axis(angle = 70)) +
+  geom_boxplot()+
+  geom_jitter(color="black", size=0.4, alpha=0.5) +
+  facet_wrap(~ Group, nrow = 1)+
+  theme_light() +
+  theme(legend.position="none")+
+  labs(y = "Number of Fixations in AOI", x = "AOI")
+
+number.plot
+
+# ### Plot Average duration of fixation
+# average.plot <- ggplot(et.table, aes(x = "Type of Disruption", y = "Mean Duration of Fixations", fill = "Type of Disruption")) +
+#   scale_x_discrete(guide = guide_axis(angle = 70)) +
+#   geom_bar(aes(y="Mean Duration of Fixations")) + 
+#   facet_wrap(~ Group)+
+#   theme_light() +
+#   theme(legend.position="none")+
+#   labs(y = "Average Duration of Looking at AOIs in sec", x = "AOI")
+# 
+# average.plot
+
+```
+
 ## Data analysis

### 2021-05-20 paper_1/paper_1_supplement_et_aoi.Rmd
update AOI plots

@@
 # prepare data (selected from AOI data)
-et.raw.data<-read.table("./Aperol_pilot_AOI_glasses_metrics_session01.txt", dec=",", sep="\t", header=T)
+et.raw.data<-read.table("./data/Aperol_pilot_AOI_glasses_metrics_session01.txt", dec=",", sep="\t", header=T)
 
 # convert into numeric
-et.raw.data <- et.raw.data %>%  mutate(Total.duration.of.fixation.in.AOI..sec. = as.numeric(Total.duration.of.fixation.in.AOI..sec.),
-                                       Average.duration.of.fixation.in.AOI..sec. = as.numeric(Average.duration.of.fixation.in.AOI..sec.),
-                                       Number.of.fixations.in.AOI = as.numeric (Number.of.fixations.in.AOI),
-                                       Total.Time.of.Interest.Duration..sec. = as.numeric(Total.Time.of.Interest.Duration..sec.))
+et.raw.data <- et.raw.data %>%  mutate(Total_duration_of_fixations = as.numeric(Total_duration_of_fixations),
+                                       Average_duration_of_fixations = as.numeric(Average_duration_of_fixations),
+                                       Number_of_fixations = as.numeric (Number_of_fixations),
+                                       Total_duration_of_Visit = as.numeric(Total_duration_of_Visit))
 
@@
 et.table <- et.raw.data %>%
-  group_by(Type.of.disruption, Group) %>%
-  filter(Type.of.disruption != "staring out the window") %>%
-  rename ('Type of Disruption' = Type.of.disruption) %>%
-  summarise("Mean Duration of Fixations" = mean(Total.duration.of.fixation.in.AOI..sec.),
-            "Number of Fixations" = mean(Number.of.fixations.in.AOI),
-            "TOI" = mean(Total.Time.of.Interest.Duration..sec.))
+  group_by(Group, AOI) %>%
+  summarise("Mean Duration of Fixations" = mean(Total_duration_of_fixations),
+            "Number of Fixations" = mean(Number_of_fixations),
+            "Mean Duration of Visits" = mean(Total_duration_of_Visit))
 
-# create a new column with name Total that gives the sum duration in sec of looking at all AOIs
-et.raw.data <- et.raw.data %>% mutate(Total = sum(Total.duration.of.fixation.in.AOI..sec.))
+view(et.table)
+
+#FIXATIONS
+# create a new column with name Total that gives the sum duration in msec of looking at all AOIs
+et.raw.data <- et.raw.data %>% mutate(total_fixations = sum(Total_duration_of_fixations))
 
@@
 # relative duration divided by total duration is the proportion
-proportion.et.data <- et.raw.data %>% group_by(Group, Type.of.disruption) %>% 
-                                      mutate(Proportion = Total.duration.of.fixation.in.AOI..sec./Total)
+proportion.et.data <- et.raw.data %>% group_by(Group, AOI) %>% 
+                                      mutate(proportion_fixations = Total_duration_of_fixations/total_fixations)
 
-### Plot data TOTAL
-total.plot <- ggplot(et.raw.data, aes(x = Type.of.disruption, y = Total.duration.of.fixation.in.AOI..sec., fill = Type.of.disruption)) +
+#VISITS
+# create a new column with name Total that gives the sum duration in msec of visits in AOIs
+et.raw.data <- et.raw.data %>% mutate(total_visits = sum(Total_duration_of_Visit))
+
+# create new columns that give proportion of the duration of looking at AOIs
+# relative duration divided by total duration is the proportion
+proportion.et.data <- et.raw.data %>% group_by(Group, AOI) %>% 
+                                      mutate(proportion_visits = Total_duration_of_Visit/Total)
+
+### Plot data TOTAL FIXATIONS
+total.fix.plot <- ggplot(et.raw.data, aes(x = AOI, y = Total_duration_of_fixations, fill = AOI)) +
   scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
@@
   theme(legend.position="none")+
-  labs(y = "Total Duration of Looking at AOIs in sec", x = "AOI")
+  labs(y = "Total Duration of Looking at AOIs", x = "AOI")
 
-total.plot
+total.fix.plot
 
-### Plot data PROPORTIONS
-prop.plot <- ggplot(proportion.et.data, aes(x = Type.of.disruption, y = Proportion, fill = Type.of.disruption)) +
+### Plot data PROPORTIONS FIXATIONS
+prop.fix.plot <- ggplot(proportion.et.data, aes(x = AOI, y = proportion_fixations, fill = AOI)) +
   scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
@@
 
-prop.plot
+prop.fix.plot
 
 ### Plot Number of Fixations
-number.plot <- ggplot(et.raw.data, aes(x = Type.of.disruption, y = Number.of.fixations.in.AOI, fill = Type.of.disruption)) +
+number.plot <- ggplot(et.raw.data, aes(x = AOI, y = Number_of_fixations, fill = AOI)) +
   scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
@@
 
-number.plot
+number.fix.plot
 
-# ### Plot Average duration of fixation
-# average.plot <- ggplot(et.table, aes(x = "Type of Disruption", y = "Mean Duration of Fixations", fill = "Type of Disruption")) +
-#   scale_x_discrete(guide = guide_axis(angle = 70)) +
-#   geom_bar(aes(y="Mean Duration of Fixations")) + 
-#   facet_wrap(~ Group)+
-#   theme_light() +
-#   theme(legend.position="none")+
-#   labs(y = "Average Duration of Looking at AOIs in sec", x = "AOI")
-# 
-# average.plot
+### Plot data TOTAL VISITS
+total.visit.plot <- ggplot(et.raw.data, aes(x = AOI, y = Total_duration_of_Visit, fill = AOI)) +
+  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
+  scale_x_discrete(guide = guide_axis(angle = 70)) +
+  geom_boxplot()+
+  geom_jitter(color="black", size=0.4, alpha=0.5) +
+  facet_wrap(~ Group, nrow = 1)+
+  theme_light() +
+  theme(legend.position="none")+
+  labs(y = "Total Duration of Visits in AOIs", x = "AOI")
+
+total.visit.plot
+
+### Plot data PROPORTIONS VISITS
+prop.visit.plot <- ggplot(proportion.et.data, aes(x = AOI, y = proportion_visits, fill = AOI)) +
+  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))+
+  scale_x_discrete(guide = guide_axis(angle = 70)) +
+  geom_boxplot()+
+  facet_wrap(~ Group, nrow = 1)+
+  theme_light() +
+  theme(legend.position="none")+
+  labs(y = "Proportion of Visits in AOIs", x = "AOI")
+
+prop.visit.plot
 

### 2021-06-21 01_studies/02_2020_Aperol-pilot/questionnaire data/gregor beispiele/Symlit_RMTS_pilot1_report/Symlit_RMTS_pilot1_report.Rmd
SRI / Erhebungsprotokoll / Versuchsleitungsmanual

---
title: "Symlit RMTS Pilot1 Report"
author: "Gregor Kachel, Johanna Merker, Patrick Hawlitschek, Ivan Kroupin"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### HOW TO PREPARE DATA IN EXCEL ###
# use filter to select only lines with an ID in it 
# (i.e. exclude all empty lines or lines with na, ?, x, etc)
# select all columns except the columns for comments
# copy/paste into a new spreadsheet
# click "save as" and choose file type "tab-delimited-text"
####################################

# load tab delimited text file into R; 
# file should be in a subfolder named "data" for the script to select it
raw.data<-read.table("./data/SymLit_RMTS_subjectlist_251220.txt",sep="\t", header=T)

# loading packages
# if a package is not installed on the current machine, it will install it
if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

# # change data structure: everything is turned into factors except for 
# main.data <- raw.data %>%
#   filter(what == "data"& valid == 1)  %>%
#   mutate(across(!correct&!agem&!aged, as.factor),
#          correct = as.integer(correct))

```

# Short Summary
This report provides a summary of the first pilot ran for SymLit_RMTS. Our aim for Pilot1 was to evaluate whether the tasks we are planning to use for SymLit_RMTS are appropriate for three- and four-year-old children. In a between-subjects design, three- and four-year-old children saw either a communicative framing of the task or a non-communicative task (condition (comm; non-comm) x agegroup (3yo; 4yo). Children were tested via online video calls. Since we were primarily interested in whether children understand the overall presentation of the task, we used very simple stimulus pairings in which the cue was a representation of the target stimulus (i.e. target is a circle; distractor is a square; cue is a drawn circle).

### Demographics
For pilot 1, we aimed at testing for four children in each condition and age-group. The table shows the state of data collection as of `r Sys.Date()`.

```{r overview demographics data table, echo=FALSE}
raw.data %>% # select data
  filter(what == "head") %>% # select only lines with data and only valid trials
  group_by(age, condition) %>%
  summarise(N = n_distinct(id),
            male = sum(sex),
            "mean age" = round(mean(agem), 2),
            "min age" = min(agem),
            "max age" = max(agem),
            "sd age" = round(sd(agem), 2),
            ) %>% 
  knitr::kable(digits = 2)

# demographics.data<- raw.data %>% # select data
#   filter(what == "head") %>% # select only lines with data and only valid trials
#   group_by(age, condition) %>%
#   summarise(N = n_distinct(id),
#             male = sum(sex),
#             "mean age" = round(mean(agem), 2),
#             "min age" = min(agem),
#             "max age" = max(agem),
#             "sd age" = round(sd(agem), 2),
#             )

```

### Performance in Familiarization Trials
All test sessions commence with a set of four familiarisation trials in which children have to point out the location of an item that was hidden in plain sight. These trials familiarize children with the task and ensure that the experimenter can read their responses (pointing) via the video call. Children need to succeed in at least half of the familiarization trials in order to progress to the test trials. In case children cannot point out the correct side of the screen, experimenters continue with a mock participation and participants would not be dropped from the sample.

```{r overview familiarization data table, echo=FALSE}
raw.data %>%
  filter(what == "data" & valid == "1" & trialtype == "fam") %>% 
  mutate(correct = as.integer(correct),
         valid = as.integer(valid))%>% 
  group_by(age, condition) %>%
  summarise(N = n_distinct(id),
            "trials/N" = round(sum(valid)/n_distinct(id), 2),
            "% correct" = round(mean(correct)*100, 2),
              ) %>% 
  knitr::kable(digits = 2)

```

### Performance in Test Trials
During the main phase of the study, children are presented with 16 test trials. In order to be submitted to the analyses, participants need to complete at least 8 test trials. Reasons for excluding trials include fuzziness and lack of attention, experimenter error, technical issues, and parental interference. Hence, the number of trials by participants can vary across conditions (cf. trials/N). Trials are coded as valid (valid = 1; drop = 0) and correct (correct = 1; error = 0). The table provides the percentages of correct choices during the main phase of the experiment.

```{r overview test data table, echo=FALSE}
raw.data %>% 
  filter(what == "data" & valid == "1" & trialtype == "test") %>% 
  mutate(correct = as.integer(correct),
         valid = as.integer(valid))%>% 
  group_by(age, condition) %>%
  summarise(N = n_distinct(id),
            "trials/N" = round(sum(valid)/n_distinct(id), 2),
            "% correct" = round(mean(correct)*100, 2),
              )  %>% 
  knitr::kable(digits = 2)

# test.data<-raw.data %>% # select data
#   filter(what == "data" & valid == "1" & trialtype == "test") %>% # select only lines with data and only valid trials
#   mutate(correct = as.integer(correct),
#          valid = as.integer(valid))%>% 
#   group_by(age, condition) %>%
#   summarise(N = n_distinct(id),
#             "trials/N" = round(sum(valid)/n_distinct(id), 2),
#             "% correct" = round(mean(correct)*100, 2),
#               )

# test.data<-raw.data %>% # select data
#   filter(what == "data" & valid == "1" & trialtype == "test") %>% # select only lines with data and only valid trials
#   mutate(correct = as.integer(correct),
#          valid = as.integer(valid))%>% 
#   group_by(age, condition) %>%
#   summarise(N = n_distinct(id),
#             "mean age" = round(mean(agem), 2),
#             "min age" = min(agem),
#             "max age" = max(agem),
#             #"sd age" = round(sd(agem), 2),
#             "trials/N" = round(sum(valid)/n_distinct(id), 2),
#             "% correct" = round(mean(correct)*100, 2)
#               ) 
# test.data %>% relocate("mean age", "min age", "max age", .after = "age")

```

### Proportion of Correct Choices
Graph provides boxplots and individual data for all experimental groups. Contrary to our hypothesis, children in both age-groups perform better in the non-communicative condition. The main reason behind this could be that the presentation of the communicative task is not clear enough. Mainly, we failed to get across that the monkey is actually drawing something for the children to help them. In the next phase we should make this more explicit. In general it needs to be noted that the number of participants per experimental group is very low. Other than that, data generally indicate that in both conditions and age-groups, children succeed in the task. Hence, our task in general and the video procedure in particular are age-appropriate and can be used to investigate our main research question.

```{r plot boxplot by groups, echo = FALSE}

test.ind.data <- raw.data %>%
  filter(what == "data" & valid == "1" & trialtype == "test") %>%
  select(id, age, condition, correct)  %>%
  mutate(correct = as.integer(correct),
         age = as.factor(age),
         condition = as.factor(condition),
         groups = paste(age,"-",condition)) %>%
  group_by(groups, age, condition, id) %>%
  summarise(proportion.correct = round(mean(correct)*100, 2))

test.all.data <- raw.data %>%
  filter(what == "data" & valid == "1" & trialtype == "test") %>%
  select(id, age, condition, correct)  %>%
  mutate(correct = as.integer(correct),
         age = as.factor(age),
         condition = as.factor(condition),
         groups = paste(age,"-",condition)) %>%
  group_by(groups, age, condition) %>%
  summarise(proportion.correct = round(mean(correct)*100, 2),
            sd = round(sd(correct)*100,2))

test.raw.data <- raw.data %>%
  filter(what == "data" & valid == "1" & trialtype == "test") %>%
  select(id, age, condition, correct)  %>%
  mutate(correct = as.integer(correct),
         age = as.factor(age),
         condition = as.factor(condition),
         groups = paste(age,"-",condition))

test.boxplot <-ggplot() +
  geom_boxplot(data = test.ind.data, aes(x = groups, y = proportion.correct), )+ # when there is more data add "notch = TRUE" for conf intervalls
  geom_jitter(data = test.ind.data, aes(x = groups, y = proportion.correct, colour=condition), size = 2, width = 0.1) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,102))+
  labs(x="Groups", y="Proportion Correct")+ # for title add --> title="Proportion of Correct Choices", 
  theme_classic()
   # geom_violin(data = test.raw.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5), mapping = aes(x=groups, y = correct))
test.boxplot

```

### Performance across trials
Children are tested without feedback. The experimenter merely acknowledges the participant's choice by saying "thank you". The plot below presents the proportion of correct choices across all test trials for both age groups and conditions.

```{r plot linegraph performance across trials, echo=FALSE}

trial.data <- raw.data %>% 
  filter(what == "data" & valid == "1" & trialtype == "test") %>% 
  mutate(correct = as.integer(correct),
         valid = as.integer(valid),
         trial = as.integer(trial))%>% 
  select(age, condition, trial, correct) %>%
  group_by(age, condition, trial) %>%
    summarise(correct = round(mean(correct)*100, 2))

trial.plot <- ggplot(trial.data, aes(x = trial, y=correct, colour=condition, linetype=condition))+
  geom_line()+
  geom_point()+
  scale_x_continuous(breaks=trial.data$trial)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,100))+
  labs(x="Trials", y="Proportion Correct")+ # to add a title --> title="Performance across test trials", 
  theme_classic() +
  facet_grid(age ~ .)
trial.plot

```

### Performance by items
In each trial, children were presented with a target and distractor shape as well as a cue matching the target shape. The counterbalancing ensures that all shapes occur both as target and distractor. Presentation in trials is counterbalanced. The graph below shows children's individual performance aggregated for all target shapes. More incorrect choices for a specific target could indicate that a cue is ambiguous.

```{r plot performance across items, echo=FALSE, warning=FALSE}

target.ind.data <- raw.data %>%
  filter(what == "data" & valid == "1" & trialtype == "test") %>%
  select(id, age, condition, tar, correct)  %>%
  mutate(correct = as.integer(correct),
         age = as.factor(age),
         condition = as.factor(condition),
         target = as.factor(tar),
         groups = paste(age,"-",condition)) %>%
  group_by(target,age, id) %>%
  summarise(proportion.correct = round(mean(correct)*100, 2))

target.boxplot <-ggplot() +
  geom_boxplot(data = target.ind.data, aes(x = target, y = proportion.correct),outlier.shape = NA)+ # when there is more data add "notch = TRUE" for conf intervalls
  geom_jitter(data = target.ind.data, aes(x = target, y = proportion.correct, colour=target), size = 2, width = 0.3) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,110))+
  labs(x="Target Shapes", y="Proportion Correct")+ # for title add --> title="Proportion of Correct Choices", 
  theme_classic()+
  facet_grid(age ~ .)
   # geom_violin(data = test.raw.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5), mapping = aes(x=groups, y = correct))
target.boxplot

```

In addition, the plot below shows individual performance across all distractor shapes. More incorrect choices for a specific distractor might indicate that children prefer to select that distractor over any target.

```{r plot performance across distractor items, echo=FALSE, warning=FALSE}

distractor.ind.data <- raw.data %>%
  filter(what == "data" & valid == "1" & trialtype == "test") %>%
  select(id, age, condition, dis, correct)  %>%
  mutate(correct = as.integer(correct),
         age = as.factor(age),
         condition = as.factor(condition),
         distractor = as.factor(dis),
         groups = paste(age,"-",condition)) %>%
  group_by(distractor,age, id) %>%
  summarise(proportion.correct = round(mean(correct)*100, 2))

distractor.boxplot <-ggplot() +
  geom_boxplot(data = distractor.ind.data, aes(x = distractor, y = proportion.correct),outlier.shape = NA)+ # when there is more data add "notch = TRUE" for conf intervalls
  geom_jitter(data = distractor.ind.data, aes(x = distractor, y = proportion.correct, colour=distractor), size = 2, width = 0.3) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,110))+
  labs(x="Distractor Shapes", y="Proportion Correct")+ # for title add --> title="Proportion of Correct Choices", 
  theme_classic()+
  facet_grid(age ~ .)
   # geom_violin(data = test.raw.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5), mapping = aes(x=groups, y = correct))
distractor.boxplot

```

### Testing individual performance against chance
For each individual, we used a binomial test to investigate whether their performance was significantly above chance level (p < 0.05; 50%). The table provides the number and proportion of individuals performing above chance for age experimental group.

```{r table individual performance against chance, echo=FALSE}

ind.binom.data <- raw.data %>%
    filter(what == "data" & valid == "1" & trialtype == "test") %>% 
    select(condition, age, id, correct) %>% 
    mutate(correct = as.integer(correct))%>% 
    group_by(condition, age, id) %>%
    summarise("% correct" = round(mean(correct)*100, 2),
              "sum correct" = sum(correct),
              "sum trials" = length(correct),
              "p" = round(binom.test(sum(correct), length(correct), 
                               p = 0.5, alternative = "greater")$p.value, 3),
              "sig" = if_else(p < 0.05, 1, 0)
              )

sum.binom.data <- ind.binom.data %>%
    group_by(age, condition) %>%
    summarise(N = n_distinct(id),
            "succesfull"  = sum(sig))

sum.binom.data %>%
  mutate("% successful" = (succesfull/N)*100)%>% 
  knitr::kable(digits = 2)

```

### Testing group performance against chance
To test whether each children in both age-group and condition performed above chance on a group level, we used Wilcoxon / Mann-Whitney-U tests.

xxx To Do xxx

```{r plot performance against chance, echo=FALSE}

# Alternative using one-sample t-tests from emopoint
# this is not working yet as the participants in 4<o comm are all 100% correct
# raw.data %>%
#   filter(what == "data" & valid == "1" & trialtype == "test") %>% 
#   mutate(correct = as.integer(correct)) %>%
#   group_by(condition, age, id) %>%
#   arrange(condition, age) %>%
#   summarise(correct = mean(correct)) %>%
#   summarise(correct = list(correct)) %>%
#   group_by(condition, age) %>%
#   mutate(m = mean(unlist(correct)),
#          sd = sd(unlist(correct)),
#          df= t.test(unlist(correct), mu = 0.5)$parameter,
#          t_value = t.test(unlist(correct), mu = 0.5)$statistic,
#          p = t.test(unlist(correct), mu = 0.5)$p.value,
#          d = cohensD(unlist(correct), mu = 0.5))%>%
#   select(condition,age, m,sd,t_value,p,d) %>% #add df
#   knitr::kable(digits = 2)

```

### Comparing Performance across age-groups and conditions
We used Wilcoxon/Mann-Whitney-U-tests to test for significant differences in children's performance across age-groups and conditions respectively.

xxx To Do xxx

### Full Analysis (GLMM, ANOVA)
We are going to analyze our outcome (correct choice 0/1) in a 2x2 design (condition (comm, noncomm); age (3yo, 4yo) using either a GLMM or ANOVA depending on prior tests on data structure and model stability.

xxx To Do xxx

# References

R Core Team (2019). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.

Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686, https://doi.org/10.21105/joss.01686

### 2021-06-21 01_studies/02_2020_Aperol-pilot/questionnaire data/gregor beispiele/eval_wise1920/evaluation_final_WS1920.Rmd
SRI / Erhebungsprotokoll / Versuchsleitungsmanual

--- 2021-01-05 studies/2020_Aperol_Git/questionnaire data/gregor beispiele/eval_wise1920/evaluation_final_WS1920.Rmd
@@
                 aes(x=item, y = mean, ymin = mean-se, ymax = mean+se, colour = Teilnehmende))+
-  # we can't make the violin transparent, so we change the bakground to white
+  # we can't make the violin transparent, so we change the background to white
   theme_light() +

### 2021-06-21 02_paper/paper_1_supplement_coding_data.Rmd
SRI / Erhebungsprotokoll / Versuchsleitungsmanual

--- 2021-02-26 paper_1/paper_1_supplement_new_table.Rmd
@@
 
-### Questionnaire data
-
-After each mini-lesson, the students answered items on the teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and scales on the teacher's presence behavior (students n = 24).
-In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire after each mini-lesson (teachers n = 8).
-
 ### Behavioral data
@@
 
-### Eyetracking data
-
-A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants.
-The head unit is a measuring device with different sensitive sensors.
-A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
-Infrared light illuminators support the eye tracking sensors which record the eye orientation.
-The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
-The scene camera has a field of view of 90 deg.
-in 16:9 format (82 deg.
-horizontal and 52 deg.
-vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
-The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
-
 ## Coding/ Data preparation/ Reliability
-
-### Questionnaire Data
-
-The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes. 
-The scales on the quality of teaching are a validated questionnaire [@helmke2014unterrichtsdiagnostik].
-Whereas the scales on the teacher's presence behavior were derived from the research literature [@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen] and were used in the pilot for the first time.
-The questionnaire is 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
-Data was obtained from N = 32 subjects (students n = 24, teachers n = 8).
-
-The following scales were assessed:
-
-(1) Classroom management
-(2) Positive climate and motivation
-(3) Clarity and structuredness
-(4) Activation and support
-(5) Presence: posture/gaze
-(6) Presence: voice
-(7) Presence: verbal and non-verbal intervention
-(8) Natural behaviour
-
-Table \@ref(tab:table-all-scales-self-assessment) provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness & Kurtosis of all scales for the teachers' self-assessment.
-
-```{r table-all-scales-self-assessment, echo = FALSE}
-
-# prepare data (selected from questionnaire data) - only equal items and without observer
-quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)
-
-# knock out NAs and duration of speaking time
-quest.raw.data <- quest.raw.data  %>% filter(
-  personID != "NA",
-  itemID != "8",
-  perspective == "self-assessment")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
-
-##############################################
-
-# calculate Cronbach's Alpha for each scale
-# activation & support
-self.as.wide <- quest.raw.data %>%
-                          filter (scale == "Activation and support") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-self.alpha.as <- alpha(self.as.wide[,-1])
-
-#clarity & structuredness
-self.cs.wide <- quest.raw.data %>%
-                          filter (scale == "Clarity and structuredness") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.cs <- alpha(self.cs.wide[,-1])
-
-#classroom management
-self.cm.wide <- quest.raw.data %>%
-                          filter (scale == "Classroom management") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.cm <- alpha(self.cm.wide[,-1])
-
-#natural behaviour
-self.nb.wide <- quest.raw.data %>%
-                          filter (scale == "Natural behaviour") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.nb <- alpha(self.nb.wide[,-1])
-
-#positive climate and motivation
-self.pcm.wide <- quest.raw.data %>%
-                          filter (scale == "Positive climate and motivation") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pcm <- alpha(self.pcm.wide[,-1])
-
-#presence: posture & gaze
-self.ppg.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: posture/gaze") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.ppg <- alpha(self.ppg.wide[,-1])
-
-#presence: voice
-self.pv.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: voice") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pv <- alpha(self.pv.wide[,-1])
-
-#presence: verbal/non-verbal intervention
-self.pvni.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pvni <- alpha(self.pvni.wide[,-1])
-
-#Presence without subscales
-self.p.wide <- quest.raw.data %>%
-                          filter(str_detect(scale,
-                                        paste(c(
-                                        "Presence: voice", 
-                                        "Presence: verbal and non-verbal intervention", 
-                                        "Presence: posture/gaze"),
-                                         collapse = '|'))) %>% 
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.p <- alpha(self.p.wide[,-1])
-
-##############################################
-
-# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
-# 
-# # activation & support
-# tab_itemscale(self.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # classroom management
-# tab_itemscale(self.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # clarity & structuredness
-# tab_itemscale(self.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # natural behaviour
-# tab_itemscale(self.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # postive clima and motivation
-# tab_itemscale(self.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence without subscales
-# tab_itemscale(self.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence: posture & gaze
-# tab_itemscale(self.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: voice
-# tab_itemscale(self.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: verbal/non-verbal intervention
-# tab_itemscale(self.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-##############################################
-
-# add alphas to excel table 
-# read in new data 
-quest.raw.data.alpha <- read.table("./data/short_questionnaire_data_260221_alpha.txt", dec=",", sep="\t", header=T)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data.alpha <- quest.raw.data.alpha %>%  mutate(alpha = as.numeric(alpha))
-
-##############################################
-
-# #####correlation between all presences' items
-# SELF-ASSESSMENT
-# install.packages("Hmisc")
-# library("Hmisc")
-
-# function cr() to format the correlation matrix
-res1.self<-cor(self.p.wide[,-1])
-
-# Visualization correlation matrix
-# Use corrplot() function: Draw a correlogram
-
-# # install.packages("corrplot")
-# library("corrplot")
-# 
-# # Insignificant correlation are crossed
-# corrplot(res1.self$r, type="upper", order="hclust",
-#          p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
-# # Insignificant correlations are leaved blank
-# corrplot(res1.self$r, type="upper", order="hclust",
-#          p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
-
-###############################################
-
-# create a basic table (tibble) using tidyverse functions for teachers' self assessment 
-# Change Number of Digits in Global R Options to reduce the number of digits after the decimal point to two
-options(digits = 2)
-
-teacher.scale.quest.table <- quest.raw.data.alpha %>% # select data
-  filter(perspective == "self-assessment")%>%
-  group_by(scale) %>%
-  summarise("M" = round(mean(value), 2),
-            "SD" = round(sd(value), 2),
-            "Min" = min(value),
-            "Max" = max(value),
-            "Skewness" = skewness(value),
-            "Kurtosis" = kurtosis(value),
-            "Cronbach's α" = mean(alpha))
-
-# format and insert table in manuscript
-apa_table(
-  teacher.scale.quest.table,
-  caption = "Scale analysis for teachers' self-assessment",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-```
-
-Table \@ref(tab:table-all-scales-students) provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness & Kurtosis of all scales for the students' perception of the teacher's behaviour in class.
-
-```{r table-all-scales-students, echo = FALSE}
-
-# prepare data (selected from questionnaire data) - only equal items and without observer
-quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)
-
-# knock out NAs and duration of speaking time
-quest.raw.data <- quest.raw.data  %>% filter(
-  personID != "NA",
-  itemID != "8",
-  perspective == "student")
-view(quest.raw.data)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
-
-###############################################
-
-# calculate Cronbach's Alpha for each scale of students' peception
-
-# activation & support
-stud.as.wide <- quest.raw.data %>%
-                          filter (scale == "Activation and support") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-stud.alpha.as <- alpha(stud.as.wide[,-1])
-
-#clarity & structuredness
-stud.cs.wide <- quest.raw.data %>%
-                          filter (scale == "Clarity and structuredness") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.cs <- alpha(stud.cs.wide[,-1])
-
-#classroom management
-stud.cm.wide <- quest.raw.data %>%
-                          filter (scale == "Classroom management") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.cm <- alpha(stud.cm.wide[,-1])
-
-#natural behaviour
-stud.nb.wide <- quest.raw.data %>%
-                          filter (scale == "Natural behaviour") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.nb <- alpha(stud.nb.wide[,-1])
-
-#positive climate and motivation
-stud.pcm.wide <- quest.raw.data %>%
-                          filter (scale == "Positive climate and motivation") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.pcm <- alpha(stud.pcm.wide[,-1])
-
-#presence: posture & gaze
-stud.ppg.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: posture/gaze") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.ppg <- alpha(stud.ppg.wide[,-1])
-
-#presence: verbal and non-verbal intervention
-stud.pvni.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.pvni <- alpha(stud.pvni.wide[,-1])
-
-#presence: voice
-stud.pv.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: voice") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.pv <- alpha(stud.pv.wide[,-1])
-
-#Presence without subscales
-stud.p.wide <- quest.raw.data %>%
-                          filter(str_detect(scale,
-                                        paste(c(
-                                        "Presence: voice", 
-                                        "Presence: verbal and non-verbal intervention", 
-                                        "Presence: posture/gaze"),
-                                         collapse = '|'))) %>% 
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.p <- alpha(stud.p.wide[,-1])
-
-# ###############################################
-
-# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
-# 
-# # activation & support
-# tab_itemscale(stud.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # classroom management
-# tab_itemscale(stud.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # clarity & structuredness
-# tab_itemscale(stud.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # natural behaviour
-# tab_itemscale(stud.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # positive clima and motivation
-# tab_itemscale(stud.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence without subscales
-# tab_itemscale(stud.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence: posture & gaze
-# tab_itemscale(stud.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: voice
-# tab_itemscale(stud.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: verbal/non-verbal intervention
-# tab_itemscale(stud.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-##############################################
-# #####correlation between all presences' items
-# SELF-ASSESSMENT
-# install.packages("Hmisc")
-library("Hmisc")
-
-# # function to format the correlation matrix
-# flattenCorrMatrix <- function(cormat, pmat) {
-#   ut <- upper.tri(cormat)
-#   data.frame(
-#     row = rownames(cormat)[row(cormat)[ut]],
-#     column = rownames(cormat)[col(cormat)[ut]],
-#     cor  =(cormat)[ut],
-#     p = pmat[ut]
-#     )
-# }
-# 
-# res1.stud<-cor(stud.p.wide[,-1])
-
-# res1.stud<-rcorr(as.matrix(stud.p.wide[,-1]))
-# 
-# flattenCorrMatrix(res1.stud$r, res1.stud$P)
-# 
-# res2.stud<-flattenCorrMatrix(res1.stud$r, res1.stud$P)
-
-# Visualization correlation matrix
-# Use corrplot() function: Draw a correlogram
-
-# install.packages("corrplot")
-library("corrplot")
-
-# # Insignificant correlation are crossed
-# corrplot(res1.stud$r, type="upper", order="hclust",
-#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
-# # Insignificant correlations are leaved blank
-# corrplot(res1.stud$r, type="upper", order="hclust",
-#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
-
-##############################################
-
-# add alphas to excel table 
-# read in new data 
-quest.raw.data.alpha <- read.table("./data/short_questionnaire_data_260221_alpha.txt", dec=",", sep="\t", header=T)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data.alpha <- quest.raw.data.alpha %>%  mutate(alpha = as.numeric(alpha))
-
-##############################################
-
-# create a basic table (tibble) using tidyverse functions for teacher self assessment 
-student.scale.quest.table <- quest.raw.data.alpha %>% # select data
-  filter(perspective == "student")%>%
-  group_by(scale) %>%
-  summarise("M" = round(mean(value), 2),
-            "SD" = round(sd(value), 2),
-            "Min" = min(value),
-            "Max" = max(value),
-            "Skewness" = skewness(value),
-            "Kurtosis" = kurtosis(value),
-            "Cronbach's α" = mean(alpha))
-
-# format and insert table in manuscript
-apa_table(
-  student.scale.quest.table,
-  caption = "Scale analysis for students' perspective",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-```
-
-\newpage
-The individual items of a scale are further represented in graphs.
-
-(1) Classroom management
-```{r Line Plots Classroom Management, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, fig.cap="Items for Classroom Management"}
-
-### classroom management
-
-# filter by parameter variable, i.e. create a subset for classroom management without perspective "observer"
-cm.data <- quest.raw.data %>% filter(scale == "Classroom management")
-
-view(cm.data)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-cm.data <- cm.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-cm.plot.sd <- cm.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-cm.plot<-ggplot(data = cm.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = perspective, colour = perspective)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = cm.data, y = "value", x = NULL,
-       title="Classroom management" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-cm.plot
-
-```
-\newpage
-(2) Positive climate and motivation
-```{r Positive climate and motivation line plots,  fig.width=6, fig.height = 7, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Positive climate and motivation"}
-
-### Positive climate and motivation
-
-# filter by parameter variable, i.e. create a subset for Positive climate and motivation
-pcm.data <- quest.raw.data %>% filter(scale == "Positive climate and motivation")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-pcm.data <- pcm.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-pcm.plot.sd <- pcm.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-pcm.plot<-ggplot(data = pcm.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = pcm.data, y = "value", x = NULL,
-       title="Positive climate and motivation" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 5))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-pcm.plot
-
-```
-\newpage
-(3) Clarity and structuredness
-```{r Clarity and structuredness line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Clarity and structuredness"}
-
-### Clarity and structuredness
-
-# filter by parameter variable, i.e. create a subset for Clarity and structuredness
-cs.data <- quest.raw.data %>% filter(scale == "Clarity and structuredness")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-cs.data <- cs.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-cs.plot.sd <- cs.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-cs.plot<-ggplot(data = cs.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = cs.data, y = "value", x = NULL,
-       title="Clarity and structuredness" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-cs.plot
-
-```
-\newpage
-(4) Activation and support
-```{r Activation and support line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Activation and support"}
-
-### Activation and support
-
-# filter by parameter variable, i.e. create a subset for Activation and support
-as.data <- quest.raw.data %>% filter(scale == "Activation and support")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-as.data <- as.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-as.plot.sd <- as.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-as.plot<-ggplot(data = as.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = as.data, y = "value", x = NULL,
-       title="Activation and support" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-as.plot
-
-```
-\newpage
-
-(ref:presenceposturegaze-caption) (5) Presence: posture/gaze
-
-```{r presenceposturegaze, fig.cap = "(ref:presenceposturegaze-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presenceposturegaze.png", dpi = 108)
-
-# ```{r Presence: posture/gaze line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-
-# ### Presence: posture/gaze 
-# 
-# # filter by parameter variable, i.e. create a subset for Presence: posture/gaze
-# ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# ppg.plot.sd <- ppg.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# ppg.plot<-ggplot(data = ppg.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = ppg.data, y = "value", x = NULL,
-#        title="Presence: posture/gaze" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# ppg.plot
-
-```
-
-\newpage
-
-(ref:presencevoice-caption) (6) Presence: voice
-
-```{r presencevoice, fig.cap = "(ref:presencevoice-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presencevoice.png", dpi = 108)
-
-# ```{r Presence: voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-# 
-# ### Presence: voice 
-# # filter by parameter variable, i.e. create a subset for Presence: voice
-# pv.data <- quest.raw.data %>% filter(scale == "Presence: voice")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# pv.plot.sd <- pv.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# pv.plot<-ggplot(data = pv.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = pv.data, y = "value", x = NULL,
-#        title="Presence: voice" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# pv.plot
-
-```
-\newpage
-
-(ref:presenceverbalnonverbalintervention-caption) (7) Presence: verbal and non-verbal intervention
-
-```{r presenceverbalnonverbalintervention, fig.cap = "(ref:presenceverbalnonverbalintervention-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presenceverbalnonverbalintervention.png", dpi = 108)
-
-# ```{r Presence: verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-# 
-# ### Presence: verbal and non-verbal intervention 
-# # filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
-# pvni.data <- quest.raw.data %>% filter(scale == "Presence: verbal and non-verbal intervention")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# pvni.plot.sd <- pvni.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# pvni.plot<-ggplot(data = pvni.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = pvni.data, y = "value", x = NULL,
-#        title="Presence: verbal and non-verbal intervention" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# pvni.plot
-
-```
-\newpage
-(8) Natural behaviour
-```{r Natural behaviour line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Natural Behaviour"}
-
-### Natural behaviour 
-# filter by parameter variable, i.e. create a subset for Natural behaviour
-nb.data <- quest.raw.data %>% filter(scale == "Natural behaviour")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-nb.data <- nb.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-nb.plot.sd <- nb.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-nb.plot<-ggplot(data = nb.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = nb.data, y = "value", x = NULL,
-       title="Natural behaviour" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-nb.plot
-
-```
-\newpage
-In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
-
-```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE, fig.cap = "Boxplots and individual data for experts and novices"}
-
-quest.plot <- quest.raw.data %>%
-  ggplot(aes(x=scale, y=value, fill=scale)) +
-    geom_boxplot() +
-    scale_x_discrete(guide = guide_axis(angle = 70)) +
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    theme_light() +
-    theme(
-      legend.position="none",
-      plot.title = element_text(size=11)
-    ) +
-    facet_grid(~group)+
-    ggtitle("Boxplot with individual points for all scales") +
-    xlab("")
-quest.plot
-
-```
-
-\newpage
 
@@
 
-### Eyetracking Data
-
-The Tobii Pro Lab 2 software was used to analyze the teachers' visual attetion during each mini-lesson.
-The software allows for non-screen based recordings of a participants’ attention while moving in real-world settings.
-The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video.
-In order to map multiple recordings to AOIs, we first imported the eye-tracking recordings into the Tobii Pro Analyzer software.
-Second, we created dynamic Areas of Interest (AOI) manually to plot the gaze data.
-Once the AOIs are created, the gaze recordings of multiple recordings can be mapped and analyzed in aggregated form.
-Tobii Pro does not allow to do AOI based analyses within Pro Lab.
-So we exported a tsv.
-file to do further analyses in the software R.
-
-#### Gaze relational index (GRI)
-
-The GRI is a measure of visual expertise in information processing.
-This metric is calculated as the ratio of mean fixation duration to fixation count.
-The GRI is higher for novices than for experts.
-[@gegenfurtner2020gaze]
-
-```{r GRItable, echo = FALSE}
-
-# prepare data (selected from questionnaire data)
-et.raw.data<-read.table("./data/Aperol_pilot_glasses_raw_fixation_saccades_metrics.tsv", dec=",", sep="\t", header=T)
-
-# converting integer to numeric
-et.raw.data <- et.raw.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.raw.table <- et.raw.data %>%
-  group_by(Participant, Variable) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-
-# format and insert table in manuscript
-apa_table(
-  et.raw.table,
-  caption = "Number and Duration (in msec) of Fixations",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
-
-```{r calibration phase TOI, echo = FALSE}
-
-# prepare data (selected from questionnaire data)
-et.calib.data<-read.table("./data/Aperol_pilot_glasses_raw_ALL_metrics_calib_without_AOI_snapshot.tsv", dec=",", sep="\t", header=T)
-
-# converting integer to numeric
-et.calib.data <- et.calib.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-# select relevant rows 
-et.calib.data <- et.calib.data %>% filter(TOI == "Calibration phase")
-
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.calib.table <- et.calib.data %>%
-  group_by(Participant, Variable1) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-
-# format and insert table in manuscript
-apa_table(
-  et.calib.table,
-  caption = "Number and Duration (in msec) of Fixations during calibration",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
-
 #########################################
@@
 
-### Questionnaire Data
-
 ### Behavioral Data
-
-### Eyetracking Data
 

### 2021-06-21 02_paper/schrott/paper_1_supplement_new_table.Rmd
SRI / Erhebungsprotokoll / Versuchsleitungsmanual

--- 2021-03-03 paper_1/paper_1_supplement_new_table.Rmd
@@
     scale_x_discrete(guide = guide_axis(angle = 70)) +
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
+    geom_jitter(color="black", size=0.4, alpha=0.5) +
     theme_light() +
@@
       legend.position="none",
-      plot.title = element_text(size=11)
-    ) +
+      plot.title = element_text(size=11)) +
     facet_grid(~group)+
@@
 
-```{r GRItable, echo = FALSE}
+```{r GRItable1, echo = FALSE}
 
 # prepare data (selected from questionnaire data)
-et.raw.data<-read.table("./data/Aperol_pilot_glasses_raw_fixation_saccades_metrics.tsv", dec=",", sep="\t", header=T)
+et.toi.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_all_TOI.tsv", dec=",", sep="\t", header=T)
 
 # converting integer to numeric
-et.raw.data <- et.raw.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
+et.toi.data <- et.toi.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
                                        Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
                                        Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
+                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations))
 
@@
 # create a basic table (tibble) using tidyverse functions
-et.raw.table <- et.raw.data %>%
-  group_by(Participant, Variable) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
+et.toi.table1 <- et.toi.data %>%
+  group_by(TOI) %>%
+  summarise("ID" = Participant,
+            "Group" = Variable1,
+            "Duration TOI ms" = Duration_of_interval,
+            "M Duration Fixation" = mean(Total_duration_of_whole_fixations),
+            "Number Fixation" = Number_of_whole_fixations,
+            "Time TOI Duration" = Duration_of_interval/mean(Total_duration_of_whole_fixations),
+            "Old GRI" = mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations,
+            "New GRI" = (Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations)
 
@@
   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  )
+
+```
+
+```{r GRItable2, echo = FALSE}
+
+# prepare data (selected from questionnaire data)
+et.toi.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_all_TOI.tsv", dec=",", sep="\t", header=T)
+
+# converting integer to numeric
+et.toi.data <- et.toi.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
+                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
+                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
+                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations))
+
+# calculate the GRI 
+# create a basic table (tibble) using tidyverse functions
+et.toi.table2 <- et.toi.data %>%
+  group_by(Variable1, TOI) %>%
+  rename("Group" = Variable1) %>%
+  summarise("M Fixation Duration" = mean(Total_duration_of_whole_fixations),
+            "M Number Fixation" = mean(Number_of_whole_fixations),
+            "M TOI" = mean(Duration_of_interval),
+            "M Old GRI" = mean(mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations),
+            "SD Old GRI" = sd(mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations),
+            "M New GRI" = mean((Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations),
+            "SD New GRI" = sd((Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations))
+
+# format and insert table in manuscript
+apa_table(
+  et.toi.table2,
+  caption = "GRI",
+  # note = "Write Note here", 
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  )
+
+```
+
+```{r GRItable3, echo = FALSE}
+
+# prepare data (selected from questionnaire data)
+et.toi.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_all_TOI.tsv", dec=",", sep="\t", header=T)
+
+# converting integer to numeric
+et.toi.data <- et.toi.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
+                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
+                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
+                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations))
+
+# calculate the GRI 
+# create a basic table (tibble) using tidyverse functions
+et.toi.table3 <- et.toi.data %>%
+  group_by(Variable1) %>%
+  rename("Group" = Variable1) %>%
+  summarise("M Fixation Duration" = mean(Total_duration_of_whole_fixations),
+            "M Number Fixation" = mean(Number_of_whole_fixations),
+            "M TOI" = mean(Duration_of_interval),
+            "M Old GRI" = mean(mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations),
+            "SD Old GRI" = sd(mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations),
+            "M New GRI" = mean((Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations),
+            "SD New GRI" = sd((Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations))
+
+# format and insert table in manuscript
+apa_table(
+  et.toi.table3,
+  caption = "GRI",
+  # note = "Write Note here", 
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
   )

### 2021-06-21 02_paper/schrott/paper_1_supplement_with_presence.Rmd
SRI / Erhebungsprotokoll / Versuchsleitungsmanual

--- 2021-02-09 paper_1/paper_1_supplement.Rmd
@@
 classoption       : "man"
-output            : papaja::apa6_pdf #bookdown::word_document2
+output            : word_document #papaja::apa6_pdf
 ---
@@
 if (!require(papaja)) install.packages('papaja'); library(papaja)
-
-# suppress "summarize" info. 
-# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
-options(dplyr.summarise.inform = FALSE)
 
@@
 
-## Procedure/ Data collection
-
-### Set up
-
-For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig.
-The subjects were divided into groups of four, so the study was conducted on two different sessions.
-All participants were asked to hold a 10-minute lesson.
-The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering questionnaires.
-
-One person from the group of 4 acted as a teacher, the other three subjects acted as the class.
-The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disruptions in the classroom (e.g.
-putting their heads on the table, chatting, looking at their mobile phones, etc.).
-
-The lesson disruptions were displayed as instructions during the lesson for all "students" but not the teacher.
-In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase.
-In addition, the order of the data collection was taken into account in the analyses and variance caused by order was controlled.
+## Data collection
 
@@
 
-### Questionnaire data
+For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig.
+The subjects were divided into groups of four, so the study was conducted on two different sessions.
+All participants were asked to hold a 10-minute lesson.
+The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering the questionnaire.
 
-After each mini-lesson, the subjects answered items on the teaching quality using a validated questionnaire ((@helmke2014unterrichtsdiagnostik)) and scales on the teacher's presence behavior.
-An external observer also completed the questionnaire.
-In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire.
+One person from the group of 4 acted as a teacher, the other three subjects acted as the class.
+The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disruptions in the classroom (e.g.
+putting their heads on the table, chatting, looking at their mobile phones, etc.).
 
-### Behavioral data
+The lesson disruptions were displayed as instructions during the lesson for all "students" but not the teacher.
+In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase.
+In addition, the order of the data collection was taken into account in the analyses and variance caused by order was controlled.
 
-The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab.
+By using mobile eye-trackers, the gaze and behavior of the experts and novices was recorded during the lesson.
+In addition, the speech and sounds and voices were recorded with an audio recorder installed in the middle of the Lab.
 Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles.
@@
 
-### Eyetracking data
+The lessons recorded on video were coded in a post-hoc procedure with a coding software by previously trained raters.
+The statistical data have been analyzed by using the program RStudio [Link: https://rstudio.com/].
 
-A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants.
-The head unit is a measuring device with different sensitive sensors.
-A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
-Infrared light illuminators support the eye tracking sensors which record the eye orientation.
-The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
-The scene camera has a field of view of 90 deg.
-in 16:9 format (82 deg.
-horizontal and 52 deg.
-vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
-The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
-
-## Coding/ Data preparation/ Reliability
+## Measures
 
 ### Questionnaire Data
+*Describe how we collect questionnaire data (paper or online). Add some basic information about the structure of the questionnaire.*
 
@@
 The scales on the quality of teaching are a validated questionnaire (@helmke2014unterrichtsdiagnostik).
-Whereas the scales on the teacher's presence behavior were derived from the research literature (@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen) and were used in the pilot for the first time.
+Whereas the scales on the teacher's presence behaviour were derived from the research literature (@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen) and were used in the pilot for the first time.
 
@@
 
-The table at the end of the manuscript provides an overview over the mean, the range and standard deviation of all scales.
+The table below provides an overview over the mean, min, max and standard deviation of all scales.
 
@@
 \newpage
-The individual items of a scale are further represented in graphs.
+The individual items of a scale were further represented in graphs.
 
@@
 (ref:presenceverbalnonverbalintervention-caption) (7) Presence: verbal and non-verbal intervention
-
 ```{r presenceverbalnonverbalintervention, fig.cap = "(ref:presenceverbalnonverbalintervention-caption)", fig.align = "center", echo = FALSE}
@@
 In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
-
 ```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE}
@@
 ```
+\newpage
+Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment.
+The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.
 
-\newpage
+```{r Duration speaking time, fig.width=5, fig.height = 5, echo = FALSE}
+# prepare data (selected from questionnaire data)
+quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)
 
-### Behavioral Data
-
-The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (@kuckartz2019analyzing). The following coding scheme was developed:
-
-First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher.
-The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.
-
-``` {r coded speaking time, echo = FALSE}
-### read in data for 01_01_expert_D
-speaking.data.01.01 <- read.delim("./data/Aperol_pilot_01_01_expert_D_cam4_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.01 <- speaking.data.01.01  %>% select(
-  Dokumentgruppe,
-  Dokumentname,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-str(speaking.data.01.01)
-
-### checking for missing values
-is.na(speaking.data.01.01)
-which(is.na(speaking.data.01.01))
-
-### filter only speaking time of teacher and "kodiert von Anna" as row 
-speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
-                                           Dokumentgruppe == "kodiert von Anna")
-
-speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)
-
-# read in data for 01_02_expert_A
-speaking.data.01.02 <- read.delim("./data/Aperol_pilot_01_02_expert_A_cam1_AL.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.01.02)
-
-### select relevant columns
-speaking.data.01.02 <- speaking.data.01.02 %>% select(
-  Dokumentname,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### checking for missing values
-is.na(speaking.data.01.02)
-which(is.na(speaking.data.01.02))
-
-### filter only speaking time of teacher as row 
-speaking.data.01.02 <- speaking.data.01.02 %>% filter (Code == "speaking time\\teacher")
-
-view(speaking.data.01.02)
-
-speaking.data.01.02 <- sum(speaking.data.01.02$Abdeckungsgrad..)
-
-# read in data for 01_03_novice_B
-speaking.data.01.03 <- read.delim("./data/Aperol_pilot_01_03_novice_B_cam1.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.01.03)
-
-### select relevant columns
-speaking.data.01.03 <- speaking.data.01.03 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-str(speaking.data.01.03)
-
-### checking for missing values
-is.na(speaking.data.01.03)
-which(is.na(speaking.data.01.03))
-
-### filter only speaking time of teacher as row 
-speaking.data.01.03 <- speaking.data.01.03 %>% filter (Code == "speaking time\\teachter")
-
-speaking.data.01.03 <- sum(speaking.data.01.03$Abdeckungsgrad..)
-
-# read in data for 01_04_novice_C
-speaking.data.01.04 <- read.delim("./data/Aperol_pilot_01_04_novice_C_cam1.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.01.04)
-
-### select relevant columns
-speaking.data.01.04 <- speaking.data.01.04 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-str(speaking.data.01.04)
-
-### checking for missing values
-is.na(speaking.data.01.04)
-which(is.na(speaking.data.01.04))
-
-### filter only speaking time of teacher as row 
-speaking.data.01.04 <- speaking.data.01.04 %>% filter (Code == "speaking time\\teachter")
-
-speaking.data.01.04 <- sum(speaking.data.01.04$Abdeckungsgrad..)
-
-# read in data for 02_01_novice_A
-speaking.data.02.01 <- read.delim("./data/Aperol_pilot_02_01_novice_A_glasses.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.02.01)
-
-### select relevant columns
-speaking.data.02.01 <- speaking.data.02.01 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-str(speaking.data.02.01)
-
-### checking for missing values
-is.na(speaking.data.02.01)
-which(is.na(speaking.data.02.01))
-
-### filter only speaking time of teacher as row 
-speaking.data.02.01 <- speaking.data.02.01 %>% filter (Code == "speaking time\\teacher")
-
-speaking.data.02.01 <- sum(speaking.data.02.01$Abdeckungsgrad..)
-
-# read in data for 02_02_novice_B
-speaking.data.02.02 <- read.delim("./data/Aperol_pilot_02_02_novice_B_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.02.02)
-
-### select relevant columns
-speaking.data.02.02 <- speaking.data.02.02 %>% select(
-  Dokumentgruppe,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-str(speaking.data.02.02)
-
-### checking for missing values
-is.na(speaking.data.02.02)
-which(is.na(speaking.data.02.02))
-
-### filter only speaking time of teacher as row 
-speaking.data.02.02 <- speaking.data.02.02 %>% filter (Code == "speaking time\\teacher",
-                                                       Dokumentgruppe == "kodiert von Anna")
-
-speaking.data.02.02 <- sum(speaking.data.02.02$Abdeckungsgrad..)
-
-# read in data for 02_03_novice_C
-speaking.data.02.03 <- read.delim("./data/Aperol_pilot_02_03_novice_C_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.02.03)
-
-### select relevant columns
-speaking.data.02.03 <- speaking.data.02.03 %>% select(
-  Dokumentgruppe,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-str(speaking.data.02.03)
-
-### checking for missing values
-is.na(speaking.data.02.03)
-which(is.na(speaking.data.02.03))
-
-### filter only speaking time of teacher as row 
-speaking.data.02.03 <- speaking.data.02.03 %>% filter (Code == "speaking time\\teachter",
-                                                       Dokumentgruppe == "02_03_kodiert von Anna")
-
-speaking.data.02.03 <- sum(speaking.data.02.03$Abdeckungsgrad..)
-
-# read in data for 02_04_novice_D
-speaking.data.02.04 <- read.delim("./data/Aperol_pilot_02_04_novice_D_cam1.txt", dec=",", sep="\t", header=T)
-
-view(speaking.data.02.04)
-
-### select relevant columns
-speaking.data.02.04 <- speaking.data.02.04 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-str(speaking.data.02.04)
-
-### checking for missing values
-is.na(speaking.data.02.04)
-which(is.na(speaking.data.02.04))
-
-### filter only speaking time of teacher as row 
-speaking.data.02.04 <- speaking.data.02.04 %>% filter (Code == "speaking time\\teachter")
-
-speaking.data.02.04 <- sum(speaking.data.02.04$Abdeckungsgrad..)
-
-# read in table with coded speaking time included
-speaking.data <- read.delim("./data/plus_coded_speaking_time_questionnaire_data_0802.txt", dec=",", sep="\t", header=T)
+# knock out NAs
+quest.raw.data <- quest.raw.data  %>% filter(
+  personID != "NA")
 
 # to compare both sessions filter only Identical items
-speaking.data <- speaking.data  %>% filter(str_detect(scale, 
+quest.raw.data <- quest.raw.data  %>% filter(str_detect(scale, 
                                                  paste(c("Duration of speaking time"),
                                                     collapse = '|')))
-
-view(speaking.data)
+view(quest.raw.data)
 
 # value sometimes contained text before filtering, we have to convert the numbers to numeric
-speaking.data <- speaking.data %>%  mutate(value = as.numeric(value))
+quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
 
-speaking.plot <- speaking.data %>%
+speaking.plot <- quest.raw.data %>%
   ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
@@
 ```
+\newpage
 
-### Eyetracking Data
+### Eye-tracking equipment
 
-The Tobii Pro Lab 2 software was used to analyze the teachers' visual attetion during each mini-lesson.
-The software allows for non-screen based recordings of a participants’ attention while moving in real-world settings.
+A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements.
+The head unit is a measuring device with different sensitive sensors.
+A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
+Infrared light illuminators support the eye tracking sensors which record the eye orientation.
+The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
+The scene camera has a field of view of 90 deg.
+in 16:9 format (82 deg.
+horizontal and 52 deg.
+vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
+The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
+
+The Tobii Pro Glasses 2 software allows for non-screen based recordings of a participants’ attention while moving in real-world settings.
 The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video.
-In order to map multiple recordings to AOIs, we first imported the eye-tracking recordings into the Tobii Pro Analyzer software.
-Second, we created dynamic Areas of Interest (AOI) manually to plot the gaze data.
-Once the AOIs are created, the gaze recordings of multiple recordings can be mapped and analyzed in aggregated form.
+In order to map multiple recordings to AOIs, it is necessary to import the eye-tracking recordings into the Tobii Pro Analyzer software.
+Also, it is necessary to create a reference image of the scene in which one wishes to plot the gaze data (i.e.
+snapshot).
+Once the snapshot is imported, the gaze recordings of multiple recordings can be mapped to the reference image and analyzed in aggregated form.
 Tobii Pro does not allow to do AOI based analyses within Pro Lab.
-So we exported a tsv.
-file to do further analyses in the software R.
-
-#### Gaze relational index (GRI)
-
-The GRI is a measure of visual expertise in information processing.
-This metric is calculated as the ratio of mean fixation duration to fixation count.
-The GRI is higher for novices than for experts.
-(@gegenfurtner2020gaze)
-
-```{r GRItable, echo = FALSE}
-
-# prepare data (selected from questionnaire data)
-et.data<-read.table("./data/Aperol_pilot_glasses_AOI.txt", dec=",", sep="\t", header=T)
-
-view(et.data)
-str(et.data)
-
-# converting integer to numeric
-et.data <- et.data %>%  mutate(Number.of.fixations.in.AOI = as.numeric(Number.of.fixations.in.AOI))
-
-# calculate the GRI
-
-# create a basic table (tibble) using tidyverse functions
-et.table <- et.data %>%
-  group_by(PersonID, Group) %>%
-  summarise("Fixation Number" = Number.of.fixations.in.AOI,
-            "Fixation Duration" = Total.duration.of.fixation.in.AOI..msec.,
-            "Average Duration Fixation" = Average.duration.of.fixation.in.AOI..msec.,
-            "SE Duration Fixation" = se(Total.duration.of.fixation.in.AOI..msec.),
-            "TOI" = Total.Time.of.Interest.Duration..msec.,
-            "GRI" = Average.duration.of.fixation.in.AOI..msec. / Number.of.fixations.in.AOI)
-
-view(et.table)
-
-# format and insert table in manuscript
-apa_table(
-  et.table,
-  caption = "Number and Duration (in msec) of Fixations",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
-
-```{r boxplot GRI, fig.width=6, fig.height = 8, echo = FALSE}
-# 
-# et.plot <- et.raw.data %>%
-#   ggplot(aes(x=Number_of_whole_fixations, y=value, fill=scale)) +
-#     geom_boxplot() +
-#     scale_x_discrete(guide = guide_axis(angle = 70)) +
-#     geom_jitter(color="black", size=0.4, alpha=0.9) +
-#     theme_light() +
-#     theme(
-#       legend.position="none",
-#       plot.title = element_text(size=11)
-#     ) +
-#     facet_grid(~Variable)+
-#     ggtitle("Boxplot with individual points for Number of fixations") +
-#     xlab("")
-# et.plot
-
-```
+Also, the dependency on snapshot reference images makes this approach impractical when working in different settings, i.e.
+different classrooms with various participants.
+Finally, mapping gaze to people or any moving objects complicated the analyses further.
 
@@
 
+# Results
+
 ### Questionnaire Data
-
-### Behavioral Data
-
-### Eyetracking Data
-
-# Results
+*Start entering descriptives and plots here* Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
+Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
+At vero eos et accusam et justo duo dolores et ea rebum.
+Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 
@@
 Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-
-### Questionnaire Data
-
-### Behavioral Data
-
-### Eyetracking Data
 

### 2021-06-22 paper_1/plots_peer/GRI_Graphics_Notebook_Peer.Rmd
add GRI plots

---
title: "Graphics GRI"
output: html_notebook
---

Packages

```{r}
library(needs)
needs(tidyverse,
      gridExtra,
      viridis,
      ggthemes)
```

```{r}
# prepare data (selected from questionnaire data)
df_gri <- read_delim("data/Aperol_pilot_glasses_raw_metrics_all_TOI.tsv", 
                     delim = "\t", escape_double = FALSE, trim_ws = TRUE)

# converting integer to numeric
df_gri <- mutate(.data = df_gri,
                 Duration_of_interval = as.numeric(Duration_of_interval),
                 Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
                 Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
                 Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
                 )

# calculate the GRI 
# create a basic table (tibble) using tidyverse functions
df_gri <- df_gri %>%
  group_by(TOI) %>%
  summarise("ID" = Participant,
            "Group" = Variable1,
            "DurTOI" = Duration_of_interval,
            "M Dur Fix" = mean(Total_duration_of_whole_fixations),
            "Number Fix" = Number_of_whole_fixations,
            "TimeTOI Dur" = Duration_of_interval/mean(Total_duration_of_whole_fixations),
            "OldGRI" = mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations,
            "NewGRI" = (Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations,
            "NewGRI_scale" = scale((Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations))

df_gri$Group <- as_factor(df_gri$Group)

```

List of Variables:

- TOI: Time of Interest; Type of Event
- ID: ID of Person
- Group: Novice or Expert
- DurTOI: Frames of TOI
- M Dur Fix: Mean time of Fixations per Type of Event
- Number Fix: Number of Fixations during Event
- TimeTOI Dur:
- OldGRI
- NewGRI

# Compare all Variables

```{r}
df_gri_comp <- select(df_gri,
                      !ID)

df_gri_comp <- pivot_longer(data = df_gri,
                            c("DurTOI","M Dur Fix","Number Fix",
                              "TimeTOI Dur","OldGRI","NewGRI","NewGRI_scale"))

df_gri_comp$name <- factor(df_gri_comp$name,
                           levels = c("DurTOI","M Dur Fix","Number Fix",
                                      "TimeTOI Dur","OldGRI","NewGRI",
                                      "NewGRI_scale"),
                           labels = c("Duration TOI","Total dur. of whole fixations (mean)",
                                      "Number of whole fixations","TimeTOI Dur","GRI","Adjusted GRI","Adjusted GRI (scaled)")
                           )

ggplot(data = df_gri_comp,
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")
```

# Novice vs. Expert (GRI)
Erste Idee:

```{r}
ggplot(data = filter(df_gri_comp,
                     name == "Old GRI" |
                     name == "Adjusted GRI" |
                     name == "Adjusted GRI (scaled)"),
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name),
             scales = "free")
```

# Comparison GRI over TOIs

```{r}
ggplot(data = filter(df_gri_comp,
                     name == "Old GRI" |
                     name == "Adjusted GRI" |
                     name == "Adjusted GRI (scaled)"),
       mapping = aes(x = TOI,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name),
             scales = "free")
```

```{r}

for (i in unique(df_gri$TOI)) {

    assign(paste("plot_", i, sep = ""), 
           ggplot(data = filter(df_gri,
                                TOI == i
                                ),
                  mapping = aes(x = factor(0),
                                y = NewGRI
                                )
                  ) +
             geom_boxplot(mapping = aes(fill = Group)
                          ) +
             labs(x = "",
                  y = "Adjusted GRI",
                  title = i)
           )

  }

plot_asking <- `plot_Asking question`
plot_chatting <- `plot_Chatting with neighbour`
plot_clicking <- `plot_Clicking pen`
plot_drawing <- `plot_Drawing on paper`
plot_drumming <- `plot_Drumming hands`
plot_looking <- `plot_Looking at phone`
plot_head <- `plot_Putting head on table`
plot_yelling <- plot_Yelling

df_gri$NewGRI_scale <- scale(df_gri$NewGRI)

grid.arrange(plot_asking,
             plot_chatting,
             plot_clicking,
             plot_drawing,
             plot_drumming,
             plot_looking,
             plot_head,
             plot_yelling,
             heights = c(1,1),
             widths = c(1,1,1,1),
             layout_matrix = matrix(1:8,
                                    nrow = 2,
                                    ncol = 4,
                                    byrow = TRUE
                                    ),
             name = "Difference between Novice and Expert"
             )

```

```{r}
ggplot(data = df_gri,
       mapping = aes(x = factor(0),
                     y = NewGRI_scale
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)
               ) +
  labs(x = "",
       y = "Adjusted GRI (standardized)"
      ) + 
  facet_wrap(vars(factor(TOI))) +
  scale_fill_brewer(palette = "RdBu")

```

### 2021-06-22 paper_1/plots_peer/presentation_plots.Rmd
add GRI plots

---
title: "Plots"
author: 'Peer Schwertfeger'
date: |
  | peer.schwertfeger@uni-leipzig.de

  | 
  | \today
fontsize: 9 pt
output: 
  beamer_presentation:
    includes:
      in_header: preambel.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r include=FALSE,warning=FALSE,message=FALSE}
library(needs)
needs(tidyverse,
      gridExtra,
      viridis,
      ggthemes)

# prepare data (selected from questionnaire data)
df_gri <- read_delim("data/Aperol_pilot_glasses_raw_metrics_all_TOI.tsv", 
                     delim = "\t", escape_double = FALSE, trim_ws = TRUE)

# converting integer to numeric
df_gri <- mutate(.data = df_gri,
                 Duration_of_interval = as.numeric(Duration_of_interval),
                 Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
                 Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
                 Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
                 )

# calculate the GRI 
# create a basic table (tibble) using tidyverse functions
df_gri <- df_gri %>%
  group_by(TOI) %>%
  summarise("ID" = Participant,
            "Group" = Variable1,
            "DurTOI" = Duration_of_interval,
            "M Dur Fix" = mean(Total_duration_of_whole_fixations),
            "Number Fix" = Number_of_whole_fixations,
            "TimeTOI Dur" = Duration_of_interval/mean(Total_duration_of_whole_fixations),
            "OldGRI" = mean(Total_duration_of_whole_fixations)/Number_of_whole_fixations,
            "NewGRI" = (Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations,
            "NewGRI_scale" = scale((Duration_of_interval/mean(Total_duration_of_whole_fixations))/Number_of_whole_fixations))

df_gri$Group <- as_factor(df_gri$Group)

```

## Comparison of all variables

```{r}

df_gri_comp <- select(df_gri,
                      !ID)

df_gri_comp <- pivot_longer(data = df_gri,
                            c("DurTOI","M Dur Fix","Number Fix",
                              "TimeTOI Dur","OldGRI","NewGRI","NewGRI_scale"))

df_gri_comp$name <- factor(df_gri_comp$name,
                           levels = c("DurTOI","M Dur Fix","Number Fix",
                                      "TimeTOI Dur","OldGRI","NewGRI",
                                      "NewGRI_scale"),
                           labels = c("Duration TOI","Total dur. of whole fixations (mean)",
                                      "Number of whole fixations","TimeTOI Dur","Old GRI","Adjusted GRI","Adjusted GRI (scaled)")
                           )

ggplot(data = df_gri_comp,
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  labs(y = "",
       x = ""
       ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")

```

## Novice vs. Expert (Calibration)

```{r message=FALSE,warning=FALSE}
ggplot(data = filter(df_gri_comp,
                     TOI == "Calibration phase"),
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  labs(y = "",
       x = ""
       ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")
```
## Novice vs. Expert (Asking Question)

```{r message=FALSE,warning=FALSE}
ggplot(data = filter(df_gri_comp,
                     TOI == "Asking question"),
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  labs(y = "",
       x = ""
       ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")
```

## Novice vs. Expert (Chatting with neighbour)

```{r message=FALSE,warning=FALSE}
ggplot(data = filter(df_gri_comp,
                     TOI == "Chatting with neighbour"),
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  labs(y = "",
       x = ""
       ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")
```

## Novice vs. Expert (Clicking pen)

```{r message=FALSE,warning=FALSE}
ggplot(data = filter(df_gri_comp,
                     TOI == "Clicking pen"),
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  labs(y = "",
       x = ""
       ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")
```

## Novice vs. Expert (Drawing on paper)

```{r message=FALSE,warning=FALSE}
ggplot(data = filter(df_gri_comp,
                     TOI == "Drawing on paper"),
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  labs(y = "",
       x = ""
       ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")
```

## Novice vs. Expert (Drumming hands)

```{r message=FALSE,warning=FALSE}
ggplot(data = filter(df_gri_comp,
                     TOI == "Drumming hands"),
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  labs(y = "",
       x = ""
       ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")
```

## Novice vs. Expert (Looking at phone)

```{r message=FALSE,warning=FALSE}
ggplot(data = filter(df_gri_comp,
                     TOI == "Looking at phone"),
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  labs(y = "",
       x = ""
       ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")
```

## Novice vs. Expert (Putting head on table)

```{r message=FALSE,warning=FALSE}
ggplot(data = filter(df_gri_comp,
                     TOI == "Putting head on table"),
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  labs(y = "",
       x = ""
       ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")
```

## Novice vs. Expert (Yelling)

```{r message=FALSE,warning=FALSE}
ggplot(data = filter(df_gri_comp,
                     TOI == "Yelling"),
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  labs(y = "",
       x = ""
       ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")
```

## Novice vs. Expert (GRI)

```{r}
ggplot(data = filter(df_gri_comp,
                     name == "Old GRI" |
                     name == "Adjusted GRI" |
                     name == "Adjusted GRI (scaled)"),
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name),
             scales = "free")
```

## Novice vs. Expert over TOIs

```{r}
ggplot(data = filter(df_gri_comp,
                     name == "Old GRI" |
                     name == "Adjusted GRI" |
                     name == "Adjusted GRI (scaled)"),
       mapping = aes(x = TOI,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  labs(x = "",
       y = "") +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  theme(axis.text.x = element_text(angle = 45,
                                   hjust = 1
                                   )
        ) +
  facet_wrap(vars(name),
             scales = "free") 
```

## Descriptive Statistics

```{r message=FALSE,warning=FALSE,}

df_table <- tibble(Value = c("GRI","Adj. GRI","Adj. GRI (scale)"),
                   Mean = c(mean(df_gri$OldGRI),mean(df_gri$NewGRI),mean(df_gri$NewGRI_scale)),
                   SD = c(sd(df_gri$OldGRI),sd(df_gri$NewGRI),sd(df_gri$NewGRI_scale)),
                   Median = c(median(df_gri$OldGRI),median(df_gri$NewGRI),median(df_gri$NewGRI_scale))
                   )

test_data <- rnorm(n = length(df_gri$OldGRI),
                   mean = 0)

knitr::kable(df_table)

```

### 2021-07-21 02_paper/paper_1/plots_peer/preambel.tex
labellist

\usetheme[progressbar=frametitle,background=light,block=fill]{metropolis}
\usepackage{appendixnumberbeamer}

\setbeamertemplate{footline}
{
	\begin{beamercolorbox}[wd=0.5\textwidth,ht=3ex,dp=1.5ex,leftskip=.5em,rightskip=.5em]{author in head/foot}
		\usebeamerfont{author in head/foot}
		\hfill\insertshortauthor
	\end{beamercolorbox}
	\vspace*{-4.5ex}\hspace*{0.5\textwidth}
	\begin{beamercolorbox}[wd=0.5\textwidth,ht=3ex,dp=1.5ex,left,leftskip=.5em]{title in head/foot}
		\usebeamerfont{title in head/foot}
		\insertshorttitle
		\hfill \hfill \insertframenumber{} von \inserttotalframenumber
	\end{beamercolorbox}	
}

\setbeamertemplate{section in toc}[sections numbered]

### 2021-07-21 02_paper/paper_1/plots_peer/presentation_plots.Rmd
labellist

--- 2021-06-22 paper_1/plots_peer/presentation_plots.Rmd
@@
 df_gri_comp <- select(df_gri,
-                      !ID)
+                      !c(ID,`M Dur Fix`))
 
-df_gri_comp <- pivot_longer(data = df_gri,
-                            c("DurTOI","M Dur Fix","Number Fix",
+df_gri_comp <- pivot_longer(data = df_gri_comp,
+                            c("DurTOI","Number Fix",
                               "TimeTOI Dur","OldGRI","NewGRI","NewGRI_scale"))
@@
 df_gri_comp$name <- factor(df_gri_comp$name,
-                           levels = c("DurTOI","M Dur Fix","Number Fix",
+                           levels = c("DurTOI","Number Fix",
                                       "TimeTOI Dur","OldGRI","NewGRI",
                                       "NewGRI_scale"),
-                           labels = c("Duration TOI","Total dur. of whole fixations (mean)",
+                           labels = c("Duration TOI",
                                       "Number of whole fixations","TimeTOI Dur","Old GRI","Adjusted GRI","Adjusted GRI (scaled)")
@@
 
-ggplot(data = df_gri_comp,
+ggplot(data = filter(df_gri_comp,
+                     TOI != "Calibration phase"),
        mapping = aes(x = Group,
@@
 ```
+
 ## Novice vs. Expert (Asking Question)
@@
 
-df_table <- tibble(Value = c("GRI","Adj. GRI","Adj. GRI (scale)"),
-                   Mean = c(mean(df_gri$OldGRI),mean(df_gri$NewGRI),mean(df_gri$NewGRI_scale)),
-                   SD = c(sd(df_gri$OldGRI),sd(df_gri$NewGRI),sd(df_gri$NewGRI_scale)),
-                   Median = c(median(df_gri$OldGRI),median(df_gri$NewGRI),median(df_gri$NewGRI_scale))
+df_gri_n <- filter(df_gri,
+                   Group == "Novice",
+                   TOI != "Calibration phase")
+
+df_table_n <- tibble(Value = c("GRI","Adj. GRI","Adj. GRI (scale)"),
+                   Mean = c(mean(df_gri_n$OldGRI),mean(df_gri_n$NewGRI),mean(df_gri_n$NewGRI_scale)),
+                   SD = c(sd(df_gri_n$OldGRI),sd(df_gri_n$NewGRI),sd(df_gri_n$NewGRI_scale)),
+                   Median = c(median(df_gri_n$OldGRI),median(df_gri_n$NewGRI),median(df_gri_n$NewGRI_scale))
+                   )
+
+df_gri_e <- filter(df_gri,
+                   Group == "Expert",
+                   TOI != "Calibration phase")
+
+df_table_e <- tibble(Value = c("GRI","Adj. GRI","Adj. GRI (scale)"),
+                   Mean = c(mean(df_gri_e$OldGRI),mean(df_gri_e$NewGRI),mean(df_gri_e$NewGRI_scale)),
+                   SD = c(sd(df_gri_e$OldGRI),sd(df_gri_e$NewGRI),sd(df_gri_e$NewGRI_scale)),
+                   Median = c(median(df_gri_e$OldGRI),median(df_gri_e$NewGRI),median(df_gri_e$NewGRI_scale))
                    )
@@
 
-knitr::kable(df_table)
+knitr::kable(df_table_n,
+             caption = "Experts")
+
+knitr::kable(df_table_e,
+            caption = "Novice")
 

### 2021-07-26 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_ET_coding_data.Rmd
coding SRI + R script eye tracking data + subject list

--- 2021-03-03 paper_1/paper_1_supplement_new_table.Rmd
@@
 keywords          : "Professional Vision, Expert-Novice-Paradigm, Eye-Tracking"
-wordcount         : "1949"
+wordcount         : "XXX"
 
@@
 
-The aim of the pilot study was to investigate whether there are differences in how expert and novice teachers manage scripted classroom disruptions.
+The aim of the study was to investigate whether there are differences in how expert and novice teachers manage scripted classroom disruptions.
 The disruptions were experimentally varied using a previously written script.
@@
 
-For the sample recruitment of the subjects (N = 8, experts n = 2, novices n = 6), schools in the city of Leipzig in Saxony were contacted.
+For the sample recruitment of the subjects (N = 80, experts n = 40, novices n = 40), schools in the city of Leipzig in Saxony were contacted.
 The institutions as well as the subjects were informed in detail about the aim and intention of the study in advance.
@@
 The selection of the subjects was based on extreme groups, whereby professional experience is the crucial criterion for the selection of experts or novices.
-Novices were recruited as teachers who have been working in the teaching profession for no more than 3 years, whereas experts were considered to have professional experience of 10 years or more [@messner2000berufliche].
+Novices were recruited as student teachers, whereas experts were considered to have professional experience  [@messner2000berufliche].
 
@@
 
-For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig.
-The subjects were divided into groups of four, so the study was conducted on two different sessions.
-All participants were asked to hold a 10-minute lesson.
-The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering questionnaires.
+The implementation of the study was composed of two parts, which took about 2 hours.
 
-One person from the group of 4 acted as a teacher, the other three subjects acted as the class.
-The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disruptions in the classroom (e.g.
-putting their heads on the table, chatting, looking at their mobile phones, etc.).
+In the first part, the subject teached a ten-minute lesson that has been prepared by him-/herself beforehand.
+During the lesson, three actors represented the class and simulated typical classroom events.
 
-The lesson disruptions were displayed as instructions during the lesson for all "students" but not the teacher.
-In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase.
-In addition, the order of the data collection was taken into account in the analyses and variance caused by order was controlled.
+In order to obtain data, four cameras (GoPro Hero 7) were set up in the room to film the events from different perspectives.
+The teacher wore mobile eye-tracking glasses to capture the gaze behavior (Tobii Glasses 2).
+Other classroom sounds and voices were recorded with an audio recorder (Zoom H3-VR Audio-Recorder).
+After the lesson, all participants received a short questionnaire about the teacher's classroom management.
+
+In a second part of the study, the teacher watched the recorded eye-tracking video with .
+The speech was recorded by the audio recorder.
+Finally, the subject answered a questionnaire in which he/she had to evaluate various teaching scenarios.
 
@@
 
-### Questionnaire data
+### Eye tracking data
 
-After each mini-lesson, the students answered items on the teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and scales on the teacher's presence behavior (students n = 24).
-In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire after each mini-lesson (teachers n = 8).
-
-### Behavioral data
-
-The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab.
-Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles.
-One camera was installed to film the class from the side.
-Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back.
-Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.
-
-### Eyetracking data
-
-A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants.
-The head unit is a measuring device with different sensitive sensors.
-A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
-Infrared light illuminators support the eye tracking sensors which record the eye orientation.
-The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
-The scene camera has a field of view of 90 deg.
-in 16:9 format (82 deg.
-horizontal and 52 deg.
-vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
-The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
+Eye tracking data was obtained ...
 
@@
 
-### Questionnaire Data
+The recorded lessons were coded in a post-hoc procedure with the eye tracking analyzer software Tobii Pro Lab by previously trained raters [@kuckartz2019analyzing].
+The coding manual of the ProVisioNET study was used to manually code the eye movement and behavior patterns of the subjects.
+The scripted events, the teacher's first visible reaction to scripted events, and the teacher's gaze points in Areas of Interests (AOIs) were coded.
 
-The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes. 
-The scales on the quality of teaching are a validated questionnaire [@helmke2014unterrichtsdiagnostik].
-Whereas the scales on the teacher's presence behavior were derived from the research literature [@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen] and were used in the pilot for the first time.
-The questionnaire is 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
-Data was obtained from N = 32 subjects (students n = 24, teachers n = 8).
+The scripted events are coded as event sampling.
+In the Tobii Pro Lab analyzer software, these events are marked as Time of Interests (TOI) with an end and start time.
+At the beginning of the coding, the TOIs have to be created in the software for all codes.
+For the creation of TOIs using events, see Supplement 1.1 Notes on working with Tobii Pro Lab for the creation of TOIs.
+The entire coding scheme is presented in the appendix.
 
-The following scales were assessed:
+The coding of the teacher's responses to scripted events is also done as event sampling in Tobii Pro Lab, but only the onset of a reaction due to difficulties to set the offset of a reaction.
 
-(1) Classroom management
-(2) Positive climate and motivation
-(3) Clarity and structuredness
-(4) Activation and support
-(5) Presence: posture/gaze
-(6) Presence: voice
-(7) Presence: verbal and non-verbal intervention
-(8) Natural behaviour
-
-Table \@ref(tab:table-all-scales-self-assessment) provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness & Kurtosis of all scales for the teachers' self-assessment.
-
-```{r table-all-scales-self-assessment, echo=FALSE, message=FALSE, warning=FALSE}
-
-# prepare data (selected from questionnaire data) - only equal items and without observer
-quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)
-
-# knock out NAs and duration of speaking time
-quest.raw.data <- quest.raw.data  %>% filter(
-  personID != "NA",
-  itemID != "8",
-  perspective == "self-assessment")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
-
-##############################################
-
-# calculate Cronbach's Alpha for each scale
-# activation & support
-self.as.wide <- quest.raw.data %>%
-                          filter (scale == "Activation and support") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-self.alpha.as <- alpha(self.as.wide[,-1])
-
-#clarity & structuredness
-self.cs.wide <- quest.raw.data %>%
-                          filter (scale == "Clarity and structuredness") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.cs <- alpha(self.cs.wide[,-1])
-
-#classroom management
-self.cm.wide <- quest.raw.data %>%
-                          filter (scale == "Classroom management") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.cm <- alpha(self.cm.wide[,-1])
-
-#natural behaviour
-self.nb.wide <- quest.raw.data %>%
-                          filter (scale == "Natural behaviour") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.nb <- alpha(self.nb.wide[,-1])
-
-#positive climate and motivation
-self.pcm.wide <- quest.raw.data %>%
-                          filter (scale == "Positive climate and motivation") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pcm <- alpha(self.pcm.wide[,-1])
-
-#presence: posture & gaze
-self.ppg.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: posture/gaze") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.ppg <- alpha(self.ppg.wide[,-1])
-
-#presence: voice
-self.pv.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: voice") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pv <- alpha(self.pv.wide[,-1])
-
-#presence: verbal/non-verbal intervention
-self.pvni.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pvni <- alpha(self.pvni.wide[,-1])
-
-#Presence without subscales
-self.p.wide <- quest.raw.data %>%
-                          filter(str_detect(scale,
-                                        paste(c(
-                                        "Presence: voice", 
-                                        "Presence: verbal and non-verbal intervention", 
-                                        "Presence: posture/gaze"),
-                                         collapse = '|'))) %>% 
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.p <- alpha(self.p.wide[,-1])
-
-##############################################
-
-# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
-# 
-# # activation & support
-# tab_itemscale(self.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # classroom management
-# tab_itemscale(self.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # clarity & structuredness
-# tab_itemscale(self.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # natural behaviour
-# tab_itemscale(self.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # postive clima and motivation
-# tab_itemscale(self.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence without subscales
-# tab_itemscale(self.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence: posture & gaze
-# tab_itemscale(self.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: voice
-# tab_itemscale(self.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: verbal/non-verbal intervention
-# tab_itemscale(self.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-##############################################
-
-# add alphas to excel table 
-# read in new data 
-quest.raw.data.alpha <- read.table("./data/short_questionnaire_data_260221_alpha.txt", dec=",", sep="\t", header=T)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data.alpha <- quest.raw.data.alpha %>%  mutate(alpha = as.numeric(alpha))
-
-##############################################
-
-# #####correlation between all presences' items
-# SELF-ASSESSMENT
-# install.packages("Hmisc")
-# library("Hmisc")
-
-# function cr() to format the correlation matrix
-res1.self<-cor(self.p.wide[,-1])
-
-# Visualization correlation matrix
-# Use corrplot() function: Draw a correlogram
-
-# # install.packages("corrplot")
-# library("corrplot")
-# 
-# # Insignificant correlation are crossed
-# corrplot(res1.self$r, type="upper", order="hclust",
-#          p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
-# # Insignificant correlations are leaved blank
-# corrplot(res1.self$r, type="upper", order="hclust",
-#          p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
-
-###############################################
-
-# create a basic table (tibble) using tidyverse functions for teachers' self assessment 
-# Change Number of Digits in Global R Options to reduce the number of digits after the decimal point to two
-options(digits = 2)
-
-teacher.scale.quest.table <- quest.raw.data.alpha %>% # select data
-  filter(perspective == "self-assessment")%>%
-  group_by(scale) %>%
-  summarise("N items" = n_distinct(shortID),
-            "M" = round(mean(value), 2),
-            "SD" = round(sd(value), 2),
-            "Min" = min(value),
-            "Max" = max(value),
-            "Skewness" = skewness(value),
-            "Kurtosis" = kurtosis(value),
-            "Cronbach's α" = mean(alpha))
-
-# format and insert table in manuscript
-apa_table(
-  teacher.scale.quest.table,
-  caption = "Scale analysis for teachers' self-assessment",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-```
-
-Table \@ref(tab:table-all-scales-students) provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness & Kurtosis of all scales for the students' perception of the teacher's behaviour in class.
-
-```{r table-all-scales-students, echo=FALSE, message=FALSE, warning=FALSE}
-
-# prepare data (selected from questionnaire data) - only equal items and without observer
-quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)
-
-# knock out NAs and duration of speaking time
-quest.raw.data <- quest.raw.data  %>% filter(
-  personID != "NA",
-  itemID != "8",
-  perspective == "student")
-view(quest.raw.data)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
-
-###############################################
-
-# calculate Cronbach's Alpha for each scale of students' peception
-
-# activation & support
-stud.as.wide <- quest.raw.data %>%
-                          filter (scale == "Activation and support") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-stud.alpha.as <- alpha(stud.as.wide[,-1])
-
-#clarity & structuredness
-stud.cs.wide <- quest.raw.data %>%
-                          filter (scale == "Clarity and structuredness") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.cs <- alpha(stud.cs.wide[,-1])
-
-#classroom management
-stud.cm.wide <- quest.raw.data %>%
-                          filter (scale == "Classroom management") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.cm <- alpha(stud.cm.wide[,-1])
-
-#natural behaviour
-stud.nb.wide <- quest.raw.data %>%
-                          filter (scale == "Natural behaviour") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.nb <- alpha(stud.nb.wide[,-1])
-
-#positive climate and motivation
-stud.pcm.wide <- quest.raw.data %>%
-                          filter (scale == "Positive climate and motivation") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.pcm <- alpha(stud.pcm.wide[,-1])
-
-#presence: posture & gaze
-stud.ppg.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: posture/gaze") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.ppg <- alpha(stud.ppg.wide[,-1])
-
-#presence: verbal and non-verbal intervention
-stud.pvni.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.pvni <- alpha(stud.pvni.wide[,-1])
-
-#presence: voice
-stud.pv.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: voice") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.pv <- alpha(stud.pv.wide[,-1])
-
-#Presence without subscales
-stud.p.wide <- quest.raw.data %>%
-                          filter(str_detect(scale,
-                                        paste(c(
-                                        "Presence: voice", 
-                                        "Presence: verbal and non-verbal intervention", 
-                                        "Presence: posture/gaze"),
-                                         collapse = '|'))) %>% 
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.p <- alpha(stud.p.wide[,-1])
-
-# ###############################################
-
-# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
-# 
-# # activation & support
-# tab_itemscale(stud.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # classroom management
-# tab_itemscale(stud.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # clarity & structuredness
-# tab_itemscale(stud.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # natural behaviour
-# tab_itemscale(stud.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # positive clima and motivation
-# tab_itemscale(stud.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence without subscales
-# tab_itemscale(stud.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence: posture & gaze
-# tab_itemscale(stud.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: voice
-# tab_itemscale(stud.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: verbal/non-verbal intervention
-# tab_itemscale(stud.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-##############################################
-# #####correlation between all presences' items
-# SELF-ASSESSMENT
-# install.packages("Hmisc")
-library("Hmisc")
-
-# # function to format the correlation matrix
-# flattenCorrMatrix <- function(cormat, pmat) {
-#   ut <- upper.tri(cormat)
-#   data.frame(
-#     row = rownames(cormat)[row(cormat)[ut]],
-#     column = rownames(cormat)[col(cormat)[ut]],
-#     cor  =(cormat)[ut],
-#     p = pmat[ut]
-#     )
-# }
-# 
-# res1.stud<-cor(stud.p.wide[,-1])
-
-# res1.stud<-rcorr(as.matrix(stud.p.wide[,-1]))
-# 
-# flattenCorrMatrix(res1.stud$r, res1.stud$P)
-# 
-# res2.stud<-flattenCorrMatrix(res1.stud$r, res1.stud$P)
-
-# Visualization correlation matrix
-# Use corrplot() function: Draw a correlogram
-
-# install.packages("corrplot")
-library("corrplot")
-
-# # Insignificant correlation are crossed
-# corrplot(res1.stud$r, type="upper", order="hclust",
-#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
-# # Insignificant correlations are leaved blank
-# corrplot(res1.stud$r, type="upper", order="hclust",
-#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
-
-##############################################
-
-# add alphas to excel table 
-# read in new data 
-quest.raw.data.alpha <- read.table("./data/short_questionnaire_data_260221_alpha.txt", dec=",", sep="\t", header=T)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data.alpha <- quest.raw.data.alpha %>%  mutate(alpha = as.numeric(alpha))
-
-##############################################
-
-# create a basic table (tibble) using tidyverse functions for teacher self assessment 
-student.scale.quest.table <- quest.raw.data.alpha %>% # select data
-  filter(perspective == "student")%>%
-  group_by(scale) %>%
-  summarise("N items" = n_distinct(shortID),
-            "M" = round(mean(value), 2),
-            "SD" = round(sd(value), 2),
-            "Min" = min(value),
-            "Max" = max(value),
-            "Skewness" = skewness(value),
-            "Kurtosis" = kurtosis(value),
-            "Cronbach's α" = mean(alpha))
-
-# format and insert table in manuscript
-apa_table(
-  student.scale.quest.table,
-  caption = "Scale analysis for students' perspective",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-```
-
-\newpage
-The individual items of a scale are further represented in graphs.
-
-(1) Classroom management
-```{r Line Plots Classroom Management, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, fig.cap="Items for Classroom Management"}
-
-### classroom management
-
-# filter by parameter variable, i.e. create a subset for classroom management without perspective "observer"
-cm.data <- quest.raw.data %>% filter(scale == "Classroom management")
-
-view(cm.data)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-cm.data <- cm.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-cm.plot.sd <- cm.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-cm.plot<-ggplot(data = cm.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = perspective, colour = perspective)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = cm.data, y = "value", x = NULL,
-       title="Classroom management" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-cm.plot
-
-```
-\newpage
-(2) Positive climate and motivation
-```{r Positive climate and motivation line plots,  fig.width=6, fig.height = 7, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Positive climate and motivation"}
-
-### Positive climate and motivation
-
-# filter by parameter variable, i.e. create a subset for Positive climate and motivation
-pcm.data <- quest.raw.data %>% filter(scale == "Positive climate and motivation")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-pcm.data <- pcm.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-pcm.plot.sd <- pcm.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-pcm.plot<-ggplot(data = pcm.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = pcm.data, y = "value", x = NULL,
-       title="Positive climate and motivation" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 5))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-pcm.plot
-
-```
-\newpage
-(3) Clarity and structuredness
-```{r Clarity and structuredness line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Clarity and structuredness"}
-
-### Clarity and structuredness
-
-# filter by parameter variable, i.e. create a subset for Clarity and structuredness
-cs.data <- quest.raw.data %>% filter(scale == "Clarity and structuredness")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-cs.data <- cs.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-cs.plot.sd <- cs.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-cs.plot<-ggplot(data = cs.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = cs.data, y = "value", x = NULL,
-       title="Clarity and structuredness" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-cs.plot
-
-```
-\newpage
-(4) Activation and support
-```{r Activation and support line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Activation and support"}
-
-### Activation and support
-
-# filter by parameter variable, i.e. create a subset for Activation and support
-as.data <- quest.raw.data %>% filter(scale == "Activation and support")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-as.data <- as.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-as.plot.sd <- as.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-as.plot<-ggplot(data = as.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = as.data, y = "value", x = NULL,
-       title="Activation and support" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-as.plot
-
-```
-\newpage
-
-(ref:presenceposturegaze-caption) (5) Presence: posture/gaze
-
-```{r presenceposturegaze, fig.cap = "(ref:presenceposturegaze-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presenceposturegaze.png", dpi = 108)
-
-# ```{r Presence: posture/gaze line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-
-# ### Presence: posture/gaze 
-# 
-# # filter by parameter variable, i.e. create a subset for Presence: posture/gaze
-# ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# ppg.plot.sd <- ppg.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# ppg.plot<-ggplot(data = ppg.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = ppg.data, y = "value", x = NULL,
-#        title="Presence: posture/gaze" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# ppg.plot
-
-```
-
-\newpage
-
-(ref:presencevoice-caption) (6) Presence: voice
-
-```{r presencevoice, fig.cap = "(ref:presencevoice-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presencevoice.png", dpi = 108)
-
-# ```{r Presence: voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-# 
-# ### Presence: voice 
-# # filter by parameter variable, i.e. create a subset for Presence: voice
-# pv.data <- quest.raw.data %>% filter(scale == "Presence: voice")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# pv.plot.sd <- pv.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# pv.plot<-ggplot(data = pv.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = pv.data, y = "value", x = NULL,
-#        title="Presence: voice" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# pv.plot
-
-```
-\newpage
-
-(ref:presenceverbalnonverbalintervention-caption) (7) Presence: verbal and non-verbal intervention
-
-```{r presenceverbalnonverbalintervention, fig.cap = "(ref:presenceverbalnonverbalintervention-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presenceverbalnonverbalintervention.png", dpi = 108)
-
-# ```{r Presence: verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-# 
-# ### Presence: verbal and non-verbal intervention 
-# # filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
-# pvni.data <- quest.raw.data %>% filter(scale == "Presence: verbal and non-verbal intervention")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# pvni.plot.sd <- pvni.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# pvni.plot<-ggplot(data = pvni.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = pvni.data, y = "value", x = NULL,
-#        title="Presence: verbal and non-verbal intervention" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# pvni.plot
-
-```
-\newpage
-(8) Natural behaviour
-```{r Natural behaviour line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Natural Behaviour"}
-
-### Natural behaviour 
-# filter by parameter variable, i.e. create a subset for Natural behaviour
-nb.data <- quest.raw.data %>% filter(scale == "Natural behaviour")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-nb.data <- nb.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-nb.plot.sd <- nb.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-nb.plot<-ggplot(data = nb.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = nb.data, y = "value", x = NULL,
-       title="Natural behaviour" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-nb.plot
-
-```
-\newpage
-In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
-
-```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE, fig.cap = "Boxplots and individual data for experts and novices"}
-
-quest.plot <- quest.raw.data %>%
-  ggplot(aes(x=scale, y=value, fill=scale)) +
-    geom_boxplot() +
-    scale_x_discrete(guide = guide_axis(angle = 70)) +
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    theme_light() +
-    theme(
-      legend.position="none",
-      plot.title = element_text(size=11)
-    ) +
-    facet_grid(~group)+
-    ggtitle("Boxplot with individual points for all scales") +
-    xlab("")
-quest.plot
-
-```
-
-\newpage
-
-### Behavioral Data
-
-The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters [@kuckartz2019analyzing]. The following coding scheme was developed:
-
-- phase - lesson begin, state event: teacher starts the lesson with a noise, talk, taking a position in class
-- phase - lesson end,	state event: teacher finishes the lesson with a noise, talk, taking a position in class
-- phase - organization/transition points, state event: any situation that does not imply effective learning time (fetching chalk, working        material, organizing desks, opening windows, printing work results etc.)
-- phase - single,	state event: any individual student activity on a given task (reading, writing, drawing etc.)
-- phase - group, state event: any student activity on a given task together in a group of at least 3 students (reading, writing, drawing etc.)
-- phase - class discussion, state event: discussion in class, teacher talks to class/individual/group
-- phase - pair: state event: any student activity on a given task together in a team of 2 students (reading, writing, drawing etc.)
-- phase - teachers lecture, state event: any teacher's presentation on a certain topic which maybe supported by a PPP, PREZI, notes on board,    OHP etc.
-- phase - other, state event: not categorizable
-- phase - break, state event: e.g. drinking, relaxation exercises
-- phase - external interruption, state event: external interruptions (e.g. fire alarm, technical problems, other teachers coming into the room)
-
-- speaking time - teacher, state event
-- speaking time - students, state event
-
-- disruption - chatting with neighbor, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - asking a question, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - yelling, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - looking at phone, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - staring out of window, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - drawing, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - head on table, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - clicking pen, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - drumming hands, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - walking around, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-
-First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher.
-The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.
-
-```{r coded speaking time, echo = FALSE }
-### read in data for 01_01_expert_D
-speaking.data.01.01 <- read.delim("./data/Aperol_pilot_01_01_expert_D_cam4_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.01 <- speaking.data.01.01  %>% select(
-  Dokumentgruppe,
-  Dokumentname,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher and "kodiert von Anna" as row 
-speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
-                                           Dokumentgruppe == "kodiert von Anna")
-speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)
-
-# read in data for 01_02_expert_A
-speaking.data.01.02 <- read.delim("./data/Aperol_pilot_01_02_expert_A_cam1_AL.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.02 <- speaking.data.01.02 %>% select(
-  Dokumentname,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.01.02 <- speaking.data.01.02 %>% filter (Code == "speaking time\\teacher")
-speaking.data.01.02 <- sum(speaking.data.01.02$Abdeckungsgrad..)
-
-# read in data for 01_03_novice_B
-speaking.data.01.03 <- read.delim("./data/Aperol_pilot_01_03_novice_B_cam1.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.03 <- speaking.data.01.03 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.01.03 <- speaking.data.01.03 %>% filter (Code == "speaking time\\teachter")
-speaking.data.01.03 <- sum(speaking.data.01.03$Abdeckungsgrad..)
-
-# read in data for 01_04_novice_C
-speaking.data.01.04 <- read.delim("./data/Aperol_pilot_01_04_novice_C_cam1.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.04 <- speaking.data.01.04 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.01.04 <- speaking.data.01.04 %>% filter (Code == "speaking time\\teachter")
-
-speaking.data.01.04 <- sum(speaking.data.01.04$Abdeckungsgrad..)
-
-# read in data for 02_01_novice_A
-speaking.data.02.01 <- read.delim("./data/Aperol_pilot_02_01_novice_A_glasses.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.01 <- speaking.data.02.01 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.01 <- speaking.data.02.01 %>% filter (Code == "speaking time\\teacher")
-speaking.data.02.01 <- sum(speaking.data.02.01$Abdeckungsgrad..)
-
-# read in data for 02_02_novice_B
-speaking.data.02.02 <- read.delim("./data/Aperol_pilot_02_02_novice_B_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.02 <- speaking.data.02.02 %>% select(
-  Dokumentgruppe,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.02 <- speaking.data.02.02 %>% filter (Code == "speaking time\\teacher",
-                                                       Dokumentgruppe == "kodiert von Anna")
-speaking.data.02.02 <- sum(speaking.data.02.02$Abdeckungsgrad..)
-
-# read in data for 02_03_novice_C
-speaking.data.02.03 <- read.delim("./data/Aperol_pilot_02_03_novice_C_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.03 <- speaking.data.02.03 %>% select(
-  Dokumentgruppe,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.03 <- speaking.data.02.03 %>% filter (Code == "speaking time\\teachter",
-                                                       Dokumentgruppe == "02_03_kodiert von Anna")
-speaking.data.02.03 <- sum(speaking.data.02.03$Abdeckungsgrad..)
-
-# read in data for 02_04_novice_D
-speaking.data.02.04 <- read.delim("./data/Aperol_pilot_02_04_novice_D_cam1.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.04 <- speaking.data.02.04 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.04 <- speaking.data.02.04 %>% filter (Code == "speaking time\\teachter")
-speaking.data.02.04 <- sum(speaking.data.02.04$Abdeckungsgrad..)
-
-```
-
-```{r speaking plot, echo=FALSE}
-
-# read in table with coded speaking time included
-speaking.data <- read.delim("./data/plus_coded_speaking_time_questionnaire_data_0802.txt", dec=",", sep="\t", header=T)
-
-# to compare both sessions filter only Identical items
-speaking.data <- speaking.data  %>% filter(str_detect(scale, 
-                                                 paste(c("Duration of speaking time"),
-                                                    collapse = '|')))
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-speaking.data <- speaking.data %>%  mutate(value = as.numeric(value))
-
-speaking.plot <- speaking.data %>%
-  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
-    geom_boxplot() +
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    theme_light() +
-    theme(
-      legend.position="none",
-      plot.title = element_text(size=11),
-      axis.text.x = element_text(size = 8)) +
-    facet_grid(group~perspective) +
-    ggtitle("Boxplot with individual points for Duration of speaking time") +
-    xlab("")
-speaking.plot
-
-```
-
-### Eyetracking Data
-
-The Tobii Pro Lab 2 software was used to analyze the teachers' visual attetion during each mini-lesson.
-The software allows for non-screen based recordings of a participants’ attention while moving in real-world settings.
-The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video.
-In order to map multiple recordings to AOIs, we first imported the eye-tracking recordings into the Tobii Pro Analyzer software.
-Second, we created dynamic Areas of Interest (AOI) manually to plot the gaze data.
-Once the AOIs are created, the gaze recordings of multiple recordings can be mapped and analyzed in aggregated form.
-Tobii Pro does not allow to do AOI based analyses within Pro Lab.
-So we exported a tsv.
-file to do further analyses in the software R.
-
-#### Gaze relational index (GRI)
-
-The GRI is a measure of visual expertise in information processing.
-This metric is calculated as the ratio of mean fixation duration to fixation count.
-The GRI is higher for novices than for experts.
-[@gegenfurtner2020gaze]
-
-```{r GRItable, echo = FALSE}
-
-# prepare data (selected from questionnaire data)
-et.raw.data<-read.table("./data/Aperol_pilot_glasses_raw_fixation_saccades_metrics.tsv", dec=",", sep="\t", header=T)
-
-# converting integer to numeric
-et.raw.data <- et.raw.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.raw.table <- et.raw.data %>%
-  group_by(Participant, Variable) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-
-# format and insert table in manuscript
-apa_table(
-  et.raw.table,
-  caption = "Number and Duration (in msec) of Fixations",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
-
-```{r calibration phase TOI, echo = FALSE}
-
-# prepare data (selected from questionnaire data)
-et.calib.data<-read.table("./data/Aperol_pilot_glasses_raw_ALL_metrics_calib_without_AOI_snapshot.tsv", dec=",", sep="\t", header=T)
-
-# converting integer to numeric
-et.calib.data <- et.calib.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-# select relevant rows 
-et.calib.data <- et.calib.data %>% filter(TOI == "Calibration phase")
-
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.calib.table <- et.calib.data %>%
-  group_by(Participant, Variable1) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-
-# format and insert table in manuscript
-apa_table(
-  et.calib.table,
-  caption = "Number and Duration (in msec) of Fixations during calibration",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
-
-```{r Calib end to lession start TOI, echo = FALSE}
-
-# prepare data (selected from questionnaire data)
-et.calib.lesson.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_calib_end_lesson_start.tsv", dec=",", sep="\t", header=T)
-
-# converting integer to numeric
-et.calib.lesson.data <- et.calib.lesson.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-options(digits = 2)
-
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.calib.lesson.table <- et.calib.lesson.data %>%
-  group_by(Participant, Variable1) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-
-# format and insert table in manuscript
-apa_table(
-  et.calib.lesson.table,
-  caption = "Number and Duration (in msec) of Fixations Calibration End to Lesson Start",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
-
-```{r Disturbance "head on table" to first intervention, echo = FALSE}
-
-# prepare data (selected from questionnaire data)
-et.distub.head.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_head_on_table_session1.tsv", dec=",", sep="\t", header=T)
-
-# converting integer to numeric
-et.distub.head.data <- et.distub.head.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-options(digits = 2)
-
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.distub.head.table <- et.distub.head.data %>%
-  group_by(Participant, Variable1) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-view(et.distub.head.data)
-
-# format and insert table in manuscript
-apa_table(
-  et.distub.head.table,
-  caption = "Number and Duration (in msec) of Fixations for Disturbance 'head on table' to first intervention",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
+To analyze gaze points in the AOIs, areas relevant to the research question must be defined in the Tobii Pro Lab software. For how AOIs are set and manually coded, see Supplement 5 Coding with AOIs.
 
@@
 
-### Questionnaire Data
-
-### Behavioral Data
-
-### Eyetracking Data
+### Eye Tracking Data
 

### 2021-08-26 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_ET_coding_data-script.R
upload R script eye tracking reli

@@ -1,0 +1,47 @@
+### ProVisioNET pilot data 
+#### intercoder reli eye tracking data 03_03
+
+
+# if a package is not installed on the current machine, it will install it
+if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
+if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
+if (!require(papaja)) install.packages("papaja"); library(papaja)
+if (!require(psych)) install.packages('psych'); library(psych) # stats
+if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
+if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
+
+r_refs("r-references.bib")
+
+# read in data from rater1 while specifying locale allows to set "," 
+coding_data_r1 <-read_tsv ("./data/03_03_EH_ProVisioNET_study_glasses Metrics_event-based.tsv", 
+                   locale = locale(decimal_mark = ","))
+
+# select variable AOI + Hit_proportion
+r1 <- coding_data_r1 %>% select(AOI, Hit_proportion)
+
+#delete NAs
+r1 <- na.omit(r1)
+
+# round Hit_proportion to 1
+options(digits = 0)              
+
+#aggregate data by AOI
+r1 <- aggregate(r1,
+                by = list(r1$AOI),
+                FUN = length)
+
+r1
+
+
+
+
+
+
+
+
+
+

### 2021-08-27 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_ET_coding_data-script.R
Update ProVisioNET_ET_coding_data-script.R

@@ -16,12 +16,19 @@ options(dplyr.summarise.inform = FALSE)
 
 r_refs("r-references.bib")
 
+
+################## RATER 1 ################
+
 # read in data from rater1 while specifying locale allows to set "," 
 coding_data_r1 <-read_tsv ("./data/03_03_EH_ProVisioNET_study_glasses Metrics_event-based.tsv", 
                    locale = locale(decimal_mark = ","))
 
+# filter only rows lesson
+r1 <- coding_data_r1 %>% filter(TOI == "Lesson")
+
 # select variable AOI + Hit_proportion
-r1 <- coding_data_r1 %>% select(AOI, Hit_proportion)
+r1 <- r1 %>% select(AOI, Hit_proportion)
+
 
 #delete NAs
 r1 <- na.omit(r1)
@@ -34,14 +41,60 @@ r1 <- aggregate(r1,
                 by = list(r1$AOI),
                 FUN = length)
 
+# select only one row and rename columns 
+r1 <- r1 %>% select (Group.1, Hit_proportion) %>%
+              rename(AOI = Group.1,
+                     AOI_hit_r1 = Hit_proportion)  
+    
 r1
 
+################## RATER 2 ################
+
+# read in data from rater1 while specifying locale allows to set "," 
+coding_data_r2 <-read_tsv ("./data/03_03_RD_ProVisioNET_study_glasses Metrics_event-based.tsv", 
+                           locale = locale(decimal_mark = ","))
+
+# filter only rows lesson
+r2 <- coding_data_r2 %>% filter(TOI == "Lesson")
+
+# select variable AOI + Hit_proportion
+r2 <- r2 %>% select(AOI, Hit_proportion)
 
 
+#delete NAs
+r2 <- na.omit(r2)
+
+# round Hit_proportion to 1
+options(digits = 0)              
+
+#aggregate data by AOI
+r2 <- aggregate(r2,
+                by = list(r2$AOI),
+                FUN = length)
+
+# select only one row and rename columns 
+r2 <- r2 %>% select (Group.1, Hit_proportion) %>%
+  rename(AOI = Group.1,
+         AOI_hit_r2 = Hit_proportion)  
+
+r2
 
 
+###### filter only for identical rows for both rater
 
+r1 <- r1 %>% filter(AOI != "Board_Screen",
+                    AOI != "Disruptive_Person,students_material", 
+                    AOI != "Material",
+                    AOI != "students_material")
 
+r1
+
[…]

### 2021-08-27 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_TOI-based_data.Rmd
Reliability test R Code

---
title: "TOI based ProVisioNet"
output: html_notebook
---

# Packages

```{r}
library(needs)
needs(tidyverse,
      psych)
```

# Read Data sets

```{r, include = FALSE}
df_EH <- read_tsv(file = "data/03_03_EH_ProVisioNET_study_glasses Metrics_interval-based.tsv"
                   )

df_RD <- read_tsv(file = "data/03_03_RD_ProVisioNET_study_glasses Metrics_interval-based.tsv"
                   )
```

# Data Wrangling

```{r}
df_EH <- df_EH %>% 
  select(TOI, Duration_of_interval, Start_of_interval)

df_RD <- df_RD %>% 
  select(TOI, Duration_of_interval, Start_of_interval)

# Start

df_cappa_start <- matrix(ncol = 3,
                         nrow = 8)

colnames(df_cappa_start) <- c("TOI","Start_of_interval_EH","Start_of_interval_RD")

df_cappa_start <- as_tibble(df_cappa_start)

TOI_names <- c("Calibration_phase","Clicking_pen","Drumming_with_hands",
               "Head_on_table","Heckling","Lesson","Snipping_with_fingers",
               "Whispering")

df_cappa_start$TOI <- TOI_names

# EH Start TOI
for (i in TOI_names) {

  val <- df_EH$Start_of_interval[df_EH == i]

  df_cappa_start$Start_of_interval_EH[df_cappa_start$TOI == i] <- val
}

# RD Start TOI
for (i in TOI_names) {

  val <- df_RD$Start_of_interval[df_RD == i]

  df_cappa_start$Start_of_interval_RD[df_cappa_start$TOI == i] <- val
}

# Duration

df_cappa_dur <- matrix(ncol = 3,
                       nrow = 8)

colnames(df_cappa_dur) <- c("TOI","Duration_of_interval_EH","Duration_of_interval_RD")

df_cappa_dur <- as_tibble(df_cappa_dur)

TOI_names <- c("Calibration_phase","Clicking_pen","Drumming_with_hands",
               "Head_on_table","Heckling","Lesson","Snipping_with_fingers",
               "Whispering")

df_cappa_dur$TOI <- TOI_names

# EH Duration TOI
for (i in TOI_names) {

  val <- df_EH$Duration_of_interval[df_EH == i]

  df_cappa_dur$Duration_of_interval_EH[df_cappa_dur$TOI == i] <- val
}

# RD Duration TOI
for (i in TOI_names) {

  val <- df_RD$Duration_of_interval[df_RD == i]

  df_cappa_dur$Duration_of_interval_RD[df_cappa_dur$TOI == i] <- val
}

```

# Reliabiltät

## Duration

```{r}
cor.test(x = df_cappa_dur$Duration_of_interval_EH[df_cappa_dur$TOI != "Lesson"],
     y = df_cappa_dur$Duration_of_interval_RD[df_cappa_dur$TOI != "Lesson"],
          method = "pearson")

ICC(x = select(df_cappa_dur,
               Duration_of_interval_EH,
               Duration_of_interval_RD
               )
    )

plot(x = df_cappa_dur$Duration_of_interval_EH[df_cappa_dur != "Lesson"],
     y = df_cappa_dur$Duration_of_interval_RD[df_cappa_dur != "Lesson"])
```

## Start

```{r}
cor.test(x = df_cappa_start$Start_of_interval_EH[df_cappa_start$TOI != "Lesson"],
     y = df_cappa_start$Start_of_interval_RD[df_cappa_start$TOI != "Lesson"],
          method = "pearson")

ICC(x = select(df_cappa_start,
               Start_of_interval_EH,
               Start_of_interval_RD
               )
    )

plot(x = df_cappa_start$Start_of_interval_EH[df_cappa_start != "Lesson"],
     y = df_cappa_start$Start_of_interval_RD[df_cappa_start != "Lesson"])
```

### 2021-08-30 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_TOI-based_data.Rmd

@@
 needs(tidyverse,
-      psych)
+      psych,
+      ggthemes
+      )
 ```
@@
 
+# In seconds
+
+df_cappa_dur$Duration_of_interval_EH <- round(df_cappa_dur$Duration_of_interval_EH/1000,
+                                              digits = 2
+                                              )
+
+df_cappa_dur$Duration_of_interval_RD <- round(df_cappa_dur$Duration_of_interval_RD/1000,
+                                              digits = 2
+                                              )
+
+df_cappa_start$Start_of_interval_EH <- round(df_cappa_start$Start_of_interval_EH/1000,
+                                              digits = 2
+                                              )
+
+df_cappa_start$Start_of_interval_RD <- round(df_cappa_start$Start_of_interval_RD/1000,
+                                              digits = 2
+                                             )
+```
+
+#
+```{r}
+fun_1 <- function(x) {
+    y <- x
+    return(y)
+  }
 ```
@@
 ```{r}
-cor.test(x = df_cappa_dur$Duration_of_interval_EH[df_cappa_dur$TOI != "Lesson"],
-     y = df_cappa_dur$Duration_of_interval_RD[df_cappa_dur$TOI != "Lesson"],
+cor.test(x = df_cappa_dur$Duration_of_interval_EH,
+     y = df_cappa_dur$Duration_of_interval_RD,
           method = "pearson")
@@
 
-plot(x = df_cappa_dur$Duration_of_interval_EH[df_cappa_dur != "Lesson"],
-     y = df_cappa_dur$Duration_of_interval_RD[df_cappa_dur != "Lesson"])
+# Lesson is significant longer and gives a biased view on the points.
+
+ggplot(data = filter(df_cappa_dur,
+                     TOI != "Lesson"),
+       mapping = aes(x = Duration_of_interval_RD,
+                     y = Duration_of_interval_EH
+                     )
+       ) +
+  geom_point(size = 2) +
+  geom_abline(intercept = 0,
+              slope = 1,
+              color = "red",
+              linetype = 3
+              ) +
+  labs(x = "Duration coded by RD",
+       y = "Duration coded by EH",
+       title = "Inter-coder reliability"
+       ) +
+  theme_minimal()
 ```
@@
 ```{r}
-cor.test(x = df_cappa_start$Start_of_interval_EH[df_cappa_start$TOI != "Lesson"],
-     y = df_cappa_start$Start_of_interval_RD[df_cappa_start$TOI != "Lesson"],
+cor.test(x = df_cappa_start$Start_of_interval_EH,
+     y = df_cappa_start$Start_of_interval_RD,
           method = "pearson")
@@
 
-plot(x = df_cappa_start$Start_of_interval_EH[df_cappa_start != "Lesson"],
-     y = df_cappa_start$Start_of_interval_RD[df_cappa_start != "Lesson"])
+ggplot(data = filter(df_cappa_start,
+                     TOI != "Lesson"),
+       mapping = aes(x = Start_of_interval_RD,
+                     y = Start_of_interval_EH
+                     )
+       ) +
+  geom_point(size = 2) +
+  geom_abline(intercept = 0,
+              slope = 1,
+              color = "red",
+              linetype = 3
+              ) +
+  labs(x = "Start coded by RD",
+       y = "Start coded by EH",
+       title = "Inter-coder reliability"
+       ) +
+  theme_minimal()
 ```

### 2021-08-30 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_ET_coding_data-script.R
update r script ICC AOI hit

@@ -96,5 +96,21 @@ r2 <- r2 %>% filter(AOI != "Board_Screen",
                     AOI != "students_material")
 r2
 
+# merge two data frames --> adding Columns
+
+r3 <- merge(r1, r2)
+
+# build a subset that contains the two AOI hit variables  
+data_icc <- subset(r3, select = c(AOI_hit_r1, AOI_hit_r2))
+
+# calculate the ICC for two raters with new subset
+ICC(data_icc)
+
+
+
+
+
+
+
 
 

### 2021-09-01 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_ET_coding_data-script_comments.R
update r script

@@ -22,7 +22,8 @@ needs(tidyverse,
       papaja,
       psych,
       moments,
-      sjPlot)
+      sjPlot,
+      DescTools)
 
 # suppress "summarize" info. 
 # if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console

### 2021-09-01 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_ET_coding_data-script_comments.R
Delete ProVisioNET_ET_coding_data-script_comments.R

@@ -1,73 +1,0 @@
-### ProVisioNET pilot data 
-#### intercoder reli eye tracking data 03_03
-
-
-# if a package is not installed on the current machine, it will install it
-if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
-if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
-if (!require(papaja)) install.packages("papaja"); library(papaja)
-if (!require(psych)) install.packages('psych'); library(psych) # stats
-if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
-if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
-
-# pro tip: There is a package called needs. needs simplyfies you code and makes it
-  # easier portable. It includes the function needs(). Needs only uses the packages 
-  # as arguments.
-
-
-# Don' run:
-install.packages("needs")
-library(needs)
-needs(tidyverse,
-      papaja,
-      psych,
-      moments,
-      sjPlot,
-      DescTools)
-
-# suppress "summarize" info. 
-# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
-options(dplyr.summarise.inform = FALSE)
-
-r_refs("r-references.bib")
-
-# read in data from rater1 while specifying locale allows to set "," 
-coding_data_r1 <-read_tsv ("./data/03_03_EH_ProVisioNET_study_glasses Metrics_event-based.tsv", 
-                   locale = locale(decimal_mark = ","))
-
-# select variable AOI + Hit_proportion
-r1 <- coding_data_r1 %>% select(AOI, Hit_proportion)
-
-#delete NAs
-r1 <- na.omit(r1)
-
-# round Hit_proportion to 1
-options(digits = 0)
-
-#alternative (maybe safer)
-
-r1$Hit_proportion <- round(r1$Hit_proportion,
-                           digits = 0)
-
-#aggregate data by AOI
-r1 <- aggregate(r1,
-                by = list(r1$AOI),
-                FUN = length)
-
-# It does not work, because aggregate from the tidyverse does only work in 
-  # combination with group_by():
-
-r1_aggr <- group_by(.data = r1,
-                    AOI) %>% summarise(Hit_count = length(Hit_proportion))
-
-
-
-
-
-
-
-
-
-
-
-

### 2021-09-06 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_AOI-event-based_data.R
update r script reli v.e.

@@ -1,0 +1,109 @@
+### ProVisioNET pilot data 
+#### intercoder reli eye tracking data 03_03
+
+
+# if a package is not installed on the current machine, it will install it
+if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
+if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
+if (!require(papaja)) install.packages("papaja"); library(papaja)
+if (!require(psych)) install.packages('psych'); library(psych) # stats
+if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
+if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
+if (!require(DescTools)) install.packages('DescTools'); library(DescTools) # cohens kappa
+
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
+
+r_refs("r-references.bib")
+
+
+################## RATER 1 ################
+
+# read in data from rater1 while specifying locale allows to set "," 
+coding_data_r1 <-read_tsv ("./data/03_03_EH_ProVisioNET_study_glasses Metrics_event-based.tsv", 
+                   locale = locale(decimal_mark = ","))
+
+# filter only rows lesson
+r1 <- coding_data_r1 %>% filter(TOI == "Lesson")
+
+# select variable AOI + Hit_proportion
+r1 <- r1 %>% select(AOI, Hit_proportion)
+
+
+#delete NAs
+r1 <- na.omit(r1)
+
+# round Hit_proportion to 1
+r1$Hit_proportion <- round(r1$Hit_proportion,
+                           digits = 0)
+
+# group data by AOI and summarise Hit_prop
+r1_aggr <- group_by(.data = r1,
+                    AOI) %>% summarise(Hit_count = length(Hit_proportion))
+
+################## RATER 2 ################
+
+# read in data from rater1 while specifying locale allows to set "," 
+coding_data_r2 <-read_tsv ("./data/03_03_RD_ProVisioNET_study_glasses Metrics_event-based.tsv", 
+                           locale = locale(decimal_mark = ","))
+
+# filter only rows lesson
+r2 <- coding_data_r2 %>% filter(TOI == "Lesson")
+
+# select variable AOI + Hit_proportion
[…]

### 2021-09-06 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_visual_engagement_reli_01_01.R

@@ -34,17 +34,29 @@ r1 <- na.omit(r1)
 r2 <-read_excel ("./data/coding_expertise_visual_engagement_FP.xlsx")
 
 
-# merge two data frames --> adding Columns, don't forget to merge BY AOI !
+################## DATA WRANGLING ################
 
-r3 <- merge(r1, r2, by = 'AOI')
+# different number of variables in r1 and r2 --> select all variables in r2 till 986
+r2new <- r2[c(1:986)]
 
-#################### Percentage Agreement ##############################
+# merge two data frames vertically with rbind
+r3 <- rbind(r1, r2new)
 
-# create a new df with only the ratings 
-r3_agree <- r3 %>% select(Hit_count.x, Hit_count.y)
+# add a new column to differentiate rater1 and rater2 in wide format
+r3$Added_Column <- c("rater1", "rater2")
 
-# function agree() with a tolerance
-agree(r3_agree, tolerance=50)
+#rename column
+r3 <- r3 %>% rename(rater = Added_Column)
+
+# relocate the column to the first place
+r3 <- r3 %>% relocate(rater)
+
+# create a new df r3 with only the ratings 
+r3 <- r3[-c(2:3)]
+
+# wide to long format
+r3_long <- gather(r3, timestamp, value, 2:985)
+
 
 #################### CohenKappa ##############################
 
@@ -54,12 +66,3 @@ ratertab
 
 # now you can calculate CohenKappa
 CohenKappa(ratertab)
-
-
-#################### ICC ##############################
-
-# build a subset that contains the two AOI hit variables  
-data_icc <- subset(r3, select = c(Hit_count.x, Hit_count.y))
-
-# calculate the ICC for two raters with new subset
-ICC(data_icc)

### 2021-09-07 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_visual_engagement_reli_01_01.R
wider_longer_bla

@@ -57,6 +57,8 @@ r3 <- r3[-c(2:3)]
 # wide to long format
 r3_long <- gather(r3, timestamp, value, 2:985)
 
+r3_long_wide <- pivot_wider(r3_long,
+                            names_from = rater)
 
 #################### CohenKappa ##############################
 

### 2021-09-07 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_visual_engagement_reli_01_01.R
Update ProVisioNET_visual_engagement_reli_01_01.R

@@ -60,10 +60,14 @@ r3_long <- gather(r3, timestamp, value, 2:985)
 r3_long_wide <- pivot_wider(r3_long,
                             names_from = rater)
 
+# create again a new df r3 with only the ratings 
+r3_long_wide <- r3_long_wide[c(2:3)]
+
+
 #################### CohenKappa ##############################
 
 # first, create a xtab and specify who is rater1 and rater2
-ratertab <- xtabs(~r3$Hit_count.x + r3$Hit_count.y)
+ratertab <- xtabs(~r3_long_wide$rater1 + r3_long_wide$rater2)
 ratertab
 
 # now you can calculate CohenKappa

### 2021-09-07 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_reli_01_01_TOI-based_data.Rmd
update R reaction video 01_01

---
title: "TOI based ProVisioNet"
output: html_notebook
---

# Packages

```{r}
if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
if (!require(papaja)) install.packages("papaja"); library(papaja)
if (!require(psych)) install.packages('psych'); library(psych) # stats
if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
if (!require(DescTools)) install.packages('DescTools'); library(DescTools) # cohens kappa
if (!require(irr)) install.packages('irr'); library(irr) # Various Coefficients of Interrater Reliability and Agreement
if (!require(readxl)) install.packages('readxl'); library(readxl) # read in excel files

```

# Read Data sets

```{r, include = FALSE}
df_AP <- read_tsv(file = "data/01_01_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv"
                   )

df_MK <- read_tsv(file = "data/01_01_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv"
                   )
```

# Data Wrangling

```{r}
df_AP <- df_AP %>% 
  select(TOI, Duration_of_interval, Start_of_interval)

df_MK <- df_MK %>% 
  select(TOI, Duration_of_interval, Start_of_interval)

# Start

df_cappa_start <- matrix(ncol = 3,
                         nrow = 8)

colnames(df_cappa_start) <- c("TOI","Start_of_interval_EH","Start_of_interval_RD")

df_cappa_start <- as_tibble(df_cappa_start)

TOI_names <- c("Calibration_phase","Clicking_pen","Drumming_with_hands",
               "Head_on_table","Heckling","Lesson","Snipping_with_fingers",
               "Whispering")

df_cappa_start$TOI <- TOI_names

# AP Start TOI
for (i in TOI_names) {

  val <- df_AP$Start_of_interval[df_AP == i]

  df_cappa_start$Start_of_interval_AP[df_cappa_start$TOI == i] <- val
}

# MK Start TOI
for (i in TOI_names) {

  val <- df_MK$Start_of_interval[df_MK == i]

  df_cappa_start$Start_of_interval_MK[df_cappa_start$TOI == i] <- val
}

# Duration

df_cappa_dur <- matrix(ncol = 3,
                       nrow = 8)

colnames(df_cappa_dur) <- c("TOI","Duration_of_interval_EH","Duration_of_interval_RD")

df_cappa_dur <- as_tibble(df_cappa_dur)

TOI_names <- c("Calibration_phase","Clicking_pen","Drumming_with_hands",
               "Head_on_table","Heckling","Lesson","Snipping_with_fingers",
               "Whispering")

df_cappa_dur$TOI <- TOI_names

# AP Duration TOI
for (i in TOI_names) {

  val <- df_AP$Duration_of_interval[df_AP == i]

  df_cappa_dur$Duration_of_interval_AP[df_cappa_dur$TOI == i] <- val
}

# MK Duration TOI
for (i in TOI_names) {

  val <- df_MK$Duration_of_interval[df_MK == i]

  df_cappa_dur$Duration_of_interval_MK[df_cappa_dur$TOI == i] <- val
}

# In seconds

df_cappa_dur$Duration_of_interval_AP <- round(df_cappa_dur$Duration_of_interval_AP/1000,
                                              digits = 2
                                              )

df_cappa_dur$Duration_of_interval_MK <- round(df_cappa_dur$Duration_of_interval_MK/1000,
                                              digits = 2
                                              )

df_cappa_start$Start_of_interval_AP <- round(df_cappa_start$Start_of_interval_AP/1000,
                                              digits = 2
                                              )

df_cappa_start$Start_of_interval_MK <- round(df_cappa_start$Start_of_interval_MK/1000,
                                              digits = 2
                                             )
```

#
```{r}
fun_1 <- function(x) {
    y <- x
    return(y)
  }
```

# Reliabiltät

## Duration

```{r}
cor.test(x = df_cappa_dur$Duration_of_interval_AP,
     y = df_cappa_dur$Duration_of_interval_MK,
          method = "pearson")

ICC(x = select(df_cappa_dur,
               Duration_of_interval_AP,
               Duration_of_interval_MK
               )
    )

# Lesson is significant longer and gives a biased view on the points.

ggplot(data = filter(df_cappa_dur,
                     TOI != "Lesson"),
       mapping = aes(x = Duration_of_interval_AP,
                     y = Duration_of_interval_MK
                     )
       ) +
  geom_point(size = 2) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Duration coded by AP",
       y = "Duration coded by MK",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```

## Start

```{r}
cor.test(x = df_cappa_start$Start_of_interval_AP,
     y = df_cappa_start$Start_of_interval_MK,
          method = "pearson")

ICC(x = select(df_cappa_start,
               Start_of_interval_AP,
               Start_of_interval_MK
               )
    )

ggplot(data = filter(df_cappa_start,
                     TOI != "Lesson"),
       mapping = aes(x = Start_of_interval_AP,
                     y = Start_of_interval_MK
                     )
       ) +
  geom_point(size = 2) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Start coded by AP",
       y = "Start coded by MK",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```

### 2021-09-07 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_expertise_reli_01_01_visual_engagement.R

@@ -1,0 +1,74 @@
+### ProVisioNET pilot data 
+#### intercoder reli expertise data 01_01
+
+
+# if a package is not installed on the current machine, it will install it
+if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
+if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
+if (!require(papaja)) install.packages("papaja"); library(papaja)
+if (!require(psych)) install.packages('psych'); library(psych) # stats
+if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
+if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
+if (!require(DescTools)) install.packages('DescTools'); library(DescTools) # cohens kappa
+if (!require(irr)) install.packages('irr'); library(irr) # Various Coefficients of Interrater Reliability and Agreement
+if (!require(readxl)) install.packages('readxl'); library(readxl) # read in excel files
+
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
+
+r_refs("r-references.bib")
+
+################## RATER 1 ################
+
+# read in data from rater1 while specifying locale allows to set "," 
+r1 <-read_excel ("./data/coding_expertise_visual_engagement_JH.xlsx")
+
+#delete NAs
+r1 <- na.omit(r1)
+
+################## RATER 2 ################
+
+# read in data from rater1 while specifying locale allows to set "," 
+r2 <-read_excel ("./data/coding_expertise_visual_engagement_FP.xlsx")
+
+
+################## DATA WRANGLING ################
+
+# different number of variables in r1 and r2 --> select all variables in r2 till 986
+r2new <- r2[c(1:986)]
+
+# merge two data frames vertically with rbind
+r3 <- rbind(r1, r2new)
+
+# add a new column to differentiate rater1 and rater2 in wide format
+r3$Added_Column <- c("rater1", "rater2")
+
+#rename column
+r3 <- r3 %>% rename(rater = Added_Column)
+
+# relocate the column to the first place
+r3 <- r3 %>% relocate(rater)
+
+# create a new df r3 with only the ratings 
+r3 <- r3[-c(2:3)]
+
+# wide to long format
+r3_long <- gather(r3, timestamp, value, 2:985)
+
[…]

### 2021-09-07 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_reli_01_01_TOI-based_data_first_reaction.R

@@ -1,0 +1,66 @@
+### ProVisioNET pilot data 
+#### intercoder reli eye tracking data 01_01
+
+if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
+if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
+if (!require(papaja)) install.packages("papaja"); library(papaja)
+if (!require(psych)) install.packages('psych'); library(psych) # stats
+if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
+if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
+if (!require(DescTools)) install.packages('DescTools'); library(DescTools) # cohens kappa
+if (!require(irr)) install.packages('irr'); library(irr) # Various Coefficients of Interrater Reliability and Agreement
+if (!require(readxl)) install.packages('readxl'); library(readxl) # read in excel files
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
+
+r_refs("r-references.bib")
+
+
+# read in data
+reaction_AP <- read_tsv(file = "data/01_01_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv"
+)
+
+reaction_MK <- read_tsv(file = "data/01_01_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv"
+)
+
+# select relevant columns
+reaction_AP <- reaction_AP %>% 
+  select(TOI, 
+         Time_to_first_Event.Reaction_chatting,
+         Time_to_first_Event.Reaction_clicking,
+         Time_to_first_Event.Reaction_drawing,
+         Time_to_first_Event.Reaction_drumming,
+         Time_to_first_Event.Reaction_head,
+         Time_to_first_Event.Reaction_heckling,
+         Time_to_first_Event.Reaction_phone,
+         Time_to_first_Event.Reaction_snipping,
+         Time_to_first_Event.Reaction_whispering
+         )
+
+reaction_MK <- reaction_MK %>% 
+  select(TOI, 
+         Time_to_first_Event.Reaction_chatting,
+         Time_to_first_Event.Reaction_clicking,
+         Time_to_first_Event.Reaction_drawing,
+         Time_to_first_Event.Reaction_drumming,
[…]

### 2021-09-08 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_reli_01_01_TOI-based_data_first_reaction.R
Update ProVisioNet_ET_reli_01_01_TOI-based_data_first_reaction.R

@@ -1,15 +1,14 @@
 ### ProVisioNET pilot data 
 #### intercoder reli eye tracking data 01_01
 
-if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
-if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
-if (!require(papaja)) install.packages("papaja"); library(papaja)
-if (!require(psych)) install.packages('psych'); library(psych) # stats
-if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
-if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
-if (!require(DescTools)) install.packages('DescTools'); library(DescTools) # cohens kappa
-if (!require(irr)) install.packages('irr'); library(irr) # Various Coefficients of Interrater Reliability and Agreement
-if (!require(readxl)) install.packages('readxl'); library(readxl) # read in excel files
+library(needs)
+needs(tidyverse,
+      psych,
+      moments,
+      sjPlot,
+      DescTools,
+      irr,
+      readxl)
 
 # suppress "summarize" info. 
 # if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
@@ -54,13 +53,67 @@ reaction_MK <- reaction_MK %>%
 
 # filter only for event TOIs 
 reaction_AP <- reaction_AP %>% 
-  filter(TOI == "Chatting_with_neighbour",
-         TOI == "Clicking_pen", 
-         TOI == "Drawing", 
-         TOI == "Drumming_with_hands", 
-         TOI == "Head_on_table", 
-         TOI == "Heckling",
-         TOI == "Looking_at_phone",
-         TOI == "Snipping_with_fingers",
+  filter(TOI == "Chatting_with_neighbour"|
+         TOI == "Clicking_pen"| 
+         TOI == "Drawing"|
+         TOI == "Drumming_with_hands"| 
+         TOI == "Head_on_table"| 
+         TOI == "Heckling"|
+         TOI == "Looking_at_phone" |
+         TOI == "Snipping_with_fingers"|
          TOI == "Whispering"
          )
+
+reaction_MK <- reaction_MK %>% 
+  filter(TOI == "Chatting_with_neighbour"|
+           TOI == "Clicking_pen"| 
+           TOI == "Drawing"|
+           TOI == "Drumming_with_hands"| 
[…]

### 2021-09-09 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_EVENTS_01_01_TOI-based_data.Rmd
R script 02_02

---
title: "TOI based ProVisioNet"
output: html_notebook
---

# Packages

```{r}
library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl)
```

# Read Data sets

```{r, include = FALSE}
df_AP_01 <- read_tsv(file = "data/01_01_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

df_MK_01 <- read_tsv(file = "data/01_01_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

df_AP_02 <- read_tsv(file = "data/02_02_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

df_MK_02 <- read_tsv(file = "data/02_02_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")
```

# Data Wrangling

```{r}

df_AP_01 <- df_AP_01 %>% 
  select(TOI, Duration_of_interval)

df_MK_01 <- df_MK_01 %>% 
  select(TOI, Duration_of_interval)

# Duration

df_cappa_dur <- matrix(ncol = 3,
                       nrow = 11)

colnames(df_cappa_dur) <- c("TOI","Duration_of_interval_AP_01","Duration_of_interval_MK_01")

df_cappa_dur <- as_tibble(df_cappa_dur)

TOI_names <- c("Calibration_phase","Chatting_with_neighbour", "Clicking_pen","Drawing", "Drumming_with_hands",
               "Head_on_table", "Looking_at_phone", "Heckling","Lesson","Snipping_with_fingers",
               "Whispering")

df_cappa_dur$TOI <- TOI_names

# AP Duration TOI
for (i in TOI_names) {

  val <- df_AP_01$Duration_of_interval[df_AP_01 == i]

  df_cappa_dur$Duration_of_interval_AP_01[df_cappa_dur$TOI == i] <- val
}

# MK Duration TOI
for (i in TOI_names) {

  val <- df_MK_01$Duration_of_interval[df_MK_01 == i]

  df_cappa_dur$Duration_of_interval_MK_01[df_cappa_dur$TOI == i] <- val
}

# In seconds

df_cappa_dur$Duration_of_interval_AP_01 <- round(df_cappa_dur$Duration_of_interval_AP_01/1000,
                                              digits = 2
                                              )

df_cappa_dur$Duration_of_interval_MK_01 <- round(df_cappa_dur$Duration_of_interval_MK_01/1000,
                                              digits = 2
                                              )

```

#
```{r}
fun_1 <- function(x) {
    y <- x
    return(y)
  }
```

# Reliabiltät

## Duration

```{r}
cor.test(x = df_cappa_dur$Duration_of_interval_AP,
     y = df_cappa_dur$Duration_of_interval_MK,
          method = "pearson")

ICC(x = select(df_cappa_dur,
               Duration_of_interval_AP,
               Duration_of_interval_MK
               )
    )

# Lesson is significant longer and gives a biased view on the points.

ggplot(data = filter(df_cappa_dur,
                     TOI != "Lesson"),
       mapping = aes(x = Duration_of_interval_AP,
                     y = Duration_of_interval_MK
                     )
       ) +
  geom_point(size = 2) +
  geom_text(mapping = aes(label = TOI)
            ) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Duration coded by AP",
       y = "Duration coded by MK",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```

## Start

```{r}
cor.test(x = df_cappa_start$Start_of_interval_AP,
     y = df_cappa_start$Start_of_interval_MK,
          method = "pearson")

ICC(x = select(df_cappa_start,
               Start_of_interval_AP,
               Start_of_interval_MK
               )
    )

ggplot(data = filter(df_cappa_start,
                     TOI != "Lesson"),
       mapping = aes(x = Start_of_interval_AP,
                     y = Start_of_interval_MK
                     )
       ) +
  geom_point(size = 2) +
  geom_text(mapping = aes(label = TOI)
            ) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Start coded by AP",
       y = "Start coded by MK",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```

### 2021-09-10 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_EVENTS_01_01_TOI-based_data.Rmd
Aggregated TOI

@@
 
-df_AP_02 <- read_tsv(file = "data/02_02_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")
+# df_AP_02 <- read_tsv(file = "data/02_02_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")
 
@@
                                               digits = 2
+                                              )
+
+```
+
+Erstellen von TOI_class
+```{r}
+df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Calibration_phase"] <- "Calibration_phase"
+
+df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Chatting_with_neighbour" |
+                         df_cappa_dur$TOI == "Heckling" |
+                         df_cappa_dur$TOI == "Whispering"] <- "Verbal_disruption"
+
+df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Head_on_table" |
+                         df_cappa_dur$TOI == "Looking_at_phone" |
+                         df_cappa_dur$TOI == "Drawing"] <- "lack_of_eagerness"
+
+df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Lesson"] <- "Lesson"
+
+df_cappa_dur$TOI_class[is.na(df_cappa_dur$TOI_class)] <- "Agitation"
+
+df_cappa_dur$TOI_class <- as_factor(df_cappa_dur$TOI_class)
+
+df_cappa_dur_aggr <- df_cappa_dur %>%
+  group_by(TOI_class) %>%
+  summarise(Duration_mean_AP = mean(Duration_of_interval_AP_01),
+            Duration_mean_MK = mean(Duration_of_interval_MK_01)
             )

### 2021-09-10 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_EVENTS_01_01_TOI-based_data.Rmd
update TOI classes

@@
 
-df_MK_02 <- read_tsv(file = "data/02_02_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")
+# df_MK_02 <- read_tsv(file = "data/02_02_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")
+
+df_AP_04 <- read_tsv(file = "data/04_04_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")
+
+df_MK_04 <- read_tsv(file = "data/04_04_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")
+
 ```
@@
 df_MK_01 <- df_MK_01 %>% 
+  select(TOI, Duration_of_interval)
+
+# df_AP_02 <- df_AP_02 %>% 
+#   select(TOI, Duration_of_interval)
+# 
+# df_MK_02 <- df_MK_02 %>% 
+#   select(TOI, Duration_of_interval)
+
+df_AP_04 <- df_AP_04 %>% 
+  select(TOI, Duration_of_interval)
+
+df_MK_04 <- df_MK_04 %>% 
   select(TOI, Duration_of_interval)
@@
 
-# AP Duration TOI
+# AP_01 Duration TOI
 for (i in TOI_names) {
@@
 
-# MK Duration TOI
+# MK_01 Duration TOI
 for (i in TOI_names) {
@@
 
-# In seconds
+# AP_04 Duration TOI
+for (i in TOI_names) {
 
-df_cappa_dur$Duration_of_interval_AP_01 <- round(df_cappa_dur$Duration_of_interval_AP_01/1000,
-                                              digits = 2
-                                              )
+  val <- df_AP_04$Duration_of_interval[df_AP_04 == i]
 
-df_cappa_dur$Duration_of_interval_MK_01 <- round(df_cappa_dur$Duration_of_interval_MK_01/1000,
-                                              digits = 2
-                                              )
+  df_cappa_dur$Duration_of_interval_AP_04[df_cappa_dur$TOI == i] <- val
+}
+
+# MK_04 Duration TOI
+for (i in TOI_names) {
+
+  val <- df_MK_04$Duration_of_interval[df_MK_04 == i]
+
+  df_cappa_dur$Duration_of_interval_MK_04[df_cappa_dur$TOI == i] <- val
+}
 
@@
                          df_cappa_dur$TOI == "Looking_at_phone" |
-                         df_cappa_dur$TOI == "Drawing"] <- "lack_of_eagerness"
+                         df_cappa_dur$TOI == "Drawing"] <- "Lack_of_eagerness"
 
@@
   group_by(TOI_class) %>%
-  summarise(Duration_mean_AP = mean(Duration_of_interval_AP_01),
-            Duration_mean_MK = mean(Duration_of_interval_MK_01)
+  summarise(Duration_mean_AP_01 = mean(Duration_of_interval_AP_01),
+            Duration_mean_MK_01 = mean(Duration_of_interval_MK_01),
+            Duration_mean_AP_04 = mean(Duration_of_interval_AP_04),
+            Duration_mean_MK_04 = mean(Duration_of_interval_MK_04)
+            )
+
+# In seconds
+
+df_cappa_dur_aggr$Duration_mean_AP_01 <- round(df_cappa_dur_aggr$Duration_mean_AP_01/1000,
+                                              digits = 2
+                                              )
+
+df_cappa_dur_aggr$Duration_mean_MK_01 <- round(df_cappa_dur_aggr$Duration_mean_MK_01/1000,
+                                              digits = 2
+                                              )
+
+df_cappa_dur_aggr$Duration_mean_AP_04 <- round(df_cappa_dur_aggr$Duration_mean_AP_04/1000,
+                                              digits = 2
+                                              )
+
+df_cappa_dur_aggr$Duration_mean_MK_04 <- round(df_cappa_dur_aggr$Duration_mean_MK_04/1000,
+                                              digits = 2
                                               )

### 2021-09-10 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_reli_01_01_04_04_AOI-based_data.Rmd
R script total duration AOIs

---
title: "AOI based ProVisioNet"
output: html_notebook
---

# Packages

```{r}
library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl)
```

# Read Data sets

```{r, include = FALSE}
AOI_AP_01 <- read_tsv(file = "data/01_01_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv"
                   )

AOI_MK_01 <- read_tsv(file = "data/01_01_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv"
                  )

AOI_AP_04 <- read_tsv(file = "data/04_04_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

AOI_MK_04 <- read_tsv(file = "data/04_04_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

```

# Data Wrangling

```{r}

# select relevant columns
AOI_AP_01 <- AOI_AP_01 %>% 
  select(TOI,
         starts_with("Total_duration_of_fixation"))

AOI_MK_01 <- AOI_MK_01 %>% 
  select(TOI,
         starts_with("Total_duration_of_fixation"))

AOI_AP_04 <- AOI_AP_04 %>% 
  select(TOI,
         starts_with("Total_duration_of_fixation"))

AOI_MK_04 <- AOI_MK_04 %>% 
  select(TOI,
         starts_with("Total_duration_of_fixation"))

# filter only for TOIs
AOI_AP_01 <- AOI_AP_01 %>% 
  filter(  TOI == "Chatting_with_neighbour" |
           TOI == "Clicking_pen" |
           TOI == "Drawing" | 
           TOI == "Drumming_with_hands" |
           TOI == "Head_on_table" |
           TOI == "Looking_at_phone" |
           TOI == "Heckling"| 
           TOI == "Lesson" | 
           TOI == "Snipping_with_fingers" |
           TOI == "Whispering" |
          TOI == "Entire Recording")

AOI_MK_01 <- AOI_MK_01 %>% 
  filter(  TOI == "Chatting_with_neighbour" |
           TOI == "Clicking_pen" |
           TOI == "Drawing" | 
           TOI == "Drumming_with_hands" |
           TOI == "Head_on_table" |
           TOI == "Looking_at_phone" |
           TOI == "Heckling"| 
           TOI == "Lesson" | 
           TOI == "Snipping_with_fingers" |
           TOI == "Whispering" |
          TOI == "Entire Recording")

AOI_AP_04 <- AOI_AP_04 %>% 
  filter(  TOI == "Chatting_with_neighbour" |
           TOI == "Clicking_pen" |
           TOI == "Drawing" | 
           TOI == "Drumming_with_hands" |
           TOI == "Head_on_table" |
           TOI == "Looking_at_phone" |
           TOI == "Heckling"| 
           TOI == "Lesson" | 
           TOI == "Snipping_with_fingers" |
           TOI == "Whispering"|
          TOI == "Entire Recording")

AOI_MK_04 <- AOI_MK_04 %>% 
  filter(  TOI == "Chatting_with_neighbour" |
           TOI == "Clicking_pen" |
           TOI == "Drawing" | 
           TOI == "Drumming_with_hands" |
           TOI == "Head_on_table" |
           TOI == "Looking_at_phone" |
           TOI == "Heckling"| 
           TOI == "Lesson" | 
           TOI == "Snipping_with_fingers" |
           TOI == "Whispering"|
          TOI == "Entire Recording")

# create new column names that give total duration of looking at all AOIs
AOI_AP_01 <- AOI_AP_01  %>% 
  rename (Anna = Total_duration_of_fixations.Anna,
          Bianca = Total_duration_of_fixations.Bianca,
          Carl_a = `Total_duration_of_fixations.Carl(a)`,
          Disruptive_Person = Total_duration_of_fixations.Disruptive_Person,
          Board_Screen = Total_duration_of_fixations.Board_Screen,
          Classroom_Others = Total_duration_of_fixations.Classroom_Others,
          Material = Total_duration_of_fixations.Material,
          Nametag_Anna = Total_duration_of_fixations.Nametag_Anna,
          Nametag_Bianca = Total_duration_of_fixations.Nametag_Bianca,
          Nametage_Carl_a = `Total_duration_of_fixations.Nametag_Carl(a)`)

AOI_MK_01 <- AOI_MK_01  %>% 
  rename (Anna = Total_duration_of_fixations.Anna,
          Bianca = Total_duration_of_fixations.Bianca,
          Carl_a = `Total_duration_of_fixations.Carl(a)`,
          Disruptive_Person = Total_duration_of_fixations.Disruptive_Person,
          Board_Screen = Total_duration_of_fixations.Board_Screen,
          Classroom_Others = Total_duration_of_fixations.Classroom_Others,
          Teacher_Material = Total_duration_of_fixations.Material_Teacher,
          Students_Material = Total_duration_of_fixations.Material_Students,
          Nametag_Anna = Total_duration_of_fixations.Nametag_Anna,
          Nametag_Bianca = Total_duration_of_fixations.Nametag_Bianca,
          Nametage_Carl_a = `Total_duration_of_fixations.Nametag_Carl(a)`)

AOI_AP_04 <- AOI_AP_04  %>% 
  rename (Anna = Total_duration_of_fixations.Anna,
          Bianca = Total_duration_of_fixations.Bianca,
          Carl_a = `Total_duration_of_fixations.Carl(a)`,
          Disruptive_Person = Total_duration_of_fixations.Disruptive_Person,
          Board_Screen = Total_duration_of_fixations.Board_Screen,
          Classroom_Others = Total_duration_of_fixations.Classroom_Others,
          Material = Total_duration_of_fixations.Material,
          Nametag_Anna = Total_duration_of_fixations.Nametag_Anna,
          Nametag_Bianca = Total_duration_of_fixations.Nametag_Bianca,
          Nametage_Carl_a = `Total_duration_of_fixations.Nametag_Carl(a)`)

AOI_MK_04 <- AOI_MK_04  %>% 
  rename (Anna = Total_duration_of_fixations.Anna,
          Bianca = Total_duration_of_fixations.Bianca,
          Carl_a = `Total_duration_of_fixations.Carl(a)`,
          Disruptive_Person = Total_duration_of_fixations.Disruptive_Person,
          Board_Screen = Total_duration_of_fixations.Board_Screen,
          Classroom_Others = Total_duration_of_fixations.Classroom_Others,
          Students_Material = Total_duration_of_fixations.Students_material,
          Teacher_Material = Total_duration_of_fixations.Teacher_material,
          Nametag_Anna = Total_duration_of_fixations.Nametag_Anna,
          Nametag_Bianca = Total_duration_of_fixations.Nametag_Bianca,
          Nametage_Carl_a = `Total_duration_of_fixations.Nametag_Carl(a)`)

# replace NAs with 0
AOI_AP_01 <- AOI_AP_01 %>%
  mutate_all(~replace(., is.na(.), 0))

AOI_AP_04 <- AOI_AP_04 %>%
  mutate_all(~replace(., is.na(.), 0))

AOI_MK_01 <- AOI_MK_01 %>%
  mutate_all(~replace(., is.na(.), 0))

AOI_MK_04 <- AOI_MK_04 %>%
  mutate_all(~replace(., is.na(.), 0))

# create data set of total durations in long format for plotting --> for later
AOI_AP_01_long <- gather(AOI_AP_01, TOI, Duration)

AOI_MK_01_long <- gather(AOI_MK_01, TOI, Duration)

AOI_AP_04_long <- gather(AOI_AP_04, TOI, Duration)

AOI_MK_04_long <- gather(AOI_MK_04, TOI, Duration)

# create a new column with name sum_aois that gives the sum of looking at all AOIs
AOI_AP_01 <- AOI_AP_01  %>% mutate(Sum_AOI = Anna + 
                                              Bianca +
                                              Carl_a + 
                                              Disruptive_Person + 
                                              Board_Screen + 
                                              Classroom_Others + 
                                              Material + 
                                              Nametag_Anna +
                                              Nametag_Bianca + 
                                              Nametage_Carl_a)

AOI_MK_01 <- AOI_MK_01  %>% mutate(Sum_AOI = Anna + 
                                              Bianca +
                                              Carl_a + 
                                              Disruptive_Person + 
                                              Board_Screen + 
                                              Classroom_Others + 
                                              Teacher_Material +
                                              Students_Material + 
                                              Nametag_Anna +
                                              Nametag_Bianca + 
                                              Nametage_Carl_a)

################################################

# In seconds

df_cappa_dur$Duration_of_interval_AP <- round(df_cappa_dur$Duration_of_interval_AP/1000,
                                              digits = 2
                                              )

df_cappa_dur$Duration_of_interval_MK <- round(df_cappa_dur$Duration_of_interval_MK/1000,
                                              digits = 2
                                              )

df_cappa_start$Start_of_interval_AP <- round(df_cappa_start$Start_of_interval_AP/1000,
                                              digits = 2
                                              )

df_cappa_start$Start_of_interval_MK <- round(df_cappa_start$Start_of_interval_MK/1000,
                                              digits = 2
                                             )
```

#
```{r}
fun_1 <- function(x) {
    y <- x
    return(y)
  }
```

# Reliabiltät

## Duration

```{r}
cor.test(x = df_cappa_dur$Duration_of_interval_AP,
     y = df_cappa_dur$Duration_of_interval_MK,
          method = "pearson")

ICC(x = select(df_cappa_dur,
               Duration_of_interval_AP,
               Duration_of_interval_MK
               )
    )

# Lesson is significant longer and gives a biased view on the points.

ggplot(data = filter(df_cappa_dur,
                     TOI != "Lesson"),
       mapping = aes(x = Duration_of_interval_AP,
                     y = Duration_of_interval_MK
                     )
       ) +
  geom_point(size = 2) +
  geom_text(mapping = aes(label = TOI)
            ) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Duration coded by AP",
       y = "Duration coded by MK",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```

## Start

```{r}
cor.test(x = df_cappa_start$Start_of_interval_AP,
     y = df_cappa_start$Start_of_interval_MK,
          method = "pearson")

ICC(x = select(df_cappa_start,
               Start_of_interval_AP,
               Start_of_interval_MK
               )
    )

ggplot(data = filter(df_cappa_start,
                     TOI != "Lesson"),
       mapping = aes(x = Start_of_interval_AP,
                     y = Start_of_interval_MK
                     )
       ) +
  geom_point(size = 2) +
  geom_text(mapping = aes(label = TOI)
            ) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Start coded by AP",
       y = "Start coded by MK",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```

### 2021-09-13 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_EVENTS_01_01_TOI-based_data.Rmd
R script TOI AOI

@@
 df_MK_01 <- read_tsv(file = "data/01_01_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")
-
-# df_AP_02 <- read_tsv(file = "data/02_02_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")
-
-# df_MK_02 <- read_tsv(file = "data/02_02_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")
 
@@
 
+# long format for plotting
+dur_event_long  <- df_cappa_dur_aggr %>% gather(TOI, Duration)
+
 # In seconds
@@
 ```
-
-#
-```{r}
-fun_1 <- function(x) {
-    y <- x
-    return(y)
-  }
-```
-
-# Reliabiltät
-
-## Duration
-
-```{r}
-cor.test(x = df_cappa_dur$Duration_of_interval_AP,
-     y = df_cappa_dur$Duration_of_interval_MK,
-          method = "pearson")
-
-ICC(x = select(df_cappa_dur,
-               Duration_of_interval_AP,
-               Duration_of_interval_MK
-               )
-    )
-
-# Lesson is significant longer and gives a biased view on the points.
-
-ggplot(data = filter(df_cappa_dur,
-                     TOI != "Lesson"),
-       mapping = aes(x = Duration_of_interval_AP,
-                     y = Duration_of_interval_MK
-                     )
-       ) +
-  geom_point(size = 2) +
-  geom_text(mapping = aes(label = TOI)
-            ) +
-  geom_abline(intercept = 0,
-              slope = 1,
-              color = "red",
-              linetype = 3
-              ) +
-  labs(x = "Duration coded by AP",
-       y = "Duration coded by MK",
-       title = "Inter-coder reliability"
-       ) +
-  theme_minimal()
-```
-
-## Start
-
-```{r}
-cor.test(x = df_cappa_start$Start_of_interval_AP,
-     y = df_cappa_start$Start_of_interval_MK,
-          method = "pearson")
-
-ICC(x = select(df_cappa_start,
-               Start_of_interval_AP,
-               Start_of_interval_MK
-               )
-    )
-
-ggplot(data = filter(df_cappa_start,
-                     TOI != "Lesson"),
-       mapping = aes(x = Start_of_interval_AP,
-                     y = Start_of_interval_MK
-                     )
-       ) +
-  geom_point(size = 2) +
-  geom_text(mapping = aes(label = TOI)
-            ) +
-  geom_abline(intercept = 0,
-              slope = 1,
-              color = "red",
-              linetype = 3
-              ) +
-  labs(x = "Start coded by AP",
-       y = "Start coded by MK",
-       title = "Inter-coder reliability"
-       ) +
-  theme_minimal()
-```

### 2021-09-13 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_ET_reli_03_03.R

@@ -1,16 +1,17 @@
 ### ProVisioNET pilot data 
-#### intercoder reli eye tracking data 01_01
+#### intercoder reli eye tracking data 03_03
 
 
 # if a package is not installed on the current machine, it will install it
-library(needs)
-needs(tidyverse,
-      psych,
-      moments,
-      sjPlot,
-      DescTools,
-      irr,
-      readxl)
+if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
+if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
+if (!require(papaja)) install.packages("papaja"); library(papaja)
+if (!require(psych)) install.packages('psych'); library(psych) # stats
+if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
+if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
+if (!require(DescTools)) install.packages('DescTools'); library(DescTools) # cohens kappa
+if (!require(irr)) install.packages('irr'); library(irr) # Various Coefficients of Interrater Reliability and Agreement
+
 
 # suppress "summarize" info. 
 # if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
@@ -22,8 +23,8 @@ r_refs("r-references.bib")
 ################## RATER 1 ################
 
 # read in data from rater1 while specifying locale allows to set "," 
-coding_data_r1 <-read_tsv ("./data/01_01_AP_ProVisioNET_study_glasses_Metrics_Event-based.tsv", 
-                           locale = locale(decimal_mark = ","))
+coding_data_r1 <-read_tsv ("./data/03_03_EH_ProVisioNET_study_glasses Metrics_event-based.tsv", 
+                   locale = locale(decimal_mark = ","))
 
 # filter only rows lesson
 r1 <- coding_data_r1 %>% filter(TOI == "Lesson")
@@ -46,7 +47,7 @@ r1_aggr <- group_by(.data = r1,
 ################## RATER 2 ################
 
 # read in data from rater1 while specifying locale allows to set "," 
-coding_data_r2 <-read_tsv ("./data/01_01_MK_ProVisioNET_study_glasses_Metrics_Event-based.tsv", 
+coding_data_r2 <-read_tsv ("./data/03_03_RD_ProVisioNET_study_glasses Metrics_event-based.tsv", 
                            locale = locale(decimal_mark = ","))
 
 # filter only rows lesson
[…]

### 2021-09-16 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_ET_reli_01_01_AOI-based_data.R
update AOI reli

@@ -16,8 +16,6 @@ needs(tidyverse,
 # if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
 options(dplyr.summarise.inform = FALSE)
 
-r_refs("r-references.bib")
-
 
 ################## RATER 1 ################
 
@@ -28,20 +26,8 @@ coding_data_r1 <-read_tsv ("./data/01_01_AP_ProVisioNET_study_glasses_Metrics_Ev
 # filter only rows lesson
 r1 <- coding_data_r1 %>% filter(TOI == "Lesson")
 
-# select variable AOI + Hit_proportion
-r1 <- r1 %>% select(AOI, Hit_proportion)
-
-
-#delete NAs
-r1 <- na.omit(r1)
-
-# round Hit_proportion to 1
-r1$Hit_proportion <- round(r1$Hit_proportion,
-                           digits = 0)
-
-# group data by AOI and summarise Hit_prop
-r1_aggr <- group_by(.data = r1,
-                    AOI) %>% summarise(Hit_count = length(Hit_proportion))
+# select relevant variables 
+r1 <- r1 %>% select(EventIndex, AOI)
 
 ################## RATER 2 ################
 
@@ -52,54 +38,39 @@ coding_data_r2 <-read_tsv ("./data/01_01_MK_ProVisioNET_study_glasses_Metrics_Ev
 # filter only rows lesson
 r2 <- coding_data_r2 %>% filter(TOI == "Lesson")
 
-# select variable AOI + Hit_proportion
-r2 <- r2 %>% select(AOI, Hit_proportion)
+# select relevant variables
+r2 <- r2 %>% select(EventIndex, AOI)
+
+#rename values in row Material = Teacher_Material
+r2$AOI[r2$AOI == "Material_Teacher"] <- "Material"
 
 
-#delete NAs
-r2 <- na.omit(r2)
+###### filter identical row number
 
-# round Hit_proportion to 1
-r2$Hit_proportion <- round(r2$Hit_proportion,
-                           digits = 0)
+r1 <- r1 %>% filter(EventIndex != 1728,
+                    EventIndex != 1729,
+                    EventIndex != 1730,
+                    EventIndex != 1731)
 
-# group data by AOI and summarise Hit_prop
-r2_aggr <- group_by(.data = r2,
-                    AOI) %>% summarise(Hit_count = length(Hit_proportion))
+r1
 
-
[…]

### 2021-09-16 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_ET_reli_03_03_AOI-based_data.R

@@ -16,8 +16,6 @@ needs(tidyverse,
 # if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
 options(dplyr.summarise.inform = FALSE)
 
-r_refs("r-references.bib")
-
 
 ################## RATER 1 ################
 

### 2021-09-27 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_reli_reactions.R
literatur fitbit hinzugefügt

@@ -31,8 +31,34 @@ r2 <-read_excel ("./data/coding_reactions_LK_ohne_Abstufung.xlsx")
 
 ################## DATA WRANGLING ################
 
-# merge two data frames vertically with rbind
-r3 <- rbind(r1, r2)
+# filter relevant rows and select relevant columns 
+r1_v1 <- r1 %>% filter(script == "01") %>%
+               select(,4:17)
+
+r2_v1 <- r2 %>% filter(script == "01") %>%
+   select(,4:17)
+
+
+# reshape data frame in long format 
+r1_long <- gather(r1_v1, reaction, value)
+
+r2_long <- gather(r2_v1, reaction, value)
+
+r1_long$value <- as.numeric(r1_long$value)
+
+r2_long$value <- as.numeric(r2_long$value)
+
+
+# merge two data frames vertically
+r3 <- merge(r1_long, r2_long, by="reaction")
+
+
+# select only value 
+r3 <- select(r3, value.x, value.y)
+
+# compare for rating for video 01
+# filter only rows lesson
+
 
 # add a new column to differentiate rater1 and rater2 in wide format
 r3$Added_Column <- c("rater1", "rater2")

### 2021-09-27 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_reli_reactions.R
Update ProVisioNET_reli_reactions.R

@@ -9,7 +9,8 @@ needs(tidyverse,
       moments,
       sjPlot,
       irr,
-      readxl)
+      readxl, 
+      DescTool)
 
 
 # suppress "summarize" info. 
@@ -29,7 +30,7 @@ r1 <-read_excel ("./data/coding_reactions_CW_ohne_Abstufung.xlsx")
 r2 <-read_excel ("./data/coding_reactions_LK_ohne_Abstufung.xlsx")
 
 
-################## DATA WRANGLING ################
+################## DATA WRANGLING video 01 ################
 
 # filter relevant rows and select relevant columns 
 r1_v1 <- r1 %>% filter(script == "01") %>%
@@ -50,43 +51,82 @@ r2_long$value <- as.numeric(r2_long$value)
 
 
 # merge two data frames vertically
-r3 <- merge(r1_long, r2_long, by="reaction")
+r3 <- bind_cols(r1_long$value, r2_long$value) %>%
+         rename(rating1 = ...1, 
+                rating2 = ...2)
 
-
-# select only value 
-r3 <- select(r3, value.x, value.y)
 
 # compare for rating for video 01
-# filter only rows lesson
-
-
 # add a new column to differentiate rater1 and rater2 in wide format
-r3$Added_Column <- c("rater1", "rater2")
-
+# r3$Added_Column <- c("rater1", "rater2")
 #rename column
-r3 <- r3 %>% rename(rater = Added_Column)
-
+# r3 <- r3 %>% rename(rater = Added_Column)
 # relocate the column to the first place
-r3 <- r3 %>% relocate(rater)
-
+# r3 <- r3 %>% relocate(rater)
 # create a new df r3 with only the ratings 
-r3 <- r3[-c(2:3)]
+# r3 <- r3[-c(2:3)]
 
-# wide to long format
-r3_long <- gather(r3, timestamp, value, 2:985)
+# # wide to long format
+# r3_long <- gather(r3, timestamp, value, 2:985)
+# 
+# r3_long_wide <- pivot_wider(r3_long,
+#                             names_from = rater)
+# 
+# # create again a new df r3 with only the ratings 
+# r3_long_wide <- r3_long_wide[c(2:3)]
 
-r3_long_wide <- pivot_wider(r3_long,
-                            names_from = rater)
 
-# create again a new df r3 with only the ratings 
-r3_long_wide <- r3_long_wide[c(2:3)]
-
-
-#################### CohenKappa ##############################
[…]

### 2021-11-05 01_studies/01_Laborstudie ProVisioNET/Fitbit/FitBit Project/Pupil_dial.Rmd
pupil dialation

---
title: "R Notebook"
output: html_notebook
---

# Packages

```{r}
library(needs)

needs(tidyverse,
      lubridate,
      hms)
```

# Data

```{r}
df_dia <- read_rds(file = "Data/df.rds")
```

```{r}
df_dia$date_time <- 
  make_datetime(hour = hour(df_dia$start_time),
                min = minute(df_dia$start_time),
                sec = second(df_dia$start_time)
                ) + 
  seconds(as.numeric(milliseconds(df_dia$time
                                          )
                             )
                )

df_dia$seconds <- floor(second(df_dia$date_time))
df_dia$minutes <- minute(df_dia$date_time)
df_dia$hours <- hour(df_dia$date_time)

df_dia_aggr <- 
df_dia %>% 
  group_by(hours, minutes, seconds, ID) %>%
  summarise(dia_left = mean(left),
            dia_right = mean(right)
            ) %>%
  ungroup() %>%
  mutate(Time = hms(hours = hours,
                    minutes = minutes,
                    seconds = seconds
                    )
         ) %>%
  select(dia_left,
         dia_right,
         Time,
         ID)

# df_dia_aggr$time <- 
# hms(hours = df_dia_aggr$hours,
#     minutes = df_dia_aggr$minutes,
#     seconds = df_dia_aggr$seconds)
#

rm(df_dia)

```

# Heart Rate data

```{r, message=FALSE, include=FALSE, error=FALSE}
part <- read_xlsx(path = "Data/Heart Rate.xlsx")

#...............................................................................
#                                                                              .
#  Enter the missing cases in Heart Rate table below.                                       .
#                                                                              .
#...............................................................................

part <- filter(part,
              `ID participant` != 108 # |
              #`ID participant` != | etc.
              )

part <- part$`ID participant`

for (i in part) {
  nam <- paste("m", i, sep = "")
  assign(x = nam, 
         value = read_csv(file = paste("Data/", i, "_m.csv", 
                                       sep = ""
                                       )
                          )
         ) 
  }
```

# Extract data sets

```{r}
df_dia_aggr <-
  df_dia_aggr %>%
  filter(ID != "108" &
           ID != "109")

for (i in unique(df_dia_aggr$ID)) {

name <- paste0("pupil", i)
df <- filter(df_dia_aggr,
             ID == i)
assign(x = name,
       value = df)  
}
```

# concetanate data sets

```{r}

for (i in unique(df_dia_aggr$ID)) {

name1 <- paste0("m", i)
name2 <- paste0("pupil", i)
name3 <- paste0("tib_", i)
df <- left_join(x = get(name1),
                y = get(name2),
                by = "Time")

assign(name3,
       value = df)  
}

rm(df)
rm(name3)

```

```{r}
df_compl <- 
  mget(ls(pattern = "tib")) %>%
  bind_rows() %>%
  mutate(ID = as_factor(ID))
```

```{r}
ggplot(data = df_compl,
       mapping = aes(x = `Heart Rate`,
                     y = dia_right
                     )
       ) +
  geom_point()
```

### 2021-11-06 01_studies/01_Laborstudie ProVisioNET/Fitbit/FitBit Project/Pupil_dial.Rmd
pupil dial

@@
       lubridate,
-      hms)
+      hms,
+      readxl)
 ```
@@
 
-```{r, message=FALSE, include=FALSE, error=FALSE}
+```{r, message=FALSE, include=FALSE, error=FALSE, }
 part <- read_xlsx(path = "Data/Heart Rate.xlsx")
@@
 
+df <- df %>% mutate(dia_left = scale(dia_left),
+                    dia_right = scale(dia_right),
+                    `Heart Rate` = scale(`Heart Rate`)
+                    )
 assign(name3,
@@
   bind_rows() %>%
-  mutate(ID = as_factor(ID))
+  mutate(ID = as_factor(ID),
+         Type = as_factor(ifelse(test = as.numeric(as.character(ID)) > 200,
+                                 yes = "advanced",
+                                 no = "novice"
+                                 )
+                          )
+         )
 ```
@@
 ```{r}
-ggplot(data = df_compl,
-       mapping = aes(x = `Heart Rate`,
-                     y = dia_right
+ggplot(data = na.omit(df_compl),
+       mapping = aes(x = dia_right,
+                     y = `Heart Rate`
                      )
        ) +
-  geom_point()
+  geom_point(mapping = aes(color = as_factor(Type))) +
+  geom_smooth(method = "lm")
+
+ggplot(data = na.omit(df_compl),
+       mapping = aes(x = dia_left,
+                     y = `Heart Rate`
+                     )
+       ) +
+  geom_point(mapping = aes(color = as_factor(Type))) +
+  geom_smooth(method = "lm")
+
+ggplot(data = na.omit(df_compl)
+       ) + 
+  geom_histogram(mapping = aes(x = dia_left),
+                 alpha = 0.4,
+                 color = "blue") +
+  geom_histogram(mapping = aes(x = dia_right),
+                 alpha = 0.4,
+                 color = "red")
+
 ```

### 2021-11-09 01_studies/01_Laborstudie ProVisioNET/SJTest/SJTest_script.R
R script SJT

@@ -18,10 +18,10 @@ df_sjt <- df_sjt %>% select(UI06_05, SJT_AL_gek, SJT_ST_gek, SJT_R_gek, SJT_KF_g
 
 # rename columns
 df_sjt <- rename(df_sjt, c("Group" = "UI06_05",
-                            "Monitoring" = "SJT_AL_gek",
-                            "Managing momentum" = "SJT_ST_gek",
-                            "Rules and routines" = "SJT_R_gek",
-                            "All" = "SJT_KF_gek"))
+                           "Monitoring" = "SJT_AL_gek",
+                           "Managing momentum" = "SJT_ST_gek",
+                           "Rules and routines" = "SJT_R_gek",
+                           "All" = "SJT_KF_gek"))
 
 # changing from wide to long format
 df_sjt_long <- df_sjt %>% 
@@ -35,8 +35,8 @@ df_sjt_long$Group = ifelse(df_sjt_long$"Group"<200, "Novice","Expert")
 mean_ plot <- 
   
   ggplot(data = df_sjt_long,
-       mapping = aes(x = Group,
-                     y = Mean)) +
+         mapping = aes(x = Group,
+                       y = Mean)) +
   geom_boxplot(mapping = aes(fill = Group)) +
   geom_point(size = 2, 
              alpha = 0.4,
@@ -45,4 +45,3 @@ mean_ plot <-
   scale_fill_brewer(palette = "RdBu") +
   facet_wrap(~ "Facets Classroom Management", nrow = 1)+
   theme_cowplot()
-

### 2021-11-09 01_studies/01_Laborstudie ProVisioNET/SJTest/SJTest_script.R
R script Plot SJT

@@ -30,11 +30,8 @@ df_sjt_long <- df_sjt %>%
 # define expert and novice with ifelse function
 df_sjt_long$Group = ifelse(df_sjt_long$"Group"<200, "Novice","Expert")
 
-
 # plotting mean
-mean_ plot <- 
-  
-  ggplot(data = df_sjt_long,
+mean_plot <- ggplot(data = df_sjt_long,
          mapping = aes(x = Group,
                        y = Mean)) +
   geom_boxplot(mapping = aes(fill = Group)) +
@@ -45,3 +42,5 @@ mean_ plot <-
   scale_fill_brewer(palette = "RdBu") +
   facet_wrap(~ "Facets Classroom Management", nrow = 1)+
   theme_cowplot()
+
+mean_plot

### 2021-11-10 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_ET_reli_01_01_AOI-based_data.R
cohen kappa time to first reaction

@@ -26,10 +26,10 @@ coding_data_r1_v1 <-read_tsv ("./data/01_01_AP_ProVisioNET_study_glasses_Metrics
                            locale = locale(decimal_mark = ","))
 
 # filter only rows lesson
-v1_r1 <- coding_data_r1 %>% filter(TOI == "Lesson")
+r1_v1 <- coding_data_r1_v1 %>% filter(TOI == "Lesson")
 
 # select relevant variables 
-v1_r1 <- r1 %>% select(EventIndex, AOI)
+r1_v1 <- r1_v1 %>% select(EventIndex, AOI)
 
 ################## RATER 2 ################
 
@@ -49,12 +49,12 @@ r2_v1$AOI[r2_v1$AOI == "Material_Teacher"] <- "Material"
 
 ###### filter identical row number
 
-r1_v1 <- r1_v1 %>% filter(EventIndex != 1728,
+v1_r1 <- v1_r1 %>% filter(EventIndex != 1728,
                     EventIndex != 1729,
                     EventIndex != 1730,
                     EventIndex != 1731)
 
-r1_v1
+v1_r1
 
 
 # merge two data frames --> adding Columns, don't forget to merge BY AOI !

### 2021-11-10 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_reli_01_01_TOI-based_data_first_reaction.R

@@ -14,8 +14,6 @@ needs(tidyverse,
 # if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
 options(dplyr.summarise.inform = FALSE)
 
-r_refs("r-references.bib")
-
 
 # read in data
 reaction_AP <- read_tsv(file = "data/01_01_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv"
@@ -85,9 +83,11 @@ reaction_AP <- reaction_AP %>%
   ungroup() %>%
   select(TOI, Time_to_first_Reaction)
 
-# replace 0 with NA
-# for AP
-reaction_AP$Time_to_first_Reaction[reaction_AP$Time_to_first_Reaction == 0] <- NA
+
+# # replace 0 with NA
+# # for AP
+# reaction_AP$Time_to_first_Reaction[reaction_AP$Time_to_first_Reaction == 0] <- NA
+
 
 # do it again for MK
 reaction_MK <- reaction_MK %>%
@@ -97,23 +97,58 @@ reaction_MK <- reaction_MK %>%
   ungroup() %>%
   select(TOI, Time_to_first_Reaction)
 
-# replace 0 with NA
-# for MK
-reaction_MK$Time_to_first_Reaction[reaction_MK$Time_to_first_Reaction == 0] <- NA
+# # replace 0 with NA
+# # for MK
+# reaction_MK$Time_to_first_Reaction[reaction_MK$Time_to_first_Reaction == 0] <- NA
 
 # combine the two rater data frames
 reaction_complete <- left_join(x = reaction_AP, 
                                y = reaction_MK,
                                by = "TOI")
 
-# ICC
-cor.test(x = reaction_complete$Time_to_first_Reaction.x,
-         y = reaction_complete$Time_to_first_Reaction.y,
-         method = "pearson")
+# changing milliseconds into seconds
+reaction_complete$Time_to_first_Reaction.x <- round(reaction_complete$Time_to_first_Reaction.x/1000,
+                                               digits = 2)
 
-ICC(x = select(reaction_complete,
-               Time_to_first_Reaction.x,
-               Time_to_first_Reaction.y
-)
-)
+reaction_complete$Time_to_first_Reaction.y <- round(reaction_complete$Time_to_first_Reaction.y/1000,
+                                                    digits = 2)
+
+
+
+#################### Percentage Agreement ##############################
+
+# create a new df with only the ratings 
[…]

### 2021-11-15 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_reli_reactions_JH_FP.R
update R script expertise reaction

@@ -1,0 +1,69 @@
+### ProVisioNET pilot data 
+#### intercoder reli expertise data 02_02
+
+
+# install needed packages
+library(needs)
+needs(tidyverse,
+      psych,
+      moments,
+      sjPlot,
+      irr,
+      readxl)
+
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
+
+
+################## RATER 1 ################
+
+# read in data from rater1 while specifying locale allows to set "," 
+r1 <-read_excel ("./data/coding_expertise_reaction_FP.xlsx")
+
+
+################## RATER 2 ################
+
+# read in data from rater1 while specifying locale allows to set "," 
+r2 <-read_excel ("./data/coding_expertise_reaction_JH.xlsx")
+
+
+################## DATA WRANGLING video 01 ################
+
+# filter relevant rows and select relevant columns 
+r1 <- r1 %>% filter(`VP ID` == "02")
+
+r2 <- r2 %>% filter(`VP ID` == "02")
+
+
+# reshape data frame in long format 
+r1_long <- r1 %>% 
+  pivot_longer(!`VP ID`, names_to = "Event", values_to = "Value")
+
+r2_long <- r2 %>% 
+  pivot_longer(!`VP ID`, names_to = "Event", values_to = "Value")
+
+r1_long$Value <- as.numeric(r1_long$Value)
+
+r2_long$Value <- as.numeric(r2_long$Value)
+
+
+# merge two data frames vertically
+r3 <- bind_cols(r1_long$Value, r2_long$Value) %>%
+  rename(rating1 = ...1, 
+         rating2 = ...2)
+
+#################### Percentage Agreement ##############################
+agree(r3)
+
+#################### CohenKappa ##############################
+psych::cohen.kappa(x = as.matrix(r3))
+
+
+
+
+
+
+
+

### 2021-11-15 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_reli_01_01_TOI-based_data_first_reaction.R

@@ -123,72 +123,83 @@ reaction_ratings <- reaction_complete %>% select(Time_to_first_Reaction.x, Time_
 # function agree() with a tolerance of 2 seconds
 ## reference for tolerance: TIMSS video study tolerance of 10 to 30 seconds 
 ### Seidel, 2003, p. 105 
-agree(reaction_ratings, 2)
-
-#################### CohenKappa ##############################
-
-# data preparation
-
-#calculate difference between columns row wise Time_to_first_Reaction.x and Time_to_first_Reaction.y
-# first, create two new data frames
-df1 <- subset.data.frame(reaction_ratings, select = c(Time_to_first_Reaction.x))
-df2 <- subset.data.frame(reaction_ratings, select = c(Time_to_first_Reaction.y))
-
-# add the difference as a new column
-reaction_ratings$diff <- df1 - df2
-
-# creating only absolute values with abs()
-reaction_ratings$diff <- abs(reaction_ratings$diff) 
-
-# if rating difference > 2 seconds --> 0
-reaction_ratings$diff = ifelse(reaction_ratings$"diff"<2, "1","0")
-reaction_ratings$diff <- as.numeric(reaction_ratings$diff)
-
-# add a new column with values --> 0 / 1 
-reaction_ratings$r2 = ifelse(reaction_ratings$"diff">2, "0","1")
+agree(reaction_ratings, tolerance = 2)
 
 
-### GREGOR
-# load packages
-if (!require(irr)) install.packages('irr'); library(irr) # cohens kappa
-if (!require(irrCAC)) install.packages('irrCAC'); library(irrCAC) # cohens kappa
-
-# calculating Cohen.Kappa
-psych::cohen.kappa(x = as.matrix(reaction_ratings_kappa))
-reaction_ratings_kappa <- select(reaction_ratings, diff, r2)
-reaction_ratings_kappa
-reli.reaction_ratings.res <- kappa2(reaction_ratings_kappa, "unweighted")
-reli.reaction_ratings.res
-
-###################################################################
+#################### Intercoder Correlation ##############################
+ICC(x = reaction_complete %>%
+      select(!TOI) %>%
+      as.matrix())
 
 
-# create percent agreement for validity
-reli.reaction_ratings.data <- reli.reaction_ratings.data  %>%
-  mutate(countagreement = if_else(diff == r2, 1, 0) )
-
-
-# create percent agreement for validity
[…]

### 2021-11-16 01_studies/01_Laborstudie ProVisioNET/R script/reli/ProVisioNet_ET_TOI_AOI-based_data.nb.Rmd
Coding data metrics + SRI + SJT

---
title: "AOI and TOI based analyses ProVisioNet"
output: html_notebook
---

# Install Packages

```{r}
library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl,
      gridExtra)
```

# Read In Data sets

```{r, include = FALSE}
AOI_AP_01 <- read_tsv(file = "data/01_01_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv"
                   )

AOI_MK_01 <- read_tsv(file = "data/01_01_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv"
                  )

AOI_AP_04 <- read_tsv(file = "data/04_04_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

AOI_MK_04 <- read_tsv(file = "data/04_04_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

```

# AOI based analyses 
# Data Wrangling - Total Duration and Proportional Duration of looking at AOIs

```{r, include = TRUE, cache = TRUE, echo=TRUE}

# select relevant columns
AOI_AP_01 <- AOI_AP_01 %>% 
  select(TOI,
         starts_with("Total_duration_of_fixation"))

AOI_MK_01 <- AOI_MK_01 %>% 
  select(TOI,
         starts_with("Total_duration_of_fixation"))

AOI_AP_04 <- AOI_AP_04 %>% 
  select(TOI,
         starts_with("Total_duration_of_fixation"))

AOI_MK_04 <- AOI_MK_04 %>% 
  select(TOI,
         starts_with("Total_duration_of_fixation"))

# filter only for TOIs
AOI_AP_01 <- AOI_AP_01 %>% 
  filter(  TOI == "Chatting_with_neighbour" |
           TOI == "Clicking_pen" |
           TOI == "Drawing" | 
           TOI == "Drumming_with_hands" |
           TOI == "Head_on_table" |
           TOI == "Looking_at_phone" |
           TOI == "Heckling"| 
           TOI == "Lesson" | 
           TOI == "Snipping_with_fingers" |
           TOI == "Whispering" |
          TOI == "Entire Recording")

AOI_MK_01 <- AOI_MK_01 %>% 
  filter(  TOI == "Chatting_with_neighbour" |
           TOI == "Clicking_pen" |
           TOI == "Drawing" | 
           TOI == "Drumming_with_hands" |
           TOI == "Head_on_table" |
           TOI == "Looking_at_phone" |
           TOI == "Heckling"| 
           TOI == "Lesson" | 
           TOI == "Snipping_with_fingers" |
           TOI == "Whispering" |
          TOI == "Entire Recording")

AOI_AP_04 <- AOI_AP_04 %>% 
  filter(  TOI == "Chatting_with_neighbour" |
           TOI == "Clicking_pen" |
           TOI == "Drawing" | 
           TOI == "Drumming_with_hands" |
           TOI == "Head_on_table" |
           TOI == "Looking_at_phone" |
           TOI == "Heckling"| 
           TOI == "Lesson" | 
           TOI == "Snipping_with_fingers" |
           TOI == "Whispering"|
          TOI == "Entire Recording")

AOI_MK_04 <- AOI_MK_04 %>% 
  filter(  TOI == "Chatting_with_neighbour" |
           TOI == "Clicking_pen" |
           TOI == "Drawing" | 
           TOI == "Drumming_with_hands" |
           TOI == "Head_on_table" |
           TOI == "Looking_at_phone" |
           TOI == "Heckling"| 
           TOI == "Lesson" | 
           TOI == "Snipping_with_fingers" |
           TOI == "Whispering"|
          TOI == "Entire Recording")

# create new column names that give total duration of looking at all AOIs
AOI_AP_01 <- AOI_AP_01  %>% 
  rename (Anna = Total_duration_of_fixations.Anna,
          Bianca = Total_duration_of_fixations.Bianca,
          Carl_a = `Total_duration_of_fixations.Carl(a)`,
          Disruptive_Person = Total_duration_of_fixations.Disruptive_Person,
          Board_Screen = Total_duration_of_fixations.Board_Screen,
          Classroom_Others = Total_duration_of_fixations.Classroom_Others,
          Material = Total_duration_of_fixations.Material,
          Nametag_Anna = Total_duration_of_fixations.Nametag_Anna,
          Nametag_Bianca = Total_duration_of_fixations.Nametag_Bianca,
          Nametage_Carl_a = `Total_duration_of_fixations.Nametag_Carl(a)`)

AOI_MK_01 <- AOI_MK_01  %>% 
  rename (Anna = Total_duration_of_fixations.Anna,
          Bianca = Total_duration_of_fixations.Bianca,
          Carl_a = `Total_duration_of_fixations.Carl(a)`,
          Disruptive_Person = Total_duration_of_fixations.Disruptive_Person,
          Board_Screen = Total_duration_of_fixations.Board_Screen,
          Classroom_Others = Total_duration_of_fixations.Classroom_Others,
          Teacher_Material = Total_duration_of_fixations.Material_Teacher,
          Students_Material = Total_duration_of_fixations.Material_Students,
          Nametag_Anna = Total_duration_of_fixations.Nametag_Anna,
          Nametag_Bianca = Total_duration_of_fixations.Nametag_Bianca,
          Nametage_Carl_a = `Total_duration_of_fixations.Nametag_Carl(a)`)

AOI_AP_04 <- AOI_AP_04  %>% 
  rename (Anna = Total_duration_of_fixations.Anna,
          Bianca = Total_duration_of_fixations.Bianca,
          Carl_a = `Total_duration_of_fixations.Carl(a)`,
          Disruptive_Person = Total_duration_of_fixations.Disruptive_Person,
          Board_Screen = Total_duration_of_fixations.Board_Screen,
          Classroom_Others = Total_duration_of_fixations.Classroom_Others,
          Material = Total_duration_of_fixations.Material,
          Nametag_Anna = Total_duration_of_fixations.Nametag_Anna,
          Nametag_Bianca = Total_duration_of_fixations.Nametag_Bianca,
          Nametage_Carl_a = `Total_duration_of_fixations.Nametag_Carl(a)`)

AOI_MK_04 <- AOI_MK_04  %>% 
  rename (Anna = Total_duration_of_fixations.Anna,
          Bianca = Total_duration_of_fixations.Bianca,
          Carl_a = `Total_duration_of_fixations.Carl(a)`,
          Disruptive_Person = Total_duration_of_fixations.Disruptive_Person,
          Board_Screen = Total_duration_of_fixations.Board_Screen,
          Classroom_Others = Total_duration_of_fixations.Classroom_Others,
          Students_Material = Total_duration_of_fixations.Students_material,
          Teacher_Material = Total_duration_of_fixations.Teacher_material,
          Nametag_Anna = Total_duration_of_fixations.Nametag_Anna,
          Nametag_Bianca = Total_duration_of_fixations.Nametag_Bianca,
          Nametage_Carl_a = `Total_duration_of_fixations.Nametag_Carl(a)`)

# replace NAs with 0
AOI_AP_01 <- AOI_AP_01 %>%
  mutate_all(~replace(., is.na(.), 0))

AOI_AP_04 <- AOI_AP_04 %>%
  mutate_all(~replace(., is.na(.), 0))

AOI_MK_01 <- AOI_MK_01 %>%
  mutate_all(~replace(., is.na(.), 0))

AOI_MK_04 <- AOI_MK_04 %>%
  mutate_all(~replace(., is.na(.), 0))

# create data set of total durations in long format for plotting --> for later
AOI_AP_01_long <- gather(AOI_AP_01, TOI, Duration)

AOI_MK_01_long <- gather(AOI_MK_01, TOI, Duration)

AOI_AP_04_long <- gather(AOI_AP_04, TOI, Duration)

AOI_MK_04_long <- gather(AOI_MK_04, TOI, Duration)

# create a new column with name sum_aois that gives the sum of looking at all AOIs
AOI_AP_01 <- AOI_AP_01  %>% mutate(Sum_AOI = Anna + 
                                              Bianca +
                                              Carl_a + 
                                              Disruptive_Person + 
                                              Board_Screen + 
                                              Classroom_Others + 
                                              Material + 
                                              Nametag_Anna +
                                              Nametag_Bianca + 
                                              Nametage_Carl_a)

AOI_MK_01 <- AOI_MK_01  %>% mutate(Sum_AOI = Anna + 
                                              Bianca +
                                              Carl_a + 
                                              Disruptive_Person + 
                                              Board_Screen + 
                                              Classroom_Others + 
                                              Teacher_Material +
                                              Students_Material + 
                                              Nametag_Anna +
                                              Nametag_Bianca + 
                                              Nametage_Carl_a)

AOI_AP_04 <- AOI_AP_04  %>% mutate(Sum_AOI = Anna + 
                                              Bianca +
                                              Carl_a + 
                                              Disruptive_Person + 
                                              Board_Screen + 
                                              Classroom_Others + 
                                              Material + 
                                              Nametag_Anna +
                                              Nametag_Bianca + 
                                              Nametage_Carl_a)

AOI_MK_04 <- AOI_MK_04  %>% mutate(Sum_AOI = Anna + 
                                              Bianca +
                                              Carl_a + 
                                              Disruptive_Person + 
                                              Board_Screen + 
                                              Classroom_Others + 
                                              Teacher_Material +
                                              Students_Material + 
                                              Nametag_Anna +
                                              Nametag_Bianca + 
                                              Nametage_Carl_a)

# create new columns that give proportion of the duration of looking at all AOIs
# the proportion is the relative duration divided by total duration 
prop_AP_01 <- AOI_AP_01  %>% 
  mutate(Anna = Anna/Sum_AOI)   %>% 
  mutate(Bianca = Bianca/Sum_AOI)   %>% 
  mutate (Carl_a = Carl_a/Sum_AOI) %>%
  mutate(Disruptive_Person = Disruptive_Person/Sum_AOI)   %>% 
  mutate(Board_Screen = Board_Screen/Sum_AOI) %>%
  mutate(Classroom_Others = Classroom_Others/Sum_AOI) %>%
  mutate (Material = Material/Sum_AOI) %>%
  mutate (Nametag_Anna = Nametag_Anna/Sum_AOI) %>%
  mutate (Nametag_Bianca = Nametag_Bianca/Sum_AOI) %>%
  mutate (Nametage_Carl_a = Nametage_Carl_a/Sum_AOI)

# chose all columns exept the last one (Sum_AOI)
prop_AP_01 <- prop_AP_01 %>% filter(TOI == "Lesson") %>%
                              select(,1:11)

prop_MK_01 <- AOI_MK_01  %>% 
  mutate(Anna = Anna/Sum_AOI)   %>% 
  mutate(Bianca = Bianca/Sum_AOI)   %>% 
  mutate (Carl_a = Carl_a/Sum_AOI) %>%
  mutate(Disruptive_Person = Disruptive_Person/Sum_AOI)   %>% 
  mutate(Board_Screen = Board_Screen/Sum_AOI) %>%
  mutate(Classroom_Others = Classroom_Others/Sum_AOI) %>%
  mutate (Teacher_Material = Teacher_Material/Sum_AOI) %>%
  mutate (Nametag_Anna = Nametag_Anna/Sum_AOI) %>%
  mutate (Nametag_Bianca = Nametag_Bianca/Sum_AOI) %>%
  mutate (Nametage_Carl_a = Nametage_Carl_a/Sum_AOI) %>%
  rename(Material = Teacher_Material)

prop_MK_01 <- prop_MK_01 %>% filter(TOI == "Lesson") %>%
                              select(!"Students_Material")

prop_AP_04 <- AOI_AP_04  %>% 
  mutate(Anna = Anna/Sum_AOI)   %>% 
  mutate(Bianca = Bianca/Sum_AOI)   %>% 
  mutate (Carl_a = Carl_a/Sum_AOI) %>%
  mutate(Disruptive_Person = Disruptive_Person/Sum_AOI)   %>% 
  mutate(Board_Screen = Board_Screen/Sum_AOI) %>%
  mutate(Classroom_Others = Classroom_Others/Sum_AOI) %>%
  mutate (Material = Material/Sum_AOI) %>%
  mutate (Nametag_Anna = Nametag_Anna/Sum_AOI) %>%
  mutate (Nametag_Bianca = Nametag_Bianca/Sum_AOI) %>%
  mutate (Nametage_Carl_a = Nametage_Carl_a/Sum_AOI)

prop_AP_04 <- prop_AP_04 %>% filter(TOI == "Lesson") %>%
                              select(,1:11)

prop_MK_04 <- AOI_MK_04  %>% 
  mutate(Anna = Anna/Sum_AOI)   %>% 
  mutate(Bianca = Bianca/Sum_AOI)   %>% 
  mutate (Carl_a = Carl_a/Sum_AOI) %>%
  mutate(Disruptive_Person = Disruptive_Person/Sum_AOI)   %>% 
  mutate(Board_Screen = Board_Screen/Sum_AOI) %>%
  mutate(Classroom_Others = Classroom_Others/Sum_AOI) %>%
  mutate (Teacher_Material = Teacher_Material/Sum_AOI) %>%
  mutate(Students_Material = Students_Material/Sum_AOI) %>%
  mutate (Nametag_Anna = Nametag_Anna/Sum_AOI) %>%
  mutate (Nametag_Bianca = Nametag_Bianca/Sum_AOI) %>%
  mutate (Nametage_Carl_a = Nametage_Carl_a/Sum_AOI) %>%
  mutate (Material = Students_Material + Teacher_Material)

prop_MK_04 <- prop_MK_04 %>% filter(TOI == "Lesson") %>%
                              select(!"Students_Material") %>%
                              select(!"Teacher_Material") %>%
                              select (!"Sum_AOI")

# create data set of proportions in long format for plotting
prop_AP_01_long  <- prop_AP_01 %>% gather(TOI, Duration)

prop_MK_01_long <- prop_MK_01 %>% gather (TOI, Duration)

prop_AP_04_long <- prop_AP_04 %>% gather (TOI, Duration)

prop_MK_04_long <- prop_MK_04 %>% gather (TOI, Duration)

################################################

```

### Ploting data - Total Duration and Proportional Data of Video 01 and 04, coded by AP and MK

```{r echo = TRUE, include=TRUE}
total_AP_01 <- AOI_AP_01_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() +
            geom_jitter(color="black", size=0.4, alpha=0.9) +
            geom_point() + ylim (0,1000) + 
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Total Duration of Looking at AOIs in ms - Video 01 Rater AP") +
             xlab("AOI")

total_AP_01

total_MK_01 <- AOI_MK_01_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() +
            geom_jitter(color="black", size=0.4, alpha=0.9) +
            geom_point() + ylim (0,1000) + 
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Total Duration of Looking at AOIs in ms - Video 01 Rater MK") +
             xlab("AOI")

total_MK_01

### Plot data TOTAL DURATION video 04
total_AP_04 <- AOI_AP_04_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() +
            geom_jitter(color="black", size=0.4, alpha=0.9) +
            geom_point() + ylim (0,1000) + 
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Total Duration of Looking at AOIs in ms - Video 04 Rater AP") +
             xlab("AOI")

total_AP_04

total_MK_04 <- AOI_MK_04_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() +
            geom_jitter(color="black", size=0.4, alpha=0.9) +
            geom_point() + ylim (0,1000) + 
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Total Duration of Looking at AOIs in ms - Video 04 Rater MK") +
             xlab("AOI")

total_MK_04

### Plot data PROPORTIONAL DURATION video 01
prop_AP_01 <- prop_AP_01_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() +
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Proportional Duration of Looking at AOIs - Video 01 Rater AP") +
             xlab("AOI")

prop_AP_01

prop_MK_01 <- prop_MK_01_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() + 
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Proportional Duration of Looking at AOIs in ms") +
             xlab("AOI")

prop_MK_01

### Plot data PROPORTIONAL DURATION video 04
prop_AP_04 <- prop_AP_04_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() +
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Proportional Duration of Looking at AOIs - Video 04 Rater AP") +
             xlab("AOI")

prop_AP_04

prop_MK_04 <- prop_MK_04_long %>%
            ggplot( aes(x=TOI, y=Duration, fill=TOI)) +
            geom_boxplot() + 
          theme(
            axis.text.x = element_text(angle=80, hjust=1),
            legend.position="none",
            plot.title = element_text(size=11)) +
          ggtitle("Proportional Duration of Looking at AOIs - Video 04 Rater MK") +
             xlab("AOI")

prop_MK_04

```

# Reliabilty for Hits in AOIs
# Read in Data Sets
```{r, include=TRUE}
AOI_hit_AP_01 <- read_tsv(file = "data/01_01_AP_ProVisioNET_study_glasses_Metrics_Event-based.tsv"
                   )

AOI_hit_MK_01 <- read_tsv(file = "data/01_01_MK_ProVisioNET_study_glasses_Metrics_Event-based.tsv"
                  )

AOI_hit_AP_04 <- read_tsv(file = "data/04_04_AP_ProVisioNET_study_glasses Metrics_event-based.tsv")

AOI_hit_MK_04 <- read_tsv(file = "data/04_04_MK_ProVisioNET_study_glasses Metrics_event-based.tsv")
```

# Data Wrangling
```{r echo=FALSE, include=TRUE}
# filter only rows lesson
AOI_hit_AP_01 <- AOI_hit_AP_01 %>% filter(TOI == "Lesson")

AOI_hit_MK_01 <- AOI_hit_MK_01 %>% filter(TOI == "Lesson")

AOI_hit_AP_04 <- AOI_hit_AP_04 %>% filter(TOI == "Lesson")

AOI_hit_MK_04 <- AOI_hit_MK_04 %>% filter(TOI == "Lesson")

# select variable AOI + Hit_proportion
AOI_hit_AP_01 <- AOI_hit_AP_01 %>% select(AOI, Hit_proportion)

AOI_hit_MK_01 <- AOI_hit_MK_01 %>% select(AOI, Hit_proportion)

AOI_hit_AP_04 <- AOI_hit_AP_04 %>% select(AOI, Hit_proportion)

AOI_hit_MK_04 <- AOI_hit_MK_04 %>% select(AOI, Hit_proportion)

# changing character to numeric
AOI_hit_AP_01$Hit_proportion <- as.numeric(AOI_hit_AP_01$Hit_proportion)

AOI_hit_MK_01$Hit_proportion <- as.numeric(AOI_hit_MK_01$Hit_proportion)

AOI_hit_AP_04$Hit_proportion <- as.numeric(AOI_hit_AP_04$Hit_proportion)

AOI_hit_MK_04$Hit_proportion <- as.numeric(AOI_hit_MK_04$Hit_proportion)

# round Hit_proportion to 1
AOI_hit_AP_01$Hit_proportion <- round(AOI_hit_AP_01$Hit_proportion, digits = 0)

AOI_hit_MK_01$Hit_proportion <- round(AOI_hit_MK_01$Hit_proportion, digits = 0)

AOI_hit_AP_04$Hit_proportion <- round(AOI_hit_AP_04$Hit_proportion, digits = 0)

AOI_hit_MK_04$Hit_proportion <- round(AOI_hit_MK_04$Hit_proportion, digits = 0)

#delete NAs
AOI_hit_AP_01 <- na.omit(AOI_hit_AP_01)

AOI_hit_MK_01 <- na.omit(AOI_hit_MK_01)

AOI_hit_AP_04 <- na.omit(AOI_hit_AP_04)

AOI_hit_MK_04 <- na.omit(AOI_hit_MK_04)

# group data by AOI and summarise Hit_prop
Hit_AP_01_aggr <- group_by(.data = AOI_hit_AP_01,
                    AOI) %>% summarise(Hit_count = length(Hit_proportion))

Hit_MK_01_aggr <- group_by(.data = AOI_hit_MK_01,
                    AOI) %>% summarise(Hit_count = length(Hit_proportion))

Hit_AP_04_aggr <- group_by(.data = AOI_hit_AP_04,
                    AOI) %>% summarise(Hit_count = length(Hit_proportion))

Hit_MK_04_aggr <- group_by(.data = AOI_hit_MK_04,
                    AOI) %>% summarise(Hit_count = length(Hit_proportion))

###### filter only for identical rows for both rater

AP_01_filter <- Hit_AP_01_aggr %>% filter(
                    AOI != "Nametag_Anna",
                    AOI != "Nametag_Bianca",
                    AOI != "Nametag_Carl(a)")

AP_01_filter

MK_01_filter <- Hit_MK_01_aggr %>% filter( 
                    AOI != "Bianca,Classroom_Others")

MK_01_filter$AOI[MK_01_filter$AOI == "Material_Teacher"] <- "Material"

MK_01_filter

# merge two data frames --> adding Columns, don't forget to merge BY AOI !

r3 <- merge(AP_01_filter, MK_01_filter, by = 'AOI')

# create a new df with only the ratings 
r3_agree <- r3 %>% select(Hit_count.x, Hit_count.y)

# function agree() with a tolerance
agree(r3_agree, tolerance=50)

#################### CohenKappa ##############################

# first, create a xtab and specify who is rater1 and rater2
ratertab <- xtabs(~r3$Hit_count.x + r3$Hit_count.y)
ratertab

# now you can calculate CohenKappa
CohenKappa(ratertab)

#################### ICC ##############################

# build a subset that contains the two AOI hit variables  
data_icc <- subset(r3, select = c(Hit_count.x, Hit_count.y))

# calculate the ICC for two raters with new subset
ICC(data_icc)

```

# TOI based analyses 
# Data Wrangling - TOIs classified by disruptions

```{r, echo=TRUE, include=TRUE}

df_AP_01 <- df_AP_01 %>% 
  select(TOI, Duration_of_interval)

df_MK_01 <- df_MK_01 %>% 
  select(TOI, Duration_of_interval)

df_AP_04 <- df_AP_04 %>% 
  select(TOI, Duration_of_interval)

df_MK_04 <- df_MK_04 %>% 
  select(TOI, Duration_of_interval)

# Duration

df_cappa_dur <- matrix(ncol = 3,
                       nrow = 11)

colnames(df_cappa_dur) <- c("TOI","Duration_of_interval_AP_01","Duration_of_interval_MK_01")

df_cappa_dur <- as_tibble(df_cappa_dur)

TOI_names <- c("Calibration_phase",
               "Chatting_with_neighbour",
               "Clicking_pen",
               "Drawing",
               "Drumming_with_hands",
               "Head_on_table",
               "Looking_at_phone",
               "Heckling","Lesson",
               "Snipping_with_fingers",
               "Whispering")

df_cappa_dur$TOI <- TOI_names

# AP_01 Duration TOI
for (i in TOI_names) {

  val <- df_AP_01$Duration_of_interval[df_AP_01 == i]

  df_cappa_dur$Duration_of_interval_AP_01[df_cappa_dur$TOI == i] <- val
}

# MK_01 Duration TOI
for (i in TOI_names) {

  val <- df_MK_01$Duration_of_interval[df_MK_01 == i]

  df_cappa_dur$Duration_of_interval_MK_01[df_cappa_dur$TOI == i] <- val
}

# AP_04 Duration TOI
for (i in TOI_names) {

  val <- df_AP_04$Duration_of_interval[df_AP_04 == i]

  df_cappa_dur$Duration_of_interval_AP_04[df_cappa_dur$TOI == i] <- val
}

# MK_04 Duration TOI
for (i in TOI_names) {

  val <- df_MK_04$Duration_of_interval[df_MK_04 == i]

  df_cappa_dur$Duration_of_interval_MK_04[df_cappa_dur$TOI == i] <- val
}

```

# Creating TOI classes
```{r, include=TRUE}
df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Calibration_phase"] <- "Calibration_phase"

df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Chatting_with_neighbour" |
                         df_cappa_dur$TOI == "Heckling" |
                         df_cappa_dur$TOI == "Whispering"] <- "Verbal_disruption"

df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Head_on_table" |
                         df_cappa_dur$TOI == "Looking_at_phone" |
                         df_cappa_dur$TOI == "Drawing"] <- "Lack_of_eagerness"

df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Lesson"] <- "Lesson"

df_cappa_dur$TOI_class[is.na(df_cappa_dur$TOI_class)] <- "Agitation"

df_cappa_dur$TOI_class <- as_factor(df_cappa_dur$TOI_class)

df_cappa_dur_aggr <- df_cappa_dur %>%
  group_by(TOI_class) %>%
  summarise(Duration_mean_AP_01 = mean(Duration_of_interval_AP_01),
            Duration_mean_MK_01 = mean(Duration_of_interval_MK_01),
            Duration_mean_AP_04 = mean(Duration_of_interval_AP_04),
            Duration_mean_MK_04 = mean(Duration_of_interval_MK_04)
            )

```

#
```{r}
fun_1 <- function(x) {
    y <- x
    return(y)
  }
```

# TOI Reliability
# Start and Duration

# Data Wrangling

```{r, include=TRUE}
df_AP <- df_AP %>% 
  select(TOI, Duration_of_interval, Start_of_interval)

df_MK <- df_MK %>% 
  select(TOI, Duration_of_interval, Start_of_interval)

# Start

df_cappa_start <- matrix(ncol = 3,
                         nrow = 8)

colnames(df_cappa_start) <- c("TOI","Start_of_interval_EH","Start_of_interval_RD")

df_cappa_start <- as_tibble(df_cappa_start)

TOI_names <- c("Calibration_phase","Clicking_pen","Drumming_with_hands",
               "Head_on_table","Heckling","Lesson","Snipping_with_fingers",
               "Whispering")

df_cappa_start$TOI <- TOI_names

# AP Start TOI
for (i in TOI_names) {

  val <- df_AP$Start_of_interval[df_AP == i]

  df_cappa_start$Start_of_interval_AP[df_cappa_start$TOI == i] <- val
}

# MK Start TOI
for (i in TOI_names) {

  val <- df_MK$Start_of_interval[df_MK == i]

  df_cappa_start$Start_of_interval_MK[df_cappa_start$TOI == i] <- val
}

# Duration

df_cappa_dur <- matrix(ncol = 3,
                       nrow = 8)

colnames(df_cappa_dur) <- c("TOI","Duration_of_interval_EH","Duration_of_interval_RD")

df_cappa_dur <- as_tibble(df_cappa_dur)

TOI_names <- c("Calibration_phase","Clicking_pen","Drumming_with_hands",
               "Head_on_table","Heckling","Lesson","Snipping_with_fingers",
               "Whispering")

df_cappa_dur$TOI <- TOI_names

# AP Duration TOI
for (i in TOI_names) {

  val <- df_AP$Duration_of_interval[df_AP == i]

  df_cappa_dur$Duration_of_interval_AP[df_cappa_dur$TOI == i] <- val
}

# MK Duration TOI
for (i in TOI_names) {

  val <- df_MK$Duration_of_interval[df_MK == i]

  df_cappa_dur$Duration_of_interval_MK[df_cappa_dur$TOI == i] <- val
}

# In seconds

df_cappa_dur$Duration_of_interval_AP <- round(df_cappa_dur$Duration_of_interval_AP/1000,
                                              digits = 2
                                              )

df_cappa_dur$Duration_of_interval_MK <- round(df_cappa_dur$Duration_of_interval_MK/1000,
                                              digits = 2
                                              )

df_cappa_start$Start_of_interval_AP <- round(df_cappa_start$Start_of_interval_AP/1000,
                                              digits = 2
                                              )

df_cappa_start$Start_of_interval_MK <- round(df_cappa_start$Start_of_interval_MK/1000,
                                              digits = 2
                                             )
```

```{r, include=FALSE}
fun_1 <- function(x) {
    y <- x
    return(y)
  }
```

# Reliabiltät

## Plotting Duration

```{r, echo=TRUE}
cor.test(x = df_cappa_dur$Duration_of_interval_AP,
     y = df_cappa_dur$Duration_of_interval_MK,
          method = "pearson")

ICC(x = select(df_cappa_dur,
               Duration_of_interval_AP,
               Duration_of_interval_MK
               )
    )

# Lesson is significant longer and gives a biased view on the points.

ggplot(data = filter(df_cappa_dur,
                     TOI != "Lesson"),
       mapping = aes(x = Duration_of_interval_AP,
                     y = Duration_of_interval_MK
                     )
       ) +
  geom_point(size = 2) +
  geom_text(mapping = aes(label = TOI)
            ) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Duration coded by AP",
       y = "Duration coded by MK",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```

### 2021-11-16 01_studies/01_Laborstudie ProVisioNET/R script/reli/ProVisioNet_ET_reli_01_01_TOI-based_data.Rmd
Coding data metrics + SRI + SJT

--- 2021-09-07 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_reli_01_01_TOI-based_data.Rmd
@@
 ```{r}
-if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
-if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
-if (!require(papaja)) install.packages("papaja"); library(papaja)
-if (!require(psych)) install.packages('psych'); library(psych) # stats
-if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
-if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
-if (!require(DescTools)) install.packages('DescTools'); library(DescTools) # cohens kappa
-if (!require(irr)) install.packages('irr'); library(irr) # Various Coefficients of Interrater Reliability and Agreement
-if (!require(readxl)) install.packages('readxl'); library(readxl) # read in excel files
-
+library(needs)
+needs(tidyverse,
+      psych,
+      moments,
+      sjPlot,
+      DescTools,
+      irr,
+      readxl)
 ```
@@
   geom_point(size = 2) +
+  geom_text(mapping = aes(label = TOI)
+            ) +
   geom_abline(intercept = 0,

### 2021-11-16 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R

@@ -1,0 +1,76 @@
+### ProVisioNET SRI Coding Data 
+
+library(needs)
+needs(tidyverse,
+      ggplot,
+      psych,
+      moments,
+      sjPlot,
+      DescTools,
+      irr,
+      readxl)
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
+
+# read in data
+sri_novice <- read_excel("./data/coding_sri_novice.xlsx")
+
+sri_expert <- read_excel("./data/coding_sri_expert.xlsx")
+
+
+# filter relevant rows and select relevant columns 
+sri_novice <- sri_novice %>% select(group, event, disturbing_factor, safety_factor)
+
+sri_expert <- sri_expert %>% select(group, event, disturbing_factor, safety_factor)
+
+
+# combine the two data frames
+sri <- rbind(sri_expert, sri_novice)
+
+# create a new data frame
+sri_disturb <- subset.data.frame(sri, select = c(group, event, disturbing_factor))
+
+sri_safe <- subset.data.frame(sri, select = c(group, event, safety_factor))
+
+# define expert and novice with ifelse function
+sri_disturb$group = ifelse(sri_disturb$group < 200, "Novice","Expert")
+
+sri_safe$group = ifelse(sri_safe$group < 200, "Novice","Expert")
+
+
+# plotting disturbing factor
+dist_plot <- 
+  ggplot(data = sri_disturb,
+         mapping = aes(x = group,
+                       y = "safety_factor")) +
+  geom_boxplot(mapping = aes(fill = group)) +
+  geom_point(size = 2, 
+             alpha = 0.4,
+             position = position_jitter(seed = 1, 
+                                        width = 0.1)) +
+  scale_fill_brewer(palette = "RdBu") +
+  facet_wrap(vars(event), 
+             nrow = 1) +
+  theme_blank()
+
+dist_plot
+
+
+# plotting safety factor
+safe_plot <- 
+  ggplot(data = sri_long,
+         mapping = aes(x = event,
+                       y = "Value")) +
+  geom_boxplot(mapping = aes(fill = group)) +
+  geom_point(size = 2, 
+             alpha = 0.4,
+             position = position_jitter(seed = 1, 
+                                        width = 0.1)) +
+  scale_fill_brewer(palette = "RdBu") +
+  facet_wrap(vars(event), 
+             nrow = 1) +
+  theme_blank()
+
+safe_plot

### 2021-11-16 01_studies/01_Laborstudie ProVisioNET/SJTest/SJTest_script.R

@@ -39,10 +39,14 @@ mean_plot <-
              alpha = 0.4,
              position = position_jitter(seed = 1, 
                                         width = 0.1)) +
+  ylim(0,1) + 
   scale_fill_brewer(palette = "RdBu") +
   facet_wrap(vars(`Facets Classroom Management`), 
-             nrow = 1) +
-  theme_cowplot()
+             nrow = 1, strip.position = "bottom") +
+  ggtitle("Situational Judgment Test of Strategic Knowledge of Classroom Management") +
+  theme(
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank())
 
 mean_plot
 

### 2021-11-17 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R
SRI plot

@@ -8,7 +8,8 @@ needs(tidyverse,
       sjPlot,
       DescTools,
       irr,
-      readxl)
+      readxl, 
+      gridExtra)
 
 # suppress "summarize" info. 
 # if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
@@ -21,56 +22,72 @@ sri_expert <- read_excel("./data/coding_sri_expert.xlsx")
 
 
 # filter relevant rows and select relevant columns 
-sri_novice <- sri_novice %>% select(group, event, disturbing_factor, safety_factor)
+sri_novice <- sri_novice %>% select(Group, Event, Disturbing_Factor, Confident_Factor)
 
-sri_expert <- sri_expert %>% select(group, event, disturbing_factor, safety_factor)
+sri_expert <- sri_expert %>% select(Group, Event, Disturbing_Factor, Confident_Factor)
 
 
-# combine the two data frames
+# combine the two data frames with novice and expert
 sri <- rbind(sri_expert, sri_novice)
 
-# create a new data frame
-sri_disturb <- subset.data.frame(sri, select = c(group, event, disturbing_factor))
 
-sri_safe <- subset.data.frame(sri, select = c(group, event, safety_factor))
+# removing all NAs
+sri_filter <- na.omit(sri)
+
+# # replacing NA with 11
+# sri[is.na(sri)] = 11
+
+# # creating a new column --> event was "seen" / "not seen" 
+# # WARNING! ifelse() needs three parameters: test, truth value, false value 
+# sri$Seen <- ifelse(sri$Disturbing_Factor <= 10, 'seen', ifelse(sri$Disturbing_Factor > 11, 'not seen', 'not seen')) 
+
 
 # define expert and novice with ifelse function
-sri_disturb$group = ifelse(sri_disturb$group < 200, "Novice","Expert")
+sri_filter$Group = ifelse(sri_filter$Group < 200, "Novice","Expert")
 
-sri_safe$group = ifelse(sri_safe$group < 200, "Novice","Expert")
+# create a new data frame with both factors
+sri_disturb <- subset.data.frame(sri_filter, select = c(Group, Event, Disturbing_Factor))
+sri_confi <- subset.data.frame(sri_filter, select = c(Group, Event, Confident_Factor))
 
 
 # plotting disturbing factor
 dist_plot <- 
   ggplot(data = sri_disturb,
-         mapping = aes(x = group,
-                       y = "safety_factor")) +
[…]

### 2021-11-18 01_studies/01_Laborstudie ProVisioNET/R script/et toi/et toi script.R
R script ET TOI

@@ -1,0 +1,63 @@
+### ProVisioNET Eyetracking TOI Coding Data 
+
+library(needs)
+needs(tidyverse,
+      ggplot,
+      psych,
+      moments,
+      sjPlot,
+      DescTools,
+      irr,
+      readxl, 
+      gridExtra)
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
+
+# read in data
+expert_toi <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_experts_intervall.tsv",
+                       locale = locale(decimal_mark = ","))
+novice_toi <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_novice_intervall.tsv",
+                       locale = locale(decimal_mark = ","))
+
+
+# combine two data frames 
+toi <- rbind(expert_toi, novice_toi)
+
+# filter relevant rows
+toi_react <- toi %>% filter(TOI == "Lesson")
+
+
+# select relevant columns
+toi_react <- toi_react %>% 
+  select(Group, TOI,
+         Time_to_first_Event.Reaction_chatting,
+         Time_to_first_Event.Reaction_clicking,
+         Time_to_first_Event.Reaction_drawing,
+         Time_to_first_Event.Reaction_drumming,
+         Time_to_first_Event.Reaction_head,
+         Time_to_first_Event.Reaction_heckling,
+         Time_to_first_Event.Reaction_phone,
+         Time_to_first_Event.Reaction_snipping,
+         Time_to_first_Event.Reaction_whispering)
+
+# changing from wide to long format
+toi_react <- df_sjt %>% 
+  pivot_longer(!Group, names_to = "Facets Classroom Management", values_to = "Mean")
+
+
+# changing milliseconds into seconds
+toi_react <- round(toi_react$Time_to_first_Event.Reaction_chatting/1000,
+                   toi_react$Time_to_first_Event.Reaction_clicking/1000,
+                   toi_react$Time_to_first_Event.Reaction_drawing/1000,
+                   toi_react$Time_to_first_Event.Reaction_drumming/1000,
+                   toi_react$Time_to_first_Event.Reaction_head/1000,
+                   toi_react$Time_to_first_Event.Reaction_heckling/1000,
+                   toi_react$Time_to_first_Event.Reaction_chatting/1000,
+                                                    digits = 2)         
+         
+         
+         
+         
+         

### 2021-11-18 01_studies/01_Laborstudie ProVisioNET/R script/et toi/et toi script.R
ET TOI

@@ -25,11 +25,12 @@ novice_toi <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_novice_i
 # combine two data frames 
 toi <- rbind(expert_toi, novice_toi)
 
-# filter relevant rows
-toi_react <- toi %>% filter(TOI == "Lesson")
+# filter relevant rows only for time to first reaction
+toi_react <- toi %>% filter(TOI == "Lesson" |
+                            TOI == "Whispering")
 
 
-# select relevant columns
+# select relevant columns only for time to first event
 toi_react <- toi_react %>% 
   select(Group, TOI,
          Time_to_first_Event.Reaction_chatting,
@@ -43,8 +44,8 @@ toi_react <- toi_react %>%
          Time_to_first_Event.Reaction_whispering)
 
 # changing from wide to long format
-toi_react <- df_sjt %>% 
-  pivot_longer(!Group, names_to = "Facets Classroom Management", values_to = "Mean")
+toi_react <- toi_react %>% 
+  pivot_longer(!Group, names_to = "Events", values_to = "Time")
 
 
 # changing milliseconds into seconds

### 2021-11-21 01_studies/01_Laborstudie ProVisioNET/R script/et toi/et toi script.R
R script ET toi time to first fixation

@@ -16,9 +16,9 @@ needs(tidyverse,
 options(dplyr.summarise.inform = FALSE)
 
 # read in data
-expert_toi <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_experts_intervall.tsv",
+expert_toi <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_experts_interval.tsv",
                        locale = locale(decimal_mark = ","))
-novice_toi <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_novice_intervall.tsv",
+novice_toi <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_novice_interval.tsv",
                        locale = locale(decimal_mark = ","))
 
 
@@ -54,7 +54,7 @@ toi_react <- toi_react %>%
          Time_to_first_Event.Reaction_whispering)
 
 
-# compute "rowise" sum across multiple columns but instead of typing column names, use tidy selection syntax
+# compute "row-wise" sum across multiple columns but instead of typing column names, use tidy selection syntax
 toi_react <- toi_react %>%
   rowwise() %>%
   mutate(Time_to_first_Reaction = sum(c_across(cols = contains("Time_to")),
@@ -91,8 +91,28 @@ react_plot
          
 ############### TIME TO FIRST FIXATION ####################
 
+# read in novice data
+toi_fix_novice1 <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_novice_interval_101;108-111.tsv",
+                           locale = locale(decimal_mark = ","))
+
+toi_fix_novice2 <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_novice_interval_102-105.tsv",
+                            locale = locale(decimal_mark = ","))
+
+# combine the novice df
+toi_fix_novice <- rbind(toi_fix_novice1, toi_fix_novice2)
+
+
+# read in expert data
+toi_fix_expert <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_202_203_interval.tsv",
+                           locale = locale(decimal_mark = ","))
+
+
+# combine two data frames 
+toi_fix <- rbind(toi_fix_novice, toi_fix_expert)
+
+
 # filter relevant rows = TOIs
-toi_fix <- toi %>% filter (TOI == "Chatting_with_neighbour"|
+toi_fix <- toi_fix %>% filter (TOI == "Chatting_with_neighbour"|
                                TOI == "Clicking_pen"| 
[…]

### 2021-11-22 01_studies/01_Laborstudie ProVisioNET/R script/et toi/et toi script.R
plots

@@ -2,7 +2,6 @@
 
 library(needs)
 needs(tidyverse,
-      ggplot,
       psych,
       moments,
       sjPlot,
@@ -16,7 +15,7 @@ needs(tidyverse,
 options(dplyr.summarise.inform = FALSE)
 
 # read in data
-expert_toi <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_experts_interval.tsv",
+expert_toi <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_202_203_interval.tsv",
                        locale = locale(decimal_mark = ","))
 novice_toi <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_novice_interval.tsv",
                        locale = locale(decimal_mark = ","))
@@ -42,7 +41,7 @@ toi_react <- toi %>% filter (TOI == "Chatting_with_neighbour"|
 
 # select relevant columns only for time to first event
 toi_react <- toi_react %>% 
-  select(Group, TOI,
+  select(Participant, Group, TOI,
          Time_to_first_Event.Reaction_chatting,
          Time_to_first_Event.Reaction_clicking,
          Time_to_first_Event.Reaction_drawing,
@@ -54,12 +53,22 @@ toi_react <- toi_react %>%
          Time_to_first_Event.Reaction_whispering)
 
 
-# compute "row-wise" sum across multiple columns but instead of typing column names, use tidy selection syntax
-toi_react <- toi_react %>%
-  rowwise() %>%
-  mutate(Time_to_first_Reaction = sum(c_across(cols = contains("Time_to")),
-                                      na.rm = T)) %>%
-  ungroup() %>%
+# # compute "row-wise" sum across multiple columns but instead of typing column names, use tidy selection syntax
+# toi_react <- toi_react %>%
+#   rowwise() %>%
+#   mutate(Time_to_first_Reaction = sum(c_across(cols = contains("Time_to")),
+#                                       na.rm = T)) %>%
+#   ungroup() %>%
+#   select(Group, TOI, Time_to_first_Reaction)
+
+
+# changing format with pivot_longer()
+toi_react <-
+  toi_react %>%
+  pivot_longer(cols = contains("Time_to"),
+               names_to = "Time_to_first_reaction",
+               values_to = "Time_to_first_Reaction") %>%
+  na.omit() %>% 
   select(Group, TOI, Time_to_first_Reaction)
 
 
[…]

### 2021-11-22 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R

@@ -59,14 +59,21 @@ dist_plot <-
   geom_point(size = 2, 
              alpha = 0.4,
              position = position_jitter(seed = 1, 
-                                        width = 0.1)) +
+                                        width = 0.1,
+                                        height = 0)) +
+  labs(x = "",
+       y = "Disturbing Factor") + 
   ylim(0,10)+
   scale_fill_brewer(palette = "RdBu") +
   facet_wrap(vars(Event), 
              nrow = 1, strip.position = "bottom") +
   ggtitle("How disturbing was the event for you?") +
+  theme_minimal() + 
   theme(axis.ticks.x = element_blank(),
-        axis.text.x = element_blank())
+        axis.text.x = element_blank(),
+        legend.position = "none",
+        strip.text.x = element_text(size = 8, 
+                                    angle = 80))
 dist_plot
 
 
@@ -76,18 +83,25 @@ confi_plot <-
          mapping = aes(x = Group,
                        y = Confident_Factor)) +
   geom_boxplot(mapping = aes(fill = Group)) +
+  labs(x = "", 
+       y = "Confident Factor") +
   geom_point(size = 2, 
              alpha = 0.4,
              position = position_jitter(seed = 1, 
-                                        width = 0.1)) +
+                                        width = 0.15, 
+                                        height = 0)) +
   scale_fill_brewer(palette = "RdBu") +
   facet_wrap(vars(Event), 
              nrow = 1, strip.position = "bottom") +
   ggtitle("How confident did you feel in dealing with this event?") +
+  theme_minimal() +
   theme(axis.ticks.x = element_blank(),
-        axis.text.x = element_blank())
+        axis.text.x = element_blank(),
+        strip.text.x = element_text(size = 8, 
+                                    angle = 80))
 
 confi_plot
 
 # arranging plots 
 grid.arrange(dist_plot, confi_plot, ncol=2, nrow =1)
+

### 2021-11-24 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
update demo table

--- 2021-03-01 paper_1/paper_1_supplement_new_table.Rmd
@@
 ```{r setup, include = FALSE}
+library("papaja")
+r_refs("r-references.bib")
+```
 
-# if a package is not installed on the current machine, it will install it
-if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
-if (!require(papaja)) install.packages('papaja'); library(papaja)
-if (!require(psych)) install.packages('psych'); library(psych) # stats
-if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
-if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(42)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+```
+
+# Packages
+
+```{r}
+#install.packages("needs")
 
@@
 
-r_refs("r-references.bib")
+library(needs)
 
+needs(tidyverse,
+      lubridate,
+      viridis,
+      grid,
+      gridExtra,
+      cowplot,
+      readxl,
+      ARTofR)
 ```
-
-```{r analysis-preferences, echo = FALSE}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
-
-# State of research
-
-Teaching and classroom management are multidimensional settings in which teachers have to respond immediately to events as they develop [@barnes2004significance].
-The different interests and abilities of students must be managed in a way that maximizes the active learning time of students and minimizes disruptions whilst teaching.
-Learning to develop such classroom management skills and to teach effectively is a complicated and complex process [@wolff2017see].
-
-During teaching, teachers must be able to select from a variety of visual and acoustic impressions to focus their attention on the essential and to distinguish between relevant and irrelevant events.
-This ability is called professional vision and is a key component of teacher expertise and successful teaching [@barth2017professionelle].
-Eye tracking technology has become a reliable means to study teachers’ visual focus of attention [@pouta2020student; @bogert2016visualperception; @wolff2017see]
-
-Educational research has repeatedly shown that there are differences between experienced and novice teachers in terms of perception and behavioral competencies [@barth2017professionelle; @bogert2016visualperception; @wolff2017see].
-For example, experts direct their attention more often and more evenly to all students, whereas novices only direct their attention to some students.
-The frequency and duration of fixations as eye movement are decisive [@stuermer2017eye].
-Mobile eye-tracking technology has also shown that experienced teachers distribute their focus more efficiently to solve tasks [@jarodzka2010eyes].
-Furthermore, in contrast to novices, experts are able to focus their attention on the entire class and guide the class while giving feedback to individual students and answering questions [@cortina2015low].
-
-## Research questions
-
-The aim of the pilot study was to investigate whether there are differences in how expert and novice teachers manage scripted classroom disruptions.
-The disruptions were experimentally varied using a previously written script.
-Thus, our aim was to find out whether differences in the allocation of attention between expertise groups can be detected in this controlled context.
-
-In order to answer this question, the hypothesis was formulated that teachers with more professional experience not only notice more disruptions but also notice them faster.
-In the hypothesis, therefore, it is necessary to check what has already been shown in the research literature: In complex teaching situations, experts have a more structured and elaborate professional knowledge than novices in order to perceive and interpret relevant events and to act appropriately [@berliner2001learning; @lachner2016makes].
 
@@
 
-For the sample recruitment of the subjects (N = 8, experts n = 2, novices n = 6), schools in the city of Leipzig in Saxony were contacted.
-The institutions as well as the subjects were informed in detail about the aim and intention of the study in advance.
-Participation in the study was voluntary and only took place after written consent has been given.
-
-```{r demographicspilottable, echo = FALSE}
+```{r demographicstable, echo = FALSE}
 
 # prepare data (selected from questionnaire data)
-quest.raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)
+demo.data <- read_excel ("./data/data_empschul_labor_lehrperson_2021-11-24.xlsx")
 
-# knock out NAs
-quest.raw.data <- quest.raw.data  %>% filter(
-  personID != "NA")
+# select relevant columns
+demo.data <- demo.data %>% select(LI02_01_1,
+                                  LI03_01,
+                                  LI04_01,
+                                  LI06_05)
+
+# rename columns
+demo.data <- rename(demo.data, c("Group" = "LI06_05",
+                                  "Gender" = "LI02_01_1",
+                                  "Age" = "LI03_01",
+                                  "Teaching Experience" = "LI04_01"))
+
+# define expert and novice with ifelse function
+demo.data$Group = ifelse(demo.data$Group < 200, "Novice","Expert")
 
 # create a basic table (tibble) using tidyverse functions
-demo.quest.table <- quest.raw.data %>%
-  filter(what == "head") %>%
-  group_by(group) %>%
+demo.table <- demo.data %>%
+  group_by(Group) %>%
   summarise(N=n(),
-            "Male" = sum(gender),
-            "M age" = round(mean(age), 2),
-            "Min age" = min(age),
-            "Max age" = max(age),
-            "SD age" = round(sd(age), 2),
-            "M exp." = round(mean(experience), 2),
-            "Min exp." = min(experience),
-            "Max exp." = max(experience),
-            "SD exp." = round(sd(experience), 2),
+            "Male" = sum(Gender),
+            "M Age" = round(mean(Age), 2),
+            "Min Age" = min(Age),
+            "Max Age" = max(Age),
+            "SD Age" = round(sd(Age), 2),
+            "M Exp." = round(mean(`Teaching Experience`), 2),
+            "Min Exp." = min(`Teaching Experience`),
+            "Max Exp." = max(`Teaching Experience`),
+            "SD Exp." = round(sd(`Teaching Experience`), 2),
            )
@@
 apa_table(
-  demo.quest.table,
-  caption = "Demographic Informationand and Teaching Experience",
+  demo.table,
+  caption = "Demographic Information and and Teaching Experience",
   # note = "Write Note here", 
@@
 
-The selection of the subjects was based on extreme groups, whereby professional experience is the crucial criterion for the selection of experts or novices.
-Novices were recruited as teachers who have been working in the teaching profession for no more than 3 years, whereas experts were considered to have professional experience of 10 years or more [@messner2000berufliche].
+## Material
 
-## Procedure/ Data collection
-
-### Set up
-
-For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig.
-The subjects were divided into groups of four, so the study was conducted on two different sessions.
-All participants were asked to hold a 10-minute lesson.
-The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering questionnaires.
-
-One person from the group of 4 acted as a teacher, the other three subjects acted as the class.
-The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disruptions in the classroom (e.g.
-putting their heads on the table, chatting, looking at their mobile phones, etc.).
-
-The lesson disruptions were displayed as instructions during the lesson for all "students" but not the teacher.
-In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase.
-In addition, the order of the data collection was taken into account in the analyses and variance caused by order was controlled.
-
-(ref:datacollection-caption) Example for set up during a mini-lesson
-
-```{r datacollection, fig.cap = "(ref:datacollection-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/datacollection.png", dpi = 108)
-
-# # How to insert images in papaja
-# - pictures must be png
-# - I created a pictures folder in the main folder, just dumb pictures there
-# - you just need to hand the name and path of the picture to the knitr::: function (see above)
-# - the dpi argument is for adjusting the size on the page in pixels
-
-# in order to write the caption, you have to use the line just above the code chunk (ref:YOURTEXT-caption) and then just write behind it
-# the code chunk then opens and after "r" it needs to provide a name for the code chunk, must be unique in the document
-# the fig.cap = then calls the text from the line just above
-# fig.align allows to position the pic on page, center ist probablby best
-# echo = false ensures that the code chunk does not occur in the pdf
-# Now, go and try putting your own images in the paper 
-#
-# TIP = check line 46 in this manuscript. THis section ets global properties for how graphs are put in the paper. 
-#         if floatsintext      : yes  --> pics, graphs, tables will be put where the code chunk is
-#         if floatsintext      : no   --> pics, graphs, tables will be put at the end as is required by some journals
-# TIP: check the folder "papaja_example&tutorial" that I put in this folder for paper1
-# Tip: make a bookmark of this and skim through it: http://frederikaust.com/papaja_man/
-
-```
-
-### Questionnaire data
-
-After each mini-lesson, the students answered items on the teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and scales on the teacher's presence behavior (students n = 24).
-In addition, the teacher was asked to give a self-assessment on his/her classroom management by completing the questionnaire after each mini-lesson (teachers n = 8).
-
-### Behavioral data
-
-The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab.
-Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles.
-One camera was installed to film the class from the side.
-Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back.
-Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.
-
-### Eyetracking data
-
-A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants.
-The head unit is a measuring device with different sensitive sensors.
-A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
-Infrared light illuminators support the eye tracking sensors which record the eye orientation.
-The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
-The scene camera has a field of view of 90 deg.
-in 16:9 format (82 deg.
-horizontal and 52 deg.
-vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
-The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
-
-## Coding/ Data preparation/ Reliability
-
-### Questionnaire Data
-
-The evaluation after each mini-lesson was conducted using paper questionnaires. Time needed to complete the questionnaire was about 5 minutes. 
-The scales on the quality of teaching are a validated questionnaire [@helmke2014unterrichtsdiagnostik].
-Whereas the scales on the teacher's presence behavior were derived from the research literature [@brophy1986classroom; @kiel2013trainingsbuch; @kounin2006techniken; @marzano2007art; @nolting2012storungen] and were used in the pilot for the first time.
-The questionnaire is 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
-Data was obtained from N = 32 subjects (students n = 24, teachers n = 8).
-
-The following scales were assessed:
-
-(1) Classroom management
-(2) Positive climate and motivation
-(3) Clarity and structuredness
-(4) Activation and support
-(5) Presence: posture/gaze
-(6) Presence: voice
-(7) Presence: verbal and non-verbal intervention
-(8) Natural behaviour
-
-Table \@ref(tab:table-all-scales-self-assessment) provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness & Kurtosis of all scales for the teachers' self-assessment.
-
-```{r table-all-scales-self-assessment, echo = FALSE}
-
-# prepare data (selected from questionnaire data) - only equal items and without observer
-quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)
-
-# knock out NAs and duration of speaking time
-quest.raw.data <- quest.raw.data  %>% filter(
-  personID != "NA",
-  itemID != "8",
-  perspective == "self-assessment")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
-
-##############################################
-
-# calculate Cronbach's Alpha for each scale
-# activation & support
-self.as.wide <- quest.raw.data %>%
-                          filter (scale == "Activation and support") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-self.alpha.as <- alpha(self.as.wide[,-1])
-
-#clarity & structuredness
-self.cs.wide <- quest.raw.data %>%
-                          filter (scale == "Clarity and structuredness") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.cs <- alpha(self.cs.wide[,-1])
-
-#classroom management
-self.cm.wide <- quest.raw.data %>%
-                          filter (scale == "Classroom management") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.cm <- alpha(self.cm.wide[,-1])
-
-#natural behaviour
-self.nb.wide <- quest.raw.data %>%
-                          filter (scale == "Natural behaviour") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.nb <- alpha(self.nb.wide[,-1])
-
-#positive climate and motivation
-self.pcm.wide <- quest.raw.data %>%
-                          filter (scale == "Positive climate and motivation") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pcm <- alpha(self.pcm.wide[,-1])
-
-#presence: posture & gaze
-self.ppg.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: posture/gaze") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.ppg <- alpha(self.ppg.wide[,-1])
-
-#presence: voice
-self.pv.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: voice") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pv <- alpha(self.pv.wide[,-1])
-
-#presence: verbal/non-verbal intervention
-self.pvni.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.pvni <- alpha(self.pvni.wide[,-1])
-
-#Presence without subscales
-self.p.wide <- quest.raw.data %>%
-                          filter(str_detect(scale,
-                                        paste(c(
-                                        "Presence: voice", 
-                                        "Presence: verbal and non-verbal intervention", 
-                                        "Presence: posture/gaze"),
-                                         collapse = '|'))) %>% 
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-self.alpha.p <- alpha(self.p.wide[,-1])
-
-##############################################
-
-# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
-# 
-# # activation & support
-# tab_itemscale(self.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # classroom management
-# tab_itemscale(self.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # clarity & structuredness
-# tab_itemscale(self.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # natural behaviour
-# tab_itemscale(self.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # postive clima and motivation
-# tab_itemscale(self.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence without subscales
-# tab_itemscale(self.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence: posture & gaze
-# tab_itemscale(self.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: voice
-# tab_itemscale(self.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: verbal/non-verbal intervention
-# tab_itemscale(self.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-##############################################
-
-# add alphas to excel table 
-# read in new data 
-quest.raw.data.alpha <- read.table("./data/short_questionnaire_data_260221_alpha.txt", dec=",", sep="\t", header=T)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data.alpha <- quest.raw.data.alpha %>%  mutate(alpha = as.numeric(alpha))
-
-##############################################
-
-# #####correlation between all presences' items
-# SELF-ASSESSMENT
-# install.packages("Hmisc")
-# library("Hmisc")
-
-# function cr() to format the correlation matrix
-res1.self<-cor(self.p.wide[,-1])
-
-# Visualization correlation matrix
-# Use corrplot() function: Draw a correlogram
-
-# # install.packages("corrplot")
-# library("corrplot")
-# 
-# # Insignificant correlation are crossed
-# corrplot(res1.self$r, type="upper", order="hclust",
-#          p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
-# # Insignificant correlations are leaved blank
-# corrplot(res1.self$r, type="upper", order="hclust",
-#          p.mat = res1.self$P, sig.level = 0.01, insig = "blank")
-
-###############################################
-
-# create a basic table (tibble) using tidyverse functions for teachers' self assessment 
-# Change Number of Digits in Global R Options to reduce the number of digits after the decimal point to two
-options(digits = 2)
-
-teacher.scale.quest.table <- quest.raw.data.alpha %>% # select data
-  filter(perspective == "self-assessment")%>%
-  group_by(scale) %>%
-  summarise("N items" = n_distinct(shortID),
-            "M" = round(mean(value), 2),
-            "SD" = round(sd(value), 2),
-            "Min" = min(value),
-            "Max" = max(value),
-            "Skewness" = skewness(value),
-            "Kurtosis" = kurtosis(value),
-            "Cronbach's α" = mean(alpha))
-
-# format and insert table in manuscript
-apa_table(
-  teacher.scale.quest.table,
-  caption = "Scale analysis for teachers' self-assessment",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-```
-
-Table \@ref(tab:table-all-scales-students) provides an overview over the mean, the standard deviation, the range, Cronbach's Alpha and the Skewness & Kurtosis of all scales for the students' perception of the teacher's behaviour in class.
-
-```{r table-all-scales-students, echo = FALSE}
-
-# prepare data (selected from questionnaire data) - only equal items and without observer
-quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)
-
-# knock out NAs and duration of speaking time
-quest.raw.data <- quest.raw.data  %>% filter(
-  personID != "NA",
-  itemID != "8",
-  perspective == "student")
-view(quest.raw.data)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(value))
-
-###############################################
-
-# calculate Cronbach's Alpha for each scale of students' peception
-
-# activation & support
-stud.as.wide <- quest.raw.data %>%
-                          filter (scale == "Activation and support") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-stud.alpha.as <- alpha(stud.as.wide[,-1])
-
-#clarity & structuredness
-stud.cs.wide <- quest.raw.data %>%
-                          filter (scale == "Clarity and structuredness") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.cs <- alpha(stud.cs.wide[,-1])
-
-#classroom management
-stud.cm.wide <- quest.raw.data %>%
-                          filter (scale == "Classroom management") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.cm <- alpha(stud.cm.wide[,-1])
-
-#natural behaviour
-stud.nb.wide <- quest.raw.data %>%
-                          filter (scale == "Natural behaviour") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.nb <- alpha(stud.nb.wide[,-1])
-
-#positive climate and motivation
-stud.pcm.wide <- quest.raw.data %>%
-                          filter (scale == "Positive climate and motivation") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.pcm <- alpha(stud.pcm.wide[,-1])
-
-#presence: posture & gaze
-stud.ppg.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: posture/gaze") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.ppg <- alpha(stud.ppg.wide[,-1])
-
-#presence: verbal and non-verbal intervention
-stud.pvni.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.pvni <- alpha(stud.pvni.wide[,-1])
-
-#presence: voice
-stud.pv.wide <- quest.raw.data %>%
-                          filter (scale == "Presence: voice") %>%  
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.pv <- alpha(stud.pv.wide[,-1])
-
-#Presence without subscales
-stud.p.wide <- quest.raw.data %>%
-                          filter(str_detect(scale,
-                                        paste(c(
-                                        "Presence: voice", 
-                                        "Presence: verbal and non-verbal intervention", 
-                                        "Presence: posture/gaze"),
-                                         collapse = '|'))) %>% 
-                          select(shortID, value) %>%
-                          group_by(shortID) %>%
-                          mutate(id=row_number()) %>%
-                          spread(shortID, value)
-
-stud.alpha.p <- alpha(stud.p.wide[,-1])
-
-# ###############################################
-
-# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
-# 
-# # activation & support
-# tab_itemscale(stud.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # classroom management
-# tab_itemscale(stud.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # clarity & structuredness
-# tab_itemscale(stud.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # natural behaviour
-# tab_itemscale(stud.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # positive clima and motivation
-# tab_itemscale(stud.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence without subscales
-# tab_itemscale(stud.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence: posture & gaze
-# tab_itemscale(stud.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: voice
-# tab_itemscale(stud.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: verbal/non-verbal intervention
-# tab_itemscale(stud.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-
-##############################################
-# #####correlation between all presences' items
-# SELF-ASSESSMENT
-# install.packages("Hmisc")
-library("Hmisc")
-
-# # function to format the correlation matrix
-# flattenCorrMatrix <- function(cormat, pmat) {
-#   ut <- upper.tri(cormat)
-#   data.frame(
-#     row = rownames(cormat)[row(cormat)[ut]],
-#     column = rownames(cormat)[col(cormat)[ut]],
-#     cor  =(cormat)[ut],
-#     p = pmat[ut]
-#     )
-# }
-# 
-# res1.stud<-cor(stud.p.wide[,-1])
-
-# res1.stud<-rcorr(as.matrix(stud.p.wide[,-1]))
-# 
-# flattenCorrMatrix(res1.stud$r, res1.stud$P)
-# 
-# res2.stud<-flattenCorrMatrix(res1.stud$r, res1.stud$P)
-
-# Visualization correlation matrix
-# Use corrplot() function: Draw a correlogram
-
-# install.packages("corrplot")
-library("corrplot")
-
-# # Insignificant correlation are crossed
-# corrplot(res1.stud$r, type="upper", order="hclust",
-#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
-# # Insignificant correlations are leaved blank
-# corrplot(res1.stud$r, type="upper", order="hclust",
-#          p.mat = res1.stud$P, sig.level = 0.01, insig = "blank")
-
-##############################################
-
-# add alphas to excel table 
-# read in new data 
-quest.raw.data.alpha <- read.table("./data/short_questionnaire_data_260221_alpha.txt", dec=",", sep="\t", header=T)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-quest.raw.data.alpha <- quest.raw.data.alpha %>%  mutate(alpha = as.numeric(alpha))
-
-##############################################
-
-# create a basic table (tibble) using tidyverse functions for teacher self assessment 
-student.scale.quest.table <- quest.raw.data.alpha %>% # select data
-  filter(perspective == "student")%>%
-  group_by(scale) %>%
-  summarise("N items" = n_distinct(shortID),
-            "M" = round(mean(value), 2),
-            "SD" = round(sd(value), 2),
-            "Min" = min(value),
-            "Max" = max(value),
-            "Skewness" = skewness(value),
-            "Kurtosis" = kurtosis(value),
-            "Cronbach's α" = mean(alpha))
-
-# format and insert table in manuscript
-apa_table(
-  student.scale.quest.table,
-  caption = "Scale analysis for students' perspective",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-)
-
-```
-
-\newpage
-The individual items of a scale are further represented in graphs.
-
-(1) Classroom management
-```{r Line Plots Classroom Management, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE, fig.cap="Items for Classroom Management"}
-
-### classroom management
-
-# filter by parameter variable, i.e. create a subset for classroom management without perspective "observer"
-cm.data <- quest.raw.data %>% filter(scale == "Classroom management")
-
-view(cm.data)
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-cm.data <- cm.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-cm.plot.sd <- cm.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-cm.plot<-ggplot(data = cm.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = perspective, colour = perspective)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = cm.data, y = "value", x = NULL,
-       title="Classroom management" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-cm.plot
-
-```
-\newpage
-(2) Positive climate and motivation
-```{r Positive climate and motivation line plots,  fig.width=6, fig.height = 7, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Positive climate and motivation"}
-
-### Positive climate and motivation
-
-# filter by parameter variable, i.e. create a subset for Positive climate and motivation
-pcm.data <- quest.raw.data %>% filter(scale == "Positive climate and motivation")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-pcm.data <- pcm.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-pcm.plot.sd <- pcm.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-pcm.plot<-ggplot(data = pcm.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = pcm.data, y = "value", x = NULL,
-       title="Positive climate and motivation" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 5))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-pcm.plot
-
-```
-\newpage
-(3) Clarity and structuredness
-```{r Clarity and structuredness line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Clarity and structuredness"}
-
-### Clarity and structuredness
-
-# filter by parameter variable, i.e. create a subset for Clarity and structuredness
-cs.data <- quest.raw.data %>% filter(scale == "Clarity and structuredness")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-cs.data <- cs.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-cs.plot.sd <- cs.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-cs.plot<-ggplot(data = cs.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = cs.data, y = "value", x = NULL,
-       title="Clarity and structuredness" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-cs.plot
-
-```
-\newpage
-(4) Activation and support
-```{r Activation and support line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Activation and support"}
-
-### Activation and support
-
-# filter by parameter variable, i.e. create a subset for Activation and support
-as.data <- quest.raw.data %>% filter(scale == "Activation and support")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-as.data <- as.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-as.plot.sd <- as.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-as.plot<-ggplot(data = as.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = as.data, y = "value", x = NULL,
-       title="Activation and support" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-as.plot
-
-```
-\newpage
-
-(ref:presenceposturegaze-caption) (5) Presence: posture/gaze
-
-```{r presenceposturegaze, fig.cap = "(ref:presenceposturegaze-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presenceposturegaze.png", dpi = 108)
-
-# ```{r Presence: posture/gaze line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-
-# ### Presence: posture/gaze 
-# 
-# # filter by parameter variable, i.e. create a subset for Presence: posture/gaze
-# ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# ppg.plot.sd <- ppg.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# ppg.plot<-ggplot(data = ppg.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = ppg.data, y = "value", x = NULL,
-#        title="Presence: posture/gaze" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# ppg.plot
-
-```
-
-\newpage
-
-(ref:presencevoice-caption) (6) Presence: voice
-
-```{r presencevoice, fig.cap = "(ref:presencevoice-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presencevoice.png", dpi = 108)
-
-# ```{r Presence: voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-# 
-# ### Presence: voice 
-# # filter by parameter variable, i.e. create a subset for Presence: voice
-# pv.data <- quest.raw.data %>% filter(scale == "Presence: voice")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# pv.plot.sd <- pv.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# pv.plot<-ggplot(data = pv.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = pv.data, y = "value", x = NULL,
-#        title="Presence: voice" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# pv.plot
-
-```
-\newpage
-
-(ref:presenceverbalnonverbalintervention-caption) (7) Presence: verbal and non-verbal intervention
-
-```{r presenceverbalnonverbalintervention, fig.cap = "(ref:presenceverbalnonverbalintervention-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presenceverbalnonverbalintervention.png", dpi = 108)
-
-# ```{r Presence: verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-# 
-# ### Presence: verbal and non-verbal intervention 
-# # filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
-# pvni.data <- quest.raw.data %>% filter(scale == "Presence: verbal and non-verbal intervention")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# pvni.plot.sd <- pvni.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# pvni.plot<-ggplot(data = pvni.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = pvni.data, y = "value", x = NULL,
-#        title="Presence: verbal and non-verbal intervention" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# pvni.plot
-
-```
-\newpage
-(8) Natural behaviour
-```{r Natural behaviour line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Natural Behaviour"}
-
-### Natural behaviour 
-# filter by parameter variable, i.e. create a subset for Natural behaviour
-nb.data <- quest.raw.data %>% filter(scale == "Natural behaviour")
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-nb.data <- nb.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-
-# to create error bars, we need to summarize the data in a separate data frame
-nb.plot.sd <- nb.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
-  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-
-# long plot
-nb.plot<-ggplot(data = nb.plot.sd,
-                  aes(x = item.wordings, y = mean,
-                      group = group, colour = group)) +
-  geom_line()+
-  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-  theme_light() +
-  ylim(1,4)+
-  facet_grid(~perspective)+
-  labs(data = nb.data, y = "value", x = NULL,
-       title="Natural behaviour" ,
-       subtitle=NULL)+
-  theme(legend.position="bottom",
-        panel.spacing.x = ,
-        plot.title = element_text(hjust = 0.5),
-        axis.text.y = element_text(size = 6))+
-  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-  coord_flip()
-nb.plot
-
-```
-\newpage
-In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
-
-```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE, fig.cap = "Boxplots and individual data for experts and novices"}
-
-quest.plot <- quest.raw.data %>%
-  ggplot(aes(x=scale, y=value, fill=scale)) +
-    geom_boxplot() +
-    scale_x_discrete(guide = guide_axis(angle = 70)) +
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    theme_light() +
-    theme(
-      legend.position="none",
-      plot.title = element_text(size=11)
-    ) +
-    facet_grid(~group)+
-    ggtitle("Boxplot with individual points for all scales") +
-    xlab("")
-quest.plot
-
-```
-
-\newpage
-
-### Behavioral Data
-
-The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters [@kuckartz2019analyzing]. The following coding scheme was developed:
-
-- phase - lesson begin, state event: teacher starts the lesson with a noise, talk, taking a position in class
-- phase - lesson end,	state event: teacher finishes the lesson with a noise, talk, taking a position in class
-- phase - organization/transition points, state event: any situation that does not imply effective learning time (fetching chalk, working        material, organizing desks, opening windows, printing work results etc.)
-- phase - single,	state event: any individual student activity on a given task (reading, writing, drawing etc.)
-- phase - group, state event: any student activity on a given task together in a group of at least 3 students (reading, writing, drawing etc.)
-- phase - class discussion, state event: discussion in class, teacher talks to class/individual/group
-- phase - pair: state event: any student activity on a given task together in a team of 2 students (reading, writing, drawing etc.)
-- phase - teachers lecture, state event: any teacher's presentation on a certain topic which maybe supported by a PPP, PREZI, notes on board,    OHP etc.
-- phase - other, state event: not categorizable
-- phase - break, state event: e.g. drinking, relaxation exercises
-- phase - external interruption, state event: external interruptions (e.g. fire alarm, technical problems, other teachers coming into the room)
-
-- speaking time - teacher, state event
-- speaking time - students, state event
-
-- disruption - chatting with neighbor, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - asking a question, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - yelling, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - looking at phone, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - staring out of window, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - drawing, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - head on table, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - clicking pen, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - drumming hands, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - walking around, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-
-First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher.
-The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.
-
-```{r coded speaking time, echo = FALSE }
-### read in data for 01_01_expert_D
-speaking.data.01.01 <- read.delim("./data/Aperol_pilot_01_01_expert_D_cam4_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.01 <- speaking.data.01.01  %>% select(
-  Dokumentgruppe,
-  Dokumentname,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher and "kodiert von Anna" as row 
-speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
-                                           Dokumentgruppe == "kodiert von Anna")
-speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)
-
-# read in data for 01_02_expert_A
-speaking.data.01.02 <- read.delim("./data/Aperol_pilot_01_02_expert_A_cam1_AL.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.02 <- speaking.data.01.02 %>% select(
-  Dokumentname,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.01.02 <- speaking.data.01.02 %>% filter (Code == "speaking time\\teacher")
-speaking.data.01.02 <- sum(speaking.data.01.02$Abdeckungsgrad..)
-
-# read in data for 01_03_novice_B
-speaking.data.01.03 <- read.delim("./data/Aperol_pilot_01_03_novice_B_cam1.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.03 <- speaking.data.01.03 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.01.03 <- speaking.data.01.03 %>% filter (Code == "speaking time\\teachter")
-speaking.data.01.03 <- sum(speaking.data.01.03$Abdeckungsgrad..)
-
-# read in data for 01_04_novice_C
-speaking.data.01.04 <- read.delim("./data/Aperol_pilot_01_04_novice_C_cam1.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.04 <- speaking.data.01.04 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.01.04 <- speaking.data.01.04 %>% filter (Code == "speaking time\\teachter")
-
-speaking.data.01.04 <- sum(speaking.data.01.04$Abdeckungsgrad..)
-
-# read in data for 02_01_novice_A
-speaking.data.02.01 <- read.delim("./data/Aperol_pilot_02_01_novice_A_glasses.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.01 <- speaking.data.02.01 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.01 <- speaking.data.02.01 %>% filter (Code == "speaking time\\teacher")
-speaking.data.02.01 <- sum(speaking.data.02.01$Abdeckungsgrad..)
-
-# read in data for 02_02_novice_B
-speaking.data.02.02 <- read.delim("./data/Aperol_pilot_02_02_novice_B_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.02 <- speaking.data.02.02 %>% select(
-  Dokumentgruppe,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.02 <- speaking.data.02.02 %>% filter (Code == "speaking time\\teacher",
-                                                       Dokumentgruppe == "kodiert von Anna")
-speaking.data.02.02 <- sum(speaking.data.02.02$Abdeckungsgrad..)
-
-# read in data for 02_03_novice_C
-speaking.data.02.03 <- read.delim("./data/Aperol_pilot_02_03_novice_C_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.03 <- speaking.data.02.03 %>% select(
-  Dokumentgruppe,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.03 <- speaking.data.02.03 %>% filter (Code == "speaking time\\teachter",
-                                                       Dokumentgruppe == "02_03_kodiert von Anna")
-speaking.data.02.03 <- sum(speaking.data.02.03$Abdeckungsgrad..)
-
-# read in data for 02_04_novice_D
-speaking.data.02.04 <- read.delim("./data/Aperol_pilot_02_04_novice_D_cam1.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.04 <- speaking.data.02.04 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.04 <- speaking.data.02.04 %>% filter (Code == "speaking time\\teachter")
-speaking.data.02.04 <- sum(speaking.data.02.04$Abdeckungsgrad..)
-
-```
-
-```{r speaking plot, echo=FALSE}
-
-# read in table with coded speaking time included
-speaking.data <- read.delim("./data/plus_coded_speaking_time_questionnaire_data_0802.txt", dec=",", sep="\t", header=T)
-
-# to compare both sessions filter only Identical items
-speaking.data <- speaking.data  %>% filter(str_detect(scale, 
-                                                 paste(c("Duration of speaking time"),
-                                                    collapse = '|')))
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-speaking.data <- speaking.data %>%  mutate(value = as.numeric(value))
-
-speaking.plot <- speaking.data %>%
-  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
-    geom_boxplot() +
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    theme_light() +
-    theme(
-      legend.position="none",
-      plot.title = element_text(size=11),
-      axis.text.x = element_text(size = 8)) +
-    facet_grid(group~perspective) +
-    ggtitle("Boxplot with individual points for Duration of speaking time") +
-    xlab("")
-speaking.plot
-
-```
-
-### Eyetracking Data
-
-The Tobii Pro Lab 2 software was used to analyze the teachers' visual attetion during each mini-lesson.
-The software allows for non-screen based recordings of a participants’ attention while moving in real-world settings.
-The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video.
-In order to map multiple recordings to AOIs, we first imported the eye-tracking recordings into the Tobii Pro Analyzer software.
-Second, we created dynamic Areas of Interest (AOI) manually to plot the gaze data.
-Once the AOIs are created, the gaze recordings of multiple recordings can be mapped and analyzed in aggregated form.
-Tobii Pro does not allow to do AOI based analyses within Pro Lab.
-So we exported a tsv.
-file to do further analyses in the software R.
-
-#### Gaze relational index (GRI)
-
-The GRI is a measure of visual expertise in information processing.
-This metric is calculated as the ratio of mean fixation duration to fixation count.
-The GRI is higher for novices than for experts.
-[@gegenfurtner2020gaze]
-
-```{r GRItable, echo = FALSE}
-
-# prepare data (selected from questionnaire data)
-et.raw.data<-read.table("./data/Aperol_pilot_glasses_raw_fixation_saccades_metrics.tsv", dec=",", sep="\t", header=T)
-
-# converting integer to numeric
-et.raw.data <- et.raw.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.raw.table <- et.raw.data %>%
-  group_by(Participant, Variable) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-
-# format and insert table in manuscript
-apa_table(
-  et.raw.table,
-  caption = "Number and Duration (in msec) of Fixations",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
-
-```{r calibration phase TOI, echo = FALSE}
-
-# prepare data (selected from questionnaire data)
-et.calib.data<-read.table("./data/Aperol_pilot_glasses_raw_ALL_metrics_calib_without_AOI_snapshot.tsv", dec=",", sep="\t", header=T)
-
-# converting integer to numeric
-et.calib.data <- et.calib.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-# select relevant rows 
-et.calib.data <- et.calib.data %>% filter(TOI == "Calibration phase")
-
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.calib.table <- et.calib.data %>%
-  group_by(Participant, Variable1) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-
-# format and insert table in manuscript
-apa_table(
-  et.calib.table,
-  caption = "Number and Duration (in msec) of Fixations during calibration",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
-
-```{r Calib end to lession start TOI, echo = FALSE}
-
-# prepare data (selected from questionnaire data)
-et.calib.lesson.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_calib_end_lesson_start.tsv", dec=",", sep="\t", header=T)
-
-# converting integer to numeric
-et.calib.lesson.data <- et.calib.lesson.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-options(digits = 2)
-
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.calib.lesson.table <- et.calib.lesson.data %>%
-  group_by(Participant, Variable1) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-
-# format and insert table in manuscript
-apa_table(
-  et.calib.lesson.table,
-  caption = "Number and Duration (in msec) of Fixations Calibration End to Lesson Start",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
-
-```{r Disturbance "head on table" to first intervention, echo = FALSE}
-
-# prepare data (selected from questionnaire data)
-et.distub.head.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_head_on_table_session1.tsv", dec=",", sep="\t", header=T)
-
-# converting integer to numeric
-et.distub.head.data <- et.distub.head.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-options(digits = 2)
-
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.distub.head.table <- et.distub.head.data %>%
-  group_by(Participant, Variable1) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-view(et.distub.head.data)
-
-# format and insert table in manuscript
-apa_table(
-  et.distub.head.table,
-  caption = "Number and Duration (in msec) of Fixations for Disturbance 'head on table' to first intervention",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
-
-#########################################
+## Procedure
 
@@
 
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-
-### Questionnaire Data
-
-### Behavioral Data
-
-### Eyetracking Data
-
 # Results
 
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-
-### Questionnaire Data
-
-### Behavioral Data
-
-### Eyetracking Data
-
 # Discussion
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 

### 2021-11-24 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic-data-script.tex
update demo table

--- 2021-03-17 paper_1/paper_1_supplement_et_gri.tex
@@
   man,floatsintext]{apa6}
+\title{Through the eyes of the teacher}
+\author{Mandy Klatt\textsuperscript{1}, Dr.~Gregor Kachel\textsuperscript{1, 2}, Dr.~Christin Lotz\textsuperscript{1}, \& Prof.~Dr.~Anne Deiglmayr\textsuperscript{1}}
+\date{}
+
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
   \usepackage{textcomp} % provide euro and other symbols
-  \usepackage{amssymb}
 \else % if luatex or xetex
@@
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 % Manuscript styling
@@
 \usepackage{csquotes}
-\ifxetex
+\ifXeTeX
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 \else
-  \usepackage[shorthands=off,main=english]{babel}
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 \fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\title{Through the eyes of the teacher}
-\author{Mandy Klatt\textsuperscript{1}, Dr.~Gregor Kachel\textsuperscript{1, 2}, Dr.~Christin Lotz\textsuperscript{1}, \& Prof.~Dr.~Anne Deiglmayr\textsuperscript{1}}
-\date{}
 
@@
 
-\hypertarget{state-of-research}{%
-\section{State of research}\label{state-of-research}}
-
-Teaching and classroom management are multidimensional settings in which teachers have to respond immediately to events as they develop (Barnes, 2004).
-The different interests and abilities of students must be managed in a way that maximizes the active learning time of students and minimizes disruptions whilst teaching.
-Learning to develop such classroom management skills and to teach effectively is a complicated and complex process (Wolff, Jarodzka, \& Boshuizen, 2017).
-
-During teaching, teachers must be able to select from a variety of visual and acoustic impressions to focus their attention on the essential and to distinguish between relevant and irrelevant events.
-This ability is called professional vision and is a key component of teacher expertise and successful teaching (Barth, 2017).
-Eye tracking technology has become a reliable means to study teachers' visual focus of attention (Bogert, 2016; Pouta, Lehtinen, \& Palonen, 2020; Wolff, Jarodzka, \& Boshuizen, 2017)
-
-Educational research has repeatedly shown that there are differences between experienced and novice teachers in terms of perception and behavioral competencies (Barth, 2017; Bogert, 2016; Wolff, Jarodzka, \& Boshuizen, 2017).
-For example, experts direct their attention more often and more evenly to all students, whereas novices only direct their attention to some students.
-The frequency and duration of fixations as eye movement are decisive (Stuermer, Seidel, Mueller, Häusler, \& Cortina, 2017).
-Mobile eye-tracking technology has also shown that experienced teachers distribute their focus more efficiently to solve tasks (Jarodzka, Scheiter, Gerjets, \& Van Gog, 2010).
-Furthermore, in contrast to novices, experts are able to focus their attention on the entire class and guide the class while giving feedback to individual students and answering questions (Cortina, Miller, McKenzie, \& Epstein, 2015).
-
-\hypertarget{research-questions}{%
-\subsection{Research questions}\label{research-questions}}
-
-The aim of the pilot study was to investigate whether there are differences in how expert and novice teachers manage scripted classroom disruptions.
-The disruptions were experimentally varied using a previously written script.
-Thus, our aim was to find out whether differences in the allocation of attention between expertise groups can be detected in this controlled context.
-
-In order to answer this question, the hypothesis was formulated that teachers with more professional experience not only notice more disruptions but also notice them faster.
-In the hypothesis, therefore, it is necessary to check what has already been shown in the research literature: In complex teaching situations, experts have a more structured and elaborate professional knowledge than novices in order to perceive and interpret relevant events and to act appropriately (Berliner, 2001; Lachner, Jarodzka, \& Nückles, 2016).
+\hypertarget{packages}{%
+\section{Packages}\label{packages}}
 
@@
 
-For the sample recruitment of the subjects (N = 8, experts n = 2, novices n = 6), schools in the city of Leipzig in Saxony were contacted.
-The institutions as well as the subjects were informed in detail about the aim and intention of the study in advance.
-Participation in the study was voluntary and only took place after written consent has been given.
-
 \begin{table}[h]
@@
 
-\caption{\label{tab:demographicspilottable}Demographic Information and Teaching Experience}
+\caption{\label{tab:demographicstable}Demographic Information and and Teaching Experience}
 
@@
 \toprule
-group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{M age} & \multicolumn{1}{c}{Min age} & \multicolumn{1}{c}{Max age} & \multicolumn{1}{c}{SD age} & \multicolumn{1}{c}{M exp.} & \multicolumn{1}{c}{Min exp.} & \multicolumn{1}{c}{Max exp.} & \multicolumn{1}{c}{SD exp.}\\
+Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{M Age} & \multicolumn{1}{c}{Min Age} & \multicolumn{1}{c}{Max Age} & \multicolumn{1}{c}{SD Age} & \multicolumn{1}{c}{M Exp.} & \multicolumn{1}{c}{Min Exp.} & \multicolumn{1}{c}{Max Exp.} & \multicolumn{1}{c}{SD Exp.}\\
 \midrule
-expert & 2 & 1 & 47.50 & 44 & 51 & 4.95 & 20.00 & 15.00 & 25.00 & 7.07\\
-novice & 6 & 2 & 25.67 & 20 & 33 & 4.89 & 0.68 & 0.00 & 1.50 & 0.68\\
+Expert & 4 & 7.00 & 49.25 & 27.00 & 59.00 & 14.93 & 25.25 & 3.00 & 37.00 & 15.20\\
+Novice & 11 & 18.00 & 23.18 & 21.00 & 25.00 & 1.08 & 0.55 & 0.00 & 6.00 & 1.81\\
 \bottomrule
@@
 
-The selection of the subjects was based on extreme groups, whereby professional experience is the crucial criterion for the selection of experts or novices.
-Novices were recruited as teachers who have been working in the teaching profession for no more than 3 years, whereas experts were considered to have professional experience of 10 years or more (Messner \& Reusser, 2000).
+\hypertarget{material}{%
+\subsection{Material}\label{material}}
 
-\hypertarget{procedure-data-collection}{%
-\subsection{Procedure/ Data collection}\label{procedure-data-collection}}
-
-\hypertarget{set-up}{%
-\subsubsection{Set up}\label{set-up}}
-
-For this study, scripted mini-lessons with n = 2 experts and n = 6 novices were recorded in the mobile Lab of the Empirical School and Classroom Research at the University of Leipzig.
-The subjects were divided into groups of four, so the study was conducted on two different sessions.
-All participants were asked to hold a 10-minute lesson.
-The duration of each appointment was approximately 2h: per group 10min briefing, 4 x 10min mini-lessons, 10min technical preparation and follow-up and 4x 10min transition points between the lessons and answering questionnaires.
-
-One person from the group of 4 acted as a teacher, the other three subjects acted as the class.
-The subjects, who represented the class, were given behavioral instructions in a pre-written script to simulate typical events and disruptions in the classroom (e.g.~putting their heads on the table, chatting, looking at their mobile phones, etc.).
-
-The lesson disruptions were displayed as instructions during the lesson for all ``students'' but not the teacher.
-In order to avoid learning effects, the disruptions in each lesson were distributed pseudo-randomly over the short teaching phase.
-In addition, the order of the data collection was taken into account in the analyses and variance caused by order was controlled.
-
-\begin{figure}
-
-{\centering \includegraphics[width=5.94in]{./pictures/datacollection}
-
-}
-
-\caption{Example for set up during a mini-lesson}\label{fig:datacollection}
-\end{figure}
-
-\hypertarget{eyetracking-data}{%
-\subsubsection{Eyetracking data}\label{eyetracking-data}}
-
-A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants.
-The head unit is a measuring device with different sensitive sensors.
-A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
-Infrared light illuminators support the eye tracking sensors which record the eye orientation.
-The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
-The scene camera has a field of view of 90 deg.
-in 16:9 format (82 deg.
-horizontal and 52 deg.
-vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
-The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
-
-\hypertarget{coding-data-preparation-reliability}{%
-\subsection{Coding/ Data preparation/ Reliability}\label{coding-data-preparation-reliability}}
-
-\hypertarget{eyetracking-data-1}{%
-\subsubsection{Eyetracking Data}\label{eyetracking-data-1}}
-
-The Tobii Pro Lab 2 software was used to analyze the teachers' visual attetion during each mini-lesson.
-The software allows for non-screen based recordings of a participants' attention while moving in real-world settings.
-The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video.
-In order to map multiple recordings to AOIs, we first imported the eye-tracking recordings into the Tobii Pro Analyzer software.
-Second, we created dynamic Areas of Interest (AOI) manually to plot the gaze data.
-Once the AOIs are created, the gaze recordings of multiple recordings can be mapped and analyzed in aggregated form.
-Tobii Pro does not allow to do AOI based analyses within Pro Lab.
-So we exported a tsv.
-file to do further analyses in the software R.
-
-\hypertarget{gaze-relational-index-gri}{%
-\paragraph{Gaze relational index (GRI)}\label{gaze-relational-index-gri}}
-
-The GRI is a measure of visual expertise in information processing.
-This metric is calculated as the ratio of mean fixation duration to fixation count.
-The GRI is higher for novices than for experts.
-(Gegenfurtner et al., 2020)
-
-The first table provides an overview over the
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:GRItable1}GRI}
-
-\tiny{
-
-\begin{tabular}{lllllllll}
-\toprule
-TOI & \multicolumn{1}{c}{ID} & \multicolumn{1}{c}{Group} & \multicolumn{1}{c}{DurTOI} & \multicolumn{1}{c}{M Dur Fix} & \multicolumn{1}{c}{Number Fix} & \multicolumn{1}{c}{TimeTOI Dur} & \multicolumn{1}{c}{OldGRI} & \multicolumn{1}{c}{NewGRI}\\
-\midrule
-Asking question & 01\_04\_C & Novice & 3,869.00 & 2,925.62 & 3.00 & 1.32 & 975.21 & 0.44\\
-Asking question & 01\_02\_A & Expert & 7,112.00 & 2,925.62 & 13.00 & 2.43 & 225.05 & 0.19\\
-Asking question & 01\_03\_B & Novice & 12,863.00 & 2,925.62 & 4.00 & 4.40 & 731.41 & 1.10\\
-Asking question & 01\_01\_D & Expert & 7,648.00 & 2,925.62 & 7.00 & 2.61 & 417.95 & 0.37\\
-Asking question & 02\_01\_A & Novice & 7,422.00 & 2,925.62 & 3.00 & 2.54 & 975.21 & 0.85\\
-Asking question & 02\_02\_B & Novice & 7,082.00 & 2,925.62 & 9.00 & 2.42 & 325.07 & 0.27\\
-Asking question & 02\_03\_C & Novice & 8,045.00 & 2,925.62 & 8.00 & 2.75 & 365.70 & 0.34\\
-Asking question & 02\_04\_D & Novice & 6,595.00 & 2,925.62 & 6.00 & 2.25 & 487.60 & 0.38\\
-Calibration phase & 01\_04\_C & Novice & 17,224.00 & 12,275.12 & 14.00 & 1.40 & 876.79 & 0.10\\
-Calibration phase & 01\_02\_A & Expert & 13,335.00 & 12,275.12 & 10.00 & 1.09 & 1,227.51 & 0.11\\
-Calibration phase & 01\_03\_B & Novice & 10,615.00 & 12,275.12 & 17.00 & 0.86 & 722.07 & 0.05\\
-Calibration phase & 01\_01\_D & Expert & 16,470.00 & 12,275.12 & 9.00 & 1.34 & 1,363.90 & 0.15\\
-Calibration phase & 02\_01\_A & Novice & 17,902.00 & 12,275.12 & 13.00 & 1.46 & 944.24 & 0.11\\
-Calibration phase & 02\_02\_B & Novice & 12,325.00 & 12,275.12 & 12.00 & 1.00 & 1,022.93 & 0.08\\
-Calibration phase & 02\_03\_C & Novice & 16,494.00 & 12,275.12 & 18.00 & 1.34 & 681.95 & 0.07\\
-Calibration phase & 02\_04\_D & Novice & 20,964.00 & 12,275.12 & 14.00 & 1.71 & 876.79 & 0.12\\
-Chatting with neighbour & 01\_04\_C & Novice & 9,843.00 & 4,070.12 & 27.00 & 2.42 & 150.75 & 0.09\\
-Chatting with neighbour & 01\_02\_A & Expert & 2,607.00 & 4,070.12 & 1.00 & 0.64 & 4,070.12 & 0.64\\
-Chatting with neighbour & 01\_03\_B & Novice & 11,060.00 & 4,070.12 & 10.00 & 2.72 & 407.01 & 0.27\\
-Chatting with neighbour & 01\_01\_D & Expert & 6,612.00 & 4,070.12 & 3.00 & 1.62 & 1,356.71 & 0.54\\
-Chatting with neighbour & 02\_01\_A & Novice & 7,429.00 & 4,070.12 & 5.00 & 1.83 & 814.02 & 0.37\\
-Chatting with neighbour & 02\_02\_B & Novice & 8,397.00 & 4,070.12 & 11.00 & 2.06 & 370.01 & 0.19\\
-Chatting with neighbour & 02\_03\_C & Novice & 11,713.00 & 4,070.12 & 11.00 & 2.88 & 370.01 & 0.26\\
-Chatting with neighbour & 02\_04\_D & Novice & 11,443.00 & 4,070.12 & 4.00 & 2.81 & 1,017.53 & 0.70\\
-Clicking pen & 01\_04\_C & Novice & 12,980.00 & 8,809.75 & 4.00 & 1.47 & 2,202.44 & 0.37\\
-Clicking pen & 01\_02\_A & Expert & 12,071.00 & 8,809.75 & 20.00 & 1.37 & 440.49 & 0.07\\
-Clicking pen & 01\_03\_B & Novice & 26,272.00 & 8,809.75 & 16.00 & 2.98 & 550.61 & 0.19\\
-Clicking pen & 01\_01\_D & Expert & 11,597.00 & 8,809.75 & 11.00 & 1.32 & 800.89 & 0.12\\
-Clicking pen & 02\_01\_A & Novice & 16,114.00 & 8,809.75 & 11.00 & 1.83 & 800.89 & 0.17\\
-Clicking pen & 02\_02\_B & Novice & 9,409.00 & 8,809.75 & 12.00 & 1.07 & 734.15 & 0.09\\
-Clicking pen & 02\_03\_C & Novice & 16,269.00 & 8,809.75 & 27.00 & 1.85 & 326.29 & 0.07\\
-Clicking pen & 02\_04\_D & Novice & 24,220.00 & 8,809.75 & 19.00 & 2.75 & 463.67 & 0.14\\
-Drawing on paper & 01\_04\_C & Novice & 39,979.00 & 34,414.38 & 27.00 & 1.16 & 1,274.61 & 0.04\\
-Drawing on paper & 01\_02\_A & Expert & 44,971.00 & 34,414.38 & 87.00 & 1.31 & 395.57 & 0.02\\
-Drawing on paper & 01\_03\_B & Novice & 129,708.00 & 34,414.38 & 79.00 & 3.77 & 435.62 & 0.05\\
-Drawing on paper & 01\_01\_D & Expert & 74,511.00 & 34,414.38 & 92.00 & 2.17 & 374.07 & 0.02\\
-Drawing on paper & 02\_01\_A & Novice & 43,469.00 & 34,414.38 & 31.00 & 1.26 & 1,110.14 & 0.04\\
-Drawing on paper & 02\_02\_B & Novice & 147,788.00 & 34,414.38 & 295.00 & 4.29 & 116.66 & 0.01\\
-Drawing on paper & 02\_03\_C & Novice & 26,495.00 & 34,414.38 & 46.00 & 0.77 & 748.14 & 0.02\\
-Drawing on paper & 02\_04\_D & Novice & 27,915.00 & 34,414.38 & 11.00 & 0.81 & 3,128.58 & 0.07\\
-Drumming hands & 01\_04\_C & Novice & 43,507.00 & 11,415.88 & 41.00 & 3.81 & 278.44 & 0.09\\
-Drumming hands & 01\_02\_A & Expert & 20,530.00 & 11,415.88 & 27.00 & 1.80 & 422.81 & 0.07\\
-Drumming hands & 01\_03\_B & Novice & 12,615.00 & 11,415.88 & 6.00 & 1.11 & 1,902.65 & 0.18\\
-Drumming hands & 01\_01\_D & Expert & 23,121.00 & 11,415.88 & 17.00 & 2.03 & 671.52 & 0.12\\
-Drumming hands & 02\_01\_A & Novice & 62,326.00 & 11,415.88 & 50.00 & 5.46 & 228.32 & 0.11\\
-Drumming hands & 02\_02\_B & Novice & 24,699.00 & 11,415.88 & 25.00 & 2.16 & 456.64 & 0.09\\
-Drumming hands & 02\_03\_C & Novice & 27,775.00 & 11,415.88 & 49.00 & 2.43 & 232.98 & 0.05\\
-Drumming hands & 02\_04\_D & Novice & 14,998.00 & 11,415.88 & 9.00 & 1.31 & 1,268.43 & 0.15\\
-Looking at phone & 01\_04\_C & Novice & 7,984.00 & 11,563.00 & 8.00 & 0.69 & 1,445.38 & 0.09\\
-Looking at phone & 01\_02\_A & Expert & 19,897.00 & 11,563.00 & 28.00 & 1.72 & 412.96 & 0.06\\
-Looking at phone & 01\_03\_B & Novice & 40,427.00 & 11,563.00 & 30.00 & 3.50 & 385.43 & 0.12\\
-Looking at phone & 01\_01\_D & Expert & 32,387.00 & 11,563.00 & 29.00 & 2.80 & 398.72 & 0.10\\
-Looking at phone & 02\_01\_A & Novice & 33,557.00 & 11,563.00 & 14.00 & 2.90 & 825.93 & 0.21\\
-Looking at phone & 02\_02\_B & Novice & 16,321.00 & 11,563.00 & 19.00 & 1.41 & 608.58 & 0.07\\
-Looking at phone & 02\_03\_C & Novice & 28,223.00 & 11,563.00 & 47.00 & 2.44 & 246.02 & 0.05\\
-Looking at phone & 02\_04\_D & Novice & 31,944.00 & 11,563.00 & 19.00 & 2.76 & 608.58 & 0.15\\
-Putting head on table & 01\_04\_C & Novice & 20,929.00 & 17,049.88 & 38.00 & 1.23 & 448.68 & 0.03\\
-Putting head on table & 01\_02\_A & Expert & 23,402.00 & 17,049.88 & 27.00 & 1.37 & 631.48 & 0.05\\
-Putting head on table & 01\_03\_B & Novice & 39,159.00 & 17,049.88 & 41.00 & 2.30 & 415.85 & 0.06\\
-Putting head on table & 01\_01\_D & Expert & 6,354.00 & 17,049.88 & 4.00 & 0.37 & 4,262.47 & 0.09\\
-Putting head on table & 02\_01\_A & Novice & 51,225.00 & 17,049.88 & 45.00 & 3.00 & 378.89 & 0.07\\
-Putting head on table & 02\_02\_B & Novice & 11,322.00 & 17,049.88 & 20.00 & 0.66 & 852.49 & 0.03\\
-Putting head on table & 02\_03\_C & Novice & 61,713.00 & 17,049.88 & 81.00 & 3.62 & 210.49 & 0.04\\
-Putting head on table & 02\_04\_D & Novice & 57,484.00 & 17,049.88 & 42.00 & 3.37 & 405.95 & 0.08\\
-Yelling & 01\_04\_C & Novice & 6,083.00 & 889.50 & 1.00 & 6.84 & 889.50 & 6.84\\
-Yelling & 01\_02\_A & Expert & 1,995.00 & 889.50 & 1.00 & 2.24 & 889.50 & 2.24\\
-Yelling & 01\_03\_B & Novice & 6,527.00 & 889.50 & 1.00 & 7.34 & 889.50 & 7.34\\
-Yelling & 01\_01\_D & Expert & 2,245.00 & 889.50 & 1.00 & 2.52 & 889.50 & 2.52\\
-Yelling & 02\_01\_A & Novice & 9,105.00 & 889.50 & 7.00 & 10.24 & 127.07 & 1.46\\
-Yelling & 02\_02\_B & Novice & 2,548.00 & 889.50 & 5.00 & 2.86 & 177.90 & 0.57\\
-Yelling & 02\_03\_C & Novice & 2,992.00 & 889.50 & 2.00 & 3.36 & 444.75 & 1.68\\
-Yelling & 02\_04\_D & Novice & 12,416.00 & 889.50 & 1.00 & 13.96 & 889.50 & 13.96\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:GRItable2}GRI}
-
-\tiny{
-
-\begin{tabular}{lllllllll}
-\toprule
-Group & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{M Fixation Duration} & \multicolumn{1}{c}{M Number Fixation} & \multicolumn{1}{c}{M TOI} & \multicolumn{1}{c}{M Old GRI} & \multicolumn{1}{c}{SD Old GRI} & \multicolumn{1}{c}{M New GRI} & \multicolumn{1}{c}{SD New GRI}\\
-\midrule
-Expert & Asking question & 2,108.50 & 10.00 & 7,380.00 & 231.70 & 98.30 & 0.39 & 0.18\\
-Expert & Calibration phase & 12,283.00 & 9.50 & 14,902.50 & 1,296.54 & 96.50 & 0.13 & 0.03\\
-Expert & Chatting with neighbour & 1,829.00 & 2.00 & 4,609.50 & 1,219.33 & 862.20 & 1.32 & 0.16\\
-Expert & Clicking pen & 5,416.50 & 15.50 & 11,834.00 & 381.62 & 156.68 & 0.15 & 0.06\\
-Expert & Drawing on paper & 25,514.50 & 89.50 & 59,741.00 & 285.30 & 11.27 & 0.03 & 0.01\\
-Expert & Drumming hands & 8,405.00 & 22.00 & 21,825.50 & 402.85 & 129.48 & 0.13 & 0.05\\
-Expert & Looking at phone & 8,484.50 & 28.50 & 26,142.00 & 297.79 & 7.39 & 0.11 & 0.03\\
-Expert & Putting head on table & 7,605.50 & 15.50 & 14,878.00 & 1,091.53 & 1,145.29 & 0.16 & 0.07\\
-Expert & Yelling & 580.00 & 1.00 & 2,120.00 & 580.00 & 0.00 & 3.66 & 0.30\\
-Novice & Asking question & 3,198.00 & 5.50 & 7,646.00 & 703.26 & 320.81 & 0.51 & 0.30\\
-Novice & Calibration phase & 12,272.50 & 14.67 & 15,920.67 & 853.95 & 130.15 & 0.09 & 0.03\\
-Novice & Chatting with neighbour & 4,817.17 & 11.33 & 9,980.83 & 617.28 & 384.64 & 0.26 & 0.18\\
-Novice & Clicking pen & 9,940.83 & 14.83 & 17,544.00 & 955.00 & 774.90 & 0.15 & 0.09\\
-Novice & Drawing on paper & 37,381.00 & 81.50 & 69,225.67 & 1,233.52 & 1,156.72 & 0.04 & 0.02\\
-Novice & Drumming hands & 12,419.50 & 30.00 & 30,986.67 & 791.90 & 760.35 & 0.10 & 0.04\\
-Novice & Looking at phone & 12,589.17 & 22.83 & 26,409.33 & 747.59 & 459.89 & 0.10 & 0.05\\
-Novice & Putting head on table & 20,198.00 & 44.50 & 40,305.33 & 535.53 & 252.70 & 0.04 & 0.02\\
-Novice & Yelling & 992.67 & 2.83 & 6,611.83 & 635.78 & 409.08 & 4.76 & 4.60\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:GRItable3}GRI}
-
-\tiny{
-
-\begin{tabular}{llllllll}
-\toprule
-Group & \multicolumn{1}{c}{M Fixation Duration} & \multicolumn{1}{c}{M Number Fixation} & \multicolumn{1}{c}{M TOI} & \multicolumn{1}{c}{M Old GRI} & \multicolumn{1}{c}{SD Old GRI} & \multicolumn{1}{c}{M New GRI} & \multicolumn{1}{c}{SD New GRI}\\
-\midrule
-Expert & 8,025.17 & 21.50 & 18,159.17 & 1,953.05 & 2,871.09 & 0.16 & 0.08\\
-Novice & 12,645.43 & 25.33 & 24,958.93 & 1,878.32 & 2,902.64 & 0.13 & 0.15\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:calibration phase TOI}Number and Duration (in msec) of Fixations during calibration}
-
-\scriptsize{
-
-\begin{tabular}{lllllll}
-\toprule
-Participant & \multicolumn{1}{c}{Variable1} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
-\midrule
-01\_01\_D & Expert & 9.00 & 14,372.00 & 1,597.00 & 16,470.00 & 177.44\\
-01\_02\_A & Expert & 10.00 & 10,194.00 & 1,019.00 & 13,335.00 & 101.90\\
-01\_03\_B & Novice & 17.00 & 9,234.00 & 543.00 & 10,615.00 & 31.94\\
-01\_04\_C & Novice & 14.00 & 15,311.00 & 1,094.00 & 17,224.00 & 78.14\\
-02\_01\_A & Novice & 13.00 & 5,157.00 & 397.00 & 17,902.00 & 30.54\\
-02\_02\_B & Novice & 12.00 & 10,654.00 & 888.00 & 12,325.00 & 74.00\\
-02\_03\_C & Novice & 18.00 & 14,151.00 & 786.00 & 16,494.00 & 43.67\\
-02\_04\_D & Novice & 14.00 & 19,128.00 & 1,366.00 & 20,964.00 & 97.57\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:Calib end to lession start TOI}Number and Duration (in msec) of Fixations Calibration End to Lesson Start}
-
-\scriptsize{
-
-\begin{tabular}{lllllll}
-\toprule
-Participant & \multicolumn{1}{c}{Variable1} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
-\midrule
-01\_01\_D & Expert & 101.00 & 38,177.00 & 378.00 & 53,133.00 & 3.74\\
-01\_02\_A & Expert & 27.00 & 6,736.00 & 249.00 & 15,502.00 & 9.22\\
-01\_03\_B & Novice & 57.00 & 36,378.00 & 638.00 & 58,763.00 & 11.19\\
-01\_04\_C & Novice & 65.00 & 22,387.00 & 344.00 & 39,235.00 & 5.29\\
-02\_01\_A & Novice & 14.00 & 2,619.00 & 187.00 & 30,195.00 & 13.36\\
-02\_02\_B & Novice & 46.00 & 15,851.00 & 345.00 & 30,297.00 & 7.50\\
-02\_03\_C & Novice & 86.00 & 27,643.00 & 321.00 & 42,603.00 & 3.73\\
-02\_04\_D & Novice & 53.00 & 27,783.00 & 524.00 & 36,204.00 & 9.89\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
@@
 
-We used R {[}Version 4.0.3; R Core Team (2019){]} and the R-packages \emph{\}dplyr} {[}@\}R-dplyr{]}, \emph{corrplot2017} (Wei \& Simko, 2017), \emph{forcats} {[}Version 0.5.0; Wickham (2020a){]}, \emph{Formula} {[}Version 1.2.4; Zeileis and Croissant (2010){]}, \emph{ggplot2} {[}Version 3.3.2; Wickham (2016){]}, \emph{Hmisc} {[}Version 4.4.2; Harrell Jr, Charles Dupont, and others.
-(2020){]}, \emph{lattice} {[}Version 0.20.41; Sarkar (2008){]}, \emph{moments} {[}Version 0.14; Komsta and Novomestky (2015){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{papayar} (Muschelli, 2016), \emph{psych} {[}Version 2.0.12; Revelle (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham, Hester, and Francois (2018){]}, \emph{sjPlot} {[}Version 2.8.7; Lüdecke (2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{survival} {[}Version 3.2.7; Terry M.
-Therneau and Patricia M.
-Grambsch (2000){]}, \emph{tibble} {[}Version 3.0.4; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.2; Wickham (2020b){]}, and \emph{tidyverse} {[}Version 1.3.0; Wickham et al.
-(2019){]} for all our analyses.
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-
-\hypertarget{questionnaire-data}{%
-\subsubsection{Questionnaire Data}\label{questionnaire-data}}
-
-\hypertarget{behavioral-data}{%
-\subsubsection{Behavioral Data}\label{behavioral-data}}
-
-\hypertarget{eyetracking-data-2}{%
-\subsubsection{Eyetracking Data}\label{eyetracking-data-2}}
+We used R {[}Version 4.0.3; R Core Team (2020){]} and the R-packages \emph{ARTofR} {[}Version 0.3.3; Zhang (2021){]}, \emph{cowplot} {[}Version 1.1.1; Wilke (2020){]}, \emph{dplyr} {[}Version 1.0.2; Wickham, François, Henry, and Müller (2020){]}, \emph{forcats} {[}Version 0.5.0; Wickham (2020a){]}, \emph{ggplot2} {[}Version 3.3.2; Wickham (2016){]}, \emph{gridExtra} {[}Version 2.3; Auguie (2017){]}, \emph{lubridate} {[}Version 1.7.9.2; Grolemund and Wickham (2011){]}, \emph{needs} {[}Version 0.0.3; Katz (2016){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham and Hester (2020){]}, \emph{readxl} {[}Version 1.3.1; Wickham and Bryan (2019){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.0.4; Müller and Wickham (2020){]}, \emph{tidyr} {[}Version 1.1.2; Wickham (2020b){]}, \emph{tidyverse} {[}Version 1.3.0; Wickham et al.
+(2019){]}, \emph{viridis} {[}Version 0.5.1; Garnier (2018a); Garnier (2018b){]}, and \emph{viridisLite} {[}Version 0.3.0; Garnier (2018b){]} for all our analyses.
 
@@
 
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-
-\hypertarget{questionnaire-data-1}{%
-\subsubsection{Questionnaire Data}\label{questionnaire-data-1}}
-
-\hypertarget{behavioral-data-1}{%
-\subsubsection{Behavioral Data}\label{behavioral-data-1}}
-
-\hypertarget{eyetracking-data-3}{%
-\subsubsection{Eyetracking Data}\label{eyetracking-data-3}}
-
 \hypertarget{discussion}{%
 \section{Discussion}\label{discussion}}
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-R-papaja}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-gridExtra}{}}%
+Auguie, B. (2017). \emph{gridExtra: Miscellaneous functions for "grid" graphics}. Retrieved from \url{https://CRAN.R-project.org/package=gridExtra}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
 Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
 
-\leavevmode\hypertarget{ref-barnes2004significance}{}%
-Barnes, D. (2004). The significance of teachers' frames for teaching. In \emph{Teachers and teaching} (pp. 16--38). Routledge.
+\leavevmode\vadjust pre{\hypertarget{ref-R-viridis}{}}%
+Garnier, S. (2018a). \emph{Viridis: Default color maps from 'matplotlib'}. Retrieved from \url{https://CRAN.R-project.org/package=viridis}
 
-\leavevmode\hypertarget{ref-barth2017professionelle}{}%
-Barth, V. L. (2017). \emph{Professionelle wahrnehmung von störungen im unterricht}. Springer.
+\leavevmode\vadjust pre{\hypertarget{ref-R-viridisLite}{}}%
+Garnier, S. (2018b). \emph{viridisLite: Default color maps from 'matplotlib' (lite version)}. Retrieved from \url{https://CRAN.R-project.org/package=viridisLite}
 
-\leavevmode\hypertarget{ref-berliner2001learning}{}%
-Berliner, D. C. (2001). Learning about and learning from expert teachers. \emph{International Journal of Educational Research}, \emph{35}(5), 463--482.
+\leavevmode\vadjust pre{\hypertarget{ref-R-lubridate}{}}%
+Grolemund, G., \& Wickham, H. (2011). Dates and times made easy with {lubridate}. \emph{Journal of Statistical Software}, \emph{40}(3), 1--25. Retrieved from \url{https://www.jstatsoft.org/v40/i03/}
 
-\leavevmode\hypertarget{ref-bogert2016visualperception}{}%
-Bogert, N.
-J.
-van den.
-(2016).
-\emph{On teachers' visual perception and interpretation of classroom events using eye tracking and collaborative tagging methodologies}.
-Technische Universiteit Eindhoven.
-
-\leavevmode\hypertarget{ref-cortina2015low}{}%
-Cortina, K.
-S., Miller, K.
-F., McKenzie, R., \& Epstein, A.
-(2015).
-Where low and high inference data converge: Validation of CLASS assessment of mathematics instruction using mobile eye tracking with expert and novice teachers.
-\emph{International Journal of Science and Mathematics Education}, \emph{13}(2), 389--403.
-
-\leavevmode\hypertarget{ref-gegenfurtner2020gaze}{}%
-Gegenfurtner, A., Boucheix, J.-M., Gruber, H., Hauser, F., Lehtinen, E., \& Lowe, R.
-K.
-(2020).
-The gaze relational index as a measure of visual expertise.
-\emph{Journal of Expertise.
-East Lansing, Michigan: Michigan State University, 2020, Vol.
-3, Iss.
-1}.
-
-\leavevmode\hypertarget{ref-R-Hmisc}{}%
-Harrell Jr, F. E., Charles Dupont, with contributions from, \& others., many. (2020). \emph{Hmisc: Harrell miscellaneous}. Retrieved from \url{https://CRAN.R-project.org/package=Hmisc}
-
-\leavevmode\hypertarget{ref-R-purrr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-purrr}{}}%
 Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
 
-\leavevmode\hypertarget{ref-jarodzka2010eyes}{}%
-Jarodzka, H., Scheiter, K., Gerjets, P., \& Van Gog, T. (2010). In the eyes of the beholder: How experts and novices interpret dynamic stimuli. \emph{Learning and Instruction}, \emph{20}(2), 146--154.
+\leavevmode\vadjust pre{\hypertarget{ref-R-needs}{}}%
+Katz, J. (2016). \emph{Needs: Attaches and installs packages}. Retrieved from \url{https://CRAN.R-project.org/package=needs}
 
-\leavevmode\hypertarget{ref-R-moments}{}%
-Komsta, L., \& Novomestky, F. (2015). \emph{Moments: Moments, cumulants, skewness, kurtosis and related tests}. Retrieved from \url{https://CRAN.R-project.org/package=moments}
+\leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
+Müller, K., \& Wickham, H. (2020). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
 
-\leavevmode\hypertarget{ref-lachner2016makes}{}%
-Lachner, A., Jarodzka, H., \& Nückles, M.
-(2016).
-What makes an expert teacher?
-Investigating teachers' professional vision and discourse abilities.
-\emph{Instructional Science}, \emph{44}(3), 197--203.
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
+R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
 
-\leavevmode\hypertarget{ref-R-sjPlot}{}%
-Lüdecke, D. (2021). \emph{sjPlot: Data visualization for statistics in social science}. Retrieved from \url{https://CRAN.R-project.org/package=sjPlot}
-
-\leavevmode\hypertarget{ref-messner2000berufliche}{}%
-Messner, H., \& Reusser, K. (2000). Die berufliche entwicklung von lehrpersonen als lebenslanger prozess. \emph{Beitr{ä}ge Zur Lehrerinnen-Und Lehrerbildung}, \emph{18}(2), 157--171.
-
-\leavevmode\hypertarget{ref-R-papayar}{}%
-Muschelli, J. (2016). \emph{Papayar: View medical research images using the papaya JavaScript library}. Retrieved from \url{https://CRAN.R-project.org/package=papayar}
-
-\leavevmode\hypertarget{ref-R-tibble}{}%
-Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
-
-\leavevmode\hypertarget{ref-pouta2020student}{}%
-Pouta, M., Lehtinen, E., \& Palonen, T. (2020). Student teachers' and experienced teachers' professional vision of students' understanding of the rational number concept.
-
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
-
-\leavevmode\hypertarget{ref-R-psych}{}%
-Revelle, W.
-(2020).
-\emph{Psych: Procedures for psychological, psychometric, and personality research}.
-Evanston, Illinois: Northwestern University.
-Retrieved from \url{https://CRAN.R-project.org/package=psych}
-
-\leavevmode\hypertarget{ref-R-lattice}{}%
-Sarkar, D. (2008). \emph{Lattice: Multivariate data visualization with r}. New York: Springer. Retrieved from \url{http://lmdvr.r-forge.r-project.org}
-
-\leavevmode\hypertarget{ref-stuermer2017eye}{}%
-Stuermer, K., Seidel, T., Mueller, K., Häusler, J., \& Cortina, K.
-S.
-(2017).
-What is in the eye of preservice teachers while instructing?
-An eye-tracking study about attention processes in different teaching situations.
-\emph{Zeitschrift f{ü}r Erziehungswissenschaft}, \emph{20}(1), 75--92.
-
-\leavevmode\hypertarget{ref-R-survival-book}{}%
-Terry M. Therneau, \& Patricia M. Grambsch. (2000). \emph{Modeling survival data: Extending the {C}ox model}. New York: Springer.
-
-\leavevmode\hypertarget{ref-R-corrplot2017}{}%
-Wei, T., \& Simko, V. (2017). \emph{R package "corrplot": Visualization of a correlation matrix}. Retrieved from \url{https://github.com/taiyun/corrplot}
-
-\leavevmode\hypertarget{ref-R-ggplot2}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
 Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
 
-\leavevmode\hypertarget{ref-R-stringr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
 Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
 
-\leavevmode\hypertarget{ref-R-forcats}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
 Wickham, H. (2020a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
 
-\leavevmode\hypertarget{ref-R-tidyr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
 Wickham, H. (2020b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
 
-\leavevmode\hypertarget{ref-R-tidyverse}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
 Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
@@
 
-\leavevmode\hypertarget{ref-R-readr}{}%
-Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+\leavevmode\vadjust pre{\hypertarget{ref-R-readxl}{}}%
+Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. Retrieved from \url{https://CRAN.R-project.org/package=readxl}
 
-\leavevmode\hypertarget{ref-wolff2017see}{}%
-Wolff, C.
-E., Jarodzka, H., \& Boshuizen, H.
-P.
-(2017).
-See and tell: Differences between expert and novice teachers' interpretations of problematic classroom management events.
-\emph{Teaching and Teacher Education}, \emph{66}, 295--308.
+\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2020). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
 
-\leavevmode\hypertarget{ref-R-Formula}{}%
-Zeileis, A., \& Croissant, Y.
-(2010).
-Extended model formulas in {R}: Multiple parts and multiple responses.
-\emph{Journal of Statistical Software}, \emph{34}(1), 1--13.
-\url{https://doi.org/10.18637/jss.v034.i01}
+\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
+Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-cowplot}{}}%
+Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ARTofR}{}}%
+Zhang, H. (2021). \emph{ARTofR: Who ever care about the {[}art of r{]} scripts?} Retrieved from \url{https://CRAN.R-project.org/package=ARTofR}
 

### 2021-11-28 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
r script demo data
SJT + SRI Plots

@@
 # prepare data (selected from questionnaire data)
-demo.data <- read_excel ("./data/data_empschul_labor_lehrperson_2021-11-24.xlsx")
+demo.data <- read_excel ("./data/data_empschul_labor_lehrperson.xlsx")
 
@@
 demo.data$Group = ifelse(demo.data$Group < 200, "Novice","Expert")
+
+# changing gender female 2 = 0 
+demo.data$Gender = ifelse(demo.data$Gender == 2, "0","1")
+
+# changing character into numeric
+demo.data$Gender <- as.numeric(demo.data$Gender)
 

### 2021-11-28 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R

@@ -2,7 +2,6 @@
 
 library(needs)
 needs(tidyverse,
-      ggplot,
       psych,
       moments,
       sjPlot,
@@ -22,9 +21,9 @@ sri_expert <- read_excel("./data/coding_sri_expert.xlsx")
 
 
 # filter relevant rows and select relevant columns 
-sri_novice <- sri_novice %>% select(Group, Event, Disturbing_Factor, Confident_Factor)
+sri_novice <- sri_novice %>% select(Group, Event, Disruption_Factor, Confident_Factor)
 
-sri_expert <- sri_expert %>% select(Group, Event, Disturbing_Factor, Confident_Factor)
+sri_expert <- sri_expert %>% select(Group, Event, Disruption_Factor, Confident_Factor)
 
 
 # combine the two data frames with novice and expert
@@ -39,22 +38,22 @@ sri_filter <- na.omit(sri)
 
 # # creating a new column --> event was "seen" / "not seen" 
 # # WARNING! ifelse() needs three parameters: test, truth value, false value 
-# sri$Seen <- ifelse(sri$Disturbing_Factor <= 10, 'seen', ifelse(sri$Disturbing_Factor > 11, 'not seen', 'not seen')) 
+# sri$Seen <- ifelse(sri$Disruption_Factor <= 10, 'seen', ifelse(sri$Disruption_Factor > 11, 'not seen', 'not seen')) 
 
 
 # define expert and novice with ifelse function
 sri_filter$Group = ifelse(sri_filter$Group < 200, "Novice","Expert")
 
 # create a new data frame with both factors
-sri_disturb <- subset.data.frame(sri_filter, select = c(Group, Event, Disturbing_Factor))
+sri_disrup <- subset.data.frame(sri_filter, select = c(Group, Event, Disruption_Factor))
 sri_confi <- subset.data.frame(sri_filter, select = c(Group, Event, Confident_Factor))
 
 
-# plotting disturbing factor
+# plotting Disruption factor
 dist_plot <- 
-  ggplot(data = sri_disturb,
+  ggplot(data = sri_disrup,
          mapping = aes(x = Group,
-                       y = Disturbing_Factor)) +
+                       y = Disruption_Factor)) +
   geom_boxplot(mapping = aes(fill = Group)) +
   geom_point(size = 2, 
              alpha = 0.4,
@@ -62,16 +61,15 @@ dist_plot <-
                                         width = 0.1,
                                         height = 0)) +
   labs(x = "",
-       y = "Disturbing Factor") + 
[…]

### 2021-11-28 01_studies/01_Laborstudie ProVisioNET/SJTest/SJTest.R

@@ -41,7 +41,7 @@ mean_plot <-
                                         width = 0.1)) +
   labs(x = "") +
   ylim(0,1) + 
-  scale_fill_brewer(palette = "RdBu") +
+  scale_fill_brewer(palette = "Set1") +
   facet_wrap(vars(`Facets Classroom Management`), 
              nrow = 1, strip.position = "bottom") +
   theme_minimal()+
@@ -49,8 +49,7 @@ mean_plot <-
   theme(
     axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
-    strip.text.x = element_text(size = 8, 
-                                angle = 45))
+    strip.text.x = element_text(size = 12))
 
 mean_plot
 

### 2021-11-29 01_studies/01_Laborstudie ProVisioNET/R script/et toi/et toi script.R
update R script

@@ -14,15 +14,23 @@ needs(tidyverse,
 # if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
 options(dplyr.summarise.inform = FALSE)
 
+
 # read in data
-expert_toi <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_202_203_interval.tsv",
-                       locale = locale(decimal_mark = ","))
-novice_toi <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_novice_interval.tsv",
+expert_toi <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_202_203_204_205_interval.tsv",
                        locale = locale(decimal_mark = ","))
 
+# read in novice data
+toi_novice1 <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_novice_interval_101;108-111.tsv",
+                            locale = locale(decimal_mark = ","))
+
+toi_novice2 <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics 102-107_interval.tsv",
+                            locale = locale(decimal_mark = ","))
+
+# combine the novice df
+toi_novice <- rbind(toi_novice1, toi_novice2)
 
 # combine two data frames 
-toi <- rbind(expert_toi, novice_toi)
+toi <- rbind(expert_toi, toi_novice)
 
 
 ############### TIME TO FIRST REACTION ####################
@@ -72,7 +80,6 @@ toi_react <-
   select(Group, TOI, Time_to_first_Reaction)
 
 
-
 # changing milliseconds into seconds
 toi_react$`Time to first reaction in seconds`<- round(toi_react$Time_to_first_Reaction/1000,
                                                     digits = 2)
@@ -91,7 +98,7 @@ react_plot <-
                                         height = 0)) +
   ylim(0,25) + 
   labs(x = "") +
-  scale_fill_brewer(palette = "RdBu") +
+  scale_fill_brewer(palette = "Set1") +
   facet_wrap(vars(TOI), 
              nrow = 1, strip.position = "bottom") +
   ggtitle("Time to first reaction to disruptive person") +
@@ -100,34 +107,14 @@ react_plot <-
     axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
     strip.text.x = element_text(size = 8, 
-                                angle = 80))
+                                angle = 65))
 react_plot
 
          
[…]

### 2021-11-30 01_studies/01_Laborstudie ProVisioNET/R script/et toi/et toi script.R
plots

@@ -20,14 +20,17 @@ expert_toi <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_202_203_
                        locale = locale(decimal_mark = ","))
 
 # read in novice data
-toi_novice1 <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_novice_interval_101;108-111.tsv",
+toi_novice1 <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_101_interval.tsv",
                             locale = locale(decimal_mark = ","))
 
-toi_novice2 <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics 102-107_interval.tsv",
+toi_novice2 <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics_108-111_interval.tsv",
+                       locale = locale(decimal_mark = ","))
+
+toi_novice3 <- read_tsv(file = "./data/ProVisioNET_study_glasses_metrics 102-107_interval.tsv",
                             locale = locale(decimal_mark = ","))
 
 # combine the novice df
-toi_novice <- rbind(toi_novice1, toi_novice2)
+toi_novice <- rbind(toi_novice1, toi_novice2, toi_novice3)
 
 # combine two data frames 
 toi <- rbind(expert_toi, toi_novice)
@@ -77,7 +80,7 @@ toi_react <-
                names_to = "Time_to_first_reaction",
                values_to = "Time_to_first_Reaction") %>%
   na.omit() %>% 
-  select(Group, TOI, Time_to_first_Reaction)
+  select(Group, TOI, Participant, Time_to_first_Reaction)
 
 
 # changing milliseconds into seconds
@@ -85,7 +88,30 @@ toi_react$`Time to first reaction in seconds`<- round(toi_react$Time_to_first_Re
                                                     digits = 2)
 
 
-# plotting time to first reaction
+# plotting time to first reaction for groups
+react_group_plot <- 
+  ggplot(data = toi_react,
+         mapping = aes(x = Group,
+                       y = `Time to first reaction in seconds`)) +
+  geom_boxplot(mapping = aes(fill = Group)) +
+  geom_point(size = 2, 
+             alpha = 0.4,
+             position = position_jitter(seed = 1, 
+                                        width = 0.1,
+                                        height = 0)) +
+  ylim(0,25) + 
+  labs(x = "") +
+  scale_fill_brewer(palette = "Set1") +
+  ggtitle("Time to first reaction to disruptive person") +
[…]

### 2021-11-30 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R

@@ -49,7 +49,33 @@ sri_disrup <- subset.data.frame(sri_filter, select = c(Group, Event, Disruption_
 sri_confi <- subset.data.frame(sri_filter, select = c(Group, Event, Confident_Factor))
 
 
-# plotting Disruption factor
+# plotting Disruption factor for groups
+dist_group_plot <- 
+  ggplot(data = sri_disrup,
+         mapping = aes(x = Group,
+                       y = Disruption_Factor)) +
+  geom_boxplot(mapping = aes(fill = Group)) +
+  geom_point(size = 2, 
+             alpha = 0.4,
+             position = position_jitter(seed = 1, 
+                                        width = 0.1,
+                                        height = 0)) +
+  labs(x = "",
+       y = "Disruption Factor") + 
+  ylim(0,10)+
+  scale_fill_brewer(palette = "Set1") +
+  ggtitle("How disruptive was the event for you?") +
+  theme_classic() + 
+  theme(
+    legend.position="none",
+    axis.text.x = element_text(size = 11),
+    plot.title = element_text(size = 15, face = "bold"))
+
+dist_group_plot
+
+
+
+# plotting Disruption factor for all disruptions
 dist_plot <- 
   ggplot(data = sri_disrup,
          mapping = aes(x = Group,
@@ -67,16 +93,18 @@ dist_plot <-
   facet_wrap(vars(Event), 
              nrow = 1, strip.position = "bottom") +
   ggtitle("How disruptive was the event for you?") +
-  theme_minimal() + 
+  theme_classic() + 
   theme(axis.ticks.x = element_blank(),
         axis.text.x = element_blank(),
         strip.text.x = element_text(size = 8, 
-                                    angle = 80))
+                                    angle = 80),
+        plot.title = element_text(size = 15, face = "bold"))
+
 dist_plot
 
 
-# plotting Confident factor
-confi_plot <- 
+# plotting Confident factor for group
+confi_group_plot <- 
   ggplot(data = sri_confi,
          mapping = aes(x = Group,
                        y = Confident_Factor)) +
@@ -90,17 +118,59 @@ confi_plot <-
                                         width = 0.15, 
                                         height = 0)) +
   scale_fill_brewer(palette = "Set1") +
+  ggtitle("How confident did you feel dealing with this event?") +
+  theme_classic() +
+  theme(axis.ticks.x = element_blank(),
+        legend.position="none",
[…]

### 2021-11-30 01_studies/01_Laborstudie ProVisioNET/SJTest/SJTest.R

@@ -29,7 +29,7 @@ df_sjt_long <- df_sjt %>%
 # define expert and novice with ifelse function
 df_sjt_long$Group = ifelse(df_sjt_long$Group < 200, "Novice","Expert")
 
-# plotting mean
+# plotting mean of all aspects 
 mean_plot <- 
   ggplot(data = df_sjt_long,
          mapping = aes(x = Group,
@@ -44,7 +44,7 @@ mean_plot <-
   scale_fill_brewer(palette = "Set1") +
   facet_wrap(vars(`Facets Classroom Management`), 
              nrow = 1, strip.position = "bottom") +
-  theme_minimal()+
+  theme_classic()+
   ggtitle("Situational Judgment Test of Strategic Knowledge of Classroom Management") +
   theme(
     axis.text.x = element_blank(),
@@ -53,3 +53,34 @@ mean_plot <-
 
 mean_plot
 
+#################### MEAN, SD, N ############
+
+# mean SJT ALL
+sjt_mean <- df_sjt_long %>%
+  filter(`Facets Classroom Management` == "All") %>%
+  group_by(Group) %>%
+  summarise("M" = round(mean(Mean), 2),
+            "SD" = round(sd(Mean), 2))
+
+
+# mean SJT Managing Momentum
+sjt_mm <- df_sjt_long %>%
+  filter(`Facets Classroom Management` == "Managing momentum") %>%
+  group_by(Group) %>%
+  summarise("M" = round(mean(Mean), 2),
+            "SD" = round(sd(Mean), 2))
+
+# mean SJT Monitoring
+sjt_m <- df_sjt_long %>%
+  filter(`Facets Classroom Management` == "Monitoring") %>%
+  group_by(Group) %>%
+  summarise("M" = round(mean(Mean), 2),
+            "SD" = round(sd(Mean), 2))
+
+
+# mean SJT Rules and routins
+sjt_r <- df_sjt_long %>%
+  filter(`Facets Classroom Management` == "Rules and routines") %>%
+  group_by(Group) %>%
+  summarise("M" = round(mean(Mean), 2),
+            "SD" = round(sd(Mean), 2))

### 2022-02-15 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et aoi.R
update r script aoi

@@ -193,6 +193,7 @@ df_aoi_totaldur <- df_aoi_totaldur %>% pivot_longer(
 # remove all NAs
 df_aoi_totaldur <- na.omit(df_aoi_totaldur)
 
+
 # changing milliseconds into seconds
 df_aoi_totaldur$Seconds <- round(df_aoi_totaldur$Milliseconds/1000,
                         digits = 2)

### 2022-02-15 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_reli_reactions.R
R script SRI + demographic + TOI + AOI

@@ -1,0 +1,132 @@
+### ProVisioNET pilot data 
+#### intercoder reli expertise data 01_01
+
+
+# install needed packages
+library(needs)
+needs(tidyverse,
+      psych,
+      moments,
+      sjPlot,
+      irr,
+      readxl, 
+      DescTool)
+
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
+
+
+################## RATER 1 ################
+
+# read in data from rater1 while specifying locale allows to set "," 
+r1 <-read_excel ("./data/coding_reactions_CW_ohne_Abstufung.xlsx")
+
+
+################## RATER 2 ################
+
+# read in data from rater1 while specifying locale allows to set "," 
+r2 <-read_excel ("./data/coding_reactions_LK_ohne_Abstufung.xlsx")
+
+
+################## DATA WRANGLING video 01 ################
+
+# filter relevant rows and select relevant columns 
+r1_v1 <- r1 %>% filter(script == "01") %>%
+               select(,4:17)
+
+r2_v1 <- r2 %>% filter(script == "01") %>%
+   select(,4:17)
+
+
+# reshape data frame in long format 
+r1_long <- gather(r1_v1, reaction, value)
+
+r2_long <- gather(r2_v1, reaction, value)
+
+r1_long$value <- as.numeric(r1_long$value)
+
+r2_long$value <- as.numeric(r2_long$value)
+
+
+# merge two data frames vertically
+r3 <- bind_cols(r1_long$value, r2_long$value) %>%
+         rename(rating1 = ...1, 
+                rating2 = ...2)
+
+
+# compare for rating for video 01
+# add a new column to differentiate rater1 and rater2 in wide format
+# r3$Added_Column <- c("rater1", "rater2")
+#rename column
+# r3 <- r3 %>% rename(rater = Added_Column)
+# relocate the column to the first place
+# r3 <- r3 %>% relocate(rater)
+# create a new df r3 with only the ratings 
+# r3 <- r3[-c(2:3)]
+
+# # wide to long format
+# r3_long <- gather(r3, timestamp, value, 2:985)
+# 
+# r3_long_wide <- pivot_wider(r3_long,
+#                             names_from = rater)
+# 
+# # create again a new df r3 with only the ratings 
[…]

### 2022-02-15 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_reli_01_01_TOI-based_data_first_reaction.R

@@ -1,0 +1,195 @@
+### ProVisioNET pilot data 
+#### intercoder reli eye tracking data 01_01
+
+library(needs)
+needs(tidyverse,
+      psych,
+      moments,
+      sjPlot,
+      DescTools,
+      irr,
+      readxl)
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
+
+
+# read in data
+reaction_AP <- read_tsv(file = "data/01_01_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv"
+)
+
+reaction_MK <- read_tsv(file = "data/01_01_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv"
+)
+
+# select relevant columns
+reaction_AP <- reaction_AP %>% 
+  select(TOI, 
+         Time_to_first_Event.Reaction_chatting,
+         Time_to_first_Event.Reaction_clicking,
+         Time_to_first_Event.Reaction_drawing,
+         Time_to_first_Event.Reaction_drumming,
+         Time_to_first_Event.Reaction_head,
+         Time_to_first_Event.Reaction_heckling,
+         Time_to_first_Event.Reaction_phone,
+         Time_to_first_Event.Reaction_snipping,
+         Time_to_first_Event.Reaction_whispering
+         )
+
+reaction_MK <- reaction_MK %>% 
+  select(TOI, 
+         Time_to_first_Event.Reaction_chatting,
+         Time_to_first_Event.Reaction_clicking,
+         Time_to_first_Event.Reaction_drawing,
+         Time_to_first_Event.Reaction_drumming,
+         Time_to_first_Event.Reaction_head,
+         Time_to_first_Event.Reaction_heckling,
+         Time_to_first_Event.Reaction_phone,
+         Time_to_first_Event.Reaction_snipping,
+         Time_to_first_Event.Reaction_whispering
+         )
+
+# filter only for event TOIs 
+reaction_AP <- reaction_AP %>% 
+  filter(TOI == "Chatting_with_neighbour"|
+         TOI == "Clicking_pen"| 
+         TOI == "Drawing"|
+         TOI == "Drumming_with_hands"| 
+         TOI == "Head_on_table"| 
+         TOI == "Heckling"|
+         TOI == "Looking_at_phone" |
+         TOI == "Snipping_with_fingers"|
+         TOI == "Whispering"
+         )
+
[…]

### 2022-02-15 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R

@@ -68,8 +68,10 @@ dist_group_plot <-
   theme_classic() + 
   theme(
     legend.position="none",
-    axis.text.x = element_text(size = 11),
-    plot.title = element_text(size = 15, face = "bold"))
+    axis.text.x = element_text(size = 15),
+    plot.title = element_text(size = 19, face = "bold"),
+    axis.text.y = element_text(size = 15),
+    axis.title.y = element_text(size = 15))
 
 dist_group_plot
 
@@ -77,6 +79,29 @@ dist_group_plot
 
 # plotting Disruption factor for all disruptions
 dist_plot <- 
+  sri_disrup %>% 
+  mutate(Event = factor(Event,
+                      levels = c("chatting",
+                                 "whispering",
+                                 "heckling",
+                                 "snipping",
+                                 "drumming",
+                                 "clicking",
+                                 "looking at phone",
+                                 "head on table",
+                                 "drawing"
+                      ),
+                      labels = c("Chatting",
+                                 "Whispering",
+                                 "Heckling",
+                                 "Snipping",
+                                 "Drumming",
+                                 "Clicking pen",
+                                 "Looking at phone",
+                                 "Head on table",
+                                 "Drawing"
+                      )
+  )) %>%
   ggplot(data = sri_disrup,
          mapping = aes(x = Group,
                        y = Disruption_Factor)) +
@@ -97,7 +122,7 @@ dist_plot <-
   theme(axis.ticks.x = element_blank(),
         axis.text.x = element_blank(),
         strip.text.x = element_text(size = 8, 
-                                    angle = 80),
+                                    angle = 90),
         plot.title = element_text(size = 15, face = "bold"))
 
 dist_plot

### 2022-02-15 01_studies/01_Laborstudie ProVisioNET/SJTest/SJTest.R

@@ -22,6 +22,9 @@ df_sjt <- rename(df_sjt, c("Group" = "UI06_05",
                            "Rules and routines" = "SJT_R_gek",
                            "All" = "SJT_KF_gek"))
 
+# remove NAs
+df_sjt <- na.omit(df_sjt)
+
 # changing from wide to long format
 df_sjt_long <- df_sjt %>% 
   pivot_longer(!Group, names_to = "Facets Classroom Management", values_to = "Mean")
@@ -49,7 +52,8 @@ mean_plot <-
   theme(
     axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
-    strip.text.x = element_text(size = 12))
+    strip.text.x = element_text(size = 14),
+    axis.title.y = element_text(size = 16))
 
 mean_plot
 

### 2022-02-16 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R
Plot_akt

@@ -86,8 +86,8 @@ dist_plot <-
                                  "heckling",
                                  "snipping",
                                  "drumming",
-                                 "clicking",
-                                 "looking at phone",
+                                 "clicking pen",
+                                 "locking at phone",
                                  "head on table",
                                  "drawing"
                       ),
@@ -100,10 +100,9 @@ dist_plot <-
                                  "Looking at phone",
                                  "Head on table",
                                  "Drawing"
-                      )
+                                 )
   )) %>%
-  ggplot(data = sri_disrup,
-         mapping = aes(x = Group,
+  ggplot(mapping = aes(x = Group,
                        y = Disruption_Factor)) +
   geom_boxplot(mapping = aes(fill = Group)) +
   geom_point(size = 2, 
@@ -125,8 +124,8 @@ dist_plot <-
                                     angle = 90),
         plot.title = element_text(size = 15, face = "bold"))
 
-dist_plot
 
+dist_plot
 
 # plotting Confident factor for group
 confi_group_plot <- 

### 2022-02-17 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
update r script

@@
 classoption       : "man"
-output            : papaja::apa6_pdf #bookdown::word_document2
+output            : bookdown::word_document2
 ---
@@
   demo.table,
-  caption = "Demographic Information and and Teaching Experience",
+  caption = "Demographic Information and Teaching Experience",
   # note = "Write Note here", 

### 2022-02-17 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et aoi.R

@@ -69,6 +69,13 @@ novice_aoi9 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_116_inter
 novice_aoi10 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_117_interval_complete.tsv",
                         locale = locale(decimal_mark = ","))
 
+novice_aoi11 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_118_interval_complete.tsv",
+                         locale = locale(decimal_mark = ","))
+
+novice_aoi12 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_119_interval_complete.tsv",
+                         locale = locale(decimal_mark = ","))
+
+
 # combine the novice df
 novice_aoi <- rbind(novice_aoi1, 
                     novice_aoi2, 
@@ -79,7 +86,9 @@ novice_aoi <- rbind(novice_aoi1,
                     novice_aoi7,
                     novice_aoi8,
                     novice_aoi9,
-                    novice_aoi10)
+                    novice_aoi10,
+                    novice_aoi11,
+                    novice_aoi12)
 
 
 # combine the both df

### 2022-02-17 01_studies/01_Laborstudie ProVisioNET/R script/et toi/et toi script.R
plots

@@ -68,6 +68,12 @@ novice_toi9 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_116_inter
 novice_toi10 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_117_interval_complete.tsv",
                          locale = locale(decimal_mark = ","))
 
+novice_toi11 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_118_interval_complete.tsv",
+                         locale = locale(decimal_mark = ","))
+
+novice_toi12 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_119_interval_complete.tsv",
+                         locale = locale(decimal_mark = ","))
+
 
 # combine the novice df
 novice_toi <- rbind(novice_toi1, 
@@ -79,7 +85,9 @@ novice_toi <- rbind(novice_toi1,
                     novice_toi7,
                     novice_toi8,
                     novice_toi9,
-                    novice_toi10)
+                    novice_toi10,
+                    novice_toi11,
+                    novice_toi12)
 
 
 # combine the both df
@@ -155,8 +163,10 @@ react_group_plot <-
   ggtitle("Time to first reaction to disruptive person") +
   theme_classic() + 
   theme(legend.position="none",
-        axis.text.x = element_text(size = 11),
-        plot.title = element_text(size = 15, face = "bold"))
+        axis.text.x = element_text(size = 20),
+        plot.title = element_text(size = 17, face = "bold"),
+        axis.title.y = element_text(size = 18),
+        )
 
 react_group_plot
 
@@ -195,9 +205,10 @@ react_plot <-
   theme(
     axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
-    strip.text.x = element_text(size = 8,
+    strip.text.x = element_text(size = 9,
                                 angle = 90),
-    plot.title = element_text(size = 15, face = "bold")
+    plot.title = element_text(size = 17, face = "bold"),
+    axis.title.y = element_text(size = 14),
     ) +
   facet_wrap(facets = vars(TOI),
              nrow = 1,
@@ -250,15 +261,32 @@ fix_group_plot <-
   ggtitle("Time to first fixation to disruptive person") +
   theme_classic() + 
   theme(legend.position="none",
-        axis.text.x = element_text(size = 11),
-        plot.title = element_text(size = 15, face = "bold"))
+        axis.text.x = element_text(size = 20),
+        plot.title = element_text(size = 17, face = "bold"),
[…]

### 2022-02-17 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R

@@ -144,17 +144,41 @@ confi_group_plot <-
   scale_fill_brewer(palette = "Set1") +
   ggtitle("How confident did you feel dealing with this event?") +
   theme_classic() +
-  theme(axis.ticks.x = element_blank(),
-        legend.position="none",
-        axis.text.x = element_text(size = 11),
-        plot.title = element_text(size = 15, face = "bold"))
+  theme(
+    legend.position="none",
+    axis.text.x = element_text(size = 15),
+    plot.title = element_text(size = 19, face = "bold"),
+    axis.text.y = element_text(size = 15),
+    axis.title.y = element_text(size = 15))
 
 confi_group_plot
 
 # plotting confident factor for all disruptions
 confi_plot <- 
-  ggplot(data = sri_confi,
-         mapping = aes(x = Group,
+  sri_confi %>% 
+  mutate(Event = factor(Event,
+                        levels = c("chatting",
+                                   "whispering",
+                                   "heckling",
+                                   "snipping",
+                                   "drumming",
+                                   "clicking pen",
+                                   "locking at phone",
+                                   "head on table",
+                                   "drawing"
+                        ),
+                        labels = c("Chatting",
+                                   "Whispering",
+                                   "Heckling",
+                                   "Snipping",
+                                   "Drumming",
+                                   "Clicking pen",
+                                   "Looking at phone",
+                                   "Head on table",
+                                   "Drawing"
+                        )
+  )) %>%
+  ggplot(mapping = aes(x = Group,
                        y = Confident_Factor)) +
   geom_boxplot(mapping = aes(fill = Group)) +
   geom_point(size = 2, 
@@ -173,7 +197,7 @@ confi_plot <-
   theme(axis.ticks.x = element_blank(),
         axis.text.x = element_blank(),
         strip.text.x = element_text(size = 8, 
-                                    angle = 80),
+                                    angle = 90),
         plot.title = element_text(size = 15, face = "bold"))
 
 confi_plot
@@ -191,7 +215,7 @@ sri_disrup_mean <- sri_disrup %>%
   summarise("M" = round(mean(Disruption_Factor), 2),
             "SD" = round(sd(Disruption_Factor), 2))
 
-# mean ttfr 
+# mean confi_factor
 sri_confi_mean <- sri_confi %>%
   group_by(Group) %>%
   summarise("M" = round(mean(Confident_Factor), 2),

### 2022-02-17 01_studies/01_Laborstudie ProVisioNET/SJTest/SJTest.R

@@ -50,10 +50,12 @@ mean_plot <-
   theme_classic()+
   ggtitle("Situational Judgment Test of Strategic Knowledge of Classroom Management") +
   theme(
+    plot.title = element_text(size = 18, face = "bold"),
     axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
     strip.text.x = element_text(size = 14),
-    axis.title.y = element_text(size = 16))
+    axis.title.y = element_text(size = 13),
+    axis.title.x = element_text(size = 25))
 
 mean_plot
 

### 2022-02-19 01_studies/01_Laborstudie ProVisioNET/R script/et toi/et toi script.R
update plots

@@ -217,10 +217,83 @@ react_plot <-
 react_plot
 
 
+# plotting time to first reaction for 3 disruptions sum up
+toi_react$TOI[toi_react$TOI == "Chatting_with_neighbour" |
+                toi_react$TOI == "Heckling" |
+                toi_react$TOI == "Whispering"] <- "Verbal disruption"
+
+toi_react$TOI[toi_react$TOI == "Head_on_table" |
+                toi_react$TOI == "Looking_at_phone" |
+                toi_react$TOI == "Drawing"] <- "Lack of eagerness"
+
+toi_react$TOI[toi_react$TOI == "Clicking_pen" |
+                toi_react$TOI == "Drumming_with_hands" |
+                toi_react$TOI == "Snipping_with_fingers"] <- "Agitation"
+
+
+# select relevant columns only for time to first event
+toi_react <- toi_react %>% 
+  select(Participant, Group, TOI,
+         Time_to_first_Event.Reaction_chatting,
+         Time_to_first_Event.Reaction_clicking,
+         Time_to_first_Event.Reaction_drawing,
+         Time_to_first_Event.Reaction_drumming,
+         Time_to_first_Event.Reaction_head,
+         Time_to_first_Event.Reaction_heckling,
+         Time_to_first_Event.Reaction_phone,
+         Time_to_first_Event.Reaction_snipping,
+         Time_to_first_Event.Reaction_whispering)
+
+# changing format with pivot_longer()
+toi_react <-
+  toi_react %>%
+  pivot_longer(cols = contains("Time_to"),
+               names_to = "Time_to_first_reaction",
+               values_to = "Time_to_first_Reaction") %>%
+  na.omit() %>% 
+  select(Group, TOI, Participant, Time_to_first_Reaction)
+
+
+# changing milliseconds into seconds
+toi_react$`Time to first reaction in seconds`<- round(toi_react$Time_to_first_Reaction/1000,
+                                                      digits = 2)
+
+# plotting
+react_plot_sum <-
+  ggplot(data = toi_react,
+         mapping = aes(x = Group,
+                       y = `Time to first reaction in seconds`)) +
+  geom_boxplot(mapping = aes(fill = Group)) +
+  geom_point(size = 2, 
+             alpha = 0.4,
+             position = position_jitter(seed = 1, 
+                                        width = 0.1,
+                                        height = 0)) +
+  ylim(0,25) + 
+  labs(x = "") +
[…]

### 2022-02-20 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R
r script toi

@@ -76,33 +76,26 @@ dist_group_plot <-
 dist_group_plot
 
 
+# plotting Disruption factor for 3 disruptions sum up
+sri_disrup$Event[sri_disrup$Event == "chatting" |
+                   sri_disrup$Event == "heckling" |
+                   sri_disrup$Event == "whispering"] <- "Verbal disruption"
 
-# plotting Disruption factor for all disruptions
-dist_plot <- 
-  sri_disrup %>% 
-  mutate(Event = factor(Event,
-                      levels = c("chatting",
-                                 "whispering",
-                                 "heckling",
-                                 "snipping",
-                                 "drumming",
-                                 "clicking pen",
-                                 "locking at phone",
-                                 "head on table",
-                                 "drawing"
-                      ),
-                      labels = c("Chatting",
-                                 "Whispering",
-                                 "Heckling",
-                                 "Snipping",
-                                 "Drumming",
-                                 "Clicking pen",
-                                 "Looking at phone",
-                                 "Head on table",
-                                 "Drawing"
-                                 )
-  )) %>%
-  ggplot(mapping = aes(x = Group,
+sri_disrup$Event[sri_disrup$Event == "head on table" |
+                   sri_disrup$Event == "looking at phone" |
+                   sri_disrup$Event == "drawing"] <- "Lack of eagerness"
+
+sri_disrup$Event[sri_disrup$Event == "clicking pen" |
+                   sri_disrup$Event == "drumming" |
+                   sri_disrup$Event == "snipping"] <- "Agitation"
+
+
+
+
+# plotting
+sri_disrup_sum <-
+  ggplot(data = sri_disrup,
+         mapping = aes(x = Group,
                        y = Disruption_Factor)) +
   geom_boxplot(mapping = aes(fill = Group)) +
   geom_point(size = 2, 
@@ -110,22 +103,79 @@ dist_plot <-
              position = position_jitter(seed = 1, 
                                         width = 0.1,
                                         height = 0)) +
-  labs(x = "",
-       y = "Disruption Factor") + 
-  ylim(0,10)+
+  ylim(0,10) + 
+  labs(x = "") +
+  ylab("Disruption Factor") +
   scale_fill_brewer(palette = "Set1") +
-  facet_wrap(vars(Event), 
-             nrow = 1, strip.position = "bottom") +
   ggtitle("How disruptive was the event for you?") +
-  theme_classic() + 
-  theme(axis.ticks.x = element_blank(),
-        axis.text.x = element_blank(),
[…]

### 2022-03-01 01_studies/01_Laborstudie ProVisioNET/R script/et toi/et toi script.R
update R toi script

@@ -150,19 +150,22 @@ toi_react$`Time to first reaction in seconds`<- round(toi_react$Time_to_first_Re
 react_group_plot <- 
   ggplot(data = toi_react,
          mapping = aes(x = Group,
-                       y = `Time to first reaction in seconds`)) +
+                       y = log(`Time to first reaction in seconds`))) +
   geom_boxplot(mapping = aes(fill = Group)) +
-  geom_point(size = 2, 
-             alpha = 0.4,
-             position = position_jitter(seed = 1, 
-                                        width = 0.1,
-                                        height = 0)) +
-  ylim(0,25) + 
-  labs(x = "") +
+  # geom_point(size = 2, 
+  #            alpha = 0.4,
+  #            position = position_jitter(seed = 1, 
+  #                                       width = 0.1,
+  #                                       height = 0)) +
+  labs(x = "",
+       y = "Time to first reaction in seconds") +
   scale_fill_brewer(palette = "Set1") +
   ggtitle("Time to first reaction to disruptive person") +
-  theme_classic() + 
-  theme(legend.position="none",
+  theme_bw() + 
+  theme(axis.line = element_line(colour = "black"),
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        legend.position="none",
         axis.text.x = element_text(size = 20),
         plot.title = element_text(size = 17, face = "bold"),
         axis.title.y = element_text(size = 18),
@@ -170,51 +173,50 @@ react_group_plot <-
 
 react_group_plot
 
-
 # plotting time to first reaction for all disruptions
-react_plot <- 
-  toi_react %>% 
-  mutate(TOI = factor(TOI,
-                        levels = c("Chatting_with_neighbour","Whispering",
-                                  "Heckling","Snipping_with_fingers",
-                                  "Drumming_with_hands","Clicking_pen",
-                                  "Head_on_table","Looking_at_phone",
-                                  "Drawing"
-                                  ),
-                        labels = c("Chatting with neighbour","Whispering",
-                                   "Heckling","Snipping with fingers",
-                                   "Drumming with hands","Clicking pen",
-                                   "Head on table","Looking at phone",
-                                   "Drawing"
-                        )
-                        )
-         ) %>% 
-  ggplot(mapping = aes(x = Group,
[…]

### 2022-03-01 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
r markdown method part

@@
     corresponding : yes    # Define only one corresponding author
-    address       : "Egelstraße 2a 04103 Leipzig"
+    address       : "Dittrichring 5-7, 04109 Leipzig"
     email         : "mandy.klatt@uni-leipzig.de"
@@
 authornote: |
-  The Ethics Advisory Board of Leipzig University has dealt with the research project and has come to the conclusion that there are no objections to the implementation of this research project.
-The Ethics Advisory Board points out that the scientific and ethical responsibilty for the implementation of the project remains with the project director.
+  Ethics Approval 
+All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board.
+The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
+
+  Consent to Participate
+All participants gave informed consent.
 
 abstract: |
-  This document is a supplement to the paper and shows first graphs findings from the pilot study.
 
-keywords          : "Professional Vision, Expert-Novice-Paradigm, Eye-Tracking"
-wordcount         : "1949"
+keywords          : "Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking"
+wordcount         : "XXX"
 
@@
   summarise(N=n(),
-            "Male" = sum(Gender),
+            "Gender male" = round(100 * n() / nrow(Gende)), 2,
             "M Age" = round(mean(Age), 2),

### 2022-03-01 02_paper/01_pilot/paper_1/plots_peer/presentation_plots.Rmd
r markdown method part

--- 2021-07-21 02_paper/paper_1/plots_peer/presentation_plots.Rmd
@@
       viridis,
-      ggthemes)
+      ggthemes,
+      RColorBrewer)
 
@@
 
+```
+
+## Mean Duration
+
+```{r}
+group_by(.data = df_gri,
+         TOI) %>% summarise(`Mean Duration Fix`= mean(`M Dur Fix`)) %>%
+  ggplot(mapping = aes(x = TOI,
+                     y = `Mean Duration Fix`
+                     )
+         ) +
+  geom_bar(stat = "identity",
+           color = "black",
+           fill = "#EF8A62") +
+  theme_clean() +
+  theme(axis.text.x = element_text(angle = 45,
+                                   hjust = 1
+                                   )
+        )
 ```

### 2022-03-01 02_paper/01_pilot/paper_1_supplement.Rmd
r markdown method part

--- 2021-02-11 paper_1/paper_1_supplement.Rmd
@@
 
-# knock out NAs
+# knock out NAs and filter only perspective == teacher, student
 quest.raw.data <- quest.raw.data  %>% filter(
-  personID != "NA")
+  personID != "NA",
+  str_detect(perspective, paste(c("teacher", "student"),collapse = '|')))
 
@@
 scale.quest.table <- quest.raw.data %>% # select data
-  group_by(group, scale) %>%
+  group_by(scale) %>%
   summarise("M scale" = round(mean(value), 2),
+            "SD scale" = round(sd(value), 2),
             "min scale" = min(value),
-            "max sclae" = max(value),
-            "SD scale" = round(sd(value), 2))
+            "max sclae" = max(value))
 
@@
 quest.plot <- quest.raw.data %>%
-  ggplot( aes(x=scale, y=value, fill=scale)) +
+  ggplot(aes(x=scale, y=value, fill=scale)) +
     geom_boxplot() +

### 2022-03-01 02_paper/01_pilot/paper_1_supplement_questionnaire.Rmd
r markdown method part

--- 2021-03-03 paper_1/paper_1_supplement_new_table.Rmd
@@
 title             : "Through the eyes of the teacher"
-shorttitle        : "Visual attention in teaching and learning processes"
+shorttitle        : "Visual attention in teaching and learning processes - QUESTIONNAIRE DATA"
 
@@
 
-### Behavioral data
-
-The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab.
-Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles.
-One camera was installed to film the class from the side.
-Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back.
-Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.
-
-### Eyetracking data
-
-A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants.
-The head unit is a measuring device with different sensitive sensors.
-A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
-Infrared light illuminators support the eye tracking sensors which record the eye orientation.
-The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
-The scene camera has a field of view of 90 deg.
-in 16:9 format (82 deg.
-horizontal and 52 deg.
-vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
-The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
-
 ## Coding/ Data preparation/ Reliability
@@
 
-# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
-# 
+# item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
+
 # # activation & support
@@
 ```
-
 \newpage
@@
 
+# prepare data (selected from questionnaire data) - only equal items and without observer
+quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)
+
 # filter by parameter variable, i.e. create a subset for classroom management without perspective "observer"
@@
 cm.plot.sd <- cm.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
+  group_by(group, shortID, .drop=TRUE) %>%
   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
@@
 cm.plot<-ggplot(data = cm.plot.sd,
-                  aes(x = item.wordings, y = mean,
+                  aes(x = shortID, y = mean,
                       group = perspective, colour = perspective)) +
@@
 pcm.plot.sd <- pcm.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
+  group_by(group, shortID, .drop=TRUE) %>%
   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
@@
 pcm.plot<-ggplot(data = pcm.plot.sd,
-                  aes(x = item.wordings, y = mean,
+                  aes(x = shortID, y = mean,
                       group = group, colour = group)) +
@@
 cs.plot.sd <- cs.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
+  group_by(group, shortID, .drop=TRUE) %>%
   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
@@
 cs.plot<-ggplot(data = cs.plot.sd,
-                  aes(x = item.wordings, y = mean,
+                  aes(x = shortID, y = mean,
                       group = group, colour = group)) +
@@
 ```{r Activation and support line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Activation and support"}
-
 ### Activation and support
+
+# prepare data (selected from questionnaire data) - only equal items and without observer
+quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)
 
@@
 as.plot.sd <- as.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
+  group_by(group, shortID, .drop=TRUE) %>%
   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
@@
 as.plot<-ggplot(data = as.plot.sd,
-                  aes(x = item.wordings, y = mean,
+                  aes(x = shortID, y = mean,
                       group = group, colour = group)) +
@@
 
-(ref:presenceposturegaze-caption) (5) Presence: posture/gaze
-
-```{r presenceposturegaze, fig.cap = "(ref:presenceposturegaze-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presenceposturegaze.png", dpi = 108)
-
-# ```{r Presence: posture/gaze line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+(5) Presence: posture and gaze 
+```{r Presence posture and gaze line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Presence posture and gaze"}
 
@@
 #
-# # filter by parameter variable, i.e. create a subset for Presence: posture/gaze
-# ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# ppg.plot.sd <- ppg.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# ppg.plot<-ggplot(data = ppg.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = ppg.data, y = "value", x = NULL,
-#        title="Presence: posture/gaze" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# ppg.plot
+# filter by parameter variable, i.e. create a subset for Presence: posture/gaze
+ppg.data <- quest.raw.data %>% filter(scale == "Presence: posture/gaze")
+#
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+ppg.data <- ppg.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# to create error bars, we need to summarize the data in a separate data frame
+ppg.plot.sd <- ppg.data %>%
+  group_by(group, shortID, .drop=TRUE) %>%
+  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# long plot
+ppg.plot<-ggplot(data = ppg.plot.sd,
+                        aes(x = shortID, y = mean,
+                        group = group, colour = group)) +
+    geom_line()+
+    geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+    theme_light() +
+     ylim(1,4)+
+     facet_grid(~perspective)+
+     labs(data = ppg.data, y = "value", x = NULL,
+         title="Presence: posture/gaze" ,
+         subtitle=NULL)+
+    theme(legend.position="bottom",
+          panel.spacing.x = ,
+          plot.title = element_text(hjust = 0.5),
+          axis.text.y = element_text(size = 6))+
+    scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+   coord_flip()
+ ppg.plot
 
@@
 
-(ref:presencevoice-caption) (6) Presence: voice
-
-```{r presencevoice, fig.cap = "(ref:presencevoice-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presencevoice.png", dpi = 108)
-
-# ```{r Presence: voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-# 
-# ### Presence: voice 
-# # filter by parameter variable, i.e. create a subset for Presence: voice
-# pv.data <- quest.raw.data %>% filter(scale == "Presence: voice")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# pv.plot.sd <- pv.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# pv.plot<-ggplot(data = pv.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = pv.data, y = "value", x = NULL,
-#        title="Presence: voice" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# pv.plot
+(6) Presence: voice
+```{r Presence voice line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE, fig.cap = "Items for Presence voice"}
+
+### Presence: voice
+# filter by parameter variable, i.e. create a subset for Presence: voice
+pv.data <- quest.raw.data %>% filter(scale == "Presence: voice")
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+pv.data <- pv.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# to create error bars, we need to summarize the data in a separate data frame
+pv.plot.sd <- pv.data %>%
+  group_by(group, shortID, .drop=TRUE) %>%
+  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# long plot
+pv.plot<-ggplot(data = pv.plot.sd,
+                  aes(x = shortID, y = mean,
+                      group = group, colour = group)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  facet_grid(~perspective)+
+  labs(data = pv.data, y = "value", x = NULL,
+       title="Presence: voice" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5),
+        axis.text.y = element_text(size = 6))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+pv.plot
 
@@
 
-(ref:presenceverbalnonverbalintervention-caption) (7) Presence: verbal and non-verbal intervention
-
-```{r presenceverbalnonverbalintervention, fig.cap = "(ref:presenceverbalnonverbalintervention-caption)", fig.align = "center", echo = FALSE}
-
-knitr::include_graphics("./pictures/presenceverbalnonverbalintervention.png", dpi = 108)
-
-# ```{r Presence: verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
-# 
-# ### Presence: verbal and non-verbal intervention 
-# # filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
-# pvni.data <- quest.raw.data %>% filter(scale == "Presence: verbal and non-verbal intervention")
-# 
-# # value sometimes contained text before filtering, we have to convert the numbers to numeric
-# pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))
-# 
-# # to create error bars, we need to summarize the data in a separate data frame
-# pvni.plot.sd <- pvni.data %>%
-#   group_by(group, item.wordings, .drop=TRUE) %>%
-#   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
-# 
-# # long plot
-# pvni.plot<-ggplot(data = pvni.plot.sd,
-#                   aes(x = item.wordings, y = mean,
-#                       group = group, colour = group)) +
-#   geom_line()+
-#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
-#   theme_light() +
-#   ylim(1,4)+
-#   facet_grid(~perspective)+
-#   labs(data = pvni.data, y = "value", x = NULL,
-#        title="Presence: verbal and non-verbal intervention" ,
-#        subtitle=NULL)+
-#   theme(legend.position="bottom",
-#         panel.spacing.x = ,
-#         plot.title = element_text(hjust = 0.5),
-#         axis.text.y = element_text(size = 6))+
-#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
-#   coord_flip()
-# pvni.plot
+(7) Presence: verbal and non-verbal intervention
+
+```{r Presence verbal and non-verbal intervention line plots,  fig.width=6, fig.height = 6, message = FALSE, warning = FALSE , echo=FALSE}
+
+### Presence: verbal and non-verbal intervention
+# filter by parameter variable, i.e. create a subset for Presence: verbal and non-verbal intervention
+pvni.data <- quest.raw.data %>% filter(scale == "Presence: verbal and non-verbal intervention")
+
+# value sometimes contained text before filtering, we have to convert the numbers to numeric
+pvni.data <- pvni.data %>%  mutate(value = as.numeric(as.character(factor(value))))
+
+# to create error bars, we need to summarize the data in a separate data frame
+pvni.plot.sd <- pvni.data %>%
+  group_by(group, shortID, .drop=TRUE) %>%
+  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
+
+# long plot
+pvni.plot<-ggplot(data = pvni.plot.sd,
+                  aes(x = shortID, y = mean,
+                      group = group, colour = group)) +
+  geom_line()+
+  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
+  theme_light() +
+  ylim(1,4)+
+  facet_grid(~perspective)+
+  labs(data = pvni.data, y = "value", x = NULL,
+       title="Presence: verbal and non-verbal intervention" ,
+       subtitle=NULL)+
+  theme(legend.position="bottom",
+        panel.spacing.x = ,
+        plot.title = element_text(hjust = 0.5),
+        axis.text.y = element_text(size = 6))+
+  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
+  coord_flip()
+pvni.plot
 
@@
 nb.plot.sd <- nb.data %>%
-  group_by(group, item.wordings, .drop=TRUE) %>%
+  group_by(group, shortID, .drop=TRUE) %>%
   summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
@@
 nb.plot<-ggplot(data = nb.plot.sd,
-                  aes(x = item.wordings, y = mean,
+                  aes(x = shortID, y = mean,
                       group = group, colour = group)) +
@@
 In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
-
 ```{r boxplot scales, fig.width=6, fig.height = 8, echo = FALSE, fig.cap = "Boxplots and individual data for experts and novices"}
+
+# prepare data (selected from questionnaire data) - only equal items and without observer
+quest.raw.data<-read.table("./data/short_questionnaire_data_150221.txt", dec=",", sep="\t", header=T)
 
@@
       legend.position="none",
-      plot.title = element_text(size=11)
-    ) +
-    facet_grid(~group)+
+      plot.title = element_text(size=11)) +
+    facet_grid(~perspective)+
     ggtitle("Boxplot with individual points for all scales") +
@@
 ```
-
-\newpage
-
-### Behavioral Data
-
-The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters [@kuckartz2019analyzing]. The following coding scheme was developed:
-
-- phase - lesson begin, state event: teacher starts the lesson with a noise, talk, taking a position in class
-- phase - lesson end,	state event: teacher finishes the lesson with a noise, talk, taking a position in class
-- phase - organization/transition points, state event: any situation that does not imply effective learning time (fetching chalk, working        material, organizing desks, opening windows, printing work results etc.)
-- phase - single,	state event: any individual student activity on a given task (reading, writing, drawing etc.)
-- phase - group, state event: any student activity on a given task together in a group of at least 3 students (reading, writing, drawing etc.)
-- phase - class discussion, state event: discussion in class, teacher talks to class/individual/group
-- phase - pair: state event: any student activity on a given task together in a team of 2 students (reading, writing, drawing etc.)
-- phase - teachers lecture, state event: any teacher's presentation on a certain topic which maybe supported by a PPP, PREZI, notes on board,    OHP etc.
-- phase - other, state event: not categorizable
-- phase - break, state event: e.g. drinking, relaxation exercises
-- phase - external interruption, state event: external interruptions (e.g. fire alarm, technical problems, other teachers coming into the room)
-
-- speaking time - teacher, state event
-- speaking time - students, state event
-
-- disruption - chatting with neighbor, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - asking a question, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - yelling, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - looking at phone, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - staring out of window, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - drawing, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - head on table, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - clicking pen, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - drumming hands, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-- disruption - walking around, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-
-First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher.
-The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.
-
-```{r coded speaking time, echo = FALSE }
-### read in data for 01_01_expert_D
-speaking.data.01.01 <- read.delim("./data/Aperol_pilot_01_01_expert_D_cam4_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.01 <- speaking.data.01.01  %>% select(
-  Dokumentgruppe,
-  Dokumentname,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher and "kodiert von Anna" as row 
-speaking.data.01.01 <- speaking.data.01.01 %>% filter (Code == "speaking time\\teacher",
-                                           Dokumentgruppe == "kodiert von Anna")
-speaking.data.01.01 <- sum(speaking.data.01.01$Abdeckungsgrad..)
-
-# read in data for 01_02_expert_A
-speaking.data.01.02 <- read.delim("./data/Aperol_pilot_01_02_expert_A_cam1_AL.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.02 <- speaking.data.01.02 %>% select(
-  Dokumentname,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.01.02 <- speaking.data.01.02 %>% filter (Code == "speaking time\\teacher")
-speaking.data.01.02 <- sum(speaking.data.01.02$Abdeckungsgrad..)
-
-# read in data for 01_03_novice_B
-speaking.data.01.03 <- read.delim("./data/Aperol_pilot_01_03_novice_B_cam1.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.03 <- speaking.data.01.03 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.01.03 <- speaking.data.01.03 %>% filter (Code == "speaking time\\teachter")
-speaking.data.01.03 <- sum(speaking.data.01.03$Abdeckungsgrad..)
-
-# read in data for 01_04_novice_C
-speaking.data.01.04 <- read.delim("./data/Aperol_pilot_01_04_novice_C_cam1.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.01.04 <- speaking.data.01.04 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.01.04 <- speaking.data.01.04 %>% filter (Code == "speaking time\\teachter")
-
-speaking.data.01.04 <- sum(speaking.data.01.04$Abdeckungsgrad..)
-
-# read in data for 02_01_novice_A
-speaking.data.02.01 <- read.delim("./data/Aperol_pilot_02_01_novice_A_glasses.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.01 <- speaking.data.02.01 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.01 <- speaking.data.02.01 %>% filter (Code == "speaking time\\teacher")
-speaking.data.02.01 <- sum(speaking.data.02.01$Abdeckungsgrad..)
-
-# read in data for 02_02_novice_B
-speaking.data.02.02 <- read.delim("./data/Aperol_pilot_02_02_novice_B_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.02 <- speaking.data.02.02 %>% select(
-  Dokumentgruppe,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.02 <- speaking.data.02.02 %>% filter (Code == "speaking time\\teacher",
-                                                       Dokumentgruppe == "kodiert von Anna")
-speaking.data.02.02 <- sum(speaking.data.02.02$Abdeckungsgrad..)
-
-# read in data for 02_03_novice_C
-speaking.data.02.03 <- read.delim("./data/Aperol_pilot_02_03_novice_C_cam1_AL_MK.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.03 <- speaking.data.02.03 %>% select(
-  Dokumentgruppe,
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.03 <- speaking.data.02.03 %>% filter (Code == "speaking time\\teachter",
-                                                       Dokumentgruppe == "02_03_kodiert von Anna")
-speaking.data.02.03 <- sum(speaking.data.02.03$Abdeckungsgrad..)
-
-# read in data for 02_04_novice_D
-speaking.data.02.04 <- read.delim("./data/Aperol_pilot_02_04_novice_D_cam1.txt", dec=",", sep="\t", header=T)
-
-### select relevant columns
-speaking.data.02.04 <- speaking.data.02.04 %>% select(
-  Code,
-  Anfang,
-  Ende,
-  Fläche,
-  Abdeckungsgrad..)
-
-### filter only speaking time of teacher as row 
-speaking.data.02.04 <- speaking.data.02.04 %>% filter (Code == "speaking time\\teachter")
-speaking.data.02.04 <- sum(speaking.data.02.04$Abdeckungsgrad..)
-
-```
-
-```{r speaking plot, echo=FALSE}
-
-# read in table with coded speaking time included
-speaking.data <- read.delim("./data/plus_coded_speaking_time_questionnaire_data_0802.txt", dec=",", sep="\t", header=T)
-
-# to compare both sessions filter only Identical items
-speaking.data <- speaking.data  %>% filter(str_detect(scale, 
-                                                 paste(c("Duration of speaking time"),
-                                                    collapse = '|')))
-
-# value sometimes contained text before filtering, we have to convert the numbers to numeric
-speaking.data <- speaking.data %>%  mutate(value = as.numeric(value))
-
-speaking.plot <- speaking.data %>%
-  ggplot(aes(x='Duration of speaking time', y=value, fill=group)) +
-    geom_boxplot() +
-    geom_jitter(color="black", size=0.4, alpha=0.9) +
-    theme_light() +
-    theme(
-      legend.position="none",
-      plot.title = element_text(size=11),
-      axis.text.x = element_text(size = 8)) +
-    facet_grid(group~perspective) +
-    ggtitle("Boxplot with individual points for Duration of speaking time") +
-    xlab("")
-speaking.plot
-
-```
-
-### Eyetracking Data
-
-The Tobii Pro Lab 2 software was used to analyze the teachers' visual attetion during each mini-lesson.
-The software allows for non-screen based recordings of a participants’ attention while moving in real-world settings.
-The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video.
-In order to map multiple recordings to AOIs, we first imported the eye-tracking recordings into the Tobii Pro Analyzer software.
-Second, we created dynamic Areas of Interest (AOI) manually to plot the gaze data.
-Once the AOIs are created, the gaze recordings of multiple recordings can be mapped and analyzed in aggregated form.
-Tobii Pro does not allow to do AOI based analyses within Pro Lab.
-So we exported a tsv.
-file to do further analyses in the software R.
-
-#### Gaze relational index (GRI)
-
-The GRI is a measure of visual expertise in information processing.
-This metric is calculated as the ratio of mean fixation duration to fixation count.
-The GRI is higher for novices than for experts.
-[@gegenfurtner2020gaze]
-
-```{r GRItable, echo = FALSE}
-
-# prepare data (selected from questionnaire data)
-et.raw.data<-read.table("./data/Aperol_pilot_glasses_raw_fixation_saccades_metrics.tsv", dec=",", sep="\t", header=T)
-
-# converting integer to numeric
-et.raw.data <- et.raw.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.raw.table <- et.raw.data %>%
-  group_by(Participant, Variable) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-
-# format and insert table in manuscript
-apa_table(
-  et.raw.table,
-  caption = "Number and Duration (in msec) of Fixations",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
-
-```{r calibration phase TOI, echo = FALSE}
-
-# prepare data (selected from questionnaire data)
-et.calib.data<-read.table("./data/Aperol_pilot_glasses_raw_ALL_metrics_calib_without_AOI_snapshot.tsv", dec=",", sep="\t", header=T)
-
-# converting integer to numeric
-et.calib.data <- et.calib.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-# select relevant rows 
-et.calib.data <- et.calib.data %>% filter(TOI == "Calibration phase")
-
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.calib.table <- et.calib.data %>%
-  group_by(Participant, Variable1) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-
-# format and insert table in manuscript
-apa_table(
-  et.calib.table,
-  caption = "Number and Duration (in msec) of Fixations during calibration",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
-
-```{r Calib end to lession start TOI, echo = FALSE}
-
-# prepare data (selected from questionnaire data)
-et.calib.lesson.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_calib_end_lesson_start.tsv", dec=",", sep="\t", header=T)
-
-# converting integer to numeric
-et.calib.lesson.data <- et.calib.lesson.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-options(digits = 2)
-
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.calib.lesson.table <- et.calib.lesson.data %>%
-  group_by(Participant, Variable1) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-
-# format and insert table in manuscript
-apa_table(
-  et.calib.lesson.table,
-  caption = "Number and Duration (in msec) of Fixations Calibration End to Lesson Start",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
-
-```{r Disturbance "head on table" to first intervention, echo = FALSE}
-
-# prepare data (selected from questionnaire data)
-et.distub.head.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_head_on_table_session1.tsv", dec=",", sep="\t", header=T)
-
-# converting integer to numeric
-et.distub.head.data <- et.distub.head.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
-                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
-                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
-                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
-                                       )
-options(digits = 2)
-
-# calculate the GRI 
-# create a basic table (tibble) using tidyverse functions
-et.distub.head.table <- et.distub.head.data %>%
-  group_by(Participant, Variable1) %>%
-  summarise("Fixation Number" = Number_of_whole_fixations,
-            "Fixation Duration" = Total_duration_of_whole_fixations,
-            "M Duration Fixation" = Average_duration_of_whole_fixations,
-            "TOI" = Duration_of_interval,
-            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
-view(et.distub.head.data)
-
-# format and insert table in manuscript
-apa_table(
-  et.distub.head.table,
-  caption = "Number and Duration (in msec) of Fixations for Disturbance 'head on table' to first intervention",
-  # note = "Write Note here", 
-  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
-  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
-  )
-
-```
-
-#########################################
-
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-
-### Questionnaire Data
-
-### Behavioral Data
-
-### Eyetracking Data
-
-# Results
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-
-### Questionnaire Data
-
-### Behavioral Data
-
-### Eyetracking Data
-
-# Discussion
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-
-\newpage
-
-# References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup

### 2022-03-01 02_paper/01_pilot/paper_1_supplement_questionnaire.tex
r markdown method part

--- 2021-03-03 paper_1/paper_1_supplement_new_table.tex
@@
 \makeatother
-\shorttitle{Visual attention in teaching and learning processes}
+\shorttitle{Visual attention in teaching and learning processes - QUESTIONNAIRE DATA}
 \keywords{Professional Vision, Expert-Novice-Paradigm, Eye-Tracking\newline\indent Word count: 1949}
@@
 
-\hypertarget{behavioral-data}{%
-\subsubsection{Behavioral data}\label{behavioral-data}}
-
-The speech, sounds and voices were recorded with an audio recorder installed in the middle of the Lab.
-Movements, facial expressions and gestures of the subjects were recorded by four cameras from different angles.
-One camera was installed to film the class from the side.
-Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back.
-Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.
-
-\hypertarget{eyetracking-data}{%
-\subsubsection{Eyetracking data}\label{eyetracking-data}}
-
-A binocular Tobii Pro Glasses 2 eye-tracker consisting of a wearable head unit and a recording unit was used to record the eye movements of all 8 participants.
-The head unit is a measuring device with different sensitive sensors.
-A high-definition scene camera captures a full HD video and an integrated microphone records the surrounding sounds.
-Infrared light illuminators support the eye tracking sensors which record the eye orientation.
-The videos were recorded with a sampling rate of 50 Hz and a video resolution with 1920 x 1080 at 25 frames per second.
-The scene camera has a field of view of 90 deg.
-in 16:9 format (82 deg.
-horizontal and 52 deg.
-vertical) and has a frame dimension of 179 x 159 x 57mm (width x depth x height).
-The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
-
 \hypertarget{coding-data-preparation-reliability}{%
@@
 \end{table}
-
 \newpage
@@
 \def\labelenumi{(\arabic{enumi})}
-\tightlist
 \item
   Classroom management
-  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Line Plots Classroom Management-1.pdf}
+  \includegraphics{paper_1_supplement_questionnaire_files/figure-latex/Line Plots Classroom Management-1.pdf}
   \newpage
@@
   Positive climate and motivation
-  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Positive climate and motivation line plots-1.pdf}
+  \includegraphics{paper_1_supplement_questionnaire_files/figure-latex/Positive climate and motivation line plots-1.pdf}
   \newpage
@@
   Clarity and structuredness
-  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Clarity and structuredness line plots-1.pdf}
+  \includegraphics{paper_1_supplement_questionnaire_files/figure-latex/Clarity and structuredness line plots-1.pdf}
   \newpage
@@
   Activation and support
-  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Activation and support line plots-1.pdf}
+  \includegraphics{paper_1_supplement_questionnaire_files/figure-latex/Activation and support line plots-1.pdf}
   \newpage
+\item
+  Presence: posture and gaze
+  \includegraphics{paper_1_supplement_questionnaire_files/figure-latex/Presence posture and gaze line plots-1.pdf}
 \end{enumerate}
 
-\begin{figure}
-
-{\centering \includegraphics[width=5.33in]{./pictures/presenceposturegaze}
-
-}
-
-\caption{(5) Presence: posture/gaze}\label{fig:presenceposturegaze}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-
-{\centering \includegraphics[width=5.33in]{./pictures/presencevoice}
-
-}
-
-\caption{(6) Presence: voice}\label{fig:presencevoice}
-\end{figure}
-\newpage
-
-\begin{figure}
-
-{\centering \includegraphics[width=5.33in]{./pictures/presenceverbalnonverbalintervention}
-
-}
-
-\caption{(7) Presence: verbal and non-verbal intervention}\label{fig:presenceverbalnonverbalintervention}
-\end{figure}
 \newpage
@@
 \def\labelenumi{(\arabic{enumi})}
-\setcounter{enumi}{7}
-\tightlist
+\setcounter{enumi}{5}
 \item
-  Natural behaviour
-  \includegraphics{paper_1_supplement_new_table_files/figure-latex/Natural behaviour line plots-1.pdf}
+  Presence: voice
+  \includegraphics{paper_1_supplement_questionnaire_files/figure-latex/Presence voice line plots-1.pdf}
+  \newpage
+\item
+  Presence: verbal and non-verbal intervention
+\end{enumerate}
+
+\includegraphics{paper_1_supplement_questionnaire_files/figure-latex/Presence verbal and non-verbal intervention line plots-1.pdf}
+\newpage
+(8) Natural behaviour
+\includegraphics{paper_1_supplement_questionnaire_files/figure-latex/Natural behaviour line plots-1.pdf}
 \newpage
 In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
-\end{enumerate}
+
+\begin{verbatim}
+## Warning: Removed 1 rows containing non-finite values (stat_boxplot).
+\end{verbatim}
+
+\begin{verbatim}
+## Warning: Removed 1 rows containing missing values (geom_point).
+\end{verbatim}
 
@@
 \centering
-\includegraphics{paper_1_supplement_new_table_files/figure-latex/boxplot scales-1.pdf}
+\includegraphics{paper_1_supplement_questionnaire_files/figure-latex/boxplot scales-1.pdf}
 \caption{(\#fig:boxplot scales)Boxplots and individual data for experts and novices}
@@
 
-\newpage
-
-\hypertarget{behavioral-data-1}{%
-\subsubsection{Behavioral Data}\label{behavioral-data-1}}
-
-The recorded lessons were coded in a post-hoc procedure with the coding software MAXQDA by previously trained raters (Kuckartz \& Rädiker, 2019). The following coding scheme was developed:
-
-\begin{itemize}
-\item
-  phase - lesson begin, state event: teacher starts the lesson with a noise, talk, taking a position in class
-\item
-  phase - lesson end, state event: teacher finishes the lesson with a noise, talk, taking a position in class
-\item
-  phase - organization/transition points, state event: any situation that does not imply effective learning time (fetching chalk, working material, organizing desks, opening windows, printing work results etc.)
-\item
-  phase - single, state event: any individual student activity on a given task (reading, writing, drawing etc.)
-\item
-  phase - group, state event: any student activity on a given task together in a group of at least 3 students (reading, writing, drawing etc.)
-\item
-  phase - class discussion, state event: discussion in class, teacher talks to class/individual/group
-\item
-  phase - pair: state event: any student activity on a given task together in a team of 2 students (reading, writing, drawing etc.)
-\item
-  phase - teachers lecture, state event: any teacher's presentation on a certain topic which maybe supported by a PPP, PREZI, notes on board, OHP etc.
-\item
-  phase - other, state event: not categorizable
-\item
-  phase - break, state event: e.g.~drinking, relaxation exercises
-\item
-  phase - external interruption, state event: external interruptions (e.g.~fire alarm, technical problems, other teachers coming into the room)
-\item
-  speaking time - teacher, state event
-\item
-  speaking time - students, state event
-\item
-  disruption - chatting with neighbor, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - asking a question, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - yelling, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - looking at phone, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - staring out of window, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - drawing, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - head on table, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - clicking pen, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - drumming hands, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\item
-  disruption - walking around, state event (perceived/ not perceived, reacted: verbal, non-verbal/ not reacted)
-\end{itemize}
-
-First, we coded the speaking time of the teacher and the students to compare all perspectives: coder, observer, students, teacher.
-The graph below shows the result of the coded speaking duration compared to the estimated speaking duration assessed with the questionnaire.
-
-\includegraphics{paper_1_supplement_new_table_files/figure-latex/speaking plot-1.pdf}
-
-\hypertarget{eyetracking-data-1}{%
-\subsubsection{Eyetracking Data}\label{eyetracking-data-1}}
-
-The Tobii Pro Lab 2 software was used to analyze the teachers' visual attetion during each mini-lesson.
-The software allows for non-screen based recordings of a participants' attention while moving in real-world settings.
-The recordings of the glasses contain both HD-video from the subjects' perspective as well as the respective gaze data mapped onto the video.
-In order to map multiple recordings to AOIs, we first imported the eye-tracking recordings into the Tobii Pro Analyzer software.
-Second, we created dynamic Areas of Interest (AOI) manually to plot the gaze data.
-Once the AOIs are created, the gaze recordings of multiple recordings can be mapped and analyzed in aggregated form.
-Tobii Pro does not allow to do AOI based analyses within Pro Lab.
-So we exported a tsv.
-file to do further analyses in the software R.
-
-\hypertarget{gaze-relational-index-gri}{%
-\paragraph{Gaze relational index (GRI)}\label{gaze-relational-index-gri}}
-
-The GRI is a measure of visual expertise in information processing.
-This metric is calculated as the ratio of mean fixation duration to fixation count.
-The GRI is higher for novices than for experts.
-(Gegenfurtner et al., 2020)
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:GRItable}Number and Duration (in msec) of Fixations}
-
-\scriptsize{
-
-\begin{tabular}{lllllll}
-\toprule
-Participant & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
-\midrule
-01\_01\_D & Expert & 803.00 & 316,571.00 & 394.00 & 781,978.00 & 0.49\\
-01\_02\_A & Expert & 1,070.00 & 385,812.00 & 361.00 & 838,026.00 & 0.34\\
-01\_03\_B & Novice & 617.00 & 374,315.00 & 607.00 & 744,444.00 & 0.98\\
-01\_04\_C & Novice & 769.00 & 384,537.00 & 500.00 & 723,922.00 & 0.65\\
-02\_01\_A & Novice & 569.00 & 101,541.00 & 178.00 & 729,762.00 & 0.31\\
-02\_02\_B & Novice & 1,140.00 & 520,431.00 & 457.00 & 730,565.00 & 0.40\\
-02\_03\_C & Novice & 1,048.00 & 469,018.00 & 448.00 & 737,604.00 & 0.43\\
-02\_04\_D & Novice & 613.00 & 438,655.00 & 716.00 & 747,729.00 & 1.17\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:calibration phase TOI}Number and Duration (in msec) of Fixations during calibration}
-
-\scriptsize{
-
-\begin{tabular}{lllllll}
-\toprule
-Participant & \multicolumn{1}{c}{Variable1} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
-\midrule
-01\_01\_D & Expert & 9.00 & 14,372.00 & 1,597.00 & 16,470.00 & 177.44\\
-01\_02\_A & Expert & 10.00 & 10,194.00 & 1,019.00 & 13,335.00 & 101.90\\
-01\_03\_B & Novice & 17.00 & 9,234.00 & 543.00 & 10,615.00 & 31.94\\
-01\_04\_C & Novice & 14.00 & 15,311.00 & 1,094.00 & 17,224.00 & 78.14\\
-02\_01\_A & Novice & 13.00 & 5,157.00 & 397.00 & 17,902.00 & 30.54\\
-02\_02\_B & Novice & 12.00 & 10,654.00 & 888.00 & 12,325.00 & 74.00\\
-02\_03\_C & Novice & 18.00 & 14,151.00 & 786.00 & 16,494.00 & 43.67\\
-02\_04\_D & Novice & 14.00 & 19,128.00 & 1,366.00 & 20,964.00 & 97.57\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:Calib end to lession start TOI}Number and Duration (in msec) of Fixations Calibration End to Lesson Start}
-
-\scriptsize{
-
-\begin{tabular}{lllllll}
-\toprule
-Participant & \multicolumn{1}{c}{Variable1} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
-\midrule
-01\_01\_D & Expert & 101.00 & 38,177.00 & 378.00 & 53,133.00 & 3.74\\
-01\_02\_A & Expert & 27.00 & 6,736.00 & 249.00 & 15,502.00 & 9.22\\
-01\_03\_B & Novice & 57.00 & 36,378.00 & 638.00 & 58,763.00 & 11.19\\
-01\_04\_C & Novice & 65.00 & 22,387.00 & 344.00 & 39,235.00 & 5.29\\
-02\_01\_A & Novice & 14.00 & 2,619.00 & 187.00 & 30,195.00 & 13.36\\
-02\_02\_B & Novice & 46.00 & 15,851.00 & 345.00 & 30,297.00 & 7.50\\
-02\_03\_C & Novice & 86.00 & 27,643.00 & 321.00 & 42,603.00 & 3.73\\
-02\_04\_D & Novice & 53.00 & 27,783.00 & 524.00 & 36,204.00 & 9.89\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[h]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:Disturbance "head on table" to first intervention}Number and Duration (in msec) of Fixations for Disturbance 'head on table' to first intervention}
-
-\scriptsize{
-
-\begin{tabular}{lllllll}
-\toprule
-Participant & \multicolumn{1}{c}{Variable1} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
-\midrule
-01\_01\_D & Expert & 3.00 & 2,079.00 & 693.00 & 5,735.00 & 231.00\\
-01\_02\_A & Expert & 7.00 & 2,778.00 & 397.00 & 8,454.00 & 56.71\\
-01\_03\_B & Novice & 1.00 & 460.00 & 460.00 & 3,493.00 & 460.00\\
-01\_04\_C & Novice & 29.00 & 12,653.00 & 436.00 & 16,245.00 & 15.03\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
-
-We used R {[}Version 4.0.3; R Core Team (2019){]} and the R-packages \emph{\}dplyr} {[}@\}R-dplyr{]}, \emph{corrplot2017} (Wei \& Simko, 2017), \emph{forcats} {[}Version 0.5.0; Wickham (2020a){]}, \emph{Formula} {[}Version 1.2.4; Zeileis and Croissant (2010){]}, \emph{ggplot2} {[}Version 3.3.2; Wickham (2016){]}, \emph{Hmisc} {[}Version 4.4.2; Harrell Jr, Charles Dupont, and others.
-(2020){]}, \emph{lattice} {[}Version 0.20.41; Sarkar (2008){]}, \emph{moments} {[}Version 0.14; Komsta and Novomestky (2015){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{papayar} (Muschelli, 2016), \emph{psych} {[}Version 2.0.12; Revelle (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham, Hester, and Francois (2018){]}, \emph{sjPlot} {[}Version 2.8.7; Lüdecke (2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{survival} {[}Version 3.2.7; Terry M.
-Therneau and Patricia M.
-Grambsch (2000){]}, \emph{tibble} {[}Version 3.0.4; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.2; Wickham (2020b){]}, and \emph{tidyverse} {[}Version 1.3.0; Wickham et al.
-(2019){]} for all our analyses.
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-
-\hypertarget{questionnaire-data-2}{%
-\subsubsection{Questionnaire Data}\label{questionnaire-data-2}}
-
-\hypertarget{behavioral-data-2}{%
-\subsubsection{Behavioral Data}\label{behavioral-data-2}}
-
-\hypertarget{eyetracking-data-2}{%
-\subsubsection{Eyetracking Data}\label{eyetracking-data-2}}
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-
-\hypertarget{questionnaire-data-3}{%
-\subsubsection{Questionnaire Data}\label{questionnaire-data-3}}
-
-\hypertarget{behavioral-data-3}{%
-\subsubsection{Behavioral Data}\label{behavioral-data-3}}
-
-\hypertarget{eyetracking-data-3}{%
-\subsubsection{Eyetracking Data}\label{eyetracking-data-3}}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua.
-At vero eos et accusam et justo duo dolores et ea rebum.
-Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
 \hypertarget{refs}{}
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
-
 \leavevmode\hypertarget{ref-barnes2004significance}{}%
@@
 
-\leavevmode\hypertarget{ref-gegenfurtner2020gaze}{}%
-Gegenfurtner, A., Boucheix, J.-M., Gruber, H., Hauser, F., Lehtinen, E., \& Lowe, R.
-K.
-(2020).
-The gaze relational index as a measure of visual expertise.
-\emph{Journal of Expertise.
-East Lansing, Michigan: Michigan State University, 2020, Vol.
-3, Iss.
-1}.
-
-\leavevmode\hypertarget{ref-R-Hmisc}{}%
-Harrell Jr, F. E., Charles Dupont, with contributions from, \& others., many. (2020). \emph{Hmisc: Harrell miscellaneous}. Retrieved from \url{https://CRAN.R-project.org/package=Hmisc}
-
 \leavevmode\hypertarget{ref-helmke2014unterrichtsdiagnostik}{}%
@@
 \emph{Aus-Und Fortbildung Der Lehrkr{ä}fte in Hinblick Auf Verbesserung Der Diagnosef{ä}higkeit, Umgang Mit Heterogenit{ä}t Und Individuelle F{ö}rderung}, 149--163.
-
-\leavevmode\hypertarget{ref-R-purrr}{}%
-Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
 
@@
 
-\leavevmode\hypertarget{ref-R-moments}{}%
-Komsta, L., \& Novomestky, F. (2015). \emph{Moments: Moments, cumulants, skewness, kurtosis and related tests}. Retrieved from \url{https://CRAN.R-project.org/package=moments}
-
 \leavevmode\hypertarget{ref-kounin2006techniken}{}%
 Kounin, J. S. (2006). \emph{Techniken der klassenf{ü}hrung}. Waxmann Verlag.
-
-\leavevmode\hypertarget{ref-kuckartz2019analyzing}{}%
-Kuckartz, U., \& Rädiker, S. (2019). \emph{Analyzing qualitative data with MAXQDA}. Springer.
 
@@
 
-\leavevmode\hypertarget{ref-R-sjPlot}{}%
-Lüdecke, D. (2021). \emph{sjPlot: Data visualization for statistics in social science}. Retrieved from \url{https://CRAN.R-project.org/package=sjPlot}
-
 \leavevmode\hypertarget{ref-marzano2007art}{}%
@@
 
-\leavevmode\hypertarget{ref-R-papayar}{}%
-Muschelli, J. (2016). \emph{Papayar: View medical research images using the papaya JavaScript library}. Retrieved from \url{https://CRAN.R-project.org/package=papayar}
-
-\leavevmode\hypertarget{ref-R-tibble}{}%
-Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
-
 \leavevmode\hypertarget{ref-nolting2012storungen}{}%
@@
 Pouta, M., Lehtinen, E., \& Palonen, T. (2020). Student teachers' and experienced teachers' professional vision of students' understanding of the rational number concept.
-
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
-
-\leavevmode\hypertarget{ref-R-psych}{}%
-Revelle, W.
-(2020).
-\emph{Psych: Procedures for psychological, psychometric, and personality research}.
-Evanston, Illinois: Northwestern University.
-Retrieved from \url{https://CRAN.R-project.org/package=psych}
-
-\leavevmode\hypertarget{ref-R-lattice}{}%
-Sarkar, D. (2008). \emph{Lattice: Multivariate data visualization with r}. New York: Springer. Retrieved from \url{http://lmdvr.r-forge.r-project.org}
 
@@
 
-\leavevmode\hypertarget{ref-R-survival-book}{}%
-Terry M. Therneau, \& Patricia M. Grambsch. (2000). \emph{Modeling survival data: Extending the {C}ox model}. New York: Springer.
-
-\leavevmode\hypertarget{ref-R-corrplot2017}{}%
-Wei, T., \& Simko, V. (2017). \emph{R package "corrplot": Visualization of a correlation matrix}. Retrieved from \url{https://github.com/taiyun/corrplot}
-
-\leavevmode\hypertarget{ref-R-ggplot2}{}%
-Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
-
-\leavevmode\hypertarget{ref-R-stringr}{}%
-Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
-
-\leavevmode\hypertarget{ref-R-forcats}{}%
-Wickham, H. (2020a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
-
-\leavevmode\hypertarget{ref-R-tidyr}{}%
-Wickham, H. (2020b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
-
-\leavevmode\hypertarget{ref-R-tidyverse}{}%
-Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
-D., François, R., \ldots{} Yutani, H.
-(2019).
-Welcome to the {tidyverse}.
-\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
-\url{https://doi.org/10.21105/joss.01686}
-
-\leavevmode\hypertarget{ref-R-readr}{}%
-Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
-
 \leavevmode\hypertarget{ref-wolff2017see}{}%
@@
 
-\leavevmode\hypertarget{ref-R-Formula}{}%
-Zeileis, A., \& Croissant, Y.
-(2010).
-Extended model formulas in {R}: Multiple parts and multiple responses.
-\emph{Journal of Statistical Software}, \emph{34}(1), 1--13.
-\url{https://doi.org/10.18637/jss.v034.i01}
-
 \end{CSLReferences}
 
-\endgroup
-
 \end{document}

### 2022-03-01 02_paper/01_pilot/schrott/paper_1_supplement.Rmd
r markdown method part

--- 2021-01-29 paper_1/paper_1_supplement_with_presence.Rmd
@@
 
-(ref:datacollection-caption) Example for set up during a mini-lesson
+(ref:data_collection-caption) Example for the set up during a mini-lesson
 
-```{r datacollection, fig.cap = "(ref:datacollection-caption)", fig.align = "center", echo = FALSE}
+```{r data collection, fig.cap = "(ref:data_collection-caption)", fig.align = "center", echo = FALSE}
 
-knitr::include_graphics("./pictures/datacollection.png", dpi = 108)
+knitr::include_graphics("./pictures/data_collection.png", dpi = 108)
 

### 2022-03-01 02_paper/01_pilot/schrott/paper_1_supplement_new_table.tex
r markdown method part

--- 2021-03-03 paper_1/paper_1_supplement_new_table.tex
@@
 
-\caption{\label{tab:GRItable}Number and Duration (in msec) of Fixations}
-
-\scriptsize{
-
-\begin{tabular}{lllllll}
+\caption{\label{tab:GRItable1}GRI}
+
+\tiny{
+
+\begin{tabular}{lllllllll}
 \toprule
-Participant & \multicolumn{1}{c}{Variable} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
+TOI & \multicolumn{1}{c}{ID} & \multicolumn{1}{c}{Group} & \multicolumn{1}{c}{Duration TOI ms} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{Number Fixation} & \multicolumn{1}{c}{Time TOI Duration} & \multicolumn{1}{c}{Old GRI} & \multicolumn{1}{c}{New GRI}\\
 \midrule
-01\_01\_D & Expert & 803.00 & 316,571.00 & 394.00 & 781,978.00 & 0.49\\
-01\_02\_A & Expert & 1,070.00 & 385,812.00 & 361.00 & 838,026.00 & 0.34\\
-01\_03\_B & Novice & 617.00 & 374,315.00 & 607.00 & 744,444.00 & 0.98\\
-01\_04\_C & Novice & 769.00 & 384,537.00 & 500.00 & 723,922.00 & 0.65\\
-02\_01\_A & Novice & 569.00 & 101,541.00 & 178.00 & 729,762.00 & 0.31\\
-02\_02\_B & Novice & 1,140.00 & 520,431.00 & 457.00 & 730,565.00 & 0.40\\
-02\_03\_C & Novice & 1,048.00 & 469,018.00 & 448.00 & 737,604.00 & 0.43\\
-02\_04\_D & Novice & 613.00 & 438,655.00 & 716.00 & 747,729.00 & 1.17\\
+Asking question & 01\_04\_C & Novice & 3,869.00 & 2,925.62 & 3.00 & 1.32 & 975.21 & 0.44\\
+Asking question & 01\_02\_A & Expert & 7,112.00 & 2,925.62 & 13.00 & 2.43 & 225.05 & 0.19\\
+Asking question & 01\_03\_B & Novice & 12,863.00 & 2,925.62 & 4.00 & 4.40 & 731.41 & 1.10\\
+Asking question & 01\_01\_D & Expert & 7,648.00 & 2,925.62 & 7.00 & 2.61 & 417.95 & 0.37\\
+Asking question & 02\_01\_A & Novice & 7,422.00 & 2,925.62 & 3.00 & 2.54 & 975.21 & 0.85\\
+Asking question & 02\_02\_B & Novice & 7,082.00 & 2,925.62 & 9.00 & 2.42 & 325.07 & 0.27\\
+Asking question & 02\_03\_C & Novice & 8,045.00 & 2,925.62 & 8.00 & 2.75 & 365.70 & 0.34\\
+Asking question & 02\_04\_D & Novice & 6,595.00 & 2,925.62 & 6.00 & 2.25 & 487.60 & 0.38\\
+Calibration phase & 01\_04\_C & Novice & 17,224.00 & 12,275.12 & 14.00 & 1.40 & 876.79 & 0.10\\
+Calibration phase & 01\_02\_A & Expert & 13,335.00 & 12,275.12 & 10.00 & 1.09 & 1,227.51 & 0.11\\
+Calibration phase & 01\_03\_B & Novice & 10,615.00 & 12,275.12 & 17.00 & 0.86 & 722.07 & 0.05\\
+Calibration phase & 01\_01\_D & Expert & 16,470.00 & 12,275.12 & 9.00 & 1.34 & 1,363.90 & 0.15\\
+Calibration phase & 02\_01\_A & Novice & 17,902.00 & 12,275.12 & 13.00 & 1.46 & 944.24 & 0.11\\
+Calibration phase & 02\_02\_B & Novice & 12,325.00 & 12,275.12 & 12.00 & 1.00 & 1,022.93 & 0.08\\
+Calibration phase & 02\_03\_C & Novice & 16,494.00 & 12,275.12 & 18.00 & 1.34 & 681.95 & 0.07\\
+Calibration phase & 02\_04\_D & Novice & 20,964.00 & 12,275.12 & 14.00 & 1.71 & 876.79 & 0.12\\
+Chatting with neighbour & 01\_04\_C & Novice & 9,843.00 & 4,070.12 & 27.00 & 2.42 & 150.75 & 0.09\\
+Chatting with neighbour & 01\_02\_A & Expert & 2,607.00 & 4,070.12 & 1.00 & 0.64 & 4,070.12 & 0.64\\
+Chatting with neighbour & 01\_03\_B & Novice & 11,060.00 & 4,070.12 & 10.00 & 2.72 & 407.01 & 0.27\\
+Chatting with neighbour & 01\_01\_D & Expert & 6,612.00 & 4,070.12 & 3.00 & 1.62 & 1,356.71 & 0.54\\
+Chatting with neighbour & 02\_01\_A & Novice & 7,429.00 & 4,070.12 & 5.00 & 1.83 & 814.02 & 0.37\\
+Chatting with neighbour & 02\_02\_B & Novice & 8,397.00 & 4,070.12 & 11.00 & 2.06 & 370.01 & 0.19\\
+Chatting with neighbour & 02\_03\_C & Novice & 11,713.00 & 4,070.12 & 11.00 & 2.88 & 370.01 & 0.26\\
+Chatting with neighbour & 02\_04\_D & Novice & 11,443.00 & 4,070.12 & 4.00 & 2.81 & 1,017.53 & 0.70\\
+Clicking pen & 01\_04\_C & Novice & 12,980.00 & 8,809.75 & 4.00 & 1.47 & 2,202.44 & 0.37\\
+Clicking pen & 01\_02\_A & Expert & 12,071.00 & 8,809.75 & 20.00 & 1.37 & 440.49 & 0.07\\
+Clicking pen & 01\_03\_B & Novice & 26,272.00 & 8,809.75 & 16.00 & 2.98 & 550.61 & 0.19\\
+Clicking pen & 01\_01\_D & Expert & 11,597.00 & 8,809.75 & 11.00 & 1.32 & 800.89 & 0.12\\
+Clicking pen & 02\_01\_A & Novice & 16,114.00 & 8,809.75 & 11.00 & 1.83 & 800.89 & 0.17\\
+Clicking pen & 02\_02\_B & Novice & 9,409.00 & 8,809.75 & 12.00 & 1.07 & 734.15 & 0.09\\
+Clicking pen & 02\_03\_C & Novice & 16,269.00 & 8,809.75 & 27.00 & 1.85 & 326.29 & 0.07\\
+Clicking pen & 02\_04\_D & Novice & 24,220.00 & 8,809.75 & 19.00 & 2.75 & 463.67 & 0.14\\
+Drawing on paper & 01\_04\_C & Novice & 39,979.00 & 34,414.38 & 27.00 & 1.16 & 1,274.61 & 0.04\\
+Drawing on paper & 01\_02\_A & Expert & 44,971.00 & 34,414.38 & 87.00 & 1.31 & 395.57 & 0.02\\
+Drawing on paper & 01\_03\_B & Novice & 129,708.00 & 34,414.38 & 79.00 & 3.77 & 435.62 & 0.05\\
+Drawing on paper & 01\_01\_D & Expert & 74,511.00 & 34,414.38 & 92.00 & 2.17 & 374.07 & 0.02\\
+Drawing on paper & 02\_01\_A & Novice & 43,469.00 & 34,414.38 & 31.00 & 1.26 & 1,110.14 & 0.04\\
+Drawing on paper & 02\_02\_B & Novice & 147,788.00 & 34,414.38 & 295.00 & 4.29 & 116.66 & 0.01\\
+Drawing on paper & 02\_03\_C & Novice & 26,495.00 & 34,414.38 & 46.00 & 0.77 & 748.14 & 0.02\\
+Drawing on paper & 02\_04\_D & Novice & 27,915.00 & 34,414.38 & 11.00 & 0.81 & 3,128.58 & 0.07\\
+Drumming hands & 01\_04\_C & Novice & 43,507.00 & 11,415.88 & 41.00 & 3.81 & 278.44 & 0.09\\
+Drumming hands & 01\_02\_A & Expert & 20,530.00 & 11,415.88 & 27.00 & 1.80 & 422.81 & 0.07\\
+Drumming hands & 01\_03\_B & Novice & 12,615.00 & 11,415.88 & 6.00 & 1.11 & 1,902.65 & 0.18\\
+Drumming hands & 01\_01\_D & Expert & 23,121.00 & 11,415.88 & 17.00 & 2.03 & 671.52 & 0.12\\
+Drumming hands & 02\_01\_A & Novice & 62,326.00 & 11,415.88 & 50.00 & 5.46 & 228.32 & 0.11\\
+Drumming hands & 02\_02\_B & Novice & 24,699.00 & 11,415.88 & 25.00 & 2.16 & 456.64 & 0.09\\
+Drumming hands & 02\_03\_C & Novice & 27,775.00 & 11,415.88 & 49.00 & 2.43 & 232.98 & 0.05\\
+Drumming hands & 02\_04\_D & Novice & 14,998.00 & 11,415.88 & 9.00 & 1.31 & 1,268.43 & 0.15\\
+Looking at phone & 01\_04\_C & Novice & 7,984.00 & 11,563.00 & 8.00 & 0.69 & 1,445.38 & 0.09\\
+Looking at phone & 01\_02\_A & Expert & 19,897.00 & 11,563.00 & 28.00 & 1.72 & 412.96 & 0.06\\
+Looking at phone & 01\_03\_B & Novice & 40,427.00 & 11,563.00 & 30.00 & 3.50 & 385.43 & 0.12\\
+Looking at phone & 01\_01\_D & Expert & 32,387.00 & 11,563.00 & 29.00 & 2.80 & 398.72 & 0.10\\
+Looking at phone & 02\_01\_A & Novice & 33,557.00 & 11,563.00 & 14.00 & 2.90 & 825.93 & 0.21\\
+Looking at phone & 02\_02\_B & Novice & 16,321.00 & 11,563.00 & 19.00 & 1.41 & 608.58 & 0.07\\
+Looking at phone & 02\_03\_C & Novice & 28,223.00 & 11,563.00 & 47.00 & 2.44 & 246.02 & 0.05\\
+Looking at phone & 02\_04\_D & Novice & 31,944.00 & 11,563.00 & 19.00 & 2.76 & 608.58 & 0.15\\
+Putting head on table & 01\_04\_C & Novice & 20,929.00 & 17,049.88 & 38.00 & 1.23 & 448.68 & 0.03\\
+Putting head on table & 01\_02\_A & Expert & 23,402.00 & 17,049.88 & 27.00 & 1.37 & 631.48 & 0.05\\
+Putting head on table & 01\_03\_B & Novice & 39,159.00 & 17,049.88 & 41.00 & 2.30 & 415.85 & 0.06\\
+Putting head on table & 01\_01\_D & Expert & 6,354.00 & 17,049.88 & 4.00 & 0.37 & 4,262.47 & 0.09\\
+Putting head on table & 02\_01\_A & Novice & 51,225.00 & 17,049.88 & 45.00 & 3.00 & 378.89 & 0.07\\
+Putting head on table & 02\_02\_B & Novice & 11,322.00 & 17,049.88 & 20.00 & 0.66 & 852.49 & 0.03\\
+Putting head on table & 02\_03\_C & Novice & 61,713.00 & 17,049.88 & 81.00 & 3.62 & 210.49 & 0.04\\
+Putting head on table & 02\_04\_D & Novice & 57,484.00 & 17,049.88 & 42.00 & 3.37 & 405.95 & 0.08\\
+Yelling & 01\_04\_C & Novice & 6,083.00 & 889.50 & 1.00 & 6.84 & 889.50 & 6.84\\
+Yelling & 01\_02\_A & Expert & 1,995.00 & 889.50 & 1.00 & 2.24 & 889.50 & 2.24\\
+Yelling & 01\_03\_B & Novice & 6,527.00 & 889.50 & 1.00 & 7.34 & 889.50 & 7.34\\
+Yelling & 01\_01\_D & Expert & 2,245.00 & 889.50 & 1.00 & 2.52 & 889.50 & 2.52\\
+Yelling & 02\_01\_A & Novice & 9,105.00 & 889.50 & 7.00 & 10.24 & 127.07 & 1.46\\
+Yelling & 02\_02\_B & Novice & 2,548.00 & 889.50 & 5.00 & 2.86 & 177.90 & 0.57\\
+Yelling & 02\_03\_C & Novice & 2,992.00 & 889.50 & 2.00 & 3.36 & 444.75 & 1.68\\
+Yelling & 02\_04\_D & Novice & 12,416.00 & 889.50 & 1.00 & 13.96 & 889.50 & 13.96\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:GRItable2}GRI}
+
+\tiny{
+
+\begin{tabular}{lllllllll}
+\toprule
+Variable1 & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{M Fixation Duration} & \multicolumn{1}{c}{M Number Fixation} & \multicolumn{1}{c}{M TOI} & \multicolumn{1}{c}{M Old GRI} & \multicolumn{1}{c}{SD Old GRI} & \multicolumn{1}{c}{M New GRI} & \multicolumn{1}{c}{SD New GRI}\\
+\midrule
+Expert & Asking question & 2,108.50 & 10.00 & 7,380.00 & 231.70 & 98.30 & 0.39 & 0.18\\
+Expert & Calibration phase & 12,283.00 & 9.50 & 14,902.50 & 1,296.54 & 96.50 & 0.13 & 0.03\\
+Expert & Chatting with neighbour & 1,829.00 & 2.00 & 4,609.50 & 1,219.33 & 862.20 & 1.32 & 0.16\\
+Expert & Clicking pen & 5,416.50 & 15.50 & 11,834.00 & 381.62 & 156.68 & 0.15 & 0.06\\
+Expert & Drawing on paper & 25,514.50 & 89.50 & 59,741.00 & 285.30 & 11.27 & 0.03 & 0.01\\
+Expert & Drumming hands & 8,405.00 & 22.00 & 21,825.50 & 402.85 & 129.48 & 0.13 & 0.05\\
+Expert & Looking at phone & 8,484.50 & 28.50 & 26,142.00 & 297.79 & 7.39 & 0.11 & 0.03\\
+Expert & Putting head on table & 7,605.50 & 15.50 & 14,878.00 & 1,091.53 & 1,145.29 & 0.16 & 0.07\\
+Expert & Yelling & 580.00 & 1.00 & 2,120.00 & 580.00 & 0.00 & 3.66 & 0.30\\
+Novice & Asking question & 3,198.00 & 5.50 & 7,646.00 & 703.26 & 320.81 & 0.51 & 0.30\\
+Novice & Calibration phase & 12,272.50 & 14.67 & 15,920.67 & 853.95 & 130.15 & 0.09 & 0.03\\
+Novice & Chatting with neighbour & 4,817.17 & 11.33 & 9,980.83 & 617.28 & 384.64 & 0.26 & 0.18\\
+Novice & Clicking pen & 9,940.83 & 14.83 & 17,544.00 & 955.00 & 774.90 & 0.15 & 0.09\\
+Novice & Drawing on paper & 37,381.00 & 81.50 & 69,225.67 & 1,233.52 & 1,156.72 & 0.04 & 0.02\\
+Novice & Drumming hands & 12,419.50 & 30.00 & 30,986.67 & 791.90 & 760.35 & 0.10 & 0.04\\
+Novice & Looking at phone & 12,589.17 & 22.83 & 26,409.33 & 747.59 & 459.89 & 0.10 & 0.05\\
+Novice & Putting head on table & 20,198.00 & 44.50 & 40,305.33 & 535.53 & 252.70 & 0.04 & 0.02\\
+Novice & Yelling & 992.67 & 2.83 & 6,611.83 & 635.78 & 409.08 & 4.76 & 4.60\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:GRItable3}GRI}
+
+\tiny{
+
+\begin{tabular}{llllllll}
+\toprule
+Variable1 & \multicolumn{1}{c}{M Fixation Duration} & \multicolumn{1}{c}{M Number Fixation} & \multicolumn{1}{c}{M TOI} & \multicolumn{1}{c}{M Old GRI} & \multicolumn{1}{c}{SD Old GRI} & \multicolumn{1}{c}{M New GRI} & \multicolumn{1}{c}{SD New GRI}\\
+\midrule
+Expert & 8,025.17 & 21.50 & 18,159.17 & 1,953.05 & 2,871.09 & 0.16 & 0.08\\
+Novice & 12,645.43 & 25.33 & 24,958.93 & 1,878.32 & 2,902.64 & 0.13 & 0.15\\
 \bottomrule

### 2022-03-01 02_paper/02_study/paper_methods.Rmd
r markdown method part

--- 2022-03-01 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
@@
 authornote: |
-  Ethics Approval 
-All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board.
+
+  Ethics Approval: All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board.
 The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
 
-  Consent to Participate
-All participants gave informed consent.
+  Consent to Participate: All participants gave informed consent.
 
@@
 ```{r setup, include = FALSE}
+knitr::opts_chunk$set(include = FALSE)
 library("papaja")
@@
 
-```{r analysis-preferences}
+```{r analysis-preferences, include=FALSE}
 # Seed for random number generation
@@
 
-# Packages
-
-```{r}
+```{r include=FALSE}
 #install.packages("needs")
@@
 ```
+
+```{r data, include=FALSE}
+# load data files
+
+```
+
+# Introduction
+
+Managing classroom disruptions is a crucial aspect of effective classroom management (@evertson2006classroom; @kounin2006techniken).
+
+Accordingly, teachers must be able to quickly notice and appropriately react to significant events in the classroom.
+This ability is referred to as classroom professional vision (@goodwin2015professional; @sherin2007development).
+
+The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (“noticing”) and applying knowledge to draw appropriate conclusions in these situations (“knowledge-based reasoning”; @seidel2014modeling).
+
+Therefore, the early visual perception of classroom disruptions is a key component to effectively maximize students’ learning time and minimize classroom interruptions.
+According to Kounin (2006), these important classroom management strategies are called “withitness” and “overlapping” and can be summarized under the concept of monitoring (@gold2017using).
+
+Learning to develop such classroom management skills is a demanding and complex task for student teachers (@wolff2016teacher).
+Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, “[…] whereas only a few studies have focused on the basal process of noticing, i.e.
+the recognition of possible disturbing situations” (@grub2020process, p.75).
+Mobile eye-tracking data can fill this research gap by providing new insights in how expertise differences in teacher´s professional vision manifest in teacher-student interactions (@lachner2016makes; @@wolff2016teacher).
+
+# Research Questions
+
+This study examined how the degree of teaching experience influences (a) the number of fixations on relevant areas (e.g., the student performing the disruption), (b) the fixation duration in relevant areas and (c) the time to first fixation on relevant areas, using mobile eye-tracking data in a controlled, micro-teaching setting.
+Based on the existing literature, we expect expert teachers to outperform novices by (H1) showing more fixations on relevant areas with (H2) shorter fixation durations and (H3) perceiving classroom disruptions faster (cf.
+@van2014first).
 
@@
 
-# changing gender female 2 = 0 
-demo.data$Gender = ifelse(demo.data$Gender == 2, "0","1")
+# changing gender female 1 = 0
+demo.data$Gender = ifelse(demo.data$Gender == 2, "1","0")
 
@@
 demo.data$Gender <- as.numeric(demo.data$Gender)
+
+# creating new column with percentage of gender
 
@@
   summarise(N=n(),
-            "Gender male" = round(100 * n() / nrow(Gende)), 2,
-            "M Age" = round(mean(Age), 2),
-            "Min Age" = min(Age),
-            "Max Age" = max(Age),
-            "SD Age" = round(sd(Age), 2),
-            "M Exp." = round(mean(`Teaching Experience`), 2),
-            "Min Exp." = min(`Teaching Experience`),
-            "Max Exp." = max(`Teaching Experience`),
-            "SD Exp." = round(sd(`Teaching Experience`), 2),
+            "Gender female" = sum(Gender),
+            "M Age in years" = round(mean(Age), 0),
+            "SD Age in years" = round(sd(Age), 0),
+            "Min Age in years" = min(Age),
+            "Max Age in years" = max(Age),
+            "M Exp. in years" = round(mean(`Teaching Experience`), 0),
+            "SD Exp. in years" = round(sd(`Teaching Experience`), 0),
+            "Min Exp. in years" = min(`Teaching Experience`),
+            "Max Exp.in years" = max(`Teaching Experience`),
            )
@@
 ```
+
+The planned sample consists of *n* = 40 experts (teacher training completed, active in the teaching profession) and *n* = 40 novices (student teachers, first internship completed).
+
+The currently ongoing data collection already yielded data from *n* = `r length(demo.data$Group=="Expert")` experts and
+
+*n* = r nrow(demo.data[demo.data$Group == "Novice",]) novices.
+
+Participants Teachers were primarily recruited through personal contacts
 

### 2022-03-01 02_paper/01_pilot/schrott/AOI_plots.R

@@ -1,0 +1,105 @@
+
+if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
+if (!require(papaja)) install.packages('papaja'); library(papaja)
+if (!require(psych)) install.packages('psych'); library(psych) # stats
+if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
+if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
+
+# prepare data (selected from AOI data)
+et.raw.data<-read.table("./data/Aperol_pilot_glasses_AOI.txt", dec=",", sep="\t", header=T) 
+
+# convert into numeric
+et.raw.data <- et.raw.data %>%  mutate(Total.duration.of.fixation.in.AOI..sec. = as.numeric(Total.duration.of.fixation.in.AOI..sec.),
+                                       Average.duration.of.fixation.in.AOI..sec. = as.numeric(Average.duration.of.fixation.in.AOI..sec.),
+                                       Number.of.fixations.in.AOI = as.numeric (Number.of.fixations.in.AOI),
+                                       Total.Time.of.Interest.Duration..sec. = as.numeric(Total.Time.of.Interest.Duration..sec.))
+
+
+# create a basic table (tibble) using tidyverse functions for all disruptions 
+# Change Number of Digits in Global R Options to reduce the number of digits after the decimal point to two
+options(digits = 2)              
+
+et.table <- et.raw.data %>%
+  group_by(Type.of.disruption, Group) %>%
+  filter(Type.of.disruption != "staring out the window") %>%
+  rename ('Type of Disruption' = Type.of.disruption) %>%
+  summarise("Mean Duration of Fixations" = mean(Total.duration.of.fixation.in.AOI..sec.),
+            "Number of Fixations" = mean(Number.of.fixations.in.AOI),
+            "TOI" = mean(Total.Time.of.Interest.Duration..sec.))
+  
+
+# create a new column with name Total that gives the sum duration in sec of looking at all AOIs
[…]

### 2022-03-01 02_paper/schrott/AOI_plots.R

@@ -1,105 +1,0 @@
-
-if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)
-if (!require(papaja)) install.packages('papaja'); library(papaja)
-if (!require(psych)) install.packages('psych'); library(psych) # stats
-if (!require(moments)) install.packages('moments'); library(moments) # skewness & kurtosis
-if (!require(sjPlot)) install.packages('sjPlot'); library(sjPlot) # item analysis of a scale or index
-
-# suppress "summarize" info. 
-# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
-options(dplyr.summarise.inform = FALSE)
-
-# prepare data (selected from AOI data)
-et.raw.data<-read.table("./data/Aperol_pilot_glasses_AOI.txt", dec=",", sep="\t", header=T) 
-
-# convert into numeric
-et.raw.data <- et.raw.data %>%  mutate(Total.duration.of.fixation.in.AOI..sec. = as.numeric(Total.duration.of.fixation.in.AOI..sec.),
-                                       Average.duration.of.fixation.in.AOI..sec. = as.numeric(Average.duration.of.fixation.in.AOI..sec.),
-                                       Number.of.fixations.in.AOI = as.numeric (Number.of.fixations.in.AOI),
-                                       Total.Time.of.Interest.Duration..sec. = as.numeric(Total.Time.of.Interest.Duration..sec.))
-
-
-# create a basic table (tibble) using tidyverse functions for all disruptions 
-# Change Number of Digits in Global R Options to reduce the number of digits after the decimal point to two
-options(digits = 2)              
-
-et.table <- et.raw.data %>%
-  group_by(Type.of.disruption, Group) %>%
-  filter(Type.of.disruption != "staring out the window") %>%
-  rename ('Type of Disruption' = Type.of.disruption) %>%
-  summarise("Mean Duration of Fixations" = mean(Total.duration.of.fixation.in.AOI..sec.),
-            "Number of Fixations" = mean(Number.of.fixations.in.AOI),
-            "TOI" = mean(Total.Time.of.Interest.Duration..sec.))
-  
-
-# create a new column with name Total that gives the sum duration in sec of looking at all AOIs
[…]

### 2022-03-01 02_paper/schrott/install packages.R

@@ -1,15 +1,0 @@
-
-# installing packages
-
-if(!"tinytex" %in% rownames(installed.packages())) install.packages("tinytex")
-
-tinytex::install_tinytex()
-
-# Install devtools package if necessary
-if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
-
-# Install the stable development verions from GitHub
-devtools::install_github("crsh/papaja")
-
-# Install the latest development snapshot from GitHub
-devtools::install_github("crsh/papaja@devel")

### 2022-03-04 02_paper/02_study/paper_methods.Rmd
update begleitschreiben

@@
 
-```{r demographicstable, echo = FALSE}
+```{r demographicstable}
 
@@
 
-The currently ongoing data collection already yielded data from *n* = `r length(demo.data$Group=="Expert")` experts and
-
-*n* = r nrow(demo.data[demo.data$Group == "Novice",]) novices.
+The currently ongoing data collection already yielded data from *n* = `r length(demo.data$Group[demo.data$Group == "Expert"])` experts and *n* = `r length(demo.data$Group[demo.data$Group == "Novice"])` novices.
 

### 2022-03-07 02_paper/02_study/paper_methods.Rmd
update paper

@@
 
-```{r demographicstable}
+```{r demographicstable, echo=FALSE}
 
@@
 
-The planned sample consists of *n* = 40 experts (teacher training completed, active in the teaching profession) and *n* = 40 novices (student teachers, first internship completed).
+In June 2021, the study was piloted with student teachers volunteers to refine the study procedure so that the first data collection was conducted at the beginning of July 2021.
+
+The planned sample consists of *n* = 40 expert teachers and *n* = 40 novice teachers. 
+The inclusion criterion for experts is that they have successfully completed teacher training and are actively employed in the teaching profession.
+Novices are student teachers who have already successfully completed their first internship in a school and have gained one to four hours of teaching experience.
 

### 2022-03-08 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
SJT + demo data

@@
   summarise(N=n(),
-            "Gender male" = round(100 * n() / nrow(Gende)), 2,
+            "Male" = sum(Gender),
             "M Age" = round(mean(Age), 2),

### 2022-03-10 02_paper/02_study/paper_methods.Rmd
paper method

--- 2022-03-01 02_paper/02_study/paper_methods.Rmd
@@
 title             : "Through the eyes of the teacher"
-shorttitle        : "Visual attention in teaching and learning processes"
+shorttitle        : "Multimodal exploration of expertise differences in the perception of classroom disruptions"
 
@@
 
+  Financial Support: We received funding from QualiFond to support the qualification of young academics from the University Leipzig.
+
 abstract: |
@@
 floatsintext      : yes
-figurelist        : no
-tablelist         : no
+figurelist        : yes
+tablelist         : yes
 footnotelist      : no
@@
 
+- wie wird Störung definiert
+-
+
 Managing classroom disruptions is a crucial aspect of effective classroom management (@evertson2006classroom; @kounin2006techniken).
@@
 
-```{r demographicstable, echo = FALSE}
+```{r demographicstable, echo=FALSE}
 
@@
 
-# changing gender female 1 = 0
+# changing gender to count female gender (male = 2 --> 0)
 demo.data$Gender = ifelse(demo.data$Gender == 2, "1","0")
@@
 # creating new column with percentage of gender
+demo.data <- demo.data %>%
+  group_by(Group) %>%
+  mutate(Gender_Sum=n())
+
+# create new columns that give proportion of Gender
+# percentage = female gender divided by all female Gender
+demo.data <- demo.data  %>% 
+  group_by(Group) %>% 
+  mutate(Gender_percentage = Gender/Gender_Sum) %>% 
+  mutate(Gender_percentage = round(sum(Gender_percentage)*100, digits=0))
 
@@
   summarise(N=n(),
-            "Gender female" = sum(Gender),
+            "Gender female in percentage" = Gender_percentage,
             "M Age in years" = round(mean(Age), 0),
@@
 
-The planned sample consists of *n* = 40 experts (teacher training completed, active in the teaching profession) and *n* = 40 novices (student teachers, first internship completed).
+The sample consists of *N* = `r length(demo.data$Group)` participants with *n* = `r length(demo.data$Group[demo.data$Group == "Expert"])` expert teachers and *n* = `r length(demo.data$Group[demo.data$Group == "Novice"])` novice teachers.
 
-The currently ongoing data collection already yielded data from *n* = `r length(demo.data$Group=="Expert")` experts and
+The inclusion criterion for experts was that they have successfully completed teacher training and are actively employed in the teaching profession.
+Novices were student teachers who have already successfully completed their first internship in a school and have gained one to four hours of teaching experience.
 
-*n* = r nrow(demo.data[demo.data$Group == "Novice",]) novices.
+The subjects were primarily recruited through personal contacts, social media (facebook), e-mail distribution lists and advertising in lectures at the University Leipzig.
 
-Participants Teachers were primarily recruited through personal contacts
+The expert teachers (`r sum(demo.data$Gender)`women, `r demo.data$Gender_percentage`%) had a mean age of
+
+The participants (98
+women; 80%) had a mean age of 23.96 years (SD = 5.82; range:
+18–48), and 13 of them (11%) reported to live together with
+their child/children. Whereas 21 participants (17%) lived alone,
+the remaining participants (n = 102; 83%) lived in a household
+consisting of 2–10 persons, with the majority (n = 93)
+living in a household of 2–4 persons. At baseline (July
+2020), n = 10 participants (8%) reported flu-like symptoms
+with one participant being in COVID-related quarantine.
 
@@
 ## Procedure
+In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021, and July 2022.
 
 ## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
+All reported data analyses were conducted with the `r cite_r("r-references.bib")` and IBM SPSS 28. Data analysis scripts
+can be obtained from the authors upon request.
 

### 2022-03-14 02_paper/02_study/paper_methods.Rmd
update paper method section

@@
 # percentage = female gender divided by all female Gender
-demo.data <- demo.data  %>% 
-  group_by(Group) %>% 
-  mutate(Gender_percentage = Gender/Gender_Sum) %>% 
-  mutate(Gender_percentage = round(sum(Gender_percentage)*100, digits=0))
+# demo.data <- demo.data  %>% 
+#   group_by(Group) %>% 
+#   mutate(Gender_percentage = Gender/Gender_Sum) %>% 
+#   mutate(Gender_percentage = round(sum(Gender_percentage)*100, digits=0))
 
@@
   summarise(N=n(),
-            "Gender female in percentage" = Gender_percentage,
-            "M Age in years" = round(mean(Age), 0),
-            "SD Age in years" = round(sd(Age), 0),
+            "Gender female in percentage" = round(sum(Gender/Gender_Sum) * 100, digits = 0),
+            "M Age in years" = round(mean(Age), 2),
+            "SD Age in years" = round(sd(Age), 2),
             "Min Age in years" = min(Age),
             "Max Age in years" = max(Age),
-            "M Exp. in years" = round(mean(`Teaching Experience`), 0),
-            "SD Exp. in years" = round(sd(`Teaching Experience`), 0),
+            "M Exp. in years" = round(mean(`Teaching Experience`), 2),
+            "SD Exp. in years" = round(sd(`Teaching Experience`), 2),
             "Min Exp. in years" = min(`Teaching Experience`),
@@
 
-The expert teachers (`r sum(demo.data$Gender)`women, `r demo.data$Gender_percentage`%) had a mean age of
+The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percentage")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 2)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 2)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) with average teaching experience of `r demo.data %>% filter(Group == "Expert") %>% pull("M Exp.
+in years") %>% mean() %>% round(., digits = 2)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Exp.
+in years") %>% round(., digits = 2)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Exp.
+in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Exp.
+in years")`).
+
+The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percentage")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 2)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 2)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`).
 

### 2022-03-14 02_paper/02_study/paper_methods.Rmd
meeethod section

--- 2022-03-10 02_paper/02_study/paper_methods.Rmd
@@
                                   LI04_01,
-                                  LI06_05)
+                                  LI06_05,
+                                  LI10_05,
+                                  LI11_01,
+                                  LI13_01,
+                                  LI14
+                                  )
 
@@
                                  "Age" = "LI03_01",
-                                  "Teaching Experience" = "LI04_01"))
+                                 "Teaching Experience" = "LI04_01",
+                                 "Subject" = "LI10_05",
+                                 "Semester" = "LI11_01",
+                                 "Internship" = "LI13_01",
+                                 "Extracurricular Teaching Experience" = "LI14"
+                                 ))
 
@@
 
-# changing character into numeric
+# changing character Gender into numeric
 demo.data$Gender <- as.numeric(demo.data$Gender)
+
+# changing character Semester into numeric
+demo.data$Semester <- as.numeric(demo.data$Semester)
 
@@
 
+# changing `Extracurricular Teaching Experience` to count experience (no experience = 2 --> 0)
+demo.data$`Extracurricular Teaching Experience` = ifelse(demo.data$`Extracurricular Teaching Experience` == 2, "1","0")
+
+# creating new column with percentage of Extracurricular Teaching Experience
+demo.data <- demo.data %>%
+  group_by(Group) %>%
+  mutate(`Extracurricular Teaching Experience`=n())
+
 # create new columns that give proportion of Gender
 # percentage = female gender divided by all female Gender
-demo.data <- demo.data  %>% 
-  group_by(Group) %>% 
-  mutate(Gender_percentage = Gender/Gender_Sum) %>% 
-  mutate(Gender_percentage = round(sum(Gender_percentage)*100, digits=0))
+# demo.data <- demo.data  %>% 
+#   group_by(Group) %>% 
+#   mutate(Gender_percentage = Gender/Gender_Sum) %>% 
+#   mutate(Gender_percentage = round(sum(Gender_percentage)*100, digits=0))
 
@@
   summarise(N=n(),
-            "Gender female in percentage" = Gender_percentage,
-            "M Age in years" = round(mean(Age), 0),
-            "SD Age in years" = round(sd(Age), 0),
+            "Gender female in percentage" = round(sum(Gender/Gender_Sum) * 100, digits = 1),
+            "M Age in years" = round(mean(Age), 1),
+            "SD Age in years" = round(sd(Age), 1),
             "Min Age in years" = min(Age),
             "Max Age in years" = max(Age),
-            "M Exp. in years" = round(mean(`Teaching Experience`), 0),
-            "SD Exp. in years" = round(sd(`Teaching Experience`), 0),
+            "M Exp. in years" = round(mean(`Teaching Experience`), 1),
+            "SD Exp. in years" = round(sd(`Teaching Experience`), 1),
             "Min Exp. in years" = min(`Teaching Experience`),
-            "Max Exp.in years" = max(`Teaching Experience`),
+            "Max Exp. in years" = max(`Teaching Experience`),
+            "M Semester" = round(mean(Semester), 1),
+            "SD Semester" = round(sd(Semester), 1),
+            "Min Semester" = min(Semester),
+            "Max Semester" = max(Semester),
+
            )
@@
 
-The expert teachers (`r sum(demo.data$Gender)`women, `r demo.data$Gender_percentage`%) had a mean age of
+The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percentage")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r demo.table %>% filter(Group == "Expert") %>% pull("M Exp.
+in years") %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Exp.
+in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Exp.
+in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Exp.
+in years")`).
 
-The participants (98
-women; 80%) had a mean age of 23.96 years (SD = 5.82; range:
-18–48), and 13 of them (11%) reported to live together with
-their child/children. Whereas 21 participants (17%) lived alone,
-the remaining participants (n = 102; 83%) lived in a household
-consisting of 2–10 persons, with the majority (n = 93)
-living in a household of 2–4 persons. At baseline (July
-2020), n = 10 participants (8%) reported flu-like symptoms
-with one participant being in COVID-related quarantine.
+The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percentage")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r demo.table %>% filter(Group == "Novice") %>% pull("M Exp.
+in years") %>% mean() %>% round(., digits = 1)` years.
+On average, the student teachers were in their `r demo.table %>% filter(Group == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Semester")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Semester")`).
 

### 2022-03-18 02_paper/02_study/paper_methods.Rmd
r markdown script

@@
 ---
-title             : "Through the eyes of the teacher"
-shorttitle        : "Multimodal exploration of expertise differences in the perception of classroom disruptions"
+title             : "Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions"
+shorttitle        : "Professional Vision in Micro-Teaching-Units"
 
@@
 
-  Ethics Approval: All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board.
-The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
-
-  Consent to Participate: All participants gave informed consent.
-
-  Financial Support: We received funding from QualiFond to support the qualification of young academics from the University Leipzig.
+  We received funding from QualiFond of University Leipzig.
+We have no conflicts of interest to disclose.
+This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11 2022; EARLI SIG 27, 2022).
 
@@
 classoption       : "man"
-output            : bookdown::word_document2
+output            : papaja::apa6_pdf
+# bookdown::word_document2
 ---
@@
 
-- wie wird Störung definiert
--
-
 Managing classroom disruptions is a crucial aspect of effective classroom management (@evertson2006classroom; @kounin2006techniken).
@@
 
+# Theoretical background
+
+## Professional competence
+
+## Classroom Management
+- Disruptions defintiion
+
+## Professional Vision
+
+## Expertise
+
+## Parameter/Indicators of professional vision
+
 # Research Questions
@@
 
-```{r demographicstable, echo=FALSE}
+```{r demographicstable}
 
@@
 # changing `Extracurricular Teaching Experience` to count experience (no experience = 2 --> 0)
-demo.data$`Extracurricular Teaching Experience` = ifelse(demo.data$`Extracurricular Teaching Experience` == 2, "1","0")
+demo.data$`Extracurricular Teaching Experience` = ifelse(demo.data$`Extracurricular Teaching Experience` == 1, "1","0")
 
-# creating new column with percentage of Extracurricular Teaching Experience
-demo.data <- demo.data %>%
-  group_by(Group) %>%
-  mutate(`Extracurricular Teaching Experience`=n())
+demo.data$`Extracurricular Teaching Experience` <- as.numeric(demo.data$`Extracurricular Teaching Experience`)
 
@@
             "Max Semester" = max(Semester),
-
+            "M Internship in teaching units" = round(mean(Internship), 1),
+            "SD Internship in teaching units" = round(sd(Internship), 1),
+            "Min Internship in teaching units" = min(Internship),
+            "Max Internship in teaching units" = max(Internship),
+            "Extracurricular Teaching Experience in percentage" = round(sum(`Extracurricular Teaching Experience`/Gender_Sum) * 100, digits = 1),
            )
@@
 The inclusion criterion for experts was that they have successfully completed teacher training and are actively employed in the teaching profession.
-Novices were student teachers who have already successfully completed their first internship in a school and have gained one to four hours of teaching experience.
-
-The subjects were primarily recruited through personal contacts, social media (facebook), e-mail distribution lists and advertising in lectures at the University Leipzig.
+According to @palmer2005identifying, we selected teachers as experts who had at least three years of professional experience and ideally had worked in another teaching position, such as subject advisor or trainer for trainee teachers, in addition to their teaching profession in school.
+Novices were student teachers who had successfully completed their first internship in a school and gained one to four hours of teaching experience.
 
@@
 On average, the student teachers were in their `r demo.table %>% filter(Group == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Semester")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Semester")`).
+Furthermore, they had an average teaching experience of `r demo.table %>% filter(Group == "Novice") %>% pull("M Internship in teaching units") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Internship in teaching units") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Internship in teaching units")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Internship in teaching units")`) through the internships during their studies.
+`r demo.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience in percentage")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
+
+The subjects were primarily recruited through personal contacts, social media (Facebook), e-mail distribution lists and advertising in lectures at the University Leipzig.
+All study procedures were carried out in accordance with the ethical standards of the University’s Institutional Review Board.
+The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
+All participants were informed in detail about the aim and intention of the study prior to testing.
+Participation in the study was voluntary and only took place after written consent has been given.
 
@@
 
+### Eye-Tracking equipment
+
+During the unit, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker (https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/).
+The system consisted of a wearable head unit and a recording unit.
+As shown in Figure \@ref(fig:tobiiglasses2), the head unit was a measuring device with different sensors.
+A high-definition scene camera captured a full HD video of the teacher’s field of vision.
+An integrated microphone recorded the surrounding sounds.
+Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capure the tacher's gaze point as shown in Figure \@ref(fig:teachergazepoint).
+The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second.
+The scene camera had a field of view of 90 deg.
+in 16:9 format (82 deg.
+horizontal and 52 deg.
+vertical) and a frame dimension of 179 x 159 x 57 mm (width x depth x height).
+
+```{r tobiiglasses2, include = T, fig.cap = "Tobii Pro Glasses 2; Source: https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/", fig.align = "center", echo = FALSE}
+
+knitr::include_graphics("./pictures/tobiiglasses2.png", dpi = 108)
+
+```
+
+```{r teachergazepoint, include = T, fig.cap = "Teacher's Gaze Point", fig.align = "center", echo = FALSE}
+
+knitr::include_graphics("./pictures/teachergazepoint.png", dpi = 108)
+
+```
+
+###  Video and Audio recording equipment
+
+The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder (https://zoomcorp.com/en/gb/handheld-recorders/handheld-recorders/h3-vr-360-audio-recorder/) installed in the middle of the lab setting.
+The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.
+
+Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras (https://gopro.com/content/dam/help/hero7-black/manuals/HERO7Black_UM_ENG_REVC.pdf) from different angles.
+
+The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.
+
 ## Procedure
+
 In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021, and July 2022.
 
+One camera was installed to film the class from the side.
+Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back.
+Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.
+
+The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
+
 ## Data analysis
-All reported data analyses were conducted with the `r cite_r("r-references.bib")` and IBM SPSS 28. Data analysis scripts
-can be obtained from the authors upon request.
+
+We investigated whether experts and novice teachers differed
+
+All reported data analyses were conducted with the `r cite_r("r-references.bib")` and IBM SPSS 28.
 

### 2022-03-18 02_paper/02_study/paper_methods.tex
r markdown script

--- 2021-11-24 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic-data-script.tex
@@
 \documentclass[
-  english,
   man,floatsintext]{apa6}
-\title{Through the eyes of the teacher}
-\author{Mandy Klatt\textsuperscript{1}, Dr.~Gregor Kachel\textsuperscript{1, 2}, Dr.~Christin Lotz\textsuperscript{1}, \& Prof.~Dr.~Anne Deiglmayr\textsuperscript{1}}
-\date{}
-
 \usepackage{amsmath,amssymb}
@@
 \hypersetup{
-  pdftitle={Through the eyes of the teacher},
+  pdftitle={Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions},
   pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
   pdflang={en-EN},
-  pdfkeywords={Professional Vision, Expert-Novice-Paradigm, Eye-Tracking},
+  pdfkeywords={Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking},
   hidelinks,
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 % Manuscript styling
@@
 
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
 % \usepackage{etoolbox}
@@
 \makeatother
-\shorttitle{Visual attention in teaching and learning processes}
-\keywords{Professional Vision, Expert-Novice-Paradigm, Eye-Tracking\newline\indent Word count: 1949}
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
+\keywords{Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking\newline\indent Word count: XXX}
 \usepackage{lineno}
@@
 \usepackage{csquotes}
-\ifXeTeX
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
+\usepackage[titles]{tocloft}
+\cftpagenumbersoff{figure}
+\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
+\renewcommand{\cftfigaftersnum}{.\space}
+\setlength{\cftfigindent}{0pt}
+\setlength{\cftafterloftitleskip}{0pt}
+\settowidth{\cftfignumwidth}{Figure 10.\qquad}
+\cftpagenumbersoff{table}
+\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
+\renewcommand{\cfttabaftersnum}{.\space}
+\setlength{\cfttabindent}{0pt}
+\setlength{\cftafterloftitleskip}{0pt}
+\settowidth{\cfttabnumwidth}{Table 10.\qquad}
 \ifLuaTeX
@@
 
+\title{Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions}
+\author{Mandy Klatt\textsuperscript{1}, Dr.~Gregor Kachel\textsuperscript{1, 2}, Dr.~Christin Lotz\textsuperscript{1}, \& Prof.~Dr.~Anne Deiglmayr\textsuperscript{1}}
+\date{}
+
+\shorttitle{Professional Vision in Micro-Teaching-Units}
+
 \authornote{
 
-The Ethics Advisory Board of Leipzig University has dealt with the research project and has come to the conclusion that there are no objections to the implementation of this research project.
-The Ethics Advisory Board points out that the scientific and ethical responsibilty for the implementation of the project remains with the project director.
+We received funding from QualiFond of University Leipzig.
+We have no conflicts of interest to disclose.
+This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11 2022; EARLI SIG 27, 2022).
 
-Correspondence concerning this article should be addressed to Mandy Klatt, Egelstraße 2a 04103 Leipzig. E-mail: \href{mailto:mandy.klatt@uni-leipzig.de}{\nolinkurl{mandy.klatt@uni-leipzig.de}}
+Correspondence concerning this article should be addressed to Mandy Klatt, Dittrichring 5-7, 04109 Leipzig. E-mail: \href{mailto:mandy.klatt@uni-leipzig.de}{\nolinkurl{mandy.klatt@uni-leipzig.de}}
 
@@
 
-\abstract{
-This document is a supplement to the paper and shows first graphs findings from the pilot study.
-}
-
 \begin{document}
@@
 
-\hypertarget{packages}{%
-\section{Packages}\label{packages}}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
+Managing classroom disruptions is a crucial aspect of effective classroom management (Evertson, Weinstein, et al. (2006); Kounin (2006)).
+
+Accordingly, teachers must be able to quickly notice and appropriately react to significant events in the classroom.
+This ability is referred to as classroom professional vision (Goodwin (2015); Sherin (2007)).
+
+The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (``noticing'') and applying knowledge to draw appropriate conclusions in these situations (``knowledge-based reasoning''; Seidel and Stürmer (2014)).
+
+Therefore, the early visual perception of classroom disruptions is a key component to effectively maximize students' learning time and minimize classroom interruptions.
+According to Kounin (2006), these important classroom management strategies are called ``withitness'' and ``overlapping'' and can be summarized under the concept of monitoring (Gold and Holodynski (2017)).
+
+Learning to develop such classroom management skills is a demanding and complex task for student teachers (Wolff, Jarodzka, Bogert, and Boshuizen (2016)).
+Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, ``{[}\ldots{]} whereas only a few studies have focused on the basal process of noticing, i.e.~the recognition of possible disturbing situations'' (Grub, Biermann, and Brünken (2020), p.75).
+Mobile eye-tracking data can fill this research gap by providing new insights in how expertise differences in teacher´s professional vision manifest in teacher-student interactions (Lachner, Jarodzka, and Nückles (2016); @Wolff et al.
+(2016)).
+
+\hypertarget{theoretical-background}{%
+\section{Theoretical background}\label{theoretical-background}}
+
+\hypertarget{professional-competence}{%
+\subsection{Professional competence}\label{professional-competence}}
+
+\hypertarget{classroom-management}{%
+\subsection{Classroom Management}\label{classroom-management}}
+
+\begin{itemize}
+\tightlist
+\item
+  Disruptions defintiion
+\end{itemize}
+
+\hypertarget{professional-vision}{%
+\subsection{Professional Vision}\label{professional-vision}}
+
+\hypertarget{expertise}{%
+\subsection{Expertise}\label{expertise}}
+
+\hypertarget{parameterindicators-of-professional-vision}{%
+\subsection{Parameter/Indicators of professional vision}\label{parameterindicators-of-professional-vision}}
+
+\hypertarget{research-questions}{%
+\section{Research Questions}\label{research-questions}}
+
+This study examined how the degree of teaching experience influences (a) the number of fixations on relevant areas (e.g., the student performing the disruption), (b) the fixation duration in relevant areas and (c) the time to first fixation on relevant areas, using mobile eye-tracking data in a controlled, micro-teaching setting.
+Based on the existing literature, we expect expert teachers to outperform novices by (H1) showing more fixations on relevant areas with (H2) shorter fixation durations and (H3) perceiving classroom disruptions faster (cf.
+Van den Bogert, Bruggen, Kostons, and Jochems (2014)).
 
@@
 
-\begin{table}[h]
+The sample consists of \emph{N} = 28 participants with \emph{n} = 7 expert teachers and \emph{n} = 21 novice teachers.
 
-\begin{center}
-\begin{threeparttable}
+The inclusion criterion for experts was that they have successfully completed teacher training and are actively employed in the teaching profession.
+According to Palmer, Stough, Burdenski, and Gonzales (2005), we selected teachers as experts who had at least three years of professional experience and ideally had worked in another teaching position, such as subject advisor or trainer for trainee teachers, in addition to their teaching profession in school.
+Novices were student teachers who had successfully completed their first internship in a school and gained one to four hours of teaching experience.
 
-\caption{\label{tab:demographicstable}Demographic Information and and Teaching Experience}
+The expert teachers (5 women; 71.40\%) had a mean age of 45.10 years (\emph{SD} = 12; range: 27-59) and an average teaching experience of 18.10 years (\emph{SD} = 14.10; range: 3-37).
 
-\small{
+The novice teachers (13 women; 61.90\%) had a mean age of 23.30 years (\emph{SD} = 1.70; range: 20-27) with an average teaching experience of 0 years.
+On average, the student teachers were in their 7.40 semester (\emph{SD} = 2.50; range: 3-11).
+Furthermore, they had an average teaching experience of 12.20 teaching units à 45min (\emph{SD} = 8.40; range: 4-36) through the internships during their studies.
+90.50\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
 
-\begin{tabular}{lllllllllll}
-\toprule
-Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Male} & \multicolumn{1}{c}{M Age} & \multicolumn{1}{c}{Min Age} & \multicolumn{1}{c}{Max Age} & \multicolumn{1}{c}{SD Age} & \multicolumn{1}{c}{M Exp.} & \multicolumn{1}{c}{Min Exp.} & \multicolumn{1}{c}{Max Exp.} & \multicolumn{1}{c}{SD Exp.}\\
-\midrule
-Expert & 4 & 7.00 & 49.25 & 27.00 & 59.00 & 14.93 & 25.25 & 3.00 & 37.00 & 15.20\\
-Novice & 11 & 18.00 & 23.18 & 21.00 & 25.00 & 1.08 & 0.55 & 0.00 & 6.00 & 1.81\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
+The subjects were primarily recruited through personal contacts, social media (Facebook), e-mail distribution lists and advertising in lectures at the University Leipzig.
+All study procedures were carried out in accordance with the ethical standards of the University's Institutional Review Board.
+The authors received a positive vote on the study procedures from the Ethics Committee Board of Leipzig University.
+All participants were informed in detail about the aim and intention of the study prior to testing.
+Participation in the study was voluntary and only took place after written consent has been given.
 
@@
 
+\hypertarget{eye-tracking-equipment}{%
+\subsubsection{Eye-Tracking equipment}\label{eye-tracking-equipment}}
+
+During the unit, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker (\url{https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/}).
+The system consisted of a wearable head unit and a recording unit.
+As shown in Figure \ref{fig:tobiiglasses2}, the head unit was a measuring device with different sensors.
+A high-definition scene camera captured a full HD video of the teacher's field of vision.
+An integrated microphone recorded the surrounding sounds.
+Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capure the tacher's gaze point as shown in Figure \ref{fig:teachergazepoint}.
+The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second.
+The scene camera had a field of view of 90 deg.
+in 16:9 format (82 deg.
+horizontal and 52 deg.
+vertical) and a frame dimension of 179 x 159 x 57mm (width x depth x height).
+
+\begin{figure}
+
+{\centering \includegraphics{./pictures/tobiiglasses2}
+
+}
+
+\caption{Tobii Pro Glasses 2; Source: https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/}\label{fig:tobiiglasses2}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics{./pictures/teachergazepoint}
+
+}
+
+\caption{Teacher's Gaze Point}\label{fig:teachergazepoint}
+\end{figure}
+
 \hypertarget{procedure}{%
 \subsection{Procedure}\label{procedure}}
+
+In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021, and July 2022.
+
+The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
 
@@
 
-We used R {[}Version 4.0.3; R Core Team (2020){]} and the R-packages \emph{ARTofR} {[}Version 0.3.3; Zhang (2021){]}, \emph{cowplot} {[}Version 1.1.1; Wilke (2020){]}, \emph{dplyr} {[}Version 1.0.2; Wickham, François, Henry, and Müller (2020){]}, \emph{forcats} {[}Version 0.5.0; Wickham (2020a){]}, \emph{ggplot2} {[}Version 3.3.2; Wickham (2016){]}, \emph{gridExtra} {[}Version 2.3; Auguie (2017){]}, \emph{lubridate} {[}Version 1.7.9.2; Grolemund and Wickham (2011){]}, \emph{needs} {[}Version 0.0.3; Katz (2016){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham and Hester (2020){]}, \emph{readxl} {[}Version 1.3.1; Wickham and Bryan (2019){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.0.4; Müller and Wickham (2020){]}, \emph{tidyr} {[}Version 1.1.2; Wickham (2020b){]}, \emph{tidyverse} {[}Version 1.3.0; Wickham et al.
-(2019){]}, \emph{viridis} {[}Version 0.5.1; Garnier (2018a); Garnier (2018b){]}, and \emph{viridisLite} {[}Version 0.3.0; Garnier (2018b){]} for all our analyses.
+We investigated whether experts and novice teachers differed
+
+All reported data analyses were conducted with the R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.3.3; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.1; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) and IBM SPSS 28.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
-Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
+Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
+Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://cran.r-project.org/package=tinylabels}
+
+\leavevmode\vadjust pre{\hypertarget{ref-evertson2006classroom}{}}%
+Evertson, C. M., Weinstein, C. S.others. (2006). Classroom management as a field of inquiry. \emph{Handbook of Classroom Management: Research, Practice, and Contemporary Issues}, \emph{3}(1), 16.
 
 \leavevmode\vadjust pre{\hypertarget{ref-R-viridis}{}}%
-Garnier, S. (2018a). \emph{Viridis: Default color maps from 'matplotlib'}. Retrieved from \url{https://CRAN.R-project.org/package=viridis}
+Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021a). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
 
 \leavevmode\vadjust pre{\hypertarget{ref-R-viridisLite}{}}%
-Garnier, S. (2018b). \emph{viridisLite: Default color maps from 'matplotlib' (lite version)}. Retrieved from \url{https://CRAN.R-project.org/package=viridisLite}
+Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021b). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gold2017using}{}}%
+Gold, B., \& Holodynski, M.
+(2017).
+Using digital video to measure the professional vision of elementary classroom management: Test validation and methodological challenges.
+\emph{Computers \& Education}, \emph{107}, 13--30.
+
+\leavevmode\vadjust pre{\hypertarget{ref-goodwin2015professional}{}}%
+Goodwin, C. (2015). Professional vision. In \emph{Aufmerksamkeit} (pp. 387--425). Springer.
 
@@
 Grolemund, G., \& Wickham, H. (2011). Dates and times made easy with {lubridate}. \emph{Journal of Statistical Software}, \emph{40}(3), 1--25. Retrieved from \url{https://www.jstatsoft.org/v40/i03/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-grub2020process}{}}%
+Grub, A.-S., Biermann, A., \& Brünken, R.
+(2020).
+Process-based measurement of professional vision of (prospective) teachers in the field of classroom management.
+A systematic review.
+\emph{Journal for Educational Research Online}, \emph{12}(3), 75--102.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-kounin2006techniken}{}}%
+Kounin, J. S. (2006). \emph{Techniken der klassenf{ü}hrung}. Waxmann Verlag.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lachner2016makes}{}}%
+Lachner, A., Jarodzka, H., \& Nückles, M.
+(2016).
+What makes an expert teacher?
+Investigating teachers' professional vision and discourse abilities.
+\emph{Instructional Science}, \emph{44}(3), 197--203.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
-Müller, K., \& Wickham, H. (2020). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+
+\leavevmode\vadjust pre{\hypertarget{ref-palmer2005identifying}{}}%
+Palmer, D.
+J., Stough, L.
+M., Burdenski, T.
+K., Jr, \& Gonzales, M.
+(2005).
+Identifying teacher expertise: An examination of researchers' decision making.
+\emph{Educational Psychologist}, \emph{40}(1), 13--25.
 
 \leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
-R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-seidel2014modeling}{}}%
+Seidel, T., \& Stürmer, K. (2014). Modeling and measuring the structure of professional vision in preservice teachers. \emph{American Educational Research Journal}, \emph{51}(4), 739--771.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sherin2007development}{}}%
+Sherin, M.
+(2007).
+\emph{The development of teachers' professional vision in video clubs.
+Video research in the learning sciences.
+R.
+Goldman, r.
+Pea, b.
+Barron and SJ derry}.
+Mahwah, NJ, Lawrence Erlbaum.
+
+\leavevmode\vadjust pre{\hypertarget{ref-van2014first}{}}%
+Van den Bogert, N., Bruggen, J.
+van, Kostons, D., \& Jochems, W.
+(2014).
+First steps into understanding teachers' visual perception of classroom events.
+\emph{Teaching and Teacher Education}, \emph{37}, 208--216.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
-Wickham, H. (2020a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
-Wickham, H. (2020b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+Wickham, H. (2021). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
-Wickham, H., François, R., Henry, L., \& Müller, K. (2020). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+Wickham, H., François, R., Henry, L., \& Müller, K. (2022). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
+Wickham, H., \& Girlich, M. (2022). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
 
 \leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
-Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+Wickham, H., Hester, J., \& Bryan, J. (2021). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
 
@@
 Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wolff2016teacher}{}}%
+Wolff, C.
+E., Jarodzka, H., Bogert, N.
+van den, \& Boshuizen, H.
+(2016).
+Teacher vision: Expert and novice teachers' perception of problematic classroom management scenes.
+\emph{Instructional Science}, \emph{44}(3), 243--265.
 

### 2022-03-18 02_paper/02_study/paper_methods.Rmd
update R method

@@
 
+quest.data <- read_excel ("./data/data_empschul_labor_lehrperson.xlsx")
+
 ```
@@
 
-# prepare data (selected from questionnaire data)
-demo.data <- read_excel ("./data/data_empschul_labor_lehrperson.xlsx")
-
-# select relevant columns
-demo.data <- demo.data %>% select(LI02_01_1,
+# select relevant columns from first questionnaire 
+demo.data <- quest.data %>% select(LI02_01_1,
                                   LI03_01,
@@
 
+# changing character Extra. Exp. into numeric
 demo.data$`Extracurricular Teaching Experience` <- as.numeric(demo.data$`Extracurricular Teaching Experience`)
@@
 Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras (https://gopro.com/content/dam/help/hero7-black/manuals/HERO7Black_UM_ENG_REVC.pdf) from different angles.
+The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.
 
-The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.
+### Questionnaire
+
+After each micro-teaching-unit, the students answered items on teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and scales on the teacher's presence behavior.
+In addition, participants were asked to give a self-assessment on  classroom management by completing the questionnaire after each micro-teaching-unit.
+The questionnaire was a 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
+
+```{r presence_questionnaire}
+
+# select relevant columns
+quest.data <- quest.data %>% select(LM01_01:LO01_02, LI06_05)
+
+# rename columns
+quest.data <- rename(quest.data, c("Group" = "LI06_05"))
+
+# # define expert and novice with ifelse function
+# quest.data$Group = ifelse(quest.data$Group < 200, "Novice","Expert")
+
+```
 

### 2022-03-21 02_paper/02_study/paper_methods.Rmd
update method

@@
       readxl,
-      ARTofR)
+      ARTofR,
+      moments,
+      ltm)
 ```
@@
 # select relevant columns from first questionnaire 
-demo.data <- quest.data %>% select(LI02_01_1,
+demo.data <- quest.data %>% dplyr::select(LI02_01_1,
                                   LI03_01,
@@
 # select relevant columns
-quest.data <- quest.data %>% select(LM01_01:LO01_02, LI06_05)
+quest.data <- quest.data %>% dplyr::select(LM01_01:LO01_02, LI06_05)
 
@@
 
-# # define expert and novice with ifelse function
-# quest.data$Group = ifelse(quest.data$Group < 200, "Novice","Expert")
+# define expert and novice with ifelse function
+quest.data$Group = ifelse(quest.data$Group < 200, "Novice","Expert")
+
+# creating a matrix
+quest.table <- matrix(data = NA, nrow = 4, ncol = 8)
+rownames(quest.table) <- c("LM", "LB", "LP", "LV")
+  colnames(quest.table) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")
+
+# creating a loop 
+# i <- "LM"
+
+for (i in c("LM", "LB", "LP", "LV")) {
+
+loop.data <- quest.data %>% 
+  dplyr::select(starts_with(match = i))
+
+quest.table[i, "N Items"] <- length(loop.data)
+
+# calculating mean
+loop.data %>% 
+  mutate(mean = rowMeans(.)) %>% 
+  pull(mean) %>% 
+  mean() %>% 
+  round(., digits = 2) ->
+quest.table[i, "M"]
+
+# calculating SD
+loop.data %>% 
+  mutate(mean = rowMeans(.)) %>% 
+  pull(mean) %>% 
+  sd() %>% 
+  round(., digits = 2) ->
+quest.table[i, "SD"]
+
+# calculating Min
+loop.data %>% 
+  mutate(mean = rowMeans(.)) %>% 
+  pull(mean) %>% 
+  min() %>% 
+  round(., digits = 2) ->
+quest.table[i, "Min"]
+
+# calculating Max
+loop.data %>% 
+  mutate(mean = rowMeans(.)) %>% 
+  pull(mean) %>% 
+  max() %>% 
+  round(., digits = 2) ->
+quest.table[i, "Max"]
+
+# calculating Skewness
+loop.data %>% 
+  mutate(mean = rowMeans(.)) %>% 
+  pull(mean) %>% 
+  skewness() %>% 
+  round(., digits = 2) ->
+quest.table[i, "Skewness"]
+
+# calculating Kurtosis
+loop.data %>% 
+  mutate(mean = rowMeans(.)) %>% 
+  pull(mean) %>% 
+  kurtosis() %>% 
+  round(., digits = 2) ->
+quest.table[i, "Kurtosis"]
+
+# calculating alpha
+alpha <- loop.data %>% 
+  cronbach.alpha() 
+alpha$alpha
+
+quest.table[i, "alpha"] <- round(alpha$alpha,2)
+
+}
+
+rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")
+
+# format and insert table in manuscript
+apa_table(
+  quest.table,
+  caption = "Scale analysis for teachers' self-assessment",
+  # note = "Write Note here", 
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+)
 

### 2022-03-21 02_paper/02_study/paper_methods.tex
update method

@@
 horizontal and 52 deg.
-vertical) and a frame dimension of 179 x 159 x 57mm (width x depth x height).
+vertical) and a frame dimension of 179 x 159 x 57 mm (width x depth x height).
 
@@
 
+\hypertarget{video-and-audio-recording-equipment}{%
+\subsubsection{Video and Audio recording equipment}\label{video-and-audio-recording-equipment}}
+
+The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder (\url{https://zoomcorp.com/en/gb/handheld-recorders/handheld-recorders/h3-vr-360-audio-recorder/}) installed in the middle of the lab setting.
+The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.
+
+Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras (\url{https://gopro.com/content/dam/help/hero7-black/manuals/HERO7Black_UM_ENG_REVC.pdf}) from different angles.
+The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.
+
+\hypertarget{questionnaire}{%
+\subsubsection{Questionnaire}\label{questionnaire}}
+
+After each micro-teaching-unit, the students answered items on teaching quality using a validated questionnaire (Helmke et al., 2014) and scales on the teacher's presence behavior.
+In addition, participants were asked to give a self-assessment on classroom management by completing the questionnaire after each micro-teaching-unit.
+The questionnaire was a 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
+
 \hypertarget{procedure}{%
@@
 In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021, and July 2022.
+
+One camera was installed to film the class from the side.
+Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back.
+Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.
 
@@
 \emph{Journal for Educational Research Online}, \emph{12}(3), 75--102.
+
+\leavevmode\vadjust pre{\hypertarget{ref-helmke2014unterrichtsdiagnostik}{}}%
+Helmke, A., Helmke, T., Lenske, G., Pham, G., Praetorius, A.-K., Schrader, F.-W., \& AdeThurow, M.
+(2014).
+Unterrichtsdiagnostik mit EMU.
+\emph{Aus-Und Fortbildung Der Lehrkr{ä}fte in Hinblick Auf Verbesserung Der Diagnosef{ä}higkeit, Umgang Mit Heterogenit{ä}t Und Individuelle F{ö}rderung}, 149--163.
 

### 2022-04-06 02_paper/02_study/paper_methods.Rmd
paper method section

@@
 
-floatsintext      : yes
+floatsintext      : no
 figurelist        : yes
@@
       moments,
-      ltm)
+      ltm,
+      sjPlot)
 ```
@@
                                   LI13_01,
-                                  LI14
+                                  LI14,
+                                  LI18,
+                                  LI16_05,
+                                  LI17
                                   )
@@
                                  "Teaching Experience" = "LI04_01",
+                                 "Type of School" = "LI18",
+                                 "Grade" = "LI16_05",
                                  "Subject" = "LI10_05",
@@
                                  "Internship" = "LI13_01",
-                                 "Extracurricular Teaching Experience" = "LI14"
+                                 "Extracurricular Teaching Experience" = "LI14",
+                                 "Secondary Teaching Activities" = "LI17"
                                  ))
@@
 demo.data$`Extracurricular Teaching Experience` <- as.numeric(demo.data$`Extracurricular Teaching Experience`)
+
+# changing `Secondary Teaching Activities` to count experience (no experience = 2 --> 0)
+demo.data$`Secondary Teaching Activities` = ifelse(demo.data$`Secondary Teaching Activities` == 1, "1","0")
+
+# changing character Extra. Exp. into numeric
+demo.data$`Secondary Teaching Activities` <- as.numeric(demo.data$`Secondary Teaching Activities`)
 
@@
             "Extracurricular Teaching Experience in percentage" = round(sum(`Extracurricular Teaching Experience`/Gender_Sum) * 100, digits = 1),
+            "Secondary Teaching Activities in percentage" = round(sum(`Secondary Teaching Activities`/Gender_Sum) * 100)
            )
@@
 in years")`).
+`r demo.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities in percentage")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
 
@@
 
-```{r presence_questionnaire}
+```{r presence_questionnaire, echo=FALSE}
 
@@
 
+# rename columns 
 rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")
@@
 
+# item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
+
+# Classroom Management
+tab_itemscale(quest.data[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
 ```
@@
 In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021, and July 2022.
-
-One camera was installed to film the class from the side.
-Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back.
-Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.
-
-The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
 

### 2022-04-06 02_paper/02_study/paper_methods.tex
paper method section

@@
 \documentclass[
-  man,floatsintext]{apa6}
+  man]{apa6}
 \usepackage{amsmath,amssymb}
@@
 \keywords{Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking\newline\indent Word count: XXX}
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
 \usepackage{lineno}
@@
 The expert teachers (5 women; 71.40\%) had a mean age of 45.10 years (\emph{SD} = 12; range: 27-59) and an average teaching experience of 18.10 years (\emph{SD} = 14.10; range: 3-37).
+71\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
 
@@
 On average, the student teachers were in their 7.40 semester (\emph{SD} = 2.50; range: 3-11).
-Furthermore, they had an average teaching experience of 12.20 teaching units à 45min (\emph{SD} = 8.40; range: 4-36) through the internships during their studies.
+Furthermore, they had an average teaching experience of 12 teaching units à 45min (\emph{SD} = 8.60; range: 0-36) through the internships during their studies.
 90.50\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
@@
 
-All reported data analyses were conducted with the R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.3.3; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.1; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) and IBM SPSS 28.
+All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.3.3; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.1; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) and IBM SPSS 28.
 

### 2022-04-13 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/kopie/read_data_auto.R
update

@@ -25,8 +25,7 @@ for (i in file_names) {
 
     work_data <- 
     read_tsv(file = paste0("data/", i),
-                          locale = locale(decimal_mark = ",")) %>% 
-      select(!"Minimum_amplitude_of_saccades")
+                          locale = locale(decimal_mark = ","))
   
   assign(value = work_data,
          x = str_remove(paste0("tib_", i),

### 2022-04-13 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et aoi.R
Add automated data reading to et aoi.R

@@ -15,87 +15,119 @@ needs(tidyverse,
 # if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
 options(dplyr.summarise.inform = FALSE)
 
+# 
+# # read in expert data
+# expert_aoi1 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_202_203_204_interval_complete.tsv",
+#                        locale = locale(decimal_mark = ","))
+# 
+# expert_aoi2 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_205_interval_complete.tsv",
+#                         locale = locale(decimal_mark = ","))
+# 
+# expert_aoi3 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_206_interval_complete.tsv",
+#                         locale = locale(decimal_mark = ","))
+# 
+# expert_aoi4 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_207_interval_complete.tsv",
+#                         locale = locale(decimal_mark = ","))
+# 
+# # combine the expert df
+# expert_aoi <- rbind(expert_aoi1, 
+#                     expert_aoi2, 
+#                     expert_aoi3, 
+#                     expert_aoi4)
+#                     
+# 
+# 
+# # read in novice data
+# novice_aoi1 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_101_interval_complete.tsv",
+#                         locale = locale(decimal_mark = ","))
+#                       
+# novice_aoi2 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_102_103_interval_complete.tsv",
+#                         locale = locale(decimal_mark = ","))
+# 
+# novice_aoi3 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_104_interval_complete.tsv",
+#                         locale = locale(decimal_mark = ","))
+# 
+# novice_aoi4 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_105_interval_complete.tsv",
+#                         locale = locale(decimal_mark = ","))
+# 
+# novice_aoi5 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_106_107_interval_complete.tsv",
+#                         locale = locale(decimal_mark = ","))
+# 
+# 
+# novice_aoi6 <- read_tsv(file = "data/ProVisioNET_study_glasses_metrics_108-111_interval_complete.tsv",
[…]

### 2022-04-13 02_paper/02_study/paper_methods.Rmd
update R markdown method

@@
 
-floatsintext      : no
+floatsintext      : yes
+figsintext        : yes
 figurelist        : yes
@@
       ltm,
-      sjPlot)
+      sjPlot,
+      kableExtra,
+      xtable)
 ```
@@
 # format and insert table in manuscript
-apa_table(
-  demo.table,
+demo.table %>%
+papaja::apa_table(
   caption = "Demographic Information and Teaching Experience",
@@
 
-```{r presence_questionnaire, echo=FALSE}
+```{r presence_questionnaire, echo=FALSE, results='asis'}
 
@@
 # format and insert table in manuscript
-apa_table(
+papaja::apa_table(
 quest.table,
@@
 # Classroom Management
-tab_itemscale(quest.data[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
 

### 2022-04-13 02_paper/02_study/paper_methods.tex
update R markdown method

@@
 \documentclass[
-  man]{apa6}
+  man,floatsintext]{apa6}
 \usepackage{amsmath,amssymb}
@@
 \keywords{Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking\newline\indent Word count: XXX}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
 \usepackage{lineno}
@@
 
-One camera was installed to film the class from the side.
-Two more cameras were installed on the blackboard and at the end of the Lab to film the teacher and class from the front and back.
-Furthermore, the fourth camera was installed in such a way that only facial expressions and gestures of the teacher were recorded, which enables a semi-automated analysis of the movement sequences.
-
-The Tobii Pro Glasses Controller software was used to record and calibrate the eye movements.
-
 \hypertarget{data-analysis}{%
@@
 
-All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.3.3; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.1; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) and IBM SPSS 28.
+All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.3.3; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.1; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) and IBM SPSS 28.
 
@@
 Evertson, C. M., Weinstein, C. S.others. (2006). Classroom management as a field of inquiry. \emph{Handbook of Classroom Management: Research, Practice, and Contemporary Issues}, \emph{3}(1), 16.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-polycor}{}}%
+Fox, J. (2022). \emph{Polycor: Polychoric and polyserial correlations}. Retrieved from \url{https://CRAN.R-project.org/package=polycor}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-msm}{}}%
+Jackson, C.
+H.
+(2011).
+Multi-state models for panel data: The {msm} package for {R}.
+\emph{Journal of Statistical Software}, \emph{38}(8), 1--29.
+Retrieved from \url{https://www.jstatsoft.org/v38/i08/}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-needs}{}}%
 Katz, J. (2016). \emph{Needs: Attaches and installs packages}. Retrieved from \url{https://CRAN.R-project.org/package=needs}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-moments}{}}%
+Komsta, L., \& Novomestky, F. (2015). \emph{Moments: Moments, cumulants, skewness, kurtosis and related tests}. Retrieved from \url{https://CRAN.R-project.org/package=moments}
 
@@
 \emph{Instructional Science}, \emph{44}(3), 197--203.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-sjPlot}{}}%
+Lüdecke, D. (2021). \emph{sjPlot: Data visualization for statistics in social science}. Retrieved from \url{https://CRAN.R-project.org/package=sjPlot}
 
@@
 R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ltm}{}}%
+Rizopoulos, D.
+(2006).
+Ltm: An r package for latent variable modelling and item response theory analyses.
+\emph{Journal of Statistical Software}, \emph{17}(5), 1--25.
+Retrieved from \url{https://doi.org/10.18637/jss.v017.i05}
 
@@
 \emph{Teaching and Teacher Education}, \emph{37}, 208--216.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-MASS}{}}%
+Venables, W. N., \& Ripley, B. D. (2002). \emph{Modern applied statistics with s} (Fourth). New York: Springer. Retrieved from \url{https://www.stats.ox.ac.uk/pub/MASS4/}
 

### 2022-04-13 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNET_ET_reli_01_01_AOI-based_data.R

@@ -1,332 +1,0 @@
-### ProVisioNET pilot data 
-#### intercoder reli eye tracking data 01_01
-
-
-# install needed packages
-library(needs)
-needs(tidyverse,
-      psych,
-      moments,
-      sjPlot,
-      irr,
-      readxl)
-
-# suppress "summarize" info. 
-# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
-options(dplyr.summarise.inform = FALSE)
-
-
-
-
-### VIDEO 01_01
-################## RATER 1 ################
-
-# read in data from rater1 while specifying locale allows to set "," 
-coding_data_r1_v1 <-read_tsv ("./data/01_01_AP_ProVisioNET_study_glasses_Metrics_Event-based.tsv", 
-                           locale = locale(decimal_mark = ","))
-
-# filter only rows lesson
-r1_v1 <- coding_data_r1_v1 %>% filter(TOI == "Lesson")
-
-# select relevant variables 
-r1_v1 <- r1_v1 %>% select(EventIndex, AOI)
-
-################## RATER 2 ################
-
-# read in data from rater2 while specifying locale allows to set "," 
-coding_data_r2_v1 <-read_tsv ("./data/01_01_MK_ProVisioNET_study_glasses_Metrics_Event-based.tsv", 
-                           locale = locale(decimal_mark = ","))
-
-# filter only rows lesson
-r2_v1 <- coding_data_r2_v1 %>% filter(TOI == "Lesson")
-
-# select relevant variables
-r2_v1 <- r2_v1 %>% select(EventIndex, AOI)
-
-#rename values in row Material = Teacher_Material
-r2_v1$AOI[r2_v1$AOI == "Material_Teacher"] <- "Material"
-
-
-###### filter identical row number
-
-v1_r1 <- v1_r1 %>% filter(EventIndex != 1728,
-                    EventIndex != 1729,
-                    EventIndex != 1730,
-                    EventIndex != 1731)
-
-v1_r1
-
-
-# merge two data frames --> adding Columns, don't forget to merge BY AOI !
-
-r3_v1 <- left_join(r1_v1, r2_v1, by = 'EventIndex')
-
-
-#compare AOI.x and AOI.y and output results to new column titled rating_compare
[…]

### 2022-04-13 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_reli_01_01_TOI-based_data_first_reaction.R

@@ -1,195 +1,0 @@
-### ProVisioNET pilot data 
-#### intercoder reli eye tracking data 01_01
-
-library(needs)
-needs(tidyverse,
-      psych,
-      moments,
-      sjPlot,
-      DescTools,
-      irr,
-      readxl)
-
-# suppress "summarize" info. 
-# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
-options(dplyr.summarise.inform = FALSE)
-
-
-# read in data
-reaction_AP <- read_tsv(file = "data/01_01_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv"
-)
-
-reaction_MK <- read_tsv(file = "data/01_01_MK_ProVisioNET_study_glasses_Metrics_Intervall based.tsv"
-)
-
-# select relevant columns
-reaction_AP <- reaction_AP %>% 
-  select(TOI, 
-         Time_to_first_Event.Reaction_chatting,
-         Time_to_first_Event.Reaction_clicking,
-         Time_to_first_Event.Reaction_drawing,
-         Time_to_first_Event.Reaction_drumming,
-         Time_to_first_Event.Reaction_head,
-         Time_to_first_Event.Reaction_heckling,
-         Time_to_first_Event.Reaction_phone,
-         Time_to_first_Event.Reaction_snipping,
-         Time_to_first_Event.Reaction_whispering
-         )
-
-reaction_MK <- reaction_MK %>% 
-  select(TOI, 
-         Time_to_first_Event.Reaction_chatting,
-         Time_to_first_Event.Reaction_clicking,
-         Time_to_first_Event.Reaction_drawing,
-         Time_to_first_Event.Reaction_drumming,
-         Time_to_first_Event.Reaction_head,
-         Time_to_first_Event.Reaction_heckling,
-         Time_to_first_Event.Reaction_phone,
-         Time_to_first_Event.Reaction_snipping,
-         Time_to_first_Event.Reaction_whispering
-         )
-
-# filter only for event TOIs 
-reaction_AP <- reaction_AP %>% 
-  filter(TOI == "Chatting_with_neighbour"|
-         TOI == "Clicking_pen"| 
-         TOI == "Drawing"|
-         TOI == "Drumming_with_hands"| 
-         TOI == "Head_on_table"| 
-         TOI == "Heckling"|
-         TOI == "Looking_at_phone" |
-         TOI == "Snipping_with_fingers"|
-         TOI == "Whispering"
-         )
-
[…]

### 2022-04-20 02_paper/02_study/paper_methods.Rmd
table fix

@@
 library("papaja")
-r_refs("r-references.bib")
+r_refs(file = "r-references.bib")
 ```
@@
 
-```{r demographicstable, echo=FALSE}
+```{r demographicstable, include = TRUE, echo=FALSE}
 
@@
   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
-  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
   )
@@
 
-```{r presence_questionnaire, echo=FALSE, results='asis'}
+```{r presence_questionnaire, include=TRUE, echo=FALSE, results='asis'}
 

### 2022-04-20 02_paper/02_study/paper_methods.tex
method update

@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
 
@@
 
-All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.3.3; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.1; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) and IBM SPSS 28.
+All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{knitr} (Version 1.38; Xie, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) and IBM SPSS 28.
 
@@
 Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-rlang}{}}%
+Henry, L., \& Wickham, H. (2022). \emph{Rlang: Functions for base types and core r and 'tidyverse' features}. Retrieved from \url{https://CRAN.R-project.org/package=rlang}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-knitr}{}}%
+Xie, Y. (2015). \emph{Dynamic documents with {R} and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.org/knitr/}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-ARTofR}{}}%

### 2022-04-20 02_paper/02_study/paper_methods.tex

--- 2022-04-13 02_paper/02_study/paper_methods.tex
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions},
-  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
-  pdflang={en-EN},
-  pdfkeywords={Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions},
+  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
+  pdflang={en-EN},
+  pdfkeywords={Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:demographicstable}Demographic Information and Teaching Experience}
+
+\tiny{
+
+\begin{tabular}{lllllllllllllllllllll}
+\toprule
+Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Gender female in percentage} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years} & \multicolumn{1}{c}{M Exp.
+in years} & \multicolumn{1}{c}{SD Exp.
+in years} & \multicolumn{1}{c}{Min Exp.
+in years} & \multicolumn{1}{c}{Max Exp.
+in years} & \multicolumn{1}{c}{M Semester} & \multicolumn{1}{c}{SD Semester} & \multicolumn{1}{c}{Min Semester} & \multicolumn{1}{c}{Max Semester} & \multicolumn{1}{c}{M Internship in teaching units} & \multicolumn{1}{c}{SD Internship in teaching units} & \multicolumn{1}{c}{Min Internship in teaching units} & \multicolumn{1}{c}{Max Internship in teaching units} & \multicolumn{1}{c}{Extracurricular Teaching Experience in percentage} & \multicolumn{1}{c}{Secondary Teaching Activities in percentage}\\
+\midrule
+Expert & 7 & 71.40 & 45.10 & 12.00 & 27.00 & 59.00 & 18.10 & 14.10 & 3.00 & 37.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 71.00\\
+Novice & 21 & 61.90 & 23.30 & 1.70 & 20.00 & 27.00 & 0.00 & 0.00 & 0.00 & 0.00 & 7.40 & 2.50 & 3.00 & 11.00 & 12.00 & 8.60 & 0.00 & 36.00 & 90.50 & NA\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 The sample consists of \emph{N} = 28 participants with \emph{n} = 7 expert teachers and \emph{n} = 21 novice teachers.
@@
 
-{\centering \includegraphics{./pictures/tobiiglasses2}
+{\centering \includegraphics[width=14.07in]{./pictures/tobiiglasses2}
 
@@
 
-{\centering \includegraphics{./pictures/teachergazepoint}
+{\centering \includegraphics[width=7.16in]{./pictures/teachergazepoint}
 
@@
 
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:presence_questionnaire}Scale analysis for teachers' self-assessment}
+
+\tiny{
+
+\begin{tabular}{lllllllll}
+\toprule
+ & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
+\midrule
+Classroom Management & 8.00 & 2.96 & 0.25 & 2.50 & 3.38 & -0.02 & 1.78 & 0.21\\
+Balance & 3.00 & 3.21 & 0.54 & 1.67 & 4.00 & -0.58 & 3.65 & 0.68\\
+Presence & 8.00 & 3.17 & 0.39 & 2.50 & 3.88 & -0.05 & 2.38 & 0.72\\
+Natural Behavior & 3.00 & 3.23 & 0.59 & 1.67 & 4.00 & -0.77 & 3.50 & 0.74\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 \hypertarget{procedure}{%
@@
 
-All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.3.3; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.1; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) and IBM SPSS 28.
+All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.3.3; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) and IBM SPSS 28.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-evertson2006classroom}{}}%
-Evertson, C. M., Weinstein, C. S.others. (2006). Classroom management as a field of inquiry. \emph{Handbook of Classroom Management: Research, Practice, and Contemporary Issues}, \emph{3}(1), 16.
+Evertson, C. M., Weinstein, C. S., et al. (2006). Classroom management as a field of inquiry. \emph{Handbook of Classroom Management: Research, Practice, and Contemporary Issues}, \emph{3}(1), 16.
 

### 2022-04-20 02_paper/02_study/paper_methods.tex
update method

--- 2022-04-20 02_paper/02_study/paper_methods.tex
@@
 The questionnaire was a 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:presence_questionnaire}Scale analysis for teachers' self-assessment}
+
+\tiny{
+
+\begin{tabular}{lllllllll}
+\toprule
+ & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
+\midrule
+Classroom Management & 8.00 & 2.96 & 0.25 & 2.50 & 3.38 & -0.02 & 1.78 & 0.21\\
+Balance & 3.00 & 3.21 & 0.54 & 1.67 & 4.00 & -0.58 & 3.65 & 0.68\\
+Presence & 8.00 & 3.17 & 0.39 & 2.50 & 3.88 & -0.05 & 2.38 & 0.72\\
+Natural Behavior & 3.00 & 3.23 & 0.59 & 1.67 & 4.00 & -0.77 & 3.50 & 0.74\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 

### 2022-04-27 02_paper/02_study/paper_methods.Rmd
method update
method paper new table

@@
 
-floatsintext      : yes
+floatsintext      : no
 figsintext        : yes
@@
 ```{r include=FALSE}
-#install.packages("needs")
+# install.packages("needs")
 
@@
       xtable)
+
 ```
@@
 
-# select relevant columns from first questionnaire 
-demo.data <- quest.data %>% dplyr::select(LI02_01_1,
-                                  LI03_01,
-                                  LI04_01,
-                                  LI06_05,
-                                  LI10_05,
-                                  LI11_01,
-                                  LI13_01,
-                                  LI14,
-                                  LI18,
-                                  LI16_05,
-                                  LI17
+# read in data and select and rename relevant columns with transmute 
+demo.data <- 
+  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
+  transmute(Group = LI06_05,
+                                 Gender = LI02_01_1,
+                                 Age = LI03_01,
+                                 `Teaching Experience` = LI04_01,
+                                 `Type of School` = LI18,
+                                 Grade = LI16_05,
+                                 Subject = LI10_05,
+                                 Semester = LI11_01,
+                                 Internship = LI13_01,
+                                 `Extracurricular Teaching Experience` = LI14,
+                                 `Secondary Teaching Activities` = LI17
                                  )
-
-# rename columns
-demo.data <- rename(demo.data, c("Group" = "LI06_05",
-                                 "Gender" = "LI02_01_1",
-                                 "Age" = "LI03_01",
-                                 "Teaching Experience" = "LI04_01",
-                                 "Type of School" = "LI18",
-                                 "Grade" = "LI16_05",
-                                 "Subject" = "LI10_05",
-                                 "Semester" = "LI11_01",
-                                 "Internship" = "LI13_01",
-                                 "Extracurricular Teaching Experience" = "LI14",
-                                 "Secondary Teaching Activities" = "LI17"
-                                 ))
 
@@
 
-# creating new column with percentage of gender
+# creating new column with percent of gender
 demo.data <- demo.data %>%
@@
 # create new columns that give proportion of Gender
-# percentage = female gender divided by all female Gender
+# percent = female gender divided by all female Gender
 # demo.data <- demo.data  %>% 
 #   group_by(Group) %>% 
-#   mutate(Gender_percentage = Gender/Gender_Sum) %>% 
-#   mutate(Gender_percentage = round(sum(Gender_percentage)*100, digits=0))
+#   mutate(Gender_percent = Gender/Gender_Sum) %>% 
+#   mutate(Gender_percent = round(sum(Gender_percent)*100, digits=0))
 
@@
   summarise(N=n(),
-            "Gender female in percentage" = round(sum(Gender/Gender_Sum) * 100, digits = 1),
+            "Gender female in percent" = round(sum(Gender/Gender_Sum) * 100, digits = 1),
             "M Age in years" = round(mean(Age), 1),
@@
             "Max Internship in teaching units" = max(Internship),
-            "Extracurricular Teaching Experience in percentage" = round(sum(`Extracurricular Teaching Experience`/Gender_Sum) * 100, digits = 1),
-            "Secondary Teaching Activities in percentage" = round(sum(`Secondary Teaching Activities`/Gender_Sum) * 100)
+            "Extracurricular Teaching Experience in percent" = round(sum(`Extracurricular Teaching Experience`/Gender_Sum) * 100, digits = 1),
+            "Secondary Teaching Activities in percent" = round(sum(`Secondary Teaching Activities`/Gender_Sum) * 100)
            )
@@
 
-The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percentage")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r demo.table %>% filter(Group == "Expert") %>% pull("M Exp.
+The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r demo.table %>% filter(Group == "Expert") %>% pull("M Exp.
 in years") %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Exp.
@@
 in years")`).
-`r demo.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities in percentage")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
+`r demo.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities in percent")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
 
-The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percentage")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r demo.table %>% filter(Group == "Novice") %>% pull("M Exp.
+The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r demo.table %>% filter(Group == "Novice") %>% pull("M Exp.
 in years") %>% mean() %>% round(., digits = 1)` years.
@@
 Furthermore, they had an average teaching experience of `r demo.table %>% filter(Group == "Novice") %>% pull("M Internship in teaching units") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Internship in teaching units") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Internship in teaching units")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Internship in teaching units")`) through the internships during their studies.
-`r demo.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience in percentage")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
+`r demo.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience in percent")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
 
@@
 
-```{r presence_questionnaire, include=TRUE, echo=FALSE, results='asis'}
+```{r presence_questionnaire_novices, include=TRUE, echo=FALSE, results='asis'}
+# load data files
+quest.data <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% 
+  mutate(Group = ifelse(LI06_05 < 200, "Novice","Expert")) %>% 
+  dplyr::select(Group, LM01_01:LO01_02)
 
-# select relevant columns
-quest.data <- quest.data %>% dplyr::select(LM01_01:LO01_02, LI06_05)
+# create two data frames
+quest.data.novice <- quest.data %>% filter(Group == "Novice")
+quest.data.expert <- quest.data %>% filter(Group == "Expert")
 
-# rename columns
-quest.data <- rename(quest.data, c("Group" = "LI06_05"))
-
-# define expert and novice with ifelse function
-quest.data$Group = ifelse(quest.data$Group < 200, "Novice","Expert")
+############## NOVICE TABLE #########################
 
 # creating a matrix
-quest.table <- matrix(data = NA, nrow = 4, ncol = 8)
-rownames(quest.table) <- c("LM", "LB", "LP", "LV")
-  colnames(quest.table) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")
+quest.table.novice <- matrix(data = NA, nrow = 4, ncol = 8)
+rownames(quest.table.novice) <- c("LM", "LB", "LP", "LV")
+  colnames(quest.table.novice) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")
 
@@
 
-loop.data <- quest.data %>% 
+loop.data <- quest.data.novice %>% 
   dplyr::select(starts_with(match = i))
 
-quest.table[i, "N Items"] <- length(loop.data)
+quest.table.novice[i, "N Items"] <- length(loop.data)
 
@@
   round(., digits = 2) ->
-quest.table[i, "M"]
+quest.table.novice[i, "M"]
 
@@
   round(., digits = 2) ->
-quest.table[i, "SD"]
+quest.table.novice[i, "SD"]
 
@@
   round(., digits = 2) ->
-quest.table[i, "Min"]
+quest.table.novice[i, "Min"]
 
@@
   round(., digits = 2) ->
-quest.table[i, "Max"]
+quest.table.novice[i, "Max"]
 
@@
   round(., digits = 2) ->
-quest.table[i, "Skewness"]
+quest.table.novice[i, "Skewness"]
 
@@
   round(., digits = 2) ->
-quest.table[i, "Kurtosis"]
+quest.table.novice[i, "Kurtosis"]
 
@@
   cronbach.alpha()
-alpha$alpha
 
-quest.table[i, "alpha"] <- round(alpha$alpha,2)
+quest.table.novice[i, "alpha"] <- round(alpha$alpha,2)
 
@@
 # rename columns 
-rownames(quest.table) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")
+rownames(quest.table.novice) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")
 
@@
 papaja::apa_table(
-quest.table,
-  caption = "Scale analysis for teachers' self-assessment",
+quest.table.novice,
+  caption = "Scale analysis for novices' self-assessment",
+  # note = "Write Note here", 
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+)
+```
+
+```{r presence_questionnaire_experts, include=TRUE, echo=FALSE, results='asis'}
+
+############## EXPERT TABLE #########################
+
+# creating a matrix
+quest.table.expert <- matrix(data = NA, nrow = 4, ncol = 8)
+rownames(quest.table.expert) <- c("LM", "LB", "LP", "LV")
+  colnames(quest.table.expert) <- c("N Items","M","SD","Min","Max","Skewness","Kurtosis","alpha")
+
+# creating a loop 
+# i <- "LM"
+
+for (i in c("LM", "LB", "LP", "LV")) {
+
+loop.data <- quest.data.expert %>% 
+  dplyr::select(starts_with(match = i))
+
+quest.table.expert[i, "N Items"] <- length(loop.data)
+
+# calculating mean
+loop.data %>% 
+  mutate(mean = rowMeans(.)) %>% 
+  pull(mean) %>% 
+  mean() %>% 
+  round(., digits = 2) ->
+quest.table.expert[i, "M"]
+
+# calculating SD
+loop.data %>% 
+  mutate(mean = rowMeans(.)) %>% 
+  pull(mean) %>% 
+  sd() %>% 
+  round(., digits = 2) ->
+quest.table.expert[i, "SD"]
+
+# calculating Min
+loop.data %>% 
+  mutate(mean = rowMeans(.)) %>% 
+  pull(mean) %>% 
+  min() %>% 
+  round(., digits = 2) ->
+quest.table.expert[i, "Min"]
+
+# calculating Max
+loop.data %>% 
+  mutate(mean = rowMeans(.)) %>% 
+  pull(mean) %>% 
+  max() %>% 
+  round(., digits = 2) ->
+quest.table.expert[i, "Max"]
+
+# calculating Skewness
+loop.data %>% 
+  mutate(mean = rowMeans(.)) %>% 
+  pull(mean) %>% 
+  skewness() %>% 
+  round(., digits = 2) ->
+quest.table.expert[i, "Skewness"]
+
+# calculating Kurtosis
+loop.data %>% 
+  mutate(mean = rowMeans(.)) %>% 
+  pull(mean) %>% 
+  kurtosis() %>% 
+  round(., digits = 2) ->
+quest.table.expert[i, "Kurtosis"]
+
+# calculating alpha
+alpha <- loop.data %>% 
+  cronbach.alpha()
+
+quest.table.expert[i, "alpha"] <- round(alpha$alpha,2)
+
+}
+
+# rename columns 
+rownames(quest.table.expert) <- c("Classroom Management", "Balance", "Presence", "Natural Behavior")
+
+# format and insert table in manuscript
+papaja::apa_table(
+quest.table.expert,
+  caption = "Scale analysis for experts' self-assessment",
   # note = "Write Note here", 
@@
 
-# item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
+```
 
-# Classroom Management
+```{r item_analysis_classroom_management, include=TRUE, results='asis'}
+quest.data %>% 
+  dplyr::select(contains("LM")) %>% 
+  as.data.frame() %>% 
+  tab_itemscale(CSS = list(
+    css.firsttablerow.col7 = "'cronbachs alpha';"
+  ))
+```
 
+```{r item_analysis_balance, include=TRUE}
+# quest.data %>% 
+#   dplyr::select(contains("LB")) %>% 
+#   as.data.frame() %>% 
+#   tab_itemscale()
 ```

### 2022-04-27 02_paper/02_study/paper_methods.tex
method paper new table

--- 2022-04-20 02_paper/02_study/paper_methods.tex
@@
 
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:demographicstable}Demographic Information and Teaching Experience}
+
+\tiny{
+
+\begin{tabular}{lllllllllllllllllllll}
+\toprule
+Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years} & \multicolumn{1}{c}{M Exp.
+in years} & \multicolumn{1}{c}{SD Exp.
+in years} & \multicolumn{1}{c}{Min Exp.
+in years} & \multicolumn{1}{c}{Max Exp.
+in years} & \multicolumn{1}{c}{M Semester} & \multicolumn{1}{c}{SD Semester} & \multicolumn{1}{c}{Min Semester} & \multicolumn{1}{c}{Max Semester} & \multicolumn{1}{c}{M Internship in teaching units} & \multicolumn{1}{c}{SD Internship in teaching units} & \multicolumn{1}{c}{Min Internship in teaching units} & \multicolumn{1}{c}{Max Internship in teaching units} & \multicolumn{1}{c}{Extracurricular Teaching Experience in percent} & \multicolumn{1}{c}{Secondary Teaching Activities in percent}\\
+\midrule
+Expert & 7 & 71.40 & 45.10 & 12.00 & 27.00 & 59.00 & 18.10 & 14.10 & 3.00 & 37.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 71.00\\
+Novice & 21 & 61.90 & 23.30 & 1.70 & 20.00 & 27.00 & 0.00 & 0.00 & 0.00 & 0.00 & 7.40 & 2.50 & 3.00 & 11.00 & 12.00 & 8.60 & 0.00 & 36.00 & 90.50 & NA\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 The sample consists of \emph{N} = 28 participants with \emph{n} = 7 expert teachers and \emph{n} = 21 novice teachers.
@@
 
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:presence_questionnaire_novices}Scale analysis for novices' self-assessment}
+
+\tiny{
+
+\begin{tabular}{lllllllll}
+\toprule
+ & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
+\midrule
+Classroom Management & 8.00 & 2.94 & 0.26 & 2.50 & 3.38 & 0.02 & 1.69 & 0.31\\
+Balance & 3.00 & 3.14 & 0.56 & 1.67 & 4.00 & -0.45 & 3.53 & 0.71\\
+Presence & 8.00 & 3.10 & 0.36 & 2.50 & 3.88 & 0.10 & 2.65 & 0.66\\
+Natural Behavior & 3.00 & 3.17 & 0.65 & 1.67 & 4.00 & -0.65 & 2.91 & 0.80\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:presence_questionnaire_experts}Scale analysis for experts' self-assessment}
+
+\tiny{
+
+\begin{tabular}{lllllllll}
+\toprule
+ & \multicolumn{1}{c}{N Items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{alpha}\\
+\midrule
+Classroom Management & 8.00 & 3.00 & 0.20 & 2.75 & 3.25 & 0.25 & 1.42 & -0.16\\
+Balance & 3.00 & 3.43 & 0.42 & 2.67 & 4.00 & -0.57 & 2.87 & 0.41\\
+Presence & 8.00 & 3.36 & 0.45 & 2.50 & 3.88 & -0.85 & 2.95 & 0.84\\
+Natural Behavior & 3.00 & 3.38 & 0.36 & 3.00 & 4.00 & 0.60 & 2.36 & 0.00\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+Component 1
+
+Missings
+
+Mean
+
+SD
+
+Skew
+
+Item Difficulty
+
+Item Discrimination
+
+α if deleted
+
+0.00 \%
+
+3.32
+
+0.72
+
+-0.58
+
+0.83
+
+0.18
+
+0.10
+
+0.00 \%
+
+3.32
+
+0.55
+
+0.06
+
+0.83
+
+0.08
+
+0.19
+
+0.00 \%
+
+3.36
+
+0.56
+
+-0.07
+
+0.84
+
+-0.06
+
+0.26
+
+0.00 \%
+
+3.18
+
+0.67
+
+-0.22
+
+0.79
+
+0.25
+
+0.05
+
+0.00 \%
+
+2.32
+
+0.61
+
+-0.29
+
+0.77
+
+0.00
+
+0.23
+
+0.00 \%
+
+2.21
+
+0.63
+
+0.77
+
+0.55
+
+-0.30
+
+0.41
+
+0.00 \%
+
+2.96
+
+0.58
+
+-0.01
+
+0.74
+
+0.33
+
+0.02
+
+0.00 \%
+
+2.96
+
+0.69
+
+-0.67
+
+0.74
+
+0.21
+
+0.08
+
+Mean inter-item-correlation=0.028 · Cronbach's α=0.207
+
 \hypertarget{procedure}{%
@@
 
-All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{knitr} (Version 1.38; Xie, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), and \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b) and IBM SPSS 28.
+All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.
 
@@
 Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://cran.r-project.org/package=tinylabels}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-xtable}{}}%
+Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J. (2019). \emph{Xtable: Export tables to LaTeX or HTML}. Retrieved from \url{https://CRAN.R-project.org/package=xtable}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
+Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}
+
 \end{CSLReferences}

### 2022-05-04 02_paper/01_pilot/paper_1_supplement_questionnaire.Rmd
update workflow liste

@@
                           filter (scale == "Activation and support") %>%  
-                          select(shortID, value) %>%
+                          dplyr::select(shortID, value) %>%
                           group_by(shortID) %>%
@@
                           filter (scale == "Clarity and structuredness") %>%  
-                          select(shortID, value) %>%
+                          dplyr::select(shortID, value) %>%
                           group_by(shortID) %>%
@@
                           filter (scale == "Classroom management") %>%  
-                          select(shortID, value) %>%
+                          dplyr::select(shortID, value) %>%
                           group_by(shortID) %>%
@@
                           filter (scale == "Natural behaviour") %>%  
-                          select(shortID, value) %>%
+                          dplyr::select(shortID, value) %>%
                           group_by(shortID) %>%
@@
                           filter (scale == "Positive climate and motivation") %>%  
-                          select(shortID, value) %>%
+                          dplyr::select(shortID, value) %>%
                           group_by(shortID) %>%
@@
                           filter (scale == "Presence: posture/gaze") %>%  
-                          select(shortID, value) %>%
+                          dplyr::select(shortID, value) %>%
                           group_by(shortID) %>%
@@
                           filter (scale == "Presence: voice") %>%  
-                          select(shortID, value) %>%
+                          dplyr::select(shortID, value) %>%
                           group_by(shortID) %>%
@@
                           filter (scale == "Presence: verbal and non-verbal intervention") %>%  
-                          select(shortID, value) %>%
+                          dplyr::select(shortID, value) %>%
                           group_by(shortID) %>%
@@
                                          collapse = '|'))) %>% 
-                          select(shortID, value) %>%
+                          dplyr::select(shortID, value) %>%
                           group_by(shortID) %>%
@@
 
-# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
-# 
-# # activation & support
-# tab_itemscale(self.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # classroom management
-# tab_itemscale(self.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # clarity & structuredness
-# tab_itemscale(self.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # natural behaviour
-# tab_itemscale(self.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # postive clima and motivation
-# tab_itemscale(self.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence without subscales
-# tab_itemscale(self.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# 
-# # presence: posture & gaze
-# tab_itemscale(self.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: voice
-# tab_itemscale(self.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
-# # presence: verbal/non-verbal intervention
-# tab_itemscale(self.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
+
+# activation & support
+tab_itemscale(self.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# classroom management
+tab_itemscale(self.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# clarity & structuredness
+tab_itemscale(self.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# natural behaviour
+tab_itemscale(self.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# postive clima and motivation
+tab_itemscale(self.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# presence without subscales
+tab_itemscale(self.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+
+# presence: posture & gaze
+tab_itemscale(self.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# presence: voice
+tab_itemscale(self.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
+# presence: verbal/non-verbal intervention
+tab_itemscale(self.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
 

### 2022-05-19 02_paper/02_study/paper_methods.Rmd
update R scripts SJT

@@
 floatsintext      : no
-figsintext        : yes
-figurelist        : yes
+figsintext        : no
+figurelist        : no
 tablelist         : yes
@@
             "Min Age in years" = min(Age),
-            "Max Age in years" = max(Age),
-            "M Exp. in years" = round(mean(`Teaching Experience`), 1),
-            "SD Exp. in years" = round(sd(`Teaching Experience`), 1),
-            "Min Exp. in years" = min(`Teaching Experience`),
-            "Max Exp. in years" = max(`Teaching Experience`),
-            "M Semester" = round(mean(Semester), 1),
-            "SD Semester" = round(sd(Semester), 1),
-            "Min Semester" = min(Semester),
-            "Max Semester" = max(Semester),
-            "M Internship in teaching units" = round(mean(Internship), 1),
-            "SD Internship in teaching units" = round(sd(Internship), 1),
-            "Min Internship in teaching units" = min(Internship),
-            "Max Internship in teaching units" = max(Internship),
-            "Extracurricular Teaching Experience in percent" = round(sum(`Extracurricular Teaching Experience`/Gender_Sum) * 100, digits = 1),
-            "Secondary Teaching Activities in percent" = round(sum(`Secondary Teaching Activities`/Gender_Sum) * 100)
+            "Max Age in years" = max(Age)
             )
@@
 papaja::apa_table(
-  caption = "Demographic Information and Teaching Experience",
+  caption = "Demographic Information",
+  # note = "Write Note here",
+  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
+  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
+  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
+  )
+
+# create a basic table (tibble) using tidyverse functions
+exp.table <- demo.data %>%
+  group_by(Group) %>%
+  summarise(N=n(),
+           "M Exp." = round(mean(`Teaching Experience`), 1),
+            "SD Exp." = round(sd(`Teaching Experience`), 1),
+            "Min Exp." = min(`Teaching Experience`),
+            "Max Exp." = max(`Teaching Experience`),
+            "M Semester" = round(mean(Semester), 1),
+            "SD Semester" = round(sd(Semester), 1),
+            "Min Semester" = min(Semester),
+            "Max Semester" = max(Semester),
+            "M Internship" = round(mean(Internship), 1),
+            "SD Internship" = round(sd(Internship), 1),
+            "Min Internship" = min(Internship),
+            "Max Internship" = max(Internship),
+            "Extracurricular Teaching Experience" = round(sum(`Extracurricular Teaching Experience`/Gender_Sum) * 100, digits = 1),
+            "Secondary Teaching Activities" = round(sum(`Secondary Teaching Activities`/Gender_Sum) * 100)
+           )
+
+# format and insert table in manuscript
+exp.table %>%
+papaja::apa_table(
+  caption = "Teaching Experience in years, internship experience in teaching units (45min) and extracurricular teaching experience in percent",
   # note = "Write Note here",
@@
 
-The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r demo.table %>% filter(Group == "Expert") %>% pull("M Exp.
-in years") %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Exp.
-in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Exp.
-in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Exp.
-in years")`).
-`r demo.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities in percent")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
+The expert teachers (`r demo.data %>% filter(Gender == 1 & Group == "Expert") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Expert") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Expert") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Expert") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Expert") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Expert") %>% pull("Max Age in years")`) and an average teaching experience of `r exp.table %>% filter(Group == "Expert") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years (*SD* = `r exp.table %>% filter(Group == "Expert") %>% pull("SD Exp.") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Expert") %>% pull("Min Exp.")`-`r exp.table %>%  filter(Group == "Expert") %>% pull("Max Exp.")`).
+`r exp.table %>% filter(Group == "Expert") %>% pull("Secondary Teaching Activities")`% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
 
-The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r demo.table %>% filter(Group == "Novice") %>% pull("M Exp.
-in years") %>% mean() %>% round(., digits = 1)` years.
-On average, the student teachers were in their `r demo.table %>% filter(Group == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Semester")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Semester")`).
-Furthermore, they had an average teaching experience of `r demo.table %>% filter(Group == "Novice") %>% pull("M Internship in teaching units") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Internship in teaching units") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Internship in teaching units")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Internship in teaching units")`) through the internships during their studies.
-`r demo.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience in percent")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
+The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years.
+On average, the student teachers were in their `r exp.table %>% filter(Group == "Novice") %>% pull("M Semester") %>% mean() %>% round(., digits = 1)` semester (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Semester") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Semester")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Semester")`).
+Furthermore, they had an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Internship") %>% mean() %>% round(., digits = 1)` teaching units à 45min (*SD* = `r exp.table %>% filter(Group == "Novice") %>% pull("SD Internship") %>% round(., digits = 1)`; range: `r exp.table %>%  filter(Group == "Novice") %>% pull("Min Internship")`-`r exp.table %>%  filter(Group == "Novice") %>% pull("Max Internship")`) through the internships during their studies.
+`r exp.table %>% filter(Group == "Novice") %>% pull("Extracurricular Teaching Experience")`% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
 
@@
 ```{r item_analysis_classroom_management, include=TRUE, results='asis'}
-quest.data %>% 
-  dplyr::select(contains("LM")) %>% 
-  as.data.frame() %>% 
-  tab_itemscale(CSS = list(
-    css.firsttablerow.col7 = "'cronbachs alpha';"
-  ))
+# quest.data %>% 
+#   dplyr::select(contains("LM")) %>% 
+#   as.data.frame() %>% 
+#   tab_itemscale(CSS = list(
+#     css.firsttablerow.col7 = "'cronbachs alpha';"
+#   ))
 ```
 
-```{r item_analysis_balance, include=TRUE}
+```{r item_analysis_balance, include=TRUE, results='asis'}
 # quest.data %>%
@@
 
+```{r item_analysis_presence, include=TRUE,results='asis'}
+# quest.data %>%
+#   dplyr::select(contains("LP")) %>%
+#   as.data.frame() %>%
+#   tab_itemscale()
+```
+
+```{r item_analysis_behavior, include=TRUE,results='asis'}
+# quest.data %>%
+#   dplyr::select(contains("LV")) %>%
+#   as.data.frame() %>%
+#   tab_itemscale()
+```
+
 ## Procedure
 
-In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021, and July 2022.
+In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and August 2022.
+
+The project was conducted as a laboratory study in a cross-sectional study design to investigate whether and how teachers' experience has an influence on the perception of and reaction to classroom disruptions.
+
+For the data collection, student teachers and experienced teachers were asked to prepare micro-teaching-unit of 15 minutes.
+The subjects taught the micro-teaching-unit in front of a fictitious class consisting of three student assistants who simulated typical classroom events during the lesson.
+A mobile eye-tracker recorded the subject's gaze behavior and audio data of the lesson.
+All other sounds and voices were recorded by an audio recorder.
+In addition, the test persons were given a smartwatch to record the number of steps they took and their heart rate.
+To record facial expressions, gestures and movements, four mobile cameras were installed to record the classroom from all perspectives (!!!see figures).
+After the micro-teaching-unit, the teacher conducted a letter search in the room.
+For this, four letters had to be found in order and read aloud.
+This served as a control condition for the speed of the subjects' perceptual ability.
+of the test persons. After the end of the teaching sequence, the class and the teacher
+After the end of the teaching sequence, the class and the teacher filled out a questionnaire focusing on evidence-based methods of teaching diagnostics (EMU) in order to collect data on self-assessment and assessment by others.
+
+In the second part of the survey, the investigator conducted a Stimulated-
+Recall Interview (SRI) with the respondents.
+In this interview, the recorded video of the lesson was watched in its entirety and commented on by the teacher while thinking aloud.
+Finally, the test persons answered a Situational Judgement Test (SJT, [@gold2015development]) in the form of a questionnaire.
+Here they had to assess teaching scenarios and evaluate their behavior in response to them.
+The SJT was used to assess strategic knowledge about classroom management.
+
+This study is subject to a quasi-experimental study design, as there was no random assignment of the test persons to the experimental conditions.
+Due to the use of MET technology, the study has a high external validity (Gegenfurtner et al., 2018).
+The SRI carried out afterwards explicitly investigates the subjects' sense of disturbance and feeling of safety, which speaks for a high content validity of the study.
+Internal validity can be ensured to the extent that the teaching events that occurred were exactly the same for all subjects, as the learners received precise behavioural instructions.
+These disturbances followed a script and coding guide in which the actions of the class were precisely described.
+The sequence of events varied from survey to survey so that disruptions were always random.
+The scripted behavioural instructions during the teaching sequence characterise this study with a high degree of standardization, especially when compared to events taking place in a real classroom.
+The study is based on an experimental manual, script and coding guide, which explicitly describes the implementation, evaluation as well as interpretation of the data, thus making it objectively recordable and measurable.
+As this study takes place within the framework of the dissertation ProVisioNET, the original survey will continue beyond the submission of this scientific work.
+continues.
 

### 2022-05-19 02_paper/02_study/paper_methods.tex
update R scripts SJT

@@
 \usepackage[titles]{tocloft}
-\cftpagenumbersoff{figure}
-\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
-\renewcommand{\cftfigaftersnum}{.\space}
-\setlength{\cftfigindent}{0pt}
-\setlength{\cftafterloftitleskip}{0pt}
-\settowidth{\cftfignumwidth}{Figure 10.\qquad}
 \cftpagenumbersoff{table}
@@
 
-\caption{\label{tab:demographicstable}Demographic Information and Teaching Experience}
+\caption{\label{tab:demographicstable}Demographic Information}
 
@@
 
-\begin{tabular}{lllllllllllllllllllll}
+\begin{tabular}{lllllll}
 \toprule
-Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years} & \multicolumn{1}{c}{M Exp.
-in years} & \multicolumn{1}{c}{SD Exp.
-in years} & \multicolumn{1}{c}{Min Exp.
-in years} & \multicolumn{1}{c}{Max Exp.
-in years} & \multicolumn{1}{c}{M Semester} & \multicolumn{1}{c}{SD Semester} & \multicolumn{1}{c}{Min Semester} & \multicolumn{1}{c}{Max Semester} & \multicolumn{1}{c}{M Internship in teaching units} & \multicolumn{1}{c}{SD Internship in teaching units} & \multicolumn{1}{c}{Min Internship in teaching units} & \multicolumn{1}{c}{Max Internship in teaching units} & \multicolumn{1}{c}{Extracurricular Teaching Experience in percent} & \multicolumn{1}{c}{Secondary Teaching Activities in percent}\\
+Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years}\\
 \midrule
-Expert & 7 & 71.40 & 45.10 & 12.00 & 27.00 & 59.00 & 18.10 & 14.10 & 3.00 & 37.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 71.00\\
-Novice & 21 & 61.90 & 23.30 & 1.70 & 20.00 & 27.00 & 0.00 & 0.00 & 0.00 & 0.00 & 7.40 & 2.50 & 3.00 & 11.00 & 12.00 & 8.60 & 0.00 & 36.00 & 90.50 & NA\\
+Expert & 7 & 71.40 & 45.10 & 12.00 & 27.00 & 59.00\\
+Novice & 21 & 61.90 & 23.30 & 1.70 & 20.00 & 27.00\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:demographicstable}Teaching Experience in years, internship experience in teaching units (45min) and extracurricular teaching experience in percent}
+
+\tiny{
+
+\begin{tabular}{llllllllllllllll}
+\toprule
+Group & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{M Exp.} & \multicolumn{1}{c}{SD Exp.} & \multicolumn{1}{c}{Min Exp.} & \multicolumn{1}{c}{Max Exp.} & \multicolumn{1}{c}{M Semester} & \multicolumn{1}{c}{SD Semester} & \multicolumn{1}{c}{Min Semester} & \multicolumn{1}{c}{Max Semester} & \multicolumn{1}{c}{M Internship} & \multicolumn{1}{c}{SD Internship} & \multicolumn{1}{c}{Min Internship} & \multicolumn{1}{c}{Max Internship} & \multicolumn{1}{c}{Extracurricular Teaching Experience} & \multicolumn{1}{c}{Secondary Teaching Activities}\\
+\midrule
+Expert & 7 & 18.10 & 14.10 & 3.00 & 37.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 71.00\\
+Novice & 21 & 0.00 & 0.00 & 0.00 & 0.00 & 7.40 & 2.50 & 3.00 & 11.00 & 12.00 & 8.60 & 0.00 & 36.00 & 90.50 & NA\\
 \bottomrule
@@
 
-Component 1
-
-Missings
-
-Mean
-
-SD
-
-Skew
-
-Item Difficulty
-
-Item Discrimination
-
-α if deleted
-
-0.00 \%
-
-3.32
-
-0.72
-
--0.58
-
-0.83
-
-0.18
-
-0.10
-
-0.00 \%
-
-3.32
-
-0.55
-
-0.06
-
-0.83
-
-0.08
-
-0.19
-
-0.00 \%
-
-3.36
-
-0.56
-
--0.07
-
-0.84
-
--0.06
-
-0.26
-
-0.00 \%
-
-3.18
-
-0.67
-
--0.22
-
-0.79
-
-0.25
-
-0.05
-
-0.00 \%
-
-2.32
-
-0.61
-
--0.29
-
-0.77
-
-0.00
-
-0.23
-
-0.00 \%
-
-2.21
-
-0.63
-
-0.77
-
-0.55
-
--0.30
-
-0.41
-
-0.00 \%
-
-2.96
-
-0.58
-
--0.01
-
-0.74
-
-0.33
-
-0.02
-
-0.00 \%
-
-2.96
-
-0.69
-
--0.67
-
-0.74
-
-0.21
-
-0.08
-
-Mean inter-item-correlation=0.028 · Cronbach's α=0.207
-
 \hypertarget{procedure}{%
@@
 
-In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021, and July 2022.
+In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and August 2022.
+
+The project was conducted as a laboratory study in a cross-sectional study design to investigate whether and how teachers' experience has an influence on the perception of and reaction to classroom disruptions.
+
+The subjects were informed in detail about the procedure and aim of the study before the survey.
+For the data collection, student teachers and experienced teachers were asked to prepare micro-teaching-unit of 15 minutes.
+The subjects taught the micro-teaching-unit to a fictitious class consisting of three student assistants who simulated typical classroom events during the lesson.
+A mobile eye-tracker recorded the teachers' gaze behavior and audio data of the lesson.
+All other sounds and voices were also recorded using audio recorders.
+In addition, the test persons were given a smartwatch to record the number of steps they took and their pulse rate.
+To record facial expressions, gestures and movements, four mobile cameras were installed to record the fictitious classroom from all perspectives (see figures 5-8).
+After the lesson, the teacher conducted a letter search in the room.
+For this, four letters had to be found in order and read aloud.
+This served as a control condition for the speed of the subjects' perceptual ability.
+of the test persons. After the end of the teaching sequence, the class and the teacher
+After the end of the teaching sequence, the class and the teacher filled out a questionnaire focusing on evidence-based methods of teaching diagnostics (EMU) in order to collect data on self-assessment and assessment by others.
+
+In the second part of the survey, the investigator conducted a Stimulated-
+Recall Interview (SRI) with the respondents.
+In this interview, the recorded video of the lesson was watched in its entirety and commented on by the teacher while thinking aloud.
+Finally, the test persons answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)) in the form of a questionnaire.
+Here they had to assess teaching scenarios and evaluate their behavior in response to them.
+The SJT was used to assess strategic knowledge about classroom management.
+
+This study is subject to a quasi-experimental study design, as there was no random assignment of the test persons to the experimental conditions.
+Due to the use of MET technology, the study has a high external validity (Gegenfurtner et al., 2018).
+The SRI carried out afterwards explicitly investigates the subjects' sense of disturbance and feeling of safety, which speaks for a high content validity of the study.
+Internal validity can be ensured to the extent that the teaching events that occurred were exactly the same for all subjects, as the learners received precise behavioural instructions.
+These disturbances followed a script and coding guide in which the actions of the class were precisely described.
+The sequence of events varied from survey to survey so that disruptions were always random.
+The scripted behavioural instructions during the teaching sequence characterise this study with a high degree of standardization, especially when compared to events taking place in a real classroom.
+The study is based on an experimental manual, script and coding guide, which explicitly describes the implementation, evaluation as well as interpretation of the data, thus making it objectively recordable and measurable.
+As this study takes place within the framework of the dissertation ProVisioNET, the original survey will continue beyond the submission of this scientific work.
+continues.
 
@@
 Garnier, Simon, Ross, Noam, Rudis, Robert, \ldots{} Cédric. (2021b). \emph{{viridis} - colorblind-friendly color maps for r}. \url{https://doi.org/10.5281/zenodo.4679424}
+
+\leavevmode\vadjust pre{\hypertarget{ref-gold2015development}{}}%
+Gold, B., \& Holodynski, M.
+(2015).
+Development and construct validation of a situational judgment test of strategic knowledge of classroom management in elementary schools.
+\emph{Educational Assessment}, \emph{20}(3), 226--248.
 
@@
 \clearpage
-\renewcommand{\listfigurename}{Figure captions}
-
-\clearpage
 \renewcommand{\listtablename}{Table captions}

### 2022-05-19 01_studies/01_Laborstudie ProVisioNET/SJTest/SJTest.R

@@ -12,8 +12,13 @@ needs(tidyverse,
 # read in data
 df_sjt <- read_csv2(file = "C:/Users/mk99feta/OneDrive/Dokumente/GitHub/Mandy-PhD/01_studies/01_Laborstudie ProVisioNET/SJTest/data/SJT.csv")
 
-# select relevant columns --> only mean
-df_sjt <- df_sjt %>% select(UI06_05, SJT_AL_gek, SJT_ST_gek, SJT_R_gek, SJT_KF_gek)
+# select relevant columns --> only subject ID and mean
+df_sjt <- df_sjt %>% 
+  select(UI06_05, 
+         SJT_AL_gek, 
+         SJT_ST_gek, 
+         SJT_R_gek, 
+         SJT_KF_gek)
 
 # rename columns
 df_sjt <- rename(df_sjt, c("Group" = "UI06_05",
@@ -58,6 +63,12 @@ mean_plot <-
     axis.title.x = element_text(size = 25))
 
 mean_plot
+
+ggsave(plot = mean_plot,
+       filename = "plots/sjt_plot.pdf",
+       height = 7,
+       width = 9,
+       units = "in")
 
 #################### MEAN, SD, N ############
 

### 2022-05-27 02_paper/02_study/paper_methods.tex
update method section

@@
 \urlstyle{same} % disable monospaced font for URLs
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 
-\hypertarget{eye-tracking-equipment}{%
-\subsubsection{Eye-Tracking equipment}\label{eye-tracking-equipment}}
+Experimental stimuli are freely available in the following online repository: \url{https://github.com/}\ldots{} .
 
-During the unit, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker (\url{https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/}).
+\hypertarget{eye-tracking-data}{%
+\subsubsection{Eye-Tracking data}\label{eye-tracking-data}}
+
+During the lesson, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker (\url{https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/}).
 The system consisted of a wearable head unit and a recording unit.
@@
 An integrated microphone recorded the surrounding sounds.
-Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capure the tacher's gaze point as shown in Figure \ref{fig:teachergazepoint}.
+Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capture the teacher's gaze point as shown in Figure \ref{fig:teachersgaze}.
 The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second.
@@
 
-{\centering \includegraphics{./pictures/teachergazepoint}
+{\centering \includegraphics{./pictures/teachersgaze}
 
@@
 
-\caption{Teacher's Gaze Point}\label{fig:teachergazepoint}
+\caption{Teacher's Gaze Point}\label{fig:teachersgaze}
 \end{figure}
 
-\hypertarget{video-and-audio-recording-equipment}{%
-\subsubsection{Video and Audio recording equipment}\label{video-and-audio-recording-equipment}}
+\hypertarget{behavioral-data}{%
+\subsubsection{Behavioral data}\label{behavioral-data}}
 
@@
 
-\hypertarget{questionnaire}{%
-\subsubsection{Questionnaire}\label{questionnaire}}
+\hypertarget{questionnaire-data}{%
+\subsubsection{Questionnaire data}\label{questionnaire-data}}
 
-After each micro-teaching-unit, the students answered items on teaching quality using a validated questionnaire (Helmke et al., 2014) and scales on the teacher's presence behavior.
-In addition, participants were asked to give a self-assessment on classroom management by completing the questionnaire after each micro-teaching-unit.
+After each micro-teaching-unit, the three actors answered items on teaching quality using a validated questionnaire (Helmke et al., 2014) and self developed scales on the teacher's presence behavior derived from the research literature.
+In addition, subjects were asked to give a self-assessment on classroom management by completing the same questionnaire after each micro-teaching-unit.
 The questionnaire was a 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
@@
 
+\hypertarget{verbal-data}{%
+\subsubsection{Verbal data}\label{verbal-data}}
+
+In addition to the eye-tracking, questionnaire and behavioral data, verbal data was also collected in the form of a Stimulated Recall Interview.
+
+\ref{fig:sri}
+
+\begin{figure}
+
+{\centering \includegraphics{./pictures/sri}
+
+}
+
+\caption{Subject and experimenter during the Stimulated Recall Interview}\label{fig:sri}
+\end{figure}
+
 \hypertarget{procedure}{%
@@
 
-In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and August 2022.
-
 The project was conducted as a laboratory study in a cross-sectional study design to investigate whether and how teachers' experience has an influence on the perception of and reaction to classroom disruptions.
 
-The subjects were informed in detail about the procedure and aim of the study before the survey.
-For the data collection, student teachers and experienced teachers were asked to prepare micro-teaching-unit of 15 minutes.
-The subjects taught the micro-teaching-unit to a fictitious class consisting of three student assistants who simulated typical classroom events during the lesson.
-A mobile eye-tracker recorded the teachers' gaze behavior and audio data of the lesson.
-All other sounds and voices were also recorded using audio recorders.
-In addition, the test persons were given a smartwatch to record the number of steps they took and their pulse rate.
-To record facial expressions, gestures and movements, four mobile cameras were installed to record the fictitious classroom from all perspectives (see figures 5-8).
-After the lesson, the teacher conducted a letter search in the room.
+In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and \ldots{} 2022.
+
+Before the data collection, each subject received a personal digital meeting with the experimenter to go over the study procedure and to arrange a date for the data collection.
+During the digital meeting, the subjects were asked to prepare a 15-minute lesson in a subject and grade of their choice for the data collection.
+
+On the day of a data collection, the first step was to set up the study room at the University of Leipzig.
+For this, all the appropriate technical equipment was charged and installed in the room (see set up plan {[}REFERENZ EINFÜGEN{]}).
+Next, all four cameras and the audio recorder were synced via Timecode System.
+
+After the subject arrived, a smart watch was put on to measure the heart rate during the session and to get a pretest time at least 15min before the session started.
+In addition to the experimenter and the subject, three student assistants from the working group always took part in the data collection, as they represented the class.
+
+After the welcome, the subject was again briefed about the study.
+It was explicitly pointed out that the student assistants would act as the class and simulate typical class events during the lesson.
+The subject was asked in advance to behave as naturally as possible during the entire time.
+Next, the subjects' written informed consent was obtained and contact details were collected in order to inform all persons participating in the study if a covid infection should occur.
+
+After the introduction, the eye-tracking glasses were adjusted for the subject by inserting contact lenses if necessary and changing the nose pad.
+To start the eye tracking glasses, the Tobii Glasses must be fitted onto the subject's head via an one-point-calibration.
+In the calibration process the subject was asked to look at a Calibration Card held in-front of the subject for a few seconds.
+The experimenter started the recording from Tobii Glasses Controller Software running on a computer.
+
+After starting the eye tracking recording, all other technical devices were also switched on: The four cameras and the audio recorder were controlled via iPad using the BLINK Hup app and could be started simultaneously by synchronization.
+The ZED camera was started manually on another laptop.
+
+Before the 15-minute lesson, there was a short 10-minute warm-up phase.
+The phase was divided into two parts and served on the one hand to get the subjects used to the eye-tracking glasses and on the other hand to get used to their class.
+In the first phase of the warm-up, the game ``name juggling'' was played using two balls.
+In the game, the subject and the three actors threw two balls at each other and, depending on the color of the ball, called either their own name or that of the target person.
+After the name juggling, the subjects were supposed to start a conversation.
+For this, the subject thought of a question for each student and was also asked a question of each student.
+The content could be anything that interested the participants.
+
+After the warm up phase, the experimenter ensured a manual synchronization of the technique by an acoustic signal in which she clapped her hands loudly twice standing in the middle of the room.
+After this, another nine-point calibration followed outside the study room in a neighboring room.
+Before the subject left the room for calibration, the time on the smartwatch was noted, as well as the steps recorded until that point.
+The subject had to stand at a marked point and look at a board three meters away with nine april tags.
+The subject was asked to read the nine points aloud in order at a normal speaking speed.
+This procedure was important to validate the one-point calibration on the one hand and on the other hand to give the subject the feeling of a lesson start, because after this calibration the subject came into the study room to start the 15-minute lesson.
+
+For the micro-teaching lesson, student teachers and experienced teachers were asked to prepare an introduction of 15 minutes which they taught in front of the fictitious class consisting of three student assistants.
+The actors simulated the nine classroom events during the lesson, derived by research literature.
+The order of the disruptions as well as the students performing them were fully balanced using Latin Square.
+
+\begin{longtable}[]{@{}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
+  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\centering
+verbal disruption
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+agitation
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+lack of eagerness to learn
+\end{minipage} \\
+\midrule
+\endhead
+chatting with neighbor & drumming hands & putting head on table \\
+whispering with neighbor & clicking pen & looking at phone \\
+heckling & snipping with fingers & drawing on a sheet of paper \\
+\bottomrule
+\end{longtable}
+
+The experimenter used time cards to indicate the time remaining (yellow = one minute remaining; red = time expired).
+
+A mobile eye-tracker recorded the subject's gaze behavior and audio data of the lesson.
+All other sounds and voices were recorded by an audio recorder.
+To record facial expressions, gestures and movements, four mobile cameras were installed to record the classroom from all perspectives (!!!see figures).
+After the micro-teaching-unit, the teacher conducted a letter search in the room.
 For this, four letters had to be found in order and read aloud.
 This served as a control condition for the speed of the subjects' perceptual ability.
+
 of the test persons. After the end of the teaching sequence, the class and the teacher
@@
 
-In the second part of the survey, the investigator conducted a Stimulated-
-Recall Interview (SRI) with the respondents.
-In this interview, the recorded video of the lesson was watched in its entirety and commented on by the teacher while thinking aloud.
+In the second part of the study, the experimenter conducted a Stimulated-Recall Interview (SRI) with the subject.
+In this interview, the recorded video of the lesson was watched and commented on by the subject while thinking aloud.
+
 Finally, the test persons answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)) in the form of a questionnaire.

### 2022-05-28 02_paper/01_pilot/examples/full_paper/manuscript.Rmd

---
title             : "Predicting pragmatic cue integration in adults’ and children’s inferences about novel word meanings"
shorttitle        : "Pragmatic cue integration"

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "manuel_bohn@eva.mpg.de"
  - name          : "Michael Henry Tessler"
    affiliation   : "2"
  - name          : "Megan Merrick"
    affiliation   : "3"
  - name          : "Michael C. Frank"
    affiliation   : "3"

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
  - id            : "2"
    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
  - id            : "3"
    institution   : "Department of Psychology, Stanford University"

abstract: |
  Language is learned in complex social settings where listeners must reconstruct speakers’ intended meanings from context. To navigate this challenge, children can use pragmatic reasoning to learn the meaning of unfamiliar words. One important challenge for pragmatic reasoning is that it requires integrating multiple information sources. Here we study this integration process. We isolate two sources of pragmatic information and -- using a probabilistic model of conversational reasoning -- formalize how they should be combined and how this process might develop. We use this model to generate quantitative predictions, which we test againsbibliography      : ["library.bib"]
t new behavioral data from three- to five-year-old children (N = 243) and adults (N = 694). Results show close numerical alignment between model predictions and data. Furthermore, the model provided a better explanation of the data compared to simpler alternative models assuming that participnats selectively ignore one information source. This work integrates distinct sets of findings regarding early language and suggests that pragmatic reasoning models can provide a quantitative framework for understanding developmental changes in language learning.

keywords          : "language acquisition, social cognition, pragmatics, Bayesian modeling, common ground"
wordcount         : "7708"

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
# load packages and functions

knitr::opts_chunk$set(echo = F, include = F, out.width = "\\textwidth", fig.pos = "!h")

library("papaja")
library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(matrixStats)
library(coda)
#library(ggpubr)
library(lme4)
library(broom)
library(broom.mixed)
library(readxl)
library(lsr)

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

```

```{r data}
# load data files

# adults exp 1 
adult_ex1_data <- read_csv(file="../../stats/data/adult_ex1.csv")
# adults exp 2 novelty
adult_ex2_novelty_data <- read_csv(file="../../stats/data/adult_ex2_novelty.csv")
# adults exp 2 preference
adult_ex2_preference_data <- read_csv(file="../../stats/data/adult_ex2_preference.csv")
# adults ex3
adult_ex3_data <-read_csv(file="../../stats/data/adult_ex3.csv")
# prior strength manipulation experiments in experiment 4
adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
# adults ex4
adult_ex4_data <-read_csv(file="../../stats/data/adult_ex4.csv")

# children ex1
child_ex1_data <-read_csv(file="../../stats/data/child_ex1.csv")
# children ex2 preference
child_ex2_data <-read_csv(file="../../stats/data/child_ex2.csv") 
# children ex3
child_ex3_data <-read_csv(file="../../stats/data/child_ex3.csv") 
```

# Introduction

What someone means by an utterance is oftentimes not reducible to the words they used. It takes pragmatic inference – context-sensitive reasoning about the speaker’s intentions - to recover the intended meaning [@grice1991studies; @levinson2000presumptive; @sperber2001relevance]. Contextual information comes in many forms. On the one hand, there is information provided by the utterance^[
We use the terms utterance, utterance-level information or utterance-level cues to capture all cues that the speaker provides for their intended meaning. This includes direct referential information in the form of pointing or gazing, semantic information in the form of conventional word meanings as well as pragmatic inferences that are licenced by the particular choice of words or actions.] itself. Competent language users expect each other to communicate in a cooperative way such that speakers produce utterances that are relevant and informative. Thus, semantic ambiguity can be resolved by reasoning about why the speaker produced this particular utterance [@grice1991studies; @clark1996using; @sperber2001relevance; @tomasello2008origins]. On the other hand, there is information provided by common ground [the body of mutually shared knowledge and beliefs between interlocutors; @bohn2018common; @clark1996using; @clark2015common]. Because utterances are embedded in common ground, pragmatic reasoning in context always requires information integration. But how does integration proceed? And how does it develop? Verbal theories assume that information is integrated and that this process develops but do not specify how. We bridge this gap by formalizing information integration and development in a probabilistic model of pragmatic reasoning.

Children learning their first language make inferences about intended meanings based on utterance-level and common ground information -- both for language understanding and language learning [@bohn2019pervasive; @clark2009first; @tomasello2008origins]. Starting very early, infants expect adults to produce utterances in a cooperative way [@behne2005one], and expect language to be carrying information [@vouloumanos2012twelve]. By age two, children are sensitive to the informativeness of communication [@o2001two]. By age three, children can use this expectation to make pragmatic inferences [@stiller2015ad; @yoon2019role] and to infer novel word meanings [@frank2014inferring]. And although older children continue to struggle with some complex pragmatic inferences until age five and beyond [@noveck2001children], an emerging consensus identifies these difficulties as stemming from difficulties reasoning about linguistic alternatives rather than pragmatic deficits [@skordos2016children; @horowitz2018trouble; @barner2011accessing]. Thus, children’s ability to reason about utterance-level pragmatics is present at least by ages three to five, and possibly substantially younger.

What about common ground information? Before reviewing the developmental literature, we want to briefly clarify how we use the term *common ground* in this paper. In the adult literature, common ground has traditionally been defined in recursive terms: in order to be part of common ground, some piece of information has to be not just known to both interlocutors but also known to both to be shared between them [@clark1996using]. Numerous studies probed the role of sharedness of information and found that it plays a critical role in communicative interactions [@brown2009partner; @hanna2003effects; @heller2016perspective; @mozuraitis2015privileged]. Based on this literature, one might argue that the term common ground should be restricted to describe situations in which the sharedness aspect is directly tested. However, most of this work is focused on online perspective taking. In this paper, we use the term common ground to refer to shared information that is built up over the course of an interaction - something that is likely easier for children [@matthews2006effect]. We assume that the consequence of a direct interaction (with matching perspectives) between the speaker and the listener is that information is mutually manifest; that is, not just known to both interlocutors but also assumed to be shared between them [@bohn2018common] and hence part of common ground. Thus, since this information is unproblematically in common ground, we can focus on how this information integrates with other pragmatic information sources. Construed this way, evidence for the use of common ground information by young children is strong already very early in life. For example, speaker specific contextual expectations guide how infants produce non-verbal gestures and interpret ambiguous utterances [@bohn2018social; @saylor2011s]. For slightly older children, common ground – in the form of knowledge about discourse novelty, preferences, and even discourse expectations – also facilitates word learning [@akhtar1996role; @bohn_le_peloquin_koymen_frank_2020; @saylor2009preschoolers; @sullivan2019discourse].

The examples discussed above, however, highlight children’s use of a single pragmatic information source or cue. Harnessing multiple – potentially competing – pragmatic cues poses a separate challenge. One aspect of this integration problem is how to balance common ground information that is built up over the course of an interaction against information gleaned from the current utterance. Much less is known about whether and how children combine these types of information. Developmental studies that look at the integration of multiple information sources more generally find that children are sensitive to multiple sources from early on [@graham2017words; @grosse201021; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers; @ganea2007infants]. For example, in a classic study, Nadig and Sedivy [-@nadig2002evidence] found that children rapidly integrate information provided in an utterance (a particular referring expression) with the speaker’s perspective (the objects the speaker can see). However, the information sources to be integrated in these studies are not all pragmatic in nature. Children’s ability to pick out a referent following a noun reflects their linguistic knowledge and not necessarily their ability to reason about the speaker’s intention in context. As a consequence, this work does not speak to the question of how and if listeners integrate different forms of *pragmatic* information. Thus, while many theories of pragmatic reasoning presuppose that pragmatic information sources are integrated, the nature of their relationship has typically not been specified.

Recent innovations in probabilistic models of pragmatic reasoning provide a quantitative method for addressing the problem of integrating multiple sources of contextual information. This class of computational models, which are referred to as Rational Speech Act (RSA) models [@frank2012predicting; @goodman2016pragmatic] formalize the problem of language understanding as a special case of Bayesian social reasoning. A listener interprets an utterance by assuming it was produced by a cooperative speaker who had the goal to be informative. Being informative is defined as providing a message that would increase the probability of the listener recovering the speaker’s intended meaning in context. This notion of contextual informativeness captures the Gricean idea of cooperation between speaker and listener, and provides a first approximation to what we have described above as utterance-level pragmatic information.

Within the RSA framework, one way to incorporate common ground is to treat it as a conversational prior. That is, to assume that social interactions result in prior distributions over possible intended meanings which are specific to a particular speaker. Following this logic, a natural locus for information integration within probabilistic models of pragmatic reasoning is the trade-off between the prior probability of a meaning and the informativeness of the utterance. This trade off between contextual factors during word learning is a unique aspect that is not addressed by other computational models of word learning, which have focused on learning from cross-situational, co-occurrence statistics [@fazly2010probabilistic; @frank2009using] or describing generalizations about word meaning [@xu2007word].

We make use of this framework to study pragmatic cue integration across development. To this end, we adapt a method used in perceptual cue integration studies [@ernst2002humans]: we make independent measurements of each cue’s strength and then combine them using the RSA model described above to make independent predictions about conditions in which they either coincide or conflict. Finally, we pre-register these quantitative predictions and test them against new data from adults and children.

We start by replicating previous findings with adults showing that listeners make pragmatic inferences based on non-linguistic properties of utterances in isolation (experiment 1). Then we show that adults make inferences based on common ground information (experiment 2A and 2B). We use data from these experiments as parameters to generate a priori predictions from RSA models about how utterance information and conversational priors should be integrated. We consider three models that make different assumptions about the integration process: In the *integration model*, the two information sources are integrated with one another. The other two models are lesioned models which assume that participants focus on one type of information and disregard the other whenever they are presented together. According to the *no conversational prior* model, participants focus only on the utterance information and in the *no informativeness* model, only the conversational prior is considered. We compare predictions from these models to new empirical data from experiments in which utterance and common ground information are manipulated simultaneously (Experiment 3 and 4).

After successfully validating this approach with adults in study 1, we apply the same model-driven experimental procedure to children (study 2): We first show that they make pragmatic inferences based on utterance and common ground information separately (experiment 5 and 6). Then we generate a priori model predictions and compare them to data from an experiment in which both information sources have to be integrated (experiment 7).

Taken together, this work makes two primary contributions: first, it shows that both adults and children integrate utterance-level information with conversational priors. Second, it uses Bayesian data analysis within the RSA framework to provide a model for understanding the multiple loci for developmental change in complex behaviors like contextual communication.

```{r fig1, include = T, fig.align = "center", fig.cap = "Schematic experimental procedure with screenshots from the adult experiments. In all conditions, at test (bottom), the speaker ambiguously requested an object using a non-word (e.g. “dax”). Participants clicked on the object they thought the speaker referred to. Speech bubbles represent pre-recorded utterances. Informativeness (a) translated to making one object less frequent in context. Common ground (b) was manipulated by making one object preferred by or new to the speaker. Green plus signs represent utterances that expressed preference and red minus signs represent utterances that expressed dispreference (see main text for details). Integration (c) combined informativeness and common ground manipulations. One integration condition is shown here: preference - same speaker - congruent.", out.width="100%"}
knitr::include_graphics("./figures/fig1.png")
```

# Study 1: Adults

## Participants

Adult participants were recruited via Amazon Mechanical Turk (MTurk) and received payment equivalent to an hourly wage of ~ \$9. Each participant contributed data to only one experiment. Experiment 1 and each manipulation of experiment 2 had *N* = 40 participants. Sample size in experiment 3 was *N* = `r length(unique(adult_ex3_data$id))`. *N* = `r length(unique(adult_ex4_prior_data$id))` participated in the experiments to measure the strong, medium and weak preference and novelty manipulations that went into experiment 4. Finally, experiment 4 had *N* = `r length(unique(adult_ex4_data$id))` participants. Sample sizes in all adult experiments were chosen to yield at least 120 data points per cell. All studies were approved by the Stanford Institutional Review Board (protocol no. 19960).

## Materials

All experimental procedures were pre-registered (see https://osf.io/u7kxe/registrations). Experimental stimuli are freely available in the following online repository: https://github.com/manuelbohn/mcc. All experiments were framed as games in which participants would learn words from animals. They were implemented in HTML/JavaScript as a website. Adults were directed to the website via MTurk and responded by clicking objects. For each animal character, we recorded a set of utterances (one native English speaker per animal) that were used to provide information and make requests. All experiments started with an introduction to the animals and two training trials in which familiar objects were requested (car and ball). Subsequent test trials in each condition were presented in a random order.

## Analytic approach

We preregistered sample sizes, inferential statistical analysis and computational models for all experiments. All deviations from the registered analysis plan are explicitly mentioned. All analyses were run in `R` [@R-base]. All p-values are based on two sided analysis. Cohen's d (computed via the function `cohensD`) was used as effect size for t-tests. Frequentist logistic GLMMs were fit via the function `glmer` from the package `lme4` [@R-lme4] and had a maximal random effect structure conditional on model convergence. Details about GLMMs including model formulas for each experiment can be found in the Supplementary Material.

All models and model comparisons were implemented in `WebPPL` [@dippl] using the `R` package `rwebppl` [@R-rwebppl]. Probabilistic models were evaluated using Bayesian data analysis [@lee2014bayesian], also implemented in `WebPPL`. In experiment 3, 4 and 7, we compared probabilistic models based on Bayes Factors - the ratio of the marginal likelihoods of each model given the data. Details on models, including information about priors for parameter estimation and Markov chain Monte Carlo settings can be found in the Supplementary Material available online. Code to run the models is available in the associated online repository.

## Experiment 1

### Methods

```{r ex1 results}
ex1t <- adult_ex1_data %>%
  group_by(condition, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(condition) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         mean = mean(unlist(correct)),
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         t_lci = t.test(unlist(correct), mu = 0.5)$conf.int[1],
         t_uci = t.test(unlist(correct), mu = 0.5)$conf.int[2],
         p_value = t.test(unlist(correct), mu = 0.5)$p.value,
         d = cohensD(unlist(correct), mu = 0.5)) %>%
  select(condition,mean,df,t_value,t_lci, t_uci,p_value,d)%>%
  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
         t_value = round(t_value,2),
         t_lci = round(t_lci,2),
         t_uci = round(t_uci,2),
         d = round(d,2))
# model
lm_ex1 <- glmer(correct ~ condition +
              (1 |id), 
              data = adult_ex1_data, 
              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#summary(lm_ex1)

ex1_r <- broom.mixed::tidy(lm_ex1, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))
```

In experiment 1, participants could learn which object a novel word referred to by assuming that the speaker communicated in an informative way [@frank2014inferring]. The speaker was located between two tables, one with two novel objects, A and B, and the other with only object A (Fig \ref{fig:fig1}a). At test, the speaker turned and pointed to the table with the two objects (A and B) and used a novel word to request one of them. The same utterance was used to make a request in all adult studies ( “Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?”). Participants could infer that the word referred to object B via the counter-factual inferences that, if the (informative) speaker had wanted to refer to object A, they would have pointed to the table with the single object (this being the least ambiguous way to refer to that object). In the control condition, both tables contained both objects and no inference could be made based on the speaker’s behavior. Participants received six trials, three per condition.

### Results

Participants selected object B above chance in the test condition (mean = `r ex1t%>%filter(condition == "test")%>%pull(mean)`, 95% CI of mean = [`r ex1t%>%filter(condition == "test")%>%pull(t_lci)`; `r ex1t%>%filter(condition == "test")%>%pull(t_uci)`], t(`r ex1t%>%filter(condition == "test")%>%pull(df)`) = `r ex1t%>%filter(condition == "test")%>%pull(t_value)`, *p* `r ex1t%>%filter(condition == "test")%>%pull(p_value)`, d = `r ex1t%>%filter(condition == "test")%>%pull(d)`) and more often compared to the control condition (*$\beta$* = `r ex1_r%>%filter(term == "conditiontest")%>%pull(estimate)`, se = `r ex1_r%>%filter(term == "conditiontest")%>%pull(std.error)`, *p* `r ex1_r%>%filter(term == "conditiontest")%>%pull(p.value)`, see Fig \ref{fig:fig2}). This finding replicates earlier work showing that adult listeners expect speakers to communicate in an informative way.

## Experiment 2

### Methods

```{r ex2-results}
ex2tpref <- adult_ex2_preference_data %>%
  group_by(condition, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(condition) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         mean = mean(unlist(correct)),
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         t_lci = t.test(unlist(correct), mu = 0.5)$conf.int[1],
         t_uci = t.test(unlist(correct), mu = 0.5)$conf.int[2],
         p_value = t.test(unlist(correct), mu = 0.5)$p.value,
         d = cohensD(unlist(correct), mu = 0.5)) %>%
  select(condition,mean,df,t_value,t_lci, t_uci,p_value,d)%>%
  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
         t_value = round(t_value,2),
         t_lci = round(t_lci,2),
         t_uci = round(t_uci,2),
         d = round(d,2))

# model (maximally converging)
lm_ex2pref <- glmer(correct ~ condition +
              (1|id) + (1|agent), 
              data = adult_ex2_preference_data, 
              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#summary(lm_ex2pref)

ex2pref_r <- broom.mixed::tidy(lm_ex2pref, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))

ex2tnov <- adult_ex2_novelty_data %>%
  group_by(condition, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(condition) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         mean = mean(unlist(correct)),
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         t_lci = t.test(unlist(correct), mu = 0.5)$conf.int[1],
         t_uci = t.test(unlist(correct), mu = 0.5)$conf.int[2],
         p_value = t.test(unlist(correct), mu = 0.5)$p.value,
         d = cohensD(unlist(correct), mu = 0.5)) %>%
  select(condition,mean,df,t_value,t_lci, t_uci,p_value,d)%>%
  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
         t_value = round(t_value,2),
         t_lci = round(t_lci,2),
         t_uci = round(t_uci,2),
         d = round(d,2))

# model
lm_ex2nov <- glmer(correct ~ condition +
              (condition|id), 
              data = adult_ex2_novelty_data, 
              family = binomial,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(lm_ex2nov)

ex2nov_r <- broom.mixed::tidy(lm_ex2nov, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))
```

In experiments 2A and 2B, we tested if participants use common ground information that is specific to a speaker to identify the referent of a novel word [@akhtar1996role; @diesendruck2004two; @saylor2009preschoolers]. In experiment 2A, the speaker expressed a preference for one of two objects (Fig \ref{fig:fig1}b, left). The animal introduced themselves, then turned to one of the tables and expressed either that they liked (“Oh wow, I really like that one”) or disliked (“Oh bleh, I really don’t like that one”) the object before turning to the other side and expressing the respective other attitude. Next the animal disappeared and, after a short pause, either the same or a different animal returned and requested an object while facing straight ahead. Participants could use the speakers preference to identify the referent when the same speaker returned but not when a different speaker appeared whose preferences were unknown.

In experiment 2B, common ground information came in the form of novelty (Fig \ref{fig:fig1}b, right). The animal turned to one of the sides and commented either on the presence (“Aha, look at that”) or the absence (“Hm…, nothing there”) of an object before turning to the other side and commenting in a complementary way. Later, a second object appeared on the previously empty table. Then the speaker used a novel word to request one of the objects. The referent of the novel word could be identified by assuming that the speaker uses it to refer to the object that is new to them. This inference was not licensed when a different speaker returned to whom both objects were equally new. For both novelty and preference, participants received six trials, three with the same and three with the different speaker.

### Results

In experiment 2A, participants selected the preferred object above chance (mean = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(mean)`, 95% CI of mean = [`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_lci)`; `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_uci)`], t(`r ex2tpref%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(p_value)`, d = `r ex2tpref%>%filter(condition == "same_speaker")%>%pull(d)`)  and more so than in the speaker change control condition ($\beta$ = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2pref_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`).

In experiment 2B, participants selected the novel object above chance (mean = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(mean)`, 95% CI of mean = [`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_lci)`; `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_uci)`], t(`r ex2tnov%>%filter(condition == "same_speaker")%>%pull(df)`) = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(t_value)`, *p* `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(p_value)`, d = `r ex2tnov%>%filter(condition == "same_speaker")%>%pull(d)`) when the same speaker made the request and more often compared to when a different speaker made the request ($\beta$ = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r ex2nov_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`, see Fig \ref{fig:fig2}).

```{r fig2, include = T, fig.align = "center", fig.cap = "Results from experiments 1, 2A, and 2B for adults. For preference and novelty, control refers to a different speaker (see Fig 1b). Transparent dots show data from individual participants (slightly jittered to avoid overplotting), diamonds represent condition means, error bars are 95\\% CIs. Dashed line indicates performance expected by chance.", out.width="70%"}
knitr::include_graphics("./figures/fig2.png")
```

## Modelling information integration

Experiments 1 and 2 confirmed that adults make pragmatic inferences based on information provided by the utterance as well as by common ground and provided quantitative estimates of the strength of these inferences for use in our model. We modeled the integration of utterance informativity and conversational priors (representing common ground) as a process of socially-guided probabilistic inference, using the results of experiments 1 and 2 to inform key parameters of a computational model. The Rational Speech Act (RSA) model architecture introduced by Frank and Goodman [-@frank2012predicting] encodes conversational reasoning through the perspective of a listener (“he” pronoun) who is trying to decide on the intended meaning of the utterance he heard from the speaker (“she” pronoun). The basic idea is that the listener combines his uncertainty about the speaker’s intended meaning - a prior distribution over referents $P(r)$ - with his generative model of how the utterance was produced: a speaker trying to convey information to him. To adapt this model to the word learning context, we enrich this basic architecture with a mechanism for expressing uncertainty about the meanings of words (lexical uncertainty) - a prior distribution over lexica $P(L)$ [@bergen2016pragmatic].

$$P_{L}(r, \mathcal{L}|u)\propto P_{S}(u|r, \mathcal{L}) \cdot P( \mathcal{L}) \cdot P(r)$$

In the above equation, the listener is trying to jointly resolve the speaker’s intended referent $r$ and the meaning of words (thus learning the lexicon $\mathcal{L}$). He does this by imagining what a rational speaker would say, given the referent they are trying to communicate and a lexicon. The speaker is an approximately rational Bayesian actor (with degree of rationality $\alpha$), who produces utterances as a function of their informativity. The space of utterances the speaker could produce depends upon the lexicon $P(u|\mathcal{L})$; simply put, the speaker labels objects with the true labels under a given lexicon L (see Supplementary Material available online for details):

$$P_{S}(u|r,\mathcal{L})\propto Informativity(u;r)^\alpha \cdot P(u|\mathcal{L})$$

The informativity of an utterance for a referent is taken to be the probability with which a naive listener, who only interprets utterances according to their literal semantics, would select a particular referent given an utterance.

$$Informativity(u; r) = P(r|u) \propto P(r) \cdot \mathcal{L}_{point}$$

The speaker’s possible utterances are pairs of linguistic and non-linguistic signals, namely labels and points. Because the listener does not know the lexicon, the informativity of an utterance comes from the speaker’s point, the meaning of which is encoded in $\mathcal{L}_{point}$ and is simply a truth-function checking whether or not the referent is at the location picked out by the speaker’s point. Though the speaker makes their communicative decision assuming the listener does not know the meaning of the labels, we assume that in addition to a point, the speaker produces a label consistent with their own lexicon $\mathcal{L}$, described by $P(u|\mathcal{L})$ (see Supplementary Material available online for modeling details).

This computational model provides a natural avenue to formalize quantitatively how informativeness and conversational priors trade-off during word learning. As mentioned above, we treat common ground as a conversational prior over meanings, or types of referents, that the speaker might be referring to. That is, we assume that the interactions around the referents in the present context (e.g., preference or novelty; experiment 2A and B) result in a person-specific prior distribution over referents. We use the results from experiment 2 to specify this distribution. The in-the-moment, contextual informativeness of the utterance is captured in the likelihood term, whose value depends on the rationality parameter $\alpha$. Assumptions about rationality may change depending on context and we therefore used the data from experiment 1 to specify $\alpha$ (see Supplementary Material available online for details about these parameters).

The model generates predictions for situations in which utterance and common ground expectations are jointly manipulated (Fig \ref{fig:fig1}c - see Supplementary Material available online for additional details and a worked example of how predictions were generated). In addition to the parameters fit to the data from previous experiments, we include an additional noise parameter, which can be thought of as reflecting the cost that comes with handling and integrating multiple information sources. Technically it estimates the proportion of responses better explained by a process of random guessing than by pragmatics; we estimate this parameter from the observed data (experiment 3). Including the noise parameter greatly improved the model fit to the data (see Supplementary Material available online for details). We did not pre-register the inclusion of a noise parameter for experiment 3 but did so for all subsequent experiments.

## Experiment 3

### Methods

```{r ex3 GLMM, cache=F}
# model 
lm_ex3 <- glmer(correct_inf ~ common_ground_manipulation*speaker*alignment + (alignment|id), 
              data = adult_ex3_data, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#summary(lm_ex3)

lm_ex3_r <- broom.mixed::tidy(lm_ex3, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))

```

```{r model comparison ex3}
ex3_bf <- bind_rows(
  readRDS("../../stats/saves/ex3_prior_only_model_noise_loglike.rds") %>% mutate(model = "prior_only_noise"),
  readRDS("../../stats/saves/ex3_pragm_model_noise_loglike.rds") %>% mutate(model = "pragmatic_noise"),
  readRDS("../../stats/saves/ex3_flat_prior_model_noise_loglike.rds") %>% mutate(model = "flat_prior_noise")
)%>%
  group_by(model)%>%
  summarize(logP = logSumExp(value))%>%
  bind_rows(readRDS("../../stats/saves/ex3_pragm_model_loglike.rds") %>% mutate(model = "pragmatic_parameter_free"))%>%
  spread(model, logP) %>%
  mutate("pragmatic_noise_pragmatic_parameter_free" = exp(pragmatic_noise - pragmatic_parameter_free),
         "pragmatic_noise_prior_only_noise" = exp(pragmatic_noise - prior_only_noise),
         "pragmatic_noise_flat_prior_noise" = exp(pragmatic_noise - flat_prior_noise),
         "prior_only_noise_flat_prior_noise" = exp(prior_only_noise - flat_prior_noise)) %>%
  select(-pragmatic_parameter_free,-pragmatic_noise, -flat_prior_noise, -prior_only_noise)

ex3_pragm_model_noise_param <- readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))%>%
  round(digits = 2)

ex3_flat_prior_model_noise_param <- readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))%>%
  round(digits = 2)

ex3_prior_only_model_noise_param <- readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))%>%
  round(digits = 2)
```

In experiment 3, we combined the procedures of experiment 1 and 2A or 2B. The test setup was identical to experiment 1, however, before making a request, the speaker interacted with the objects so that some of them were preferred by or new to them (Fig \ref{fig:fig1}c). This combination resulted in two ways in which the two information sources could be aligned with one another. In the congruent condition, the object that was the more informative referent was also the one that was preferred by or new to the speaker. In the incongruent condition, the other object was the one that was preferred by or new to the speaker. Taken together, there were 2 (novelty or preference) x 2 (same or different speaker) x 2 (congruent or incongruent) = 8 conditions in experiment 3. For each of these eight conditions, we generated model predictions using the modelling framework introduced above. The test hypothesis about how information is integrated we compared the three models introduced in the introduction: The *integration model* in which both information sources are flexibly combined, the *no common ground model* that focused only on utterance-level information and the the *no informativeness model* that focused only on common ground information.

Participants completed eight trials for one of the common ground manipulations with two trials per condition (same/different speaker x congruent/incongruent). Conditions were presented in a random order. We discuss and visualize the results as the proportion with which participants chose the more informative object (i.e., the object that would be the more informative referent when only utterance information is considered).

### Results

As a first step, we used a GLMM to test whether participants were sensitive to the different ways in which information could be aligned. We found that participants distinguished between congruent and incongruent trials when the speaker remained the same (model term: `alignment x speaker`; $\beta$ = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r lm_ex3_r%>%filter(term == "speakersame_speaker:alignmentincongruent")%>%pull(p.value)`). Thus, participants were sensitive to the different combinations of manipulations.

```{r fig3, include = T, fig.align = "center", fig.cap = "Results from experiment 3 and 4 for adults. Data and model predictions by condition for experiment 3 (a). Transparent dots show data from individual participants (slightly jittered to avoid overplotting), diamonds represent condition means. Correlation between model predictions and data in Experiment 3 (b), between data in Experiment 3 and the direct replication in experiment 4 (c) and between model predictions and data in experiment 4 (d). Coefficients and p-values are based on Pearson correlation statistics. Error bars represent 95\\% HDIs." , out.width="100%"}

knitr::include_graphics("./figures/fig3.png")
```

As a second step, we compared the model predictions to the data. Participants’ average responses were highly correlated with the  predictions from the *integration model* in each condition (Fig \ref{fig:fig3}b). When comparing models, we found that model fit was considerably better for the *integration model* compared to the *no conversational prior model* (Bayes Factor (BF) = `r format(ex3_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the *no informativeness model* (BF = `r format(ex3_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`), suggesting that participants considered and integrated both sources of information.

Finally, we examined the noise parameter for each model. The estimated proportion of random responses according to the *integration model* was `r ex3_pragm_model_noise_param%>%pull(mean)` (95% Highest Density Interval (HDI): `r ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r ex3_pragm_model_noise_param%>%pull(ci_upper)`). This parameter was substantially lower for the *integration model* compared to the alternative models (*no conversational prior model*: `r ex3_flat_prior_model_noise_param%>%pull(mean)` [`r ex3_flat_prior_model_noise_param%>%pull(ci_lower)` - `r ex3_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r ex3_prior_only_model_noise_param%>%pull(mean)` [`r ex3_prior_only_model_noise_param%>%pull(ci_lower)` - `r ex3_prior_only_model_noise_param%>%pull(ci_upper)`]), lending additional support to the conclusion that the *integration model* better captured the behavioral data. Rather than explaining systematic structure in the data, the alternative models achieved their best fit only by assuming a very high level of noise.

## Experiment 4

### Methods

```{r model comparison ex4}
ex4_bf <- bind_rows(
  readRDS("../../stats/saves/ex4_prior_only_model_noise_loglike.rds") %>% mutate(model = "prior_only_noise"),
  readRDS("../../stats/saves/ex4_pragm_model_noise_loglike.rds") %>% mutate(model = "pragmatic_noise"),
  readRDS("../../stats/saves/ex4_flat_prior_model_noise_loglike.rds") %>% mutate(model = "flat_prior_noise")
)%>%
  group_by(model)%>%
  summarize(logP = logSumExp(value))%>%
  spread(model, logP) %>%
  mutate("pragmatic_noise_prior_only_noise" = exp(pragmatic_noise - prior_only_noise),
         "pragmatic_noise_flat_prior_noise" = exp(pragmatic_noise - flat_prior_noise),
         "prior_only_noise_flat_prior_noise" = exp(prior_only_noise - flat_prior_noise)) %>%
  select(-pragmatic_noise, -flat_prior_noise, -prior_only_noise)

ex4_pragm_model_noise_param <- readRDS("../../stats/saves/ex4_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))%>%
  round(digits = 2)

ex4_flat_prior_model_noise_param <- readRDS("../../stats/saves/ex4_flat_prior_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))%>%
  round(digits = 2)

ex4_prior_only_model_noise_param <- readRDS("../../stats/saves/ex4_prior_only_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))%>%
  round(digits = 2)

```

To test if the *integration model* makes accurate predictions for different combinations, we first replicated and then extended the results of experiment 3 to a broader range of experimental conditions. Specifically, we manipulated the strength of the common ground information (3 levels - strong, medium and weak - for preference and 2 levels - strong and medium - for novelty) by changing the way the speaker interacted with the objects prior to the request. The procedural details and statistical analysis for these these manipulations are described in the Supplementary Material available online. For experiment 4, we paired each level of prior strength manipulation with the informativeness inference in the same way as in experiment 3. This resulted in a total of 20 conditions, for which we generated a priori model predictions in the same way as in experiment 3. That is, we conducted a separate experiment for each level of prior strength and common ground manipulation to estimate the prior probability of each object following this particular manipulation (analogous to experiment 2). This prior distribution was then passed through the model for the congruent and incongruent conditions, resulting in a unique prediction for each of the 20 conditions. Given the graded nature of the prior manipulations, experiment 4 basically tests how well the model performs with different types of prior distributions.

The strong prior manipulation in experiment 4 was a direct replication of experiment 3 (see Fig \ref{fig:fig3}c). Each participant was randomly assigned to a common ground manipulation and a level of prior strength and completed eight trials in total, two in each unique condition in that combination.

### Results

The direct replication of experiment 3 within experiment 4 showed a very close correspondence between the two rounds of data collection (see Fig \ref{fig:fig3}c). GLMM results for experiment 4 can be found in the Supplementary Material available online. Here we focus on the analysis based on the probabilistic models. Model predictions from the *integration model* were again highly correlated with the average response in each condition (see Fig \ref{fig:fig3}d). We evaluated model fit for the same models as in experiment 3 and found again that the *integration model* fit the data much better compared to the *no conversational prior* (BF = `r format(ex4_bf%>%pull(pragmatic_noise_flat_prior_noise), digits = 2)`) or the *no informativeness model* (BF = `r format(ex4_bf%>%pull(pragmatic_noise_prior_only_noise), digits = 2)`). The inferred level of noise based on the data for the *integration model* was `r ex4_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r ex4_pragm_model_noise_param%>%pull(ci_lower)` - `r ex4_pragm_model_noise_param%>%pull(ci_upper)`), which was similar to experiment 3 and again lower compared to the alternative models (*no conversational prior model*: `r ex4_flat_prior_model_noise_param%>%pull(mean)` [`r ex4_flat_prior_model_noise_param%>%pull(ci_lower)` - `r ex4_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r ex4_prior_only_model_noise_param%>%pull(mean)` [`r ex4_prior_only_model_noise_param%>%pull(ci_lower)` - `r ex4_prior_only_model_noise_param%>%pull(ci_upper)`]).

# Study 2: Children

The previous section showed that competent language users flexibly integrate information during pragmatic word learning. Do children make use of multiple information sources during word learning as well? When does this integration emerge developmentally? While many verbal theories of language learning imply that this integration takes place, the actual process has neither been described nor tested in detail. Here we provide an explanation in the form of our *integration model* and test if it is able to capture children’s word learning. Embedded in the assumptions of the model is the idea that developmental change is change in the strength of the individual inferences, leading to a change in the strength of the integrated inference. As a starting point, our model assumes developmental continuity in the integration process itself [@bohn2019pervasive], though this assumption could be called into question by a poor model fit. The study for children followed the same general pattern as the one for adults. We generated model predictions for how information should be integrated by first measuring children’s ability to use utterance (informativeness) and common ground (preference) information in isolation when making pragmatic inferences. We then adapted our model to study developmental change: We sampled children continuously between 3.0 and 5.0 years of age – a time in which children have been found to make the kind of pragmatic inferences we studied here [@bohn2019pervasive; @frank2014inferring] - and generated model predictions for the average developmental trajectory in each condition.

## Participants

Children were recruited from the floor of the Children’s Discovery Museum in San Jose, California, USA. Parents gave informed consent and provided demographic information. Each child contributed data to only one experiment. We collected data from a total of 243 children between 3.0 and 5.0 years of age. We excluded 15 children due to less than 75% of reported exposure to English, five because they responded incorrectly on 2/2 training trials, three because of equipment malfunction, and two because they quit before half of the test trials were completed. The final sample size in each experiment was as follows: *N* = `r length(unique(child_ex1_data$id))` (41 girls, mean age = `r round(mean(child_ex1_data$age_num),2)`) in experiment 5,  *N* = `r length(unique(child_ex2_data$id))` (28 girls, mean age = `r round(mean(child_ex2_data$age_num),2)`) in experiment 6 and *N* = `r length(unique(child_ex3_data$id))` (54 girls, mean age = `r round(mean(child_ex3_data$age_num),2)`) in experiment 7. For experiment 5 and 6, we also tested two-year-olds but did not find sufficient evidence that they use utterance and/or common ground information in the tasks we used to justify investigating their ability to integrate the two. Sample sizes in all experiments were chosen to yield at least 80 data points in each cell for each age group.

## Materials

Experiments were implemented in the same general way as for adults. Children were guided through the games by an experimenter and responded by touching objects on the screen of an iPad tablet [@frank2016using].

## Experiment 5

### Methods

```{r child ex1 and 2 results}
#experiment 1
child_ex1t <- child_ex1_data %>%
  group_by(age_bin, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(age_bin) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         mean = mean(unlist(correct)),
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         t_lci = t.test(unlist(correct), mu = 0.5)$conf.int[1],
         t_uci = t.test(unlist(correct), mu = 0.5)$conf.int[2],
         p_value = t.test(unlist(correct), mu = 0.5)$p.value,
         d = cohensD(unlist(correct), mu = 0.5)) %>%
  select(age_bin,mean,df,t_value,t_lci, t_uci,p_value,d)%>%
  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
         t_value = round(t_value,2),
         t_lci = round(t_lci,2),
         t_uci = round(t_uci,2),
         d = round(d,2))

child_ex1_lm_data <- child_ex1_data%>%
  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))

# GLMM
child_ex1_lm <- glmer(correct ~ age_num + (1 | id), 
              data = child_ex1_lm_data, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#summary(child_ex1_lm)

child_lm_ex1_r <- broom.mixed::tidy(child_ex1_lm, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))

# experiment 2
child_ex2t <- child_ex2_data %>%
  group_by(condition,age_bin, id) %>%
  summarise(correct = mean(correct)) %>%
  summarise(correct = list(correct)) %>%
  group_by(condition,age_bin) %>%
  mutate(df= t.test(unlist(correct), mu = 0.5)$parameter,
         mean = mean(unlist(correct)),
         t_value = t.test(unlist(correct), mu = 0.5)$statistic,
         t_lci = t.test(unlist(correct), mu = 0.5)$conf.int[1],
         t_uci = t.test(unlist(correct), mu = 0.5)$conf.int[2],
         p_value = t.test(unlist(correct), mu = 0.5)$p.value,
         d = cohensD(unlist(correct), mu = 0.5)) %>%
  select(condition,age_bin,mean,df,t_value,t_lci, t_uci,p_value,d)%>%
  mutate(p_value = ifelse(p_value<.001,"< .001",as.character(paste("=",substr(round(p_value,3),2,5),sep=" "))),
         t_value = round(t_value,2),
         t_lci = round(t_lci,2),
         t_uci = round(t_uci,2),
         d = round(d,2))

# GLMM

child_ex2_lm_data <- child_ex2_data%>%
  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))

child_ex2_lm <- glmer(correct ~ age_num*condition + (condition | id) + (1 | agent), 
              data = child_ex2_lm_data, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(child_ex2_lm)

child_lm_ex2_r <- broom.mixed::tidy(child_ex2_lm, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))

```

Experiment 5 for children was modeled after @frank2014inferring. Instead of on tables, objects were presented as hanging in trees (to facilitate showing points to distinct locations). After introducing themselves, the animal turned to the tree with two objects and said: “This is a tree with a [non-word], how neat, a tree with a [non-word]”). Next, the trees and the objects in them disappeared and new trees replaced them. The two objects from the tree the animal turned to previously were now spread across the two trees (one object per tree, position counterbalanced). While facing straight, the animal first said “Here are some more trees” and then asked the child to pick the tree with the object that corresponded to the novel word (“Which of these trees has a [non-word]?”). Children received six trials in a single test condition.

### Results

To compare children’s performance to chance level, we binned age by year. Four-year-olds selected the more informative object (i.e. the object that was unique to the location the speaker turned to) above chance (mean = `r child_ex1t%>%filter(age_bin =="4")%>%pull(mean)`, 95% CI of mean = [`r child_ex1t%>%filter(age_bin =="4")%>%pull(t_lci)`; `r child_ex1t%>%filter(age_bin =="4")%>%pull(t_uci)`], t(`r child_ex1t%>%filter(age_bin =="4")%>%pull(df)`) = `r child_ex1t%>%filter(age_bin =="4")%>%pull(t_value)`, *p* `r child_ex1t%>%filter(age_bin =="4")%>%pull(p_value)`, d = `r child_ex1t%>%filter(age_bin =="4")%>%pull(d)`). Three-year-olds, on the other hand, did not (mean = `r child_ex1t%>%filter(age_bin =="3")%>%pull(mean)`, 95% CI of mean = [`r child_ex1t%>%filter(age_bin =="3")%>%pull(t_lci)`; `r child_ex1t%>%filter(age_bin =="3")%>%pull(t_uci)`], t(`r child_ex1t%>%filter(age_bin =="3")%>%pull(df)`) = `r child_ex1t%>%filter(age_bin =="3")%>%pull(t_value)`, *p* `r child_ex1t%>%filter(age_bin =="3")%>%pull(p_value)`, d = `r child_ex1t%>%filter(age_bin =="3")%>%pull(d)`). Consequently, when we fit a GLMM to the data with age as a continuous predictor, performance increased with age ($\beta$ = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex1_r%>%filter(term == "age_num")%>%pull(p.value)`, see Fig \ref{fig:fig4}). Thus, children’s ability to use utterance information in a word learning context increased with age.

```{r fig4, include = T, fig.align = "center", fig.cap = "Results from experiment 5 and 6 for children. For preference, control refers to to the different speaker condition (see Fig. 1B). Transparent dots show data from individual participants (slightly jittered to avoid overplotting), regression lines show fitted linear models with 95\\% CIs. Dashed line indicates performance expected by chance.", out.width="70%"}
knitr::include_graphics("./figures/fig4.png")
```

## Experiment 6

### Methods

In experiment 6, we assessed whether children use common ground information to identify the referent of a novel word. We tested children only with the preference manipulation^[We initially tested children with the novelty as well as the preference manipulation. We found that children made the basic inference in that they selected the object that was preferred by or new to the speaker, but found little evidence that children distinguished between requests made by the same speaker or a different speaker in the case of novelty. This finding contrasts with earlier work [@diesendruck2004two]. Since our focus was on how children integrate informativeness and conversational priors resulting from common ground, we did not follow up on this finding but dropped the novelty manipulation and focused on preference for the remainder of the study.]. The procedure for children was identical to the preference manipulation for adults. Children received eight trials, four with the same and four with a different speaker.

### Results

Four-year-olds selected the preferred object above chance when the same speaker made the request (mean = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(mean)`, 95% CI of mean = [`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_lci)`; `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_uci)`], t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(p_value)`, d = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="4")%>%pull(d)`), whereas three-year-olds did not (mean = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(mean)`, 95% CI of mean = [`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_lci)`; `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_uci)`], t(`r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(df)`) = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(t_value)`, *p* `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(p_value)`, d = `r child_ex2t%>%filter(condition == "same_speaker" ,age_bin =="3")%>%pull(d)`). However, when we fit a GLMM to the data with age as a continuous predictor, we found an effect of speaker identity ($\beta$ = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "conditionsame_speaker")%>%pull(p.value)`) but no effect of age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num")%>%pull(p.value)`) or interaction between speaker identity and age ($\beta$ = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(estimate)`, se = `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(std.error)`, *p* `r child_lm_ex2_r%>%filter(term == "age_num:conditionsame_speaker")%>%pull(p.value)`, see Fig \ref{fig:fig4}). Thus, children across the age range used common ground information to infer the referent of a novel word.

## Modelling information integration in children

Model predictions for children were generated using the same model described above for adults. However, to incorporate developmental change in the model, we allowed the rationality parameter $\alpha$ and the prior distribution over objects to change with age. That is, instead of a single value, we used Bayesian data analysis to infer the intercept and slope for each parameter that best described the developmental trajectory in the data of experiment 5 and 6 (see Supplementary Material for details on how parameters were estimated). These parameter settings were then used to generate age sensitive model predictions in 2 (same or different speaker) x 2 (congruent or incongruent) = 4 conditions. As for adults, all models included a noise parameter, which was estimated based on the data of experiment 7.

## Experiment 7

### Methods

```{r child ex3 GLMM, cache = F}
child_ex3_lm_data <- child_ex3_data%>%
  mutate(age_num = scale(age_num, center = TRUE, scale = TRUE))

child_ex3_lm <- glmer(correct_inf ~ age_num*speaker*alignment 
      + (speaker+alignment | id), 
      family = "binomial",
      data = child_ex3_lm_data,
      control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(child_ex3_lm)

child_lm_ex3_r <- broom.mixed::tidy(child_ex3_lm, effects = "fixed")%>%
  mutate(p.value = ifelse(p.value<.001,"< .001",as.character(paste("=",substr(round(p.value,3),2,5),sep=" "))),
         std.error = round(std.error,2),
         estimate = round(estimate,2))
```

In experiment 7, we combined the procedures of experiment 5 and 6 and collected new data from children between 3.0 and 5.0 years of age in each of the four conditions (Fig \ref{fig:fig1}c). We again inserted the preference manipulation into the setup of experiment 5. After greeting the child, the animal turned to one of the trees, pointed to an object (object was temporarily enlarged and moved closer to the animal) and expressed liking or disliking. Then the animal turned to the other tree and expressed the other attitude for the other kind of object. Next, the animal disappeared and either the same or a different animal returned. The rest of the trial was identical to the request phase of experiment 5. Children received eight trials, two per condition (same/different speaker x congruent/incongruent) in a randomized order.

### Results

As a first step, we used a GLMM to test whether children were sensitive to the different ways in which information could be aligned. Children’s propensity to differentiate between congruent and incongruent trials for the same or a different speaker increased with age (model term: `age x alignment x speaker`; $\beta$ = `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(estimate)`, se = `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(std.error)`, *p* `r child_lm_ex3_r%>%filter(term == "age_num:speakersame_speaker:alignmentincongruent")%>%pull(p.value)`).

```{r child model comparison}

child_ex3_bf <- readRDS("../../stats/saves/child_ex3_model_comparison.rds") %>%
  group_by(parameter)%>%
  select(-ci_lower, -ci_upper)%>%
  spread(model, logP) %>%
  mutate("pragmatic_flat_prior" = exp(pragmatic - flat_prior),
         "pragmatic_prior_only" = exp(pragmatic - prior_only),
         "flat_prior_prior_only" = exp(flat_prior - prior_only)) %>%
  select(-pragmatic,-flat_prior, -prior_only)

child_ex3_pragm_model_noise_param <- readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

child_ex3_flat_prior_model_noise_param <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

child_ex3_prior_only_model_noise_param <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

```

Analyses comparing the model predictions from the probabilistic models to the data suggest that children flexibly integrate conversational priors and informativity information. Furthermore, this integration process is accurately captured by the *integration model* at least for four-year-olds. For the correlational analysis, we binned model predictions and data by year. There was a substantial correlation between the predicted and measured average response for four-year-olds, but less so for three-year-olds (Fig \ref{fig:fig5}b). One of the reasons for the latter was the low variation between conditions. For the model comparison, we treated age continuously. As with adults, we found a much better model fit for the *integration model* compared to the *no conversational prior* (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_flat_prior), digits = 2)`) or the *no informativeness model* (BF = `r format(child_ex3_bf%>%filter (parameter=="noise")%>%pull(pragmatic_prior_only), digits = 2)`).

The inferred level of noise based on the data for the integration model was `r child_ex3_pragm_model_noise_param%>%pull(mean)` (95% HDI: `r child_ex3_pragm_model_noise_param%>%pull(ci_lower)` - `r child_ex3_pragm_model_noise_param%>%pull(ci_upper)`), which was lower compared to the alternative models considered (*no conversational prior model*: `r child_ex3_flat_prior_model_noise_param%>%pull(mean)` [`r child_ex3_flat_prior_model_noise_param%>%pull(ci_lower)` - `r child_ex3_flat_prior_model_noise_param%>%pull(ci_upper)`]; *no informativeness model*: `r child_ex3_prior_only_model_noise_param%>%pull(mean)` [`r child_ex3_prior_only_model_noise_param%>%pull(ci_lower)` - `r child_ex3_prior_only_model_noise_param%>%pull(ci_upper)`]) but numerically higher than that of adults (see Fig \ref{fig:fig5}c).

The high level of inferred noise moved the model predictions for children in all conditions close to chance level. We therefore compared two additional sets of models with different parameterizations of the noise parameter that emphasized differences between conditions in the model predictions more (see Supplementary Material and Fig \ref{fig:fig5}a). This analysis was not pre-registered. Parameter free models did not include a noise parameter and developmental noise models allowed the noise parameter to change with age. In each case, the *integration model* provided a better fit compared to the alternative models (*no conversational prior*: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_flat_prior), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_flat_prior), digits = 2)`; *no informativeness*: parameter free BF = `r format(child_ex3_bf%>%filter (parameter=="parameter free")%>%pull(pragmatic_prior_only), digits = 2)`, developmental noise BF = `r format(child_ex3_bf%>%filter (parameter=="developmental noise")%>%pull(pragmatic_prior_only), digits = 2)`). The developmental noise parameter for the integration model decreased with age, suggesting that older children behaved more in line with model predictions compared to younger children (see Fig \ref{fig:fig5}d).

```{r fig5, include = T, fig.align = "center", fig.cap = "Results from experiment 7 for children. (a) Model predictions (with 95\\% HDIs) and data across age in the four conditions. Transparent black dots show data from individual participants and black lines show conditional means of the data with 95\\% CI. Black diamonds show the mean of the data for age bins by year and error bars show 95\\% CIs. (b) Correlation between model predictions (with noise parameter) and condition means binned by year (with 95\\% HDIs). For 4-year-olds, two conditions yielded the same data means and model predicitons and are thus plotted on top of each other. (c) Posterior distribution of the noise parameter for the different models. (d) Developmental trajectory of the noise paramter for the three developmental noise models; trajectories are based on MAPs of the posterior distribution for the intercept and slope.", out.width = "100%"}
knitr::include_graphics("./figures/fig5.png")
```

# Discussion

Integrating multiple sources of information is an integral part of human communication. To infer the intended meaning of an utterance, listeners must combine their knowledge of communicative conventions (semantics and syntax) with social expectations about their interlocutor. This integration is especially vital in early language learning, when the different varieties of pragmatic information are among the most important sources [@bohn2019pervasive]. But how are pragmatic cues integrated during word learning? Here we used a Bayesian cognitive model to formalize this integration process. We studied how utterance-level (Gricean) expectations about informative communication are integrated with conversational priors (resulting from common ground). Adults’ and children’s learning was best predicted by a model in which both sources of information traded-off flexibly. Alternative models that considered only one source of information made substantially worse predictions.

Cue integration is an integral part of language comprehension and learning [as well as perception more generally; @trommershauser2011sensory]. As such, it has been extensively studied in recent decades. The focus of this work has usually been on how adults combine perceptual, semantic or syntactic information [e.g. @tanenhaus1995integration; @kamide2003integration; @hagoort2004integration; @ozyurek2007line]. We extend the study of linguistic cue integration to pragmatics. Most importantly, however, we present a substantive theory of the integration process itself. Real world language comprehension and learning happens in socially dynamic and complex situations which inevitably require integrating multiple pragmatic information sources. The *integration model* provides a formal description of the (hypothetical) psychological representations that may underlie information integration. As such, our work complements theorizing about information integration in other domains of language comprehension [e.g. @fourtassi2020optimal; @mcclelland2006there; @smith2017multimodal].

How is information integrated in this context? The *integration model* assumes that the informativeness of an utterance depends on the person-specific conversational priors (resulting from common ground). This conception of information integration explains the seemingly counterintuitive predictions of the model. For example, one might expect that the model predicts a performance at chance level in the same speaker -- incongruent conditions because the two cues "pull" the listener in opposite directions. Instead, the model predicts a performance below chance, favoring the object implicated by the prior (which also matches adults' responses). This is because the listener assumes that the speaker takes the conversational prior shared between the speaker and the (naive) listener as a starting point when computing the effect of each utterance. As a consequence, when prior interactions strongly implicate one object as the more likely referent, the speaker reasons that this object will be the inferred referent of any semantically plausible utterance, even when the same utterance would point to a different object in the absence of a conversational prior. Taken together, our model advances classic theories on pragmatic language comprehension [@grice1991studies; @sperber2001relevance] and learning [@bruner1983child; @tomasello2009constructing] by providing an explicit and formal description of the integration process, thereby offering an answer to the question of *how* information may be integrated during pragmatic word learning. Predictions generated based on this process accurately captured adults' inferences across a wide range of conditions.

All of the models we compared here integrated some explicit structure, rather than (for example) simply weighing information sources by some ratio. We made this decision because we wanted to make predictions within a framework in which the models were models of the task, rather than simply models of the data. That is, inferences are not computed separately by the modeler and specified as inputs to a regression model, but instead are the results of an integrated process that operates over a (schematic) representation of the experimental stimuli. Further, our models are variants derived from the broader RSA framework, which has been integrated into larger systems for language learning in context [@wang2016learning; @cohn2018pragmatically; @monroe2017colors].

The *integration model* predicted information integration in four-year-olds. However, the model did not successfully describe three-year-olds’ inferences; thus, it is possible that they were not able to integrate information sources. But our findings are also consistent with a simpler explanation, namely that the overall weaker responses we observed in the independent measurement experiments (experiments 5 and 6), combined with some noise in responding, led the younger children to appear relatively random in their responses. As a consequence, there was not much variation in three-year-old's responses for the model to explain. Future work in this direction should use tasks (or age groups) that show a clear and strong response for each information source.

The primary source of developmental change in our model is age related changes in the propensity to make the individual inferences. As they get older, children expect speakers to be more informative and to be more likely to follow the conversational prior, but the process by which the two information sources are integrated at any given age is assumed to be the same. Other developmental models are also worth exploring in future work; one possible candidate would be a model in which the integration process itself changes with age.

The developmental noise model reported for experiment 7 offers another way to address the question of what changes with development. This model estimates a developmental trajectory for the proportion of responses that are better explained by random guessing than by the model structure (see Fig \ref{fig:fig5}d). If such a model would find that model fit is comparable for younger and older children but that the noise parameter through which this fit is achieved decreases with age, we might conclude that cognitive abilities that have to do with task demands are the major locus of change rather than abilities that have to do with integrating information. In the developmental noise model in experiment 7, we found that noise decreased with age but, at the same time, that the resulting model fit was substantially worse for younger children. However, rather than a difference in how information is integrated, we think that a lack of variation in children's responses is the reason for this poor model fit. The strongest evidence for developmental changes in integration would come in a case where younger children showed evidence of above/below-chance judgment in the combined task that was distinct from that predicted by the two above/below-chance component tasks. Such a comparison would require more precision (either via more trials or more participants) than our current experiment affords, however.

We did not model the social-cognitive processes that underlie common ground. Instead, we assumed that the interactions that preceded the utterance (and presumably constitute common ground) result in a person-specific conversational prior. From a modeling perspective, this approach treats common ground as equivalent to more basic manipulations of contextual salience [e.g. in @frank2012predicting]. Thus, our model would not differentiate between a situation in which an object would be salient because it has been the focus of an interaction and one in which it would be more salient because it was big or colorful. Thus, evoking common ground in this context is largely backed-up by the experimental tasks: the fact that participants (children and adults) were sensitive to the identity of the speaker tells us that the contextual salience of the referents resulted from a process of social reasoning. Thus, we feel confident in saying that our results speak to how participants integrated different sources of pragmatic information. Based on a process model of common ground, one could further specify how common ground information (i.e. social context) interacts with other contextual information [@degen2015wonky; @tessler2017warm]. A further limitation of our work here is that we did not specify how common ground is integrated into the process of compositional interpretation at work in more complex sentences. This is an open challenge for future research on pragmatic inference. One possible approach would be to make inferences about relevant common ground at the level of individual lexical items and to propagate this uncertainty through compositions into larger sentences [as in e.g., @potts2016embedded].

Our model also does not take into account the important distinction for psycholinguistics, namely the difference between privileged ground vs. common ground. This distinction has been addressed computationally by Heller and colleagues [@heller2016perspective; @mozuraitis2018modeling]. In their work, they focus on how listeners identify the referent of ambiguous referring expressions. Their probabilistic model simultaneously considers the (differing) perspectives of both interlocutors and trades off between them. In principle, the model of Heller and colleagues [-@heller2016perspective] and the *integration model* could be combined with one another to address how privileged vs common ground trades off with other pragmatic information.

# Conclusion

Studying how multiple types of pragmatic cues are balanced contributes to a more comprehensive understanding of word learning. In the current study, participants inferred the referent by integrating non-linguistic cues (speakers pointing to a table) with assumptions about speaker informativeness and common ground information, going beyond previous experimental work in measuring how these information sources were combined. The real learning environment is far richer than what we captured in our experimental design, however. For example, in addition to multiple layers of social information, children can rely on semantic and syntactic features of the utterances as cues to meaning [@clark1973s; @gleitman1990structural]. Across development, children learn to recruit these different sources of information and integrate them. RSA models allow for the inclusion of semantic information as part of the utterance [@bergen2016pragmatic] and it will be a fruitful avenue for future research to model the integration of linguistic and pragmatic information across development. To conclude, our work here shows how computational models of language comprehension can be used as powerful tools to explicate and test hypotheses about information integration across development.

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

\newpage

# Declarations of interest

None.

# Author Contributions

M. Bohn and M.C. Frank conceptualized the study, M. Merrick collected the data, M. Bohn and M.H. Tessler analyzed the data, M. Bohn, M. H. Tessler and M.C. Frank wrote the manuscript, all authors approved the final version of the manuscript.

# Acknowledgments

We thank Jacqueline Quirke and Sabina Zacco for help with the data collection and Bria Long and Gregor Kachel for comments on an earlier version of the paper.

# Funding

M. Bohn received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement no. 749229. M. C. Frank was supported by a Jacobs Foundation Advanced Research Fellowship and the Zhou Fund for Language and Cognition.

### 2022-05-28 02_paper/02_study/paper_methods.Rmd

@@
 
-### Eye-Tracking equipment
+Experimental stimuli are freely available in the following online repository: https://github.com/... .
 
-During the unit, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker (https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/).
+### Eye-Tracking data
+
+During the lesson, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker (https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/).
 The system consisted of a wearable head unit and a recording unit.
@@
 An integrated microphone recorded the surrounding sounds.
-Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capure the tacher's gaze point as shown in Figure \@ref(fig:teachergazepoint).
+Infrared light illuminators supported the eye tracking sensors which recorded the eye orientation to capture the teacher's gaze point as shown in Figure \@ref(fig:teachersgaze).
 The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 25 frames per second.
@@
 
-```{r teachergazepoint, include = T, fig.cap = "Teacher's Gaze Point", fig.align = "center", echo = FALSE}
+```{r teachersgaze, include = T, fig.cap = "Teacher's Gaze Point", fig.align = "center", echo = FALSE}
 
-knitr::include_graphics("./pictures/teachergazepoint.png", dpi = 108)
+knitr::include_graphics("./pictures/teachersgaze.pdf", dpi = 108)
 
@@
 
-###  Video and Audio recording equipment
+### Behavioral data
 
@@
 
-### Questionnaire
+### Questionnaire data
 
-After each micro-teaching-unit, the students answered items on teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and scales on the teacher's presence behavior.
-In addition, participants were asked to give a self-assessment on  classroom management by completing the questionnaire after each micro-teaching-unit.
+After each micro-teaching-unit, the three actors answered items on teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and self developed scales on the teacher's presence behavior derived from the research literature.
+In addition, subjects were asked to give a self-assessment on  classroom management by completing the same questionnaire after each micro-teaching-unit.
 The questionnaire was a 4-point Likert scale (1 = Strongly Disagree; 2 = Disagree; 3 = Agree; 4 = Strongly Agree).
@@
 
+### Verbal data
+
+In addition to the eye-tracking, questionnaire and behavioral data, verbal data was also collected in the form of a Stimulated Recall Interview.
+
+\@ref(fig:sri)
+
+```{r sri, include = T, fig.cap = "Subject and experimenter during the Stimulated Recall Interview", fig.align = "center", echo = FALSE}
+
+knitr::include_graphics("./pictures/sri.pdf", dpi = 108)
+
+```
+
 ## Procedure
-
-In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and August 2022.
 
@@
 
-For the data collection, student teachers and experienced teachers were asked to prepare micro-teaching-unit of 15 minutes.
-The subjects taught the micro-teaching-unit in front of a fictitious class consisting of three student assistants who simulated typical classroom events during the lesson.
-A mobile eye-tracker recorded the subject's gaze behavior and audio data of the lesson.
+In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and ... 2022.
+
+Before the data collection, each subject received a personal digital meeting with the experimenter to go over the study procedure and to arrange a date for the data collection.
+During the digital meeting, the subjects were asked to prepare a 15-minute lesson in a subject and grade of their choice for the data collection.
+
+On the day of a data collection, the first step was to set up the study room at the University of Leipzig.
+For this, all the appropriate technical equipment was charged and installed in the room (see set up plan [REFERENZ EINFÜGEN]).
+Next, all four cameras and the audio recorder were synced via Timecode System.
+
+After the subject arrived, a smart watch was put on to measure the heart rate during the session and to get a pretest time at least 15min before the session started.
+In addition to the experimenter and the subject, three student assistants from the working group always took part in the data collection, as they represented the class.
+
+After the welcome, the subject was again briefed about the study.
+It was explicitly pointed out that the student assistants would act as the class and simulate typical class events during the lesson.
+The subject was asked in advance to behave as naturally as possible during the entire time.
+Next, the subjects' written informed consent was obtained and contact details were collected in order to inform all persons participating in the study if a covid infection should occur.
+
+After the introduction, the eye-tracking glasses were adjusted for the subject by inserting contact lenses if necessary and changing the nose pad.
+To start the eye tracking glasses, the Tobii Glasses must be fitted onto the subject's head via an one-point-calibration.
+In the calibration process the subject was asked to look at a Calibration Card held in-front of the subject for a few seconds.
+The experimenter started the recording from Tobii Glasses Controller Software running on a computer.
+
+After starting the eye tracking recording, all other technical devices were also switched on: The four cameras and the audio recorder were controlled via iPad using the BLINK Hup app and could be started simultaneously by synchronization.
+The ZED camera was started manually on another laptop.
+
+Before the 15-minute lesson, there was a short 10-minute warm-up phase.
+The phase was divided into two parts and served on the one hand to get the subjects used to the eye-tracking glasses and on the other hand to get used to their class.
+In the first phase of the warm-up, the game "name juggling" was played using two balls.
+In the game, the subject and the three actors threw two balls at each other and, depending on the color of the ball, called either their own name or that of the target person.
+After the name juggling, the subjects were supposed to start a conversation.
+For this, the subject thought of a question for each student and was also asked a question of each student.
+The content could be anything that interested the participants.
+
+After the warm up phase, the experimenter ensured a manual synchronization of the technique by an acoustic signal in which she clapped her hands loudly twice standing in the middle of the room.
+After this, another nine-point calibration followed outside the study room in a neighboring room.
+Before the subject left the room for calibration, the time on the smartwatch was noted, as well as the steps recorded until that point.
+The subject had to stand at a marked point and look at a board three meters away with nine april tags.
+The subject was asked to read the nine points aloud in order at a normal speaking speed.
+This procedure was important to validate the one-point calibration on the one hand and on the other hand to give the subject the feeling of a lesson start, because after this calibration the subject came into the study room to start the 15-minute lesson.
+
+For the micro-teaching lesson, student teachers and experienced teachers were asked to prepare an introduction of 15 minutes which they taught in front of the fictitious class consisting of three student assistants.
+The actors simulated the nine classroom events during the lesson, derived by research literature.
+The order of the disruptions as well as the students performing them were fully balanced using Latin Square.
+The disruptions were only visible for the class on a screen.
+
+verbal disruption         | agitation               | lack of eagerness to learn
+:---------------:         | :---------------:       | :---------------:
+chatting with neighbor    | drumming hands          | putting head on table
+whispering with neighbor  | clicking pen            | looking at phone
+heckling                  | snipping with fingers   | drawing on a sheet of paper
+
+During the lesson, a mobile eye-tracker recorded the subject's gaze behavior and audio data of the lesson.
 All other sounds and voices were recorded by an audio recorder.
-In addition, the test persons were given a smartwatch to record the number of steps they took and their heart rate.
 To record facial expressions, gestures and movements, four mobile cameras were installed to record the classroom from all perspectives (!!!see figures).
-After the micro-teaching-unit, the teacher conducted a letter search in the room.
-For this, four letters had to be found in order and read aloud.
-This served as a control condition for the speed of the subjects' perceptual ability.
-of the test persons. After the end of the teaching sequence, the class and the teacher
-After the end of the teaching sequence, the class and the teacher filled out a questionnaire focusing on evidence-based methods of teaching diagnostics (EMU) in order to collect data on self-assessment and assessment by others.
 
-In the second part of the survey, the investigator conducted a Stimulated-
-Recall Interview (SRI) with the respondents.
-In this interview, the recorded video of the lesson was watched in its entirety and commented on by the teacher while thinking aloud.
+After the lesson, the time was again noted from the smartwatch as well as the subject's steps.
+The nine-point calibration was also performed again in the neighboring room.
+This time, however, the subject was asked to wait outside the room until he or she was called in, because four letters from A to D were placed in the study room.
+The subject was asked to stand facing the board at a marked point in the room and, when given an acoustic signal, to turn around and search the letters and read them aloud in order.
+This served as a control condition for the speed of the subjects' perceptual ability as no expertise is required for searching letters.
+
+After the letter search, all technical devices were turn
+
+the class and the teacher filled out a questionnaire focusing on evidence-based methods of teaching diagnostics (EMU) in order to collect data on self-assessment and assessment by others.
+
+In the second part of the study, the experimenter conducted a Stimulated-Recall Interview (SRI) with the subject.
+In this interview, the recorded video of the lesson was watched and commented on by the subject while thinking aloud.
+
 Finally, the test persons answered a Situational Judgement Test (SJT, [@gold2015development]) in the form of a questionnaire.

### 2022-05-30 02_paper/02_study/paper_methods.Rmd
method section

@@
 
-verbal disruption         | agitation               | lack of eagerness to learn
-:---------------:         | :---------------:       | :---------------:
-chatting with neighbor    | drumming hands          | putting head on table
-whispering with neighbor  | clicking pen            | looking at phone
-heckling                  | snipping with fingers   | drawing on a sheet of paper
+```{r disruption_categories, include=TRUE, echo=FALSE, results='asis'}
+df_disrup_table <- data.frame(`Verbal Disruption` = c("chatting with neighbor", "whispering with neighbor", "heckling"),
+                              Agitation = c("drumming hands", "clicking pen", "snipping with fingers"),
+                              `Lack of eagerness to learn` = c("putting head on table", "looking at phone", "drawing on a sheet of paper")
+                              )
+
+papaja::apa_table(x = df_disrup_table,
+                  caption = "Categories of Disruptions (Lohmann, 2015)",
+                  escape = TRUE,
+                  placement = "h",
+                  font_size = "tiny")
+
+```
 

### 2022-05-30 02_paper/02_study/paper_methods.tex
method section

@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 \usepackage[titles]{tocloft}
+\cftpagenumbersoff{figure}
+\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
+\renewcommand{\cftfigaftersnum}{.\space}
+\setlength{\cftfigindent}{0pt}
+\setlength{\cftafterloftitleskip}{0pt}
+\settowidth{\cftfignumwidth}{Figure 10.\qquad}
 \cftpagenumbersoff{table}
@@
 The order of the disruptions as well as the students performing them were fully balanced using Latin Square.
+The disruptions were only visible for the class on a screen.
 
-\begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}
-  >{\centering\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3333}}@{}}
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:disruption_categories}Categories of Disruptions (Lohmann, 2015)}
+
+\tiny{
+
+\begin{tabular}{lll}
 \toprule
-\begin{minipage}[b]{\linewidth}\centering
-verbal disruption
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-agitation
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-lack of eagerness to learn
-\end{minipage} \\
+Verbal.Disruption & \multicolumn{1}{c}{Agitation} & \multicolumn{1}{c}{Lack.of.eagerness.to.learn}\\
 \midrule
-\endhead
-chatting with neighbor & drumming hands & putting head on table \\
-whispering with neighbor & clicking pen & looking at phone \\
-heckling & snipping with fingers & drawing on a sheet of paper \\
+chatting with neighbor & drumming hands & putting head on table\\
+whispering with neighbor & clicking pen & looking at phone\\
+heckling & snipping with fingers & drawing on a sheet of paper\\
 \bottomrule
-\end{longtable}
+\end{tabular}
 
-The experimenter used time cards to indicate the time remaining (yellow = one minute remaining; red = time expired).
+}
 
-A mobile eye-tracker recorded the subject's gaze behavior and audio data of the lesson.
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+During the lesson, a mobile eye-tracker recorded the subject's gaze behavior and audio data of the lesson.
 All other sounds and voices were recorded by an audio recorder.
 To record facial expressions, gestures and movements, four mobile cameras were installed to record the classroom from all perspectives (!!!see figures).
-After the micro-teaching-unit, the teacher conducted a letter search in the room.
-For this, four letters had to be found in order and read aloud.
-This served as a control condition for the speed of the subjects' perceptual ability.
 
-of the test persons. After the end of the teaching sequence, the class and the teacher
-After the end of the teaching sequence, the class and the teacher filled out a questionnaire focusing on evidence-based methods of teaching diagnostics (EMU) in order to collect data on self-assessment and assessment by others.
+After the lesson, the time was again noted from the smartwatch as well as the subject's steps.
+The nine-point calibration was also performed again in the neighboring room.
+This time, however, the subject was asked to wait outside the room until he or she was called in, because four letters from A to D were placed in the study room.
+The subject was asked to stand facing the board at a marked point in the room and, when given an acoustic signal, to turn around and search the letters and read them aloud in order.
+This served as a control condition for the speed of the subjects' perceptual ability as no expertise is required for searching letters.
+
+After the letter search, all technical devices were turn
+
+the class and the teacher filled out a questionnaire focusing on evidence-based methods of teaching diagnostics (EMU) in order to collect data on self-assessment and assessment by others.
 
@@
 
-All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.
+All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E.
+Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E.
+J.
+Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.0; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggthemes}{}}%
+Arnold, J. B. (2021). \emph{Ggthemes: Extra themes, scales and geoms for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggthemes}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-gridExtra}{}}%
@@
 Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://cran.r-project.org/package=tinylabels}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-lme4}{}}%
+Bates, D., Mächler, M., Bolker, B., \& Walker, S.
+(2015).
+Fitting linear mixed-effects models using {lme4}.
+\emph{Journal of Statistical Software}, \emph{67}(1), 1--48.
+\url{https://doi.org/10.18637/jss.v067.i01}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-Matrix}{}}%
+Bates, D., \& Maechler, M. (2021). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-rgeos}{}}%
+Bivand, R., \& Rundel, C. (2021). \emph{Rgeos: Interface to geometry engine - open source ('GEOS')}. Retrieved from \url{https://CRAN.R-project.org/package=rgeos}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggmosaic}{}}%
+Jeppson, H., Hofmann, H., \& Cook, D. (2021). \emph{Ggmosaic: Mosaic plots in the 'ggplot2' framework}. Retrieved from \url{https://CRAN.R-project.org/package=ggmosaic}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-needs}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-sjlabelled}{}}%
+Lüdecke, D. (2022). \emph{Sjlabelled: Labelled data utility functions (version 1.2.0)}. \url{https://doi.org/10.5281/zenodo.1249215}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
@@
 \emph{Educational Psychologist}, \emph{40}(1), 13--25.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-sf}{}}%
+Pebesma, E. (2018). {Simple Features for R: Standardized Support for Spatial Vector Data}. \emph{{The R Journal}}, \emph{10}(1), 439--446. \url{https://doi.org/10.32614/RJ-2018-009}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-sp}{}}%
+Pebesma, E. J., \& Bivand, R. S. (2005). Classes and methods for spatial data in {R}. \emph{R News}, \emph{5}(2), 9--13. Retrieved from \url{https://CRAN.R-project.org/doc/Rnews/}
 
@@
 Mahwah, NJ, Lawrence Erlbaum.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggrepel}{}}%
+Slowikowski, K. (2021). \emph{Ggrepel: Automatically position non-overlapping text labels with 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggrepel}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-rnaturalearth}{}}%
+South, A. (2017a). \emph{Rnaturalearth: World map data from natural earth}. Retrieved from \url{https://CRAN.R-project.org/package=rnaturalearth}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-rnaturalearthdata}{}}%
+South, A. (2017b). \emph{Rnaturalearthdata: World vector map data from natural earth used in 'rnaturalearth'}. Retrieved from \url{https://CRAN.R-project.org/package=rnaturalearthdata}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-haven}{}}%
+Wickham, H., \& Miller, E. (2021). \emph{Haven: Import and export 'SPSS', 'stata' and 'SAS' files}. Retrieved from \url{https://CRAN.R-project.org/package=haven}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-cowplot}{}}%
@@
 \clearpage
+\renewcommand{\listfigurename}{Figure captions}
+
+\clearpage
 \renewcommand{\listtablename}{Table captions}

### 2022-06-01 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et aoi.R
update et aoi

@@ -36,18 +36,15 @@ for (i in file_names) {
 }
 
 # Bind every tibble that contains "interval_complete" to a new tiblle
-
 df_aoi <- 
   mget(ls(pattern = "interval_complete")) %>%
   bind_rows()
 
 # Remove temporary data for a cleaner workspace
-
 rm(list = ls(pattern = "^tib_ProVisio"))
 rm(work_data)
 rm(file_names)
 rm(i)
-
 
 # filter relevant rows
 df_aoi <- df_aoi %>% filter (TOI == "Chatting_with_neighbour"|
@@ -92,6 +89,17 @@ df_aoi$Time_to_first_fixation_seconds.Disruptive_Person <- round(df_aoi$Time_to_
                                                     digits = 2)
 
 ########################### TIME TO FIRST FIXATION ON DISRUPTIVE PERSON ######################
+
+# t-test for expertise differences
+t.test(x = df_aoi$Time_to_first_fixation.Disruptive_Person[df_aoi$Group == "Expert"],
+       y = df_aoi$Time_to_first_fixation.Disruptive_Person[df_aoi$Group == "Novice"])
+
+
+# effect size for group differenes
+d <- CohenD(x = df_aoi$Time_to_first_fixation.Disruptive_Person[df_aoi$Group == "Novice"],
+            y = df_aoi$Time_to_first_fixation.Disruptive_Person[df_aoi$Group == "Expert"],
+            na.rm = TRUE
+            )
 
 # plotting time to first fixation for groups
 fix_group_plot <- 
@@ -180,6 +188,29 @@ fix_plot_sum
 
 ########################### TOTAL DURATION OF FIXATIONS IN AOIS ######################
 
+df_aoi_dur <-
+  df_aoi %>% 
+  mutate(
+    Total_duration_of_fixations = sum(c_across(starts_with("Total_duration")
+                                                      )
+                                               ),
+                                      na.rm = TRUE
+                                      )
+    )
+
+# t-test für Gruppenunterschiede 
+t.test(x = df_aoi_totaldur$Total_Durations_Of_Fixations[Total_Durations_Of_Fixations$Group == "Expert"],
+       y = df_aoi_totaldur$Total_Durations_Of_Fixations[Total_Durations_Of_Fixations$Group == "Novice"])
+
+
+# Effektstärke berechnen für Gruppenunterschiede
[…]

### 2022-06-01 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et aoi.R
update code

@@ -47,15 +47,17 @@ rm(file_names)
 rm(i)
 
 # filter relevant rows
-df_aoi <- df_aoi %>% filter (TOI == "Chatting_with_neighbour"|
-                               TOI == "Clicking_pen"| 
-                               TOI == "Drawing"|
-                               TOI == "Drumming_with_hands"| 
-                               TOI == "Head_on_table"| 
-                               TOI == "Heckling"|
-                               TOI == "Looking_at_phone" |
-                               TOI == "Snipping_with_fingers"|
-                               TOI == "Whispering")
+df_aoi <- df_aoi %>% filter (TOI %in% c("Chatting_with_neighbour",
+                                        "Clicking_pen",
+                                        "Drawing",
+                                        "Drumming_with_hands",
+                                        "Head_on_table",
+                                        "Heckling",
+                                        "Looking_at_phone",
+                                        "Snipping_with_fingers",
+                                        "Whispering"
+                                        )
+                             )
 
 # creating new variable with sum disruptions
 df_aoi$TOI_sum[df_aoi$TOI == "Chatting_with_neighbour" |
@@ -190,22 +192,22 @@ fix_plot_sum
 
 df_aoi_dur <-
   df_aoi %>% 
-  mutate(
-    Total_duration_of_fixations = sum(c_across(starts_with("Total_duration")
-                                                      )
-                                               ),
-                                      na.rm = TRUE
-                                      )
-    )
+  rowwise() %>% 
+  mutate(Total_duration_of_fixations = sum(c_across(starts_with("Total_duration")
+                                                    ),
+                                           na.rm = TRUE
+                                           )
+         )
+    
 
 # t-test für Gruppenunterschiede 
-t.test(x = df_aoi_totaldur$Total_Durations_Of_Fixations[Total_Durations_Of_Fixations$Group == "Expert"],
-       y = df_aoi_totaldur$Total_Durations_Of_Fixations[Total_Durations_Of_Fixations$Group == "Novice"])
+t.test(x = df_aoi_dur$Total_duration_of_fixations[df_aoi_dur$Group == "Expert"],
+       y = df_aoi_dur$Total_duration_of_fixations[df_aoi_dur$Group == "Novice"])
 
 
 # Effektstärke berechnen für Gruppenunterschiede
[…]

### 2022-06-02 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et aoi.R
update SJT + AOI script

@@ -14,13 +14,11 @@ needs(tidyverse,
 # if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
 options(dplyr.summarise.inform = FALSE)
 
-# Return a character vector with names of .tsv data in data folder
-
+# return a character vector with names of .tsv data in data folder
 file_names <- list.files(path = "data",
                          pattern = "interval_complete.tsv")
 
-# Read every object names in file_names and save it as a tibble
-
+# read every object names in file_names and save it as a tibble
 for (i in file_names) {
   
   work_data <- 
@@ -86,19 +84,20 @@ df_aoi <- df_aoi %>%
 # # remove all NAs
 # df_aoi <- na.omit(df_aoi)
 
-# changing milliseconds into seconds
-df_aoi$Time_to_first_fixation_seconds.Disruptive_Person <- round(df_aoi$Time_to_first_fixation.Disruptive_Person/1000,
-                                                    digits = 2)
 
 ########################### TIME TO FIRST FIXATION ON DISRUPTIVE PERSON ######################
 
+# changing milliseconds into seconds
+df_aoi$Time_to_first_fixation_seconds.Disruptive_Person <- round(df_aoi$Time_to_first_fixation.Disruptive_Person/1000, digits = 2)
+
+# TIME TO FIRST FIXATION ON DISRUPTIVE PERSON 
 # t-test for expertise differences
 t.test(x = df_aoi$Time_to_first_fixation.Disruptive_Person[df_aoi$Group == "Expert"],
        y = df_aoi$Time_to_first_fixation.Disruptive_Person[df_aoi$Group == "Novice"])
 
-
+# TIME TO FIRST FIXATION ON DISRUPTIVE PERSON 
 # effect size for group differenes
-d <- CohenD(x = df_aoi$Time_to_first_fixation.Disruptive_Person[df_aoi$Group == "Novice"],
+d_time <- CohenD(x = df_aoi$Time_to_first_fixation.Disruptive_Person[df_aoi$Group == "Novice"],
             y = df_aoi$Time_to_first_fixation.Disruptive_Person[df_aoi$Group == "Expert"],
             na.rm = TRUE
             )
@@ -152,7 +151,6 @@ fix_group_plot
 # fix_plot
 
 
-
 # plotting time to first fixation for 3 disruptions sum up
 fix_plot_sum <-
   ggplot(data = df_aoi,
[…]

### 2022-06-02 01_studies/01_Laborstudie ProVisioNET/SJTest/SJTest.R

@@ -7,7 +7,8 @@ needs(tidyverse,
       gridExtra,
       cowplot,
       readxl,
-      ARTofR)
+      ARTofR,
+      DescTools)
 
 # read in data
 df_sjt <- read_csv2(file = "C:/Users/mk99feta/OneDrive/Dokumente/GitHub/Mandy-PhD/01_studies/01_Laborstudie ProVisioNET/SJTest/data/SJT.csv")
@@ -60,7 +61,12 @@ mean_plot <-
     axis.ticks.x = element_blank(),
     strip.text.x = element_text(size = 14),
     axis.title.y = element_text(size = 13),
-    axis.title.x = element_text(size = 25))
+    axis.title.x = element_text(size = 25)
+        )
+  # + annotate(geom = "text",
+  #          x = "All",
+  #          y = 0.25,
+  #          label = paste ("d = ", round(d_sjt_all),3))
 
 mean_plot
 
@@ -101,4 +107,60 @@ sjt_r <- df_sjt_long %>%
   group_by(Group) %>%
   summarise("M" = round(mean(Mean), 2),
             "SD" = round(sd(Mean), 2))
+
+#################### T-TEST & EFFECT SIZE ##################
+
+# define expert and novice with ifelse function in wide format
+df_sjt$Group = ifelse(df_sjt$Group < 200, "Novice","Expert")
+
+#### ALL #### 
+# t-test for expertise differences 
+t.test(x = df_sjt$All[df_sjt$Group == "Expert"],
+       y = df_sjt$All[df_sjt$Group == "Novice"])
+
+
+# effect size for expertise differences
+d_sjt_all <- CohenD(x = df_sjt$All[df_sjt$Group == "Novice"],
+                y = df_sjt$All[df_sjt$Group == "Expert"],
+                na.rm = TRUE
+                    )
+
+#### MANAGING MOMENTUM #### 
+# t-test for expertise differences 
+t.test(x = df_sjt$`Managing momentum`[df_sjt$Group == "Expert"],
+       y = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"]
+       )
+
+
+# effect size for expertise differences
+d_sjt_mm <- CohenD(x = df_sjt$`Managing momentum`[df_sjt$Group == "Novice"],
+                    y = df_sjt$`Managing momentum`[df_sjt$Group == "Expert"],
+                    na.rm = TRUE
+                  )
+
+#### MONITORING ####
[…]

### 2022-06-02 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et aoi.R
Rrrrrrrrrr

@@ -103,23 +103,29 @@ d_time <- CohenD(x = df_aoi$Time_to_first_fixation.Disruptive_Person[df_aoi$Grou
             )
 
 # plotting time to first fixation for groups
-fix_group_plot <- 
+fix_group_plot <-
   ggplot(data = df_aoi,
          mapping = aes(x = Group,
                        y = Time_to_first_fixation_seconds.Disruptive_Person)) +
   geom_boxplot(mapping = aes(fill = Group)) +
-  geom_point(size = 2, 
+  geom_point(size = 2,
              alpha = 0.4,
-             position = position_jitter(seed = 1, 
-                                        width = 0.1)) +
-  ylim(0,25) + 
-  labs(x ="") + 
-  scale_fill_brewer(palette = "Set1") +
-  ggtitle("Time to first fixation in seconds to disruptive person") +
-  theme_classic() + 
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0)) +
+  ylim(0,15) +
+  labs(x = "",
+       y = "Time to first fixation in seconds") +
+  scale_fill_manual(values=c("steelblue","firebrick")) +  
+  ggtitle("Time to first fixation to disruptive person for expertise groups") +
+  theme_classic() +
   theme(legend.position="none",
-        axis.text.x = element_text(size = 11),
-        plot.title = element_text(size = 15, face = "bold"))
+        axis.text.x = element_text(size = 14),
+        axis.text.y = element_text(size = 14),
+        axis.title = element_text(size=14),
+        plot.title = element_text(size = 15, 
+                                  face = "bold")
+        )
 
 fix_group_plot
 
@@ -136,7 +142,7 @@ fix_group_plot
 #                                         width = 0.1)) +
 #   ylim(0,25) + 
 #   labs(x ="") + 
-#   scale_fill_brewer(palette = "Set1") +
+#   scale_fill_manual(values=c("steelblue","firebrick")) +
 #   facet_wrap(vars(TOI), 
 #              nrow = 1, strip.position = "bottom") +
 #   ggtitle("Time to first fixation in seconds to disruptive person") +
@@ -157,17 +163,17 @@ fix_plot_sum <-
          mapping = aes(x = Group,
                        y = Time_to_first_fixation_seconds.Disruptive_Person)) +
   geom_boxplot(mapping = aes(fill = Group)) +
-  # geom_point(size = 2, 
-  #            alpha = 0.4,
[…]

### 2022-06-03 02_paper/02_study/paper_methods.Rmd
update method

@@
 We have no conflicts of interest to disclose.
-This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11 2022; EARLI SIG 27, 2022).
+This article is based on data used at conference presentations (DACH-Nachwuchsakademie, 2022; EARLI SIG 11, 2022; EARLI SIG 27, 2022).
 
@@
       kableExtra,
-      xtable)
+      xtable,
+      DescTools)
 
@@
 
-# creating new column with percent of gender
+# creating new column with total participants to calculate percent of gender
 demo.data <- demo.data %>%
@@
   mutate(Gender_Sum=n())
+
+# changing Type of School into character
+# LI18:
+# 1: Grundschule
+# 2: Oberschule
+# 3: Gymnasium
+# 4: Förderschule/Sondershausen
+# 5: Berufsbildende Schule
+# -1: andere Schulform
+demo.data$`Type of School` <- factor(x = demo.data$`Type of School`,
+                   levels = c("1","2","3","4","5","-1"), # Mögliche Werte # andere Möglichkeit: unique(demo.data$`Type of School`)
+                   labels = c("Grundschule","Oberschule","Gymnasium","Förderschule","Berufsbildende Schule", "andere Schulform")) # Bezeichnungen
 
@@
 
+### XXX Type of School noch eintragen
+
 The novice teachers (`r demo.data %>% filter(Gender == 1 & Group == "Novice") %>% pull(Gender) %>% length()` women; `r demo.table %>% filter(Group == "Novice") %>% pull("Gender female in percent")`%) had a mean age of `r demo.data %>% filter(Group == "Novice") %>% pull(Age) %>% mean() %>% round(., digits = 1)` years (*SD* = `r demo.table %>% filter(Group == "Novice") %>% pull("SD Age in years") %>% round(., digits = 1)`; range: `r demo.table %>%  filter(Group == "Novice") %>% pull("Min Age in years")`-`r demo.table %>%  filter(Group == "Novice") %>% pull("Max Age in years")`) with an average teaching experience of `r exp.table %>% filter(Group == "Novice") %>% pull("M Exp.") %>% mean() %>% round(., digits = 1)` years.
@@
 
-## Material
+## Variables
 
-Experimental stimuli are freely available in the following online repository: https://github.com/... .
+All stimuli are freely available in the following online repository: https://github.com/... .
 
@@
 
-During the lesson, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker (https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/).
+To record eye-tracking data, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker during the micro-teaching-unit.
 The system consisted of a wearable head unit and a recording unit.
@@
 
-### Behavioral data
+### Video data
 
-The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder (https://zoomcorp.com/en/gb/handheld-recorders/handheld-recorders/h3-vr-360-audio-recorder/) installed in the middle of the lab setting.
+The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder installed in the middle of the lab setting (see set up plan \@ref(fig:setup).
 The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.
 
-Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras (https://gopro.com/content/dam/help/hero7-black/manuals/HERO7Black_UM_ENG_REVC.pdf) from different angles.
+Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras from different angles (see set up plan \@ref(fig:setup).
 The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.
@@
 
-### Verbal data
-
-In addition to the eye-tracking, questionnaire and behavioral data, verbal data was also collected in the form of a Stimulated Recall Interview.
+#### Rating scales
 
@@
 ```
+
+#### Situational Jugdement Test
+To assess the strategic knowledge of classroom management, subjects answered a Situational Judgement Test (SJT, [@gold2015development]).
+
+Gold and Holodynski (2015, p.
+229) developed a 'Situational Judgment Test of Strategic Knowledge of Classroom Management in Elementary Schools (SJT)' to measure strategic knowledge of classroom management among elementary school teachers.
+This is a test procedure for situation-specific action in which the participants are presented with hypothetical scenarios for which they are to indicate how a teacher should ideally behave or how promising the presented options for action are on the basis of given answer options.
+
+In developing the test procedure, the authors divided the concept of classroom management into three main aspects: *Monitoring*, *managing momentum* (structuring) and *rules and routines* [@gold2015development, p.
+230f].
+
+*Monitoring* includes proactive strategies such as omnipresence.
+This means, the teacher is always informed about the students' behavior, regulates it and reports it back to them.
+The second strategy is overlapping.
+In this case, the teacher is able to control several teaching processes at the same time.
+Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions (cf.
+ibid.; [@kounin2006techniken, p.
+89ff).
+
+By *managing momentum* (structuring), Gold and Holodynski (2015) understand the skillful control of teaching processes so that they can run smoothly and without delays, taking into account the students' level of understanding and attention [@kounin2006techniken, p.
+101ff].
+They also include the group focus specifically identified by Kounin [@kounin2006techniken, p.
+117ff], i.e.
+mobilizing the whole class and demanding accountability [@gold2015development, p.
+231].
+
+The third facet of classroom management, establishing *rules, routines and rituals*, supports the other two facets and offers the pupils, orientation and structure in everyday school life (cf. ibid.).
+
+When taking the test, participants must rate all six response options for each scenario as suitable or unsuitable using a six-point scale (see sample scenario in Appendix 1).
+Prior to this, the effectiveness of the strategies proposed in the answers was determined by expert judgement.
+Based on these, an overall rating was created, which is used for the evaluation of the answer keys.
+All three mentioned knowledge facets of class management (monitoring, transition design and rules and routines) are recorded separately with separate tasks in this SJT by Gold and Holodynski.
+The original 14 individual scenarios can each be assigned to one facet: Scenarios 1-5 cover the area of ubiquity, scenarios 6-10 the area of structuring and scenarios 11-14 the area of rules and routines.
+Scenarios 10 and 12 were removed from the test due to insufficient agreement between the expert judgement.
+In the evaluation, in addition to an overall assessment, all three knowledge areas can be presented and compared individually.
 
@@
 
-Finally, the test persons answered a Situational Judgement Test (SJT, [@gold2015development]) in the form of a questionnaire.
+Finally, the subjects answered a Situational Judgement Test (SJT, [@gold2015development]) in the form of a questionnaire.
 Here they had to assess teaching scenarios and evaluate their behavior in response to them.

### 2022-06-03 02_paper/02_study/paper_methods.tex
update method

@@
 
+\begin{verbatim}
+## Warning: NAs durch Umwandlung erzeugt
+\end{verbatim}
+
 \begin{table}[h]
@@
 Expert & 7 & 18.10 & 14.10 & 3.00 & 37.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 71.00\\
-Novice & 21 & 0.00 & 0.00 & 0.00 & 0.00 & 7.40 & 2.50 & 3.00 & 11.00 & 12.00 & 8.60 & 0.00 & 36.00 & 90.50 & NA\\
+Novice & 21 & 0.00 & 0.00 & 0.00 & 0.00 & NA & NA & NA & NA & 12.00 & 8.60 & 0.00 & 36.00 & 90.50 & NA\\
 \bottomrule
@@
 The novice teachers (13 women; 61.90\%) had a mean age of 23.30 years (\emph{SD} = 1.70; range: 20-27) with an average teaching experience of 0 years.
-On average, the student teachers were in their 7.40 semester (\emph{SD} = 2.50; range: 3-11).
+On average, the student teachers were in their NA semester (\emph{SD} = NA; range: NA-NA).
 Furthermore, they had an average teaching experience of 12 teaching units à 45min (\emph{SD} = 8.60; range: 0-36) through the internships during their studies.

### 2022-06-04 02_paper/02_study/paper_methods.Rmd
method

@@
 <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
+
+This study had a quasi-experimental study design, as there was no random assignment of the subjects to experimental conditions.
+Due to the use of mobile eye-tracking technology, the study had a high external validity [@gegenfurtner2018mobiles].
+Internal validity could be ensured to the extent that the disruptive events that occurred were exactly the same for all subjects, as the actors received precise behavioral instructions.
+These disruptions followed a script and coding scheme in which the actions of the class were precisely described.
+The order of the disruptions as well as the performing actors were fully balanced with Lain Square to exclude row effects.
+
+The scripted behavioral instructions during the micro-teaching unit characterized the study with a high degree of standardization, especially when compared to events taking place in a real classroom.
+The study was based on an experimental manual, script and coding, which explicitly described the implementation, evaluation as well as interpretation of the data, thus making it objectively recordable and measurable.
 
@@
 
-\@ref(fig:sri)
+Two self-developed 11-point rating scales were used to record how disruptive the individual disruptions were perceived by the subjects and how confident they felt in dealing with the disruptions.
+Data for rating scales were collected during the Stimulted Recall Interview, where the experimenter watched the pre-recorded eye-tracking video with the subject.
 
-```{r sri, include = T, fig.cap = "Subject and experimenter during the Stimulated Recall Interview", fig.align = "center", echo = FALSE}
+The questionnaire included nine questions for each scripted disruptive event. The subjects did not have to complete the questionnaire themselves at any time, as this was done by the experimenter.
 
-knitr::include_graphics("./pictures/sri.pdf", dpi = 108)
+For the present study, the following two questions from the interview were relevant:
+1. "How disturbing did you perceive this event to be?"
+2. "How confident did you feel in dealing with this event?"
 
-```
+Both questions were answered using a scale ranging from 0 to 10. On this scale, 0 stood for "not at all disruptive" or "not at all safe" and 10 for "extremely disturbing" or "extremely safe."
+
+With these rating scales, the subjects indicated their personal subjective feeling towards the individual lesson disruption.
+Rating scales usually consist of a number of clearly arranged categories that can be presented visually in a variety of ways [@albers2009methodik, p.
+67f].
+In the present questionnaire, the numerical representation with eleven answer options (0-10) was used.
+There was no specific designated neutral position.
+In this questionnaire, the middle category 5 was not interpreted as a neutral position.
+In order to avoid misinterpretations of the scaling, the questionnaire was described verbally by the experimenter and follow-up questions from the test subjects were possible at any time.
+With regard to the quality criteria, it should be made clear that complete objectivity in answering the two questions is given by the rating scales.
+The question remained the same for all subjects and no additional comments were made.
+Validity can also be assumed for the questionnaire, since the subjects couls ask follow-up questions and thus uncertainties were clarified.
+However, similar to the video data, there was no perfect reliability with this survey instrument, because in a few exceptional cases, for example, the experimenter forgot to ask the subject the relevant questions.
 
 #### Situational Jugdement Test
+
 To assess the strategic knowledge of classroom management, subjects answered a Situational Judgement Test (SJT, [@gold2015development]).
-
-Gold and Holodynski (2015, p.
-229) developed a 'Situational Judgment Test of Strategic Knowledge of Classroom Management in Elementary Schools (SJT)' to measure strategic knowledge of classroom management among elementary school teachers.
-This is a test procedure for situation-specific action in which the participants are presented with hypothetical scenarios for which they are to indicate how a teacher should ideally behave or how promising the presented options for action are on the basis of given answer options.
+In the questionnaire, participants were given hypothetical school scenarios with with 5-7 response strategy for which they had to evaluate the effectiveness of each strategy on a 6-point rating scale from 1 (A) to 6 (F) according to school grades (see example scenario XXX REFERENZ EINFÜGEN).
 
@@
 
-The third facet of classroom management, establishing *rules, routines and rituals*, supports the other two facets and offers the pupils, orientation and structure in everyday school life (cf. ibid.).
+The third facet of classroom management, establishing *rules, routines and rituals*, supports the other two facets and offers pupils orientation and structure in everyday school life (cf. ibid.).
 
-When taking the test, participants must rate all six response options for each scenario as suitable or unsuitable using a six-point scale (see sample scenario in Appendix 1).
-Prior to this, the effectiveness of the strategies proposed in the answers was determined by expert judgement.
-Based on these, an overall rating was created, which is used for the evaluation of the answer keys.
-All three mentioned knowledge facets of class management (monitoring, transition design and rules and routines) are recorded separately with separate tasks in this SJT by Gold and Holodynski.
-The original 14 individual scenarios can each be assigned to one facet: Scenarios 1-5 cover the area of ubiquity, scenarios 6-10 the area of structuring and scenarios 11-14 the area of rules and routines.
-Scenarios 10 and 12 were removed from the test due to insufficient agreement between the expert judgement.
-In the evaluation, in addition to an overall assessment, all three knowledge areas can be presented and compared individually.
+The construction of the SJT included 14 scenarios that were based on transcribed classroom videos from Germany.
+For the 14 scenarios, response strategies were derived from evidence-based and theoretical principles by 17 experts on classroom management.
+With the exception of scenario 5, which was subsequently excluded, the 17 experts agreed on an appropriate level of content validity for all other scenarios (cf.
+ibid.).
+For the validation of the strategies, pair comparisons were made between different strategies and the frequencies were calculated in relation to the expert responses (cf.
+ibid., p.
+238).
+Scenarios 10 and 12 were excluded from further analysis because they did not reach the minimum level of agreement (cf.
+ibid.).
+
+The construct validity of the SJT with the other 11 scenarios and the sensitivity to differences in strategic knowledge was then examined in a pilot study with 98 trainee teachers and their results validated in a cross-validation with a larger sample (cf.
+ibid., p.
+238ff).
+Despite limitations in reliability, the test was confirmed to have content and construct validity (cf.
+ibid., p.
+243).
+On the basis of these results, sufficient reliability and validity of the SJT test procedure was assumed.
+
+The scenarios could each be assigned to one facet of the mentioned classroom management: Scenarios 1-4 cover the facet *monitoring*, scenarios 6-9 the facet *managing momentum* and scenarios 11-14 the facet *rules and routines*.
+
+In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study *ProVisioNET*.
+The objectivity of analysis was given by processing the obtained questionnaire data in `r cite_r("r-references.bib")` and IBM SPSS 28.
+
+Since the test was a questionnaire designed to assess strategic knowledge of classroom management of *primary school teachers*, but the sample of the study included several types of schools, changes were made in 10 out of 12 scenarios by deleting the indicated class grade.
+Only in two scenarios was the class grade information not deleted, as the action alternatives would otherwise not be appropriate without the information.
 
@@
 
-In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and ... 2022.
+In June 2021, the study was piloted with student teachers volunteers to refine the study procedure. Data collection was conducted between July 2021 and Septemper 2022.
 
@@
 
-After the letter search, all technical devices were turn
+After the letter search, the experimenter clapped twice with the hands to record an acoustic signal for the synchronization of all technical devices.
+Afterwards, all devices were switched off and the subjects as well as the actors were given a short questionnaire, which contained items to collect demographic information as well as items about the previously given lesson on teaching quality using a validated questionnaire [@helmke2014unterrichtsdiagnostik] and self developed scales on the teacher's presence behavior derived from the research literature.
+The completion of the questionnaire took approximately 5 minutes.
 
-the class and the teacher filled out a questionnaire focusing on evidence-based methods of teaching diagnostics (EMU) in order to collect data on self-assessment and assessment by others.
+In the second part of the study, the experimenter conducted a Stimulated Recall Interview (SRI) with the subject(see in Figure \@ref(fig:sri).
+The interview was recorded by the ambient recorder and additionally with a software called OBS to record the speech and screen.
+The recorded eye-tracking video was watched and commented on by the subject while thinking aloud.
+The interview was structured by a guideline based on a fixed sequence of questions, however the subjects were allowed to answer completely open to these questions.
+The objective was to collect data that would provide insight into the subjects' thoughts and reactions in relation to the scripted classroom disruptions.
+The eye-tracking video was not completely re-watched, but stopped at the points where disruptions occurred.
+After the disruption occurred, the subject was asked to describe what had just happened.
+If the disruption was noticed, the subject was asked how disruptive the event was at that moment on a scale from 0 to 10 (for a detailed description of the scale question, see Rating Scales).
+In addition, the subject was asked to reason the given number.
+In a next step, the experimenter re-played the subject's reaction to the disruption and asked to describe and reason the reaction.
+The
 
-In the second part of the study, the experimenter conducted a Stimulated-Recall Interview (SRI) with the subject.
-In this interview, the recorded video of the lesson was watched and commented on by the subject while thinking aloud.
+```{r sri, include = T, fig.cap = "Subject and experimenter during the Stimulated Recall Interview", fig.align = "center", echo = FALSE}
+
+knitr::include_graphics("./pictures/sri.pdf", dpi = 108)
+
+```
 
@@
 The SJT was used to assess strategic knowledge about classroom management.
-
-This study is subject to a quasi-experimental study design, as there was no random assignment of the test persons to the experimental conditions.
-Due to the use of MET technology, the study has a high external validity (Gegenfurtner et al., 2018).
-The SRI carried out afterwards explicitly investigates the subjects' sense of disturbance and feeling of safety, which speaks for a high content validity of the study.
-Internal validity can be ensured to the extent that the teaching events that occurred were exactly the same for all subjects, as the learners received precise behavioural instructions.
-These disturbances followed a script and coding guide in which the actions of the class were precisely described.
-The sequence of events varied from survey to survey so that disruptions were always random.
-The scripted behavioural instructions during the teaching sequence characterise this study with a high degree of standardization, especially when compared to events taking place in a real classroom.
-The study is based on an experimental manual, script and coding guide, which explicitly describes the implementation, evaluation as well as interpretation of the data, thus making it objectively recordable and measurable.
-As this study takes place within the framework of the dissertation ProVisioNET, the original survey will continue beyond the submission of this scientific work.
-continues.
+The
+completion of the entire survey took 15 min on average.
 

### 2022-06-04 02_paper/02_study/paper_methods.tex
method

@@
 
-\begin{verbatim}
-## Warning: NAs durch Umwandlung erzeugt
-\end{verbatim}
-
 \begin{table}[h]
@@
 \midrule
-Expert & 7 & 71.40 & 45.10 & 12.00 & 27.00 & 59.00\\
-Novice & 21 & 61.90 & 23.30 & 1.70 & 20.00 & 27.00\\
+Expert & 15 & 60.00 & 42.90 & 11.30 & 27.00 & 59.00\\
+Novice & 24 & 66.70 & 23.50 & 1.80 & 20.00 & 27.00\\
 \bottomrule
@@
 \midrule
-Expert & 7 & 18.10 & 14.10 & 3.00 & 37.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 71.00\\
-Novice & 21 & 0.00 & 0.00 & 0.00 & 0.00 & NA & NA & NA & NA & 12.00 & 8.60 & 0.00 & 36.00 & 90.50 & NA\\
+Expert & 15 & 15.70 & 13.30 & 2.00 & 37.00 & NA & NA & NA & NA & NA & NA & NA & NA & NA & 60.00\\
+Novice & 24 & 0.00 & 0.00 & 0.00 & 0.00 & 7.20 & 2.60 & 3.00 & 11.00 & 11.30 & 8.20 & 4.00 & 36.00 & 87.50 & NA\\
 \bottomrule
@@
 
-The sample consists of \emph{N} = 28 participants with \emph{n} = 7 expert teachers and \emph{n} = 21 novice teachers.
+The sample consists of \emph{N} = 39 participants with \emph{n} = 15 expert teachers and \emph{n} = 24 novice teachers.
 
@@
 
-The expert teachers (5 women; 71.40\%) had a mean age of 45.10 years (\emph{SD} = 12; range: 27-59) and an average teaching experience of 18.10 years (\emph{SD} = 14.10; range: 3-37).
-71\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
+The expert teachers (9 women; 60\%) had a mean age of 42.90 years (\emph{SD} = 11.30; range: 27-59) and an average teaching experience of 15.70 years (\emph{SD} = 13.30; range: 2-37).
+60\% of the experienced teachers were also engaged in an secondary teaching activity, such as lecturers at the university, main training supervisors for trainee teachers and subject advisers.
 
-The novice teachers (13 women; 61.90\%) had a mean age of 23.30 years (\emph{SD} = 1.70; range: 20-27) with an average teaching experience of 0 years.
-On average, the student teachers were in their NA semester (\emph{SD} = NA; range: NA-NA).
-Furthermore, they had an average teaching experience of 12 teaching units à 45min (\emph{SD} = 8.60; range: 0-36) through the internships during their studies.
-90.50\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
+\hypertarget{xxx-type-of-school-noch-eintragen}{%
+\subsubsection{XXX Type of School noch eintragen}\label{xxx-type-of-school-noch-eintragen}}
+
+The novice teachers (16 women; 66.70\%) had a mean age of 23.50 years (\emph{SD} = 1.80; range: 20-27) with an average teaching experience of 0 years.
+On average, the student teachers were in their 7.20 semester (\emph{SD} = 2.60; range: 3-11).
+Furthermore, they had an average teaching experience of 11.30 teaching units à 45min (\emph{SD} = 8.20; range: 4-36) through the internships during their studies.
+87.50\% of the student teachers were also engaged in an extracurricular teaching activity, such as tutoring or homework supervision.
 
@@
 
-\hypertarget{material}{%
-\subsection{Material}\label{material}}
+\hypertarget{variables}{%
+\subsection{Variables}\label{variables}}
 
-Experimental stimuli are freely available in the following online repository: \url{https://github.com/}\ldots{} .
+All stimuli are freely available in the following online repository: \url{https://github.com/}\ldots{} .
 
@@
 
-During the lesson, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker (\url{https://www.tobiipro.com/product-listing/tobii-pro-glasses-2/}).
+To record eye-tracking data, teachers wore a binocular Tobii Pro Glasses 2 eye-tracker during the micro-teaching-unit.
 The system consisted of a wearable head unit and a recording unit.
@@
 
-\hypertarget{behavioral-data}{%
-\subsubsection{Behavioral data}\label{behavioral-data}}
+\hypertarget{video-data}{%
+\subsubsection{Video data}\label{video-data}}
 
-The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder (\url{https://zoomcorp.com/en/gb/handheld-recorders/handheld-recorders/h3-vr-360-audio-recorder/}) installed in the middle of the lab setting.
+The speech, sounds and voices of the participants were recorded with Zoom H3-VR Ambient Recorder installed in the middle of the lab setting (see set up plan \ref{fig:setup}.
 The Zoom H3-VR recorded with four built-in mics arranged in an Ambisonic array with a bitrate of 4608 kBits/s.
 
-Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras (\url{https://gopro.com/content/dam/help/hero7-black/manuals/HERO7Black_UM_ENG_REVC.pdf}) from different angles.
+Movements, facial expressions and gestures of the subjects were recorded by four Go Pro Hero 7 black cameras from different angles (see set up plan \ref{fig:setup}.
 The videos were recorded with a sampling rate of 50 Hz in a video resolution with 1920 x 1080 at 50 frames per second in 16:9 format with a linear field of view.
@@
 \midrule
-Classroom Management & 8.00 & 2.94 & 0.26 & 2.50 & 3.38 & 0.02 & 1.69 & 0.31\\
-Balance & 3.00 & 3.14 & 0.56 & 1.67 & 4.00 & -0.45 & 3.53 & 0.71\\
-Presence & 8.00 & 3.10 & 0.36 & 2.50 & 3.88 & 0.10 & 2.65 & 0.66\\
-Natural Behavior & 3.00 & 3.17 & 0.65 & 1.67 & 4.00 & -0.65 & 2.91 & 0.80\\
+Classroom Management & 8.00 & 2.92 & 0.25 & 2.50 & 3.38 & 0.20 & 1.76 & 0.32\\
+Balance & 3.00 & 3.15 & 0.55 & 1.67 & 4.00 & -0.47 & 3.53 & 0.60\\
+Presence & 8.00 & 3.12 & 0.34 & 2.50 & 3.88 & -0.08 & 2.81 & 0.64\\
+Natural Behavior & 3.00 & 3.14 & 0.61 & 1.67 & 4.00 & -0.51 & 2.99 & 0.79\\
 \bottomrule
@@
 \midrule
-Classroom Management & 8.00 & 3.00 & 0.20 & 2.75 & 3.25 & 0.25 & 1.42 & -0.16\\
-Balance & 3.00 & 3.43 & 0.42 & 2.67 & 4.00 & -0.57 & 2.87 & 0.41\\
-Presence & 8.00 & 3.36 & 0.45 & 2.50 & 3.88 & -0.85 & 2.95 & 0.84\\
-Natural Behavior & 3.00 & 3.38 & 0.36 & 3.00 & 4.00 & 0.60 & 2.36 & 0.00\\
+Classroom Management & 8.00 & 3.17 & 0.27 & 2.75 & 3.62 & 0.30 & 2.21 & 0.38\\
+Balance & 3.00 & 3.27 & 0.58 & 2.00 & 4.00 & -0.78 & 2.81 & 0.77\\
+Presence & 8.00 & 3.44 & 0.37 & 2.50 & 3.88 & -1.10 & 3.97 & 0.74\\
+Natural Behavior & 3.00 & 3.42 & 0.50 & 2.67 & 4.00 & -0.07 & 1.66 & 0.68\\
 \bottomrule
@@
 
-\hypertarget{verbal-data}{%
-\subsubsection{Verbal data}\label{verbal-data}}
-
-In addition to the eye-tracking, questionnaire and behavioral data, verbal data was also collected in the form of a Stimulated Recall Interview.
+\hypertarget{rating-scales}{%
+\paragraph{Rating scales}\label{rating-scales}}
 
@@
 \end{figure}
+
+\hypertarget{situational-jugdement-test}{%
+\paragraph{Situational Jugdement Test}\label{situational-jugdement-test}}
+
+To assess the strategic knowledge of classroom management, subjects answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)).
+
+Gold and Holodynski (2015, p.~229) developed a `Situational Judgment Test of Strategic Knowledge of Classroom Management in Elementary Schools (SJT)' to measure strategic knowledge of classroom management among elementary school teachers.
+This is a test procedure for situation-specific action in which the participants were presented with hypothetical scenarios for which they are to indicate how a teacher should ideally behave or how promising the presented options for action are on the basis of given answer options.
+
+In developing the test procedure, the authors divided the concept of classroom management into three main aspects: \emph{Monitoring}, \emph{managing momentum} (structuring) and \emph{rules and routines} (Gold \& Holodynski, 2015, p.
+230f).
+
+\emph{Monitoring} includes proactive strategies such as omnipresence.
+This means, the teacher is always informed about the students' behavior, regulates it and reports it back to them.
+The second strategy is overlapping.
+In this case, the teacher is able to control several teaching processes at the same time.
+Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions (cf.~ibid.; {[}Kounin (2006), p.~89ff).
+
+By \emph{managing momentum} (structuring), Gold and Holodynski (2015) understand the skillful control of teaching processes so that they can run smoothly and without delays, taking into account the students' level of understanding and attention (Kounin, 2006, p.
+101ff).
+They also include the group focus specifically identified by Kounin (Kounin, 2006, p.
+117ff), i.e.~mobilizing the whole class and demanding accountability (Gold \& Holodynski, 2015, p.
+231).
+
+The third facet of classroom management, establishing \emph{rules, routines and rituals}, supports the other two facets and offers pupils orientation and structure in everyday school life (cf.~ibid.).
+
+In the questionnaire, subjects were asked to evaluate the effectiveness of each strategy on a 6-point rating scale from 1 (A) to 6 (F) according to school grades (see example scenario).
+
+Prior to this, the effectiveness of the strategies proposed in the answers was determined by expert judgement.
+Based on these, an overall rating was created, which is used for the evaluation of the answer keys.
+All three mentioned knowledge facets of class management (monitoring, managing momentum and rules and routines) were recorded separately with separate tasks in this SJT by Gold and Holodynski.
+The original 14 individual scenarios can each be assigned to one facet: Scenarios 1-5 cover the area of ubiquity, scenarios 6-10 the area of structuring and scenarios 11-14 the area of rules and routines.
+Scenarios 10 and 12 were removed from the test due to insufficient agreement between the expert judgement.
+In the evaluation, in addition to an overall assessment, all three knowledge areas can be presented and compared individually.
+
+The SJT is a standardized test in which the instructions are explicitly specified.
+When creating the test, the 14 constructed scenarios with 5-7 response options were first subjected to an expert survey to examine the content validity (Gold \& Holodynski, 2015, p.
+235f).
+With the exception of scenario 5, which was subsequently excluded, the 17 experts certified an appropriate level of content validity for all other scenarios (cf.~ibid.).
+For the validation of the strategies, pair comparisons were made between different strategies and the frequencies were calculated in relation to the expert responses (cf.~ibid., p.~238).
+Scenarios 10 and 12 were excluded from further analysis because they did not reach the minimum level of agreement (cf.~ibid.).
+The construct validity of the SJT with the remaining 11 scenarios and the sensitivity to differences in subject knowledge was then examined in a pilot study with 98 trainee teachers and their results validated in a cross-validation with a larger sample (cf.~ibid., p.~238ff).
+Despite limitations in reliability, the test was confirmed to have content and construct validity (cf.~ibid., p.~243).
+On the basis of these results, a sufficient reliability and validity of the SJT test procedure is assumed.
+Objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study \emph{ProVisioNET}.
+The objectivity of analysis was given by processing the obtained questionnaire data in the statistical program SPSS.
 
@@
 
-Finally, the test persons answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)) in the form of a questionnaire.
+Finally, the subjects answered a Situational Judgement Test (SJT, (Gold \& Holodynski, 2015)) in the form of a questionnaire.
 Here they had to assess teaching scenarios and evaluate their behavior in response to them.
 The SJT was used to assess strategic knowledge about classroom management.
+The
+completion of the entire survey took 15 min on average.
 
@@
 
-All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E.
+All reported data analyses were conducted with the R (Version 4.1.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.45; Andri et mult.
+al., 2022), \emph{dplyr} (Version 1.0.8; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggmosaic} (Version 0.3.3; Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggrepel} (Version 0.9.1; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.4.3; Wickham \& Miller, 2021), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{knitr} (Version 1.38; Xie, 2015), \emph{lme4} (Version 1.1.29; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.4.0; Bates \& Maechler, 2021), \emph{moments} (Version 0.14; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.2; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2019), \emph{rgeos} (Version 0.5.9; Bivand \& Rundel, 2021), \emph{rlang} (Version 1.0.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (Version 0.1.0; South, 2017a, 2017b), \emph{rnaturalearthdata} (Version 0.1.0; South, 2017b), \emph{sf} (Version 1.0.7; E.
 Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.10; Lüdecke, 2021), \emph{sp} (Version 1.4.7; E.
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-R-DescTools}{}}%
+Andri et mult. al., S. (2022). \emph{{DescTools}: Tools for descriptive statistics}. Retrieved from \url{https://cran.r-project.org/package=DescTools}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-ggthemes}{}}%

### 2022-06-14 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et aoi.R
plotssss

@@ -322,7 +322,8 @@ totaldur_group_plot <-
   ggplot(data = df_aoi_dur,
          mapping = aes(x = Group,
                        y = Seconds)) +
-  geom_boxplot(mapping = aes(fill = Group)) +
+  geom_boxplot(mapping = aes(fill = Group),
+               outlier.shape = NA) +
   geom_point(size = 2,
              alpha = 0.1,
              position = position_jitter(seed = 1,
@@ -478,13 +479,13 @@ df_aoi <-
                                        )
          )
 
-# NUMBER OF FIXATIONS iN all AOIs 
+# NUMBER OF FIXATIONS on all AOIs 
 # t-test for expertise differences
 t.test(x = df_aoi$Sum_number_of_fixations[df_aoi$Group == "Expert"],
        y = df_aoi$Sum_number_of_fixations[df_aoi$Group == "Novice"])
 
 
-# NUMBER OF FIXATIONS iN all AOIs
+# NUMBER OF FIXATIONS on all AOIs
 # effect size for expertise differences
 d_num_all <- CohenD(x = df_aoi$Sum_number_of_fixations[df_aoi$Group == "Expert"],
                     y = df_aoi$Sum_number_of_fixations[df_aoi$Group == "Novice"],
@@ -587,7 +588,8 @@ number_group_plot <-
   ggplot(data = df_aoi_number,
          mapping = aes(x = Group,
                        y = Count)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
+  geom_boxplot(mapping = aes(fill = Group), 
+               outlier.shape = NA) +
   geom_point(size = 1,
              alpha = 0.1,
              position = position_jitter(seed = 1,

### 2022-06-14 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R

@@ -64,7 +64,8 @@ dist_group_plot <-
   ggplot(data = sri_disrup,
          mapping = aes(x = Group,
                        y = `Disruption Factor`)) +
-  geom_boxplot(mapping = aes(fill = Group)) +
+  geom_boxplot(mapping = aes(fill = Group),
+               outlier.shape = NA) +
   geom_point(size = 1,
              alpha = 0.4,
              position = position_jitter(seed = 1,
@@ -202,7 +203,8 @@ confi_group_plot <-
   ggplot(data = sri_confi,
          mapping = aes(x = Group,
                        y = `Confident Factor`)) +
-  geom_boxplot(mapping = aes(fill = Group)) +
+  geom_boxplot(mapping = aes(fill = Group), 
+               outlier.shape = NA) +
   labs(x = "", 
        y = "Confident Factor") +
   scale_x_discrete(limits = c("Novice", "Expert")) +
@@ -254,7 +256,8 @@ sri_confi_sum <-
   ggplot(data = sri_confi,
          mapping = aes(x = Group,
                        y = `Confident Factor`)) +
-  geom_boxplot(mapping = aes(fill = Group)) +
+  geom_boxplot(mapping = aes(fill = Group), 
+               outliner.shape = NA) +
   geom_point(size = 1, 
              alpha = 0.4,
              position = position_jitter(seed = 1, 

### 2022-06-14 01_studies/01_Laborstudie ProVisioNET/SJTest/SJTest.R

@@ -40,10 +40,10 @@ mean_plot <-
   ggplot(data = df_sjt_long,
          mapping = aes(x = Group,
                        y = Mean)) +
-  geom_boxplot(mapping = aes(fill = Group)) +
-  # scale_linetype_manual(values = c("Expert", "Novice"),
-  #                       labels = c("Expert", "Novice"),
-  #                       guide = guide_legend(reverse = TRUE)) +
+  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
+  scale_linetype_manual(values = c("Expert", "Novice"),
+                        labels = c("Novice", "Expert"),
+                        guide = guide_legend(reverse = TRUE)) +
   geom_point(size = 1, 
              alpha = 0.4,
              position = position_jitter(seed = 1, 

### 2022-06-14 01_studies/01_Laborstudie ProVisioNET/SJTest/SJTest_script.R
plot update

@@ -37,22 +37,26 @@ df_sjt_long$Group = ifelse(df_sjt_long$Group < 200, "Novice","Expert")
 
 # plotting mean of all aspects 
 mean_plot <- 
-  ggplot(data = df_sjt_long,
-         mapping = aes(x = Group,
+df_sjt_long %>% 
+  mutate(Group = factor(Group,
+                        levels = c("Novice","Expert")
+                        )
+         ) %>% 
+  ggplot(mapping = aes(x = Group,
                        y = Mean)) +
   geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-  scale_linetype_manual(values = c("Expert", "Novice"),
-                        labels = c("Novice", "Expert"),
-                        guide = guide_legend(reverse = TRUE)) +
+  # scale_linetype_manual(values = c("Expert", "Novice"),
+  #                       labels = c("Novice", "Expert"),
+  #                       guide = guide_legend(reverse = TRUE)) +
   geom_point(size = 1, 
              alpha = 0.4,
              position = position_jitter(seed = 1, 
                                         width = 0.1,
                                         height = 0.1)) +
-  scale_x_discrete(limits = c("Novice", "Expert")) +
   labs(x = "") +
   ylim(0,1) + 
-  scale_fill_manual(values=c("steelblue","firebrick")) +  
+  scale_fill_manual(values=c("firebrick","steelblue")) +  
+ # scale_x_discrete(limits = c("Novice", "Expert")) +
   facet_wrap(vars(`Facets Classroom Management`), 
              nrow = 1, strip.position = "bottom") +
   theme_classic()+
@@ -73,7 +77,7 @@ mean_plot <-
   #          y = 0.25,
   #          label = paste ("d = ", round(d_sjt_all),3))
 
-mean_plot
+#mean_plot
 
 ggsave(plot = mean_plot,
        filename = "plots/sjt_plot.png",

### 2022-06-14 01_studies/01_Laborstudie ProVisioNET/SJTest/SJTest_script.R
plotssss

@@ -39,15 +39,14 @@ df_sjt_long$Group = ifelse(df_sjt_long$Group < 200, "Novice","Expert")
 mean_plot <- 
 df_sjt_long %>% 
   mutate(Group = factor(Group,
-                        levels = c("Novice","Expert")
+                        levels = c("Novice", 
+                                   "Expert")
                         )
          ) %>% 
   ggplot(mapping = aes(x = Group,
                        y = Mean)) +
-  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
-  # scale_linetype_manual(values = c("Expert", "Novice"),
-  #                       labels = c("Novice", "Expert"),
-  #                       guide = guide_legend(reverse = TRUE)) +
+  geom_boxplot(mapping = aes(fill = Group), 
+               outlier.shape = NA) +
   geom_point(size = 1, 
              alpha = 0.4,
              position = position_jitter(seed = 1, 
@@ -56,7 +55,6 @@ df_sjt_long %>%
   labs(x = "") +
   ylim(0,1) + 
   scale_fill_manual(values=c("firebrick","steelblue")) +  
- # scale_x_discrete(limits = c("Novice", "Expert")) +
   facet_wrap(vars(`Facets Classroom Management`), 
              nrow = 1, strip.position = "bottom") +
   theme_classic()+
@@ -64,8 +62,8 @@ df_sjt_long %>%
   theme(
     plot.title = element_text(size = 18, 
                               face = "bold"),
-    legend.title = element_text(size = 17),
-    legend.text = element_text(size = 15),
+    legend.title = element_text(size = 20),
+    legend.text = element_text(size = 18),
     axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
     strip.text.x = element_text(size = 14),
@@ -77,7 +75,7 @@ df_sjt_long %>%
   #          y = 0.25,
   #          label = paste ("d = ", round(d_sjt_all),3))
 
-#mean_plot
+mean_plot
 
 ggsave(plot = mean_plot,
        filename = "plots/sjt_plot.png",

### 2022-06-15 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et_aoi.Rmd
plots plots plots

---
title: "AOI - number and duration of fixations"
output: html_notebook
---

This is an [R Markdown](http://rmarkdown.rstudio.com) Notebook. When you execute code within the notebook, the results appear beneath the code.

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*.

# Load packages and read in data
```{r}
library(needs)
needs(tidyverse,
      psych,
      moments,
      sjPlot,
      DescTools,
      irr,
      readxl, 
      gridExtra,
      janitor,
      RColorBrewer,
      cowplot)

# suppress "summarize" info. 
# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

# return a character vector with names of .tsv data in data folder
file_names <- list.files(path = "data",
                         pattern = "interval_complete.tsv")

# read every object names in file_names and save it as a tibble
for (i in file_names) {

  work_data <- 
    read_tsv(file = paste0("data/", i),
             locale = locale(decimal_mark = ","))

  assign(value = work_data,
         x = str_remove(paste0("tib_", i),
                        pattern = ".tsv"
         )
  )

}

# Bind every tibble that contains "interval_complete" to a new tiblle
df_aoi <- 
  mget(ls(pattern = "interval_complete")) %>%
  bind_rows()

# Remove temporary data for a cleaner workspace
rm(list = ls(pattern = "^tib_ProVisio"))
rm(work_data)
rm(file_names)
rm(i)

```

# Average duration of fixations on all AOIs

```{r}
##################### AVERAGE DURATION ON ALL AOIS ########################

# filter group & total duration & number fixation on all AOIs

df_aoi %>% 
  filter(TOI == "Entire Recording") %>% 
  select (Group,
          starts_with("Total_duration_of_fixations"),
          starts_with("Number_of_fixations"),
          !"Total_duration_of_fixations.Disruptive_Person",
          !"Number_of_fixations.Disruptive_Person") %>% 
  rowwise() %>% 
  transmute(Group = Group,
            Sum_duration_fixation = sum(c_across(starts_with("Total_duration")
                                                    ),
                                           na.rm = TRUE
                                           ),
            Sum_number_fixation = sum(c_across(starts_with("Number_of")
                                                  ),
                                         na.rm = TRUE
                                         )
            ) %>% 
  mutate(Average_duration = round(Sum_duration_fixation/Sum_number_fixation,
                                         digits = 0),
         Group = as_factor(Group)) -> df_aoi_sum

# mean & SD average duration 
# novices
mean_dur_nov <- 
  df_aoi_sum %>%
  filter(Group == "Novice") %>% 
  pull(Average_duration) %>% 
  mean() %>% 
  round(., digits = 0)

sd_dur_nov <- 
  df_aoi_sum %>%
  filter(Group == "Novice") %>% 
  pull(Average_duration) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_dur_exp <-
  df_aoi_sum %>%
  filter(Group == "Expert") %>% 
  pull(Average_duration) %>% 
  mean() %>% 
  round(., digits = 0)

sd_dur_exp <- 
  df_aoi_sum %>%
  filter(Group == "Expert") %>% 
  pull(Average_duration) %>% 
  sd() %>% 
  round(., digits = 0)

# plotting average duration on ALL AOIS
df_aoi_sum %>% 
  ggplot(mapping = aes(x = Group,
                       y = Average_duration)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  labs(x ="",
       y = "Milliseconds") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Average Duration of Fixations on all AOIs") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
        ) -> plot_average_duration_group

# saving plot average plot
ggsave(plot = plot_average_duration_group,
       filename = "plots/plot_average_duration_group.svg",
       height = 8,
       width = 14,
       units = "in")

# AVERAGE DURATION OF FIXATIONS on all AOIs 
# t-test for expertise differences
t.test(x = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Expert"],
       y = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Novice"])

# AVERAGE DURATION OF FIXATIONS on all AOIs
# effect size for expertise differences
d_aver_all <- CohenD(x = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Expert"],
                    y = df_aoi_sum$Average_duration[df_aoi_sum$Group == "Novice"],
                    na.rm = TRUE)

```

# Average duration of fixations on AOI "Disruptive Person"

```{r}
##################### AVERAGE DURATION ON AOI DISRUPTIVE PERSON ########################

# filter group & total duration & number fixation on AOI Disruptive person

df_aoi %>% 
  filter(TOI == "Entire Recording") %>% 
  select (Group,
          "Total_duration_of_fixations.Disruptive_Person",
          "Number_of_fixations.Disruptive_Person") %>% 
  rowwise() %>% 
  mutate(Average_duration_disrup = round(Total_duration_of_fixations.Disruptive_Person/Number_of_fixations.Disruptive_Person, 
                                  digits = 0),
         Group = as_factor(Group)) -> df_aoi_disrup

# mean & SD average duration AOI Disruptive person
# novices
mean_dur_disrup_nov <- 
  df_aoi_disrup %>%
  filter(Group == "Novice") %>% 
  pull(Average_duration_disrup) %>% 
  mean() %>% 
  round(., digits = 0)

sd_dur_disrup_nov <- 
  df_aoi_disrup %>%
  filter(Group == "Novice") %>% 
  pull(Average_duration_disrup) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_dur_disrup_exp <-
  df_aoi_disrup %>%
  filter(Group == "Expert") %>% 
  pull(Average_duration_disrup) %>% 
  mean() %>% 
  round(., digits = 0)

sd_dur_disrup_exp <- 
  df_aoi_disrup %>%
  filter(Group == "Expert") %>% 
  pull(Average_duration_disrup) %>% 
  sd() %>% 
  round(., digits = 0)

# plotting average duration on AOI Disruptive person
df_aoi_disrup %>% 
  ggplot(mapping = aes(x = Group,
                       y = Average_duration_disrup)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  labs(x ="",
       y = "Milliseconds") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Average Duration of Fixations\non AOI `Disruptive Person`") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
  ) -> plot_average_duration_disrup

# saving plot average plot
ggsave(plot = plot_average_duration_disrup,
       filename = "plots/plot_average_duration_disrup.svg",
       height = 8,
       width = 8,
       units = "in")

# AVERAGE DURATION OF FIXATIONS on AOI disruptive person 
# t-test for expertise differences
t.test(x = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Expert"],
       y = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"])

# AVERAGE DURATION OF FIXATIONS 
# effect size for expertise differences
d_aver_disrup <- CohenD(x = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Expert"],
                        y = df_aoi_disrup$Average_duration_disrup[df_aoi_disrup$Group == "Novice"],
                        na.rm = TRUE)

```

# Average duration of fixations on AOI "Students"

```{r}
##################### AVERAGE DURATION ON AOI STUDENTS ########################

# filter group & total duration & number fixation on AOI Students
df_aoi %>% 
  filter(TOI == "Entire Recording") %>% 
  select (Group,
          "Total_duration_of_fixations.Anna",
          "Total_duration_of_fixations.Bianca",
          "Total_duration_of_fixations.Carl(a)",
          "Number_of_fixations.Anna",
          "Number_of_fixations.Bianca",
          "Number_of_fixations.Carl(a)") %>% 
  rowwise() %>% 
  transmute(Group = Group,
            Stud_duration_fixation = sum(c_across(starts_with("Total_duration")
                                                 ),
                                         na.rm = TRUE
                                         ),
            Stud_number_fixation = sum(c_across(starts_with("Number_of")
                                                ),
                                       na.rm = TRUE
                                       )
            ) %>% 
  mutate(Average_duration_stud = round(Stud_duration_fixation/Stud_number_fixation, 
                                  digits = 0),
         Group = as_factor(Group)) -> df_aoi_stud

# mean & SD average duration on AOI Students
# novices
mean_dur_stud_nov <- 
  df_aoi_stud %>%
  filter(Group == "Novice") %>% 
  pull(Average_duration_stud) %>% 
  mean() %>% 
  round(., digits = 0)

sd_dur_stud_nov <- 
  df_aoi_stud %>%
  filter(Group == "Novice") %>% 
  pull(Average_duration_stud) %>% 
  sd() %>% 
  round(., digits = 0)

# experts
mean_dur_stud_exp <-
  df_aoi_stud %>%
  filter(Group == "Expert") %>% 
  pull(Average_duration_stud) %>% 
  mean() %>% 
  round(., digits = 0)

sd_dur_stud_exp <- 
  df_aoi_stud %>%
  filter(Group == "Expert") %>% 
  pull(Average_duration_stud) %>% 
  sd() %>% 
  round(., digits = 0)

# plotting average duration on AOI Students
df_aoi_stud %>% 
  ggplot(mapping = aes(x = Group,
                       y = Average_duration_stud)) +
  geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
  #                                  )
  #                  ) +
  labs(x ="",
       y = "Milliseconds") + 
  scale_fill_brewer(palette  = "RdBu") +  
  ggtitle("Average Duration of Fixations\non AOI `Students`") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.text.x = element_text(size = 34),
        axis.text.y = element_text(size = 18),
        axis.title = element_text(size = 34),
        plot.title = element_text(size = 35, 
                                  face = "bold")
  ) -> plot_average_duration_stud

# saving plot average plot
ggsave(plot = plot_average_duration_stud,
       filename = "plots/plot_average_duration_stud.svg",
       height = 8,
       width = 8,
       units = "in")

# AVERAGE DURATION OF FIXATIONS on AOI Students 
# t-test for expertise differences
t.test(x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
       y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"])

# AVERAGE DURATION OF FIXATIONS on AOI Students
# effect size for expertise differences
d_aver_stud <- CohenD(x = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Expert"],
                      y = df_aoi_stud$Average_duration_stud[df_aoi_stud$Group == "Novice"],
                      na.rm = TRUE)

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

### 2022-06-15 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et aoi_old.R

@@ -8,7 +8,8 @@ needs(tidyverse,
       irr,
       readxl, 
       gridExtra,
-      janitor)
+      janitor,
+      RColorBrewer)
 
 # suppress "summarize" info. 
 # if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
@@ -43,6 +44,55 @@ rm(list = ls(pattern = "^tib_ProVisio"))
 rm(work_data)
 rm(file_names)
 rm(i)
+
+# filter group & total duration & number fixation
+df_aoi %>% 
+  filter(TOI == "Entire Recording") %>% 
+  select (Group,
+          starts_with("Total_duration_of_fixations"),
+          starts_with("Number_of_fixations"),
+          !"Total_duration_of_fixations.Disruptive_Person",
+          !"Number_of_fixations.Disruptive_Person") %>% 
+  rowwise() %>% 
+  transmute(Group = Group,
+            Sum_duration_fixation = sum(c_across(starts_with("Total_duration")
+                                                 ),
+                                  na.rm = TRUE
+                                  ),
+         Sum_number_fixation = sum(c_across(starts_with("Number_of")
+                                            ),
+                                   na.rm = TRUE
+                                   )) %>% 
+  mutate(Average_duration = Sum_duration_fixation/Sum_number_fixation,
+         Group = as_factor(Group)) -> df_aoi_sum
+df_aoi_sum %>% 
+  ggplot(mapping = aes(x = Group,
+                       y = Average_duration)) +
+  geom_boxplot(mapping = aes(fill = Group),
+               outlier.shape = NA) +
+  geom_point(size = 2,
+             alpha = 0.1,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  # scale_x_discrete(labels = paste0(c("Expert\n","Novice\n"),
+  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
+  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
+  #                                  )
+  #                  ) +
+  labs(x ="",
[…]

### 2022-06-15 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/old_versions/et aoi_old.R

@@ -1,0 +1,1108 @@
+### ProVisioNET Eyetracking AOI Coding Data 
+library(needs)
+needs(tidyverse,
+      psych,
+      moments,
+      sjPlot,
+      DescTools,
+      irr,
+      readxl, 
+      gridExtra,
+      janitor,
+      RColorBrewer)
+
+# suppress "summarize" info. 
+# if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
+options(dplyr.summarise.inform = FALSE)
+
+# return a character vector with names of .tsv data in data folder
+file_names <- list.files(path = "data",
+                         pattern = "interval_complete.tsv")
+
+# read every object names in file_names and save it as a tibble
+for (i in file_names) {
+  
+  work_data <- 
+    read_tsv(file = paste0("data/", i),
+             locale = locale(decimal_mark = ","))
+  
+  assign(value = work_data,
+         x = str_remove(paste0("tib_", i),
+                        pattern = ".tsv"
+         )
+  )
+  
+}
+
+# Bind every tibble that contains "interval_complete" to a new tiblle
+df_aoi <- 
+  mget(ls(pattern = "interval_complete")) %>%
+  bind_rows()
+
+# Remove temporary data for a cleaner workspace
+rm(list = ls(pattern = "^tib_ProVisio"))
+rm(work_data)
+rm(file_names)
+rm(i)
+
+# filter group & total duration & number fixation
+df_aoi %>% 
+  filter(TOI == "Entire Recording") %>% 
+  select (Group,
+          starts_with("Total_duration_of_fixations"),
+          starts_with("Number_of_fixations"),
+          !"Total_duration_of_fixations.Disruptive_Person",
+          !"Number_of_fixations.Disruptive_Person") %>% 
+  rowwise() %>% 
+  transmute(Group = Group,
+            Sum_duration_fixation = sum(c_across(starts_with("Total_duration")
+                                                 ),
+                                  na.rm = TRUE
+                                  ),
+         Sum_number_fixation = sum(c_across(starts_with("Number_of")
+                                            ),
+                                   na.rm = TRUE
+                                   )) %>% 
+  mutate(Average_duration = Sum_duration_fixation/Sum_number_fixation,
+         Group = as_factor(Group)) -> df_aoi_sum
+df_aoi_sum %>% 
+  ggplot(mapping = aes(x = Group,
[…]

### 2022-06-15 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R

@@ -8,7 +8,8 @@ needs(tidyverse,
       DescTools,
       irr,
       readxl, 
-      gridExtra)
+      gridExtra,
+      cowplot)
 
 # suppress "summarize" info. 
 # if this line is ommitted, each table using the summarize function will be accompanied with a warning from the console
@@ -19,23 +20,22 @@ sri <-
   excel_sheets("data/Coding_SRI.xlsx") %>% 
   map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% 
   select(Group, Event, `Disruption Factor`, `Confident Factor`) %>% # select relevant columns 
-  filter(Group %in% c(101:122, 201:212))# filter relevant rows
+  filter(Group %in% c(101:122, 202:212))# filter relevant rows
 
  
-# counting drop outs (-99 not perceived, -100 not answered)
-# all dropout
-sri$dropout <- 
-  length(which(sri$`Disruption Factor`== -99 |
-               sri$`Disruption Factor`== -100 |
-                sri$`Confident Factor` == -100)) %>% 
-  as.numeric(sri$dropout)
-
-# not perceived
-sri$not_perceived <-
-  length(which(sri$`Disruption Factor`== -99)) %>% 
-  as.numeric(sri$not_perceived)
-
-
+# # counting drop outs (-99 not perceived, -100 not answered)
+# # all dropout
+# sri$dropout <- 
+#   length(which(sri$`Disruption Factor`== -99 |
+#                sri$`Disruption Factor`== -100 |
+#                 sri$`Confident Factor` == -100)) %>% 
+#   as.numeric(sri$dropout)
+# 
+# # not perceived
+# sri$not_perceived <-
+#   length(which(sri$`Disruption Factor`== -99)) %>% 
+#   as.numeric(sri$not_perceived)
+# 
 # # count all events and calculate percentage of dropouts
 # sri$sum_events <-
 #   length(summary(as.factor(sri$Group))) %>% 
@@ -47,8 +47,9 @@ sri$not_perceived <-
 sri <- 
   sri %>% 
   filter(!`Disruption Factor` == -100,
-           !`Confident Factor` == -100,
-           !`Disruption Factor`== -99)
+         !`Confident Factor` == -100,
+         !`Disruption Factor`== -99,
+         !`Confident Factor` == -99)
   
          
 # define expert and novice with ifelse function
@@ -75,22 +76,22 @@ dist_group_plot <-
[…]

### 2022-06-15 01_studies/01_Laborstudie ProVisioNET/SJTest/SJTest_script.R

@@ -54,21 +54,21 @@ df_sjt_long %>%
                                         height = 0.1)) +
   labs(x = "") +
   ylim(0,1) + 
-  scale_fill_manual(values=c("firebrick","steelblue")) +  
+  scale_fill_brewer(palette  = "RdBu") +  
   facet_wrap(vars(`Facets Classroom Management`), 
              nrow = 1, strip.position = "bottom") +
-  theme_classic()+
-  ggtitle("Situational Judgment Test of Strategic Knowledge of Classroom Management") +
+  theme_cowplot()+
+  ggtitle("SJT") +
   theme(
-    plot.title = element_text(size = 18, 
+    plot.title = element_text(size = 34, 
                               face = "bold"),
-    legend.title = element_text(size = 20),
-    legend.text = element_text(size = 18),
+    legend.title = element_text(size = 27),
+    legend.text = element_text(size = 25),
     axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
-    strip.text.x = element_text(size = 14),
-    axis.title.y = element_text(size = 14),
-    axis.title.x = element_text(size = 25)
+    strip.text.x = element_text(size = 22),
+    axis.title.y = element_text(size = 27),
+    axis.title.x = element_text(size = 27)
         )
   # + annotate(geom = "text",
   #          x = "All",
@@ -78,9 +78,9 @@ df_sjt_long %>%
 mean_plot
 
 ggsave(plot = mean_plot,
-       filename = "plots/sjt_plot.png",
-       height = 8,
-       width = 14,
+       filename = "plots/sjt_plot.svg",
+       height = 9,
+       width = 16,
        units = "in")
 
 #################### MEAN, SD, N ############

### 2022-06-15 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et_aoi.Rmd
und noch mehr plots

@@
 ---
-
-This is an [R Markdown](http://rmarkdown.rstudio.com) Notebook. When you execute code within the notebook, the results appear beneath the code.
-
-Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*.
 
@@
 
-# Average duration of fixations on all AOIs
+# Number of fixation on all AOI
 
 ```{r}
-##################### AVERAGE DURATION ON ALL AOIS ########################
+##################### NUMBER OF FIXATION ON ALL AOIS ########################
 
@@
 df_aoi %>% 
-  filter(TOI == "Entire Recording") %>% 
+  filter(TOI == "Lesson") %>% 
   select (Group,
@@
          Group = as_factor(Group)) -> df_aoi_sum
+
+# mean & SD number fixation 
+# novices
+mean_number_nov <- 
+  df_aoi_sum %>%
+  filter(Group == "Novice") %>% 
+  pull(Sum_number_fixation) %>% 
+  mean() %>% 
+  round(., digits = 0)
+
+sd_number_nov <- 
+  df_aoi_sum %>%
+  filter(Group == "Novice") %>% 
+  pull(Sum_number_fixation) %>% 
+  sd() %>% 
+  round(., digits = 0)
+
+# experts
+mean_number_exp <-
+  df_aoi_sum %>%
+  filter(Group == "Expert") %>% 
+  pull(Sum_number_fixation) %>% 
+  mean() %>% 
+  round(., digits = 0)
+
+sd_number_exp <- 
+  df_aoi_sum %>%
+  filter(Group == "Expert") %>% 
+  pull(Sum_number_fixation) %>% 
+  sd() %>% 
+  round(., digits = 0)
+
+# plotting number of fixations on ALL AOIS
+df_aoi_sum %>% 
+  ggplot(mapping = aes(x = Group,
+                       y = Sum_number_fixation)) +
+  geom_boxplot(mapping = aes(fill = Group),
+               outlier.shape = NA) +
+  geom_point(size = 2,
+             alpha = 0.7,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
+  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
+  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
+  #                                  )
+  #                  ) +
+  labs(x ="",
+       y = "Number") + 
+  scale_fill_brewer(palette  = "RdBu") +  
+  ggtitle("Number of Fixations on all AOIs") +
+  theme_cowplot() +
+  theme(legend.position="none",
+        axis.text.x = element_text(size = 34),
+        axis.text.y = element_text(size = 18),
+        axis.title = element_text(size = 34),
+        plot.title = element_text(size = 35, 
+                                  face = "bold")
+        ) -> plot_number_group
+
+# saving plot number plot
+ggsave(plot = plot_number_group,
+       filename = "plots/plot_number_group.svg",
+       height = 8,
+       width = 14,
+       units = "in")
+
+# NUMBER OF FIXATIONS on all AOIs 
+# t-test for expertise differences
+t.test(x = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Expert"],
+       y = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Novice"])
+
+# NUMBER OF FIXATIONS on all AOIs
+# effect size for expertise differences
+d_number_all <- CohenD(x = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Expert"],
+                       y = df_aoi_sum$Sum_number_fixation[df_aoi_sum$Group == "Novice"],
+                       na.rm = TRUE)
+
+```
+
+# Number of fixations on AOI "Disruptive person"
+
+```{r}
+##################### NUMBER OF FIXATION ON AOI DISRUPTIVE PERSON ########################
+
+# filter group & total duration & number fixation on AOI Disruptive person
+
+df_aoi %>% 
+  filter(TOI == "Lesson") %>% 
+  select (Group,
+          "Number_of_fixations.Disruptive_Person") %>%
+  mutate(Group = as_factor(Group)) -> df_aoi_disrup
+
+# mean & SD average duration AOI Disruptive person
+# novices
+mean_number_disrup_nov <- 
+  df_aoi_disrup %>%
+  filter(Group == "Novice") %>% 
+  pull(Number_of_fixations.Disruptive_Person) %>% 
+  mean() %>% 
+  round(., digits = 0)
+
+sd_number_disrup_nov <- 
+  df_aoi_disrup %>%
+  filter(Group == "Novice") %>% 
+  pull(Number_of_fixations.Disruptive_Person) %>% 
+  sd() %>% 
+  round(., digits = 0)
+
+# experts
+mean_number_disrup_exp <-
+  df_aoi_disrup %>%
+  filter(Group == "Expert") %>% 
+  pull(Number_of_fixations.Disruptive_Person) %>% 
+  mean() %>% 
+  round(., digits = 0)
+
+sd_number_disrup_exp <- 
+  df_aoi_disrup %>%
+  filter(Group == "Expert") %>% 
+  pull(Number_of_fixations.Disruptive_Person) %>% 
+  sd() %>% 
+  round(., digits = 0)
+
+# plotting average duration on AOI Disruptive person
+df_aoi_disrup %>% 
+  ggplot(mapping = aes(x = Group,
+                       y = Number_of_fixations.Disruptive_Person)) +
+  geom_boxplot(mapping = aes(fill = Group),
+               outlier.shape = NA) +
+  geom_point(size = 2,
+             alpha = 0.7,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
+  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
+  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
+  #                                  )
+  #                  ) +
+  labs(x ="",
+       y = "Number") + 
+  scale_fill_brewer(palette  = "RdBu") +  
+  ggtitle("Number of Fixations\non AOI `Disruptive Person`") +
+  theme_cowplot() +
+  theme(legend.position="none",
+        axis.text.x = element_text(size = 34),
+        axis.text.y = element_text(size = 18),
+        axis.title = element_text(size = 34),
+        plot.title = element_text(size = 35, 
+                                  face = "bold")
+  ) -> plot_number_disrup
+
+# saving plot average plot
+ggsave(plot = plot_number_disrup,
+       filename = "plots/plot_number_disrup.svg",
+       height = 8,
+       width = 8,
+       units = "in")
+
+# AVERAGE DURATION OF FIXATIONS on AOI disruptive person 
+# t-test for expertise differences
+t.test(x = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Expert"],
+       y = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Novice"])
+
+# AVERAGE DURATION OF FIXATIONS 
+# effect size for expertise differences
+d_number_disrup <- CohenD(x = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Expert"],
+                        y = df_aoi_disrup$Number_of_fixations.Disruptive_Person[df_aoi_disrup$Group == "Novice"],
+                        na.rm = TRUE)
+
+```
+
+# Number of fixations on AOI "Students"
+
+```{r}
+##################### NUMBER OF FIXATIONS ON AOI STUDENTS ########################
+
+# mean & SD average duration on AOI Students
+# novices
+mean_number_stud_nov <- 
+  df_aoi_stud %>%
+  filter(Group == "Novice" ) %>% 
+  pull(Stud_number_fixation) %>% 
+  mean() %>% 
+  round(., digits = 0)
+
+sd_number_stud_nov <- 
+  df_aoi_stud %>%
+  filter(Group == "Novice") %>% 
+  pull(Stud_number_fixation) %>% 
+  sd() %>% 
+  round(., digits = 0)
+
+# experts
+mean_number_stud_exp <-
+  df_aoi_stud %>%
+  filter(Group == "Expert") %>% 
+  pull(Stud_number_fixation) %>% 
+  mean() %>% 
+  round(., digits = 0)
+
+sd_number_stud_exp <- 
+  df_aoi_stud %>%
+  filter(Group == "Expert") %>% 
+  pull(Stud_number_fixation) %>% 
+  sd() %>% 
+  round(., digits = 0)
+
+# plotting average duration on AOI Students
+df_aoi_stud %>% 
+  ggplot(mapping = aes(x = Group,
+                       y = Stud_number_fixation)) +
+  geom_boxplot(mapping = aes(fill = Group),
+               outlier.shape = NA) +
+  geom_point(size = 2,
+             alpha = 0.7,
+             position = position_jitter(seed = 1,
+                                        width = 0.1,
+                                        height = 0.1)) +
+  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
+  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
+  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
+  #                                  )
+  #                  ) +
+  labs(x ="",
+       y = "Number") + 
+  scale_fill_brewer(palette  = "RdBu") +  
+  ggtitle("Number of Fixations\non AOI `Students`") +
+  theme_cowplot() +
+  theme(legend.position="none",
+        axis.text.x = element_text(size = 34),
+        axis.text.y = element_text(size = 18),
+        axis.title = element_text(size = 34),
+        plot.title = element_text(size = 35, 
+                                  face = "bold")
+  ) -> plot_number_stud
+
+# saving plot average plot
+ggsave(plot = plot_number_stud,
+       filename = "plots/plot_number_stud.svg",
+       height = 8,
+       width = 8,
+       units = "in")
+
+# AVERAGE DURATION OF FIXATIONS on AOI Students 
+# t-test for expertise differences
+t.test(x = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Expert"],
+       y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"])
+
+# AVERAGE DURATION OF FIXATIONS on AOI Students
+# effect size for expertise differences
+d_number_stud <- CohenD(x = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Expert"],
+                      y = df_aoi_stud$Stud_number_fixation[df_aoi_stud$Group == "Novice"],
+                      na.rm = TRUE)
+
+```
+
+# Average duration of fixations on all AOIs
+
+```{r}
+##################### AVERAGE DURATION ON ALL AOIS ########################
+
+# filter group & total duration & number fixation on all AOIs
 

### 2022-06-16 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et_aoi.Rmd
noch mehr plots

@@
 ##################### NUMBER OF FIXATIONS ON AOI STUDENTS ########################
+# filter group & total duration & number fixation on AOI Students
+df_aoi %>% 
+  filter(TOI == "Lesson") %>% 
+  select (Group,
+          "Total_duration_of_fixations.Anna",
+          "Total_duration_of_fixations.Bianca",
+          "Total_duration_of_fixations.Carl(a)",
+          "Number_of_fixations.Anna",
+          "Number_of_fixations.Bianca",
+          "Number_of_fixations.Carl(a)") %>% 
+  rowwise() %>% 
+  transmute(Group = Group,
+            Stud_duration_fixation = sum(c_across(starts_with("Total_duration")
+                                                 ),
+                                         na.rm = TRUE
+                                         ),
+            Stud_number_fixation = sum(c_across(starts_with("Number_of")
+                                                ),
+                                       na.rm = TRUE
+                                       )
+            ) %>% 
+  mutate(Average_duration_stud = round(Stud_duration_fixation/Stud_number_fixation, 
+                                  digits = 0),
+         Group = as_factor(Group)) -> df_aoi_stud
 
@@
 
+df_aoi %>% 
+  filter(TOI == "Lesson") %>% 
+  select (Group,
+          starts_with("Total_duration_of_fixations"),
+          starts_with("Number_of_fixations"),
+          !"Total_duration_of_fixations.Disruptive_Person",
+          !"Number_of_fixations.Disruptive_Person") %>% 
+  rowwise() %>% 
+  transmute(Group = Group,
+            Sum_duration_fixation = sum(c_across(starts_with("Total_duration")
+                                                    ),
+                                           na.rm = TRUE
+                                           ),
+            Sum_number_fixation = sum(c_across(starts_with("Number_of")
+                                                  ),
+                                         na.rm = TRUE
+                                         )
+            ) %>% 
+  mutate(Average_duration = round(Sum_duration_fixation/Sum_number_fixation,
+                                         digits = 0),
+         Group = as_factor(Group)) -> df_aoi_sum
 # mean & SD average duration 

### 2022-06-18 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
upload demo datat
noch mehr plottsssss

@@
 # prepare data (selected from questionnaire data)
-demo.data <- read_excel ("./data/data_empschul_labor_lehrperson.xlsx")
+demo.data <- readxl::read_xlsx("./data/data_empschul_labor_lehrperson.xlsx")
 
@@
 
-# changing gender female 2 = 0 
-demo.data$Gender = ifelse(demo.data$Gender == 2, "0","1")
+# changing gender female 2 = 1 
+demo.data$Gender = ifelse(demo.data$Gender == 2, "1","0")
 
@@
 demo.data$Gender <- as.numeric(demo.data$Gender)
+
+# #filter --> 121 two times
+# demo.data <-  demo.data[-c(28), ]
 
@@
   summarise(N=n(),
-            "Male" = sum(Gender),
+            "Female" = sum(Gender),
             "M Age" = round(mean(Age), 2),

### 2022-06-18 01_studies/01_Laborstudie ProVisioNET/R script/sri coding/sri coding.R

@@ -62,8 +62,14 @@ sri_confi <- subset.data.frame(sri, select = c(Group, Event, `Confident Factor`)
 
 # plotting Disruption factor for groups
 dist_group_plot <- 
-  ggplot(data = sri_disrup,
-         mapping = aes(x = Group,
+  sri_disrup %>% 
+  mutate(Group = factor(Group,
+                        levels = c("Novice", 
+                                   "Expert"
+                                   )
+                        )
+         ) %>% 
+  ggplot(mapping = aes(x = Group,
                        y = `Disruption Factor`)) +
   geom_boxplot(mapping = aes(fill = Group),
                outlier.shape = NA) +
@@ -73,9 +79,9 @@ dist_group_plot <-
                                         width = 0.1,
                                         height = 0.1)) +
   scale_x_discrete(limits = c("Novice", "Expert")) +
+  scale_y_continuous(breaks = seq(from = 0, to = 10, by = 1)) + 
   labs(x = "",
        y = "Disruption Factor") + 
-  ylim(0,10)+
   scale_fill_brewer(palette  = "RdBu") +  
   ggtitle("How disruptive was the event for you?") +
   theme_cowplot() + 
@@ -97,55 +103,55 @@ ggsave(plot = dist_group_plot,
        units = "in")
 
 
-# plotting Disruption factor for 3 disruptions sum up
-sri_disrup$Event[sri_disrup$Event == "chatting" |
-                   sri_disrup$Event == "heckling" |
-                   sri_disrup$Event == "whispering"] <- "Verbal disruption"
-
-sri_disrup$Event[sri_disrup$Event == "head on table" |
-                   sri_disrup$Event == "looking at phone" |
-                   sri_disrup$Event == "drawing"] <- "Lack of eagerness"
-
-sri_disrup$Event[sri_disrup$Event == "clicking pen" |
-                   sri_disrup$Event == "drumming" |
-                   sri_disrup$Event == "snipping"] <- "Agitation"
-
-
-
-
-# plotting
-sri_disrup_sum <-
-  ggplot(data = sri_disrup,
-         mapping = aes(x = Group,
-                       y = `Disruption Factor`)) +
-  geom_boxplot(mapping = aes(fill = Group)) +
-  geom_point(size = 1, 
-             alpha = 0.4,
-             position = position_jitter(seed = 1, 
-                                        width = 0.1,
-                                        height = 0.1)) +
[…]

### 2022-06-18 01_studies/01_Laborstudie ProVisioNET/SJTest/SJTest_script.R

@@ -14,8 +14,11 @@ needs(tidyverse,
 df_sjt <- read_csv2(file = "C:/Users/mk99feta/OneDrive/Dokumente/GitHub/Mandy-PhD/01_studies/01_Laborstudie ProVisioNET/SJTest/data/SJT.csv")
 
 # select relevant columns --> only subject ID and mean 
-df_sjt <- df_sjt %>% select(UI06_05, SJT_AL_gek, SJT_ST_gek, SJT_R_gek, SJT_KF_gek) %>% 
-  slice(1:34) # filter only relevant rows for analysis
+df_sjt <- df_sjt %>% select(UI06_05, SJT_AL_gek, SJT_ST_gek, SJT_R_gek, SJT_KF_gek) 
+# %>% slice(1:34) # filter only relevant rows for analysis
+
+# remove NAs
+df_sjt <- na.omit(df_sjt)
 
 
 # rename columns
@@ -25,8 +28,6 @@ df_sjt <- rename(df_sjt, c("Group" = "UI06_05",
                            "Rules and routines" = "SJT_R_gek",
                            "All" = "SJT_KF_gek"))
 
-# remove NAs
-df_sjt <- na.omit(df_sjt)
 
 # changing from wide to long format
 df_sjt_long <- df_sjt %>% 
@@ -85,7 +86,7 @@ ggsave(plot = mean_plot,
 
 #################### MEAN, SD, N ############
 
-# mean SJT ALL
+# mean & SD SJT ALL
 sjt_mean <- df_sjt_long %>%
   filter(`Facets Classroom Management` == "All") %>%
   group_by(Group) %>%

### 2022-06-20 01_studies/01_Laborstudie ProVisioNET/R script/et aoi/et_aoi.Rmd
script aoi kursiv

@@
                                         height = 0.1)) +
-  # scale_x_discrete(labels = paste0(c("Novice\n","Expert\n"),
-  #                                  "M = ", c(mean_dur_nov, mean_dur_exp),
-  #                                  "; SD = ", c(sd_dur_nov, sd_dur_exp)
+  # scale_x_discrete(labels = paste(
+  #   c("Novice\n", "Expert\n"),
+  #   glue("$M$ = "),
+  #   c(mean_number_nov, mean_number_exp),
+  #   glue("; $SD$ = "),
+  #   c(sd_number_nov, sd_number_exp)
+  # )) +
+
+  # scale_x_discrete(labels = c(
+  #   paste(
+  #     "Novice\n",
+  #     glue("<i>M</i>"),
+  #     " = ",
+  #     c(mean_number_nov, mean_number_exp)
+  #   ),
+  #   c(
+  #     "Expert\n",
+  #     ";",
+  #     glue("<i>SD</i>"),
+  #     " = ",
+  #     c(sd_number_nov, sd_number_exp)
   #   ) 
-  #                  ) +
+  # )) +
   labs(x ="",
@@
         ) -> plot_number_group
+plot_number_group
 

### 2022-06-29 02_paper/02_study/paper_methods.Rmd
method update

@@
 
-keywords          : "Professional Vision, Expert-Novice-Paradigm, mobile Eye-Tracking"
+keywords          : "professional vision, expertise, classroom management, mobile Eye-Tracking"
 wordcount         : "XXX"
@@
 Managing classroom disruptions is a crucial aspect of effective classroom management (@evertson2006classroom; @kounin2006techniken).
-
 Accordingly, teachers must be able to quickly notice and appropriately react to significant events in the classroom.
 This ability is referred to as classroom professional vision (@goodwin2015professional; @sherin2007development).
-
 The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (“noticing”) and applying knowledge to draw appropriate conclusions in these situations (“knowledge-based reasoning”; @seidel2014modeling).
-
 Therefore, the early visual perception of classroom disruptions is a key component to effectively maximize students’ learning time and minimize classroom interruptions.
 According to Kounin (2006), these important classroom management strategies are called “withitness” and “overlapping” and can be summarized under the concept of monitoring (@gold2017using).
-
 Learning to develop such classroom management skills is a demanding and complex task for student teachers (@wolff2016teacher).
@@
 
-## Professional competence
+## Professional competence in teaching profession
+
+Competence is a common term in everyday school life.
+In most cases, it refers to the acquisition of competencies by students and how to promote them and make them effective.
+In the same way, the term competence can be applied to teachers.
+Teachers have to be competent in things such as teaching, educating, evaluating or innovating.
+Therefore, competencies form an important and practical contribution in current educational research and teacher education (Klieme, Hartig & Rauch, 2008).
+They replace the rigid canon of knowledge that defined professional qualification for generations.
+In recent years, the concept of competence has experienced an upswing and is in the focus of educational research in particular (ibid.).
+To put it simply, the concept of competence in empirical research deals with the development of human resources and the productivity of education (cf.
+Klieme et al., 2008, p.
+4).
+In order to be able to make a meaningful conceptualization definition of competence, it is necessary to take a closer look at different of research have to be considered in more detail.
+
+In science, there is some agreement on the two opposing perspectives of competence versus empowerment.
+The former means a broad, concept, whereas empowerment refers to the different components of competence (cf.
+of competence (cf.
+Blömeke, Gustafsson & Shavelson, 2015, p.5).
+These can be of a cognitive, conative, affective, or motivational nature (ibid.).
+To determining professional qualification, competence is an irreplaceable tool.
+
+In contrast to intelligence, an instrument that is also used as a measure of quality, competence is learnable and can thus be improved through targeted practice (cf.
+Weinert 2001; cited in Blömeke et al.
+2015, p.
+5).
+This is one reason, among others, why this concept is so relevant for empirical school and development research.
+Another crucial step in clarifying the concept of competence is to understand that the framework of competence recognizes the importance of everyday life situations (Blömeke et al., 2015).
+Therefore scholars argue, a definition must start from an authentic "analysis of occupational or societal situations and must take into account the tasks and associated associated cognitive, conceptual, affective, and motivational aspects" (Blömeke et al., 2015, p.
+5).
+Through this comprehensive approach, many inconsistencies in the definition of the term can be resolved.
+The definition of competence is now no longer a question of whether it is a number of cognitive skills or a combination of cognition, conation, affect, or motivation.
+It combines "complex intellectual characteristics together with affect-motivation, which underlies observable underlying performances" (Blömeke et al.
+2015, p.
+6).
+This is best defined as a process or even continuum (see Figure 1), which consists of different levels and should be understood as a multidimensional construct with stronger and weaker Domains (ibid.).
+
+The term competence finds its place in a variety of disciplines as an assessment standard of qualifications.
+In this context, the term professional competence has become established in research, which defines competence in a specific professional field.
+Thus, based on the assumption that competence is more than mere knowledge, professional competence offers a way to make teacher success in schools tangible (Kunter et al., 2013).
+
+The term "professional competence" is the application of the concept to working life, particularly in highly complex and demanding professions, in which mastery of situations is especially dependent on the interplay of knowledge, skills, attitudes, and motivation." (cf.
+Epstein & Hundert, 2002; cited in Kunter et al.
+2013, p.
+807).
+Several studies could prove that this idea can be successfully transferred to the teaching profession (cf.
+Goodmann et al., 2008; Oster, Achtenhagen & Renold, 2006; Tannenbaum & Rosenfeld, 1994; cited in Kunter et al., 2013, p.
+807).
+Accordingly, a quality standard can be applied to assess the quality of a teacher.
+This quality is elementary in the school context because the teacher factor most influences student learning (Marzano, Marzano & Pickering, 2003).
+Thus, the effectiveness of education and the learning growth of individual students can be enhanced by the teacher.
+Research has shown that this component can even offset the influence of an ineffective school setting (Marzano et al., 2003).
+This effect places teachers at the center of ensuring effective teaching and learning and underscores the importance of professional competence in this career field.
 
 ## Classroom Management
-- Disruptions defintiion
 
-## Professional Vision
+Teachers and students are in the classroom in a place that is always alive, characteristic of its heterogeneity and the interests of different groups.
+These the circumstances of a classroom are also characterized as multidimensional, simultaneous, immediate, unpredictable, public, and shared (Doyle, 2011, p.
+99).
+All of these circumstances place a number of demands on teachers, which primarily involve planning and monitoring activities (ibid.).
+"Order in classrooms is not a consequence of reactions to misbehavior but a condition established and sustained by the way a teacher organizes and guides a complex system of classroom activities" (Doyle, 1989, p.12).
+Thus, "good" teachers create the conditions for effective teaching through pre-planned actions and activities that they are always in control of while teaching.
+This enables them to maximize work time while keeping disruptions of any kind to a minimum to facilitate learning for all participants (Doyle, 1989).
 
-## Expertise
+However, lessons, and specifically classroom disruptions, are unpredictable as well as multifaceted and require a high level of expertise and competence on the part of the teacher to handle.
+This trained handling, as described above, can be summarized under the aspect of professional competence.
+It is expressed, among other things, in knowledge about classroom management (Grub, Biermann & Brünken, 2020) and can be understood as a manifold toolbox of teachers to find their way in the challenging environment of the classroom.
 
-## Parameter/Indicators of professional vision
+Classroom management significantly influences the ability to perceive and subsequently respond to classroom events and thus organize for disruption-free instruction (Wolff, van den Bogert, Jarodzka & Boshuizen, 2015).
+Marzano et al.'s (2003) research created a foundational work in school and developmental research by manifesting that instructional strategy, curriculum design, and classroom management are significant roles in effective teaching.
+In this regard, research agrees that effective leadership and effective learning are closely related and classroom management can be considered a key component of teaching (Wolff et al., 2015).
+Therefore, it is often referred to as the central variable of successful teaching (Helmke & Helmke, 2015).
+Good classroom management is thus the prerequisite for learning to take place (Wolff et al., 2015).
+While the term suggests that it is mainly about rituals, rules, or measures that are meant to maintain order within the classroom, it is about much more than these two components.
 
-# Research Questions
+An initial explanatory approach to classroom management was provided by Doyle (1990, p.355) with his definition of teaching, which he described as a "cognitive activity based on knowledge of the probable course of events in the classroom and the ways in which actions affect situations." From this, it is clear that in order to teach successfully, a teacher needs knowledge of how to process as well as represent the full range of classroom events.
+In addition, it is necessary to be able to respond or interact proactively and effectively to potential events at best.
 
-This study examined how the degree of teaching experience influences (a) the number of fixations on relevant areas (e.g., the student performing the disruption), (b) the fixation duration in relevant areas and (c) the time to first fixation on relevant areas, using mobile eye-tracking data in a controlled, micro-teaching setting.
-Based on the existing literature, we expect expert teachers to outperform novices by (H1) showing more fixations on relevant areas with (H2) shorter fixation durations and (H3) perceiving classroom disruptions faster (cf.
-@van2014first).
+Ultimately, classroom management is composed of a set of multifaceted skills that include classroom structure and atmosphere, instructional decisions made by the teacher, and pedagogical as well as practical knowledge (cf.
+Wolff et al., 2015, p.
+71).
+These skills essentially determine teacher decisions, interactions, and exchanges in the course of instruction (ibid.).
+If these very skills are well-developed, they guarantee a smooth and trouble-free course of instruction.
+This is crucial to maximize students' active learning time (Helmke & Helmke, 2015).
+It, in turn, has been shown to correlate positively with achievement growth and learning interest in a class (Helmke, 2008), placing effective classroom management at the center of empirical research.
+In principle, these skills can be developed in the course of teaching education, as well as subsequent professional experience, which is why they constitute an essential component of teacher expertise (Wolff et al., 2015).
 
-# Methods
+## Parameters and indicators of teachers' professional vision
+
+In university education, there is an increasing focus on developing the professional vision of future teachers (Stürmer et al., 2017).
+In order to determine the professional vision of teachers by means of mobile eye-tracking (MET), different indicators are worth considering.
+This scientific work focuses primarily on processes of noticing, i.e., the identification of relevant teaching situations as well as perception time.
+Therefore, in the following we will focus more on the parameters and indicators necessary for these processes.
+
+In MET, collected data sets are usually output according to different parameters: Fixations and Saccades (Gegenfurtner et al., 2018).
+The latter describes gaze jumps, i.e., movements of both eyes, which are useful to capture new fixations (Eye-Tracking Kompetenzzentrum Schweiz, 2021).
+Significant for this scientific work and the analysis of professional perception are the fixations as well as attention areas of subjects.
+Fixations describe the period of time in which no movements are emitted by the eye (Holmquist et al.
+2011; cited in Grub et al., 2020) and are based on the eye-mind hypothesis described in the previous chapter.
+A fixation of an object can be characterized according to its duration, frequency, and distribution.
+In the illustration, the radius of a circle defines the duration of a fixation (Gegenfurtner et al., 2018).
+Based on these data can likewise be used to describe perception times, such as the time to the first fixation, to a certain object can be described.
+In order to make this time period objectively measurable make it objectively measurable, a concept developed by Tobii ProLab is used.
+In this software these organized recorded data are called Time of Interests (short TOIs), which describe time intervals of corresponding events or behaviors (Tobii Pro, 2021).
+Specifically, they are defined by the beginning and end of the corresponding event.
+
+By means of eye movement measurement, attention allocations to areas of interest or objects are made accessible in addition to pure fixations (Gegenfurtner et al., 2018).
+In research, these regions in the field of view of subjects are referred to as areas of interest (AOI) (edb.).
+They are significant in that, for the measurement of perceptual velocities of a relevant instructional event, not only TOIs but also the locations of fixations are crucial.
+Thus, it can be determined how subjects distribute their attentional resources and whether they recognize and perceive relevant events.
+
+As it is assumed that professional perception is a preferably knowledge-based process, it was Since it is assumed that professional perception is a preferably knowledge-based process, differences between experienced and inexperienced teachers have already been found.
+These were in favor of experts, as a relationship between teaching experience and associated increased knowledge acquisition is assumed (Grub et al., 2020).
+Student teachers do not have well-structured experiential knowledge due to their almost non-existent practice in everyday school life (Wolff et al., 2016).
+This causes them selection difficulties in perception and is called pedagogical knowledge gap (cf.
+Wolff et al., 2016, S.260).
+Through newly gained experiences, the professional perception of a teacher is continuously restructured and updated, and mental representation is constantly realigned accordingly (ibid.).
+This could be proven in studies in that a positive correlation of input to teaching and learning theories in studies and professional teaching perception was found (Stürmer et al., 2012).
+
+Therefore, it can be assumed that there is a relationship between teacher expertise, their visual processing, and mindfulness of classroom management (Wolff et al., 2016).
+Research has also shown that declarative knowledge acquisition, i.e., acquisition of factual knowledge, supports perceptual processes (Seidel et al., 2012; cited in Treisch, 2018, p.26).
+Accordingly, this increased knowledge acquisition would explain a positive impact on professional teaching perception.
+Among the most important prerequisites for this acquisition, Baumert and Kunter (2006) include prior knowledge and interest.
+The former is elementary for new knowledge acquisition about effective teaching and learning, as it supports processing, integration, and consolidation of it (Stürmer, 2011).
+Furthermore, it should be noted that teachers who have developed schemas through teaching experience also exhibit good professional teaching perceptions (cf.
+Sabers, 1991; cited in Treisch, 2018).
+This is explained by increased filtering mechanisms that support perceptual processes, i.e., recognition.
+Specifically, it has been shown that experienced teachers have more fixations on relevant areas because they have already learned theories on how to detect potential clutter in the classroom (Grub et al., 2020.).
+Furthermore, Expert:ins have an advantage when it comes to coding information.
+Novices have on average a longer viewing time, which is due to their still weak expertise (ibid.).
+
+### Mobile eye tracking in teaching-learning situations
+
+As explained in detail earlier, teachers face a number of challenges during teaching.
+The teacher, as organizer:in of the action, has to permanently scan the classroom for potential disruptions or possible events occurring.
+One such relevant event is classroom disruption.
+In the worst case, they force a standstill in the flow of instruction, which is naturally to be avoided.
+Lohmann (2015, p.13) describes classroom disruptions as "events that impair, interrupt, or make impossible the teaching-learning process by partially or completely overriding the conditions under which teaching and learning can first take place." However, such an event only becomes a disruption when actors:inside the classroom, perceive, interpret and finally evaluate it as disruptive (cf.
+Eckstein, Grob & Reusser, 2016; cited in, Eckstein, 2018, p.11).
+Thus, instructional disruptions are strongly dependent on perception and involve elements of production as well as reception (ibid.).
+These discipline conflicts can be divided into four categories of disruptive student behavior: Verbal disruptive behavior (chattering, heckling), lack of eagerness to learn (mental absence in the form of drawing or playing on the cell phone), physical disruptions (snapping, drumming, pen clicking), and aggressive behavior (temper tantrums, attacking people; Lohmann, 2015).
+
+In order to be able to recognize inappropriate behavior in a timely manner, the teacher must have a pronounced omnipresence, as well as pedagogical-psychological knowledge about teaching and learning processes (Cortina et al., 2018).
+These skills and competencies are reflected in how teaching situations relevant to learning are perceived and interpreted by teachers (ibid.).
+In this context, a multitude of visual attention processes occur during classroom activities.
+This simply means the attention or the conscious non-attention to visual stimuli (Rüth et al., 2020).
+This situational awareness of a teacher and the accompanying control of his or her visual attention forms the foundation of situation-specific skills (cf.
+Rüth et al.
+2020).
+These data and insights potentially to be collected form an interesting field of research and useful tool for problem-based teaching education (Cortina et al., 2018).
+In the last decade, visual input through recorded teaching situations has been preferred (ibid.).
+Subjects are thus shown an outside perspective from different points of view.
+This can happen either as self or external video and allows micro-analysis or interaction sequences through the characteristic of repeated playing of a video (ibid.).
+This characteristic makes it possible to analyze corresponding scenes more intensively and in more detail.
+This results in a potential for reflection on teaching situations in teacher education that should not be underestimated (cf.
+Rüth et al., 2020).
+
+The problem with these videotaped sequences, however, is the lack of access to the first-person perspective (ibid.).
+As a result, students usually evaluate and comment on their own videos more negatively than those of others afterwards (Cortina et al., 2018).
+They find it difficult to analyze the sequences objectively and to leave out unimportant details that concern their person.
+However, this is not purposeful and conducive to the intended learning process of the participating teachers.
+This is due to the fact that self-drawn cognition is activated in self-videos and that when negative events occur, subjects tend to defend their actions (ibid.).
+Kleinknecht and Schneider (2013) analyzed this process in more detail and found that this is particularly problematic for the reflective learning process, as it has a counterproductive effect on analyzing possible alternative actions.
+They also found that in third-party videos, reflection on potential alternative actions was twice as frequent as in self-recorded videos (ibid.)!
+In addition, recorded video sequences differ significantly from real classroom settings in which the teacher can independently determine her field of view.
+The observers cannot decide for themselves what to pay attention to and for how long to pay attention to a situation or event (Sherin, 2001).
+Based on this finding, it was significant for researchers to use an alternative elicitation technique to factor out the negative effects of self and other videos.
+A successful method to reduce this hindering factor of self-drawn cognition and still use self videos for teacher education is to use recordings that show the teacher's perspective and furthermore make it known where the teacher was looking (cf.
+Cortina et al., 2018).
+
+In MET's video material, teachers can never see their teaching through their own eyes.
+This makes it possible to focus more specifically on essential aspects, such as classroom disruptions and interactions with learners.
+Although it has not yet been clearly demonstrated that significantly less self-referential cognition was elicited, self-videos counteract over-focusing on the acting person (cf.
+Cortina et al., 2018).
+Therefore, MET represents a target-rich method for capturing teachers' attentional processes in the classroom.
+Previous studies with large data sets on teachers' visual expertise have predominantly used stationary ET (Wolff et al., 2016).
+In MET studies, the samples turn out to be much smaller; here, the largest study to be mentioned is with 12 experienced and 12 inexperienced teachers by Cortina et al.
+(2015).
+
+### Perceptions of classroom disruptions and their parameters
+
+The attentional processes of teachers in the classroom to be captured by MET are complex, as explained earlier, and are related to various parameters.
+In this context, individual personality characteristics play a central role when it comes to the perception of relevant classroom events.
+In general, it should be noted that novices have greater problems in classroom management as well as in dealing with difficult student behavior (Barth, 2017).
+Often, this is due to their late or even absent perception of classroom disruptions.
+
+However, their lack of expertise is not exclusively a reason for this phenomenon.
+Individual beliefs and convictions of teachers have a direct influence on the perception of a classroom situation and are thus independent of the experience of the teacher (Baumert & Kunter, 2006).
+Thus, in addition to teaching quality, emotions and emotional behavior of teachers can also be cited as factors.
+Individual person characteristics as well as contextual factors not only have an effect on teaching perception, but likewise on the sense of disturbance of a situation (Eckstein, 2019).
+These specific characteristics include aspects such as self-image, motivation, level of aspiration, attitudes, coping goals, and value orientations (Bakker & Demerouti, 2006; cited in Wickeren, 2019, p.
+33).
+Contextual characteristics include didactic staging or general level of disruption.
+Undesirable behavior is perceived more by teachers when the class usually displays disciplined and orderly behavior (Eckstein, 2018).
+This reference group effect is also known as the Big-Fish-Little-Pond effect.
+Thus, it can be said that teachers' perceptions of situations and people are significantly shaped by their expectations and biases (cf.
+Eckstein, 2018).
+Furthermore, how strongly a disorder is perceived and felt can depend on psychological characteristics such as self-efficacy beliefs (ibid.).
+As self-efficacy decreases, an increasing sense of disturbance could be found (ibid.).
+The aspect of the teacher-student relationship, which includes the recognition of student needs, must also be considered.
+In order to be able to adequately counteract classroom disturbances, and thus automatically reduce the sense of disturbance as well as the experience of stress, it is important to address the concerns of the learners with empathy (Wickeren, 2019).
+Regarding the factor of gender, it should be noted that previous research has found a higher level of disruptiveness in discipline problems among female teachers (Kovess-Masféty, Rios-Seidel & Sevilla-Dedieu, 2007; cited in Wickeren, 2019, p.
+33).
+
+In summary, then, the extent and perception of disruption can be attributed to individual cognitive evaluation processes, the situational context, attentional focus, didactic staging, and, indeed, professional experience (cf.
+Wickeren, 2019).
+
+# Research Questions and hypothesis
+
+This study examined how the degree of teaching experience of novice and expert teachers influences (1) the number of fixations on relevant areas, (2) the fixation duration on relevant areas and (3) the time to first fixation on relevant events (e.g., the student performing the disruption), using mobile eye-tracking data in a controlled, micro-teaching setting.
+Furthermore, the study examined the individual evaluation of classroom disruptions among experts and novices by assessing (4) how disruptive an event was and (5) how confident the subjects felt dealing with the events.
+
+Based on the existing literature, we expected expert teachers to outperform novices by (H1) showing more fixations on relevant areas with (H2) shorter fixation duration and (H3) perceiving classroom disruptions faster (cf.
+@van2014first), (H4) feeling less troubled by disruptions and (H5) more confident in dealing with disruptions (Barth, 2017), and (H6) having higher scores in strategic knowledge of classroom management (Gold et al., 2016).
+
+# Materials and Methods
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
@@
 These disruptions followed a script and coding scheme in which the actions of the class were precisely described.
-The order of the disruptions as well as the performing actors were fully balanced with Lain Square to exclude row effects.
+The order of the disruptions as well as the performing actors were fully balanced with Latin Square to exclude row effects.
 
@@
 
-The sample consists of *N* = `r length(demo.data$Group)` participants with *n* = `r length(demo.data$Group[demo.data$Group == "Expert"])` expert teachers and *n* = `r length(demo.data$Group[demo.data$Group == "Novice"])` novice teachers.
+The sample consisted of *N* = `r length(demo.data$Group)` participants with *n* = `r length(demo.data$Group[demo.data$Group == "Expert"])` expert teachers and *n* = `r length(demo.data$Group[demo.data$Group == "Novice"])` novice teachers.
 
@@
 Participation in the study was voluntary and only took place after written consent has been given.
+
+##
 

### 2022-06-30 01_studies/01_Laborstudie ProVisioNET/R script/reli/ProVisioNET_reli_reactions_JH_FP.R
update reli reaction coding

@@ -20,21 +20,21 @@ options(dplyr.summarise.inform = FALSE)
 ################## RATER 1 ################
 
 # read in data from rater1 while specifying locale allows to set "," 
-r1 <-read_excel ("./data/coding_expertise_reaction_FP.xlsx")
+r1 <-read_excel ("./data/coding_expertise_reaction_MN.xlsx", col_names = TRUE)
 
 
 ################## RATER 2 ################
 
 # read in data from rater1 while specifying locale allows to set "," 
-r2 <-read_excel ("./data/coding_expertise_reaction_JH.xlsx")
+r2 <-read_excel ("./data/coding_expertise_reaction_NT.xlsx", col_names = TRUE)
 
 
 ################## DATA WRANGLING video 01 ################
 
 # filter relevant rows and select relevant columns 
-r1 <- r1 %>% filter(`VP ID` == "02")
+r1 <- r1 %>% filter(`VP ID` == "101")
 
-r2 <- r2 %>% filter(`VP ID` == "02")
+r2 <- r2 %>% filter(`VP ID` == "101")
 
 
 # reshape data frame in long format 
@@ -58,7 +58,7 @@ r3 <- bind_cols(r1_long$Value, r2_long$Value) %>%
 agree(r3)
 
 #################### CohenKappa ##############################
-psych::cohen.kappa(x = as.matrix(r3))
+kappa <- psych::cohen.kappa(x = as.matrix(r3))
 
 
 
